### 2014-11-27 content/background.tex
changing formatting of thesis according to springer guidelines

\section{Background}\label{sec:bg}
The purpose of the correlated-calls analysis is to solve IFDS problems more precisely than using the standard IFDS algorithm by ruling out some infeasible paths. The correlated-calls analysis works by transforming an IFDS problem to an IDE problem, solving the IDE problem, and transforming the IDE result to a solution to the original IFDS problem. This section describes the general ideas underlying IFDS and IDE.

\subsection{Related Work}
IFDS is a version of the functional approach to data-flow analysis developed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}. Their algorithm is based on computing \textit{summary functions} that return the data-flow value at the end of a procedure, given the data-flow value at the start of the procedure. IFDS problems form a more restricted set of data-flow problems: unlike in the functional approach, IFDS flow functions have to be distributive, and the set of data-flow facts $D$ has to be finite. However, the IFDS algorithm is more general than Sharir's and Pnueli's algorithm in that it can handle programs containing local variables and parameters in recursive methods.

IFDS has been used to encode a variety of data-flow problems. More complex examples of applications include typestate analysis (determining which operations can be performed on an object at a given program point)~\cite{naeem2008typestate} or shape analysis (detecting errors and validating properties of programs at compile time)~\cite{DBLP:conf/birthday/KreikerRRSWY13}.

IFDS is implemented for two popular static-analysis frameworks, the T.J. Watson Libraries for Analysis (WALA)~\cite{fink2012wala} and Soot~\cite{vallee1999soot}.

WALA is a framework for static analysis on Java bytecode developed by the IBM T.J.~Watson Research Center.
In the implementation of our work, we use WALA to build and traverse the supergraph (a special kind of control-flow graph) of a Java program\footnote{However, we do not use WALA's IFDS implementation, as explained in~Section~\ref{chapter:eval}.}.

Soot is a framework for program analysis and optimization on Java bytecode, developed by the Sable Research Group at McGill University. Unlike WALA, Soot also has an implementation of the IDE algorithm. The IFDS and IDE implementations for Soot are part of the Heros project~\cite{bodden2012inter}.

Whereas one advantage of Soot's IFDS implementation (and other static analysis tools) is ease of use and extensibility, WALA's primary focus is efficiency. For example, WALA uses bit-vectors to represent some of the analysis data types, like local variables and parameters. Another difference is that WALA's intermediate representation of a program uses static single assignment (SSA) form~\cite{cytron1991efficiently}. SSA form is a representation of the program in which each variable has only one definition (assignment). SSA can make dataflow analysis simpler and more efficient~\cite{appel1998ssa}.

Work on improving the IFDS algorithm includes Practical Extensions by~N.\,Naeem and O.\,Lhot\'ak~\cite{naeem2010pei}. Their paper presents four extensions to the IFDS algorithm. Two of the extensions improve the efficiency of the IFDS analysis for certain classes of IFDS problems. Another extension widens the class of problems applicable for the IFDS analysis. However, those extensions do not affect the precision of IFDS problems. Our analysis, in contrast, does not improve the efficiency or generality of IFDS, but it allows us to solve IFDS problems more precisely.

The fourth extension is targeted towards programs that are represented in SSA form. Executing the IFDS analysis on such programs results in loss of precision in the presence of control-flow constructs (e.g. conditionals and loops), compared to programs in non-SSA form.
The extension makes the IFDS analysis on programs in SSA form as precise as on programs that are not represented in SSA form. In contrast, the correlated-calls analysis is applicable to programs in both SSA and non-SSA forms. Even if applied to a program in SSA form, our analysis and the extension improve the precision of IFDS in unrelated situations: the first analysis handles correlated calls, and the latter handles control-flow constructs. Thus, an IFDS analysis could benefit from both precision improvements independently.

Another work on improving the efficiency of the IFDS algorithm is E.\,Bodden et~al.'s framework for the analysis of software products lines~\cite{bodden2013spl}. Their paper uses transformations from IFDS to IDE problems, a technique we also employ. Finally, J.\,Rodriguez and O.\,Lhot\'ak implemented a concurrent version of the IFDS algorithm using actors~\cite{rodriguez2010concurrent}. However, neither of those works is concerned with improving the precision of IFDS results.

The correlated-calls analysis improves the precision of a data-flow analysis by eliminating a special type of infeasible paths. This is similar to the idea of context-sensitive analysis: just as a context-sensitive analysis eliminates infeasible paths from the end of a procedure to the call sites that do not match the given procedure call, the correlated-calls analysis eliminates infeasible paths caused by correlated method calls.

The idea of using correlated calls to remove infeasible paths in data-flow analyses of object-oriented programs was introduced by F.\,Tip~\cite{frank2014correlated}. The possibility of using IDE to achieve this is mentioned, but not elaborated upon. Our work presents a concrete solution to the problem and an implementation of that solution.

The idea of eliminating infeasible paths caused by correlated calls is similar to M.~Sridharan et~al.'s work on improving the precision of pointer analysis for JavaScript programs~\cite{DBLP:conf/ecoop/SridharanDCST12}. For each pointer, a pointer analysis determines the possible set of objects (the \textit{points-to} set) that the pointer can reference at a given program point. In JavaScript, it is challenging to compute the points-to set of fields because in general, field names can be derived from arbitrary expressions and bound at runtime.
As a result, an imprecise data-flow analysis will include infeasible paths between values of the form \verb'o[p]' (access of a property \verb'p' of object \verb'o'), where at compile time, \verb'p' can be bound to different values.
The idea of the paper is to track all dynamic property accesses (reads and writes) on an object \verb'o' with property name \verb'p'. The code snippets containing the references \verb'o[p]' are then extracted into a separate function $f$. The analysis is then run so that for each possible value of \verb'p', $f$ is analyzed separately; therefore, for a given property name, all correlated objects with that name are analyzed together.

The differences between this method of tracking correlated calls and our analysis are the following.
\begin{itemize}
  \item \textit{Type of target data-flow analysis} whose precision is to be improved. Our analysis improves the precision of IFDS data-flow analyses, whereas the JavaScript analysis improves the precision of pointer analysis.
  \item \textit{Target language}. Our analysis is for object-oriented languages where polymorphic methods, and not property names (which are known at compile time), cause infeasible paths.
  \item \textit{Different handling of correlated calls}. Extracting code that contains correlated calls into separate methods would not prevent infeasible paths. Instead, our analysis uses IDE flow functions to detect and eliminate infeasible paths caused by correlated calls.
\end{itemize}

\subsection{Terminology and Notation}
We will start by introducing several concepts used by the IFDS and IDE analyses.

A \textit{control-flow graph} is a directed graph in which nodes correspond to instructions and edges represent transfer of control between the instructions during an execution of the program. 
A control-flow graph has a unique start node, $\startmain$, which is the node corresponding to the program entrypoint.

An \textit{intra-procedural} path is a path in a control-flow graph whose nodes are in the same procedure. By contrast, an \textit{inter-procedural path} is one that contains nodes from different procedures.

A \textit{control-flow supergraph} is a control-flow graph
in which each procedure $p$ is augmented with an additional \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$, and for each call $c_q$ to a procedure $q$, there is a \textit{call node} \textsf{call}$_{c_q}$ and subsequent \textit{return node} \textsf{return}$_{c_q}$.

A control-flow supergraph allows us to model the control flow in inter-procedural paths.
 The flow from the caller to the callee is represented using an edge \[(\textsf{call}_{c_q},\,\textsf{start}_q)\,.\] The control flow from the callee back to the caller goes through an edge \[(\textsf{end}_q,\,\textsf{return}_{c_q})\,.\]

\begin{example}
  Consider the program in Listing~\ref{list:examplejava}. The supergraph corresponding to that program is shown in Figure~\ref{fig:examplesupergraph}.
  \begin{listing}
  \inputMinted{java}{examplesupergraph.java}
  \caption{An example Java program}
  \label{list:examplejava}  
  \end{listing}

  \begin{figure}%
  \centering
  \scalebox{.9}{
      \tikzset{
        ashadow/.style={
          opacity=.25,
          shadow xshift=0.07,
          shadow yshift=-0.07
        },
      }
    \tikzstyle{supergraph}=[
      fill=greyblue,
      rounded corners,
      font=\small,
      align=center,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_s}=[
      fill=bisque,
      rounded corners,
      font=\small,
      align=center,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_f}=[
      fill=lightsalmonpink,
      rounded corners,
      font=\small,
      align=center,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{description}=[fill=white]
\begin{tikzpicture}

% main method nodes
    \node [supergraph] (st_main) {\textsf{start}$_{\texttt{main}}$};
    \node [supergraph] (call_secret) [below = \dist of st_main.south] {\textsf{call}$_\texttt{secret}$};
    \node [supergraph] (return_secret) [below = \dist of call_secret.south] {\textsf{return}$_\texttt{secret}$\\\texttt{a = secret()}};
    \node [supergraph] (call_f_main) [below = \dist of return_secret.south] {\textsf{call}$_\texttt{A.f}$};
    \node [supergraph] (return_f_main) [below = \dist of call_f_main.south] {\textsf{return}$_\texttt{A.f}$\\\texttt{b = f(a)}};
    \node [supergraph] (end_main) [below = \dist of return_f_main.south] {\textsf{end}$_{\texttt{main}}$};
% main method edges
    \path[->] (st_main) edge (call_secret);
    \path[->] (call_secret) edge (return_secret);
    \path[->] (return_secret) edge (call_f_main);
    \path[->] (call_f_main) edge (return_f_main);
    \path[->] (return_f_main) edge (end_main);

%secret method nodes
    \node [supergraph_s] (st_secret) [above right = 2*\dist and 6*\dist of st_main] {\textsf{start}$_{\texttt{secret}}$};
    \node [supergraph_s] (return_secret_string) [below = \dist of st_secret.south] {\texttt{return "secret"}};
    \node [supergraph_s] (end_secret) [below = \dist of return_secret_string.south] {\textsf{end}$_\texttt{secret}$};
%secret method edges
    \path[dashed,->] (call_secret) edge[out=20,in=130,->] (st_secret);
    \path[->] (st_secret) edge (return_secret_string);
    \path[->] (return_secret_string) edge (end_secret);
    \path[dashed,->] (end_secret) edge[out=240,in=5] (return_secret);

%f method nodes
    \node [supergraph_f] (st_f) [below right = 2*\dist and \dist of end_secret.south] {\textsf{start}$_\texttt f$};
    \node [supergraph_f] (if) [below = \dist of st_f.south] {\texttt{if (s == null)}};
    \node [supergraph_f] (return_x) [below right = \dist and 2*\dist of if.south] {\texttt{return s}};
    \node [supergraph_f] (call_f_f) [below left = \dist and 2*\dist of if.south] {\textsf{call}$_\texttt{f}$};
    \node [supergraph_f] (return_f_f) [below = \dist of call_f_f.south] {\textsf{return}$_\texttt{f}$\\\texttt{r = f("not secret")}};
    \node [supergraph_f] (return_r) [below = \dist of return_f_f.south] {\texttt{return r}};
    \node [supergraph_f] (end_f) [below right = \dist and 2*\dist of return_r.south] {\textsf{end}$_\texttt f$};
%f method edges
    \path[dashed,->] (call_f_main) edge[out=0,in=160] (st_f);
    \draw[->] (st_f) edge (if);
    \draw[->] (if) edge [out=210,in=45] (call_f_f);
    \draw[->] (call_f_f) edge (return_f_f);
    \draw[dashed,->] (call_f_f) [out=170,in=200] edge (st_f);
    \draw[->] (return_f_f) edge (return_r);
    \draw[->] (return_r) edge [out=-80,in=175] (end_f);
    \draw[->] (if) edge [out=330,in=135] (return_x);
    \draw[->] (return_x) edge [out=270,in=10] (end_f);
    \draw[dashed,->] (end_f) edge [out=200,in=180] (return_f_f);
    \draw[dashed,->] (end_f) edge [out=215,in=-50] (return_f_main);

%arrow description
    \node [description] (intra_arrow_left) [above right = \dist and 2*\dist of st_secret] {};
    \node [description] (intra_arrow_right) [right = \dist of intra_arrow_left] {};
    \node [description] (inter_arrow_left) [below = .5*\dist of intra_arrow_left] {};
    \node [description] (inter_arrow_right) [below = .5*\dist of intra_arrow_right] {};
    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intra-procedural edge} (intra_arrow_right);
    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{inter-procedural edge} (inter_arrow_right);
\end{tikzpicture}
}
  \caption{An example supergraph for Listing~\ref{list:examplejava}}%
  \label{fig:examplesupergraph}%
  \end{figure}
\end{example}

A \textit{flow-sensitive} data-flow analysis is one that takes the order of program instructions into account.

Let each call node in a program be labeled with a distinct opening parenthesis and the corresponding return node with the matching closing parenthesis. For a given path $p$, let $s$ be the string that is obtained by concatenating the labels of the nodes in $p$.
Then $p$ is \textit{valid} if $s$ belongs to the language of substrings of balanced parentheses. The set of all inter-procedurally valid paths from the start node to a node $n$ is denoted as $\ivp(n)$. The set $\ivp(n)$ is a conservative approximation of all concrete execution paths from the start node to $n$.

A \textit{context-sensitive} data-flow analysis is an analysis that considers only inter-procedurally valid paths.

\begin{example}
  In the supergraph in Figure~\ref{fig:examplesupergraph}, let us assign $\{,\,\}$ parentheses to $\textsf{call}_\texttt{A.f}$ and $\textsf{return}_\texttt{A.f}$, and $\langle,\,\rangle$ parentheses to $\textsf{call}_\texttt{f}$ and $\textsf{return}_\texttt{f}$. 
  Then the string corresponding to the path 
  \[
    p_1=\left[\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,
          \highlight{\textsf{start}_\texttt{f}}{lightsalmonpink},\,
          \highlight{\texttt{if (s == null)}}{lightsalmonpink},\,
          \highlight{\texttt{return s}}{lightsalmonpink},\,
          \highlight{\textsf{end}_\texttt{f}}{lightsalmonpink},\,
          \highlight{\textsf{return}_\texttt{A.f}}{greyblue}
    \right]
  \]
  is $\{\}$, which indicates that $p_1$ is valid. Every prefix of $p_1$ is also a valid path.

However, the graph also contains an inter-procedurally invalid path
  \[
    p_2=\left[\highlight{\textsf{call}_\texttt{f}}{lightsalmonpink},\,
          \highlight{\textsf{start}_\texttt{f}}{lightsalmonpink},\,
          \highlight{\texttt{if (s == null)}}{lightsalmonpink},\,
          \highlight{\texttt{return s}}{lightsalmonpink},\,
          \highlight{\textsf{end}_\texttt{f}}{lightsalmonpink},\,
          \highlight{\textsf{return}_\texttt{A.f}}{greyblue}
    \right]
  \]
  with corresponding string $\langle\}$.
\end{example}

A \textit{lattice} is a partially ordered set in which each subset has a least upper bound and a greatest lower bound.

A \textit{meet semilattice} $L=(S,\,\sqcap)$ is defined by a set $S$ and a meet operation $\sqcap$ that is  associative, commutative, and idempotent.
  The meet operation induces a partial order $(S,\,\sqsubseteq)$ where every subset contains  a greatest lower bound: For all $x,\,y\in S$, $x\sqsubseteq y$ if $x\sqcap y=x$. The greatest lower bound, or top element, of the semilattice is denoted as $\top$.
  If $k$ is the length of the longest chains of elements in the semilattice, then the \textit{height} of the semilattice is~$k-1$.

Finally, we introduce the notion of \textit{distributivity}. Given a set $D$, a function $f:2^D\to2^D$ is distributive if $\forall x_1,\,x_2\in 2^D$,
\begin{equation}
  f(x_1\cup x_2)=f(x_1)\cup f(x_2).
\end{equation}

In this work, we will denote a map from a set of keys $K$ to values from set $V$ as
\begin{equation}
  \{(k,\,v)\,|\,k\in K,\,v\in V\}.
\end{equation}
For an arbitrary map $m$,  $m(x)$ is the value to which $x$ is mapped in $m$. We denote by $m[x\to y]$ a map identical to $m$, except that the element $x$ is mapped to $y$.
To avoid excessive parentheses, we write $\left(m[x_1\to y_1]\right)[x_2\to y_2]$ as $m[x_1\to y_1][x_2\to y_2]$.

We will denote the identity function $\lambda x\,.x$ by $\textsf{id}$.
We will use a typed version of this function in various contexts, where the type of $x$ will vary with
the context.

\subsection{IFDS}\label{sec:bgifds}
The purpose of the IFDS framework is to solve a special subset of inter-procedural, flow-sensitive, context-sensitive data-flow-analysis problems. The main idea of IFDS is to encode the data-flow analysis problem into a graph-reachability problem.

\subsubsection{Data-Flow Problems Suitable for IFDS}\label{sec:suitableifds}
In this section we describe the data-flow problems that can be solved by an IFDS analysis. We will start with an intuitive definition and later on formalize the notion of an IFDS-suitable problem.

Informally, an IFDS analysis can only solve decision problems. An IFDS analysis answers questions of the following kind: ``is property $X$ true at program point~$Y$?''. For example, a taint-analysis problem asks, for each variable $v$ in the program, ``is $v$ secret at a given program point?''. 
An available-expressions problem asks, for each expression $e$, ``does $e$ have to be recomputed at a given program point?''.

Formally, a data-flow analysis problem is suitable for an IFDS analysis if it can be encoded as an IFDS problem
\begin{equation}
  G^*,\,D,\,F,\,M_F,\,\sqcap)\,,
\end{equation} where $G^*=(N^*,\,E^*)$ is the supergraph of the input program with nodes $N^*$ and edges $E^*$, $D$ is a finite set of \textit{data-flow facts}, $F$ is a set of distributive dataflow functions of type $2^D\to2^D$, $M_F:\,E^*\to F$ is a function that maps supergraph edges to dataflow functions, and $M_F$ is extended to paths by composition\footnote{%
  Let $A$ be a set and $f:\,E^*\to(A\to A)$ a function from supergraph edges to functions on $A$.
  We say that $f$ is extended to  paths by composition to denote that for a path $q$ consisting of the edges $e_1,\,\dots,\,e_k$, $f(q)=f(e_k)\circ\ldots\circ f(e_1)\circ\id$.
}. The \textit{meet operator} $\sqcap$ is either union or intersection.

Without loss of generality, we will take meet to denote union. It can be shown that any problem where meet is defined as intersection can be reformulated into an equivalent one where meet is defined as union~\cite{reps1995precise}.

\subsubsection{Overview of the IFDS Algorithm}\label{sec:overviewifds}
Formally, given an IFDS problem, for each node $n\in N^*$ the IFDS algorithm computes the \textit{meet-over-all-valid-paths} solution
\begin{equation}
 \mvp{F}(n)=\bigsqcap_{q\in\ivp(n)}M_F(q)(\varnothing)\,.
\end{equation}

To compute the meet-over-all-valid-paths solution, each node in the control-flow supergraph is paired with a \textit{fact} $d\in D\cup\{\mathbf0\},\,\mathbf0\notin D$, yielding the nodes $N^\#$ of the \textit{exploded supergraph} $G^\#=(N^\#,\,E^\#)$.
Roughly, for each node in the program, a fact denotes a binary property whose value (true or false) we want to find out.
The start node of the exploded supergraph is the node $(\startmain,\,\mathbf0)$.

The flow functions $F$ define the edges of the exploded supergraph.
Using the flow functions, the IFDS algorithm computes the inter-procedurally \textit{realizable} paths from the start to the rest of the exploded graph's nodes. A realizable path is a valid path in the exploded supergraph that starts with the entry node $\startmain$.

If there is a realizable path from the node $(\startmain,\,\mathbf0)$ to a given node $(n,\,d),\,d\ne\mathbf0$, then the fact $d$ is considered to hold at node $n$. A path to a node $(n,\,\mathbf0)$ means that in the control-flow supergraph, there is a path from $\startmain$ to $n$.

In this way, the IFDS algorithm reduces the input data-flow problem to a graph-reachability problem.
\begin{example}
  In a taint analysis, $D$ is the set of variables in the program. If a fact $d\in D$ is reachable at a given node, then the variable is considered secret at that node. Otherwise, it is considered not secret. The question ``is $d$ secret at node $n$?'' becomes ``is there a realizable path from (\textsf{start}$_\texttt{main}$,\,\textbf{0}) to $(n,\,d)$?''.
\end{example}
\begin{example} 
  In an available-expressions analysis, $D$ is the set of all expressions in the program. If an expression $d\in D$ is reachable at a certain node, it means that it does not need to be recomputed at that node. 
\end{example}
\begin{example}
  The exploded supergraph for Listing~\ref{list:examplejava} is shown in Figure~\ref{fig:exampleexploded}.
  We can see that there is a realizable path
  from the start node of the exploded graph to the variable \verb'b' at~the~node~$\textsf{return}_\texttt{A.f}$ in the \verb'main' method. This means that at that node, \verb'b' is considered secret.

    \begin{figure}%
      \hspace*{-30pt}
\scalebox{.9}{
      \tikzset{
        ashadow/.style={
          opacity=.25,
          shadow xshift=0.07,
          shadow yshift=-0.07
        },
      }
    \tikzstyle{supergraph}=[
      fill=greyblue,
      rounded corners,
      font=\small,
      align=right,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_s}=[
      fill=bisque,
      rounded corners,
      font=\small,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_f}=[
      fill=lightsalmonpink,
      rounded corners,
      font=\small,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{description}=[fill=white]
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]

\begin{tikzpicture}[>=stealth,on grid, auto]

% main method nodes
    \node [supergraph] (st_main) {\textsf{start}$_{\texttt{main}}$};
    \node [supergraph] (call_secret) [below = \dist of st_main.south east, anchor=east] {\textsf{call}$_\texttt{secret}$};
    \node [supergraph] (return_secret) [below = \dist of call_secret.south east,anchor=east] {\textsf{return}$_\texttt{secret}$\\\texttt{a = secret()}};
    \node [supergraph] (call_f_main) [below = \dist of return_secret.south east, anchor=east] {\textsf{call}$_\texttt{A.f}$};
    \node [supergraph] (return_f_main) [below = \dist of call_f_main.south east, anchor=east] {\textsf{return}$_\texttt{A.f}$\\\texttt{b = f(a)}};
    \node [supergraph] (end_main) [below = \dist of return_f_main.south east, anchor=east] {\textsf{end}$_{\texttt{main}}$};

    \node [n,label=$\mathbf{0}$] (st_main_z) [right=\ndd of st_main.east] {};
    \node [n,label=\texttt{a}] (st_main_x) [right=\ndd of st_main_z] {};
    \node [n,label=\texttt{b}] (st_main_y) [right=\ndd of st_main_x] {};

    \node [n] (call_secret_z) [right=\ndd of call_secret.east] {};
    \node [n] (call_secret_x) [right=\ndd of call_secret_z] {};
    \node [n] (call_secret_y) [right=\ndd of call_secret_x] {};

    \node [n] (return_secret_z) [right=\ndd of return_secret.east] {};
    \node [n] (return_secret_x) [right=\ndd of return_secret_z] {};
    \node [n] (return_secret_y) [right=\ndd of return_secret_x] {};

    \node [n] (call_f_main_z) [right=\ndd of call_f_main.east] {};
    \node [n] (call_f_main_x) [right=\ndd of call_f_main_z] {};
    \node [n] (call_f_main_y) [right=\ndd of call_f_main_x] {};

    \node [n] (return_f_main_z) [right=\ndd of return_f_main.east] {};
    \node [n] (return_f_main_x) [right=\ndd of return_f_main_z] {};
    \node [n] (return_f_main_y) [right=\ndd of return_f_main_x] {};

    \node [n] (end_main_z) [right=\ndd of end_main.east] {};
    \node [n] (end_main_x) [right=\ndd of end_main_z] {};
    \node [n] (end_main_y) [right=\ndd of end_main_x] {};
% main method edges
    \path[->](st_main_z) edge (call_secret_z);
    \path[->](call_secret_z) edge (return_secret_z);
    \path[->](return_secret_z) edge (call_f_main_z);
    \path[->](call_f_main_z) edge (return_f_main_z);
    \path[->](return_f_main_z) edge (end_main_z);  
    \path[->](return_f_main_y) edge (end_main_y);

%secret method nodes
    \node [supergraph_s] (st_secret) [above right = 2*\dist and 6*\dist of st_main] {\textsf{start}$_{\texttt{secret}}$};
    \node [supergraph_s] (return_secret_string) [below = \dist of st_secret.south west, anchor=west] {\texttt{return "secret"}};
    \node [supergraph_s] (end_secret) [below = \dist of return_secret_string.south west,anchor = west] {\textsf{end}$_\texttt{secret}$};

    \node [n,label=$\mathbf{0}$] (st_secret_z) [left=\ndd of st_secret.west] {};
    \node [n] (return_secret_string_z) [left=\ndd of return_secret_string.west] {};
    \node [n] (end_secret_z) [left=\ndd of end_secret.west] {};
%secret method edges
    \path[->](st_secret_z) edge (return_secret_string_z); 
    \path[->](return_secret_string_z) edge (end_secret_z); 
    \path[->,dashed](call_secret_z) edge [out=30,in=180] (st_secret_z);
    \path[->,dashed](end_secret_z) edge [out=240,in=40] (return_secret_z);
    \path[->,dashed](end_secret_z) edge [out=260,in=30] (return_secret_x);
    \path[->](return_secret_x) edge (call_f_main_x);
    \path[->](call_f_main_x) edge (return_f_main_x);
    \path[->](return_f_main_x) edge (end_main_x);

%f method nodes
    \node [supergraph_f] (st_f) [below=2*\dist of end_secret.south west,anchor=west] {\textsf{start}$_\texttt f$};
    \node [supergraph_f] (if) [below = \dist of st_f.south west,anchor=west] {\texttt{if (s == null)}};
    \node [supergraph_f] (return_x) [below right = \dist and 2.5*\dist of if.south] {\texttt{return s}};
    \node [supergraph_f] (call_f_f) [below=\dist of if.south west,anchor=west] {\textsf{call}$_\texttt{f}$};
    \node [supergraph_f] (return_f_f) [below = \dist of call_f_f.south west,anchor=west] {\textsf{return}$_\texttt{f}$\\\texttt{r = f("not secret")}};
    \node [supergraph_f] (return_r) [below = \dist of return_f_f.south west,anchor=west] {\texttt{return r}};
    \node [supergraph_f] (end_f) [below=\dist of return_r.south west,anchor=west] {\textsf{end}$_\texttt f$};

     \node [n,label=\texttt{s}] (st_f_s) [left=\ndd of st_f.west] {}; 
     \node [n,label=\texttt{r}] (st_f_r) [left=\ndd of st_f_s] {};
     \node [n,label=$\mathbf{0}$] (st_f_z) [left=\ndd of st_f_r] {};

     \node [n] (if_s) [left=\ndd of if.west] {};
     \node [n] (if_r) [left=\ndd of if_s] {};
     \node [n] (if_z) [left=\ndd of if_r] {};

     \node [n] (call_f_f_s) [left=\ndd of call_f_f.west] {};
     \node [n] (call_f_f_r) [left=\ndd of call_f_f_s] {};
     \node [n] (call_f_f_z) [left=\ndd of call_f_f_r] {};

     \node [n] (return_f_f_s) [left=\ndd of return_f_f.west] {};
     \node [n] (return_f_f_r) [left=\ndd of return_f_f_s] {};
     \node [n] (return_f_f_z) [left=\ndd of return_f_f_r] {};

     \node [n] (return_r_s) [left=\ndd of return_r.west] {};
     \node [n] (return_r_r) [left=\ndd of return_r_s] {};
     \node [n] (return_r_z) [left=\ndd of return_r_r] {};

     \node [n] (end_f_s) [left=\ndd of end_f.west] {};
     \node [n] (end_f_r) [left=\ndd of end_f_s] {};
     \node [n] (end_f_z) [left=\ndd of end_f_r] {};

     \node [n,label=$\mathbf0$] (return_x_z) [right=\ndd of return_x.east] {};
     \node [n,label=\texttt{r}] (return_x_r) [right=\ndd of return_x_z] {};
     \node [n,label=\texttt{s}] (return_x_s) [right=\ndd of return_x_r] {};
%f method edges
    \path[->](st_f_z) edge (if_z);
    \path[->](if_z) edge (call_f_f_z);
    \path[->](call_f_f_z) edge (return_r_z);  
    \path[->](return_r_z) edge (end_f_z);
    \path[->](if_z) edge [out=-43,in=127] (return_x_z);
    \path[->](return_x_z) edge [out=270,in=25] (end_f_z);
    \path[->](st_f_s) edge (if_s);
    \path[->](if_s) edge (call_f_f_s);
    \path[->](call_f_f_s) edge (return_r_s);  
    \path[->](return_r_s) edge (end_f_s);
    \path[->](if_s) edge [out=-30,in=110] (return_x_s);
    \path[->](return_x_s) edge [out=270,in=25] (end_f_s);
    \path[->](return_f_f_r) edge (return_r_r);
    \path[->](return_r_r) edge (end_f_r);
    \path[->,dashed](call_f_main_z) edge [out=20,in=160] (st_f_z);
    \path[->,dashed](end_f_z) edge [out=150,in=-20] (return_f_main_z);
    \path[->,dashed](call_f_f_z) edge [out=110,in=250] (st_f_z);
    \path[->,dashed](end_f_z) edge [out=110,in=250] (return_f_f_z);
    \path[->,dashed](call_f_main_x) edge [out=32,in=112] (st_f_s);
    \path[->,dashed](end_f_s) edge [out=155,in=-40] (return_f_main_y);
    \path[->,dashed](end_f_s) edge [out=120,in=-50] (return_f_f_r);
    \path[->,dashed](end_f_r) edge [out=110,in=250] (return_f_f_r);
    \path[->,dashed](end_f_r) edge [out=150,in=-50] (return_f_main_y);
\end{tikzpicture}
}
  \caption{The exploded supergraph corresponding to a taint analysis for the input program in Listing~\ref{list:examplejava}}%
  \label{fig:exampleexploded}%
  \end{figure}
\end{example}

%\subsubsection{Flow Functions}\label{sec:flowfunifds}
The flow functions $F\subseteq 2^D\to2^D$ allow us to establish the edges in the exploded supergraph.

Given a control-flow-graph edge $e=(n_1,\,n_2)\in E^*$ and a distributive dataflow function $f=M(e)$, the \textit{representation relation} $R_f:\,(D\cup\{\mathbf0\})\times (D\cup\{\mathbf0\})$ of $f$ is defined as
\[
  R_f=\{(\mathbf0,\,\mathbf0)\}\cup
      \{(\mathbf0,\,d_j)\,|\,d_j\in f(\varnothing)\}\cup
      \{(d_i,\,d_j)\,|\,d_j\in f(\{d_i\}),\,d_j\notin f(\varnothing)\}.
\]
Each pair $(d_i,\,d_j)\in R_f$ corresponds to an edge $((n_1,\,d_i),\,(n_2,\,d_j))$ in the exploded supergraph.

Note that $R_f$ constructs pairs of dataflow facts so that
\begin{itemize}
  \item there is always an edge $(\mathbf0,\,\mathbf0)$ corresponding to the control-flow-graph edge;
  \item if there is an edge $(\mathbf0,\,d_j)$, then there is no other edge leading to $d_j$; in particular, there is never an edge $(d_i,\,\mathbf0)$ where $d_i\ne\mathbf0$.
\end{itemize}

\begin{example}\label{ex:flowfun}
  The representation relation $R_f$ for a set of data-flow facts $D=\{u,\,v,\,w\}$ and dataflow function $f=\lambda S\,.\,S\setminus\{v\}\cup\{u\}$ looks as follows:
  \[
    R_f=\{(\mathbf0,\,\mathbf0),\,(\mathbf0,\,u),\,(w,\,w)\}.
  \]

The corresponding exploded-graph edges are shown below.
   \begin{center}
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
\begin{tikzpicture}[>=stealth,on grid, auto]
    \node [n,label=$\mathbf{0}$] (zero){};
    \node [n,] (zero_) [below=\edge of zero] {};
    \node [n,label=$u$] (u) [right=\nd of zero] {};
    \node [n,] (u_) [below=\edge of u] {};
    \node [n,label=$v$] (v) [right=\nd of u] {};
    \node [n,] (v_) [below=\edge of v] {};
    \node [n,label=$w$] (w) [right=\nd of v] {};
    \node [n,] (w_) [below=\edge of w] {};
    \path[->](zero) edge (zero_);
    \path[->](zero) edge (u_);
    \path[->](w) edge (w_);
  \end{tikzpicture}
  \end{center}
\end{example}

The representation relation lets us decompose a flow function into functions that operate on each fact individually. This is possible due to distributivity: we can apply the flow function on each single fact and take the union of the results, rather than applying the function to the union of the facts.

The representation relation allows us to compactly represent the composition and meet operations which are required for the IFDS algorithm.

For two representation relations $R_{f_1},\,R_{f_2}$, the composition and meet operations are defined as follows:
\begin{align}
  R_{f_1}\circ R_{f_2}&=\{(d_1,\,d_3)\ |\ \exists d_2:\ (d_1,\,d_2)\in R_{f_1},\,(d_2,\,d_3)\in R_{f_2}\}\,.
\intertext{and}
  R_{f_1}\sqcap R_{f_2}&=R_{f_1}\cup R_{f_2}\,.
\end{align}

The representation relation distributes over composition and meet:
\begin{align}
  R_{f_1}\circ R_{f_2}=R_{f_1\circ f_2}\,,
\intertext{and}
  R_{f_1}\sqcap R_{f_2}=R_{f_1\sqcap f_2}\,.
\end{align}

On the exploded graph, the composition of two functions is represented by the paths that are formed when the exploded-graph edges are combined.

\begin{example}
  If $g=\lambda S\,.\,S\setminus\{w\}$ and $f$ is defined as in example~\ref{ex:flowfun}, then
  \[
    R_f\circ R_g=\{(\mathbf0,\,\mathbf0),\,(\mathbf0,\,u)\},
  \]
  as illustrated by the corresponding exploded graph edges:
    \begin{center}
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
\begin{tikzpicture}[>=stealth,on grid, auto]
    \node [n,label=$\mathbf{0}$] (zero){};
    \node [n] (zero_) [below=\edge of zero] {};
    \node [n,label=$u$] (u) [right=\nd of zero] {};
    \node [n] (u_) [below=\edge of u] {};
    \node [n,label=$v$] (v) [right=\nd of u] {};
    \node [n] (v_) [below=\edge of v] {};
    \node [n,label=$w$] (w) [right=\nd of v] {};
    \node [n] (w_) [below=\edge of w] {};
    \node [n] (zero__) [below=\edge of zero_] {};
    \node [n] (u__) [below=\edge of u_] {};
    \node [n] (v__) [below=\edge of v_] {};
    \node [n] (w__) [below=\edge of w_] {};

    \path[->](zero) edge node[left] {$R_f$} (zero_);
    \path[->](zero) edge (u_);
    \path[->](w) edge (w_);
    \path[->](zero_) edge node[left] {$R_g$} (zero__);
    \path[->](u_) edge (u__);
    \path[->](v_) edge (v__);

    \node [n,label=$\mathbf{0}$] (zeroC) [below right= .5\edge and 3.5\dist of w] {};
    \node [n] (zeroC_) [below=\edge of zeroC] {};
    \node [n,label=$u$] (uC) [right=\nd of zeroC] {};
    \node [n] (uC_) [below=\edge of uC] {};
    \node [n,label=$v$] (vC) [right=\nd of uC] {};
    \node [n] (vC_) [below=\edge of vC] {};
    \node [n,label=$w$] (wC) [right=\nd of vC] {};
    \node [n] (wC_) [below=\edge of wC] {};

    \path[->](zeroC) edge node[left] {$R_f\circ R_g$} (zeroC_);
    \path[->](zeroC) edge (uC_);
  \end{tikzpicture}
  \end{center}
\end{example}

To convert a representation relation $R_f$ back into the original flow function $f$, we can use the \textit{interpretation} function $\denote {R_f}$:
\begin{align}
  f&=\denote{R_f}\notag\\
  &=\lambda D_1\,.\,\left(\left\{d_2\ |\ \exists d_1\in D_1:\,(d_1,\,d_2)\in R_f\right\}\cup\{d_2\ |\ (\mathbf0,\,d_2)\in R_f\}\right)
  \setminus\{\mathbf0\}\,.
\end{align}

We presented an overview of the IFDS analysis. IFDS problems are transformed into IDE problems by the correlated-calls analysis. The IDE analysis is described in the next section.

\subsection{IDE}\label{sec:bgide}
There exists an entire class of data-flow problems that cannot be formulated as IFDS problems. Informally, the problems cannot be formulated as decision problems. For instance, a constant-propagation problem asks, for each variable $v$ in the program, ``if $v$ is a constant at a given program point, what is $v$'s value?''.
The questions asked by constant propagation are of the form ``if property $X$ \textit{($v$ being a constant)} is true at program point~$Y$, what is the value of some property~$Z$ \textit{(the value of the constant)} corresponding to~$X$?''. It turns out that problems with such questions can often be solved by the IDE algorithm.

Instead of just telling us whether a fact holds or not, the IDE analysis can provide us with additional information about facts.

Just as in the IFDS analysis, the IDE algorithm reduces a data-flow problem to a graph-reachability problem. Additionally, for each program point, the algorithm computes an \textit{environment} $\textsf{Env}(D,\,L)$, where data-flow facts are mapped to values of a lattice $L$.

For example, using the IDE analysis, we can encode a restricted version of a constant-propagation analysis\footnote{%
  In the general case, constant propagation cannot be encoded with distributive flow functions and is therefore not suitable for an IDE analysis~\cite{muller2001complexity}.
}. The data-flow facts  correspond to program variables, and the lattice incorporates all possible values for constants. 
If a fact $d$ in the exploded supergraph is reachable at node $n$, and $\textsf{Env}(d)\notin\{\bot,\,\top\}$, it means that the variable associated with $d$ is a constant. Furthermore, the value of the constant can be inferred from the environment for the corresponding node and is equal to $\textsf{Env}(d)$.

Formally, an IDE problem is defined as a four-tuple
\begin{equation}
  (G^*,\,D,\,L,\,M_\textsf{Env})\,,
\end{equation}
where $G^*$ is a control-flow supergraph, $D$ is a set of data-flow facts, and $L$ is a meet semilattice
with finite height. 
Finally, $M_\textsf{Env}:\,E^*\to(\textsf{Env}(D,\,L)\to \textsf{Env}(D,\,L))$ is a function from the edges of the control-flow supergraph to distributive \textit{environment transformers}. $M_\textsf{Env}$ is extended to paths by composition.

Given an IDE problem, for each node $n\in N^*$ and fact $d\in D$, the IDE algorithm computes the meet-over-all-valid-paths solution
\begin{equation}\label{eq:mvpdef}
  \mvp{\textsf{Env}}(n,\,d)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\Omega)(d)\,,
\end{equation}
where $M_\textsf{Env}$ is extended to paths by composition and
\begin{equation}
  \Omega=\lambda d\,.\,\top
\end{equation}
is the top element in the environment lattice~$\mathsf{Env}(D,\,L)$.

The IDE analysis is a generalization of the IFDS analysis: every IFDS problem can be converted into an equivalent IDE problem~\cite{reps1995precise}. The equivalent problem can be solved by the IDE algorithm, and the result converted into an IFDS result. In~an~IFDS-equivalent IDE problem, the~graph~$G^*$ and the~set~$D$ of~data-flow facts remain the~same. The $L$ lattice is a two-point lattice: if a fact is mapped to the top (bottom) element, then it is reachable (unreachable). The conversion between IFDS and IDE problems is discussed in detail in Section~\ref{seq:transIfdsIde}.

\subsubsection{Environment Transformers}
For each node in the control-flow graph, the result of an IDE analysis computes an environment $\textsf{Env}(D,\,L)$, which is a map from data-flow facts to lattice elements.

Instead of flow functions that show how to propagate facts, the IDE framework uses distributive environment transformers to propagate environments. For each edge $(n_1,\,n_2)$ in the control-flow supergraph, an environment transformer indicates how the environment at node $n_1$ is modified at node $n_2$.

From Section~\ref{sec:overviewifds} we know that flow functions can be represented with exploded-graph edges. To represent environment transformers, we will construct \textit{labeled} exploded-graph edges, where each edge is associated with a distributive \textit{micro function}%
\footnote{See~Sagiv et al.~\cite{sagiv1996precise} for a formal definition of the representation relation for environment transformers.}
$f:\,L\to L$. A~micro function shows how to change a lattice element for a given node and fact.

If an IDE problem is equivalent to an IFDS problem, the edges of the exploded supergraph are the same for both problems. In the IDE problem, the edges of the exploded supergraph are labeled with identity micro functions.

We extend the meet operator to work on micro functions by defining
\begin{equation}
  (f_1\sqcap f_2)(l)=f_1(l)\sqcap f_2(l)
\end{equation}
for all $l\in L$.

In IDE problems, the auxiliary fact analogous to $\mathbf0$ in IFDS is denoted as $\Lambda$.

\begin{example}\label{ex:constprop}
  One version of the constant propagation analysis that can be encoded with IDE is \textit{linear constant propagation}. A linear constant propagation analysis can detect constants of the form $a\cdot x+b$, where $a$ and $b$ are integers and $x$ is a variable. In particular, a variable can only be considered constant if it depends on at most one other constant variable: even if $y$ and $z$ are variables that are considered constant, the variable $x=y+z$ will be considered not constant. If we encoded the analysis in a way to handle non-linear constant assignments, we would have to use non-distributive flow functions, which would violate the requirements of the IDE algorithm.

  For linear constant propagation, the $L$ lattice consists of the set of integers $\mathbb Z$, a top element denoting ``not a constant'', and a bottom element denoting an unknown value.
  The meet of two lattice elements is defined as follows: for any lattice element $l\in L$,
  \[
    \top\sqcap l=\top\qquad\text{and}\qquad\bot\sqcap l=l.
  \]
  For two lattice elements $l_1,\,l_2\in\mathbb Z$, $$l_1\sqcap l_2=\top.$$

  We define the addition and multiplication operations on lattice elements $l\in L$ and integers $c\in\mathbb Z$ as follows:
  \[
    l+c=\begin{cases}
      \bot&\text{if }l=\bot;\\
      \top&\text{if }l=\top;\\
      l+c&\text{otherwise.}
    \end{cases}
    \qquad
    c\cdot l=\begin{cases}
      \bot&\text{if }l=\bot;\\
      \top&\text{if }l=\top;\\
      c\cdot l&\text{otherwise.}
    \end{cases}
  \]
   Let the function $M$ that maps supergraph edges to environment transformers be defined in the following way:
  \[
    M=\lambda((n_1,\,n_2))\,.\,
    \begin{cases}
      \lambda\textsf{env}\,.\,\textsf{env}[x\to a\cdot\textsf{env}(y)+c\,]
        &\text{if $n_1$ contains an assignment}\\&\text{$x=a\cdot y+c$, where $y$ is a variable}\\&\text{and $a,\,c$ are constants;}\\
      \id
        &\text{otherwise.}
    \end{cases}
  \]
  Here, we denote with $\textsf{env}[x\to a]$ an environment \textsf{env} in which the key $x$ is mapped to $a$, and all other keys $y\ne x$ are mapped to their old values $\textsf{env}(y)$.
  When $M$ is applied to an edge whose source node contains an assignment for a variable $x$, $M$ returns an environment transformer that updates the argument environment with a new value for $x$.

  Consider the following program:
\inputMinted{java}{constprop.java}
  For the edges $e_1,\,e_2,\,e_3$, and $e_4$ that start at the first, second, third, and fourth instruction, $M$ creates the following environment transformers:
  \begin{align*}
    M(e_1)
    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt u\to 1]\\
    M(e_2)
    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt v\to\textsf{env}(\texttt u)+2]\\
    M(e_3)
    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt w\to\top]\\
    M(e_4)
    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt u\to 5].
  \end{align*}

  The corresponding labeled exploded supergraph is shown in Figure~\ref{fig:constprop}.

  The result of the analysis yields a map from nodes to environments. Each environment maps variables to elements of the constant-propagation lattice. The environment at the last node will look as follows:
  \[
    \{(\texttt u,\,5),\ (\texttt v,\,3),\ (\texttt w,\,\top)\}.
  \]
\end{example}
\begin{figure}
  \centering
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt,sm]
    \tikzstyle{sm}=[font=\footnotesize]
\begin{tikzpicture}[>=stealth,on grid, auto]
    \node [n,label=$\Lambda$] (zero){};
    \node [n] (zero_) [below=\edge of zero] {};
    \node [n,label={\texttt u}] (u) [right=\dist of zero] {};
    \node [n] (u_) [below=\edge of u] {};
    \node [n,label={\texttt v}] (v) [right=\dist of u] {};
    \node [n] (v_) [below=\edge of v] {};
    \node [n,label=\texttt{w}] (w) [right=\dist of v] {};
    \node [n] (w_) [below=\edge of w] {};
    \node [n] (zero__) [below=\edge of zero_]{};
    \node [n] (u__) [below=\edge of u_]{};
    \node [n] (v__) [below=\edge of v_]{};
    \node [n] (w__) [below=\edge of w_]{};
    \node [n] (zero___) [below=\edge of zero__]{};
    \node [n] (u___) [below=\edge of u__]{};
    \node [n] (v___) [below=\edge of v__)]{};
    \node [n] (w___) [below=\edge of w__]{};  
    \node [n] (zero____) [below=\edge of zero___]{};
    \node [n] (u____) [below=\edge of u___]{};
    \node [n] (v____) [below=\edge of v___)]{};
    \node [n] (w____) [below=\edge of w___]{};

    \path[->](zero) edge node[left,sm]{$\id$} (zero_);
    \path[->](zero) edge node[right,sm]{$\lambda l.1$} (u_);
    \path[->](zero_) edge node[left,sm]{$\id$} (zero__);
    \path[->](u_) edge node[right,sm]{$\lambda l.l+2$} (v__);
    \path[->](u_) edge node[left,sm]{$\id$} (u__);
    \path[->](zero__) edge node[left,sm]{$\id$} (zero___);
    \path[->](u__) edge node[left,sm]{$\id$} (u___);
    \path[->](v__) edge node[left,sm]{$\id$} (v___);

    \path[->,dashed,color=gray](v) edge node[left,sm]{$\id$} (v_);
    \path[->,dashed,color=gray](w) edge node[left,sm]{$\id$} (w_);
    \path[->,dashed,color=gray](w_) edge node[right,sm]{$\id$} (w__);

    \path[->] (zero___) edge node[left,sm]{$\id$} (zero____);
    \path[->] (u___) edge node[left,sm]{$\lambda l.5$} (u____);
    \path[->] (v___) edge node[left,sm]{$\id$} (v____);
    \path[->,dashed,color=gray] (w___) edge node[left,sm]{$\id$} (w____);
  \end{tikzpicture}
  \caption[A labeled exploded supergraph for a constant-propagation analysis described in Example~\ref{ex:constprop}]{A labeled exploded supergraph for a constant-propagation analysis described in Example~\ref{ex:constprop}. The dashed edges are edges not reachable from the entry node.}%
  \label{fig:constprop}%
  \end{figure}

In this way, each edge in the exploded graph is labeled with a micro function. The mapping from exploded-graph edges to the corresponding micro functions is stored in \textit{edge functions},  denoted as \textsf{EdgeFn}$:\,E^\#\to(L\to L)$.

\subsubsection{Overview of the IDE Algorithm}\label{sec:ideoverview}
Given a labeled exploded supergraph, the IDE algorithm computes the environments for all nodes in the control-flow graph.

The algorithm first computes the lattice elements $l_{n,\,d}$ that correspond to each reachable node $(n,\,d)$ in the exploded supergraph. The union of the exploded nodes $(n,\,d)$ for a given control-flow node $n$, mapped to the corresponding lattice elements $l_{n,\,d}$, form the environment $\textsf{Env}_n$  for that node:
\begin{equation}
  \textsf{Env}_n=\left\{(d,\,l_{n,\,d})\ |\ (n,\,d)\in N^\#\right\}\,.
\end{equation}

The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each inter-procedurally realizable path
\[
  p=\left[(\startmain,\,\Lambda),\,(n_1,\,d_1),\,\dots,\,(n_k,\,d_k)\right]
\]
 that starts with the entrypoint of the exploded supergraph, we compute the function $f_p$ that corresponds to $p$. The micro function consists of the composition of all individual micro functions with which the edges of $p$ are labeled:
\begin{align}
  f_p=\textsf{EdgeFn}((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))\,\circ\ldots\circ
      \textsf{EdgeFn}(\startmain,\,\Lambda),\,(n_1,\,d_1))\,.
\end{align}

Let the lattice element that $(n,\,d)$ is mapped to according to path $p$ be denoted as $l_{n,\,d}^p$. As shown in~Sagiv et al.~\cite{sagiv1996precise}, the lattice element can be obtained by applying $f_p$ to the bottom element:
\begin{equation}
 l^p_{n,\,d}=f_p(\bot)\,.
\end{equation}

Let $Q$ be the set of paths that start at the entry point and end at the given node $(n,\,d)$.

The lattice element $l_{n,\,d}$ is the meet of the lattice elements corresponding to all the paths in $Q$:
\[
  l_{n,\,d}=\bigsqcap_{q\in Q}l^q_{n,\,d}\,.
\]

This is a general outline of the IDE analysis. We use the IDE framework to improve the precision of IFDS problems in the presence of correlated calls.
The next section describes how this is done.

### 2014-11-27 content/concl.tex
changing formatting of thesis according to springer guidelines

\section{Conclusions}\label{chapter:concl}
We presented a technique to improve the precision of solutions to IFDS problems in the presence of correlated calls. Correlated calls occur when there are multiple polymorphic method invocations on the same receiver. Such method calls cause a data-flow analysis to consider infeasible paths, which makes the data-flow analysis less precise.

Our method of eliminating infeasible paths caused by correlated calls works by transforming an existing IFDS problem into a specialized IDE problem. In this way, we are able to track the classes to which method invocations get dispatched. After solving the specialized IDE problem, we convert its result into an IFDS result that is potentially more precise than the solution to the original IFDS problem. The increase in precision can occur for programs that contain correlated calls. Specifically, if, on a certain data-flow path, there are two polymorphic method invocations on the same receiver that dispatch to incompatible classes, the IDE analysis will consider the path infeasible.

We proved that the correlated-calls analysis is sound and that it improves the precision of IFDS results.

Our Scala implementation of the correlated-calls analysis includes
\begin{itemize}
  \item an implementation of the IDE analysis, which is based on the WALA static program analysis framework;
  \item a taint-analysis implementation as an IFDS problem instance;
  \item a transformer of IFDS problems to equivalent IDE problems, and a second transformer that accounts for correlated calls.
\end{itemize}

We tested the correlated-calls analysis on our taint analysis implementation by comparing the number of secret values that were leaked when using an IFDS taint analysis and a taint analysis that accounts for correlated calls. We used the Dacapo benchmarks as input programs. Although the benchmarks contained a number of correlated calls, we were not able to improve the precision of the taint analysis, because the correlated calls did not occur on paths of secret information leaks.

We are hopeful that other analyses can benefit from the extra information provided by the correlated-calls analysis, and plan to test this hypothesis in the future.

### 2014-11-27 content/datastr.tex
changing formatting of thesis according to springer guidelines

\section{Correlated Calls Representations}\label{sec:ccdatastr}

In order to define a correlated-calls transformation, we need to represent 
 lattice elements $\lcc_\rcc:\ \rcc\to 2^T$ of the target IDE problem, which are functions from receivers to sets of types,
and micro functions $\lcc_\rcc\to\lcc_\rcc$.

As defined in~Sagiv et al.~\cite{sagiv1996precise}, a representation of micro functions is efficient if the following conditions hold:
\begin{enumerate}
	\item There is a representation for the identity and top functions.
  \item The representation is closed under the meet and composition operations.
  \item The micro functions form a finite-height lattice.
  \item The apply, meet, composition, and equality-check operations can be computed in constant time.
  \item There is a constant bound on the storage space for a micro function representation.
\end{enumerate}

We will distinguish the representation of a concept from its denotation. For a concept $c$, we will write $\denote c$ for its denotation and just $c$ for its representation. For example, if we want to represent a constant function $g$ with the constant value $v$ that it returns, we will write for $g$'s representation, $g=v$, and for $g$'s denotation, $\denote g=\lambda x\,.\,v$.

\subsection{Lattice Elements}Elements of the $\lcc_\rcc$ lattice can be represented with a map from receivers to sets of types. The bottom element maps each receiver to the set~$T$ of all types:
\begin{align}
  \botcc&=\left\{(r,\,T)\ |\ r\in \rcc\right\}
\intertext{and the top element maps each receiver to the empty set:}
  \topcc&=\left\{(r,\,\varnothing)\ |\ r\in \rcc\right\}.
\end{align}

\subsection{Micro Functions}
In the context of the correlated-calls transformation to an IDE problem, a lattice element is a map from receivers to sets of types. Thus, a micro function transforms, or updates, an existing receiver-to-types map with new information about the types of a receiver.

We will represent micro functions with \textit{update maps} which we describe in the next section.

\subsubsection{Update Maps}
To represent micro functions that transform maps from receivers to sets of types, we use \textit{update maps}. To define update maps, we first introduce the notions of \textit{update functions} and \textit{normalization}.

Let $f$ be a micro function, $r\in\rcc$ a correlated-call receiver, and $T$ the set of types in a program.

\begin{definition}
  A non-normalized update function $\updfun f^*$ is a pair of sets
  \begin{equation}
    \updfun f^*=\setpair{I_{f,\,r}}{U_{f,\,r}},
  \end{equation}
  where $I_{f,\,r}\subseteq T$ is called the intersection set and $U_{f,\,r}\subseteq T$ the union set of the update function.
\end{definition}

\begin{definition}
  Let $\setpair IU$ be a pair of sets. The normalization function $\mathcal N$ is defined as
    \begin{equation}
        \mathcal N(\setpair I U)=\setpair{I\cup U} U.
    \end{equation}
\end{definition}

\begin{definition}\label{def:updfun}
  An update function $\updfun f$ is a normalized pair of sets
  \begin{equation}
    \updfun f=\mathcal N(\updfun f^*)=\mathcal N(\setpair{I_{f,\,r}}{U_{f,\,r}})\,.
  \end{equation}
\end{definition}

\begin{definition}
  The update map of $f$ is a map from receivers to update functions:
  \begin{equation}
    \updmap f=\{(r,\,\updfun f)\,|\,r\in\rcc\}\,.
  \end{equation}
\end{definition}
Thus, each micro function $f$ is represented with an update map:
\begin{equation}
  f=\denote{\updmap f}.
\end{equation}

\subsubsection{Denotation of Update Maps}
Intuitively, the meaning of a micro function is the update that it performs on a receiver-to-types map. To represent a micro function, it is enough to specify how the set of types for a given receiver has to be transformed. This is what the update map does.

For a micro function $f$, an update map takes a receiver and returns an update function:
\begin{equation}
  \denote{\updmap f}=\lambda r\,.\,\denote{\updfun f}.
\end{equation}

Given a micro function $f:(\rcc\to 2^T)\to(\rcc\to2^T)$, an update map is defined so that
\begin{equation}
    f(m)=\left\{\left(r,\,\denote{\updmap f}(r)(m(r)\right)\ |\ r\in\rcc\right\},
\end{equation}
where the update map $\denote{\updmap f}$ has type $\rcc\to(2^T\to2^T)$, and the update function  $\denote{\updfun f}=\denote{\updmap f}(r)$ has type $2^T\to2^T$.

For any receiver-to-types map $m$, an update function specifies two things:
\begin{itemize}
    \item which elements of $m(r)$ should be preserved, and 
    \item which new elements should be added to $m(r)$.
\end{itemize}
This can be achieved by maintaining  the intersection $I_{f,\,r}$ and union set $U_{f,\,r}$, where
\begin{equation}
    \denote{\updfun f}(m(r))=(m(r)\cap I_{f,\,r})\cup U_{f,\,r}\,.
\end{equation}

However, as we will see in Section~\ref{sec:equality}, we need to be able to check update functions for equality, which is difficult to do with non-normalized update functions.

\begin{example}
 For a non-empty set of types $T$, consider two update functions
 $$u_1=\setpair T T$$ 
and 
$$u_2=\setpair\varnothing T.$$
The denotations of the functions look as follows:
$$\denote{u_1}=\lambda t\,.\,(t\cap T)\cup T$$ and $$\denote{u_2}=\lambda t\,.\,(t\cap\varnothing)\cup T\,.$$
We can see that both $\denote{u_1}$ and $\denote{u_2}$ are equal to the function $\lambda t\,.\,T$.

Therefore, the same function can have more than one non-normalized representation. This means that to check two functions for equality, it is not enough to compare their non-normalized representations.
\end{example}

This is why Definition~\ref{def:updfun} requires update functions to be normalized. Normalization makes the union set of the update function a subset of the intersection set.
As we show later, normalization guarantees that each update function has a unique representation.

\subsubsection{Equality of Micro Functions}\label{sec:equality}
We will now show that micro functions can be checked for equality if their representations use normalized update functions.

First, let us show that normalization does not change the behaviour of an update function. This means that the normalized and non-normalized versions of an update function always denote the same function.

\newpage    
\begin{lemma}\label{lem:normeq}
    $\denote{\mathcal N(\updfun f^*)}=\denote{\updfun f^*}.$
\end{lemma}

\begin{proof}
    Let $\updfun f^*=\setpair I U$.
    For any $\tau\in T,$
    \[
        \begin{aligned}
            \denote{\mathcal N(\updfun f^*)}(\tau)
            &=\denote{\mathcal N(\langle I,\ U\rangle)}(\tau)\\
            &=\denote{\setpair{I\cup U}U}(\tau)\\
            &=\tau\cap(I\cup U)\cup U\\
            &=(\tau\cap I)\cup(\tau\cap U)\cup U\\
            &=\tau\cap I\cup U\\
            &=\denote{\setpair IU}(\tau)\\
            &=\denote{\updfun f^*}(\tau)\,.
        \end{aligned}
    \]
    Thus, $\denote{\mathcal N(\updfun f^*)}=\denote{\updfun f^*}$.
\end{proof}

Let us show that two update functions are equal if and only if their normalized representations are equal.

It is obvious that two functions represented with the same pairs of sets are equal. Let us prove that two different pairs of sets represent different update functions.

\begin{lemma}
    Let $\setpair IU$ and $\setpair{I'}{U'}$ be two normalized update functions such that $\setpair IU\ne\setpair {I'}{U'}$. Then $\denote{\setpair IU}\ne\denote{\setpair {I'}{U'}}$.
\end{lemma}

\begin{proof}
    Let us show that there always exists a set $\tau\subseteq T$ such that $\denote{\setpair IU}(\tau)\ne\denote{\setpair{I'}{U'}}(\tau)$. There are two cases:
    \begin{enumerate}
        \item $U\ne U'$. Then for the empty set $\tau=\varnothing$,
            \[
                \denote{\setpair IU}(\tau)=\denote{\setpair IU}(\varnothing)=(\varnothing\cap I)\cup U=U\,,
            \]
            whereas 
            \[ 
                \denote{\setpair {I'}{U'}}(\tau)=\denote{\setpair {I'}{U'}}(\varnothing)=(\varnothing\cap I')\cup U'=U'.
            \]
            Hence, $\denote{\setpair IU}\ne\denote{\setpair {I'}{U'}}$.
        \item $I\ne I'$. Then for the set of all types $\tau=T$,
            \[
                \denote{\setpair IU}(\tau)=\denote{\setpair IU}(T)=(T\cap I)\cup U=I\cup U\,.
            \]
            Since $\setpair IU$ is normalized, $U\subseteq I$, and
            \[
                I\cup U= I\,.
            \]
            At the same time,
            \[
                \denote{\setpair {I'}{U'}}(\tau)=\denote{\setpair {I'}{U'}}(T)=(T\cap I')\cup U'=I'\cup U'=I'\,.
            \]
            Since $I\ne I'$, it follows that $\denote{\setpair IU}\ne \denote{\setpair {I'}{U'}}$. \qedhere
    \end{enumerate}
\end{proof}

We have shown that transfer functions can be represented using update maps.

\subsubsection{Operations on Update Maps}\label{sec:opsTransRep}

Let us now define the apply, compose, meet, and equals functions on micro function representations.

For an update map $f$ and  a receiver $r\in \rcc$, let the update function $f(r)=\setpair{I_{f,\,r}}{U_{f,\,r}}$.

Then the operations on the update maps $f_1$ and $f_2$ are defined as follows:
        \begin{align}
    %apply
            \textsf{apply}_{f_1}=&\lambda m\,.\,
              \left\{
                \left(
                  r,\,
                  (m(r)\cap I_{f,\,r})\cup U_{f,\,r}
                \right)\,|\,
                r\in\rcc
              \right\},\\\notag \\
    %compose
            f_1\circ f_2=&
            \left\{
              \left(
                r,\,
                  \mathcal N(\langle
                    I_{f_1,\,r}\cap I_{f_2,\,r},\ 
                    (I_{f_1,\,r}\cap U_{f_2,\,r})\cup U_{f_1,\,r}
                  \rangle)
              \right)\,|\,
              r\in\rcc
            \right\},\\\notag \\
    %meet
            f_1\sqcap f_2=&
            \left\{
              \left(
                r,\,
                  \langle
                    I_{f_1,\,r}\cup I_{f_2,\,r},\ 
                    U_{f_1,\,r}\cup U_{f_2,\,r}
                  \rangle
              \right)\,|\,
              r\in\rcc
            \right\},\\\notag \\
    %equals
            \textsf{equals}(f_1,\,f_2)=&
              \begin{cases}
                 \mathsf{true}&\text{ if }f_1\text{ and }f_2\text{ are structurally equal,}\\
                 \mathsf{false}&\text{otherwise.}
              \end{cases}
        \end{align}

The denotation of the operations on update maps can be explained in the following way.

The apply function of a micro function $f$ maps over all receivers. For each receiver $r\in \rcc$, \textsf{update}$_f(r)$ transforms the argument 
receiver-to-types map $m$. It returns a new map in which $r$ is mapped to a new set of types, $\updfun f(m(r))$:
\begin{align*}
    \denote{\textsf{apply}_f}
    &=\denote{\lambda m\,.\,\left\{
                \left(
                  r,\,
                  (m(r)\cap I_{f,\,r})\cup U_{f,\,r}
                \right)\,|\,
                r\in\rcc
              \right\}}\\
    &=\lambda m\,.\,\left\{\left(r,\,\denote{\updfun f}(m(r))\right)\,|\,r\in \rcc\right\}.
\end{align*}
Note that in the beginning of the algorithm, $m$ maps each receiver to $\bot_T$ (all types).

Composing two micro functions means to compose their update-map denotations:
\begin{align}
    \denote{f_1\circ f_2}
    &=\denote{\left\{
              \left(
                r,\,
                  \mathcal N(\langle
                    \ione\cap\itwo,\ 
                    (\ione\cap\utwo)\cup\uone
                  \rangle)
              \right)\,|\,
              r\in\rcc
            \right\}}\notag\\
    &=\footnotemark\lambda m\,.\,\left\{
              \left(
                r,\,
                  \denote{\langle
                    \ione\cap\itwo,\ 
                    (\ione\cap\utwo)\cup\uone
                  \rangle}(m(r))
              \right)\,|\,
              r\in\rcc
            \right\}\notag\\
    &=\lambda m\,.\,\left\{\left(r,\,(\ione\cap m(r)\cap\itwo)\cup(\ione\cap\utwo)\cup\uone\right)\,|\,r\in\rcc\right\}\notag\\
    &=\lambda m\,.\,\left\{\left(r,\,(((m(r)\cap\itwo)\cup\utwo)\cap\ione)\cup\uone\right)\,|\,r\in\rcc\right\}\notag\\
    &=\left(\lambda m\,.\,\{(r,\,(m(r)\cap\ione)\cup\uone)\,|\,r\in\rcc\}\right)\notag\\
      &\quad\circ\left((\lambda m\,.\,\{(r,\,(m(r)\cap\itwo)\cup\utwo)\,|\,r\in\rcc\}\right)\notag\\
    &=\denote{\{(r,\,\setpair{\ione}{\itwo})\}}\circ\denote{\{(r,\,\setpair\itwo\utwo)\}}\notag\\
    &=\denote{f_1}\circ\denote{f_2}.\label{eq:compclosed}
\end{align}
\footnotetext{See Lemma~\ref{lem:normeq}.}
\indent Finally, the meet operation on two micro functions is the union of their update maps:
\begin{align}
    \denote{f_1\sqcap f_2}
    &=\denote{\left\{
              \left(
                r,\,
                  \langle
                    \ione\cup\itwo,\ 
                    \uone\cup\utwo
                  \rangle
              \right)\,|\,
              r\in\rcc
            \right\}}\notag\\
    &=\lambda m\,.\,\left\{\left(r,\,m(r)\cap(\ione\cup\itwo)\cup\uone\cup\utwo\right)\,|\,r\in\rcc\right\}\notag\\
    &=\lambda m\,.\,\left\{\left(r,\,((m(r)\cap\ione)\cup\uone)\cup((m(r)\cap\itwo)\cup\utwo)\right)\,|\,r\in\rcc\right\}\notag\\
    &=\lambda m\,.\,\left\{\left(r,\,(m(r)\cap\ione)\cup\uone\right)\,|\,r\in\rcc\right\}\notag\\
      &\quad\sqcap\lambda m\,.\,\left\{\left(r,\,(m(r)\cap\itwo)\cup\utwo\right)\,|\,r\in\rcc\right\}\notag\\
    &=\denote{f_1}\sqcap\denote{f_2}.\label{eq:meetclosed}
\end{align}

We can now show how the correlated-calls definitions of the meet and composition operations on micro functions allow us to detect infeasible paths in a program.
\begin{example}\label{ex:cc}
  The edges of the exploded supergraph in Figure~\ref{fig:cc_edgefn_example} correspond to the edges of an IFDS taint analysis. We can see that there is a path from the node $(\highlight{\startmain}{greyblue},\,\Lambda)$ to $(\highlight{\texttt{print(s)}}{lightsalmonpink},\,\texttt s)$. This means that the IFDS taint analysis considers \texttt s to be a secret value that is leaked at the print statement.

  The correlated-calls analysis, on the other hand, detects that the path to $(\highlight{\texttt{print(s)}}{lightsalmonpink},\,\texttt s)$ is infeasible: at the print node, the lattice element corresponding to the fact \verb's' contains a mapping $\texttt a\to\top_T$.

  The lattice element for the print statement is evaluated as follows:
  \begin{align*}
    &((\lambda m\,.\,m[\texttt a\to m(\texttt a)\cap\{\texttt B\}])\circ
    \id\circ
    (\lambda m\,.\,m[\texttt a\to m(\texttt a)\cap\{\texttt A\}])\\
    &\circ
    (\lambda m\,.\,\botcc)\circ
    \id\circ\ldots\circ\id)(\topcc)
    \\
    =&(\botcc[\texttt a\to m(\texttt a)\cap(\{\texttt A\}\cap\{\texttt B\})])
    \\
    =&(\botcc[\texttt a\to\top_T])\,.
  \end{align*}

  Therefore, the path to the print statement will be considered infeasible, and the analysis does not claim that the program leaks a secret value.
\end{example}

\subsubsection{Efficiency}\label{sec:efficiency}
In this section, we will show that our representation of micro functions is efficient according to the definition  of efficiency discussed in Section~\ref{sec:ccdatastr}.
\begin{lemma}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient.
\end{lemma}
\begin{proof}
\leavevmode
  \begin{enumerate}
    \item The identity function is represented as
      \[
        \denote{\id}=\{(r,\,\langle \bot_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,;
      \]
      the top function is represented as
      \[
        \denote{\lambda m\,.\,\topcc}=\{(r,\,\langle \top_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,.
      \]
    \item Equations~\eqref{eq:compclosed} and~\eqref{eq:meetclosed} show that the representation of micro functions is closed under composition and meet.
    \item To show that our representation for micro functions forms a lattice with finite height, let us first show that $\lcc_\rcc:\,\rcc\to2^T$ forms a lattice. Since $T$ is a finite set, $(2^T,\,\subseteq)$ is a finite-height lattice. $\rcc$ is a finite set. Hence, the mapping
    \[
      \rcc\mapsto2^T=\{(r,\,t)\,|\,r\in \rcc,\,t\in 2^T\}=\lcc_\rcc
    \]        
    also forms a finite-height lattice \cite{nielson1999principles}.

    Furthermore, $\lcc_\rcc$ is a finite set. 
    Every element of $\lcc_\rcc$ can be applied to $|\rcc|$ receivers, where each receiver is mapped to a set of types. There are $|\rcc|\cdot2^{|T|}$ different possibilities to form those mappings, so
    \[
      |\lcc_\rcc|=|\rcc|\cdot2^{|T|}.
    \]
    Therefore, $\lcc_\rcc\mapsto \lcc_\rcc$ also forms a finite-height lattice.
    \item All operations can be computed in $O(\rcc\times T)$ time. Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
    \item The space bound is $O(\rcc\times T)$.
  \end{enumerate}
\end{proof}

\paragraph{Final Remarks}

A straightforward solution to representing micro functions would be to use the function constructs that are provided by many programming languages. The efficiency requirement prohibits us from doing so.
For most programming languages, equality for functions is either defined as reference equality (as in Scala), or is not defined at all (as in Haskell). Even if we were to define our own definition of equality for functions, we would have to iterate over the whole domain of the functions and compare the results of the function applications, which would be inefficient. Additionally, the equality check would be non-terminating if the domain of the functions were infinite, and undecidable if the language for defining the functions were Turing-complete.

Second, a composition $f$ of two functions $f_1$ and $f_2$ would have to store both $f_1$ and $f_2$. For instance, if $f_1=\lambda x\,.\,x+1$ and $f_2=\lambda x\,.\,x+2$, then $f=f_2\circ f_1$ would be represented as 
\[
  f=\lambda x\,.\,(\lambda y\,.\,y+2)((\lambda z\,.\,z+1)\,x)
\]
instead of
\[
  f=\lambda x\,.\,x+3.
\]
Having a compact representation for function composition is especially important for the first phase of the IDE algorithm, in the computation of jump functions~\cite{sagiv1996precise}. The same argument applies to computing function meets.

\subsubsection{Edge Function Representation}  \label{sec:edgefnrep}
We will now show the representations for the correlated-call micro functions $\ccedgefn{\rcc}(e)$, described in Definition~\ref{def:edgefn}. Let $\textsf{identity}=\setpair{\bot_T}{\top_T}$ represent the identity function $\id$ and $\textsf{bottom}=\setpair{\bot_T}{\bot_T}$ represent the function $\lambda t\,.\,\bot_T$.

On the call-start edge,
\begin{align}
  &m\left[r\to (m(r)\cap\tau(s_\mathcal F,\,f))\right]\notag\\
  =&\denote{\{(r,\,\langle\tau(s_\mathcal F,\,f),\,\top_T\rangle)\}
    \cup
    \{(r',\,\textsf{identity})\,|\,r'\in \rcc,\,r'\ne r\}}.
\end{align}

On the end-return edge,
\begin{align}
  \lambda m\,.\,m&\left[v_1\to\bot_T\right]\dots[v_k\to\bot_T][r\to (m(r)\cap\tau(s_\mathcal F,\,f))]\notag
  \\=&\denote{
    \{(r,\,\langle\tau(s_\mathcal F,\,f),\,\top_T\rangle)\}
    \cup
    \left\{(r',\,w(r'))\,|\,r\in\rcc,\,r'\ne r
  \right\}},
\end{align}
where
\[
w(r)=\begin{cases}
      \textsf{bottom}&\text{if $r$ is a local variable in the exiting method,}\\
      \textsf{identity}&\text{otherwise}.
    \end{cases}
\]

For assignments in the source node of $e$,
\begin{align}
  \lambda m.m\left[r\to \bot_T\right]
  =\denote{\left\{(r,\,\textsf{bottom})\}
    \cup
    \{(r',\,\textsf{identity})\,|\,r'\in \rcc,\,r'\ne r\right\}}.
\end{align}%

In the default case,
\[
  \id
  =\denote{\{(r,\,\textsf{identity}),\,r\in \rcc\}}.
\]

We have shown how IDE problems that account for correlated calls can be represented in an efficient way. In the next section, we address the implementation and present an evaluation of the correlated-calls analysis.

### 2014-11-27 content/eval.tex
changing formatting of thesis according to springer guidelines

\section{Evaluation}\label{chapter:eval}

This section discusses implementation aspects of the correlated-calls analysis and presents experimental results.

\subsection{Implementation of the Analysis}
The correlated-calls analysis was implemented in the Scala programming language~\cite{odersky2004overview}. 
We chose Java as the target language for client programs of the analysis.
To retrieve information about an input program, such as its control-flow supergraph or the set of receivers and their types, we used the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.

Since WALA currently only contains an implementation of IFDS, we implemented IDE from scratch. Instead of using WALA's IFDS implementation, to run an IFDS problem, we converted it to an IDE problem and used our own IDE solver.

\subsubsection{IFDS}
As described in Section~\ref{sec:ifdsdef}, an IFDS problem is defined in terms of an exploded supergraph. The control-flow supergraph of an input program can be retrieved using WALA. Hence, our implementation of an IFDS problem should be able to convert a control-flow supergraph into an exploded supergraph.

We represent an IFDS problem with a trait, or protocol, that contains declarations of four \textit{flow functions}. Each function has type 
\[
  F:\,(N\times D\times N)\to2^D
\]
and defines a set of edges on the exploded graph. 
Given an edge $(n_1,\,n_2)$ of the control-flow supergraph and the fact $d_1$ that 
corresponds to the source node $n_1$, $F(n_1,\,d_1,\,n_2)$ returns the set of all facts $d_2\in D_2$ such that $((n_1,\,d_1),\,(n_2,\,d_2))\in E^\#$\footnote{In each invocation of a flow function, the fact $d_1$ is provided by the IDE algorithm.}.
The four functions are:
\begin{itemize}
  \item \textsf{call-start}, for inter-procedural edges from a call node to the start node of the target method;
  \item \textsf{call-return}, for intra-procedural edges from a call node to its return node;
  \item \textsf{end-return}, for inter-procedural edges from the end node of a method to the return node of the callee;
  \item \textsf{default}, for all other intra-procedural edges.
\end{itemize}

\paragraph{Taint Analysis}
Using this representation of an IFDS problem, we implemented an IFDS problem instance for taint analysis. We used it as a sample IFDS problem on which to evaluate the correlated-calls-IDE construction.

Let $N^*$ be the control-flow supergraph of a program and $D$ the set of the program variables.
Let \textsf{encl}$(n)$ be a function that returns the enclosing method of a node $n\in N^*$. Finally, let the function $r_m:\,D\to 2^D$ be defined as follows:
\begin{equation}
  r_m(d)=\begin{cases}
                \varnothing&\text{if }d\text{ is a local variable in method }m,\\
                \{d\}&\text{otherwise.}
              \end{cases}
\end{equation}
When defining the flow functions for a taint analysis, we will use $r_m$ to avoid the propagation of local variables, as shown below.

For a fact $d_1\in D\cup\{\mathbf0\}$ and two nodes $n_1,\,n_2\in N^*$, the simplified\footnote{For simplicity, the shown flow functions do not account for different Java-specific features such as arrays, fields, operations on strings, etc.} version of flow functions for a taint-analysis looks as follows.

If $n_1$ is a call node that calls method $m$, and $n_2$ is $m$'s start node,
\begin{align*}
  \textsf{call-start}(n_1,\,d_1,\,n_2)&=
    \begin{cases}
      r_{\textsf{encl}(n_1)}(d_1)\cup\{v\}
        &\text{if $a$ is the $i$th argument of the call,}\\
        &\text{$d_1=a$, and $v$ is the $i$th parameter}\\
        &\text{of $m$;}\\
      r_{\textsf{encl}(n_1)}(d_1)&\text{otherwise.}
    \end{cases}
\intertext{If $n_1$ is a call node with corresponding return node $n_2$,}
  \textsf{call-return}(n_1,\,d_1,\,n_2)&=
    \begin{cases}
      \{d_1\}&\text{if $d_1$ is a local variable in \textsf{encl}$(n_1)$,}\\
      \varnothing&\text{otherwise.}
    \end{cases}
\intertext{If $c$ is a call node calling method $m$, $n_1$ is $m$'s end node, and $n_2$ is $c$'s return node,}
  \textsf{end-return}(n_1,\,d_1,\,n_2)&=
    \begin{cases}
        r_{\textsf{encl}(n_1)}(d_1)\cup\{x\}
          &\text{if $n_1$ is a return statement}\\
          &\text{returning $v$, $n_2$ is an assignment}\\
          &\text{with left-hand side $x$, and $d_1=v$;}
        \\
        r_{\textsf{encl}(n_1)}(d_1)&\text{otherwise.}
    \end{cases}
\intertext{Otherwise,}
  \textsf{default}(n_1,\,d_1,\,n_2)&=\{d_1\}.
\end{align*}

\begin{example}
  Consider the supergraph in Figure~\ref{fig:exampleexploded}. The call-to-start flow function from method \verb'main' to \verb'f' looks as follows:
  \begin{align*}
    \textsf{call-start}(\highlight{\textsf{call}_{\texttt{A.f}}}{greyblue},\,\texttt a,\,\highlight{\textsf{start}_\texttt{f}}{lightsalmonpink})
    &=r_\texttt{main}(\texttt a)\cup\{\texttt s\}\\
    &=\{\texttt s\}.
  \end{align*}
  We can see that correspondingly, the exploded supergraph contains an edge from $(\highlight{\textsf{call}_{\texttt{A.f}}}{greyblue},\,\texttt a)$ to $(\highlight{\textsf{start}_\texttt{f}}{lightsalmonpink},\,\texttt s)$.
\end{example}

\subsubsection{IDE}
The correlated-calls analysis was implemented as an IDE problem instance.

We defined an IDE problem in the same way as an IFDS problem, except that the IDE flow functions are of type
\[
  (N\times D\times N)\to2^{D\times (L\to L)}.
\]
With the new flow functions, we can implement a labeled exploded supergraph, since the new flow functions return a set of facts that are paired with micro functions.

For example, if $Q$ is an IDE problem, then the call-to-start flow function for $Q$ is defined as follows:
\begin{align*}
  &\textsf{call-start}^Q(n_1,\,d_1,\,n_2)\\
  =&\left\{(d_2,\,f)\,|\,d_2\in D,\,f\in L^Q\to L^Q:\,\edgefn^Q((n_1,\,d_1),\,(n_2,\,d_2))=f\right\}.
\end{align*}
The other flow functions are defined analogously.

\subsection{Testing}
In this section we assess the correctness and effectiveness of the correlated-calls analysis.

\subsubsection{Conversion from IFDS to IDE}
We implemented the equivalence transformation $\transEq$ and the correlated-calls transformation $\transCC_\rcc$ from IFDS to IDE described in Section~\ref{sec:equivtrans}. To run an IFDS problem, we converted it to an IDE problem using $\transEq$ and $\transCC_\rcc$ and used our IDE analysis algorithm to run the latter.

Given an IFDS problem described with IFDS flow functions, an equivalence transformation creates an IDE problem described with the following IDE flow functions:
\begin{align*}
  \textsf{call-start}^\equiv(n_1,\,d_1,\,n_2)=&\{(d_2,\,\epsilon(d_1,\,d_2))\,|\,d_2\in\textsf{call-start}(n_1,\,d_1,\,n_2)\}\\
  \textsf{call-return}^\equiv(n_1,\,d_1,\,n_2)=&\{(d_2,\,\epsilon(d_1,\,d_2))\,|\,d_2\in\textsf{call-return}(n_1,\,d_1,\,n_2)\}\\
  \textsf{end-return}^\equiv(n_1,\,d_1,\,n_2)=&\{(d_2,\,\epsilon(d_1,\,d_2))\,|\,d_2\in\textsf{end-return}(n_1,\,d_1,\,n_2)\}\\
  \textsf{default}^\equiv(n_1,\,d_1,\,n_2)=&\{(d_2,\,\epsilon(d_1,\,d_2))\,|\,d_2\in\textsf{default}(n_1,\,d_1,\,n_2)\}\,,
\end{align*}
where $\epsilon$ is the bottom function on an edge from a $\Lambda$-fact to a non-$\Lambda$-fact, and the identity function otherwise:
\[
  \epsilon(d_1,\,d_2)=\begin{cases}
    \lambda l\,.\,\bot&\text{if $d_1=\Lambda$ and $d_2\ne\Lambda$;}\\
    \id&\text{otherwise.}
  \end{cases}
\]

We also implemented a correlated-call transformation from IFDS into IDE problems that consider correlated calls. This transformation is described in Section~\ref{sec:cctrans}. The flow functions can be easily inferred from Section~\ref{sec:edgefnrep}.

\subsubsection{Regression Testing}
We used regression tests to assess the correctness of the implemented analyses. Each test involves running a certain analysis on one input Java program.

\paragraph{IDE-Implementation Correctness}
To test the correctness of the IDE algorithm implementation, we implemented a copy-constant-propagation IDE problem~\cite{sagiv1996precise}. 
In a copy-constant propagation analysis, a variable is considered constant if it is assigned a constant literal or another variable that is also a constant. For example, in a program
\inputMinted{java}{correct.java}
\verb'a' and \verb'b' are considered constant, but \verb'c' and \verb'd' are not (although \verb'd' would be considered constant in linear-constant propagation).

We tested the propagation of constants on different intra- and inter-procedural data-flow paths, in parameter passing,
and in conditional branches. Each regression test contained assertions of the form ``at the end of method $m$, variable with name $x$ should be (not) constant''.

We also tested the implementation of the IDE algorithm on an IDE problem generated by conversion from an IFDS problem.

To do that, we implemented an IFDS instance for taint analysis.

Recall from Section~\ref{sec:bgifds} that taint analysis aims to discover variables that are secret at a given program point called a sink.

We used assertions of the form ``at program statement $n$, variable $x$ should be (not) secret'' by defining the sink of a secret value through special \verb'isSecret' and \verb'notSecret' methods.
Those methods asserted that the parameter passed to them is secret and not secret, respectively.
To define a source secret value we created a static \verb'secret()' method that returned a string.

\begin{example}
  Listing~\ref{list:assertions} illustrates the use of the \verb'isSecret' and \verb'notSecret' assertions.
  \begin{listing}[H]
  \inputMinted{java}{assertions.java}
  \caption{Example usage of \texttt{isSecret} and \texttt{notSecret} assertions in regression tests}
  \label{list:assertions}
\end{listing}
\end{example}

We tested data flow through
\begin{itemize}
  \item method calls and returns;
  \item conditional branches and loops, including nested constructions, the ternary operator, and \verb'switch' statements;
  \item arrays and fields\footnote{%
    In Java, arrays are allocated on the heap, and array elements can be aliases of each other. 
    Hence, if any array element gets assigned a secret value, we considered all elements of any \texttt{String} or \texttt{Object} array in the program secret. 
    For the same reason, if a field \texttt{f} of an object of class \texttt{A} is assigned a secret value, then we considered the field \texttt{f} of any object of class \texttt{A} secret.%  
  };
  \item static and instance class members;
  \item classes and interfaces that involve inheritance, overriding, and overloading;
  \item recursion;
  \item library calls\footnote{%
    We created a specification for library functions that allowed us to indicate under which conditions a library function returned a secret value. This let us avoid the expensive analysis of library functions.%
  };
  \item string concatenation and usage of the \texttt{StringBuffer} and \texttt{StringBuilder} classes\footnote{%
    Using mutation, objects of these classes can be converted into wrappers around secret strings. This is why we added a special handling for \texttt{StringBuffer} and \texttt{StringBuilder} objects. For instance, if a field had the  \texttt{StringBuilder} type, it was considered secret.%
  };
  \item generics, type conversions through castings, and exception handling.
\end{itemize}

Our taint analysis implementation becomes unsound in the presence of static initializers. If a static field is initialized to a secret value, our analysis will not detect it as such.

A static initializer is invoked only once, before the instance creation of a class or the access of a static member of that class.
Static initializers are invoked lazily by the Java Virtual Machine~\cite{lindholmjava}. This makes finding out at which program point a static initializer is invoked undecidable~\cite{hubert2009soundly}. To account for static initializers in the analysis would require modifying WALA's control-flow supergraph (which does not have edges to static initializers) or using a data-flow analysis for static initialization. Since the primary purpose of the taint-analysis implementation was to test the correlated-call analysis, we did not include a static-initializer analysis in this work.

\paragraph{Correlated-Calls-Analysis Correctness}
We tested the implementation of the correlated-calls analysis by converting the taint analysis into an IDE problem with an implementation of $\transCC_\rcc$.

Since none of the test cases in the previous section contained correlated calls, we used the same tests with the same assertions to ensure that the correlated-calls analysis produces the same results as an IFDS-equivalent analysis in the absence of correlated calls.

We then added test cases that contained correlated calls. We added a new assertion method, \verb'notSecretCC'. For the IFDS-equivalent analysis, the method asserted that the argument passed to it was secret, and for the correlated-calls analysis, it asserted that the argument was not secret.

Separately, we used unit tests to check the implementation correctness of micro functions. We wrote assertions for the results of the equality, meet, and composition operations on all possible combinations of the identity, top, bottom, and constant functions.

\subsubsection{Benchmark Testing}
To assess the benefit of the correlated-calls analysis, we counted the frequencies of correlated-call occurrences in the Dacapo benchmarks~\cite{blackburn2006dacapo}. We then ran the normal- and correlated-call-taint analysis on the Dacapo benchmarks to see what improvement we would get from the correlated-calls analysis.

\paragraph{Occurrences of Correlated Calls}
Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis.
We counted the number of correlated calls that occurred in programs of the Dacapo benchmarks, as shown in Table~\ref{tab:dacapostat}.

In the table, the number of all call sites in a program is denoted as $C$. 
Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. 
The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
The last three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.

\begin{table}
\caption{Frequencies of correlated-call occurrences in the Dacapo benchmarks}\label{tab:dacapostat}
\centering
%\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lrrrr
>{\columncolor[HTML]{FFFFFF}}r 
>{\columncolor[HTML]{FFFFFF}}l r@{}}
\toprule
\textbf{Benchmark}  &
  \multicolumn{1}{c}{\textbf{$|C|$}} & 
  \multicolumn{1}{c}{\textbf{$|C_P|$}} & 
  \multicolumn{1}{c}{\textbf{$|C^\Subset|$}} & 
  \multicolumn{1}{c}{\textbf{$|\rcc|$}} & 
  {\color[HTML]{000000} \textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C_P|}{|C|}$\end{tabular}}} & 
  {\color[HTML]{000000} \textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C^\Subset|}{|C_P|}$\end{tabular}}} & 
  \textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C^\Subset|}{|\rcc|}$\end{tabular}} \\ \midrule
\textbf{antlr}      & 7,610                             & 428                                   & 299                              & 70                                   & {\color[HTML]{000000} \textbf{6\%}}                                                      & {\color[HTML]{000000} \textbf{70\%}}                                                     & 4                                                                \\
\textbf{bloat}      & 18,157                            & 933                                   & 429                              & 119                                  & {\color[HTML]{000000} \textbf{5\%}}                                                      & {\color[HTML]{000000} \textbf{46\%}}                                                     & 4                                                                \\
\textbf{chart}      & 18,101                            & 466                                   & 195                              & 61                                   & {\color[HTML]{000000} \textbf{3\%}}                                                      & {\color[HTML]{000000} \textbf{42\%}}                                                     & 3                                                                \\
\textbf{eclipse}    & 3,222                             & 100                                   & 35                               & 10                                   & {\color[HTML]{000000} \textbf{3\%}}                                                      & {\color[HTML]{000000} \textbf{35\%}}                                                     & 4                                                                \\
\textbf{fop}        & 4,831                             & 129                                   & 40                               & 12                                   & {\color[HTML]{000000} \textbf{3\%}}                                                      & {\color[HTML]{000000} \textbf{31\%}}                                                     & 3                                                                \\
\textbf{hsqldb}     & 3,573                             & 81                                    & 35                               & 10                                   & {\color[HTML]{000000} \textbf{2\%}}                                                      & {\color[HTML]{000000} \textbf{43\%}}                                                     & 4                                                                \\
\textbf{jython}     & 12,149                            & 487                                   & 129                              & 54                                   & {\color[HTML]{000000} \textbf{4\%}}                                                      & {\color[HTML]{000000} \textbf{26\%}}                                                     & 2                                                                \\
\textbf{luindex}    & 7,190                             & 188                                   & 79                               & 29                                   & {\color[HTML]{000000} \textbf{3\%}}                                                      & {\color[HTML]{000000} \textbf{42\%}}                                                     & 3                                                                \\
\textbf{lusearch}   & 9,043                             & 350                                   & 126                              & 47                                   & {\color[HTML]{000000} \textbf{4\%}}                                                      & {\color[HTML]{000000} \textbf{36\%}}                                                     & 3                                                                \\
\textbf{pmd}        & 10,972                            & 219                                   & 68                               & 23                                   & {\color[HTML]{000000} \textbf{2\%}}                                                      & {\color[HTML]{000000} \textbf{31\%}}                                                     & 3                                                                \\
\textbf{xalan}      & 3,889                             & 110                                   & 35                               & 10                                   & {\color[HTML]{000000} \textbf{3\%}}                                                      & {\color[HTML]{000000} \textbf{32\%}}                                                     & 4                                                                \\
\textbf{Geom. mean} & \textbf{7,572}                    & \textbf{240}                          & \textbf{91}                      & \textbf{29}                          & {\color[HTML]{000000} \textbf{3\%}}                                                      & {\color[HTML]{000000} \textbf{38\%}}                                                     & \textbf{3}                                                       \\ \bottomrule
\end{tabular}
%}
\end{table}

We can see that on average, 3\% of all call sites $C$ are polymorphic call sites $C_P$. Out of those call sites, 38\% are correlated call sites $C^\Subset$. We also see that for one correlated-call receiver, there are on average three correlated calls.

\paragraph{Experiments}
We ran the analysis on the Dacapo benchmarks to test if the taint analysis would benefit from the improved, correlated-calls based, analysis. 
We defined any user input string to be considered a secret source and compared the overall number of results in the original and correlated-call taint analyses. If the number of secret values in the original result were larger than in the correlated-call result, we would see a practical benefit from our analysis.

However, even when we considered each program point as a sink, the ``improved'' analysis revealed the same number of secret values as the original taint analysis.

A correlated call that could affect a taint-analysis result could most likely occur in the following scenario:
\begin{itemize}
  \item there is a receiver with at least two polymorphic calls;
  \item at least one of the calls $c_1$ returns a string~--- this would mean that the method potentially returns a secret value;
  \item at least one of the calls $c_2$ takes a string parameter~--- this would mean that a secret value could potentially be propagated to the method as an argument.
\end{itemize}
Then, if the correlated call occurred on an invocation $c_2(c_1())$, there might be a possibility of benefiting from the correlated-calls analysis. 
Given the relatively rare occurrence of correlated calls, this situation is not likely to appear often. 
This is illustrated in Table~\ref{tab:stringstat} which shows how often correlated calls would invoke methods that either take a string as a parameter \textit{or} return a string.
The set of receivers on which there are invocations of such methods is denoted as $\rcc_S$. 
A situation where one correlated call returned a string, \textit{and} another correlated call on the same receiver took a string parameter, appeared in only one case in the \verb'antlr' benchmark. However, the strings invoked were not designated as secret.

This explains why, specifically for a taint analysis as the client analysis, and specifically for the Dacapo benchmarks, the correlated call analysis did not make a difference.

\begin{table}
\caption{Frequency of correlated-call receivers for which at least one of the correlated calls takes a string as a parameter or returns a string}

\centering
\begin{tabular}{@{}lrrr@{}}
\toprule
\textbf{Benchmark}   & 
  \textbf{$|\rcc_S|$} & 
  \textbf{$|\rcc|$} & 
  \textbf{$\cfrac{|\rcc_S|}{|\rcc|}$} \\ \midrule
\textbf{antlr}       & 43                     & 70               & 62\%                            \\
\textbf{bloat}       & 0                      & 119              & 0\%                             \\
\textbf{chart}       & 1                      & 61               & 2\%                             \\
\textbf{eclipse}     & 0                      & 10               & 0\%                             \\
\textbf{fop}         & 0                      & 12               & 0\%                             \\
\textbf{hsqldb}      & 0                      & 10               & 0\%                             \\
\textbf{jython}      & 6                      & 54               & 23\%                            \\
\textbf{luindex}     & 0                      & 29               & 0\%                             \\
\textbf{lusearch}    & 2                      & 47               & 6\%                             \\
\textbf{pmd}         & 1                      & 23               & 3\%                             \\
\textbf{xalan}       & 0                      & 10               & 0\%                             \\
\textbf{Geom. mean} & \textbf{3}             & \textbf{29}      & \textbf{9}                    \\ \bottomrule
\end{tabular}
\label{tab:stringstat}
\end{table}

\subsection{Future Work}
In this section we point out the limitations of the correlated-calls analysis and suggest improvements to the analysis for future work.

One limitation of the analysis is that it only works for IFDS problems like taint analysis, reachable definitions, or available expressions. The correlated-call analysis is not applicable to IDE problems like copy- or linear-constant propagation. Therefore, a possible direction for future work is to create a correlated-calls analysis that transforms an original IDE problem into one that considers correlated calls (with a modified lattice and edge function definition), and then transforms the correlated-calls result into a more precise result of the original IDE problem.

\begin{listing}
  \inputMinted{java}{interprocRec.java}
  \caption{Inter-procedurally-correlated calls}
  \label{list:interProcRec}
\end{listing}

Another constraint of the algorithm is that it only accounts for intra-procedurally-correlated receivers, or receivers on which correlated calls occur within one method. For example, in Listing~\ref{list:interProcRec}, \verb'a' is a correlated-call receiver, since there are two polymorphic method invocations on \verb'a'. However, the first one, \verb'a.setString()', is inside method \verb'main', and the second one, \verb'a.printString()', is inside method \verb'propagate'. Therefore, we do not treat \verb'a' as a correlated-call receiver, and the analysis would not improve the original IFDS result for this program.

Finally, correlated calls can occur on multiple receivers and other scenarios discussed in~\cite{frank2014correlated} that are not handled in this work.

### 2014-11-27 content/impl.tex
changing formatting of thesis according to springer guidelines

\section{Correlated Calls Analysis}\label{chapter:cca}
The correlated-calls analysis is presented as a transformation from an arbitrary IFDS problem to a corresponding IDE problem.

After solving the generated IDE problem, its result can be converted to an IFDS result. If the input program contains correlated calls, the converted IFDS result can be more precise than the original IFDS result.

In this section, we first discuss what is necessary to define IFDS and IDE problems. Next we describe how to convert any IFDS problem into an equivalent IDE problem, and, given a solution to the generated IDE problem, how to obtain the result of the original IFDS problem. We then show how to transform an IFDS problem into an IDE problem using the correlated-calls transformation, and how to convert the solution to the latter IDE problem into a more precise IFDS result.

\subsection{Defining IFDS and IDE Problems}
In Section~\ref{sec:bg}, we defined what IFDS and IDE problems are, their applications, and their constraints. In this section, we describe how to create instances of IFDS and IDE problems.

\subsubsection{Defining an IFDS Problem}\label{sec:ifdsdef}
Recall that an IFDS problem instance is defined as a five-tuple
\[
    (G^*,\ D,\ F,\ M_F,\,\sqcap)\,,
\]
where $G^*=(N^*,\,E^*)$ is the control-flow supergraph of the program, $D$ is the set of dataflow facts, $F\subseteq2^D\to2^D$ is a set of distributive dataflow functions, and the function $$M_F:\,E^*\to(2^D\to2^D)$$ maps the supergraph edges to dataflow functions, and is extended to paths by composition.

In practice, an IFDS problem can be defined by providing an exploded supergraph
$G^\#=(N^\#,\,E^\#)$. Each node of $G^\#$ is a pair $(n,\ d)$, where $n\in N^*$ is a node in the control-flow supergraph and $d\in (D\cup\{\mathbf{0}\}),\ \mathbf0\notin D$, where $\mathbf0$ is an auxiliary fact that is necessary for the IFDS algorithm.

The meaning of an edge in the exploded supergraph is the following.
Let $(n_1,\,d_1)$ and $(n_2,\,d_2)$ be two nodes in the exploded supergraph $G^\#$. Furthermore, assume that if fact $d_1$ at node~$n_1$ holds, then the fact~$d_2$ at node~$n_2$ also holds. Then there is an edge $(n_1,\,d_1),\,(n_2,\,d_2)\in E^\#$.

\subsubsection{Defining an IDE Problem}\label{sec:defide}
An IDE problem instance is a four-tuple
\[
    (G^*,\ D,\ L,\ \menv),
\]
where $G^*$ and $D$ are defined in the same way as for IFDS. $L$ is a finite-height lattice that represents the values to which dataflow facts are mapped in an IDE problem. An environment $Env(D, L)$ maps dataflow facts to lattice elements. Finally, the map $$M_{\textsf{Env}}:\,E^*\to(\textsf{Env}(D, L)\to \textsf{Env}(D, L))$$ is a function from the control-flow-supergraph edges to environment transformers, extended to paths by composition.

An IDE problem can be defined with a labeled exploded supergraph\footnote{
    The exploded supergraph in an IDE problem is defined in the same way as in an IFDS problem. The only difference is that the $\mathbf0$ fact is denoted as $\Lambda$~\cite{reps1995precise,sagiv1996precise}.
}, in which an edge function
\begin{equation}
  \edgefn:\ E^\#\to(L\to L)
\end{equation}
pairs edges with \textit{micro functions}, and is extended to paths by composition.

The set of micro functions of an IDE problem is a subset of $L\to L$ that is closed under function meet and composition.

The meaning of an edge in the labeled exploded supergraph is the following. Let $e=((n_1,\,d_1),\,(n_2,\,d_2))\in E^\#$ be an edge in the exploded supergraph with label $f=\mathsf{EdgeFn}(e)$. Then
\begin{itemize}
%	\item the fact that $d_1$ holds at node $n_1$ implies that $d_2$ holds at $n_2$;
  \item if at node $n_1$ the fact $d_1$ was mapped to a lattice element $l_1$ by an environment $Env(D,\,L)$, then the fact $d_2$ at node $n_2$ should be mapped to $f(l_1)$.
\end{itemize}

As shown in~Sagiv et al.~\cite{sagiv1996precise}, the relationship between environment transformers and edge functions can be described with the following equations. For individual edges $(n_1,\,n_2)\in E^*$,
\begin{align}\label{eq:envTransToEdgeFnEdge}
  \menv&((n_1,\,n_2))(\textsf{env})(d)\notag\\
  &=\edgefn((n_1,\,\Lambda),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,,
\end{align}
where $\textsf{env}$ is an environment $\textsf{Env}(D,\,L)$. Informally, for a given control-flow-supergraph edge $e$ and data-flow fact $d$, the $M_\textsf{Env}$ function captures the meet of the edge function applied to all possible exploded-graph edges along $e$.

For paths $p$ that start with the entry point~$\startmain$,
\begin{equation}\label{eq:envTransToEdgefn}
  \menv(p)(\Omega)(d)=\bigsqcap_{r\in\mathsf{RP}(p,\,d)}\edgefn(r)(\top)\,,
\end{equation}
where $n\in N^*$, $d\in D$, $p\in\ivp(n)$, and $\mathsf{RP}$ is the set of all inter-procedurally realizable paths.

To summarize, an IDE problem can be defined by a labeled exploded supergraph 
\begin{equation}(G^\#,\,L,\,\mathsf{EdgeFn})\,,\end{equation}
where each edge of the exploded supergraph corresponds to a micro function.

\subsection{Transformations Between IFDS and IDE}\label{seq:transIfdsIde}

The correlated-call analysis transforms an existing IFDS problem into a special kind of IDE problem. We described what is necessary to define IFDS and IDE problems independently.

Let $P=(G^\#)$ be an IFDS problem and $Q=(G^\#,\,\edgefn)$ an IDE problem obtained by a conversion from $P$.

We will look at two kinds of transformations
\begin{equation}
  \mathcal T:\ (G^\#)\to (G^\#,\,\edgefn)
\end{equation}
from IFDS to IDE problems:
\begin{itemize}
	\item an equivalence transformation $\transEq$ (pronounced as ``t-equiv''), in which we show how to transform IFDS problems into equivalent IDE problems;
  \item a correlated-call transformation $\transCC$ (pronounced as ``t-c-c''), where we show how to convert IFDS problems into a special form of IDE problems that help eliminate infeasible paths.
\end{itemize}
In each case we also show how to convert the result of the generated IDE problem to a result of the original IFDS problem.

An overview of the transformations is shown in Figure~\ref{fig:transformations}.
\begin{figure}
  \centering
    \tikzset{
  ashadow/.style={opacity=.25, shadow xshift=0.07, shadow yshift=-0.07},
}
  \tikzstyle{problem}=[fill=greyblue,text width=2.3cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
  \tikzstyle{result}=[fill=bisque,text width=1.8cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
\begin{tikzpicture}
    \node [problem] (ifds) {IFDS problem};
    \node [problem] (equiv) [above right=0.9cm and .7\dist of ifds.east] {Equivalent IDE problem};
    \node [problem] (ccide)[below=3cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
    \node [result] (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
    \node [result] (ccres) [below=3cm of equivres.west,anchor=west] {Correlated-calls result};
    \node [result] (ifdsres) [right=\dist of equivres.east] {IFDS result};
    \node [result] (improved) [right=\dist of ccres.east] {Improved IFDS result};
    \path[->] (equivres) edge node[above]{$\backEq$} (ifdsres);
    \path[->] (ccres) edge node[above] {$\backCC$} (improved);
    \path[->] (ccres) edge[out=30,in=240] node[above] {$\backEq$} (ifdsres);
    \path[->] (ifds) edge[out=40,in=190] node[above] {$\transEq$} (equiv);
    \path[->] (ifds) edge[out=-60,in=165] node[above] {$\transCC$} (ccide);
    \path[->] (equiv) edge node[above]{$\result$} (equivres);
    \path[->] (ccide) edge node[above]{$\result$} (ccres);
\end{tikzpicture}
  \caption{Transformations between IFDS and IDE problems and their results}%
  \label{fig:transformations}%
\end{figure}

\subsubsection{Equivalence Transformation}\label{sec:equivtrans}
We start with an equivalence transformation $\transEq$ to present a simple IFDS-to-IDE conversion that does not change the result of the original IFDS problem. We will compare the correlated-calls transformation with the equivalence transformation, and use the latter to show  that the correlated-calls analysis results in a
precision improvement of the original IFDS problem result.

\paragraph{Converting IFDS problems to IDE problems}
Since IDE is a generalization of IFDS, any IFDS problem can be converted into an equivalent IDE problem~\cite{sagiv1996precise}.
For an equivalence transformation $\transEq$, the generated lattice $L^\equiv$ consists of two elements, bottom and top:
\[
    L^\equiv=\{\bot,\ \top\}\,,
\]
where $\bot$ means ``reachable'', and $\top$ means ``not reachable''.

 All micro functions are identity functions.

Given an exploded supergraph $G^\#$ provided by an IFDS problem, we want to create an edge function $\edgefn^\equiv$ that maps $G^\#$'s edges $E^\#$ to micro functions $L^\equiv\to L^\equiv$.

The edge functions $\edgefn^\equiv$ are defined as
\begin{equation}
    \edgefn^\equiv=
    \begin{cases}
      \lambda e\,.\,\lambda m\,.\,\bot&\text{if $d_1(e)=\Lambda$ and $d_2(e)\ne\Lambda$;}\\
      \lambda e\,.\,\id&\text{otherwise,}
    \end{cases}
\end{equation}
where $d_1(e)$ is the source fact of an edge $e$ and $d_2(e)$ is its target fact. At a ``diagonal'' edge from a $\Lambda$-fact to a non-$\Lambda$-fact $d$, the micro function is a constant function that returns $\bot$, which makes it a bottom element in the $L\to L$ lattice. Since the initial lattice element passed to the micro function at the start node is the top element (see~\eqref{eq:envTransToEdgefn}), the bottom function at the diagonal edge swaps the top element to bottom to make the fact $d$ reachable.

The resulting equivalence transformation looks as follows:
\begin{equation}
  \transEq((G^\#))=(G^\#,\,L^\equiv,\,\mathsf{EdgeFn}^\equiv).
\end{equation}

Thus, in $\transEq$, all non-diagonal edges in the original IFDS problem are mapped to identity functions.

\paragraph{Converting IDE Results to IFDS Results}

The output of an IFDS analysis states whether a node is reachable in the exploded supergraph. This means that for an IFDS problem $P$, the IFDS-analysis result $\result_{\text{IFDS}}(P):\ N^*\to 2^D$ is a map from nodes of the control-flow supergraph to sets of facts:
\begin{equation}
  \result_{\text{IFDS}}(P)=\{(n,\,\mvp F(n))\,|\,n\in N^*\}\,.
\end{equation}

\begin{example}\label{ex:ifdsresult}
  The solution to the taint-analysis IFDS problem $\mathcal P$ in Listing~\ref{list:examplejava} whose exploded supergraph is presented in Figure~\ref{fig:exampleexploded} looks as follows:
  \small\begin{align*}
    \result_\text{IFDS}(\mathcal P)=\{&(\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\{\texttt a\}),
      &(\highlight{\textsf{start}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
      &\qquad\qquad(\highlight{\textsf{return}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
%      
      &(\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\{\texttt a\}),
      &(\highlight{\texttt{if(s==null)}}{lightsalmonpink},\,\{\texttt s\}),
      &\qquad\qquad(\highlight{\texttt{return r}}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
%
      &(\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\{\texttt a,\,\texttt b\}),
      &(\highlight{\textsf{call}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
      &\qquad\qquad(\highlight{\textsf{end}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\})\}.\\
%
      &(\highlight{\textsf{end}_\texttt{main}}{greyblue},\,\{\texttt a,\,\texttt b\}),&(\highlight{\texttt{return s}}{lightsalmonpink},\,\{\texttt s\}),
  \end{align*}\normalsize
  All other nodes of the control-flow supergraph are mapped to the empty set.
\end{example}

 The IDE analysis associates a lattice element with each node in the exploded supergraph. For an IDE problem $Q$, the result $\result(Q):\ N^\#\to L$ maps nodes of the exploded supergraph to lattice elements (see~\eqref{eq:mvpdef}):
\begin{equation}\label{eq:ideresult}
  \result(Q)=\{((n,\,d),\,\mvp{\textsf{Env}}(n,\,d))\ |\ n\in N^*,\,d\in D\}\,.
\end{equation}
In other words, for each fact $d\in D$ at a given node $n\in N^*$, $\result(Q)(n,\,d)$ returns a lattice element. If a fact $d\in D$ is unreachable, $\result(Q)(n,\,d)=\top$.

In the case of an equivalence transformation from IFDS to IDE, if a node in the IFDS result is reachable, it will be also reachable in the IDE result, and it will be mapped to the bottom lattice element. For an exploded node in the IDE result, being mapped to the top element means being not reachable.

The~domain of an equivalence-IDE result 
\begin{equation}
  \resultEq=\result(\transEq(P))
\end{equation}
consists of pairs of control-flow-supergraph nodes and data-flow facts. The range of the result is the set of lattice elements. To transform an IDE result to an IFDS result, we need to map each control-flow-supergraph node to the set of facts with which it is paired, provided that the pair is mapped to the bottom lattice element.

\begin{example}\label{ex:ideresult}
  Converting the IFDS problem $\mathcal P$ from Example~\ref{ex:ifdsresult} into an equivalent IDE problem and solving it will yield the following result:
    \small\begin{align*}
    \result(\transEq(\mathcal P))=\{&((\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\texttt a),\,\bot),\\
      &((\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt b),\,\bot),\\
      &\dots\}.\\
    \end{align*}\normalsize
  Suppose that for a pair $(n,\,d)$, where $n\in N^*$ and $d\in D$, there is no corresponding result in ~$\result_\text{IFDS}(\mathcal P)$ (see Example~\ref{ex:ifdsresult}). Then $(n,\,d)$ appears in $\result(\transEq(\mathcal P))$ as $((n,\,d),\,\top)$.
\end{example}

Let $\rho$ be the result of an equivalence-IDE analysis for an IFDS problem $P$:
\[
  \rho=\result(\transEq(P)).
\]
For a node $n\in N^*$, let $D_n^\equiv(\rho)$ be a set of data-flow facts such that
\begin{equation}
  D_n^\equiv(\rho)=\{d\ |\ d\in D\,\wedge\,\rho(n,\,d)\ne\top\}\,.
\end{equation}
Then the transformation function
$\backEq:\,(N^\#\to L)\to(N^*\to2^D)$
from an IDE result to~an~IFDS result looks as follows:
\begin{equation}
  \backEq\left(\rho\right)=
    \left\{(n,\,D_n^\equiv(\rho))\ |\ n\in N^*\right\}\,.
\end{equation}

Obviously, if applied to the result of an equivalence-IDE problem, $\backEq$ returns a result equivalent to the original IFDS problem result. In other words, for any IFDS problem $P$ with supergraph $N^*$, and any node $n\in N^*$,
\begin{equation}
  \backEq\left(\result(\transEq(P))\right)(n)=\result_{\text{IFDS}}(P)(n)\,.
\end{equation}

\begin{example}
  Converting the result in Example~\ref{ex:ideresult} with the equivalence-transformation from an IDE result to an IFDS result $\backEq$ will yield the same result as in Example~\ref{ex:ifdsresult}.
\end{example}
\subsubsection{Correlated-Call Transformation}\label{sec:cctrans}

To improve the precision of an IFDS problem, we can convert it to a special type of IDE problem, and use lattice elements to provide us with additional information about a node.
When converting the IDE result to an IFDS result, lattice elements will tell us whether to make the corresponding exploded nodes reachable. This is the idea of the correlated-calls analysis.

\paragraph{Lattice Elements}
Just like in the equivalence transformation $\transEq$, the exploded supergraph for $\transCC$ is the same as in the original IFDS problem. The elements of the correlated-calls lattice $\lcc$ are functions that map receivers to sets of types:
\[
    \lcc=\left\{\,m:\ R\to2^T\right\},
\]
where $R$ is the set of receivers and $T$ is the set of all types in the program. 
The type power set $2^T$ is also a lattice with a bottom element 
\begin{align*}
\bot_T&=T
\intertext{and top element}
\top_T&=\varnothing.
\intertext{The top element of the function lattice}
\topcc&=\lambda r.\top_T
\intertext{is a function that maps any receiver to the empty set\footnote{%
  We prove that $\lcc$ is a lattice in the Proof of Lemma~\ref{lem:efficient}%
}. 
The bottom element}
\botcc&=\lambda r.\bot_T
\end{align*}
maps any receiver to all types in the program.

To understand the meaning of lattice elements in a correlated-call analysis, suppose that an IFDS problem has been converted to an IDE problem using the correlated-calls transformation. 
Assume also that $s$ is the entrypoint of the program, $n$ is a node in the exploded supergraph, and that in the IDE result, $n$ is mapped to a lattice element $l\in \lcc$. 
Then the purpose of $l$ is to provide information about the set of types of the objects that may be referenced by each receiver at runtime at a path from $s$ to $n$. 
If a receiver is mapped to the empty set $\top_T$, it means that for the given program point, the receiver cannot reference an object of any type.
In other words, the corresponding data-flow fact is considered not reachable.

\paragraph{Micro Functions}\label{sec:micro}
Unlike in the equivalence transformation, the micro functions returned by the edge function $\edgefn^\Subset$ are not always identity functions.

Let $e=(n_1,\,n_2)\in E^\#$ be an edge in the exploded supergraph.
$\edgefn^\Subset(e)$ returns a micro function $f\subset\lcc\to \lcc$.
Given a micro function (a map from receivers to sets of types) $m\in \lcc$, $f(m)$ returns a new map from receivers to sets of types.
In other words, $f$ shows how to update the map from receivers to sets of types when we encounter program point $n_1$.

Let $f_1$ and $f_2$ be two micro functions such that ${f_1=\lambda m\,.\,\lambda r\,.\,t_1(r)}$ and ${f_2={\lambda m\,.\,\lambda r\,.\,t_2(r)}}$. We define the meet operation on micro-functions as follows:
\begin{equation}\label{eq:micromeet}
  \lambda m\,.\,\lambda r\,.\,t_1(r)\sqcap\lambda m\,.\,\lambda r\,.\,t_2(r)
  =\lambda m\,.\,\lambda r\,.\,t_1(r)\cup t_2(r)\,.
\end{equation}

The composition of micro functions is defined as ordinary function composition.

\paragraph{Edge Functions}\label{sec:ef}

Let $\mathcal F$ be the set of methods in a program with a signature $s_\mathcal F$.
\begin{definition}
  Let $r.c()$ be a call site on a receiver $r\in R$ with runtime type $t\in T$.
  Let~$s_\mathcal F$ be the method signature corresponding to the call $c()$.
  For $s_\mathcal F$ and $t$, a \textit{lookup function} returns the method implementation $f\in\mathcal F$ to which the call $r.c()$ is dispatched:
  \begin{equation}
    \textsf{lookup}(s_\mathcal F,\,t)=f.
  \end{equation}
\end{definition}

\begin{definition}
  For a method signature $s_\mathcal F$ and a method implementation $f\in\mathcal F$, the static-type function $\tau$ returns the set of types for which the lookup function yields $f$:
  \begin{equation}
    \tau(s_\mathcal F,\,f)=\{\,t\ |\ \textsf{lookup}(s_\mathcal F,\,t)=f\}\,.
  \end{equation}
\end{definition}
In other words, $\tau$ computes the set of types for which calls to methods
with signatures~$s_\mathcal F$ are dispatched to~$f$.

If there is a supergraph path from a method call with signature $s_\mathcal F$ to the start of $f$, then the set $\tau(s_\mathcal F,\,f)$ is always non-empty.

\begin{definition}\label{def:momopoly}
  A call site is called monomorphic if it can be dispatched to only one method. If a call site can be dispatched to more than one method it is called polymorphic.
\end{definition}

  Let $r.c()$ be a call on a receiver $r\in R$ with a method signature $s_\mathcal F$ to a function $f\in\mathcal F$.
  If the call site is monomorphic, then $\tau(s_\mathcal F,\,f)$ contains all types $T'\subseteq T$ that are compatible with the static type of $r$.
  If the call site is polymorphic, then $\tau(s_\mathcal F,\,f)\subset T'$, since some types $t\in T'$ cause dispatch to a method other than $f$.

\begin{definition}\label{def:edgefn}
  For an edge $e$, let $n_1(e)$ and $n_2(e)$ be the source and target nodes of $e$, and $d_1(e)$ and $d_2(e)$ be its source and target facts. A correlated-call edge function for the set $S\subseteq R$ is defined as follows:
  \begin{equation}\label{eq:edgefndef}
    \ccedgefn S=\lambda e\,.\,
        \begin{cases}
          \id  &\text{if $d_1(e)=d_2(e)=\Lambda$},\\
          \lambda m\,.\,\varepsilon_S(e)(\botcc) &\text{if $d_1(e)=\Lambda$ and $d_2(e)\ne\Lambda$},\\
          \lambda m\,.\,\varepsilon_S(e)(m)  &\text{otherwise,}
        \end{cases}
  \end{equation}
  where $\varepsilon_S:\,E\to(L\to L)$ is a function defined as
  \begin{equation}\label{eq:varepsilon}
    \varepsilon_S=\lambda e\,.\,
        \begin{cases}
            \lambda m\,.\,m[r\to m(r)\cap \tau(s_\mathcal F,\,f)],
                &\text{if $e$ is a call-start edge. $r.c()$ is}\\
                &\text{the call site at $n_1(e)$, $f$ is the called}\\
                &\text{procedure with signature $s_\mathcal F$,}\\
                &\text{and $r\in S$;}\\
            \lambda m\,.\,m[r\to m(r)\cap \tau(s_\mathcal F,\,f)]
                &\text{if $e$ is an end-return edge.}\\
            \textcolor{white}{\lambda m\,.\,m}[v_1\to\bot_T]
                &\text{$v_1,\,\dots,\,v_k\in S$ are the local variables}\\
            \textcolor{white}{\lambda m\,.\,m}\dots
                &\text{in the callee method, $r.c()$ is the call}\\
            \textcolor{white}{\lambda m\,.\,m}[v_k\to\bot_T],
                &\text{corresponding to the return node}\\
                &\text{at $n_2(e)$, $f$ is the called method with}\\
                &\text{signature $s_\mathcal F$, and $r\in S$;}\\
            \lambda m\,.\,m\left[r\to \bot_T\right],
                &\text{if $n_1(e)$ contains an assignment}\\
                &\text{for $r\in S$;}\\
            \id
                &\text{otherwise.}
        \end{cases}
  \end{equation}
  We define both $\ccedgefn S$ and $\varepsilon_S$ to be extended to paths by composition.
\end{definition}
In the above definition, the purpose of the set $S$ is to limit the set of considered receivers. We will use $S$ in Section~\ref{sec:ccreceivers}.

The micro functions returned by a correlated-calls edge function can be described as follows. Along $\Lambda$-edges, the micro functions are identity functions. All other functions can be described with $\varepsilon_S$. On ``diagonal'' edges from $\Lambda$ facts to non-$\Lambda$ facts, $\varepsilon_S$ creates edge-specific mappings for a set of receivers, and maps all the other receivers to the set of all types $\bot_T$. On all other edges, $\varepsilon_S$ modifies the mappings for a set of receivers and leaves the mappings for the other receivers unchanged.

\begin{example}
  Consider the program Listing~\ref{list:ccexample}. The exploded supergraph for that program is shown in Figure~\ref{fig:cc_edgefn_example}.

  Returning a secret value in method \verb'A.foo' creates a ``diagonal'' edge from the $\Lambda$-fact to the secret fact $\psi$. 
  The diagonal edge is labeled with the micro function $\lambda m\,.\,\botcc$. Thus, at the end node of the method, every receiver is mapped to the set of all types~$\bot_T$.

On the end-return edge from \verb'A.foo' to \verb'main', we need to restrict the set of types for the receiver \verb'a' by labeling the end-return edge from the fact $\psi$ to the fact \verb'v' with the micro function $\lambda m\,.\,m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$.

Similarly, on the call-start edge from method \verb'main' to method \verb'B.bar', from fact \verb'v' to \verb's', we restrict the type of the receiver \verb'a' to the set \{\texttt B\} with the micro function~$\lambda m\,.\,m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$.

After we have shown the definitions for the meet and composition operations, we will show in Example~\ref{ex:cc} how the correlated-calls analysis uses the presented micro functions to detect infeasible paths.

\begin{figure}%
  \centering
    \tikzstyle{supergraph}=[
      fill=greyblue,
      rounded corners,
      font=\footnotesize,
      align=right,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_y}=[
      fill=bisque,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_f}=[
      fill=lightsalmonpink,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{description}=[fill=white]
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
    \tikzstyle{arrowtext}=[font=\tiny,color=black,above]

\hspace*{-10pt}
\begin{tikzpicture}
\scalebox{.8}{
% main method nodes
    \node [supergraph] (st_main) {\textsf{start}$_{\texttt{main}}$};
    \node [supergraph] (asgn_a) [below = \dist of st_main.south east, anchor=east] {\texttt{a = args==null\,?}\\\texttt{new\,A()\,:\,new\,B()}};
    \node [supergraph] (call_foo) [below = \dist of asgn_a.south east, anchor=east] {\textsf{call}$_\texttt{foo}$};
    \node [supergraph] (return_foo) [below = \dist of call_foo.south east,anchor=east] {\textsf{return}$_\texttt{foo}$\\\texttt{v = a.foo()}};
    \node [supergraph] (call_bar) [below = \dist of return_foo.south east, anchor=east] {\textsf{call}$_\texttt{bar}$};
    \node [supergraph] (return_bar) [below = \dist of call_bar.south east, anchor=east] {\textsf{return}$_\texttt{bar}$};
    \node [supergraph] (end_main) [below = \dist of return_bar.south east, anchor=east] {\textsf{end}$_{\texttt{main}}$};

    \node [n,label=$\Lambda$] (st_main_z) [right=\nd of st_main.east] {};
    \node [n,label=\texttt{v}] (st_main_v) [right=\nd of st_main_z] {};
    \node [n] (asgn_a_z) [right=\nd of asgn_a.east] {};
    \node [n] (call_foo_z) [right=\nd of call_foo.east] {};
    \node [n] (return_foo_z) [right=\nd of return_foo.east] {};
    \node [n] (call_bar_z) [right=\nd of call_bar.east] {};
    \node [n] (return_bar_z) [right=\nd of return_bar.east] {};
    \node [n] (end_main_z) [right=\nd of end_main.east] {};
    \node [n] (asgn_a_v) [right=\nd of asgn_a_z] {};
    \node [n] (call_foo_v) [right=\nd of call_foo_z] {};
    \node [n] (return_foo_v) [right=\nd of return_foo_z] {};
    \node [n] (call_bar_v) [right=\nd of call_bar_z] {};
    \node [n] (return_bar_v) [right=\nd of return_bar_z] {};
    \node [n] (end_main_v) [right=\nd of end_main_z] {};
% main method edges
    \path[->](st_main_z) edge (asgn_a_z);
    \path[->](asgn_a_z) edge (call_foo_z);
    \path[->](call_foo_z) edge (return_foo_z);
    \path[->](return_foo_z) edge (call_bar_z);
    \path[->](call_bar_z) edge (return_bar_z);
    \path[->](return_bar_z) edge (end_main_z);  
    \path[->](st_main_v) edge (asgn_a_v);
    \path[->](asgn_a_v) edge (call_foo_v);
    \path[->](call_foo_v) edge (return_foo_v);
    \path[->](return_foo_v) edge (call_bar_v);
    \path[->](call_bar_v) edge (return_bar_v);
    \path[->](return_bar_v) edge (end_main_v);

%A.foo method nodes
    \node [supergraph_y] (st_a_foo) [right = 6*\dist of st_main] {\textsf{start}$_{\texttt{A.foo}}$};
    \node [supergraph_y] (return_secret) [below = \dist of st_a_foo.south west, anchor=west] {\texttt{return secret()}};
    \node [supergraph_y] (end_a_foo) [below = \dist of return_secret.south west,anchor = west] {\textsf{end}$_\texttt{A.foo}$};

    \node [n,label=$\psi$] (st_a_foo_p) [left=\nd of st_a_foo.west] {};
    \node [n] (return_secret_p) [left=\nd of return_secret.west] {};
    \node [n] (end_a_foo_p) [left=\nd of end_a_foo.west] {};
    \node [n,label=$\Lambda$] (st_a_foo_z) [left=\nd of st_a_foo_p] {};
    \node [n] (return_secret_z) [left=\nd of return_secret_p] {};
    \node [n] (end_a_foo_z) [left=\nd of end_a_foo_p] {};
%A.foo method edges
    \path[->](st_a_foo_z) edge (return_secret_z); 
    \path[->](return_secret_z) edge node[arrowtext,near start,above right=0.4cm and -.15cm,rotate=-60]{$\lambda m.\botcc$} (end_a_foo_z); 
    \path[->,dashed](call_foo_z) edge [out=38,in=238]  (st_a_foo_z);
    \path[->,dashed](end_a_foo_z) edge [out=200,in=43] (return_foo_z);
    \path[->,dashed](end_a_foo_p) edge  [out=200,in=43] node[arrowtext,below,rotate=30]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (return_foo_v);
    \path[->](st_a_foo_p) edge (return_secret_p); 
    \path[->](return_secret_p) edge (end_a_foo_p);
    \path[->](return_secret_z) edge (end_a_foo_p);

%A.bar method nodes
    \node [supergraph_y] (st_a_bar) [right = 6*\dist of st_a_foo] {\textsf{start}$_{\texttt{A.bar}}$};
    \node [supergraph_y] (end_a_bar) [below = \dist of st_a_bar.south west,anchor = west] {\textsf{end}$_\texttt{A.bar}$};

    \node [n,label=\texttt{s}] (st_a_bar_s) [left=\nd of st_a_bar.west] {};
    \node [n,label=$\Lambda$] (st_a_bar_z) [left=\nd of st_a_bar_s] {};
    \node [n] (end_a_bar_s) [left=\nd of end_a_bar.west] {};    
    \node [n] (end_a_bar_z) [left=\nd of end_a_bar_s] {};
%A.bar method edges
    \path[->](st_a_bar_z) edge (end_a_bar_z);
    \path[->,dashed](call_bar_z) edge [out=20,in=229] (st_a_bar_z);
    \path[->,dashed](end_a_bar_z) edge [out=220,in=35] (return_bar_z);
    \path[->](st_a_bar_s) edge (end_a_bar_s);
    \path[->,dashed](call_bar_v) edge [out=20,in=230] node[arrowtext,near end,above left=-.1cm and -.15cm,rotate=36]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (st_a_bar_s);

%B.foo method nodes
    \node [supergraph_f] (st_b_foo) [right = 6*\dist of call_bar] {\textsf{start}$_{\texttt{B.foo}}$};
    \node [supergraph_f] (return_not_secret) [below = \dist of st_b_foo.south west, anchor=west] {\texttt{return "not secret"}};
    \node [supergraph_f] (end_b_foo) [below = \dist of return_not_secret.south west,anchor = west] {\textsf{end}$_\texttt{B.foo}$};

    \node [n,label=$\Lambda$] (st_b_foo_z) [left=\nd of st_b_foo.west] {};
    \node [n] (return_not_secret_z) [left=\nd of return_not_secret.west] {};
    \node [n] (end_b_foo_z) [left=\nd of end_b_foo.west] {};

%B.foo method edges
    \path[->](st_b_foo_z) edge (return_not_secret_z); 
    \path[->](return_not_secret_z) edge (end_b_foo_z); 
    \path[->,dashed](call_foo_z) edge [out=-60,in=160,color=lightsalmonpink] (st_b_foo_z);
    \path[->,dashed](end_b_foo_z) edge [out=145,in=-65,color=lightsalmonpink] (return_foo_z);

%B.bar method nodes
    \node [supergraph_f] (st_b_bar) [right = 6*\dist of st_b_foo] {\textsf{start}$_{\texttt{B.bar}}$};
    \node [supergraph_f] (print) [below = \dist of st_b_bar.south west,anchor = west] {\texttt{print(s)}};
    \node [supergraph_f] (end_b_bar) [below = \dist of print.south west,anchor = west] {\textsf{end}$_\texttt{B.bar}$};

    \node [n,label=\texttt{s}] (st_b_bar_s) [left=\nd of st_b_bar.west] {};
    \node [n] (print_s) [left=\nd of print.west] {};
    \node [n] (end_b_bar_s) [left=\nd of end_b_bar.west] {};
    \node [n,label=$\Lambda$] (st_b_bar_z) [left=\nd of st_b_bar_s] {};
    \node [n] (print_z) [left=\nd of print_s] {};
    \node [n] (end_b_bar_z) [left=\nd of end_b_bar_s] {};
%B.bar method edges
    \path[->](st_b_bar_z) edge (print_z);
    \path[->](print_z) edge (end_b_bar_z);
    \path[->](st_b_bar_s) edge (print_s);
    \path[->](print_s) edge (end_b_bar_s);
    \path[->,dashed](call_bar_z) edge [out=40,in=140,color=lightsalmonpink] (st_b_bar_z);
    \path[->,dashed](call_bar_v) edge [out=20,in=160,color=lightsalmonpink] node[arrowtext,above right=-.4cm and .4cm,rotate=-10]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$} (st_b_bar_s);
    \path[->,dashed](end_b_bar_z) edge [out=210,in=-40,color=lightsalmonpink] (return_bar_z);    
}
\end{tikzpicture}
  \caption[An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}]{An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}. All non-labeled edges are implicitly labeled with identity functions $\id$. The variable corresponding to an initial secret value is denoted as $\psi$.}%
  \label{fig:cc_edgefn_example}%
  \end{figure}
\end{example}

\begin{definition}
  For an IFDS problem $P=(G^\#)$ and a set $S$, the correlated-calls transformation $\transCC_S$ is defined as
  \begin{equation}
    \transCC_S((G^\#))=\left(G^\#,\,\lcc_S,\,\ccedgefn S\right),
  \end{equation}
  where $\lcc_S:\,S\to2^T$.
\end{definition}

Then, for an edge $e$, the correlated-call micro functions can be defined as $\ccedgefn R$ and a correlated-calls transformation is defined as $\transCC_R$.

\paragraph{Converting IDE Results to IFDS Results}

Let $P$ be an IFDS problem. 
Let $E:\,N\times D$ be the domain of the IDE result $\result(Q)$.
To convert $\result(\transCC_R(P))$ to an IFDS result, we need to map the control-flow-supergraph nodes $n\in N^*$ to the corresponding facts $d\in D$. 
Unlike in~$\backEq$, we will only map each~$n$ to the facts~$d$ for~which~$\result(\transCC_R(P))(n,\,d)$ does not contain an~empty mapping for~any~receiver.

For a node $n\in N^*$ and a correlated-calls IDE problem result $\rho=\result(\transCC_S(P))$, let $D_n^\Subset(\rho)$ be a set of data-flow facts defined as
\begin{equation}\label{eq:dnq}
  D_n^\Subset(\rho)=\left\{d\ |\ 
    d\in\mvp F(n)\,\wedge\,\forall r\in R:\ \rho(n,\ d)(r)\ne\top_T\right\}.
\end{equation}
Then, for a set $S\subseteq R$, the~correlated-calls-conversion function from a~correlated-calls IDE~result $\rho$ to~an~IFDS~result looks as~follows:
\begin{equation}\label{eq:ucc}
  \backCC\left(\rho\right)=
    \left\{(n,\,D_n^\Subset(\rho)\ | \ n\in N^*\right\}.
\end{equation}

In the following lemma we show that the result of an IDE problem obtained through a correlated-calls transformation is a subset of the original IFDS result.

\begin{lemma}[Precision]\label{lem:subsetifds}
    For an IFDS problem $P$ and all ${n\in N^*}$,
    \begin{equation}\label{eq:correct}
      \backCC\left(\result(\transCC_R(P))\right)(n)
      \subseteq
      \result_{\text{IFDS}}(P)(n)\,.
    \end{equation}
\end{lemma}
\begin{proof}
  The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
  \begin{align*}
    \backCC\left(\result(\transCC_R(P))\right)(n)&=\{(n',\,D_n'^\Subset(\result(\transCC_R(P))))\ |\ n\in N^*\}(n)\\
      &=D_n^\Subset(\result(\transCC_R(P)))\\
      &\subseteq\mvp F(n)\\
      &=\result_\text{IFDS}(P)(n)\,.\qedhere
  \end{align*}
\end{proof}

We will next show, in Lemma~\ref{lem:sound}, that our analysis is sound, i.e. that the result of an IDE problem obtained through a correlated-calls transformation removes only facts that occur on infeasible paths. To prove the Soundness Lemma, we first introduce Lemmas~\ref{lem:sound1} and~\ref{lem:sound3}.

We will denote the top element in the environment lattice as
\begin{equation}
  \Omega=\lambda d\,.\,\topcc\,.
\end{equation}

For the purpose of the proofs, we will rewrite Equation~\eqref{eq:edgefndef} that defines an edge function as follows:
  \begin{equation}\label{eq:edgefnThroughDelta}
    \ccedgefn S=\lambda e\,.\,
    \begin{cases}
      \id&\text{if $d_1=d_2=\Lambda$,}\\
      \lambda m\,.\,\varepsilon(e)(\delta(m))&\text{otherwise},
    \end{cases}
  \end{equation}
  where $S\subseteq R$, $d_1$ and $d_2$ are the source and target facts, and for a map $m\in\lcc_U$, $\delta(m)$ is either $m$ or $\botcc$:
  \begin{equation}\label{eq:deltadef}
    \delta(m)=\begin{cases}
      \botcc&\text{if $d_1=\Lambda$}\\
      m&\text{otherwise.}
    \end{cases}
  \end{equation}

Additionally, for a path $p=[\startmain,\,\dots]$ and a fact $d\in D$, we will denote the lattice element that is mapped to $d$ according to the flow functions of path $p$ as follows:
\begin{equation}
  \mpd=\menv(p)(\Omega)(d)\,.
\end{equation}

The following Lemma shows that the lattice elements (receiver-to-types maps) of a correlated-calls IDE analysis correctly overapproximate the possible types of a receiver in a program execution.

\begin{lemma}\label{lem:sound1}
Let $p=[\startmain,\,\dots,\,n]$ be some concrete execution trace of the program, and let $r\in R$ be a receiver. If after the execution trace $p$, at node $n$, $r$ points to an object of runtime type~$t$, and $d\in D$ is a fact such that $d\in M_F(p)(\varnothing)$, then
  \begin{equation}
    t\in\mpd(r)\,.
  \end{equation}
\end{lemma}
\begin{proof}
  By induction on the length of the trace.

  \textit{Basis:} $p=[\startmain]$. Then there is no instruction at which a receiver $r$ could be instantiated, and the Lemma is trivially true.

  \textit{Induction hypothesis:} Let $p=[\startmain,\,\dots,\,n_{k-1}]$, and let $\uptau$ be the set of types to which $\mpdkm$ maps $r$:
  \begin{equation}
    \uptau=\mpdkm(r)\,.
  \end{equation}
  Assume that for a concrete execution path $p=[\startmain,\,\dots,\,n_{k-1}]$, at node $(n_{k-1},\,d_{k-1})$, the Lemma holds, i.e. $t\in\uptau$.

  \textit{Induction step:} Let $p'=[\startmain,\,\dots,n_{k-1},\,n_k]$ and $t'\in T$ be the type to which $r$ is mapped at $n_k$.

  For each $i$, let $e_i$ be the edge $((n_{i-1},\,d_{i-1}),\,(n_i,\,d_i))$. Note that $$e_1=((\startmain,\,\Lambda),\,(n_1,\,d_1))\,.$$

  Observe that
  \begin{align*}
    \mppd
    &=\menv(p')(\Omega)(d)\\
    &=\left(\menv(e_k)\circ\menv(e_{k-1})\circ\ldots\circ\menv(e_1)\right)(\Omega)(d)\\
    &=\menv(e_k)\left(\menv(p)(\Omega)\right)(d)\,.
  \end{align*}

  According to~\eqref{eq:envTransToEdgeFnEdge},
  \begin{align*}
    &\menv(e_k)\left(\menv(p)(\Omega)\right)(d)(r)\\
      =&\bigg(\ccedgefn R((n_{k-1},\,\Lambda),\,(n_k,\,d))(\topcc)\sqcap\\
       &\bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\Omega)(d'))\bigg)(r)\\
      \supseteq&
        \bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\Omega)(d'))(r)\\
      \supseteq&\,\ccedgefn R((n_{k-1},\,d_{k-1}),\,(n_k,\,d))(\mpdkm)(r)\,.
  \end{align*}
  Therefore, 
  \begin{equation}\label{eq:musubset}
    \efek\subseteq\mppd(r)\,.
  \end{equation}

  We will now show that
  \[
    t'\in\efek\,,
  \]
  which, due to~\eqref{eq:musubset}, means that the Lemma holds.

  According to~\eqref{eq:edgefnThroughDelta}, there are two cases in which $\ccedgefn R(e_k)$ could fall.

  If $d_{k-1}=d_k=\Lambda$, then $d_k\notin M_F(p)(\varnothing)$, since it does not belong to the set $D$, and the Lemma trivially holds.

  Otherwise, 
  \[
    \ccedgefn R(e_k)=\lambda m\,.\varepsilon(e_k)(\delta(m))\,.
  \]
  It follows that
  \begin{align}\label{eq:efek}
    \efek
    &=(\lambda m\,.\varepsilon(e_k)(\delta(m)))(\mpdkm)(r)\notag\\
    &=\varepsilon(e_k)(\delta(\mpdkm))(r).
  \end{align}
  Let us denote the lattice element $\delta(\mpdkm)$ with $\Delta$:
  \[
    \Delta=\delta(\mpdkm)\,.
  \]
  Note that since $\Delta$, according to~\eqref{eq:deltadef}, can be either $\botcc$ or $\mpdkm$, it always maps $r$ to a set containing~$t$:
  \begin{equation}\label{eq:deltaContainsT}
    t\in\Delta(r)\,.
  \end{equation}
  Note also that unless the instruction at $n_{k-1}$ contains an assignment for $r$, $r$ is mapped to the same object of type $t$ as at node $n_{k-1}$, and $t=t'$. Therefore, for the non-assignment instructions, it is sufficient to prove that $t\in\Delta(r)$.

   Depending on the instructions at the nodes $n_{k-1}$ and $n_k$, there are four cases:
  \begin{enumerate}
    \item\label{item:asgn} The instruction at $n_{k-1}$ is an assignment for a receiver $r'\in R$.
        Since $\varepsilon_R(e_k)=\lambda m\,.\,m[r'\to\bot_T]$,
        \begin{align*}
          \efek&=            
            (\lambda m\,.\,m[r'\to\bot_T])(\Delta)(r)\\
          &=\Delta[r'\to\bot_T](r)\,.
        \end{align*}
      In the resulting map, $r'$ is mapped to $\bot_T$. Then

      \begin{enumerate}
        \item if $r=r'$, then $\efek=\bot_T$, which contains $t'$.
        \item\label{item:defaultmap} If $r\ne r'$, then $r$ has not been reassigned a value, and still maps to the same object of type $t$. The receiver $r$ is mapped to $\Delta(r)$, which, according to~\eqref{eq:deltaContainsT}, contains $t$. Since $t=t'$, $\Delta(r)$ contains $t'$.
      \end{enumerate}
    \item\label{item:callstart} $e_k$ is a call-start edge with signature $s_\mathcal F$, and $f\in\mathcal F$ is the called procedure.
      Then
        \begin{align*}
          \efek
          &=(\lambda m\,.\,m[r'\to m(r')\cap\tau(s_\mathcal F,\,f)])(\Delta)(r)\\
          &=\Delta[r'\to\Delta(r')\cap\tau(s_\mathcal F,\,f)]\,,
        \end{align*}
      where $r'$ is the receiver of the call.
      \begin{itemize}
        \item If $r'=r$, then $\Delta(r')=\Delta(r)$ which contains $t$. Since $t\in\tau(s_\mathcal F,\,f)$, it follows that $t\in\Delta(r)\cap\tau(s_\mathcal F,\,f)$, and $t\in\efek$.
         \item If $r'\ne r$, see~(\ref{item:defaultmap}).
       \end{itemize}
    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_k\in R$ are the local variables in the callee method, $r'$ is the receiver of the call site corresponding to the return node $n_k$, and $f\in\mathcal F$ is the called method with signature~$s_\mathcal F$.
      Then 
      \[
        \varepsilon_R(e_k)=\lambda m\,.\,m[r'\to m(r')\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_k\to\bot_T].
      \]
      If $r\in\{r_1,\,\dots,\,r_k\}$, see~Case~\ref{item:asgn}. Otherwise, the case is analogous to Case~\ref{item:callstart}.
    \item\label{item:idcase} The node contains any other instruction.
      Then 
      \[
        \ccedgefn R(e_k)(\mpdkm)(r)=\id(\Delta)(r)=\Delta(r),
      \]
      which contains $t$ according to~\eqref{eq:deltaContainsT}.\qedhere
  \end{enumerate}
\end{proof}

We will now show that on a node of a concrete execution path, the correlated-calls analysis does not map receivers to $\top_T$. In other words, the analysis never considers nodes of a concrete execution path unreachable.

\begin{lemma}\label{lem:sound3}
  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, $r\in R$ a receiver, and $d\in D$ a data-flow fact. Then if $d\in M_F(p)(\varnothing)$,
  \begin{equation}
    \mpd(r)\ne\top_T\,.
  \end{equation}
\end{lemma}
\begin{proof}
  By induction on the length of the execution trace.

  \textit{Basis:} 
    Let $p=[\startmain]$. Since the only realizable path corresponding to $p$ is $[(\startmain,\,\Lambda)]$, there is no fact $d\in D$ such that $d\in M_F(p)(\varnothing)$, and the claim follows immediately.

  \textit{Induction hypothesis:} 
  Let $p=[\startmain,\,\dots,\,n_{k-1}]$. Let $\uptau$ be the set of types to which $r$ is mapped by $\mpdkm$:
  \begin{equation}
    \uptau=\mpdkm(r)\,.
  \end{equation}
  Assume the Lemma holds for that for a concrete execution path $$p=[\startmain,\,n_1,\,\dots,\,n_{k-1}]\,,$$ i.e. $\uptau\ne\top_T$ for an arbitrary $r\in R$ and $d_{k-1}\in D$.

  \textit{Induction step:}
    Let $p'=[\startmain,\,n_1,\,\dots,n_{k-1},\,n_k]$ be a concrete execution path.

    Let $e_k=((n_{k-1},\,d_{k-1}),\,(n_k,\,d))$. As shown in~\eqref{eq:musubset},
    \begin{align*}
      \mppd(r)
        &\supseteq\ccedgefn R(e_k)(\mpdkm)(r)\,.
    \end{align*}

    From Definition~\ref{def:edgefn}, we can see that unless $e_k$ is a call-start edge or an end-return edge, the result follows from the induction hypothesis.
    More formally, if $e_k$ is not a call-start or end-return edge, then for all $m\in\lcc_R$,
    \[
      \ccedgefn R(e_k)(m)\sqsubseteq m\,.
    \]
     The edge function corresponding to the call-start and end-return edges is the only place in which the set of types that a receiver maps to can be reduced.

    Assume that $e_k$ is a end-return edge with a call on the receiver $r'\in R$ with a signature $s_\mathcal F$ to a function $f\in\mathcal F$.
    \begin{align*}
      \ccedgefn R&(e_k)(\mpdkm)(r)\\
      &=\left(\lambda m\,.\,m[r'\to m(r)\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(\mpdkm)(r)\\
      &=\left(\mpdkm[r'\to \uptau\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(r)\,,
    \end{align*}
  where $r_1,\,\dots,r_l\in R$ are the local variables in the called method.

    If $r\in\{r_1,\,\dots,\,r_l\}$, then $\efek=\bot_T\ni t$\footnote{In the case of a recursive call, it is possible that both $r\in\{r_1,\,\dots,\,r_l\}$ and $r=r'$.
    In that case, the set to which $r$ will be mapped would be still ``overwritten'' by $\bot_T$.}.

    Otherwise, if $r=r'$, then $\efek=\uptau\cap\tau(s_\mathcal F,\,f)$.

    According to Lemma~\ref{lem:sound1} and by the induction hypothesis, the runtime type $t$ of $r$ must be contained in $\mpdkm(r)=\uptau$. At the same time, by definition, $t$ is part of $\tau(s_\mathcal F,\,f)$. Therefore, $t\in\uptau\cap\tau(s_\mathcal F,\,f)\subseteq\efek$, which means that $\efek\ne\top_T$.

    The same reasoning applies to the case where $e_k$ is a call-start edge.
\end{proof}

Finally, we will prove the soundness of the correlated-calls analysis: we will show that our analysis only considers a path infeasible if it cannot occur in a concrete execution of a program.

\begin{lemma}[Soundness]\label{lem:sound}
  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, and let $d\in D$.
  If $d\in M_F(p)(\varnothing),$
  then
  \begin{equation}
    d\in \backCC\left(\result(\transCC_R(P))\right)(n)\,.
  \end{equation}
\end{lemma}
\begin{proof} Let $\rho=\result(\transCC_R(P))$. Then
  \begin{align*}
    \backCC(\rho)(n)
    &=D_n^\Subset(\rho)\\
    &=\left\{d'\ |\ 
        d'\in\mvp F(n)\,\wedge\,\forall r\in R:\ \rho(n,\ d')(r)\ne\top_T\right\}.
  \end{align*}
  Since $\mvp F(n)=\bigsqcap_{q\in\ivp(n)}M_F(q)(\varnothing)$, and $p\in\ivp(n)$, it follows that
    \begin{align*}
      d&\in M_F(p)(\varnothing)\\&\subseteq\mvp F(n)\,.
    \end{align*}
  At the same time, for all receivers $r\in R$,
  \begin{align*}
    \rho(n,\,d)(r)
    &=\left(\bigsqcap_{q\in\ivp(n)}\mpddef q d\right)(r)\\
    &=\bigsqcap_{q\in\ivp(n)}\mpddef q d(r)\,.
  \end{align*}
  According to~Lemma~\ref{lem:sound3}, $\mpd(r)\ne\top_T$.
  Since $p\in\ivp(n)$,
  \begin{align*}
    \mpd(r)\subseteq\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)\,.
  \end{align*}
  From $\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)=\rho(n,\,d)(r)$ it follows that
  $\mpd(r)\subseteq\rho(n,\,d)(r)$.
  Therefore, $\rho(n,\,d)(r)\ne\top_T$, and $d\in D_n^\Subset(\rho)=\backCC(\rho)(n)$.
\end{proof}

\paragraph{Correlated-Call Receivers}\label{sec:ccreceivers}
We will now show that in a correlated-calls transformation, it is enough to consider only some of the receivers of set $R$.

\begin{definition}
Let $c_1$ and $c_2$ be two call sites on a receiver $r\in R$.
  If both call sites are polymorphic, then we say that $r$ is a \textit{correlated-call receiver}.
\end{definition}
In other words, a correlated-call receiver is a receiver that has at least two polymorphic call invocations.
We will denote the set of correlated-call receivers as $\rcc$.

We will describe a ``reduced'' correlated-calls transformation in which we only consider receivers from $\rcc$ and ignore other receivers of $R$. We will show that IDE problems obtained through ordinary and reduced correlated-calls transformations yield the same results.

The following Lemma shows that the types to which a given receiver is mapped in the result of the algorithm is not affected by other receivers and the types to which they are mapped.

\begin{lemma}\label{lem:recindepedgefn}
  Let $P$ be an IFDS problem. Let $N^*$ be the supergraph for $P$, $D$ the set of data-flow facts, $n\in N^*$ a node, and $p=[\startmain,\,\dots,\,n]$ a path in the supergraph. Let $d\in D\cup\{\Lambda\}$.
  Then for any realizable path $p'\in\textsf{RP}(p,\,d)$, set $S\subseteq R$, and receiver $r\in S$,
  \begin{equation}
    \ccedgefn S(p')(\topcc)(r)=
    \ccedgefn{\{r\}}(p')(\topcc)(r)\,.
  \end{equation}
\end{lemma}
\begin{proof}
  By induction on the length of $p$.

  \textit{Basis:} $p'=[(\startmain,\,\Lambda)]$. Then $\ccedgefn S(p')=\id=\ccedgefn{\{r\}}(p')$, and the Lemma follows directly.

  \textit{Induction hypothesis:} Suppose that for a path $q=[(\startmain,\,\Lambda),\,\dots,\,(n_{k-1},\,d_{k-1})]$, where $q\in\textsf{RP}(n,\,d)$, the Lemma holds, i.e. both edge functions map $r$ to the same set of types $\uptau$:
  \begin{align*}
    \uptau
    &=\ccedgefn S(q)(\topcc)(r)\\
    &=\ccedgefn{\{r\}}(q)(\topcc)(r)\,.
  \end{align*}

  \textit{Induction step:} Let $q'=[(\startmain,\,\Lambda),\,\dots,\,(n_{k-1},\,d_{k-1}),\,(n_k,\,d_k)]$ and the edge $e_k=((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))$.

  Observe that for any set $U\subseteq R$ such that $r\in U$,
  \begin{align}\label{eq:edgefnU}
    \ccedgefn U(q')(\topcc)(r)
    &=\ccedgefn U(e_k)(\ccedgefn U(q)(\topcc))(r)\,.
  \end{align}

  We can see from~\eqref{eq:edgefnThroughDelta} that there are two cases.

  If $d_{k-1}=d_k=\Lambda$, $\ccedgefn S(e_k)=\id=\ccedgefn{\{r\}}(e_k)$, and, due to~\eqref{eq:edgefnU},
  \begin{align*}
    \ccedgefn S(q')(\topcc)(r)&=\uptau\\
    &=\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
  \end{align*}

  Otherwise, there are four sub-cases.
  \begin{enumerate}
    \item $e_k$ is a call-start edge, $r'.c()$ is the call site at $n_{k-1}$ with signature $s_\mathcal F$, $f\in\mathcal F$ is the called procedure, and $r'\in U$.
    Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\delta(m)(r)\cap\tau(s_\mathcal F,\,f)]\,.
    \]
    There are two sub-cases.
    \begin{enumerate}
      \item\label{item:callstartreceq} If $r=r'$, then, according to~\eqref{eq:edgefnU}, the resulting set of types 
        \[
          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\cap\tau(s_\mathcal F,\,f).
        \]
        If $d_{k-1}=\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\botcc(r)=\bot_T$. If $d_{k-1}\ne\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\ccedgefn U(q)(\topcc)(r)=\uptau$. The set $\tau(s_\mathcal F,\,f)$ is the same for either case.

        Therefore, the value of $\ccedgefn U(q')(\topcc)(r)$ has the same result regardless of $U$,
        which means that $\ccedgefn S(q')(\topcc)(r)=\ccedgefn{\{r\}}(q')(\topcc)(r)$, and the Lemma holds.
      \item\label{item:callstartrecneq} If $r\ne r'$, then
        \begin{equation}
          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\,,
        \end{equation}
        which, as we have seen in~Case~\eqref{item:callstartreceq}, does not depend on~$U$, and the Lemma holds.
    \end{enumerate}
    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_l\in U$ are the local variables in the callee method, $r'.c()$ is the call corresponding to the return node at $n_k$, $f\in\mathcal F$ is the called method with signature $s_\mathcal F$, and $r'\in U$.
    Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)
      [r'\to\delta(m)(r)\cap\tau(s_\mathcal F,\,f)]
      [r_1\to\bot_T]\ldots[r_l\to\bot_T]\,.
    \]
    There are three sub-cases.
    \begin{enumerate}
      \item\label{item:localvarrec} If $r\in\{r_1,\,\dots,\,r_l\}$, then regardless of the value of $U$,
      \[
        \ccedgefn U(q')(\topcc)(r)=\bot_T\,,
      \]
      and the Lemma holds.
      \item Otherwise, if $r=r'$, the case is analogous to Case~\eqref{item:callstartreceq}.
      \item If $r\notin\{r',\,r_1,\,\dots,\,r_l\}$, then see Case~\eqref{item:callstartrecneq}.
    \end{enumerate}
    \item $n_{k-1}$ contains an assignment for $r'\in U$. Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\bot_T]\,.
    \]
    If $r=r'$, see Case~\eqref{item:localvarrec}. If $r\ne r'$, see Case~\eqref{item:callstartrecneq}.
    \item Otherwise,
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)\,,
    \]
    and the case is analogous to Case~\eqref{item:callstartrecneq}.\qedhere
  \end{enumerate}
\end{proof}

The following Lemma shows that the correlated-calls analysis computes the results for each receiver independently, or separately. To compute the set of types to which a receiver~$r$ is mapped at each exploded-graph node, we can exclude all other receivers in the program from the analysis (recall from~\eqref{eq:edgefndef} that the set of receivers that are considered in the analysis is specified by the set $S$ in a correlated-calls transformation $\transCC_S$). Therefore, for a given receiver $r$, the results of a $\transCC_S$- and a $\transCC_{\{r\}}$-analysis are the same.

\begin{lemma}\label{lem:recindep} Let $P$ be an IFDS problem. Let $N^*$ be the supergraph for $P$, $D$ the set of data-flow facts, and $S\subseteq R$ a set of receivers.
  Then for any $n\in N^*$, $d\in D$, and receiver $r\in S$,
  \begin{equation}
    \result\left(\transCC_S(P)\right)(n,\,d)(r)=
    \result(\transCC_{\{r\}}(P))(n,\,d)(r)\,.
  \end{equation}
\end{lemma}
\begin{proof}
  According to~\eqref{eq:ideresult}, \eqref{eq:mvpdef}, and~\eqref{eq:envTransToEdgefn},
  \begin{align}
    \result\left(\transCC_S(P)\right)(n,\,d)(r)
    &=\mvp{\textsf{Env}}(n,\,d)(r)\notag\\
    &=\left(\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\Omega)(d)\right)(r)\notag\\
    &=\left(\bigsqcap_{q\in\ivp(n)}\bigsqcap_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)\right)(r)\notag\\
    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)(r)\,.\label{eq:resultThroughEdgefn}
  \end{align}
  Then from Lemma~\ref{lem:recindepedgefn},
  \begin{align*}
    \result\left(\transCC_S(P)\right)(n,\,d)(r)
    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\\
    &=\result\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)\,.\qedhere
  \end{align*}
\end{proof}

The next lemma shows that the set of types to which a receiver is mapped in a correlated-calls lattice element can be represented as an intersection of static-type function applications $\tau(s_{\mathcal F_i},\,f_i)$.
\begin{lemma}\label{lem:edgefnThroughTaus}
  For an IFDS problem $P$, a node $n\in N^*$, and fact $d\in D$, let $p\in\mathsf{RP}(n,\,d)$ be a realizable path and $r\in R$ a receiver. Then there exists a non-negative number $\gamma$ of calls on the receiver $r$ with signatures $s_{\mathcal F_\gamma}$ to the functions $f_\gamma\in\mathcal F_\gamma$, for which
  \[
    \ccedgefn{\{r\}}(p)(\topcc)(r)=
      \bigcap_{\gamma\ge0}\tau(s_{\mathcal F_\gamma},\,f_\gamma)\,.
  \]
\end{lemma}
\begin{proof}
  Let $p$ have the following form\footnote{It can be shown from the definition of a pointwise representation in~Sagiv et al.~\cite{sagiv1996precise} that in a realizable path, there is never an edge from a fact of the set $D$ to a $\Lambda$ fact. Therefore, we can represent $p$ as a sequence of nodes that has a prefix of $\Lambda$-fact nodes, after which all nodes are non-$\Lambda$ facts.}:
  \[
    p=[(\startmain,\,\Lambda),\,(n_1,\,\Lambda),\,\dots,\,(n_k,\,\Lambda),
       (n_{k+1},\,d_{k+1}),\,\dots,\,(n_{k+l},\,d_{k+l})]\,,
  \]
  where $l\ge1$ and the facts for all nodes up to $n_k$ are equal to $\Lambda$ and $d_{k+i}\in D$ for $0<i\le l$.

  As previously, for all $i$, we will denote the edge $(n_i,\,n_{i+1})$ by $e_i$.

  From~\eqref{eq:edgefndef} we can infer that
  \[
    \ccedgefn{\{r\}}(p)=
    \ccedgefn{\{r\}}(e_{k+l})
    \circ\ldots
    \circ\ccedgefn{\{r\}}(e_{k+2})
    \circ(\lambda m\,.\,\beta)
    \circ\id
    \circ\ldots
    \circ\id\,,
  \]
  where
  \[
    \beta=
    \begin{cases}
      \botcc[r\to\tau(s_\mathcal F,\,f)]&\text{if $(n_k,\,n_{k+1})$ is a call-start or end-return edge, and}\\&\text{the call site $r.c()$ with signature $s_\mathcal F$ to the function}\\
      &\text{$f\in\mathcal F$ corresponds to the call-start or end-return edge,}\\
      \botcc&\text{otherwise\footnotemark.}
    \end{cases}
  \]
  \footnotetext{Since $d_k=\Lambda$ and $d_{k+1}\ne\Lambda$, the micro function for the edge $e_{k+1} $ is equal to $\lambda m\,.\,\varepsilon_{\{r\}}(e_{k+1})(\botcc)$. From the definition of $\varepsilon_S$~\eqref{eq:varepsilon} we can see that the only case where $\varepsilon_{\{r\}}(e_{k+1})(m)$ would not be equal to $\botcc$ is when $e_{k+1}$ is call-start or end-return edge.}

  Therefore,
  \begin{align}\label{eq:edgefnbeta}
    \ccedgefn{\{r\}}(p)(\topcc)
      &=\left(\ccedgefn{\{r\}}(e_{k+l})\circ\ldots\circ
        \ccedgefn{\{r\}}(e_{k+2})\right)((\lambda m\,.\,\beta)(\topcc))\notag\\
      &=\left(\ccedgefn{\{r\}}(e_{k+l})\circ\ldots\circ
        \ccedgefn{\{r\}}(e_{k+2})\circ\id\right)(\beta)\,.
  \end{align}

We can now prove the lemma by induction on $l$.

\textit{Basis:}
If $l=1$, then $\ccedgefn{\{r\}}(p)(\topcc)=\id(\beta)=\beta$.
There are two cases.

If $\beta=\botcc$, then 
\begin{align*}
  \ccedgefn{\{r\}}(p)(\topcc)(r)&=\beta(r)\\&=\bot_T\,,
\end{align*} and $\gamma=0$.

If $\beta=\botcc[r\to\tau(s_\mathcal F,\,f)]$, then 
\[
  \ccedgefn{\{r\}}(p)(\topcc)(r)=\tau(s_\mathcal F,\,f)\,,
\]
and $\gamma=1$.

\textit{Induction hypothesis:}
Assume that for a path $p=[(\startmain,\,\Lambda),\,\dots,\,(n_{k+l},\,d_{k+l})]$, the Lemma holds for $\gamma=N$, where $N\ge0$.

\textit{Induction step:}
Let $p'=[(\startmain,\,\Lambda),\,\dots,\,(n_{k+l},\,d_{k+l}),\,(n_{k+l+1},\,d_{k+l+1})]$.

Recall that
\begin{align*}
  \ccedgefn{\{r\}}(p')(\topcc)(r)
  &=\ccedgefn{\{r\}}(e_{k+l+1})\left(\ccedgefn{\{r\}}(p)(\topcc)\right)(r)\,.
\end{align*}

From~\eqref{eq:varepsilon} we can see that unless $e_{k+l+1}$ is a call-start or end-return edge corresponding to a call on the receiver $r$, then $\ccedgefn{\{r\}}(e_{k+l+1})(r)$ must be equal to either $\bot_T$ or $m(r)$, where $m=\ccedgefn{\{r\}}(p)(\topcc)$.

If $\ccedgefn{\{r\}}(e_{k+l+1})(r)=\bot_T$, then the Lemma holds for $\gamma=0$.

Otherwise,
\begin{align*}
  \ccedgefn{\{r\}}(e_{k+l+1})(\topcc)(r)&=\ccedgefn{\{r\}}(p)(\topcc)(r)\\
  &=\bigcap_{N}\tau(s_{\mathcal F_N},\,f_N)\,,
\end{align*}
and therefore $\gamma=N$.

Suppose that $e_{k+l+1}$ is a call-start edge with a call on the receiver $r$ with signature $s_\mathcal G$ to a function $g\in\mathcal G$. Then, according to~\eqref{eq:varepsilon}, 
\[
  \ccedgefn{\{r\}}(e_{k+l+1})=\lambda m\,.\,m[r\to m(r)\cap\tau(s_\mathcal G,\,g)]\,.
\]
Therefore,
\begin{align*}
  \ccedgefn{\{r\}}&(p')(\topcc)(r)\\
  &=\lambda m\,.\,m[r\to m(r)\cap\tau(s_\mathcal G,\,g)]\left(\ccedgefn{\{r\}}(p)(\topcc)\right)(r)\\
  &=\ccedgefn{\{r\}}(p)(\topcc)(r)\cap\tau(s_\mathcal G,\,g)\\
  &=\left(\bigcap_{N}\tau(s_{\mathcal F_N},\,f_N)\right)\cap\tau(s_\mathcal G,\,g)\,,
\end{align*}
and the Lemma holds for $\gamma=N+1$.

The case where $e_{k+l+1}$ is an end-return edge is analogous to the previous case.
\end{proof}

We now show that a receiver will be only mapped to $\topcc$ if it is the receiver of a correlated call.

\begin{lemma}\label{lem:ccrectop}
   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a dataflow fact such that there exists a realizable path $p\in\textsf{RP}(n,\,d)$. Let $T$ be the set of all types in the program.
   If there exists a receiver $r\in R$ such that
  \[
    \ccedgefn{\{r\}}(p)(\topcc)(r)=\top_T\,,                       
  \]
  then $r\in \rcc$.
\end{lemma}
\begin{proof}
 According to Lemma~\ref{lem:edgefnThroughTaus},
 \[
   \ccedgefn{\{r\}}(p)(\topcc)(r)=
      \bigcap_{\gamma\ge0}\tau(s_{\mathcal F_\gamma},\,f_\gamma).
 \]

 Let $\tau_i=\tau(s_{\mathcal F_i},\,f_i)$. 
 For a given $k$, let $r.m_k()$ be the call site corresponding to $\tau_k$, and $T'$ the set of types compatible with the static type of $r$.
 Recall from Section~\ref{sec:ef} that 
 \begin{itemize}
   \item $\tau_k\ne\top_T$;
   \item if $\tau_k=T'$ then the corresponding call site is monomorphic;
   \item if $\tau_k\subset T'$ then the call site is polymorphic.
 \end{itemize}

 From the conditions of the Lemma, 
 \begin{equation}
   \bigcap_{\gamma\ge 0}\tau_\gamma=\top_T\,.
 \end{equation}

 If all $\tau_k=T'$, then $\bigcap_{\gamma\ge 0}\tau_\gamma$ is also equal to $T'$. Since $T'\ne\top_T$, this is a contradiction.

 If exactly one $\tau_k\subset T'$ and the rest are equal to $T'$, then $\bigcap_{\gamma\ge 0}\tau_\gamma$ is equal to $\tau_k$, which cannot be $\top_T$ either.

 Therefore, there are at least two sets, $\tau_i$ and $\tau_j$, which are strict subsets of $T'$. Since both $\tau_i$ and $\tau_j$ are non-empty and their intersection equals $\top_T$, $\tau_i$ and $\tau_j$ must be disjoint. If $\tau_i$ and $\tau_j$ are disjoint, they must correspond to different call sites.

 In other words, there are at least two calls on the same receiver for which the static-type function is a strict subset of the set of types compatible with a given receiver $r$. It follows that both calls have to be polymorphic. Therefore,~${r\in\rcc}$.
\end{proof}

We will now show that if a receiver ever gets mapped to top, then it is a correlated-calls receiver.

\begin{lemma}\label{lem:ccrectop}
   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a dataflow fact such there exists a realizable path $p\in\textsf{RP}(n,\,d)$.
   Then, if there exists a receiver $r\in R$, such that
  \[
    \result\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)=\top_T\,,
  \]
  then $r\in \rcc$.
\end{lemma}
\begin{proof}
  As shown in~\eqref{eq:resultThroughEdgefn},
  \[
    \result\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
  \]
  Since the latter is equal to $\top_T$, it follows that for each realizable path $p'$ to node $n$, $\ccedgefn{\{r\}}(p')(\top)(r)=\top_T$. According to~Lemma~\ref{lem:ccrectop}, this is only possible if $r\in\rcc$.
\end{proof}

Finally, we show that if a correlated calls analysis considers only correlated-call receivers, no precision is lost. A correlated-calls analysis that considers all receivers computes the same result as an analysis that considers only correlated-call receivers.

\begin{lemma}\label{lem:onlycorrrec}
  Let $P$ be an IFDS problem. Then
  \begin{equation}
    \backCC\left(\result\left(\transCC_\rcc(P)\right)\right)=\backCC(\result\left(\transCC_R(P)\right))\,.
  \end{equation}
\end{lemma}
\begin{proof}
  From~\eqref{eq:ucc} we know that
  \begin{align*}
    \backCC(\result\left(\transCC_R(P)\right))
    &=\left\{(n,\,D_n^\Subset(\result(\transCC_R(P))))\ |\ n\in N^*\right\}.
  \end{align*}
  According to~\eqref{eq:dnq} and~Lemma~\ref{lem:recindep}, for a given $n\in N^*$,
  \begin{align*}
    D_n^\Subset&(\result(\transCC_R(P))))\\
    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall r\in R:\ \left\{(r,\,\result(\transCC_{\{r\}}(P))(n,\,d)(r))\ |\ r\in R\right\}(r)\ne\top_T\right\}\\
    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in R}:\ \result(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}.
  \end{align*}

Since, according to Lemma~\ref{lem:ccrectop}, $\result(\transCC_{\{r\}}(P))(n,\,d)(r)$ can only be equal to $\top_T$ when $r\in\rcc$, we can conclude that
  \begin{align*}
    D_n^\Subset&(\result(\transCC_R(P))))\\
    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in\rcc}:\ \result(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}\\
    &=D_n^\Subset(\result(\transCC_\rcc(P)))).
  \end{align*}

  Therefore,
  \begin{align*}
    \backCC(\result\left(\transCC_R(P)\right))
    &=\left\{(n,\,D_n^\Subset(\result(\transCC_\rcc(P))))\ |\ n\in N^*\right\}\\
    &=\backCC(\result\left(\transCC_\rcc(P)\right))\,.\qedhere
  \end{align*}
\end{proof}

To summarize, Lemma~\ref{lem:sound} shows that the result $\resultCC$ of a correlated-calls analysis is sound since it overapproximates the data flow of all possible concrete execution paths.
We have also shown in Lemma~\ref{lem:subsetifds} that the correlated-calls analysis improves the precision of the original IFDS result $\result_\text{IFDS}$, because the correlated-calls result $\resultCC$ underapproximates an equivalence-IDE result $\resultEq=\result_\text{IFDS}$.
Finally, we showed that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result $\resultCC$ that is obtained when considering all receivers $R$.

This is the general idea of the correlated-calls analysis. The analysis involves a transformation from IFDS to IDE problems. To implement an IDE problem, it is necessary to define a representation of lattice elements and micro functions. An efficient representation of those data structures for the correlated-calls analysis is presented in the next section.

### 2014-11-27 content/intro.tex
changing formatting of thesis according to springer guidelines

\section{Introduction}
Static program analysis aims to discover properties of computer programs without running them.
Static analysis has applications in compiler optimization, development of programming tools, and computer security, among others.
As an example, we might want to analyze a program to know which variables are constants. 
We could then write a compiler optimization that ensures that the values of those variables are computed only once.
Alternatively, we could use the information about constant variables in an integrated development environment; for instance, to notify the user when an if-expression executes only one of its branches because its test condition has a constant value.

There are demonstrable limits on what information we can obtain about a program without running it.
Rice's theorem states that verifying any non-trivial property of a program is an undecidable problem~\cite{rice1953classes}. However, it is sometimes possible to design an algorithm that \textit{over}- or \textit{underapproximates} the solution that we are seeking.

\textit{Data-flow analysis} is an area of program analysis whose goal is to compute approximations of certain information (for example, which variables must be constants) for each program point.

Other examples of data-flow analyses are \textit{reaching definitions} (finding out up to which instruction a given assignment of a variable must be valid) and \textit{available expressions} (retrieving the expressions in the program that do not need to be recomputed at a given program point).

Another example of a data-flow analysis is \textit{taint analysis}~\cite{tripp2009taj}. Taint analysis discovers if ``secret'' values, like passwords or other confidential user information, can leak to an external observer. Methods that generate secret values, e.g. those that read user input, are called \textit{sources}. Methods that can leak information, e.g. those that write data to a file or send data through a network, are called \textit{sinks}. The goal of taint analysis is to find out whether data can propagate from sources to sinks.

An important property of a data-flow analysis is \textit{precision}.
Precision reflects how closely a data-flow-analysis result over- or underapproximates the information we are interested in. In the case of taint analysis, let $T$ be the number of sinks that the analysis considers to leak secret information, and $R$ the real number of potential information leaks. The smaller the difference between $T$ and $R$, the greater the precision of the taint analysis.

Data-flow analyses operate on \textit{control-flow graphs} that model the order in which the instructions of a program are executed.
A data-flow-analysis problem defines \textit{flow functions} that represent how data is propagated along the edges of the control-flow graph. The \textit{confluence operator} specifies how the data that has been computed along different paths should be merged when the paths join.

Since a control-flow graph is an overapproximation of the possible flows of control in concrete executions of a program, the graph may contain \textit{infeasible} paths that cannot occur at runtime.

One way to improve the precision of a data-flow analysis is to detect and eliminate infeasible paths.

Our goal is to improve the precision of solutions to problems that can be solved by the \textit{Inter-procedural Finite Distributive Subset} (IFDS) algorithm~\cite{reps1995precise}.
The IFDS algorithm is a general data-flow algorithm that can compute solutions to various data-flow problems, like reaching definitions, available expressions, and taint analysis.

We improve the precision of IFDS problem solutions by eliminating infeasible paths that occur in object-oriented programs in the presence of \textit{correlated method calls}~--- polymorphic calls that are invoked on the same object~\cite{frank2014correlated}.

\subsection{Correlated Calls}

Consider a call site~$r.m()$ in an object-oriented programming language, where the variable~$r$ is the \textit{receiver} variable of the call site and $m$ is the name of the invoked method\footnote{We assume an internal representation of the program in which for each call site $e_r.m()$, the expression~$e_r$ has been evaluated to the variable~$r$.}. In the rest of the paper, we use the general term \textit{receiver} to mean a receiver variable.
At runtime, the actual method that will be invoked by the call site depends on the runtime type of the object referenced by $r$. If the call site $r.m()$ can be associated with more than one method at compile time, we will say that the call site is \textit{polymorphic}.

For example, in Listing~\ref{list:ccexample}, it is not possible to infer statically whether the runtime type of the variable \verb'a' in line~\ref{line:newa} is \verb'A' or \verb'B'.
The call \verb'a.foo()' can be dispatched to either \verb'A.foo' or \verb'B.foo', and \verb'a.bar(v)' can be dispatched to either \verb'A.bar' or \verb'B.bar'.
A concrete execution path for the main method might therefore go through \verb'A.foo' and \verb'A.bar', or through \verb'B.foo' and \verb'B.bar'.
However, there cannot be an execution path through \verb'A.foo' and \verb'B.bar' or through \verb'B.foo' and \verb'A.bar'.

  \begin{listing}[h]
    \inputMinted{java}{ccexample.java}
    \caption{Example program containing correlated calls}
    \label{list:ccexample}
  \end{listing}

We call the invocations to methods \verb'foo' and \verb'bar' \textit{correlated}.
More generally, correlated calls occur when more than one polymorphic call is invoked on the same receiver variable.

Suppose we wanted to perform a taint analysis on the program in Listing~\ref{list:ccexample}.
Most dataflow-analysis algorithms, including IFDS, would conservatively assume that the call \verb'a.bar' could be dispatched to both \verb'A.bar' and \verb'B.bar', independently of what \verb'a.foo' had been dispatched to in the previous line.

As a result, 
such an analysis would consider a path through \verb'A.foo' and \verb'B.bar' feasible. This means that the variable \verb'v' would be considered secret. We would conclude that a secret value is passed to \verb'B.bar' and printed to the user. In other words, we would consider the program to leak secret information, which it does not do in any concrete execution.

Our technique for improving the precision of an IFDS result is based on transforming the original IFDS problem into a more expressive \textit{Inter-procedural Distributive Environment} (IDE) problem. IDE problems can be solved with the IDE algorithm which is a generalization of IFDS~\cite{sagiv1996precise}. The IDE algorithm can, for instance, solve certain versions of the constant propagation problem that IFDS cannot.

To improve the precision of IFDS results, given an IFDS problem $P$, we convert it into an IDE problem $Q$ that accounts for correlated calls. We then use the IDE algorithm to obtain a solution to $Q$. Finally, we convert the IDE result into a IFDS result. In the presence of correlated calls, the obtained IFDS result can be more precise than the solution that the IFDS algorithm would compute for $P$.

\subsection{IFDS and IDE}
The IFDS framework is a precise and efficient algorithm for data-flow analysis. IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}. The IFDS analysis is a version of the classic \textit{functional approach} to data-flow analysis proposed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.

Given a data-flow problem that satisfies the restrictions of IFDS, the algorithm provides a \textit{context-sensitive} solution in polynomial time. In other data-flow algorithms not based on the functional approach, the result of the analysis at the entry of a procedure ``merges'' the incoming data obtained from all callers of the procedure. As a consequence, there is one global data-flow result computed at the end of the procedure. Context-sensitivity, however, allows an analysis to compute the data-flow result for a given procedure as a \textit{function} of the data-flow value at the start of the procedure. 
In other words, the analysis result for a procedure varies depending on where the procedure was called from. This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.

Compared to IFDS, most data-flow analyses are either general but do not run in polynomial time~\cite{knoop1992interprocedural,pnueli1981two} or handle a very specific set of problems~\cite{knoop1993efficient}.

The IFDS algorithm is applicable to problems which can be expressed with data-flow functions that satisfy certain restrictions. \textit{Inter-procedural} flow functions specify how data flows from the invocation of a procedure to its start, and from the procedure's end back to its call site. \textit{Distributive} flow functions are those that distribute over the confluence operator. In the context of IFDS, the confluence operator is called meet, and it can be either union or intersection. The data-flow facts on which the analysis operates must be a \textit{finite} set $D$. Each flow function operates on a \textit{subset} of $D$ (for example, the set of variables in the program) which makes the domain of the flow functions the power set of $D$. We describe the IFDS restrictions in detail in Section~\ref{sec:suitableifds}.

The IDE framework is an expressive extension to IFDS that was created by the same authors in 1996.
The problems that IDE can solve include, but are not limited to, IFDS problems. Just as the IFDS algorithm, the IDE algorithm is suitable for data-flow analyses that can be encoded with inter-procedural, distributive flow functions. However, in IDE, the domain of the flow functions is not restricted to sets $D$ of data-flow facts. The IDE domain of a flow function consists of \textit{environments} that map data-flow facts from the set $D$ to lattice elements.

As an example, in a constant propagation problem, an IDE environment would map each variable to the (possibly) constant value that it is bound to. To illustrate the distinction between IFDS and IDE we could say that IFDS can find out which variables in a program are constants, whereas IDE can additionally retrieve the values of the constant variables.

\subsection{Paper Outline}

The goal of the correlated-calls analysis presented in this work is to modify the output of an IFDS analysis to account for correlated calls. Specifically, the correlated-calls analysis improves the precision of IFDS problem results by eliminating infeasible execution paths caused by correlated calls. This is done by converting the input-IFDS problem to an IDE problem that detects infeasible paths, and converting the IDE result back to a more precise IFDS result.

The contributions of this work are:
\begin{itemize}
  \item A transformation from IFDS to IDE problems that considers correlated calls.
  \item An implementation in Scala of the correlated-calls transformation and the IDE algorithm which is based on the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
\end{itemize}

  We prove that the solution to an IDE problem that considers correlated calls is more precise than the solution to the original IFDS problem.
  We also show that the correlated-calls analysis is sound, i.e. that it never considers concrete execution paths as infeasible.

 Finally, we evaluate the effectiveness of the correlated-calls analysis using an implementation of taint analysis as the source IFDS problem.

The remainder of this paper is organized as follows. In the next section, we describe the IFDS and IDE analyses in detail. In Section~\ref{chapter:cca} we present the correlated-calls analysis as a transformation of IFDS problems into a special kind of IDE problem. Section~\ref{sec:ccdatastr} describes an efficient representation of the data structures that are required to define a correlated-calls IDE transformation.
In Section~\ref{chapter:eval} we address some implementation aspects of the correlated-calls analysis and present an evaluation of its results. Section~\ref{chapter:concl} contains concluding remarks.

### 2014-11-27 main.tex
changing formatting of thesis according to springer guidelines

\documentclass[runningheads,a4paper]{llncs}

\usepackage{style/packages}

\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

\title{Data Flow Analysis\\in the Presence of Correlated Calls}

\author{
 Marianna Rapoport\inst{1} \and
 Ond\v{r}ej Lhot\'ak\inst{1} \and
 Frank Tip\inst{2}
}
\institute{
 University of Waterloo\\
 \email{ \{mrapoport, olhotak\}@uwaterloo.ca }
  \and
 Samsung Research America\\
 \email{ ftip@samsung.com  }
}

\pagenumbering{gobble}

\toctitle{Data Flow Analysis in the Presence of Correlated Calls}
%\tocauthor{Authors' Instructions} % TODO
\maketitle

\begin{abstract}
We present a technique to improve the precision of data-flow analyses on object-oriented programs in the presence of 	\textit{correlated calls}. Two method calls are correlated if they are polymorphic and are invoked on the same object. Correlated calls are problematic because they can make  existing data-flow analyses consider certain infeasible data-flow paths as valid. This leads to loss in precision of the analysis solution.

We show how infeasible paths can be eliminated for \textit{Inter-procedural Finite Distributive Subset} (IFDS) problems, a large class of data-flow analysis problems. We show how the precision of IFDS problems can be improved in the presence of correlated calls, by using the \textit{Inter-procedural Distributive Environment} (IDE) algorithm to eliminate infeasible paths.  Using IDE, we eliminate the infeasible paths and obtain a more precise result for the original IFDS problem.

Our analysis is implemented in Scala, using the WALA framework for static program analysis on Java bytecode.

%\keywords{We would like to encourage you to list your keywords within
%the abstract section}
\end{abstract}

\input{style/commands}

\input{content/intro}
\input{content/background}
\input{content/impl}
\input{content/datastr}
\input{content/eval}
\input{content/concl}

\bibliographystyle{plain}
\bibliography{bib/ref}
\end{document}

### 2014-11-27 code/assertions.java

@@ -1,0 +1,19 @@
+  public static void main(String[] args) {
+    String n = "not secret";
+    notSecret(n);  // assert that n is not secret
+    String s1 = f(n);
+    isSecret(s1);  // in the next statement, f is invoked with a secret value
+                   // hence, the argument of f will always be considered secret
+                   // and f will always return a secret value
+    String s2 = f(secret());
+  }
+
+  static String f(String str) {
+    isSecret(str); // the function is once invoked with a secret value
+                   // hence, assert that str is secret
+    return str;
+  }
+  
+  public static String secret() {  // the secret source
+    return "secret";
+  }

### 2014-11-27 code/ccexample.java

@@ -1,0 +1,25 @@
+class A {
+  String foo {
+    return secret();
+  }
+  
+  void bar(String s) {}
+}
+
+class B extends A {
+  String foo {
+    return "not secret";
+  }
+  
+  void bar(String s) {
+    System.out.println(s);
+  }
+}
+
+class Main {
+  public static void main(String[] args) {
+    A a = args == null ? new A() : new B(); // a has runtime type A or B$\label{line:newa}$
+    String v = a.foo();
+    a.bar(v);
+  }
+}

### 2014-11-27 code/correct.java

@@ -1,0 +1,4 @@
+  int a = 1;
+  int b = a;
+  int c = a + b;
+  int d = a + 2;

### 2014-12-03 content/datastr.tex
started to move proofs to appendix; removing dependency on minted

@@
 
-\newpage    
 \begin{lemma}\label{lem:normeq}
@@
 \end{lemma}
-
-\begin{proof}
-    Let $\updfun f^*=\setpair I U$.
-    For any $\tau\in T,$
-    \[
-        \begin{aligned}
-            \denote{\mathcal N(\updfun f^*)}(\tau)
-            &=\denote{\mathcal N(\langle I,\ U\rangle)}(\tau)\\
-            &=\denote{\setpair{I\cup U}U}(\tau)\\
-            &=\tau\cap(I\cup U)\cup U\\
-            &=(\tau\cap I)\cup(\tau\cap U)\cup U\\
-            &=\tau\cap I\cup U\\
-            &=\denote{\setpair IU}(\tau)\\
-            &=\denote{\updfun f^*}(\tau)\,.
-        \end{aligned}
-    \]
-    Thus, $\denote{\mathcal N(\updfun f^*)}=\denote{\updfun f^*}$.
-\end{proof}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:normuneq}
     Let $\setpair IU$ and $\setpair{I'}{U'}$ be two normalized update functions such that $\setpair IU\ne\setpair {I'}{U'}$. Then $\denote{\setpair IU}\ne\denote{\setpair {I'}{U'}}$.
 \end{lemma}
-
-\begin{proof}
-    Let us show that there always exists a set $\tau\subseteq T$ such that $\denote{\setpair IU}(\tau)\ne\denote{\setpair{I'}{U'}}(\tau)$. There are two cases:
-    \begin{enumerate}
-        \item $U\ne U'$. Then for the empty set $\tau=\varnothing$,
-            \[
-                \denote{\setpair IU}(\tau)=\denote{\setpair IU}(\varnothing)=(\varnothing\cap I)\cup U=U\,,
-            \]
-            whereas 
-            \[ 
-                \denote{\setpair {I'}{U'}}(\tau)=\denote{\setpair {I'}{U'}}(\varnothing)=(\varnothing\cap I')\cup U'=U'.
-            \]
-            Hence, $\denote{\setpair IU}\ne\denote{\setpair {I'}{U'}}$.
-        \item $I\ne I'$. Then for the set of all types $\tau=T$,
-            \[
-                \denote{\setpair IU}(\tau)=\denote{\setpair IU}(T)=(T\cap I)\cup U=I\cup U\,.
-            \]
-            Since $\setpair IU$ is normalized, $U\subseteq I$, and
-            \[
-                I\cup U= I\,.
-            \]
-            At the same time,
-            \[
-                \denote{\setpair {I'}{U'}}(\tau)=\denote{\setpair {I'}{U'}}(T)=(T\cap I')\cup U'=I'\cup U'=I'\,.
-            \]
-            Since $I\ne I'$, it follows that $\denote{\setpair IU}\ne \denote{\setpair {I'}{U'}}$. \qedhere
-    \end{enumerate}
-\end{proof}
 

### 2014-12-03 content/impl.tex
started to move proofs to appendix; removing dependency on minted

@@
 
-We will next show, in Lemma~\ref{lem:sound}, that our analysis is sound, i.e.
-that the result of an IDE problem obtained through a correlated-calls transformation removes only facts that occur on infeasible paths.
-To prove the Soundness Lemma, we first introduce Lemmas~\ref{lem:sound1} and~\ref{lem:sound3}.
-
-We will denote the top element in the environment lattice as
-\begin{equation}
-  \Omega=\lambda d\,.\,\topcc\,.
-\end{equation}
-
-For the purpose of the proofs, we will rewrite Equation~\eqref{eq:edgefndef} that defines an edge function as follows:
-  \begin{equation}\label{eq:edgefnThroughDelta}
-    \ccedgefn S=\lambda e\,.\,
-    \begin{cases}
-      \id&\text{if $d_1=d_2=\Lambda$,}\\
-      \lambda m\,.\,\varepsilon(e)(\delta(m))&\text{otherwise},
-    \end{cases}
-  \end{equation}
-  where $S\subseteq R$, $d_1$ and $d_2$ are the source and target facts, and for a map $m\in\lcc_U$, $\delta(m)$ is either $m$ or $\botcc$:
-  \begin{equation}\label{eq:deltadef}
-    \delta(m)=\begin{cases}
-      \botcc&\text{if $d_1=\Lambda$}\\
-      m&\text{otherwise.}
-    \end{cases}
-  \end{equation}
-
-Additionally, for a path $p=[\startmain,\,\dots]$ and a fact $d\in D$, we will denote the lattice element that is mapped to $d$ according to the flow functions of path $p$ as follows:
-\begin{equation}
-  \mpd=\menv(p)(\Omega)(d)\,.
-\end{equation}
-
-The following Lemma shows that the lattice elements (receiver-to-types maps) of a correlated-calls IDE analysis correctly overapproximate the possible types of a receiver in a program execution.
-
-\begin{lemma}\label{lem:sound1}
-Let $p=[\startmain,\,\dots,\,n]$ be some concrete execution trace of the program, and let $r\in R$ be a receiver.
-If after the execution trace $p$, at node $n$, $r$ points to an object of runtime type~$t$, and $d\in D$ is a fact such that $d\in M_F(p)(\varnothing)$, then
-  \begin{equation}
-    t\in\mpd(r)\,.
-  \end{equation}
-\end{lemma}
-\begin{proof}
-  By induction on the length of the trace.
-
-  \textit{Basis:} $p=[\startmain]$. Then there is no instruction at which a receiver $r$ could be instantiated, and the Lemma is trivially true.
-
-  \textit{Induction hypothesis:} Let $p=[\startmain,\,\dots,\,n_{k-1}]$, and let $\uptau$ be the set of types to which $\mpdkm$ maps $r$:
-  \begin{equation}
-    \uptau=\mpdkm(r)\,.
-  \end{equation}
-  Assume that for a concrete execution path $p=[\startmain,\,\dots,\,n_{k-1}]$, at node $(n_{k-1},\,d_{k-1})$, the Lemma holds, i.e. $t\in\uptau$.
-
-  \textit{Induction step:} Let $p'=[\startmain,\,\dots,n_{k-1},\,n_k]$ and $t'\in T$ be the type to which $r$ is mapped at $n_k$.
-
-  For each $i$, let $e_i$ be the edge $((n_{i-1},\,d_{i-1}),\,(n_i,\,d_i))$. Note that $$e_1=((\startmain,\,\Lambda),\,(n_1,\,d_1))\,.$$
-
-  Observe that
-  \begin{align*}
-    \mppd
-    &=\menv(p')(\Omega)(d)\\
-    &=\left(\menv(e_k)\circ\menv(e_{k-1})\circ\ldots\circ\menv(e_1)\right)(\Omega)(d)\\
-    &=\menv(e_k)\left(\menv(p)(\Omega)\right)(d)\,.
-  \end{align*}
-
-  According to~\eqref{eq:envTransToEdgeFnEdge},
-  \begin{align*}
-    &\menv(e_k)\left(\menv(p)(\Omega)\right)(d)(r)\\
-      =&\bigg(\ccedgefn R((n_{k-1},\,\Lambda),\,(n_k,\,d))(\topcc)\sqcap\\
-       &\bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\Omega)(d'))\bigg)(r)\\
-      \supseteq&
-        \bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\Omega)(d'))(r)\\
-      \supseteq&\,\ccedgefn R((n_{k-1},\,d_{k-1}),\,(n_k,\,d))(\mpdkm)(r)\,.
-  \end{align*}
-  Therefore, 
-  \begin{equation}\label{eq:musubset}
-    \efek\subseteq\mppd(r)\,.
-  \end{equation}
-
-  We will now show that
-  \[
-    t'\in\efek\,,
-  \]
-  which, due to~\eqref{eq:musubset}, means that the Lemma holds.
-
-  According to~\eqref{eq:edgefnThroughDelta}, there are two cases in which $\ccedgefn R(e_k)$ could fall.
-
-  If $d_{k-1}=d_k=\Lambda$, then $d_k\notin M_F(p)(\varnothing)$, since it does not belong to the set $D$, and the Lemma trivially holds.
-
-  Otherwise, 
-  \[
-    \ccedgefn R(e_k)=\lambda m\,.\varepsilon(e_k)(\delta(m))\,.
-  \]
-  It follows that
-  \begin{align}\label{eq:efek}
-    \efek
-    &=(\lambda m\,.\varepsilon(e_k)(\delta(m)))(\mpdkm)(r)\notag\\
-    &=\varepsilon(e_k)(\delta(\mpdkm))(r).
-  \end{align}
-  Let us denote the lattice element $\delta(\mpdkm)$ with $\Delta$:
-  \[
-    \Delta=\delta(\mpdkm)\,.
-  \]
-  Note that since $\Delta$, according to~\eqref{eq:deltadef}, can be either $\botcc$ or $\mpdkm$, it always maps $r$ to a set containing~$t$:
-  \begin{equation}\label{eq:deltaContainsT}
-    t\in\Delta(r)\,.
-  \end{equation}
-  Note also that unless the instruction at $n_{k-1}$ contains an assignment for $r$, $r$ is mapped to the same object of type $t$ as at node $n_{k-1}$, and $t=t'$.
-Therefore, for the non-assignment instructions, it is sufficient to prove that $t\in\Delta(r)$.
-
-   Depending on the instructions at the nodes $n_{k-1}$ and $n_k$, there are four cases:
-  \begin{enumerate}
-    \item\label{item:asgn} The instruction at $n_{k-1}$ is an assignment for a receiver $r'\in R$.
-        Since $\varepsilon_R(e_k)=\lambda m\,.\,m[r'\to\bot_T]$,
-        \begin{align*}
-          \efek&=            
-            (\lambda m\,.\,m[r'\to\bot_T])(\Delta)(r)\\
-          &=\Delta[r'\to\bot_T](r)\,.
-        \end{align*}
-      In the resulting map, $r'$ is mapped to $\bot_T$. Then
-
-      \begin{enumerate}
-        \item if $r=r'$, then $\efek=\bot_T$, which contains $t'$.
-        \item\label{item:defaultmap} If $r\ne r'$, then $r$ has not been reassigned a value, and still maps to the same object of type $t$.
-The receiver $r$ is mapped to $\Delta(r)$, which, according to~\eqref{eq:deltaContainsT}, contains $t$.
-Since $t=t'$, $\Delta(r)$ contains $t'$.
-      \end{enumerate}
-    \item\label{item:callstart} $e_k$ is a call-start edge with signature $s_\mathcal F$, and $f\in\mathcal F$ is the called procedure.
-      Then
-        \begin{align*}
-          \efek
-          &=(\lambda m\,.\,m[r'\to m(r')\cap\tau(s_\mathcal F,\,f)])(\Delta)(r)\\
-          &=\Delta[r'\to\Delta(r')\cap\tau(s_\mathcal F,\,f)]\,,
-        \end{align*}
-      where $r'$ is the receiver of the call.
-      \begin{itemize}
-        \item If $r'=r$, then $\Delta(r')=\Delta(r)$ which contains $t$. Since $t\in\tau(s_\mathcal F,\,f)$, it follows that $t\in\Delta(r)\cap\tau(s_\mathcal F,\,f)$, and $t\in\efek$.
-         \item If $r'\ne r$, see~(\ref{item:defaultmap}).
-       \end{itemize}
-    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_k\in R$ are the local variables in the callee method, $r'$ is the receiver of the call site corresponding to the return node $n_k$, and $f\in\mathcal F$ is the called method with signature~$s_\mathcal F$.
-      Then 
-      \[
-        \varepsilon_R(e_k)=\lambda m\,.\,m[r'\to m(r')\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_k\to\bot_T].
-      \]
-      If $r\in\{r_1,\,\dots,\,r_k\}$, see~Case~\ref{item:asgn}. Otherwise, the case is analogous to Case~\ref{item:callstart}.
-    \item\label{item:idcase} The node contains any other instruction.
-      Then 
-      \[
-        \ccedgefn R(e_k)(\mpdkm)(r)=\id(\Delta)(r)=\Delta(r),
-      \]
-      which contains $t$ according to~\eqref{eq:deltaContainsT}.\qedhere
-  \end{enumerate}
-\end{proof}
-
-We will now show that on a node of a concrete execution path, the correlated-calls analysis does not map receivers to $\top_T$.
-In other words, the analysis never considers nodes of a concrete execution path unreachable.
-
-\begin{lemma}\label{lem:sound3}
-  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, $r\in R$ a receiver, and $d\in D$ a data-flow fact. Then if $d\in M_F(p)(\varnothing)$,
-  \begin{equation}
-    \mpd(r)\ne\top_T\,.
-  \end{equation}
-\end{lemma}
-\begin{proof}
-  By induction on the length of the execution trace.
-
-  \textit{Basis:} 
-    Let $p=[\startmain]$.
-Since the only realizable path corresponding to $p$ is $[(\startmain,\,\Lambda)]$, there is no fact $d\in D$ such that $d\in M_F(p)(\varnothing)$, and the claim follows immediately.
-
-  \textit{Induction hypothesis:} 
-  Let $p=[\startmain,\,\dots,\,n_{k-1}]$. Let $\uptau$ be the set of types to which $r$ is mapped by $\mpdkm$:
-  \begin{equation}
-    \uptau=\mpdkm(r)\,.
-  \end{equation}
-  Assume the Lemma holds for that for a concrete execution path $$p=[\startmain,\,n_1,\,\dots,\,n_{k-1}]\,,$$ i.e. $\uptau\ne\top_T$ for an arbitrary $r\in R$ and $d_{k-1}\in D$.
-
-  \textit{Induction step:}
-    Let $p'=[\startmain,\,n_1,\,\dots,n_{k-1},\,n_k]$ be a concrete execution path.
-
-    Let $e_k=((n_{k-1},\,d_{k-1}),\,(n_k,\,d))$. As shown in~\eqref{eq:musubset},
-    \begin{align*}
-      \mppd(r)
-        &\supseteq\ccedgefn R(e_k)(\mpdkm)(r)\,.
-    \end{align*}
-
-    From Definition~\ref{def:edgefn}, we can see that unless $e_k$ is a call-start edge or an end-return edge, the result follows from the induction hypothesis.
-    More formally, if $e_k$ is not a call-start or end-return edge, then for all $m\in\lcc_R$,
-    \[
-      \ccedgefn R(e_k)(m)\sqsubseteq m\,.
-    \]
-     The edge function corresponding to the call-start and end-return edges is the only place in which the set of types that a receiver maps to can be reduced.
-
-    Assume that $e_k$ is a end-return edge with a call on the receiver $r'\in R$ with a signature $s_\mathcal F$ to a function $f\in\mathcal F$.
-    \begin{align*}
-      \ccedgefn R&(e_k)(\mpdkm)(r)\\
-      &=\left(\lambda m\,.\,m[r'\to m(r)\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(\mpdkm)(r)\\
-      &=\left(\mpdkm[r'\to \uptau\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(r)\,,
-    \end{align*}
-  where $r_1,\,\dots,r_l\in R$ are the local variables in the called method.
-
-    If $r\in\{r_1,\,\dots,\,r_l\}$, then $\efek=\bot_T\ni t$\footnote{In the case of a recursive call, it is possible that both $r\in\{r_1,\,\dots,\,r_l\}$ and $r=r'$.
-    In that case, the set to which $r$ will be mapped would be still ``overwritten'' by $\bot_T$.}.
-
-    Otherwise, if $r=r'$, then $\efek=\uptau\cap\tau(s_\mathcal F,\,f)$.
-
-    According to Lemma~\ref{lem:sound1} and by the induction hypothesis, the runtime type $t$ of $r$ must be contained in $\mpdkm(r)=\uptau$.
-At the same time, by definition, $t$ is part of $\tau(s_\mathcal F,\,f)$.
-Therefore, $t\in\uptau\cap\tau(s_\mathcal F,\,f)\subseteq\efek$, which means that $\efek\ne\top_T$.
-
-    The same reasoning applies to the case where $e_k$ is a call-start edge.
-\end{proof}
-
-Finally, we will prove the soundness of the correlated-calls analysis: we will show that our analysis only considers a path infeasible if it cannot occur in a concrete execution of a program.
+We will next show that our analysis is sound, i.e. that the result of an IDE problem obtained through a correlated-calls transformation removes only facts that occur on infeasible paths.
 
@@
 \end{lemma}
-\begin{proof} Let $\rho=\result(\transCC_R(P))$. Then
-  \begin{align*}
-    \backCC(\rho)(n)
-    &=D_n^\Subset(\rho)\\
-    &=\left\{d'\ |\ 
-        d'\in\mvp F(n)\,\wedge\,\forall r\in R:\ \rho(n,\ d')(r)\ne\top_T\right\}.
-  \end{align*}
-  Since $\mvp F(n)=\bigsqcap_{q\in\ivp(n)}M_F(q)(\varnothing)$, and $p\in\ivp(n)$, it follows that
-    \begin{align*}
-      d&\in M_F(p)(\varnothing)\\&\subseteq\mvp F(n)\,.
-    \end{align*}
-  At the same time, for all receivers $r\in R$,
-  \begin{align*}
-    \rho(n,\,d)(r)
-    &=\left(\bigsqcap_{q\in\ivp(n)}\mpddef q d\right)(r)\\
-    &=\bigsqcap_{q\in\ivp(n)}\mpddef q d(r)\,.
-  \end{align*}
-  According to~Lemma~\ref{lem:sound3}, $\mpd(r)\ne\top_T$.
-  Since $p\in\ivp(n)$,
-  \begin{align*}
-    \mpd(r)\subseteq\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)\,.
-  \end{align*}
-  From $\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)=\rho(n,\,d)(r)$ it follows that
-  $\mpd(r)\subseteq\rho(n,\,d)(r)$.
-  Therefore, $\rho(n,\,d)(r)\ne\top_T$, and $d\in D_n^\Subset(\rho)=\backCC(\rho)(n)$.
-\end{proof}
 
@@
 We will show that IDE problems obtained through ordinary and reduced correlated-calls transformations yield the same results.
-
-The following Lemma shows that the types to which a given receiver is mapped in the result of the algorithm is not affected by other receivers and the types to which they are mapped.
-
-\begin{lemma}\label{lem:recindepedgefn}
-  Let $P$ be an IFDS problem.
-Let $N^*$ be the supergraph for $P$, $D$ the set of data-flow facts, $n\in N^*$ a node, and $p=[\startmain,\,\dots,\,n]$ a path in the supergraph.
-Let $d\in D\cup\{\Lambda\}$.
-  Then for any realizable path $p'\in\textsf{RP}(p,\,d)$, set $S\subseteq R$, and receiver $r\in S$,
-  \begin{equation}
-    \ccedgefn S(p')(\topcc)(r)=
-    \ccedgefn{\{r\}}(p')(\topcc)(r)\,.
-  \end{equation}
-\end{lemma}
-\begin{proof}
-  By induction on the length of $p$.
-
-  \textit{Basis:} $p'=[(\startmain,\,\Lambda)]$. Then $\ccedgefn S(p')=\id=\ccedgefn{\{r\}}(p')$, and the Lemma follows directly.
-
-  \textit{Induction hypothesis:} Suppose that for a path $q=[(\startmain,\,\Lambda),\,\dots,\,(n_{k-1},\,d_{k-1})]$, where $q\in\textsf{RP}(n,\,d)$, the Lemma holds, i.e.
-both edge functions map $r$ to the same set of types $\uptau$:
-  \begin{align*}
-    \uptau
-    &=\ccedgefn S(q)(\topcc)(r)\\
-    &=\ccedgefn{\{r\}}(q)(\topcc)(r)\,.
-  \end{align*}
-
-  \textit{Induction step:} Let $q'=[(\startmain,\,\Lambda),\,\dots,\,(n_{k-1},\,d_{k-1}),\,(n_k,\,d_k)]$ and the edge $e_k=((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))$.
-
-  Observe that for any set $U\subseteq R$ such that $r\in U$,
-  \begin{align}\label{eq:edgefnU}
-    \ccedgefn U(q')(\topcc)(r)
-    &=\ccedgefn U(e_k)(\ccedgefn U(q)(\topcc))(r)\,.
-  \end{align}
-
-  We can see from~\eqref{eq:edgefnThroughDelta} that there are two cases.
-
-  If $d_{k-1}=d_k=\Lambda$, $\ccedgefn S(e_k)=\id=\ccedgefn{\{r\}}(e_k)$, and, due to~\eqref{eq:edgefnU},
-  \begin{align*}
-    \ccedgefn S(q')(\topcc)(r)&=\uptau\\
-    &=\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
-  \end{align*}
-
-  Otherwise, there are four sub-cases.
-  \begin{enumerate}
-    \item $e_k$ is a call-start edge, $r'.c()$ is the call site at $n_{k-1}$ with signature $s_\mathcal F$, $f\in\mathcal F$ is the called procedure, and $r'\in U$.
-    Then
-    \[
-      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\delta(m)(r)\cap\tau(s_\mathcal F,\,f)]\,.
-    \]
-    There are two sub-cases.
-    \begin{enumerate}
-      \item\label{item:callstartreceq} If $r=r'$, then, according to~\eqref{eq:edgefnU}, the resulting set of types 
-        \[
-          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\cap\tau(s_\mathcal F,\,f).
-        \]
-        If $d_{k-1}=\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\botcc(r)=\bot_T$.
-If $d_{k-1}\ne\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\ccedgefn U(q)(\topcc)(r)=\uptau$.
-The set $\tau(s_\mathcal F,\,f)$ is the same for either case.
-
-        Therefore, the value of $\ccedgefn U(q')(\topcc)(r)$ has the same result regardless of $U$,
-        which means that $\ccedgefn S(q')(\topcc)(r)=\ccedgefn{\{r\}}(q')(\topcc)(r)$, and the Lemma holds.
-      \item\label{item:callstartrecneq} If $r\ne r'$, then
-        \begin{equation}
-          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\,,
-        \end{equation}
-        which, as we have seen in~Case~\eqref{item:callstartreceq}, does not depend on~$U$, and the Lemma holds.
-    \end{enumerate}
-    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_l\in U$ are the local variables in the callee method, $r'.c()$ is the call corresponding to the return node at $n_k$, $f\in\mathcal F$ is the called method with signature $s_\mathcal F$, and $r'\in U$.
-    Then
-    \[
-      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)
-      [r'\to\delta(m)(r)\cap\tau(s_\mathcal F,\,f)]
-      [r_1\to\bot_T]\ldots[r_l\to\bot_T]\,.
-    \]
-    There are three sub-cases.
-    \begin{enumerate}
-      \item\label{item:localvarrec} If $r\in\{r_1,\,\dots,\,r_l\}$, then regardless of the value of $U$,
-      \[
-        \ccedgefn U(q')(\topcc)(r)=\bot_T\,,
-      \]
-      and the Lemma holds.
-      \item Otherwise, if $r=r'$, the case is analogous to Case~\eqref{item:callstartreceq}.
-      \item If $r\notin\{r',\,r_1,\,\dots,\,r_l\}$, then see Case~\eqref{item:callstartrecneq}.
-    \end{enumerate}
-    \item $n_{k-1}$ contains an assignment for $r'\in U$. Then
-    \[
-      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\bot_T]\,.
-    \]
-    If $r=r'$, see Case~\eqref{item:localvarrec}. If $r\ne r'$, see Case~\eqref{item:callstartrecneq}.
-    \item Otherwise,
-    \[
-      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)\,,
-    \]
-    and the case is analogous to Case~\eqref{item:callstartrecneq}.\qedhere
-  \end{enumerate}
-\end{proof}
-
-The following Lemma shows that the correlated-calls analysis computes the results for each receiver independently, or separately.
-To compute the set of types to which a receiver~$r$ is mapped at each exploded-graph node, we can exclude all other receivers in the program from the analysis (recall from~\eqref{eq:edgefndef} that the set of receivers that are considered in the analysis is specified by the set $S$ in a correlated-calls transformation $\transCC_S$).
-Therefore, for a given receiver $r$, the results of a $\transCC_S$- and a $\transCC_{\{r\}}$-analysis are the same.
-
-\begin{lemma}\label{lem:recindep} Let $P$ be an IFDS problem. Let $N^*$ be the supergraph for $P$, $D$ the set of data-flow facts, and $S\subseteq R$ a set of receivers.
-  Then for any $n\in N^*$, $d\in D$, and receiver $r\in S$,
-  \begin{equation}
-    \result\left(\transCC_S(P)\right)(n,\,d)(r)=
-    \result(\transCC_{\{r\}}(P))(n,\,d)(r)\,.
-  \end{equation}
-\end{lemma}
-\begin{proof}
-  According to~\eqref{eq:ideresult}, \eqref{eq:mvpdef}, and~\eqref{eq:envTransToEdgefn},
-  \begin{align}
-    \result\left(\transCC_S(P)\right)(n,\,d)(r)
-    &=\mvp{\textsf{Env}}(n,\,d)(r)\notag\\
-    &=\left(\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\Omega)(d)\right)(r)\notag\\
-    &=\left(\bigsqcap_{q\in\ivp(n)}\bigsqcap_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)\right)(r)\notag\\
-    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)(r)\,.\label{eq:resultThroughEdgefn}
-  \end{align}
-  Then from Lemma~\ref{lem:recindepedgefn},
-  \begin{align*}
-    \result\left(\transCC_S(P)\right)(n,\,d)(r)
-    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\\
-    &=\result\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)\,.\qedhere
-  \end{align*}
-\end{proof}
-
-The next lemma shows that the set of types to which a receiver is mapped in a correlated-calls lattice element can be represented as an intersection of static-type function applications $\tau(s_{\mathcal F_i},\,f_i)$.
-\begin{lemma}\label{lem:edgefnThroughTaus}
-  For an IFDS problem $P$, a node $n\in N^*$, and fact $d\in D$, let $p\in\mathsf{RP}(n,\,d)$ be a realizable path and $r\in R$ a receiver.
-Then there exists a non-negative number $\gamma$ of calls on the receiver $r$ with signatures $s_{\mathcal F_\gamma}$ to the functions $f_\gamma\in\mathcal F_\gamma$, for which
-  \[
-    \ccedgefn{\{r\}}(p)(\topcc)(r)=
-      \bigcap_{\gamma\ge0}\tau(s_{\mathcal F_\gamma},\,f_\gamma)\,.
-  \]
-\end{lemma}
-\begin{proof}
-  Let $p$ have the following form\footnote{It can be shown from the definition of a pointwise representation in~Sagiv et al.~\cite{sagiv1996precise} that in a realizable path, there is never an edge from a fact of the set $D$ to a $\Lambda$ fact.
-Therefore, we can represent $p$ as a sequence of nodes that has a prefix of $\Lambda$-fact nodes, after which all nodes are non-$\Lambda$ facts.}:
-  \[
-    p=[(\startmain,\,\Lambda),\,(n_1,\,\Lambda),\,\dots,\,(n_k,\,\Lambda),
-       (n_{k+1},\,d_{k+1}),\,\dots,\,(n_{k+l},\,d_{k+l})]\,,
-  \]
-  where $l\ge1$ and the facts for all nodes up to $n_k$ are equal to $\Lambda$ and $d_{k+i}\in D$ for $0<i\le l$.
-
-  As previously, for all $i$, we will denote the edge $(n_i,\,n_{i+1})$ by $e_i$.
-
-  From~\eqref{eq:edgefndef} we can infer that
-  \[
-    \ccedgefn{\{r\}}(p)=
-    \ccedgefn{\{r\}}(e_{k+l})
-    \circ\ldots
-    \circ\ccedgefn{\{r\}}(e_{k+2})
-    \circ(\lambda m\,.\,\beta)
-    \circ\id
-    \circ\ldots
-    \circ\id\,,
-  \]
-  where
-  \[
-    \beta=
-    \begin{cases}
-      \botcc[r\to\tau(s_\mathcal F,\,f)]&\text{if $(n_k,\,n_{k+1})$ is a call-start or end-return edge, and}\\&\text{the call site $r.c()$ with signature $s_\mathcal F$ to the function}\\
-      &\text{$f\in\mathcal F$ corresponds to the call-start or end-return edge,}\\
-      \botcc&\text{otherwise\footnotemark.}
-    \end{cases}
-  \]
-  \footnotetext{Since $d_k=\Lambda$ and $d_{k+1}\ne\Lambda$, the micro function for the edge $e_{k+1} $ is equal to $\lambda m\,.\,\varepsilon_{\{r\}}(e_{k+1})(\botcc)$.
-From the definition of $\varepsilon_S$~\eqref{eq:varepsilon} we can see that the only case where $\varepsilon_{\{r\}}(e_{k+1})(m)$ would not be equal to $\botcc$ is when $e_{k+1}$ is call-start or end-return edge.}
-
-  Therefore,
-  \begin{align}\label{eq:edgefnbeta}
-    \ccedgefn{\{r\}}(p)(\topcc)
-      &=\left(\ccedgefn{\{r\}}(e_{k+l})\circ\ldots\circ
-        \ccedgefn{\{r\}}(e_{k+2})\right)((\lambda m\,.\,\beta)(\topcc))\notag\\
-      &=\left(\ccedgefn{\{r\}}(e_{k+l})\circ\ldots\circ
-        \ccedgefn{\{r\}}(e_{k+2})\circ\id\right)(\beta)\,.
-  \end{align}
-
-We can now prove the lemma by induction on $l$.
-
-\textit{Basis:}
-If $l=1$, then $\ccedgefn{\{r\}}(p)(\topcc)=\id(\beta)=\beta$.
-There are two cases.
-
-If $\beta=\botcc$, then 
-\begin{align*}
-  \ccedgefn{\{r\}}(p)(\topcc)(r)&=\beta(r)\\&=\bot_T\,,
-\end{align*} and $\gamma=0$.
-
-If $\beta=\botcc[r\to\tau(s_\mathcal F,\,f)]$, then 
-\[
-  \ccedgefn{\{r\}}(p)(\topcc)(r)=\tau(s_\mathcal F,\,f)\,,
-\]
-and $\gamma=1$.
-
-\textit{Induction hypothesis:}
-Assume that for a path $p=[(\startmain,\,\Lambda),\,\dots,\,(n_{k+l},\,d_{k+l})]$, the Lemma holds for $\gamma=N$, where $N\ge0$.
-
-\textit{Induction step:}
-Let $p'=[(\startmain,\,\Lambda),\,\dots,\,(n_{k+l},\,d_{k+l}),\,(n_{k+l+1},\,d_{k+l+1})]$.
-
-Recall that
-\begin{align*}
-  \ccedgefn{\{r\}}(p')(\topcc)(r)
-  &=\ccedgefn{\{r\}}(e_{k+l+1})\left(\ccedgefn{\{r\}}(p)(\topcc)\right)(r)\,.
-\end{align*}
-
-From~\eqref{eq:varepsilon} we can see that unless $e_{k+l+1}$ is a call-start or end-return edge corresponding to a call on the receiver $r$, then $\ccedgefn{\{r\}}(e_{k+l+1})(r)$ must be equal to either $\bot_T$ or $m(r)$, where $m=\ccedgefn{\{r\}}(p)(\topcc)$.
-
-If $\ccedgefn{\{r\}}(e_{k+l+1})(r)=\bot_T$, then the Lemma holds for $\gamma=0$.
-
-Otherwise,
-\begin{align*}
-  \ccedgefn{\{r\}}(e_{k+l+1})(\topcc)(r)&=\ccedgefn{\{r\}}(p)(\topcc)(r)\\
-  &=\bigcap_{N}\tau(s_{\mathcal F_N},\,f_N)\,,
-\end{align*}
-and therefore $\gamma=N$.
-
-Suppose that $e_{k+l+1}$ is a call-start edge with a call on the receiver $r$ with signature $s_\mathcal G$ to a function $g\in\mathcal G$. Then, according to~\eqref{eq:varepsilon}, 
-\[
-  \ccedgefn{\{r\}}(e_{k+l+1})=\lambda m\,.\,m[r\to m(r)\cap\tau(s_\mathcal G,\,g)]\,.
-\]
-Therefore,
-\begin{align*}
-  \ccedgefn{\{r\}}&(p')(\topcc)(r)\\
-  &=\lambda m\,.\,m[r\to m(r)\cap\tau(s_\mathcal G,\,g)]\left(\ccedgefn{\{r\}}(p)(\topcc)\right)(r)\\
-  &=\ccedgefn{\{r\}}(p)(\topcc)(r)\cap\tau(s_\mathcal G,\,g)\\
-  &=\left(\bigcap_{N}\tau(s_{\mathcal F_N},\,f_N)\right)\cap\tau(s_\mathcal G,\,g)\,,
-\end{align*}
-and the Lemma holds for $\gamma=N+1$.
-
-The case where $e_{k+l+1}$ is an end-return edge is analogous to the previous case.
-\end{proof}
-
-We now show that a receiver will be only mapped to $\topcc$ if it is the receiver of a correlated call.
-
-\begin{lemma}\label{lem:ccrectop}
-   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a dataflow fact such that there exists a realizable path $p\in\textsf{RP}(n,\,d)$. Let $T$ be the set of all types in the program.
-   If there exists a receiver $r\in R$ such that
-  \[
-    \ccedgefn{\{r\}}(p)(\topcc)(r)=\top_T\,,                       
-  \]
-  then $r\in \rcc$.
-\end{lemma}
-\begin{proof}
- According to Lemma~\ref{lem:edgefnThroughTaus},
- \[
-   \ccedgefn{\{r\}}(p)(\topcc)(r)=
-      \bigcap_{\gamma\ge0}\tau(s_{\mathcal F_\gamma},\,f_\gamma).
- \]
-
- Let $\tau_i=\tau(s_{\mathcal F_i},\,f_i)$. 
- For a given $k$, let $r.m_k()$ be the call site corresponding to $\tau_k$, and $T'$ the set of types compatible with the static type of $r$.
- Recall from Section~\ref{sec:ef} that 
- \begin{itemize}
-   \item $\tau_k\ne\top_T$;
-   \item if $\tau_k=T'$ then the corresponding call site is monomorphic;
-   \item if $\tau_k\subset T'$ then the call site is polymorphic.
- \end{itemize}
-
- From the conditions of the Lemma, 
- \begin{equation}
-   \bigcap_{\gamma\ge 0}\tau_\gamma=\top_T\,.
- \end{equation}
-
- If all $\tau_k=T'$, then $\bigcap_{\gamma\ge 0}\tau_\gamma$ is also equal to $T'$. Since $T'\ne\top_T$, this is a contradiction.
-
- If exactly one $\tau_k\subset T'$ and the rest are equal to $T'$, then $\bigcap_{\gamma\ge 0}\tau_\gamma$ is equal to $\tau_k$, which cannot be $\top_T$ either.
-
- Therefore, there are at least two sets, $\tau_i$ and $\tau_j$, which are strict subsets of $T'$.
-Since both $\tau_i$ and $\tau_j$ are non-empty and their intersection equals $\top_T$, $\tau_i$ and $\tau_j$ must be disjoint.
-If $\tau_i$ and $\tau_j$ are disjoint, they must correspond to different call sites.
-
- In other words, there are at least two calls on the same receiver for which the static-type function is a strict subset of the set of types compatible with a given receiver $r$.
-It follows that both calls have to be polymorphic.
-Therefore,~${r\in\rcc}$.
-\end{proof}
-
-We will now show that if a receiver ever gets mapped to top, then it is a correlated-calls receiver.
-
-\begin{lemma}\label{lem:ccrectop}
-   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a dataflow fact such there exists a realizable path $p\in\textsf{RP}(n,\,d)$.
-   Then, if there exists a receiver $r\in R$, such that
-  \[
-    \result\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)=\top_T\,,
-  \]
-  then $r\in \rcc$.
-\end{lemma}
-\begin{proof}
-  As shown in~\eqref{eq:resultThroughEdgefn},
-  \[
-    \result\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
-  \]
-  Since the latter is equal to $\top_T$, it follows that for each realizable path $p'$ to node $n$, $\ccedgefn{\{r\}}(p')(\top)(r)=\top_T$.
-According to~Lemma~\ref{lem:ccrectop}, this is only possible if $r\in\rcc$.
-\end{proof}
-
-Finally, we show that if a correlated calls analysis considers only correlated-call receivers, no precision is lost.
-A correlated-calls analysis that considers all receivers computes the same result as an analysis that considers only correlated-call receivers.
+In other words, we show that if a correlated calls analysis considers only correlated-call receivers, no precision is lost.
 
@@
 \end{lemma}
-\begin{proof}
-  From~\eqref{eq:ucc} we know that
-  \begin{align*}
-    \backCC(\result\left(\transCC_R(P)\right))
-    &=\left\{(n,\,D_n^\Subset(\result(\transCC_R(P))))\ |\ n\in N^*\right\}.
-  \end{align*}
-  According to~\eqref{eq:dnq} and~Lemma~\ref{lem:recindep}, for a given $n\in N^*$,
-  \begin{align*}
-    D_n^\Subset&(\result(\transCC_R(P))))\\
-    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall r\in R:\ \left\{(r,\,\result(\transCC_{\{r\}}(P))(n,\,d)(r))\ |\ r\in R\right\}(r)\ne\top_T\right\}\\
-    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in R}:\ \result(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}.
-  \end{align*}
-
-Since, according to Lemma~\ref{lem:ccrectop}, $\result(\transCC_{\{r\}}(P))(n,\,d)(r)$ can only be equal to $\top_T$ when $r\in\rcc$, we can conclude that
-  \begin{align*}
-    D_n^\Subset&(\result(\transCC_R(P))))\\
-    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in\rcc}:\ \result(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}\\
-    &=D_n^\Subset(\result(\transCC_\rcc(P)))).
-  \end{align*}
-
-  Therefore,
-  \begin{align*}
-    \backCC(\result\left(\transCC_R(P)\right))
-    &=\left\{(n,\,D_n^\Subset(\result(\transCC_\rcc(P))))\ |\ n\in N^*\right\}\\
-    &=\backCC(\result\left(\transCC_\rcc(P)\right))\,.\qedhere
-  \end{align*}
-\end{proof}
 

### 2014-12-03 code/ccexample.java

@@ -18,7 +18,7 @@ class B extends A {
 
 class Main {
   public static void main(String[] args) {
-    A a = args == null ? new A() : new B(); // a has runtime type A or B$\label{line:newa}$
+    A a = args == null ? new A() : new B();
     String v = a.foo();
     a.bar(v);
   }

### 2014-12-03 content/datastr.tex
moving more stuff to appendix

@@
 
-\subsubsection{Efficiency}\label{sec:efficiency}
-In this section, we will show that our representation of micro functions is efficient according to the definition  of efficiency discussed in Section~\ref{sec:ccdatastr}.
+The following Lemma states that the representation of micro functions is efficient according to the definition  of efficiency discussed in Section~\ref{sec:ccdatastr}.
 \begin{lemma}\label{lem:efficient}
@@
 \end{lemma}
-\begin{proof}
-\leavevmode
-  \begin{enumerate}
-    \item The identity function is represented as
-      \[
-        \denote{\id}=\{(r,\,\langle \bot_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,;
-      \]
-      the top function is represented as
-      \[
-        \denote{\lambda m\,.\,\topcc}=\{(r,\,\langle \top_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,.
-      \]
-    \item Equations~\eqref{eq:compclosed} and~\eqref{eq:meetclosed} show that the representation of micro functions is closed under composition and meet.
-    \item To show that our representation for micro functions forms a lattice with finite height, let us first show that $\lcc_\rcc:\,\rcc\to2^T$ forms a lattice.
-Since $T$ is a finite set, $(2^T,\,\subseteq)$ is a finite-height lattice.
-$\rcc$ is a finite set.
-Hence, the mapping
-    \[
-      \rcc\mapsto2^T=\{(r,\,t)\,|\,r\in \rcc,\,t\in 2^T\}=\lcc_\rcc
-    \]        
-    also forms a finite-height lattice \cite{nielson1999principles}.
-
-    Furthermore, $\lcc_\rcc$ is a finite set. 
-    Every element of $\lcc_\rcc$ can be applied to $|\rcc|$ receivers, where each receiver is mapped to a set of types.
-There are $|\rcc|\cdot2^{|T|}$ different possibilities to form those mappings, so
-    \[
-      |\lcc_\rcc|=|\rcc|\cdot2^{|T|}.
-    \]
-    Therefore, $\lcc_\rcc\mapsto \lcc_\rcc$ also forms a finite-height lattice.
-    \item All operations can be computed in $O(\rcc\times T)$ time.
-Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
-    \item The space bound is $O(\rcc\times T)$.
-  \end{enumerate}
-\end{proof}
 

### 2014-12-03 content/intro.tex
started to move proofs to appendix; removing dependency on minted
moving more stuff to appendix

@@
 
-For example, in Listing~\ref{list:ccexample}, it is not possible to infer statically whether the runtime type of the variable \verb'a' in line~\ref{line:newa} is \verb'A' or \verb'B'.
+For example, in Listing~\ref{list:ccexample}, it is not possible to infer statically whether the runtime type of the variable \verb'a' in the \texttt{main} method is \verb'A' or \verb'B'.
 The call \verb'a.foo()' can be dispatched to either \verb'A.foo' or \verb'B.foo', and \verb'a.bar(v)' can be dispatched to either \verb'A.bar' or \verb'B.bar'.
@@
 
-  \begin{listing}[h]
+\begin{figure}
+  \centering
+  \begin{minipage}{\textwidth}
     \inputMinted{java}{ccexample.java}
+  \end{minipage}
   \caption{Example program containing correlated calls}
   \label{list:ccexample}
-  \end{listing}
+\end{figure}
 

### 2014-12-03 code/assertions.java

@@ -2,15 +2,12 @@
     String n = "not secret";
     notSecret(n);  // assert that n is not secret
     String s1 = f(n);
-    isSecret(s1);  // in the next statement, f is invoked with a secret value
-                   // hence, the argument of f will always be considered secret
-                   // and f will always return a secret value
+    isSecret(s1);
     String s2 = f(secret());
   }
 
   static String f(String str) {
-    isSecret(str); // the function is once invoked with a secret value
-                   // hence, assert that str is secret
+    isSecret(str);
     return str;
   }
   

### 2014-12-03 content/datastr.tex
adding comments

@@
 
-It is obvious that two functions represented with the same pairs of sets are equal. Let us prove that two different pairs of sets represent different update functions.
+It is obvious that two functions represented with the same pairs of sets are equal. The following lemma states that two different pairs of sets represent different update functions.
 
@@
 
-Composing two micro functions means to compose their update-map denotations:
+Composing two micro functions means to compose their update-map denotations:\mtodo{Should this be somehow moved to the appendix?
+Or should we just say ``It can be shown that ...'' and remove the whole computations at all?}
 \begin{align}
@@
 
+\begin{mdelete}
 The following Lemma states that the representation of micro functions is efficient according to the definition  of efficiency discussed in Section~\ref{sec:ccdatastr}.
+\end{mdelete}
 \begin{lemma}\label{lem:efficient}

### 2014-12-03 content/eval.tex
started to move proofs to appendix; removing dependency on minted
adding comments

@@
 
-We also implemented a correlated-call transformation from IFDS into IDE problems that consider correlated calls.
-This transformation is described in Section~\ref{sec:cctrans}.
-The flow functions can be easily inferred from Section~\ref{sec:edgefnrep}.
+We also implemented a correlated-call transformation from IFDS into IDE problems that consider correlated calls. This transformation is described in Section~\ref{sec:cctrans}.
 
@@
 
+\begin{mdelete}
 \paragraph{IDE-Implementation Correctness}
@@
 \inputMinted{java}{correct.java}
-\verb'a' and \verb'b' are considered constant, but \verb'c' and \verb'd' are not (although \verb'd' would be considered constant in linear-constant propagation).
+\texttt a and \texttt b are considered constant, but \texttt c and \texttt d are not (although \texttt d would be considered constant in linear-constant propagation).
 
@@
   Listing~\ref{list:assertions} illustrates the use of the \verb'isSecret' and \verb'notSecret' assertions.
-  \begin{listing}[H]
+\begin{figure}
+  \centering
+  \begin{minipage}{\textwidth}
     \inputMinted{java}{assertions.java}
+  \end{minipage}
   \caption{Example usage of \texttt{isSecret} and \texttt{notSecret} assertions in regression tests}
   \label{list:assertions}
-\end{listing}
+\end{figure}
 \end{example}
@@
 Since the primary purpose of the taint-analysis implementation was to test the correlated-call analysis, we did not include a static-initializer analysis in this work.
+\end{mdelete}
 
@@
 
-\begin{listing}
+\begin{figure}
+  \centering
+  \begin{minipage}{\textwidth}
     \inputMinted{java}{interprocRec.java}
+  \end{minipage}
   \caption{Inter-procedurally-correlated calls}
   \label{list:interProcRec}
-\end{listing}
+\end{figure}
 

### 2014-12-03 content/impl.tex
adding comments

@@
 
+\begin{mdelete}
 \begin{example}\label{ex:ifdsresult}
@@
 \end{example}
+\end{mdelete}
 
@@
 
+\begin{mdelete}
 \begin{example}\label{ex:ideresult}
@@
 We have also shown in Lemma~\ref{lem:subsetifds} that the correlated-calls analysis improves the precision of the original IFDS result $\result_\text{IFDS}$, because the correlated-calls result $\resultCC$ underapproximates an equivalence-IDE result $\resultEq=\result_\text{IFDS}$.
-Finally, we showed that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result $\resultCC$ that is obtained when considering all receivers $R$.
+Finally, we showed in Lemma~\ref{lem:onlycorrrec} that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result $\resultCC$ that is obtained when considering all receivers $R$.
 

### 2014-12-03 content/appendix.tex
missing f ile

\section*{Appendix}
In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:ccdatastr}.

\subsection*{Soundness and Precision}

We start by proving the Lemmas of Soundness and Precision of the correlated-calls analysis.

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:subsetifds}}]
  The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
  \begin{align*}
    \backCC\left(\result(\transCC_R(P))\right)(n)&=\{(n',\,D_n'^\Subset(\result(\transCC_R(P))))\ |\ n\in N^*\}(n)\\
      &=D_n^\Subset(\result(\transCC_R(P)))\\
      &\subseteq\mvp F(n)\\
      &=\result_\text{IFDS}(P)(n)\,.\qedhere
  \end{align*}
\end{proof}

To prove the Soundness Lemma, we first introduce Lemmas~\ref{lem:sound1} and~\ref{lem:sound3}.

We will denote the top element in the environment lattice as
\begin{equation}
  \Omega=\lambda d\,.\,\topcc\,.
\end{equation}

For the purpose of the proofs, we will rewrite Equation~\eqref{eq:edgefndef} that defines an edge function as follows:
  \begin{equation}\label{eq:edgefnThroughDelta}
    \ccedgefn S=\lambda e\,.\,
    \begin{cases}
      \id&\text{if $d_1=d_2=\Lambda$,}\\
      \lambda m\,.\,\varepsilon(e)(\delta(m))&\text{otherwise},
    \end{cases}
  \end{equation}
  where $S\subseteq R$, $d_1$ and $d_2$ are the source and target facts, and for a map $m\in\lcc_U$, $\delta(m)$ is either $m$ or $\botcc$:
  \begin{equation}\label{eq:deltadef}
    \delta(m)=\begin{cases}
      \botcc&\text{if $d_1=\Lambda$}\\
      m&\text{otherwise.}
    \end{cases}
  \end{equation}

Additionally, for a path $p=[\startmain,\,\dots]$ and a fact $d\in D$, we will denote the lattice element that is mapped to $d$ according to the flow functions of path $p$ as follows:
\begin{equation}
  \mpd=\menv(p)(\Omega)(d)\,.
\end{equation}

The following Lemma shows that the lattice elements (receiver-to-types maps) of a correlated-calls IDE analysis correctly overapproximate the possible types of a receiver in a program execution.

\begin{lemma}\label{lem:sound1}
Let $p=[\startmain,\,\dots,\,n]$ be some concrete execution trace of the program, and let $r\in R$ be a receiver. If after the execution trace $p$, at node $n$, $r$ points to an object of runtime type~$t$, and $d\in D$ is a fact such that $d\in M_F(p)(\varnothing)$, then
  \begin{equation}
    t\in\mpd(r)\,.
  \end{equation}
\end{lemma}
\begin{proof}
  By induction on the length of the trace.

  \textit{Basis:} $p=[\startmain]$. Then there is no instruction at which a receiver $r$ could be instantiated, and the Lemma is trivially true.

  \textit{Induction hypothesis:} Let $p=[\startmain,\,\dots,\,n_{k-1}]$, and let $\uptau$ be the set of types to which $\mpdkm$ maps $r$:
  \begin{equation}
    \uptau=\mpdkm(r)\,.
  \end{equation}
  Assume that for a concrete execution path $p=[\startmain,\,\dots,\,n_{k-1}]$, at node $(n_{k-1},\,d_{k-1})$, the Lemma holds, i.e. $t\in\uptau$.

  \textit{Induction step:} Let $p'=[\startmain,\,\dots,n_{k-1},\,n_k]$ and $t'\in T$ be the type to which $r$ is mapped at $n_k$.

  For each $i$, let $e_i$ be the edge $((n_{i-1},\,d_{i-1}),\,(n_i,\,d_i))$. Note that $$e_1=((\startmain,\,\Lambda),\,(n_1,\,d_1))\,.$$

  Observe that
  \begin{align*}
    \mppd
    &=\menv(p')(\Omega)(d)\\
    &=\left(\menv(e_k)\circ\menv(e_{k-1})\circ\ldots\circ\menv(e_1)\right)(\Omega)(d)\\
    &=\menv(e_k)\left(\menv(p)(\Omega)\right)(d)\,.
  \end{align*}

  According to~\eqref{eq:envTransToEdgeFnEdge},
  \begin{align*}
    &\menv(e_k)\left(\menv(p)(\Omega)\right)(d)(r)\\
      =&\bigg(\ccedgefn R((n_{k-1},\,\Lambda),\,(n_k,\,d))(\topcc)\sqcap\\
       &\bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\Omega)(d'))\bigg)(r)\\
      \supseteq&
        \bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\Omega)(d'))(r)\\
      \supseteq&\,\ccedgefn R((n_{k-1},\,d_{k-1}),\,(n_k,\,d))(\mpdkm)(r)\,.
  \end{align*}
  Therefore, 
  \begin{equation}\label{eq:musubset}
    \efek\subseteq\mppd(r)\,.
  \end{equation}

  We will now show that
  \[
    t'\in\efek\,,
  \]
  which, due to~\eqref{eq:musubset}, means that the Lemma holds.

  According to~\eqref{eq:edgefnThroughDelta}, there are two cases in which $\ccedgefn R(e_k)$ could fall.

  If $d_{k-1}=d_k=\Lambda$, then $d_k\notin M_F(p)(\varnothing)$, since it does not belong to the set $D$, and the Lemma trivially holds.

  Otherwise, 
  \[
    \ccedgefn R(e_k)=\lambda m\,.\varepsilon(e_k)(\delta(m))\,.
  \]
  It follows that
  \begin{align}\label{eq:efek}
    \efek
    &=(\lambda m\,.\varepsilon(e_k)(\delta(m)))(\mpdkm)(r)\notag\\
    &=\varepsilon(e_k)(\delta(\mpdkm))(r).
  \end{align}
  Let us denote the lattice element $\delta(\mpdkm)$ with $\Delta$:
  \[
    \Delta=\delta(\mpdkm)\,.
  \]
  Note that since $\Delta$, according to~\eqref{eq:deltadef}, can be either $\botcc$ or $\mpdkm$, it always maps $r$ to a set containing~$t$:
  \begin{equation}\label{eq:deltaContainsT}
    t\in\Delta(r)\,.
  \end{equation}
  Note also that unless the instruction at $n_{k-1}$ contains an assignment for $r$, $r$ is mapped to the same object of type $t$ as at node $n_{k-1}$, and $t=t'$. Therefore, for the non-assignment instructions, it is sufficient to prove that $t\in\Delta(r)$.

   Depending on the instructions at the nodes $n_{k-1}$ and $n_k$, there are four cases:
  \begin{enumerate}
    \item\label{item:asgn} The instruction at $n_{k-1}$ is an assignment for a receiver $r'\in R$.
        Since $\varepsilon_R(e_k)=\lambda m\,.\,m[r'\to\bot_T]$,
        \begin{align*}
          \efek&=            
            (\lambda m\,.\,m[r'\to\bot_T])(\Delta)(r)\\
          &=\Delta[r'\to\bot_T](r)\,.
        \end{align*}
      In the resulting map, $r'$ is mapped to $\bot_T$. Then

      \begin{enumerate}
        \item if $r=r'$, then $\efek=\bot_T$, which contains $t'$.
        \item\label{item:defaultmap} If $r\ne r'$, then $r$ has not been reassigned a value, and still maps to the same object of type $t$. The receiver $r$ is mapped to $\Delta(r)$, which, according to~\eqref{eq:deltaContainsT}, contains $t$. Since $t=t'$, $\Delta(r)$ contains $t'$.
      \end{enumerate}
    \item\label{item:callstart} $e_k$ is a call-start edge with signature $s_\mathcal F$, and $f\in\mathcal F$ is the called procedure.
      Then
        \begin{align*}
          \efek
          &=(\lambda m\,.\,m[r'\to m(r')\cap\tau(s_\mathcal F,\,f)])(\Delta)(r)\\
          &=\Delta[r'\to\Delta(r')\cap\tau(s_\mathcal F,\,f)]\,,
        \end{align*}
      where $r'$ is the receiver of the call.
      \begin{itemize}
        \item If $r'=r$, then $\Delta(r')=\Delta(r)$ which contains $t$. Since $t\in\tau(s_\mathcal F,\,f)$, it follows that $t\in\Delta(r)\cap\tau(s_\mathcal F,\,f)$, and $t\in\efek$.
         \item If $r'\ne r$, see~(\ref{item:defaultmap}).
       \end{itemize}
    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_k\in R$ are the local variables in the callee method, $r'$ is the receiver of the call site corresponding to the return node $n_k$, and $f\in\mathcal F$ is the called method with signature~$s_\mathcal F$.
      Then 
      \[
        \varepsilon_R(e_k)=\lambda m\,.\,m[r'\to m(r')\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_k\to\bot_T].
      \]
      If $r\in\{r_1,\,\dots,\,r_k\}$, see~Case~\ref{item:asgn}. Otherwise, the case is analogous to Case~\ref{item:callstart}.
    \item\label{item:idcase} The node contains any other instruction.
      Then 
      \[
        \ccedgefn R(e_k)(\mpdkm)(r)=\id(\Delta)(r)=\Delta(r),
      \]
      which contains $t$ according to~\eqref{eq:deltaContainsT}.\qedhere
  \end{enumerate}
\end{proof}

We will now show that on a node of a concrete execution path, the correlated-calls analysis does not map receivers to $\top_T$. In other words, the analysis never considers nodes of a concrete execution path unreachable.

\begin{lemma}\label{lem:sound3}
  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, $r\in R$ a receiver, and $d\in D$ a data-flow fact. Then if $d\in M_F(p)(\varnothing)$,
  \begin{equation}
    \mpd(r)\ne\top_T\,.
  \end{equation}
\end{lemma}
\begin{proof}
  By induction on the length of the execution trace.

  \textit{Basis:} 
    Let $p=[\startmain]$. Since the only realizable path corresponding to $p$ is $[(\startmain,\,\Lambda)]$, there is no fact $d\in D$ such that $d\in M_F(p)(\varnothing)$, and the claim follows immediately.

  \textit{Induction hypothesis:} 
  Let $p=[\startmain,\,\dots,\,n_{k-1}]$. Let $\uptau$ be the set of types to which $r$ is mapped by $\mpdkm$:
  \begin{equation}
    \uptau=\mpdkm(r)\,.
  \end{equation}
  Assume the Lemma holds for that for a concrete execution path $$p=[\startmain,\,n_1,\,\dots,\,n_{k-1}]\,,$$ i.e. $\uptau\ne\top_T$ for an arbitrary $r\in R$ and $d_{k-1}\in D$.

  \textit{Induction step:}
    Let $p'=[\startmain,\,n_1,\,\dots,n_{k-1},\,n_k]$ be a concrete execution path.

    Let $e_k=((n_{k-1},\,d_{k-1}),\,(n_k,\,d))$. As shown in~\eqref{eq:musubset},
    \begin{align*}
      \mppd(r)
        &\supseteq\ccedgefn R(e_k)(\mpdkm)(r)\,.
    \end{align*}

    From Definition~\ref{def:edgefn}, we can see that unless $e_k$ is a call-start edge or an end-return edge, the result follows from the induction hypothesis.
    More formally, if $e_k$ is not a call-start or end-return edge, then for all $m\in\lcc_R$,
    \[
      \ccedgefn R(e_k)(m)\sqsubseteq m\,.
    \]
     The edge function corresponding to the call-start and end-return edges is the only place in which the set of types that a receiver maps to can be reduced.

    Assume that $e_k$ is a end-return edge with a call on the receiver $r'\in R$ with a signature $s_\mathcal F$ to a function $f\in\mathcal F$.
    \begin{align*}
      \ccedgefn R&(e_k)(\mpdkm)(r)\\
      &=\left(\lambda m\,.\,m[r'\to m(r)\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(\mpdkm)(r)\\
      &=\left(\mpdkm[r'\to \uptau\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(r)\,,
    \end{align*}
  where $r_1,\,\dots,r_l\in R$ are the local variables in the called method.

    If $r\in\{r_1,\,\dots,\,r_l\}$, then $\efek=\bot_T\ni t$\footnote{In the case of a recursive call, it is possible that both $r\in\{r_1,\,\dots,\,r_l\}$ and $r=r'$.
    In that case, the set to which $r$ will be mapped would be still ``overwritten'' by $\bot_T$.}.

    Otherwise, if $r=r'$, then $\efek=\uptau\cap\tau(s_\mathcal F,\,f)$.

    According to Lemma~\ref{lem:sound1} and by the induction hypothesis, the runtime type $t$ of $r$ must be contained in $\mpdkm(r)=\uptau$. At the same time, by definition, $t$ is part of $\tau(s_\mathcal F,\,f)$. Therefore, $t\in\uptau\cap\tau(s_\mathcal F,\,f)\subseteq\efek$, which means that $\efek\ne\top_T$.

    The same reasoning applies to the case where $e_k$ is a call-start edge.
\end{proof}

Finally, we can prove the Soundness Lemma.

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:sound}}] Let $\rho=\result(\transCC_R(P))$. Then
  \begin{align*}
    \backCC(\rho)(n)
    &=D_n^\Subset(\rho)\\
    &=\left\{d'\ |\ 
        d'\in\mvp F(n)\,\wedge\,\forall r\in R:\ \rho(n,\ d')(r)\ne\top_T\right\}.
  \end{align*}
  Since $\mvp F(n)=\bigsqcap_{q\in\ivp(n)}M_F(q)(\varnothing)$, and $p\in\ivp(n)$, it follows that
    \begin{align*}
      d&\in M_F(p)(\varnothing)\\&\subseteq\mvp F(n)\,.
    \end{align*}
  At the same time, for all receivers $r\in R$,
  \begin{align*}
    \rho(n,\,d)(r)
    &=\left(\bigsqcap_{q\in\ivp(n)}\mpddef q d\right)(r)\\
    &=\bigsqcap_{q\in\ivp(n)}\mpddef q d(r)\,.
  \end{align*}
  According to~Lemma~\ref{lem:sound3}, $\mpd(r)\ne\top_T$.
  Since $p\in\ivp(n)$,
  \begin{align*}
    \mpd(r)\subseteq\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)\,.
  \end{align*}
  From $\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)=\rho(n,\,d)(r)$ it follows that
  $\mpd(r)\subseteq\rho(n,\,d)(r)$.
  Therefore, $\rho(n,\,d)(r)\ne\top_T$, and $d\in D_n^\Subset(\rho)=\backCC(\rho)(n)$.
\end{proof}

\subsection*{Correlated Call Receivers}
This appendix contains the proof for Lemma~\ref{} which shows that in a correlated-calls analysis, it is enough to consider only correlated-call receivers~$\rcc$.

The following Lemma shows that the types to which a given receiver is mapped in the result of the algorithm is not affected by other receivers and the types to which they are mapped.

\begin{lemma}\label{lem:recindepedgefn}
  Let $P$ be an IFDS problem. Let $N^*$ be the supergraph for $P$, $D$ the set of data-flow facts, $n\in N^*$ a node, and $p=[\startmain,\,\dots,\,n]$ a path in the supergraph. Let $d\in D\cup\{\Lambda\}$.
  Then for any realizable path $p'\in\textsf{RP}(p,\,d)$, set $S\subseteq R$, and receiver $r\in S$,
  \begin{equation}
    \ccedgefn S(p')(\topcc)(r)=
    \ccedgefn{\{r\}}(p')(\topcc)(r)\,.
  \end{equation}
\end{lemma}
\begin{proof}
  By induction on the length of $p$.

  \textit{Basis:} $p'=[(\startmain,\,\Lambda)]$. Then $\ccedgefn S(p')=\id=\ccedgefn{\{r\}}(p')$, and the Lemma follows directly.

  \textit{Induction hypothesis:} Suppose that for a path $q=[(\startmain,\,\Lambda),\,\dots,\,(n_{k-1},\,d_{k-1})]$, where $q\in\textsf{RP}(n,\,d)$, the Lemma holds, i.e. both edge functions map $r$ to the same set of types $\uptau$:
  \begin{align*}
    \uptau
    &=\ccedgefn S(q)(\topcc)(r)\\
    &=\ccedgefn{\{r\}}(q)(\topcc)(r)\,.
  \end{align*}

  \textit{Induction step:} Let $q'=[(\startmain,\,\Lambda),\,\dots,\,(n_{k-1},\,d_{k-1}),\,(n_k,\,d_k)]$ and the edge $e_k=((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))$.

  Observe that for any set $U\subseteq R$ such that $r\in U$,
  \begin{align}\label{eq:edgefnU}
    \ccedgefn U(q')(\topcc)(r)
    &=\ccedgefn U(e_k)(\ccedgefn U(q)(\topcc))(r)\,.
  \end{align}

  We can see from~\eqref{eq:edgefnThroughDelta} that there are two cases.

  If $d_{k-1}=d_k=\Lambda$, $\ccedgefn S(e_k)=\id=\ccedgefn{\{r\}}(e_k)$, and, due to~\eqref{eq:edgefnU},
  \begin{align*}
    \ccedgefn S(q')(\topcc)(r)&=\uptau\\
    &=\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
  \end{align*}

  Otherwise, there are four sub-cases.
  \begin{enumerate}
    \item $e_k$ is a call-start edge, $r'.c()$ is the call site at $n_{k-1}$ with signature $s_\mathcal F$, $f\in\mathcal F$ is the called procedure, and $r'\in U$.
    Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\delta(m)(r)\cap\tau(s_\mathcal F,\,f)]\,.
    \]
    There are two sub-cases.
    \begin{enumerate}
      \item\label{item:callstartreceq} If $r=r'$, then, according to~\eqref{eq:edgefnU}, the resulting set of types 
        \[
          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\cap\tau(s_\mathcal F,\,f).
        \]
        If $d_{k-1}=\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\botcc(r)=\bot_T$. If $d_{k-1}\ne\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\ccedgefn U(q)(\topcc)(r)=\uptau$. The set $\tau(s_\mathcal F,\,f)$ is the same for either case.

        Therefore, the value of $\ccedgefn U(q')(\topcc)(r)$ has the same result regardless of $U$,
        which means that $\ccedgefn S(q')(\topcc)(r)=\ccedgefn{\{r\}}(q')(\topcc)(r)$, and the Lemma holds.
      \item\label{item:callstartrecneq} If $r\ne r'$, then
        \begin{equation}
          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\,,
        \end{equation}
        which, as we have seen in~Case~\eqref{item:callstartreceq}, does not depend on~$U$, and the Lemma holds.
    \end{enumerate}
    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_l\in U$ are the local variables in the callee method, $r'.c()$ is the call corresponding to the return node at $n_k$, $f\in\mathcal F$ is the called method with signature $s_\mathcal F$, and $r'\in U$.
    Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)
      [r'\to\delta(m)(r)\cap\tau(s_\mathcal F,\,f)]
      [r_1\to\bot_T]\ldots[r_l\to\bot_T]\,.
    \]
    There are three sub-cases.
    \begin{enumerate}
      \item\label{item:localvarrec} If $r\in\{r_1,\,\dots,\,r_l\}$, then regardless of the value of $U$,
      \[
        \ccedgefn U(q')(\topcc)(r)=\bot_T\,,
      \]
      and the Lemma holds.
      \item Otherwise, if $r=r'$, the case is analogous to Case~\eqref{item:callstartreceq}.
      \item If $r\notin\{r',\,r_1,\,\dots,\,r_l\}$, then see Case~\eqref{item:callstartrecneq}.
    \end{enumerate}
    \item $n_{k-1}$ contains an assignment for $r'\in U$. Then
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\bot_T]\,.
    \]
    If $r=r'$, see Case~\eqref{item:localvarrec}. If $r\ne r'$, see Case~\eqref{item:callstartrecneq}.
    \item Otherwise,
    \[
      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)\,,
    \]
    and the case is analogous to Case~\eqref{item:callstartrecneq}.\qedhere
  \end{enumerate}
\end{proof}

The following Lemma shows that the correlated-calls analysis computes the results for each receiver independently, or separately. To compute the set of types to which a receiver~$r$ is mapped at each exploded-graph node, we can exclude all other receivers in the program from the analysis (recall from~\eqref{eq:edgefndef} that the set of receivers that are considered in the analysis is specified by the set $S$ in a correlated-calls transformation $\transCC_S$). Therefore, for a given receiver $r$, the results of a $\transCC_S$- and a $\transCC_{\{r\}}$-analysis are the same.

\begin{lemma}\label{lem:recindep} Let $P$ be an IFDS problem. Let $N^*$ be the supergraph for $P$, $D$ the set of data-flow facts, and $S\subseteq R$ a set of receivers.
  Then for any $n\in N^*$, $d\in D$, and receiver $r\in S$,
  \begin{equation}
    \result\left(\transCC_S(P)\right)(n,\,d)(r)=
    \result(\transCC_{\{r\}}(P))(n,\,d)(r)\,.
  \end{equation}
\end{lemma}
\begin{proof}
  According to~\eqref{eq:ideresult}, \eqref{eq:mvpdef}, and~\eqref{eq:envTransToEdgefn},
  \begin{align}
    \result\left(\transCC_S(P)\right)(n,\,d)(r)
    &=\mvp{\textsf{Env}}(n,\,d)(r)\notag\\
    &=\left(\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\Omega)(d)\right)(r)\notag\\
    &=\left(\bigsqcap_{q\in\ivp(n)}\bigsqcap_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)\right)(r)\notag\\
    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)(r)\,.\label{eq:resultThroughEdgefn}
  \end{align}
  Then from Lemma~\ref{lem:recindepedgefn},
  \begin{align*}
    \result\left(\transCC_S(P)\right)(n,\,d)(r)
    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\\
    &=\result\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)\,.\qedhere
  \end{align*}
\end{proof}

The next lemma shows that the set of types to which a receiver is mapped in a correlated-calls lattice element can be represented as an intersection of static-type function applications $\tau(s_{\mathcal F_i},\,f_i)$.
\begin{lemma}\label{lem:edgefnThroughTaus}
  For an IFDS problem $P$, a node $n\in N^*$, and fact $d\in D$, let $p\in\mathsf{RP}(n,\,d)$ be a realizable path and $r\in R$ a receiver. Then there exists a non-negative number $\gamma$ of calls on the receiver $r$ with signatures $s_{\mathcal F_\gamma}$ to the functions $f_\gamma\in\mathcal F_\gamma$, for which
  \[
    \ccedgefn{\{r\}}(p)(\topcc)(r)=
      \bigcap_{\gamma\ge0}\tau(s_{\mathcal F_\gamma},\,f_\gamma)\,.
  \]
\end{lemma}
\begin{proof}
  Let $p$ have the following form\footnote{It can be shown from the definition of a pointwise representation in~Sagiv et al.~\cite{sagiv1996precise} that in a realizable path, there is never an edge from a fact of the set $D$ to a $\Lambda$ fact. Therefore, we can represent $p$ as a sequence of nodes that has a prefix of $\Lambda$-fact nodes, after which all nodes are non-$\Lambda$ facts.}:
  \[
    p=[(\startmain,\,\Lambda),\,(n_1,\,\Lambda),\,\dots,\,(n_k,\,\Lambda),
       (n_{k+1},\,d_{k+1}),\,\dots,\,(n_{k+l},\,d_{k+l})]\,,
  \]
  where $l\ge1$ and the facts for all nodes up to $n_k$ are equal to $\Lambda$ and $d_{k+i}\in D$ for $0<i\le l$.

  As previously, for all $i$, we will denote the edge $(n_i,\,n_{i+1})$ by $e_i$.

  From~\eqref{eq:edgefndef} we can infer that
  \[
    \ccedgefn{\{r\}}(p)=
    \ccedgefn{\{r\}}(e_{k+l})
    \circ\ldots
    \circ\ccedgefn{\{r\}}(e_{k+2})
    \circ(\lambda m\,.\,\beta)
    \circ\id
    \circ\ldots
    \circ\id\,,
  \]
  where
  \[
    \beta=
    \begin{cases}
      \botcc[r\to\tau(s_\mathcal F,\,f)]&\text{if $(n_k,\,n_{k+1})$ is a call-start or end-return edge, and}\\&\text{the call site $r.c()$ with signature $s_\mathcal F$ to the function}\\
      &\text{$f\in\mathcal F$ corresponds to the call-start or end-return edge,}\\
      \botcc&\text{otherwise\footnotemark.}
    \end{cases}
  \]
  \footnotetext{Since $d_k=\Lambda$ and $d_{k+1}\ne\Lambda$, the micro function for the edge $e_{k+1} $ is equal to $\lambda m\,.\,\varepsilon_{\{r\}}(e_{k+1})(\botcc)$. From the definition of $\varepsilon_S$~\eqref{eq:varepsilon} we can see that the only case where $\varepsilon_{\{r\}}(e_{k+1})(m)$ would not be equal to $\botcc$ is when $e_{k+1}$ is call-start or end-return edge.}

  Therefore,
  \begin{align}\label{eq:edgefnbeta}
    \ccedgefn{\{r\}}(p)(\topcc)
      &=\left(\ccedgefn{\{r\}}(e_{k+l})\circ\ldots\circ
        \ccedgefn{\{r\}}(e_{k+2})\right)((\lambda m\,.\,\beta)(\topcc))\notag\\
      &=\left(\ccedgefn{\{r\}}(e_{k+l})\circ\ldots\circ
        \ccedgefn{\{r\}}(e_{k+2})\circ\id\right)(\beta)\,.
  \end{align}

We can now prove the lemma by induction on $l$.

\textit{Basis:}
If $l=1$, then $\ccedgefn{\{r\}}(p)(\topcc)=\id(\beta)=\beta$.
There are two cases.

If $\beta=\botcc$, then 
\begin{align*}
  \ccedgefn{\{r\}}(p)(\topcc)(r)&=\beta(r)\\&=\bot_T\,,
\end{align*} and $\gamma=0$.

If $\beta=\botcc[r\to\tau(s_\mathcal F,\,f)]$, then 
\[
  \ccedgefn{\{r\}}(p)(\topcc)(r)=\tau(s_\mathcal F,\,f)\,,
\]
and $\gamma=1$.

\textit{Induction hypothesis:}
Assume that for a path $p=[(\startmain,\,\Lambda),\,\dots,\,(n_{k+l},\,d_{k+l})]$, the Lemma holds for $\gamma=N$, where $N\ge0$.

\textit{Induction step:}
Let $p'=[(\startmain,\,\Lambda),\,\dots,\,(n_{k+l},\,d_{k+l}),\,(n_{k+l+1},\,d_{k+l+1})]$.

Recall that
\begin{align*}
  \ccedgefn{\{r\}}(p')(\topcc)(r)
  &=\ccedgefn{\{r\}}(e_{k+l+1})\left(\ccedgefn{\{r\}}(p)(\topcc)\right)(r)\,.
\end{align*}

From~\eqref{eq:varepsilon} we can see that unless $e_{k+l+1}$ is a call-start or end-return edge corresponding to a call on the receiver $r$, then $\ccedgefn{\{r\}}(e_{k+l+1})(r)$ must be equal to either $\bot_T$ or $m(r)$, where $m=\ccedgefn{\{r\}}(p)(\topcc)$.

If $\ccedgefn{\{r\}}(e_{k+l+1})(r)=\bot_T$, then the Lemma holds for $\gamma=0$.

Otherwise,
\begin{align*}
  \ccedgefn{\{r\}}(e_{k+l+1})(\topcc)(r)&=\ccedgefn{\{r\}}(p)(\topcc)(r)\\
  &=\bigcap_{N}\tau(s_{\mathcal F_N},\,f_N)\,,
\end{align*}
and therefore $\gamma=N$.

Suppose that $e_{k+l+1}$ is a call-start edge with a call on the receiver $r$ with signature $s_\mathcal G$ to a function $g\in\mathcal G$. Then, according to~\eqref{eq:varepsilon}, 
\[
  \ccedgefn{\{r\}}(e_{k+l+1})=\lambda m\,.\,m[r\to m(r)\cap\tau(s_\mathcal G,\,g)]\,.
\]
Therefore,
\begin{align*}
  \ccedgefn{\{r\}}&(p')(\topcc)(r)\\
  &=\lambda m\,.\,m[r\to m(r)\cap\tau(s_\mathcal G,\,g)]\left(\ccedgefn{\{r\}}(p)(\topcc)\right)(r)\\
  &=\ccedgefn{\{r\}}(p)(\topcc)(r)\cap\tau(s_\mathcal G,\,g)\\
  &=\left(\bigcap_{N}\tau(s_{\mathcal F_N},\,f_N)\right)\cap\tau(s_\mathcal G,\,g)\,,
\end{align*}
and the Lemma holds for $\gamma=N+1$.

The case where $e_{k+l+1}$ is an end-return edge is analogous to the previous case.
\end{proof}

We now show that a receiver will be only mapped to $\topcc$ if it is the receiver of a correlated call.

\begin{lemma}\label{lem:ccrectop}
   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a dataflow fact such that there exists a realizable path $p\in\textsf{RP}(n,\,d)$. Let $T$ be the set of all types in the program.
   If there exists a receiver $r\in R$ such that
  \[
    \ccedgefn{\{r\}}(p)(\topcc)(r)=\top_T\,,                       
  \]
  then $r\in \rcc$.
\end{lemma}
\begin{proof}
 According to Lemma~\ref{lem:edgefnThroughTaus},
 \[
   \ccedgefn{\{r\}}(p)(\topcc)(r)=
      \bigcap_{\gamma\ge0}\tau(s_{\mathcal F_\gamma},\,f_\gamma).
 \]

 Let $\tau_i=\tau(s_{\mathcal F_i},\,f_i)$. 
 For a given $k$, let $r.m_k()$ be the call site corresponding to $\tau_k$, and $T'$ the set of types compatible with the static type of $r$.
 Recall from Section~\ref{sec:ef} that 
 \begin{itemize}
   \item $\tau_k\ne\top_T$;
   \item if $\tau_k=T'$ then the corresponding call site is monomorphic;
   \item if $\tau_k\subset T'$ then the call site is polymorphic.
 \end{itemize}

 From the conditions of the Lemma, 
 \begin{equation}
   \bigcap_{\gamma\ge 0}\tau_\gamma=\top_T\,.
 \end{equation}

 If all $\tau_k=T'$, then $\bigcap_{\gamma\ge 0}\tau_\gamma$ is also equal to $T'$. Since $T'\ne\top_T$, this is a contradiction.

 If exactly one $\tau_k\subset T'$ and the rest are equal to $T'$, then $\bigcap_{\gamma\ge 0}\tau_\gamma$ is equal to $\tau_k$, which cannot be $\top_T$ either.

 Therefore, there are at least two sets, $\tau_i$ and $\tau_j$, which are strict subsets of $T'$. Since both $\tau_i$ and $\tau_j$ are non-empty and their intersection equals $\top_T$, $\tau_i$ and $\tau_j$ must be disjoint. If $\tau_i$ and $\tau_j$ are disjoint, they must correspond to different call sites.

 In other words, there are at least two calls on the same receiver for which the static-type function is a strict subset of the set of types compatible with a given receiver $r$. It follows that both calls have to be polymorphic. Therefore,~${r\in\rcc}$.
\end{proof}

We will now show that if a receiver ever gets mapped to top, then it is a correlated-calls receiver.

\begin{lemma}\label{lem:ccrectop}
   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a dataflow fact such there exists a realizable path $p\in\textsf{RP}(n,\,d)$.
   Then, if there exists a receiver $r\in R$, such that
  \[
    \result\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)=\top_T\,,
  \]
  then $r\in \rcc$.
\end{lemma}
\begin{proof}
  As shown in~\eqref{eq:resultThroughEdgefn},
  \[
    \result\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
  \]
  Since the latter is equal to $\top_T$, it follows that for each realizable path $p'$ to node $n$, $\ccedgefn{\{r\}}(p')(\top)(r)=\top_T$. According to~Lemma~\ref{lem:ccrectop}, this is only possible if $r\in\rcc$.
\end{proof}

Finally, we present the proof for Lemma~\ref{lem:onlycorrec} which states that a correlated-calls analysis that considers all receivers computes the same result as an analysis that considers only correlated-call receivers.

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:onlycorrrec}}]
  From~\eqref{eq:ucc} we know that
  \begin{align*}
    \backCC(\result\left(\transCC_R(P)\right))
    &=\left\{(n,\,D_n^\Subset(\result(\transCC_R(P))))\ |\ n\in N^*\right\}.
  \end{align*}
  According to~\eqref{eq:dnq} and~Lemma~\ref{lem:recindep}, for a given $n\in N^*$,
  \begin{align*}
    D_n^\Subset&(\result(\transCC_R(P))))\\
    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall r\in R:\ \left\{(r,\,\result(\transCC_{\{r\}}(P))(n,\,d)(r))\ |\ r\in R\right\}(r)\ne\top_T\right\}\\
    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in R}:\ \result(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}.
  \end{align*}

Since, according to Lemma~\ref{lem:ccrectop}, $\result(\transCC_{\{r\}}(P))(n,\,d)(r)$ can only be equal to $\top_T$ when $r\in\rcc$, we can conclude that
  \begin{align*}
    D_n^\Subset&(\result(\transCC_R(P))))\\
    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in\rcc}:\ \result(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}\\
    &=D_n^\Subset(\result(\transCC_\rcc(P)))).
  \end{align*}

  Therefore,
  \begin{align*}
    \backCC(\result\left(\transCC_R(P)\right))
    &=\left\{(n,\,D_n^\Subset(\result(\transCC_\rcc(P))))\ |\ n\in N^*\right\}\\
    &=\backCC(\result\left(\transCC_\rcc(P)\right))\,.\qedhere
  \end{align*}
\end{proof}

\section*{Representation of Micro Functions}
In this part of the appendix we present the proofs to the Lemmas related to the representation of micro functions with update maps.

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:normeq}}]
    Let $\updfun f^*=\setpair I U$.
    For any $\tau\in T,$
    \[
        \begin{aligned}
            \denote{\mathcal N(\updfun f^*)}(\tau)
            &=\denote{\mathcal N(\langle I,\ U\rangle)}(\tau)\\
            &=\denote{\setpair{I\cup U}U}(\tau)\\
            &=\tau\cap(I\cup U)\cup U\\
            &=(\tau\cap I)\cup(\tau\cap U)\cup U\\
            &=\tau\cap I\cup U\\
            &=\denote{\setpair IU}(\tau)\\
            &=\denote{\updfun f^*}(\tau)\,.
        \end{aligned}
    \]
    Thus, $\denote{\mathcal N(\updfun f^*)}=\denote{\updfun f^*}$.
\end{proof}

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:normuneq}}]
    Let us show that there always exists a set $\tau\subseteq T$ such that $\denote{\setpair IU}(\tau)\ne\denote{\setpair{I'}{U'}}(\tau)$. There are two cases:
    \begin{enumerate}
        \item $U\ne U'$. Then for the empty set $\tau=\varnothing$,
            \[
                \denote{\setpair IU}(\tau)=\denote{\setpair IU}(\varnothing)=(\varnothing\cap I)\cup U=U\,,
            \]
            whereas 
            \[ 
                \denote{\setpair {I'}{U'}}(\tau)=\denote{\setpair {I'}{U'}}(\varnothing)=(\varnothing\cap I')\cup U'=U'.
            \]
            Hence, $\denote{\setpair IU}\ne\denote{\setpair {I'}{U'}}$.
        \item $I\ne I'$. Then for the set of all types $\tau=T$,
            \[
                \denote{\setpair IU}(\tau)=\denote{\setpair IU}(T)=(T\cap I)\cup U=I\cup U\,.
            \]
            Since $\setpair IU$ is normalized, $U\subseteq I$, and
            \[
                I\cup U= I\,.
            \]
            At the same time,
            \[
                \denote{\setpair {I'}{U'}}(\tau)=\denote{\setpair {I'}{U'}}(T)=(T\cap I')\cup U'=I'\cup U'=I'\,.
            \]
            Since $I\ne I'$, it follows that $\denote{\setpair IU}\ne \denote{\setpair {I'}{U'}}$. \qedhere
    \end{enumerate}
\end{proof}

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:efficient}}]
  \begin{enumerate}
    \item The identity function is represented as
      \[
        \denote{\id}=\{(r,\,\langle \bot_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,;
      \]
      the top function is represented as
      \[
        \denote{\lambda m\,.\,\topcc}=\{(r,\,\langle \top_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,.
      \]
    \item Equations~\eqref{eq:compclosed} and~\eqref{eq:meetclosed} show that the representation of micro functions is closed under composition and meet.
    \item To show that our representation for micro functions forms a lattice with finite height, let us first show that $\lcc_\rcc:\,\rcc\to2^T$ forms a lattice. Since $T$ is a finite set, $(2^T,\,\subseteq)$ is a finite-height lattice. $\rcc$ is a finite set. Hence, the mapping
    \[
      \rcc\mapsto2^T=\{(r,\,t)\,|\,r\in \rcc,\,t\in 2^T\}=\lcc_\rcc
    \]        
    also forms a finite-height lattice \cite{nielson1999principles}.

    Furthermore, $\lcc_\rcc$ is a finite set. 
    Every element of $\lcc_\rcc$ can be applied to $|\rcc|$ receivers, where each receiver is mapped to a set of types. There are $|\rcc|\cdot2^{|T|}$ different possibilities to form those mappings, so
    \[
      |\lcc_\rcc|=|\rcc|\cdot2^{|T|}.
    \]
    Therefore, $\lcc_\rcc\mapsto \lcc_\rcc$ also forms a finite-height lattice.
    \item All operations can be computed in $O(\rcc\times T)$ time. Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
    \item The space bound is $O(\rcc\times T)$.
  \end{enumerate}
\end{proof}

### 2014-12-05 content/background.tex
started to move proofs to appendix; removing dependency on minted
adding comments
updated reference to Frank's paper

@@
 
-The idea of using correlated calls to remove infeasible paths in data-flow analyses of object-oriented programs was introduced by F.\,Tip~\cite{frank2014correlated}.
+The idea of using correlated calls to remove infeasible paths in data-flow analyses of object-oriented programs was introduced by F.\,Tip~\cite{DBLP:journals/scp/Tip15}.
 The possibility of using IDE to achieve this is mentioned, but not elaborated upon.
@@
   Consider the program in Listing~\ref{list:examplejava}. The supergraph corresponding to that program is shown in Figure~\ref{fig:examplesupergraph}.
-  \begin{listing}
+\begin{figure}
+  \centering
+  \begin{minipage}{\textwidth}
     \inputMinted{java}{examplesupergraph.java}
+  \end{minipage}
   \caption{An example Java program}
   \label{list:examplejava}
-  \end{listing}
+\end{figure}
 
@@
 
+\begin{mdelete}
 \begin{example}\label{ex:constprop}
@@
   Consider the following program:
+
 \inputMinted{java}{constprop.java}
@@
 \end{example}
+
 \begin{figure}
@@
   \end{figure}
+\end{mdelete}
 

### 2014-12-05 content/eval.tex
updated reference to Frank's paper

@@
 
-Finally, correlated calls can occur on multiple receivers and other scenarios discussed in~\cite{frank2014correlated} that are not handled in this work.
+Finally, correlated calls can occur on multiple receivers and other scenarios discussed in~\cite{DBLP:journals/scp/Tip15} that are not handled in this work.

### 2014-12-05 content/intro.tex
adding comments
updated reference to Frank's paper

@@
 
-We improve the precision of IFDS problem solutions by eliminating infeasible paths that occur in object-oriented programs in the presence of \textit{correlated method calls}~--- polymorphic calls that are invoked on the same object~\cite{frank2014correlated}.
+We improve the precision of IFDS problem solutions by eliminating infeasible paths that occur in object-oriented programs in the presence of \textit{correlated method calls}~--- polymorphic calls that are invoked on the same object~\cite{DBLP:journals/scp/Tip15}.
 
@@
 
-The remainder of this paper is organized as follows.
+\mtodo{Reference appendix?}The remainder of this paper is organized as follows.
 In the next section, we describe the IFDS and IDE analyses in detail.

### 2014-12-05 content/background.tex
add comments on what to remove

@@
 \subsection{Related Work}
+\otodo{should we move Related Work to near the end of the paper?}
 IFDS is a version of the functional approach to data-flow analysis developed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.
@@
   Consider the program in Listing~\ref{list:examplejava}. The supergraph corresponding to that program is shown in Figure~\ref{fig:examplesupergraph}.
+  \otodo{Can we merge the examples from Figures 1 and 2 into a single example program?}
+\otodo{I think we can remove the supergraph Figure 3.}
 \begin{figure}

### 2014-12-05 content/eval.tex
add comments on what to remove

@@
 
+\begin{odelete}
 \subsubsection{IFDS}
+\otodo{We should incorporate the four functions into the explanation of IFDS in the background. Then we don't need them here.}
 As described in Section~\ref{sec:ifdsdef}, an IFDS problem is defined in terms of an exploded supergraph.
@@
 \end{itemize}
+\end{odelete}
 
@@
 
+\begin{odelete}
 \begin{example}
@@
 \end{example}
+\end{odelete}
 
@@
 
+\begin{odelete}
 \subsubsection{Conversion from IFDS to IDE}
@@
 We also implemented a correlated-call transformation from IFDS into IDE problems that consider correlated calls. This transformation is described in Section~\ref{sec:cctrans}.
+\end{odelete}
 
@@
 \subsubsection{Benchmark Testing}
+\otodo{We need to decide what exactly we want to include in the evaluation.
+    The numbers of correlated calls are interesting. But I think we want
+    to leave out all mention of the taint analysis. Perhaps we should
+    have no empirical results at all (and only the theory/proofs)?}
 To assess the benefit of the correlated-calls analysis, we counted the frequencies of correlated-call occurrences in the Dacapo benchmarks~\cite{blackburn2006dacapo}.
@@
 
+\begin{odelete}
 \subsection{Future Work}
+\otodo{We should convert this section into two or three sentences to be added to the conclusion. They should focus especially on the interprocedurally-correlated receivers.}
 In this section we point out the limitations of the correlated-calls analysis and suggest improvements to the analysis for future work.
@@
 Finally, correlated calls can occur on multiple receivers and other scenarios discussed in~\cite{DBLP:journals/scp/Tip15} that are not handled in this work.
+
+\end{odelete}

### 2014-12-05 content/intro.tex
add comments on what to remove

@@
 \section{Introduction}
+\otodo{This section should be shrunk a lot (not completely deleted)}
+\begin{odelete}
 Static program analysis aims to discover properties of computer programs without running them.
@@
 We improve the precision of IFDS problem solutions by eliminating infeasible paths that occur in object-oriented programs in the presence of \textit{correlated method calls}~--- polymorphic calls that are invoked on the same object~\cite{DBLP:journals/scp/Tip15}.
+\end{odelete}
 
@@
 \subsection{IFDS and IDE}
+\otodo{This section should be moved to the Background section (and suitably merged with the text there).}
 The IFDS framework is a precise and efficient algorithm for data-flow analysis.

### 2014-12-05 content/background.tex
restructuring

@@
 This section describes the general ideas underlying IFDS and IDE.
-
-\subsection{Related Work}
-\otodo{should we move Related Work to near the end of the paper?}
-IFDS is a version of the functional approach to data-flow analysis developed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.
-Their algorithm is based on computing \textit{summary functions} that return the data-flow value at the end of a procedure, given the data-flow value at the start of the procedure.
-IFDS problems form a more restricted set of data-flow problems: unlike in the functional approach, IFDS flow functions have to be distributive, and the set of data-flow facts $D$ has to be finite.
-However, the IFDS algorithm is more general than Sharir's and Pnueli's algorithm in that it can handle programs containing local variables and parameters in recursive methods.
-
-IFDS has been used to encode a variety of data-flow problems.
-More complex examples of applications include typestate analysis (determining which operations can be performed on an object at a given program point)~\cite{naeem2008typestate} or shape analysis (detecting errors and validating properties of programs at compile time)~\cite{DBLP:conf/birthday/KreikerRRSWY13}.
-
-IFDS is implemented for two popular static-analysis frameworks, the T.J. Watson Libraries for Analysis (WALA)~\cite{fink2012wala} and Soot~\cite{vallee1999soot}.
-
-WALA is a framework for static analysis on Java bytecode developed by the IBM T.J.~Watson Research Center.
-In the implementation of our work, we use WALA to build and traverse the supergraph (a special kind of control-flow graph) of a Java program\footnote{However, we do not use WALA's IFDS implementation, as explained in~Section~\ref{chapter:eval}.}.
-
-Soot is a framework for program analysis and optimization on Java bytecode, developed by the Sable Research Group at McGill University.
-Unlike WALA, Soot also has an implementation of the IDE algorithm.
-The IFDS and IDE implementations for Soot are part of the Heros project~\cite{bodden2012inter}.
-
-Whereas one advantage of Soot's IFDS implementation (and other static analysis tools) is ease of use and extensibility, WALA's primary focus is efficiency.
-For example, WALA uses bit-vectors to represent some of the analysis data types, like local variables and parameters.
-Another difference is that WALA's intermediate representation of a program uses static single assignment (SSA) form~\cite{cytron1991efficiently}.
-SSA form is a representation of the program in which each variable has only one definition (assignment).
-SSA can make dataflow analysis simpler and more efficient~\cite{appel1998ssa}.
-
-Work on improving the IFDS algorithm includes Practical Extensions by~N.\,Naeem and O.\,Lhot\'ak~\cite{naeem2010pei}.
-Their paper presents four extensions to the IFDS algorithm.
-Two of the extensions improve the efficiency of the IFDS analysis for certain classes of IFDS problems.
-Another extension widens the class of problems applicable for the IFDS analysis.
-However, those extensions do not affect the precision of IFDS problems.
-Our analysis, in contrast, does not improve the efficiency or generality of IFDS, but it allows us to solve IFDS problems more precisely.
-
-The fourth extension is targeted towards programs that are represented in SSA form.
-Executing the IFDS analysis on such programs results in loss of precision in the presence of control-flow constructs (e.g.
-conditionals and loops), compared to programs in non-SSA form.
-The extension makes the IFDS analysis on programs in SSA form as precise as on programs that are not represented in SSA form.
-In contrast, the correlated-calls analysis is applicable to programs in both SSA and non-SSA forms.
-Even if applied to a program in SSA form, our analysis and the extension improve the precision of IFDS in unrelated situations: the first analysis handles correlated calls, and the latter handles control-flow constructs.
-Thus, an IFDS analysis could benefit from both precision improvements independently.
-
-Another work on improving the efficiency of the IFDS algorithm is E.\,Bodden et~al.'s framework for the analysis of software products lines~\cite{bodden2013spl}.
-Their paper uses transformations from IFDS to IDE problems, a technique we also employ.
-Finally, J.\,Rodriguez and O.\,Lhot\'ak implemented a concurrent version of the IFDS algorithm using actors~\cite{rodriguez2010concurrent}.
-However, neither of those works is concerned with improving the precision of IFDS results.
-
-The correlated-calls analysis improves the precision of a data-flow analysis by eliminating a special type of infeasible paths.
-This is similar to the idea of context-sensitive analysis: just as a context-sensitive analysis eliminates infeasible paths from the end of a procedure to the call sites that do not match the given procedure call, the correlated-calls analysis eliminates infeasible paths caused by correlated method calls.
-
-The idea of using correlated calls to remove infeasible paths in data-flow analyses of object-oriented programs was introduced by F.\,Tip~\cite{DBLP:journals/scp/Tip15}.
-The possibility of using IDE to achieve this is mentioned, but not elaborated upon.
-Our work presents a concrete solution to the problem and an implementation of that solution.
-
-The idea of eliminating infeasible paths caused by correlated calls is similar to M.~Sridharan et~al.'s work on improving the precision of pointer analysis for JavaScript programs~\cite{DBLP:conf/ecoop/SridharanDCST12}.
-For each pointer, a pointer analysis determines the possible set of objects (the \textit{points-to} set) that the pointer can reference at a given program point.
-In JavaScript, it is challenging to compute the points-to set of fields because in general, field names can be derived from arbitrary expressions and bound at runtime.
-As a result, an imprecise data-flow analysis will include infeasible paths between values of the form \verb'o[p]' (access of a property \verb'p' of object \verb'o'), where at compile time, \verb'p' can be bound to different values.
-The idea of the paper is to track all dynamic property accesses (reads and writes) on an object \verb'o' with property name \verb'p'.
-The code snippets containing the references \verb'o[p]' are then extracted into a separate function $f$.
-The analysis is then run so that for each possible value of \verb'p', $f$ is analyzed separately; therefore, for a given property name, all correlated objects with that name are analyzed together.
-
-The differences between this method of tracking correlated calls and our analysis are the following.
-\begin{itemize}
-  \item \textit{Type of target data-flow analysis} whose precision is to be improved.
-Our analysis improves the precision of IFDS data-flow analyses, whereas the JavaScript analysis improves the precision of pointer analysis.
-  \item \textit{Target language}. Our analysis is for object-oriented languages where polymorphic methods, and not property names (which are known at compile time), cause infeasible paths.
-  \item \textit{Different handling of correlated calls}.
-Extracting code that contains correlated calls into separate methods would not prevent infeasible paths.
-Instead, our analysis uses IDE flow functions to detect and eliminate infeasible paths caused by correlated calls.
-\end{itemize}
 
@@
 
+\commentout{
 \begin{example}
@@
 \end{example}
+}
 
@@
 
+\begin{mdelete}
 \begin{example}
@@
 
+\mtodo{The figure that we deleted was constructed so that there would be a realizable and a non-realizable path. Now that we deleted that figure, let's delete this example as well.}
+
 However, the graph also contains an inter-procedurally invalid path
@@
 the context.
+
+\subsection{IFDS and IDE}\mtodo{I will merge this section with the following two sections}
+The IFDS framework is a precise and efficient algorithm for data-flow analysis.
+IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
+The IFDS analysis is a version of the classic \textit{functional approach} to data-flow analysis proposed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.
+
+Given a data-flow problem that satisfies the restrictions of IFDS, the algorithm provides a \textit{context-sensitive} solution in polynomial time.
+In other data-flow algorithms not based on the functional approach, the result of the analysis at the entry of a procedure ``merges'' the incoming data obtained from all callers of the procedure.
+As a consequence, there is one global data-flow result computed at the end of the procedure.
+Context-sensitivity, however, allows an analysis to compute the data-flow result for a given procedure as a \textit{function} of the data-flow value at the start of the procedure.
+In other words, the analysis result for a procedure varies depending on where the procedure was called from.
+This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.
+
+Compared to IFDS, most data-flow analyses are either general but do not run in polynomial time~\cite{knoop1992interprocedural,pnueli1981two} or handle a very specific set of problems~\cite{knoop1993efficient}.
+
+The IFDS algorithm is applicable to problems which can be expressed with data-flow functions that satisfy certain restrictions.
+\textit{Inter-procedural} flow functions specify how data flows from the invocation of a procedure to its start, and from the procedure's end back to its call site.
+\textit{Distributive} flow functions are those that distribute over the confluence operator.
+In the context of IFDS, the confluence operator is called meet, and it can be either union or intersection.
+The data-flow facts on which the analysis operates must be a \textit{finite} set $D$.
+Each flow function operates on a \textit{subset} of $D$ (for example, the set of variables in the program) which makes the domain of the flow functions the power set of $D$.
+We describe the IFDS restrictions in detail in Section~\ref{sec:suitableifds}.
+
+The IDE framework is an expressive extension to IFDS that was created by the same authors in 1996.
+The problems that IDE can solve include, but are not limited to, IFDS problems.
+Just as the IFDS algorithm, the IDE algorithm is suitable for data-flow analyses that can be encoded with inter-procedural, distributive flow functions.
+However, in IDE, the domain of the flow functions is not restricted to sets $D$ of data-flow facts.
+The IDE domain of a flow function consists of \textit{environments} that map data-flow facts from the set $D$ to lattice elements.
+
+As an example, in a constant propagation problem, an IDE environment would map each variable to the (possibly) constant value that it is bound to.
+To illustrate the distinction between IFDS and IDE we could say that IFDS can find out which variables in a program are constants, whereas IDE can additionally retrieve the values of the constant variables.
 
@@
 \begin{example}
-  The exploded supergraph for Listing~\ref{list:examplejava} is shown in Figure~\ref{fig:exampleexploded}.
+  The exploded supergraph for Listing~\ref{list:ccexample} is shown in Figure~\ref{fig:cc_edgefn_example}.
   We can see that there is a realizable path
-  from the start node of the exploded graph to the variable \verb'b' at~the~node~$\textsf{return}_\texttt{A.f}$ in the \verb'main' method. This means that at that node, \verb'b' is considered secret.
+  from the start node of the exploded graph to the variable \verb's' at~the~node~$\textsf{print(s)}$ in the \verb'B.bar' method. This means that at that node, \verb's' is considered secret.
 
+\commentout{  
     \begin{figure}%
@@
   \end{figure}
+}
 \end{example}
@@
 
+\commentout{
 \begin{mdelete}
@@
 \end{mdelete}
+}
 

### 2014-12-05 content/impl.tex
add comments on what to remove
restructuring

@@
 An overview of the transformations is shown in Figure~\ref{fig:transformations}.
-\begin{figure}
-  \centering
-    \tikzset{
-  ashadow/.style={opacity=.25, shadow xshift=0.07, shadow yshift=-0.07},
-}
-  \tikzstyle{problem}=[fill=greyblue,text width=2.3cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
-  \tikzstyle{result}=[fill=bisque,text width=1.8cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
-\begin{tikzpicture}
-    \node [problem] (ifds) {IFDS problem};
-    \node [problem] (equiv) [above right=0.9cm and .7\dist of ifds.east] {Equivalent IDE problem};
-    \node [problem] (ccide)[below=3cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
-    \node [result] (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
-    \node [result] (ccres) [below=3cm of equivres.west,anchor=west] {Correlated-calls result};
-    \node [result] (ifdsres) [right=\dist of equivres.east] {IFDS result};
-    \node [result] (improved) [right=\dist of ccres.east] {Improved IFDS result};
-    \path[->] (equivres) edge node[above]{$\backEq$} (ifdsres);
-    \path[->] (ccres) edge node[above] {$\backCC$} (improved);
-    \path[->] (ccres) edge[out=30,in=240] node[above] {$\backEq$} (ifdsres);
-    \path[->] (ifds) edge[out=40,in=190] node[above] {$\transEq$} (equiv);
-    \path[->] (ifds) edge[out=-60,in=165] node[above] {$\transCC$} (ccide);
-    \path[->] (equiv) edge node[above]{$\result$} (equivres);
-    \path[->] (ccide) edge node[above]{$\result$} (ccres);
-\end{tikzpicture}
-  \caption{Transformations between IFDS and IDE problems and their results}%
-  \label{fig:transformations}%
-\end{figure}
 
@@
 \begin{example}
-  Consider the program Listing~\ref{list:ccexample}. The exploded supergraph for that program is shown in Figure~\ref{fig:cc_edgefn_example}.
+  Consider the program Listing~\ref{list:ccexample}.
+The exploded supergraph for that program is shown in Figure~\ref{fig:cc_edgefn_example}.\mtodo{Move Figure~\ref{fig:cc_edgefn_example} up to where it's mentioned first?
+If yes, the caption won't make sense.}
+  \otodo{Can we combine the IDE Figure\ref{fig:cc_edgefn_example} with the IFDS Figure 4?
+It should be the same figure, just that Figure\ref{fig:cc_edgefn_example} has labels on the edges.
+We can initially tell the reader to ignore the labels until later.}
 

### 2014-12-05 content/intro.tex
restructuring

@@
 
-\subsection{Correlated Calls}
+\section{Motivating Example}
 
@@
 
-\subsection{IFDS and IDE}
-\otodo{This section should be moved to the Background section (and suitably merged with the text there).}
-The IFDS framework is a precise and efficient algorithm for data-flow analysis.
-IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
-The IFDS analysis is a version of the classic \textit{functional approach} to data-flow analysis proposed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.
-
-Given a data-flow problem that satisfies the restrictions of IFDS, the algorithm provides a \textit{context-sensitive} solution in polynomial time.
-In other data-flow algorithms not based on the functional approach, the result of the analysis at the entry of a procedure ``merges'' the incoming data obtained from all callers of the procedure.
-As a consequence, there is one global data-flow result computed at the end of the procedure.
-Context-sensitivity, however, allows an analysis to compute the data-flow result for a given procedure as a \textit{function} of the data-flow value at the start of the procedure.
-In other words, the analysis result for a procedure varies depending on where the procedure was called from.
-This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.
-
-Compared to IFDS, most data-flow analyses are either general but do not run in polynomial time~\cite{knoop1992interprocedural,pnueli1981two} or handle a very specific set of problems~\cite{knoop1993efficient}.
-
-The IFDS algorithm is applicable to problems which can be expressed with data-flow functions that satisfy certain restrictions.
-\textit{Inter-procedural} flow functions specify how data flows from the invocation of a procedure to its start, and from the procedure's end back to its call site.
-\textit{Distributive} flow functions are those that distribute over the confluence operator.
-In the context of IFDS, the confluence operator is called meet, and it can be either union or intersection.
-The data-flow facts on which the analysis operates must be a \textit{finite} set $D$.
-Each flow function operates on a \textit{subset} of $D$ (for example, the set of variables in the program) which makes the domain of the flow functions the power set of $D$.
-We describe the IFDS restrictions in detail in Section~\ref{sec:suitableifds}.
-
-The IDE framework is an expressive extension to IFDS that was created by the same authors in 1996.
-The problems that IDE can solve include, but are not limited to, IFDS problems.
-Just as the IFDS algorithm, the IDE algorithm is suitable for data-flow analyses that can be encoded with inter-procedural, distributive flow functions.
-However, in IDE, the domain of the flow functions is not restricted to sets $D$ of data-flow facts.
-The IDE domain of a flow function consists of \textit{environments} that map data-flow facts from the set $D$ to lattice elements.
-
-As an example, in a constant propagation problem, an IDE environment would map each variable to the (possibly) constant value that it is bound to.
-To illustrate the distinction between IFDS and IDE we could say that IFDS can find out which variables in a program are constants, whereas IDE can additionally retrieve the values of the constant variables.
-
-\subsection{Paper Outline}
-
 The goal of the correlated-calls analysis presented in this work is to modify the output of an IFDS analysis to account for correlated calls.
@@
   \item An implementation in Scala of the correlated-calls transformation and the IDE algorithm which is based on the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
-\end{itemize}
+\end{itemize}\mtodo{Reference the figure here.}
+
+\begin{figure}
+  \centering
+    \tikzset{
+  ashadow/.style={opacity=.25, shadow xshift=0.07, shadow yshift=-0.07},
+}
+  \tikzstyle{problem}=[fill=greyblue,text width=2.3cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
+  \tikzstyle{result}=[fill=bisque,text width=1.8cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
+\begin{tikzpicture}
+    \node [problem] (ifds) {IFDS problem};
+    \node [problem] (equiv) [above right=0.9cm and .7\dist of ifds.east] {Equivalent IDE problem};
+    \node [problem] (ccide)[below=3cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
+    \node [result] (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
+    \node [result] (ccres) [below=3cm of equivres.west,anchor=west] {Correlated-calls result};
+    \node [result] (ifdsres) [right=\dist of equivres.east] {IFDS result};
+    \node [result] (improved) [right=\dist of ccres.east] {Improved IFDS result};
+    \path[->] (equivres) edge node[above]{$\backEq$} (ifdsres);
+    \path[->] (ccres) edge node[above] {$\backCC$} (improved);
+    \path[->] (ccres) edge[out=30,in=240] node[above] {$\backEq$} (ifdsres);
+    \path[->] (ifds) edge[out=40,in=190] node[above] {$\transEq$} (equiv);
+    \path[->] (ifds) edge[out=-60,in=165] node[above] {$\transCC$} (ccide);
+    \path[->] (equiv) edge node[above]{$\result$} (equivres);
+    \path[->] (ccide) edge node[above]{$\result$} (ccres);
+\end{tikzpicture}
+  \caption{Transformations between IFDS and IDE problems and their results}%
+  \label{fig:transformations}%
+\end{figure}
 
   We prove that the solution to an IDE problem that considers correlated calls is more precise than the solution to the original IFDS problem.
-  We also show that the correlated-calls analysis is sound, i.e. that it never considers concrete execution paths as infeasible.
+  We also show that the correlated-calls analysis is sound, i.e.
+that it never considers concrete execution paths as infeasible.\mtodo{As discussed on the phone, we want to talk more about the results here.}
 
@@
 
-\mtodo{Reference appendix?}The remainder of this paper is organized as follows.
+The remainder of this paper is organized as follows.
 In the next section, we describe the IFDS and IDE analyses in detail.
@@
 Section~\ref{sec:ccdatastr} describes an efficient representation of the data structures that are required to define a correlated-calls IDE transformation.
-In Section~\ref{chapter:eval} we address some implementation aspects of the correlated-calls analysis and present an evaluation of its results. Section~\ref{chapter:concl} contains concluding remarks.
+In Section~\ref{chapter:eval} we address some implementation aspects of the correlated-calls analysis and present an evaluation of its results.
+Section~\ref{chapter:concl} contains concluding remarks.
+The proofs for the lemmas in the paper are provided in the Appendix.\mtodo{Reference appendix like this?}

### 2014-12-05 content/related.tex
restructuring

\section{Related Work}
\otodo{should we move Related Work to near the end of the paper?}
IFDS is a version of the functional approach to data-flow analysis developed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}. Their algorithm is based on computing \textit{summary functions} that return the data-flow value at the end of a procedure, given the data-flow value at the start of the procedure. IFDS problems form a more restricted set of data-flow problems: unlike in the functional approach, IFDS flow functions have to be distributive, and the set of data-flow facts $D$ has to be finite. However, the IFDS algorithm is more general than Sharir's and Pnueli's algorithm in that it can handle programs containing local variables and parameters in recursive methods.

IFDS has been used to encode a variety of data-flow problems. More complex examples of applications include typestate analysis (determining which operations can be performed on an object at a given program point)~\cite{naeem2008typestate} or shape analysis (detecting errors and validating properties of programs at compile time)~\cite{DBLP:conf/birthday/KreikerRRSWY13}.

IFDS is implemented for two popular static-analysis frameworks, the T.J. Watson Libraries for Analysis (WALA)~\cite{fink2012wala} and Soot~\cite{vallee1999soot}.

WALA is a framework for static analysis on Java bytecode developed by the IBM T.J.~Watson Research Center.
In the implementation of our work, we use WALA to build and traverse the supergraph (a special kind of control-flow graph) of a Java program\footnote{However, we do not use WALA's IFDS implementation, as explained in~Section~\ref{chapter:eval}.}.

Soot is a framework for program analysis and optimization on Java bytecode, developed by the Sable Research Group at McGill University. Unlike WALA, Soot also has an implementation of the IDE algorithm. The IFDS and IDE implementations for Soot are part of the Heros project~\cite{bodden2012inter}.

Whereas one advantage of Soot's IFDS implementation (and other static analysis tools) is ease of use and extensibility, WALA's primary focus is efficiency. For example, WALA uses bit-vectors to represent some of the analysis data types, like local variables and parameters. Another difference is that WALA's intermediate representation of a program uses static single assignment (SSA) form~\cite{cytron1991efficiently}. SSA form is a representation of the program in which each variable has only one definition (assignment). SSA can make dataflow analysis simpler and more efficient~\cite{appel1998ssa}.

Work on improving the IFDS algorithm includes Practical Extensions by~N.\,Naeem and O.\,Lhot\'ak~\cite{naeem2010pei}. Their paper presents four extensions to the IFDS algorithm. Two of the extensions improve the efficiency of the IFDS analysis for certain classes of IFDS problems. Another extension widens the class of problems applicable for the IFDS analysis. However, those extensions do not affect the precision of IFDS problems. Our analysis, in contrast, does not improve the efficiency or generality of IFDS, but it allows us to solve IFDS problems more precisely.

The fourth extension is targeted towards programs that are represented in SSA form. Executing the IFDS analysis on such programs results in loss of precision in the presence of control-flow constructs (e.g. conditionals and loops), compared to programs in non-SSA form.
The extension makes the IFDS analysis on programs in SSA form as precise as on programs that are not represented in SSA form. In contrast, the correlated-calls analysis is applicable to programs in both SSA and non-SSA forms. Even if applied to a program in SSA form, our analysis and the extension improve the precision of IFDS in unrelated situations: the first analysis handles correlated calls, and the latter handles control-flow constructs. Thus, an IFDS analysis could benefit from both precision improvements independently.

Another work on improving the efficiency of the IFDS algorithm is E.\,Bodden et~al.'s framework for the analysis of software products lines~\cite{bodden2013spl}. Their paper uses transformations from IFDS to IDE problems, a technique we also employ. Finally, J.\,Rodriguez and O.\,Lhot\'ak implemented a concurrent version of the IFDS algorithm using actors~\cite{rodriguez2010concurrent}. However, neither of those works is concerned with improving the precision of IFDS results.

The correlated-calls analysis improves the precision of a data-flow analysis by eliminating a special type of infeasible paths. This is similar to the idea of context-sensitive analysis: just as a context-sensitive analysis eliminates infeasible paths from the end of a procedure to the call sites that do not match the given procedure call, the correlated-calls analysis eliminates infeasible paths caused by correlated method calls.

The idea of using correlated calls to remove infeasible paths in data-flow analyses of object-oriented programs was introduced by F.\,Tip~\cite{DBLP:journals/scp/Tip15}. The possibility of using IDE to achieve this is mentioned, but not elaborated upon. Our work presents a concrete solution to the problem and an implementation of that solution.

The idea of eliminating infeasible paths caused by correlated calls is similar to M.~Sridharan et~al.'s work on improving the precision of pointer analysis for JavaScript programs~\cite{DBLP:conf/ecoop/SridharanDCST12}. For each pointer, a pointer analysis determines the possible set of objects (the \textit{points-to} set) that the pointer can reference at a given program point. In JavaScript, it is challenging to compute the points-to set of fields because in general, field names can be derived from arbitrary expressions and bound at runtime.
As a result, an imprecise data-flow analysis will include infeasible paths between values of the form \verb'o[p]' (access of a property \verb'p' of object \verb'o'), where at compile time, \verb'p' can be bound to different values.
The idea of the paper is to track all dynamic property accesses (reads and writes) on an object \verb'o' with property name \verb'p'. The code snippets containing the references \verb'o[p]' are then extracted into a separate function $f$. The analysis is then run so that for each possible value of \verb'p', $f$ is analyzed separately; therefore, for a given property name, all correlated objects with that name are analyzed together.

The differences between this method of tracking correlated calls and our analysis are the following.
\begin{itemize}
  \item \textit{Type of target data-flow analysis} whose precision is to be improved. Our analysis improves the precision of IFDS data-flow analyses, whereas the JavaScript analysis improves the precision of pointer analysis.
  \item \textit{Target language}. Our analysis is for object-oriented languages where polymorphic methods, and not property names (which are known at compile time), cause infeasible paths.
  \item \textit{Different handling of correlated calls}. Extracting code that contains correlated calls into separate methods would not prevent infeasible paths. Instead, our analysis uses IDE flow functions to detect and eliminate infeasible paths caused by correlated calls.
\end{itemize}

### 2014-12-08 content/impl.tex
shrinking/rewriting section 4 (IFDS to IDE transformation)

@@
-\section{Correlated Calls Analysis}\label{chapter:cca}
-The correlated-calls analysis is presented as a transformation from an arbitrary IFDS problem to a corresponding IDE problem.
-
-After solving the generated IDE problem, its result can be converted to an IFDS result.
-If the input program contains correlated calls, the converted IFDS result can be more precise than the original IFDS result.
-
-In this section, we first discuss what is necessary to define IFDS and IDE problems.
-Next we describe how to convert any IFDS problem into an equivalent IDE problem, and, given a solution to the generated IDE problem, how to obtain the result of the original IFDS problem.
-We then show how to transform an IFDS problem into an IDE problem using the correlated-calls transformation, and how to convert the solution to the latter IDE problem into a more precise IFDS result.
-
-\subsection{Defining IFDS and IDE Problems}
-In Section~\ref{sec:bg}, we defined what IFDS and IDE problems are, their applications, and their constraints. In this section, we describe how to create instances of IFDS and IDE problems.
-
-\subsubsection{Defining an IFDS Problem}\label{sec:ifdsdef}
-Recall that an IFDS problem instance is defined as a five-tuple
-\[
-    (G^*,\ D,\ F,\ M_F,\,\sqcap)\,,
-\]
-where $G^*=(N^*,\,E^*)$ is the control-flow supergraph of the program, $D$ is the set of dataflow facts, $F\subseteq2^D\to2^D$ is a set of distributive dataflow functions, and the function $$M_F:\,E^*\to(2^D\to2^D)$$ maps the supergraph edges to dataflow functions, and is extended to paths by composition.
-
-In practice, an IFDS problem can be defined by providing an exploded supergraph
-$G^\#=(N^\#,\,E^\#)$.
-Each node of $G^\#$ is a pair $(n,\ d)$, where $n\in N^*$ is a node in the control-flow supergraph and $d\in (D\cup\{\mathbf{0}\}),\ \mathbf0\notin D$, where $\mathbf0$ is an auxiliary fact that is necessary for the IFDS algorithm.
-
-The meaning of an edge in the exploded supergraph is the following.
-Let $(n_1,\,d_1)$ and $(n_2,\,d_2)$ be two nodes in the exploded supergraph $G^\#$.
-Furthermore, assume that if fact $d_1$ at node~$n_1$ holds, then the fact~$d_2$ at node~$n_2$ also holds.
-Then there is an edge $(n_1,\,d_1),\,(n_2,\,d_2)\in E^\#$.
-
-\subsubsection{Defining an IDE Problem}\label{sec:defide}
-An IDE problem instance is a four-tuple
-\[
-    (G^*,\ D,\ L,\ \menv),
-\]
-where $G^*$ and $D$ are defined in the same way as for IFDS.
-$L$ is a finite-height lattice that represents the values to which dataflow facts are mapped in an IDE problem.
-An environment $Env(D, L)$ maps dataflow facts to lattice elements.
-Finally, the map $$M_{\textsf{Env}}:\,E^*\to(\textsf{Env}(D, L)\to \textsf{Env}(D, L))$$ is a function from the control-flow-supergraph edges to environment transformers, extended to paths by composition.
-
-An IDE problem can be defined with a labeled exploded supergraph\footnote{
-    The exploded supergraph in an IDE problem is defined in the same way as in an IFDS problem.
-The only difference is that the $\mathbf0$ fact is denoted as $\Lambda$~\cite{reps1995precise,sagiv1996precise}.
-}, in which an edge function
-\begin{equation}
-  \edgefn:\ E^\#\to(L\to L)
-\end{equation}
-pairs edges with \textit{micro functions}, and is extended to paths by composition.
-
-The set of micro functions of an IDE problem is a subset of $L\to L$ that is closed under function meet and composition.
-
-The meaning of an edge in the labeled exploded supergraph is the following. Let $e=((n_1,\,d_1),\,(n_2,\,d_2))\in E^\#$ be an edge in the exploded supergraph with label $f=\mathsf{EdgeFn}(e)$. Then
-\begin{itemize}
-%	\item the fact that $d_1$ holds at node $n_1$ implies that $d_2$ holds at $n_2$;
-  \item if at node $n_1$ the fact $d_1$ was mapped to a lattice element $l_1$ by an environment $Env(D,\,L)$, then the fact $d_2$ at node $n_2$ should be mapped to $f(l_1)$.
-\end{itemize}
-
-As shown in~Sagiv et al.~\cite{sagiv1996precise}, the relationship between environment transformers and edge functions can be described with the following equations.
-For individual edges $(n_1,\,n_2)\in E^*$,
-\begin{align}\label{eq:envTransToEdgeFnEdge}
-  \menv&((n_1,\,n_2))(\textsf{env})(d)\notag\\
-  &=\edgefn((n_1,\,\Lambda),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,,
-\end{align}
-where $\textsf{env}$ is an environment $\textsf{Env}(D,\,L)$.
-Informally, for a given control-flow-supergraph edge $e$ and data-flow fact $d$, the $M_\textsf{Env}$ function captures the meet of the edge function applied to all possible exploded-graph edges along $e$.
-
-For paths $p$ that start with the entry point~$\startmain$,
-\begin{equation}\label{eq:envTransToEdgefn}
-  \menv(p)(\Omega)(d)=\bigsqcap_{r\in\mathsf{RP}(p,\,d)}\edgefn(r)(\top)\,,
-\end{equation}
-where $n\in N^*$, $d\in D$, $p\in\ivp(n)$, and $\mathsf{RP}$ is the set of all inter-procedurally realizable paths.
-
-To summarize, an IDE problem can be defined by a labeled exploded supergraph 
-\begin{equation}(G^\#,\,L,\,\mathsf{EdgeFn})\,,\end{equation}
-where each edge of the exploded supergraph corresponds to a micro function.
-
-\subsection{Transformations Between IFDS and IDE}\label{seq:transIfdsIde}
-
-The correlated-call analysis transforms an existing IFDS problem into a special kind of IDE problem. We described what is necessary to define IFDS and IDE problems independently.
-
-Let $P=(G^\#)$ be an IFDS problem and $Q=(G^\#,\,\edgefn)$ an IDE problem obtained by a conversion from $P$.
-
-We will look at two kinds of transformations
-\begin{equation}
-  \mathcal T:\ (G^\#)\to (G^\#,\,\edgefn)
-\end{equation}
-from IFDS to IDE problems:
-\begin{itemize}
-	\item an equivalence transformation $\transEq$ (pronounced as ``t-equiv''), in which we show how to transform IFDS problems into equivalent IDE problems;
-  \item a correlated-call transformation $\transCC$ (pronounced as ``t-c-c''), where we show how to convert IFDS problems into a special form of IDE problems that help eliminate infeasible paths.
-\end{itemize}
-In each case we also show how to convert the result of the generated IDE problem to a result of the original IFDS problem.
-
-An overview of the transformations is shown in Figure~\ref{fig:transformations}.
-
-\subsubsection{Equivalence Transformation}\label{sec:equivtrans}
-We start with an equivalence transformation $\transEq$ to present a simple IFDS-to-IDE conversion that does not change the result of the original IFDS problem.
-We will compare the correlated-calls transformation with the equivalence transformation, and use the latter to show  that the correlated-calls analysis results in a
-precision improvement of the original IFDS problem result.
-
-\paragraph{Converting IFDS problems to IDE problems}
-Since IDE is a generalization of IFDS, any IFDS problem can be converted into an equivalent IDE problem~\cite{sagiv1996precise}.
-For an equivalence transformation $\transEq$, the generated lattice $L^\equiv$ consists of two elements, bottom and top:
-\[
-    L^\equiv=\{\bot,\ \top\}\,,
-\]
-where $\bot$ means ``reachable'', and $\top$ means ``not reachable''.
-
- All micro functions are identity functions.
-
-Given an exploded supergraph $G^\#$ provided by an IFDS problem, we want to create an edge function $\edgefn^\equiv$ that maps $G^\#$'s edges $E^\#$ to micro functions $L^\equiv\to L^\equiv$.
-
-The edge functions $\edgefn^\equiv$ are defined as
-\begin{equation}
-    \edgefn^\equiv=
-    \begin{cases}
-      \lambda e\,.\,\lambda m\,.\,\bot&\text{if $d_1(e)=\Lambda$ and $d_2(e)\ne\Lambda$;}\\
-      \lambda e\,.\,\id&\text{otherwise,}
-    \end{cases}
-\end{equation}
-where $d_1(e)$ is the source fact of an edge $e$ and $d_2(e)$ is its target fact.
-At a ``diagonal'' edge from a $\Lambda$-fact to a non-$\Lambda$-fact $d$, the micro function is a constant function that returns $\bot$, which makes it a bottom element in the $L\to L$ lattice.
-Since the initial lattice element passed to the micro function at the start node is the top element (see~\eqref{eq:envTransToEdgefn}), the bottom function at the diagonal edge swaps the top element to bottom to make the fact $d$ reachable.
-
-The resulting equivalence transformation looks as follows:
-\begin{equation}
-  \transEq((G^\#))=(G^\#,\,L^\equiv,\,\mathsf{EdgeFn}^\equiv).
-\end{equation}
-
-Thus, in $\transEq$, all non-diagonal edges in the original IFDS problem are mapped to identity functions.
-
-\paragraph{Converting IDE Results to IFDS Results}
-
-The output of an IFDS analysis states whether a node is reachable in the exploded supergraph.
-This means that for an IFDS problem $P$, the IFDS-analysis result $\result_{\text{IFDS}}(P):\ N^*\to 2^D$ is a map from nodes of the control-flow supergraph to sets of facts:
-\begin{equation}
-  \result_{\text{IFDS}}(P)=\{(n,\,\mvp F(n))\,|\,n\in N^*\}\,.
-\end{equation}
-
-\begin{mdelete}
-\begin{example}\label{ex:ifdsresult}
-  The solution to the taint-analysis IFDS problem $\mathcal P$ in Listing~\ref{list:examplejava} whose exploded supergraph is presented in Figure~\ref{fig:exampleexploded} looks as follows:
-  \small\begin{align*}
-    \result_\text{IFDS}(\mathcal P)=\{&(\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\{\texttt a\}),
-      &(\highlight{\textsf{start}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
-      &\qquad\qquad(\highlight{\textsf{return}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
-%      
-      &(\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\{\texttt a\}),
-      &(\highlight{\texttt{if(s==null)}}{lightsalmonpink},\,\{\texttt s\}),
-      &\qquad\qquad(\highlight{\texttt{return r}}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
-%
-      &(\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\{\texttt a,\,\texttt b\}),
-      &(\highlight{\textsf{call}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
-      &\qquad\qquad(\highlight{\textsf{end}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\})\}.\\
-%
-      &(\highlight{\textsf{end}_\texttt{main}}{greyblue},\,\{\texttt a,\,\texttt b\}),&(\highlight{\texttt{return s}}{lightsalmonpink},\,\{\texttt s\}),
-  \end{align*}\normalsize
-  All other nodes of the control-flow supergraph are mapped to the empty set.
-\end{example}
-\end{mdelete}
-
- The IDE analysis associates a lattice element with each node in the exploded supergraph.
-For an IDE problem $Q$, the result $\result(Q):\ N^\#\to L$ maps nodes of the exploded supergraph to lattice elements (see~\eqref{eq:mvpdef}):
-\begin{equation}\label{eq:ideresult}
-  \result(Q)=\{((n,\,d),\,\mvp{\textsf{Env}}(n,\,d))\ |\ n\in N^*,\,d\in D\}\,.
-\end{equation}
-In other words, for each fact $d\in D$ at a given node $n\in N^*$, $\result(Q)(n,\,d)$ returns a lattice element. If a fact $d\in D$ is unreachable, $\result(Q)(n,\,d)=\top$.
-
-In the case of an equivalence transformation from IFDS to IDE, if a node in the IFDS result is reachable, it will be also reachable in the IDE result, and it will be mapped to the bottom lattice element.
-For an exploded node in the IDE result, being mapped to the top element means being not reachable.
-
-The~domain of an equivalence-IDE result 
-\begin{equation}
-  \resultEq=\result(\transEq(P))
-\end{equation}
-consists of pairs of control-flow-supergraph nodes and data-flow facts.
-The range of the result is the set of lattice elements.
-To transform an IDE result to an IFDS result, we need to map each control-flow-supergraph node to the set of facts with which it is paired, provided that the pair is mapped to the bottom lattice element.
-
-\begin{mdelete}
-\begin{example}\label{ex:ideresult}
-  Converting the IFDS problem $\mathcal P$ from Example~\ref{ex:ifdsresult} into an equivalent IDE problem and solving it will yield the following result:
-    \small\begin{align*}
-    \result(\transEq(\mathcal P))=\{&((\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\texttt a),\,\bot),\\
-      &((\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
-      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
-      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt b),\,\bot),\\
-      &\dots\}.\\
-    \end{align*}\normalsize
-  Suppose that for a pair $(n,\,d)$, where $n\in N^*$ and $d\in D$, there is no corresponding result in ~$\result_\text{IFDS}(\mathcal P)$ (see Example~\ref{ex:ifdsresult}).
-Then $(n,\,d)$ appears in $\result(\transEq(\mathcal P))$ as $((n,\,d),\,\top)$.
-\end{example}
-\end{mdelete}
-
-Let $\rho$ be the result of an equivalence-IDE analysis for an IFDS problem $P$:
-\[
-  \rho=\result(\transEq(P)).
-\]
-For a node $n\in N^*$, let $D_n^\equiv(\rho)$ be a set of data-flow facts such that
-\begin{equation}
-  D_n^\equiv(\rho)=\{d\ |\ d\in D\,\wedge\,\rho(n,\,d)\ne\top\}\,.
-\end{equation}
-Then the transformation function
-$\backEq:\,(N^\#\to L)\to(N^*\to2^D)$
-from an IDE result to~an~IFDS result looks as follows:
-\begin{equation}
-  \backEq\left(\rho\right)=
-    \left\{(n,\,D_n^\equiv(\rho))\ |\ n\in N^*\right\}\,.
-\end{equation}
-
-Obviously, if applied to the result of an equivalence-IDE problem, $\backEq$ returns a result equivalent to the original IFDS problem result.
-In other words, for any IFDS problem $P$ with supergraph $N^*$, and any node $n\in N^*$,
-\begin{equation}
-  \backEq\left(\result(\transEq(P))\right)(n)=\result_{\text{IFDS}}(P)(n)\,.
-\end{equation}
-
-\begin{example}
-  Converting the result in Example~\ref{ex:ideresult} with the equivalence-transformation from an IDE result to an IFDS result $\backEq$ will yield the same result as in Example~\ref{ex:ifdsresult}.
-\end{example}
-\subsubsection{Correlated-Call Transformation}\label{sec:cctrans}
-
-To improve the precision of an IFDS problem, we can convert it to a special type of IDE problem, and use lattice elements to provide us with additional information about a node.
-When converting the IDE result to an IFDS result, lattice elements will tell us whether to make the corresponding exploded nodes reachable. This is the idea of the correlated-calls analysis.
-
-\paragraph{Lattice Elements}
-Just like in the equivalence transformation $\transEq$, the exploded supergraph for $\transCC$ is the same as in the original IFDS problem.
-The elements of the correlated-calls lattice $\lcc$ are functions that map receivers to sets of types:
-\[
-    \lcc=\left\{\,m:\ R\to2^T\right\},
-\]
-where $R$ is the set of receivers and $T$ is the set of all types in the program. 
-The type power set $2^T$ is also a lattice with a bottom element 
-\begin{align*}
-\bot_T&=T
-\intertext{and top element}
-\top_T&=\varnothing.
-\intertext{The top element of the function lattice}
-\topcc&=\lambda r.\top_T
-\intertext{is a function that maps any receiver to the empty set\footnote{%
-  We prove that $\lcc$ is a lattice in the Proof of Lemma~\ref{lem:efficient}%
-}. 
-The bottom element}
-\botcc&=\lambda r.\bot_T
-\end{align*}
-maps any receiver to all types in the program.
-
-To understand the meaning of lattice elements in a correlated-call analysis, suppose that an IFDS problem has been converted to an IDE problem using the correlated-calls transformation. 
-Assume also that $s$ is the entrypoint of the program, $n$ is a node in the exploded supergraph, and that in the IDE result, $n$ is mapped to a lattice element $l\in \lcc$. 
-Then the purpose of $l$ is to provide information about the set of types of the objects that may be referenced by each receiver at runtime at a path from $s$ to $n$. 
-If a receiver is mapped to the empty set $\top_T$, it means that for the given program point, the receiver cannot reference an object of any type.
-In other words, the corresponding data-flow fact is considered not reachable.
-
-\paragraph{Micro Functions}\label{sec:micro}
-Unlike in the equivalence transformation, the micro functions returned by the edge function $\edgefn^\Subset$ are not always identity functions.
-
-Let $e=(n_1,\,n_2)\in E^\#$ be an edge in the exploded supergraph.
-$\edgefn^\Subset(e)$ returns a micro function $f\subset\lcc\to \lcc$.
-Given a micro function (a map from receivers to sets of types) $m\in \lcc$, $f(m)$ returns a new map from receivers to sets of types.
-In other words, $f$ shows how to update the map from receivers to sets of types when we encounter program point $n_1$.
-
-Let $f_1$ and $f_2$ be two micro functions such that ${f_1=\lambda m\,.\,\lambda r\,.\,t_1(r)}$ and ${f_2={\lambda m\,.\,\lambda r\,.\,t_2(r)}}$.
-We define the meet operation on micro-functions as follows:
-\begin{equation}\label{eq:micromeet}
-  \lambda m\,.\,\lambda r\,.\,t_1(r)\sqcap\lambda m\,.\,\lambda r\,.\,t_2(r)
-  =\lambda m\,.\,\lambda r\,.\,t_1(r)\cup t_2(r)\,.
-\end{equation}
-
-The composition of micro functions is defined as ordinary function composition.
-
-\paragraph{Edge Functions}\label{sec:ef}
-
-Let $\mathcal F$ be the set of methods in a program with a signature $s_\mathcal F$.
-\begin{definition}
-  Let $r.c()$ be a call site on a receiver $r\in R$ with runtime type $t\in T$.
-  Let~$s_\mathcal F$ be the method signature corresponding to the call $c()$.
-  For $s_\mathcal F$ and $t$, a \textit{lookup function} returns the method implementation $f\in\mathcal F$ to which the call $r.c()$ is dispatched:
-  \begin{equation}
-    \textsf{lookup}(s_\mathcal F,\,t)=f.
-  \end{equation}
-\end{definition}
-
-\begin{definition}
-  For a method signature $s_\mathcal F$ and a method implementation $f\in\mathcal F$, the static-type function $\tau$ returns the set of types for which the lookup function yields $f$:
-  \begin{equation}
-    \tau(s_\mathcal F,\,f)=\{\,t\ |\ \textsf{lookup}(s_\mathcal F,\,t)=f\}\,.
-  \end{equation}
-\end{definition}
-In other words, $\tau$ computes the set of types for which calls to methods
-with signatures~$s_\mathcal F$ are dispatched to~$f$.
-
-If there is a supergraph path from a method call with signature $s_\mathcal F$ to the start of $f$, then the set $\tau(s_\mathcal F,\,f)$ is always non-empty.
-
-\begin{definition}\label{def:momopoly}
-  A call site is called monomorphic if it can be dispatched to only one method. If a call site can be dispatched to more than one method it is called polymorphic.
-\end{definition}
-
-  Let $r.c()$ be a call on a receiver $r\in R$ with a method signature $s_\mathcal F$ to a function $f\in\mathcal F$.
-  If the call site is monomorphic, then $\tau(s_\mathcal F,\,f)$ contains all types $T'\subseteq T$ that are compatible with the static type of $r$.
-  If the call site is polymorphic, then $\tau(s_\mathcal F,\,f)\subset T'$, since some types $t\in T'$ cause dispatch to a method other than $f$.
-
-\begin{definition}\label{def:edgefn}
-  For an edge $e$, let $n_1(e)$ and $n_2(e)$ be the source and target nodes of $e$, and $d_1(e)$ and $d_2(e)$ be its source and target facts.
-A correlated-call edge function for the set $S\subseteq R$ is defined as follows:
-  \begin{equation}\label{eq:edgefndef}
-    \ccedgefn S=\lambda e\,.\,
-        \begin{cases}
-          \id  &\text{if $d_1(e)=d_2(e)=\Lambda$},\\
-          \lambda m\,.\,\varepsilon_S(e)(\botcc) &\text{if $d_1(e)=\Lambda$ and $d_2(e)\ne\Lambda$},\\
-          \lambda m\,.\,\varepsilon_S(e)(m)  &\text{otherwise,}
-        \end{cases}
-  \end{equation}
-  where $\varepsilon_S:\,E\to(L\to L)$ is a function defined as
-  \begin{equation}\label{eq:varepsilon}
-    \varepsilon_S=\lambda e\,.\,
-        \begin{cases}
-            \lambda m\,.\,m[r\to m(r)\cap \tau(s_\mathcal F,\,f)],
-                &\text{if $e$ is a call-start edge. $r.c()$ is}\\
-                &\text{the call site at $n_1(e)$, $f$ is the called}\\
-                &\text{procedure with signature $s_\mathcal F$,}\\
-                &\text{and $r\in S$;}\\
-            \lambda m\,.\,m[r\to m(r)\cap \tau(s_\mathcal F,\,f)]
-                &\text{if $e$ is an end-return edge.}\\
-            \textcolor{white}{\lambda m\,.\,m}[v_1\to\bot_T]
-                &\text{$v_1,\,\dots,\,v_k\in S$ are the local variables}\\
-            \textcolor{white}{\lambda m\,.\,m}\dots
-                &\text{in the callee method, $r.c()$ is the call}\\
-            \textcolor{white}{\lambda m\,.\,m}[v_k\to\bot_T],
-                &\text{corresponding to the return node}\\
-                &\text{at $n_2(e)$, $f$ is the called method with}\\
-                &\text{signature $s_\mathcal F$, and $r\in S$;}\\
-            \lambda m\,.\,m\left[r\to \bot_T\right],
-                &\text{if $n_1(e)$ contains an assignment}\\
-                &\text{for $r\in S$;}\\
-            \id
-                &\text{otherwise.}
-        \end{cases}
-  \end{equation}
-  We define both $\ccedgefn S$ and $\varepsilon_S$ to be extended to paths by composition.
-\end{definition}
-In the above definition, the purpose of the set $S$ is to limit the set of considered receivers. We will use $S$ in Section~\ref{sec:ccreceivers}.
-
-The micro functions returned by a correlated-calls edge function can be described as follows.
-Along $\Lambda$-edges, the micro functions are identity functions.
-All other functions can be described with $\varepsilon_S$.
-On ``diagonal'' edges from $\Lambda$ facts to non-$\Lambda$ facts, $\varepsilon_S$ creates edge-specific mappings for a set of receivers, and maps all the other receivers to the set of all types $\bot_T$.
-On all other edges, $\varepsilon_S$ modifies the mappings for a set of receivers and leaves the mappings for the other receivers unchanged.
-
-\begin{example}
-  Consider the program Listing~\ref{list:ccexample}.
-The exploded supergraph for that program is shown in Figure~\ref{fig:cc_edgefn_example}.\mtodo{Move Figure~\ref{fig:cc_edgefn_example} up to where it's mentioned first?
-If yes, the caption won't make sense.}
-  \otodo{Can we combine the IDE Figure\ref{fig:cc_edgefn_example} with the IFDS Figure 4?
-It should be the same figure, just that Figure\ref{fig:cc_edgefn_example} has labels on the edges.
-We can initially tell the reader to ignore the labels until later.}
-
-  Returning a secret value in method \verb'A.foo' creates a ``diagonal'' edge from the $\Lambda$-fact to the secret fact $\psi$. 
-  The diagonal edge is labeled with the micro function $\lambda m\,.\,\botcc$. Thus, at the end node of the method, every receiver is mapped to the set of all types~$\bot_T$.
-
-On the end-return edge from \verb'A.foo' to \verb'main', we need to restrict the set of types for the receiver \verb'a' by labeling the end-return edge from the fact $\psi$ to the fact \verb'v' with the micro function $\lambda m\,.\,m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$.
-
-Similarly, on the call-start edge from method \verb'main' to method \verb'B.bar', from fact \verb'v' to \verb's', we restrict the type of the receiver \verb'a' to the set \{\texttt B\} with the micro function~$\lambda m\,.\,m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$.
-
-After we have shown the definitions for the meet and composition operations, we will show in Example~\ref{ex:cc} how the correlated-calls analysis uses the presented micro functions to detect infeasible paths.
-
 \begin{figure}%
@@
   \end{figure}
+\otodo{we agreed to move this figure to the initial example section}
+  \mtodo{Move Figure~\ref{fig:cc_edgefn_example} up to where it's mentioned first? If yes, the caption won't make sense.}
+  \otodo{Can we combine the IDE Figure\ref{fig:cc_edgefn_example} with the IFDS Figure 4?
+It should be the same figure, just that Figure\ref{fig:cc_edgefn_example} has labels on the edges.
+We can initially tell the reader to ignore the labels until later.}
+
+\otodo{The following definitions are very general, and not related to the transformation.
+    Can we move them somewhere earlier?}
+\paragraph{Edge Functions}\label{sec:ef}
+
+Let $\mathcal F$ be the set of methods in a program with a signature $s_\mathcal F$.
+\begin{definition}
+  Let $r.c()$ be a call site on a receiver $r\in R$ with runtime type $t\in T$.
+  Let~$s_\mathcal F$ be the method signature corresponding to the call $c()$.
+  For $s_\mathcal F$ and $t$, a \textit{lookup function} returns the method implementation $f\in\mathcal F$ to which the call $r.c()$ is dispatched:
+  \begin{equation}
+    \textsf{lookup}(s_\mathcal F,\,t)=f.
+  \end{equation}
+\end{definition}
+
+\begin{definition}
+  For a method signature $s_\mathcal F$ and a method implementation $f\in\mathcal F$, the static-type function $\tau$ returns the set of types for which the lookup function yields $f$:
+  \begin{equation}
+    \tau(s_\mathcal F,\,f)=\{\,t\ |\ \textsf{lookup}(s_\mathcal F,\,t)=f\}\,.
+  \end{equation}
+\end{definition}
+In other words, $\tau$ computes the set of types for which calls to methods
+with signatures~$s_\mathcal F$ are dispatched to~$f$.
+
+If there is a supergraph path from a method call with signature $s_\mathcal F$ to the start of $f$, then the set $\tau(s_\mathcal F,\,f)$ is always non-empty.
+
+\begin{definition}\label{def:momopoly}
+  A call site is called monomorphic if it can be dispatched to only one method. If a call site can be dispatched to more than one method it is called polymorphic.
+\end{definition}
+
+  Let $r.c()$ be a call on a receiver $r\in R$ with a method signature $s_\mathcal F$ to a function $f\in\mathcal F$.
+  If the call site is monomorphic, then $\tau(s_\mathcal F,\,f)$ contains all types $T'\subseteq T$ that are compatible with the static type of $r$.
+  If the call site is polymorphic, then $\tau(s_\mathcal F,\,f)\subset T'$, since some types $t\in T'$ cause dispatch to a method other than $f$.
+
+\otodo{incorporate into previous section}
+\subsection{Defining IFDS and IDE Problems}
+In Section~\ref{sec:bg}, we defined what IFDS and IDE problems are, their applications, and their constraints. In this section, we describe how to create instances of IFDS and IDE problems.
+
+\subsubsection{Defining an IFDS Problem}\label{sec:ifdsdef}
+Recall that an IFDS problem instance is defined as a five-tuple
+\[
+    (G^*,\ D,\ F,\ M_F,\,\sqcap)\,,
+\]
+where $G^*=(N^*,\,E^*)$ is the control-flow supergraph of the program, $D$ is the set of dataflow facts, $F\subseteq2^D\to2^D$ is a set of distributive dataflow functions, and the function $$M_F:\,E^*\to(2^D\to2^D)$$ maps the supergraph edges to dataflow functions, and is extended to paths by composition.
+
+In practice, an IFDS problem can be defined by providing an exploded supergraph
+$G^\#=(N^\#,\,E^\#)$.
+Each node of $G^\#$ is a pair $(n,\ d)$, where $n\in N^*$ is a node in the control-flow supergraph and $d\in (D\cup\{\mathbf{0}\}),\ \mathbf0\notin D$, where $\mathbf0$ is an auxiliary fact that is necessary for the IFDS algorithm.
+
+The meaning of an edge in the exploded supergraph is the following.
+Let $(n_1,\,d_1)$ and $(n_2,\,d_2)$ be two nodes in the exploded supergraph $G^\#$.
+Furthermore, assume that if fact $d_1$ at node~$n_1$ holds, then the fact~$d_2$ at node~$n_2$ also holds.
+Then there is an edge $(n_1,\,d_1),\,(n_2,\,d_2)\in E^\#$.
+
+\subsubsection{Defining an IDE Problem}\label{sec:defide}
+An IDE problem instance is a four-tuple
+\[
+    (G^*,\ D,\ L,\ \menv),
+\]
+where $G^*$ and $D$ are defined in the same way as for IFDS.
+$L$ is a finite-height lattice that represents the values to which dataflow facts are mapped in an IDE problem.
+An environment $Env(D, L)$ maps dataflow facts to lattice elements.
+Finally, the map $$M_{\textsf{Env}}:\,E^*\to(\textsf{Env}(D, L)\to \textsf{Env}(D, L))$$ is a function from the control-flow-supergraph edges to environment transformers, extended to paths by composition.
+
+An IDE problem can be defined with a labeled exploded supergraph\footnote{
+    The exploded supergraph in an IDE problem is defined in the same way as in an IFDS problem.
+The only difference is that the $\mathbf0$ fact is denoted as $\Lambda$~\cite{reps1995precise,sagiv1996precise}.
+}, in which an edge function
+\begin{equation}
+  \edgefn:\ E^\#\to(L\to L)
+\end{equation}
+pairs edges with \textit{micro functions}, and is extended to paths by composition.
+
+The set of micro functions of an IDE problem is a subset of $L\to L$ that is closed under function meet and composition.
+
+The meaning of an edge in the labeled exploded supergraph is the following. Let $e=((n_1,\,d_1),\,(n_2,\,d_2))\in E^\#$ be an edge in the exploded supergraph with label $f=\mathsf{EdgeFn}(e)$. Then
+\begin{itemize}
+%	\item the fact that $d_1$ holds at node $n_1$ implies that $d_2$ holds at $n_2$;
+  \item if at node $n_1$ the fact $d_1$ was mapped to a lattice element $l_1$ by an environment $Env(D,\,L)$, then the fact $d_2$ at node $n_2$ should be mapped to $f(l_1)$.
+\end{itemize}
+
+As shown in~Sagiv et al.~\cite{sagiv1996precise}, the relationship between environment transformers and edge functions can be described with the following equations.
+For individual edges $(n_1,\,n_2)\in E^*$,
+\begin{align}\label{eq:envTransToEdgeFnEdge}
+  \menv&((n_1,\,n_2))(\textsf{env})(d)\notag\\
+  &=\edgefn((n_1,\,\Lambda),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,,
+\end{align}
+where $\textsf{env}$ is an environment $\textsf{Env}(D,\,L)$.
+Informally, for a given control-flow-supergraph edge $e$ and data-flow fact $d$, the $M_\textsf{Env}$ function captures the meet of the edge function applied to all possible exploded-graph edges along $e$.
+
+For paths $p$ that start with the entry point~$\startmain$,
+\begin{equation}\label{eq:envTransToEdgefn}
+  \menv(p)(\Omega)(d)=\bigsqcap_{r\in\mathsf{RP}(p,\,d)}\edgefn(r)(\top)\,,
+\end{equation}
+where $n\in N^*$, $d\in D$, $p\in\ivp(n)$, and $\mathsf{RP}$ is the set of all inter-procedurally realizable paths.
+
+To summarize, an IDE problem can be defined by a labeled exploded supergraph 
+\begin{equation}(G^\#,\,L,\,\mathsf{EdgeFn})\,,\end{equation}
+where each edge of the exploded supergraph corresponds to a micro function.
+
+\section{Correlated Calls Analysis}\label{chapter:cca}
+The correlated-calls analysis is defined as a transformation from an arbitrary IFDS problem to a corresponding IDE problem.
+The solution of the IDE problem is converted to a solution of the original IFDS problem.
+The converted IFDS result can be more precise than the original IFDS result because it avoids infeasible paths corresponding to correlated calls.
+
+%In this section, we first discuss what is necessary to define IFDS and IDE problems.
+Next we describe how to convert any IFDS problem into an equivalent IDE problem, and, given a solution to the generated IDE problem, how to obtain the result of the original IFDS problem.
+We then show how to transform an IFDS problem into an IDE problem using the correlated-calls transformation, and how to convert the solution to the latter IDE problem into a more precise IFDS result.
+
+\subsection{Transformations from IFDS to IDE}\label{seq:transIfdsIde}
+
+%The correlated-call analysis transforms an existing IFDS problem into a special kind of IDE problem. We described what is necessary to define IFDS and IDE problems independently.
+
+%Let $P=(G^\#)$ be an IFDS problem and $Q=(G^\#,\,\edgefn)$ an IDE problem obtained by a conversion from $P$.
+\otodo{Here, you defined the output of a transformation as just G\# and an edge function. Later, you also include the lattice. Should we include the lattice here?}
+Let $G^\#$ be the exploded supergraph of an IFDS problem. A \emph{transformation}
+$\mathcal T:\ (G^\#)\to (G^\#,\,\edgefn)$
+converts it into an equivalent IDE problem. We consider two transformations:
+\begin{itemize}
+	\item an equivalence transformation $\transEq$ (pronounced ``t-equiv'') that generates IDE problems with the same precision as the original IFDS problem, and
+  \item a correlated-call transformation $\transCC$ (pronounced ``t-c-c'') that generates IDE problems that exclude infeasible paths.
+\end{itemize}
+Both transformations keep the exploded supergraph $G^\#$ the same, and only generate different edge functions.
+%In each case we also show how to convert the result of the generated IDE problem to a result of the original IFDS problem.
+
+%An overview of the transformations is shown in Figure~\ref{fig:transformations}.
+
+\subsubsection{Equivalence Transformation}\label{sec:equivtrans}
+%We start with an equivalence transformation $\transEq$ to present a simple IFDS-to-IDE conversion that does not change the result of the original IFDS problem.
+We will compare the correlated-calls transformation with the equivalence transformation, and use the latter to show  that the correlated-calls analysis results in a
+%precision improvement of the original IFDS problem result.
+
+%\paragraph{Converting IFDS problems to IDE problems}
+%Since IDE is a generalization of IFDS, any IFDS problem can be converted into an equivalent IDE problem~\cite{sagiv1996precise}.
+The lattice
+for the equivalence transformation $\transEq$ 
+is the two-point lattice
+    $L^\equiv=\{\bot,\ \top\}$,
+where $\bot$ means ``reachable'', and $\top$ means ``not reachable''. 
+The edge functions $\edgefn^\equiv$ are defined as
+\begin{equation}
+    \edgefn^\equiv=
+    \begin{cases}
+      \lambda e\,.\,\lambda m\,.\,\bot&\text{if $d_1(e)=\Lambda$ and $d_2(e)\ne\Lambda$;}\\
+      \lambda e\,.\,\id&\text{otherwise,}
+    \end{cases}
+\end{equation}
+where $d_1(e)$ is the source fact of an edge $e$ and $d_2(e)$ is its target fact. 
+At a ``diagonal'' edge from a $\Lambda$-fact to a non-$\Lambda$-fact
+$d$, the micro function returns $\bot$
+to make
+the fact $d$ reachable. All other micro-functions are the identity.
+The equivalence transformation is thus defined as:
+  $\transEq((G^\#))=(G^\#,\,L^\equiv,\,\mathsf{EdgeFn}^\equiv)$.
+
+%Thus, in $\transEq$, all non-diagonal edges in the original IFDS problem are mapped to identity functions.
+
+\subsubsection{Correlated-Calls Transformation}\label{sec:cctrans}
+
+%To improve the precision of an IFDS problem, we can convert it to a special type of IDE problem, and use lattice elements to provide us with additional information about a node.
+%When converting the IDE result to an IFDS result, lattice elements will tell us whether to make the corresponding exploded nodes reachable. This is the idea of the correlated-calls analysis.
+
+%\paragraph{Lattice Elements}
+In the correlated-calls transformation, the 
+%Just like in the equivalence transformation $\transEq$, the exploded supergraph for $\transCC$ is the same as in the original IFDS problem. The 
+lattice elements are maps from receivers to sets of types:
+    $\lcc=\left\{\,m:\ R\to2^T\right\}$,
+where $R$ is the set of receivers and $T$ is the set of all types.
+For each receiver $r$, the map gives an overapproximation of the possible
+runtime types of $r$.
+Sets of types are ordered by the superset relation, and this is lifted to maps from receivers
+to sets of types, so the bottom element $\botcc$ maps every receiver to the set of all types,
+and the top element $\topcc$ maps every receiver to the empty set of types.
+During an actual execution, every receiver $r$ points to an object of some
+runtime type. \otodo{What if $r$ points to null?} Therefore, a data flow fact
+is unreachable along any feasible path if its corresponding lattice element
+maps any receiver to the empty set of types.
+
+\commentout{
+The type power set $2^T$ is also a lattice with a bottom element 
+\begin{align*}
+\bot_T&=T
+\intertext{and top element}
+\top_T&=\varnothing.
+\intertext{The top element of the function lattice}
+\topcc&=\lambda r.\top_T
+\intertext{is a function that maps any receiver to the empty set\footnote{%
+  We prove that $\lcc$ is a lattice in the Proof of Lemma~\ref{lem:efficient}%
+}. 
+The bottom element}
+\botcc&=\lambda r.\bot_T
+\end{align*}
+maps any receiver to all types in the program.
+
+To understand the meaning of lattice elements in a correlated-call analysis, suppose that an IFDS problem has been converted to an IDE problem using the correlated-calls transformation. 
+Assume also that $s$ is the entrypoint of the program, $n$ is a node in the exploded supergraph, and that in the IDE result, $n$ is mapped to a lattice element $l\in \lcc$. 
+Then the purpose of $l$ is to provide information about the set of types of the objects that may be referenced by each receiver at runtime at a path from $s$ to $n$. 
+If a receiver is mapped to the empty set $\top_T$, it means that for the given program point, the receiver cannot reference an object of any type.
+In other words, the corresponding data-flow fact is considered not reachable.
+}
+
+%\paragraph{Micro Functions}\label{sec:micro}
+%Unlike in the equivalence transformation, the micro functions returned by the edge function $\edgefn^\Subset$ are not always identity functions.
+
+A micro-function $f\in\lcc\to \lcc$ defines how the map from receivers to types should
+be updated when an instruction is executed.
+The micro-function for most kinds of instructions is the identity.
+On a call to and return from a specific method $m$ called on receiver $r$,
+the micro-function restricts the receiver-to-type map to map $r$ only to
+types consistent with the polymorphic dispatch to method $m$.
+Finally, when an instruction assigns an object of unknown type to a receiver
+$r$, the corresponding micro-function updates the map to map $r$ to the
+set of all types. This is made precise by the following definition:
+\begin{definition}\label{def:microfn}
+Given a previously fixed set $S \subseteq R$ of receivers, the micro-function $\varepsilon_S(e)$
+of a supergraph edge $e$ is defined as:
+                    \otodo{define $n_1(e)$ globally somewhere early on, and consider using a more decriptive name like src instead of $n_1$}
+  \begin{align}\label{eq:varepsilon}
+      &\varepsilon_S(e)= \lambda m\,.\,\\
+        &\begin{cases}
+            m[r\to m(r)\cap \tau(s_\mathcal F,\,f)],
+            &\text{\parbox{75mm}{
+                if $e$ is a call-start edge, $r.c()$ is
+                the call site at $n_1(e)$, $f$ is the called
+                procedure with signature $s_\mathcal F$,
+                and $r\in S$;}}\\[3ex]
+        \parbox{30mm}{\[\begin{array}{l}
+                m[r\to m(r)\cap \tau(s_\mathcal F,\,f)]\\
+            [v_1\to\bot_T] \ldots [v_k\to\bot_T],
+        \end{array}
+        \]
+        }
+        &
+        \text{\parbox{75mm}{
+                if $e$ is an end-return edge,
+                $r.c()$ is the call
+                corresponding to the return node
+                at $n_2(e)$,
+                $f$ is the called method with
+                signature $s_\mathcal F$,
+                $v_1,\,\dots,\,v_k\in S$ are the local variables
+                in $f$,
+                and $r\in S$;}}\\
+            m\left[r\to \bot_T\right],
+            &\text{\parbox{75mm}{if $n_1(e)$ contains an assignment
+                    for $r\in S$;}}\\
+            m
+                &\text{otherwise.}
+        \end{cases}
+  \end{align}
+\end{definition}
+
+In the above definition, the purpose of the set $S$ is to limit the set of considered receivers. We will use $S$ in Section~\ref{sec:ccreceivers}.
+
+%Let $e=(n_1,\,n_2)\in E^\#$ be an edge in the exploded supergraph.
+%$\edgefn^\Subset(e)$ returns a micro function $f\subset\lcc\to \lcc$.
+%Given a micro function (a map from receivers to sets of types) $m\in \lcc$, $f(m)$ returns a new map from receivers to sets of types.
+%In other words, $f$ shows how to update the map from receivers to sets of types when we encounter program point $n_1$.
+
+%Let $f_1$ and $f_2$ be two micro functions such that ${f_1=\lambda m\,.\,\lambda r\,.\,t_1(r)}$ and ${f_2={\lambda m\,.\,\lambda r\,.\,t_2(r)}}$.
+We define the meet operation on micro-functions as follows:
+%\begin{equation}\label{eq:micromeet}
+  %\lambda m\,.\,\lambda r\,.\,t_1(r)\sqcap\lambda m\,.\,\lambda r\,.\,t_2(r)
+  %=\lambda m\,.\,\lambda r\,.\,t_1(r)\cup t_2(r)\,.
+%\end{equation}
+%
+%The composition of micro functions is defined as ordinary function composition.
+
+We can now define $\edgefn$, which assigns a micro-function to each edge in
+the exploded supergraph. 
+Along a $\Lambda$-edge, the micro function is the identity. 
+All other functions can be described with $\varepsilon_S$.
+On a ``diagonal'' edge from $\Lambda$ to a non-$\Lambda$ fact that corresponds
+to some data flow fact becoming reachable, $\varepsilon_S(e)$ is applied to the initial
+map $\botcc$ that conservatively allows every receiver to point to an object of any type.
+On all other edges, $\varepsilon_S(e)$ is applied to the existing map before the edge.
+The is formalized in the following definition.
+\begin{definition}\label{def:edgefn}
+For each edge $e = (n_1,d_1) \to (n_2,d_2)$, $\ccedgefn S(e)$ is defined as follows:
+  \begin{equation}\label{eq:edgefndef}
+      \ccedgefn S(e)=
+        \begin{cases}
+          \id  &\text{if $d_1=d_2=\Lambda$},\\
+          \lambda m\,.\,\varepsilon_S(e)(\botcc) &\text{if $d_1=\Lambda$ and $d_2\ne\Lambda$},\\
+          \lambda m\,.\,\varepsilon_S(e)(m)  &\text{otherwise.}
+        \end{cases}
+  \end{equation}
+  %We define both $\ccedgefn S$ and $\varepsilon_S$ to be extended to paths by composition.
+\end{definition}
+
+\begin{example}
+  Consider the program from Listing~\ref{list:ccexample}, whose exploded supergraph appeared in Figure~\ref{fig:cc_edgefn_example}.
+
+  Returning a secret value in method \verb'A.foo' creates a ``diagonal'' edge from the $\Lambda$-fact to the secret fact $\psi$. 
+  The diagonal edge is labeled with the micro function $\lambda m\,.\,\botcc$. Thus, at the end node of the method, every receiver is mapped to the set of all types~$\bot_T$.
+
+On the end-return edge from \verb'A.foo' to \verb'main', the set of types for the receiver \verb'a' is restricted by the micro function $\lambda m\,.\,m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$ on the edge corresponding to the assignment of the return value $\psi$ to \verb'v'.
+
+Similarly, on the call-start edge from \verb'main' to \verb'B.bar', the possible types
+of the receiver \verb'a' are further restricted by the micro-function
+$\lambda m\,.\,m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$.
+on the edge that passes the argument \verb'v' to the parameter \verb's'.
+
+The composition of these micro functions results in the empty set as the possible
+types of the receiver \verb'a', indicating that this data flow path that would
+result in an information leak is actually infeasible.
 \end{example}
 
-\begin{definition}
-  For an IFDS problem $P=(G^\#)$ and a set $S$, the correlated-calls transformation $\transCC_S$ is defined as
+%After we have shown the definitions for the meet and composition operations, we will show in Example~\ref{ex:cc} how the correlated-calls analysis uses the presented micro functions to detect infeasible paths.
+
+Finally, the correlated-calls transformation is defined as
+    $\transCC_S((G^\#))=\left(G^\#,\,\lcc_S,\,\ccedgefn S\right)$.
+
+%Then, for an edge $e$, the correlated-call micro functions can be defined as $\ccedgefn R$ and a correlated-calls transformation is defined as $\transCC_R$.
+
+\subsection{Converting IDE Results to IFDS Results}
+
+\todo{What does the notation $N^*$ and $N^\#$ mean? What is the difference between the two?}
+
+For each program point $n$, the result of an IFDS analysis gives
+a set of facts $d$ that may be reached at $n$. The result of an IDE analysis
+pairs each such fact $d$ with a lattice element $\ell$. Formally,
+for an IFDS problem $P$, the result $\result_{\text{IFDS}}$ has type
+$N \to D$. Similarly, for an IFDS problem $Q$, the result $\result_{\text{IDE}}$
+has type $N \to D \times L$.
+
+Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
+and $\top$ means unreachable. Therefore, a result $\rho$ of the equivalence IDE analysis
+is converted to an IFDS result as follows:
+$\backEq(\rho) = \lambda n.\{d\mid\rho(n) = (d,\top)\}$.
+
+In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
+to the empty set of possible types means that the corresponding data flow path is
+infeasible. Therefore, a result $\rho$ of the correlated-calls IDE analysis is
+converted to an IFDS result as follows:
+$\backCC(\rho) = \lambda n.\{d\mid\rho(n) = (d,\ell), \forall r\,.\, \ell(r) \neq \top\}$.
+
+\commentout{
+
+The output of an IFDS analysis states whether a node is reachable in the exploded supergraph.
+This means that for an IFDS problem $P$, the IFDS-analysis result $\result_{\text{IFDS}}(P):\ N^*\to 2^D$ is a map from nodes of the control-flow supergraph to sets of facts:
 \begin{equation}
-    \transCC_S((G^\#))=\left(G^\#,\,\lcc_S,\,\ccedgefn S\right),
+  \result_{\text{IFDS}}(P)=\{(n,\,\mvp F(n))\,|\,n\in N^*\}\,.
 \end{equation}
-  where $\lcc_S:\,S\to2^T$.
-\end{definition}
 
-Then, for an edge $e$, the correlated-call micro functions can be defined as $\ccedgefn R$ and a correlated-calls transformation is defined as $\transCC_R$.
+\begin{mdelete}
+\begin{example}\label{ex:ifdsresult}
+  The solution to the taint-analysis IFDS problem $\mathcal P$ in Listing~\ref{list:examplejava} whose exploded supergraph is presented in Figure~\ref{fig:exampleexploded} looks as follows:
+  \small\begin{align*}
+    \result_\text{IFDS}(\mathcal P)=\{&(\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\{\texttt a\}),
+      &(\highlight{\textsf{start}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
+      &\qquad\qquad(\highlight{\textsf{return}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
+%      
+      &(\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\{\texttt a\}),
+      &(\highlight{\texttt{if(s==null)}}{lightsalmonpink},\,\{\texttt s\}),
+      &\qquad\qquad(\highlight{\texttt{return r}}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
+%
+      &(\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\{\texttt a,\,\texttt b\}),
+      &(\highlight{\textsf{call}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
+      &\qquad\qquad(\highlight{\textsf{end}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\})\}.\\
+%
+      &(\highlight{\textsf{end}_\texttt{main}}{greyblue},\,\{\texttt a,\,\texttt b\}),&(\highlight{\texttt{return s}}{lightsalmonpink},\,\{\texttt s\}),
+  \end{align*}\normalsize
+  All other nodes of the control-flow supergraph are mapped to the empty set.
+\end{example}
+\end{mdelete}
 
-\paragraph{Converting IDE Results to IFDS Results}
+ The IDE analysis associates a lattice element with each node in the exploded supergraph.
+For an IDE problem $Q$, the result $\result(Q):\ N^\#\to L$ maps nodes of the exploded supergraph to lattice elements (see~\eqref{eq:mvpdef}):
+\begin{equation}\label{eq:ideresult}
+  \result(Q)=\{((n,\,d),\,\mvp{\textsf{Env}}(n,\,d))\ |\ n\in N^*,\,d\in D\}\,.
+\end{equation}
+In other words, for each fact $d\in D$ at a given node $n\in N^*$, $\result(Q)(n,\,d)$ returns a lattice element. If a fact $d\in D$ is unreachable, $\result(Q)(n,\,d)=\top$.
+
+In the case of an equivalence transformation from IFDS to IDE, if a node in the IFDS result is reachable, it will be also reachable in the IDE result, and it will be mapped to the bottom lattice element.
+For an exploded node in the IDE result, being mapped to the top element means being not reachable.
+
+The~domain of an equivalence-IDE result 
+\begin{equation}
+  \resultEq=\result(\transEq(P))
+\end{equation}
+consists of pairs of control-flow-supergraph nodes and data-flow facts.
+The range of the result is the set of lattice elements.
+To transform an IDE result to an IFDS result, we need to map each control-flow-supergraph node to the set of facts with which it is paired, provided that the pair is mapped to the bottom lattice element.
+
+\begin{mdelete}
+\begin{example}\label{ex:ideresult}
+  Converting the IFDS problem $\mathcal P$ from Example~\ref{ex:ifdsresult} into an equivalent IDE problem and solving it will yield the following result:
+    \small\begin{align*}
+    \result(\transEq(\mathcal P))=\{&((\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\texttt a),\,\bot),\\
+      &((\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
+      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
+      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt b),\,\bot),\\
+      &\dots\}.\\
+    \end{align*}\normalsize
+  Suppose that for a pair $(n,\,d)$, where $n\in N^*$ and $d\in D$, there is no corresponding result in ~$\result_\text{IFDS}(\mathcal P)$ (see Example~\ref{ex:ifdsresult}).
+Then $(n,\,d)$ appears in $\result(\transEq(\mathcal P))$ as $((n,\,d),\,\top)$.
+\end{example}
+\end{mdelete}
+
+Let $\rho$ be the result of an equivalence-IDE analysis for an IFDS problem $P$:
+\[
+  \rho=\result(\transEq(P)).
+\]
+For a node $n\in N^*$, let $D_n^\equiv(\rho)$ be a set of data-flow facts such that
+\begin{equation}
+  D_n^\equiv(\rho)=\{d\ |\ d\in D\,\wedge\,\rho(n,\,d)\ne\top\}\,.
+\end{equation}
+Then the transformation function
+$\backEq:\,(N^\#\to L)\to(N^*\to2^D)$
+from an IDE result to~an~IFDS result looks as follows:
+\begin{equation}
+  \backEq\left(\rho\right)=
+    \left\{(n,\,D_n^\equiv(\rho))\ |\ n\in N^*\right\}\,.
+\end{equation}
+
+Obviously, if applied to the result of an equivalence-IDE problem, $\backEq$ returns a result equivalent to the original IFDS problem result.
+In other words, for any IFDS problem $P$ with supergraph $N^*$, and any node $n\in N^*$,
+\begin{equation}
+  \backEq\left(\result(\transEq(P))\right)(n)=\result_{\text{IFDS}}(P)(n)\,.
+\end{equation}
+
+\begin{example}
+  Converting the result in Example~\ref{ex:ideresult} with the equivalence-transformation from an IDE result to an IFDS result $\backEq$ will yield the same result as in Example~\ref{ex:ifdsresult}.
+\end{example}
 
@@
 \end{equation}
+}
+
+\subsection{Implementation of Correlated Calls Micro-Functions}
+\otodo{move material from following section here}
+
+Conceptually, micro-functions are functions from $L$ to $L$, where $L$
+is the IDE lattice, either $L^\equiv$ or $\lcc$ in our context. However,
+the IDE algorithm requires an efficient representation of micro-functions.
+The chosen representation needs to support the basic micro-functions that
+we presented in Section~\ref{seq:transIfdsIde}. The representation must also
+support function application, comparison, and be closed under function composition
+and meet. We now propose such a representation for the correlated-calls micro-functions.
+
+The representation of a micro-function is a map from receivers to pairs $\setpair{I}{U}$,
+where we require $U \subseteq I$.
+The meaning of such a map $\lambda r\,.\,\setpair{I_r}{U_r}$ is the micro-function
+$\lambda m\,.\,\lambda r\,.\,(m(r)\cap I_r) \cup U_r$. All of the micro-functions
+in definition \ref{def:microfn} can be represented in this form. \otodo{Say
+    how application, comparison, composition, and meet are implemented. Decide
+    how much detail and how much proof to give. Also need to introduce normalization.}
+
+\subsection{Theoretical Results}
 
@@
 \begin{lemma}[Precision]\label{lem:subsetifds}
+    \otodo{Should we say $\result_{\text{IDE}}$ instead of $\result$ everywhere, to
+        be consistent with $\result_{\text{IFDS}}$?}
     For an IFDS problem $P$ and all ${n\in N^*}$,
@@
 \end{lemma}
+\otodo{We agreed to move the proofs to the appendix.}
 \begin{proof}
@@
 
-\paragraph{Correlated-Call Receivers}\label{sec:ccreceivers}
+\subsection{Correlated-Call Receivers}\label{sec:ccreceivers}
+\otodo{should this be a section or subsection? should it be moved somewhere else (or maybe not included at all)?}
 We will now show that in a correlated-calls transformation, it is enough to consider only some of the receivers of set $R$.
@@
 
-This is the general idea of the correlated-calls analysis.
+%This is the general idea of the correlated-calls analysis.
 The analysis involves a transformation from IFDS to IDE problems.

### 2014-12-08 content/background.tex
comments

@@
 \begin{equation}
-  G^*,\,D,\,F,\,M_F,\,\sqcap)\,,
+  (G^*,\,D,\,F,\,M_F,\,\sqcap)\,,
 \end{equation} where $G^*=(N^*,\,E^*)$ is the supergraph of the input program with nodes $N^*$ and edges $E^*$, $D$ is a finite set of \textit{data-flow facts}, $F$ is a set of distributive dataflow functions of type $2^D\to2^D$, $M_F:\,E^*\to F$ is a function that maps supergraph edges to dataflow functions, and $M_F$ is extended to paths by composition\footnote{%
@@
 \end{example}
-\begin{example} 
+\commentout{\begin{example} 
   In an available-expressions analysis, $D$ is the set of all expressions in the program.
 If an expression $d\in D$ is reachable at a certain node, it means that it does not need to be recomputed at that node.
-\end{example}
+\end{example}}
 \begin{example}
@@
 
+\begin{mdelete}\mtodo{We never use the interpretation function}
 To convert a representation relation $R_f$ back into the original flow function $f$, we can use the \textit{interpretation} function $\denote {R_f}$:
@@
 \end{align}
+\end{mdelete}
 
@@
 \]
- that starts with the entrypoint of the exploded supergraph, we compute the function $f_p$ that corresponds to $p$.
+ that starts with the entrypoint of the exploded supergraph, we compute the micro function $f_p$ that corresponds to $p$.
 The micro function consists of the composition of all individual micro functions with which the edges of $p$ are labeled:
@@
 Let $Q$ be the set of paths that start at the entry point and end at the given node $(n,\,d)$.
-
 The lattice element $l_{n,\,d}$ is the meet of the lattice elements corresponding to all the paths in $Q$:

### 2014-12-08 content/background.tex
rewriting IFDS section

@@
 
-\subsection{IFDS and IDE}\mtodo{I will merge this section with the following two sections}
+\subsection{IFDS}\label{sec:bgifds}
 The IFDS framework is a precise and efficient algorithm for data-flow analysis.
-IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
-The IFDS analysis is a version of the classic \textit{functional approach} to data-flow analysis proposed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.
-
-Given a data-flow problem that satisfies the restrictions of IFDS, the algorithm provides a \textit{context-sensitive} solution in polynomial time.
-In other data-flow algorithms not based on the functional approach, the result of the analysis at the entry of a procedure ``merges'' the incoming data obtained from all callers of the procedure.
+IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}\mtodo{
+The four references take away space in the References section. Remove some of them?
+}. 
+\commentout{The IFDS analysis is a version of the classic \textit{functional approach} to data-flow analysis proposed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.}
+\commentout{In other data-flow algorithms not based on the functional approach, the result of the analysis at the entry of a procedure ``merges'' the incoming data obtained from all callers of the procedure.
 As a consequence, there is one global data-flow result computed at the end of the procedure.
@@
 In other words, the analysis result for a procedure varies depending on where the procedure was called from.
-This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.
-
-Compared to IFDS, most data-flow analyses are either general but do not run in polynomial time~\cite{knoop1992interprocedural,pnueli1981two} or handle a very specific set of problems~\cite{knoop1993efficient}.
+This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.}
+\mtodo{I'm not saying any more that IFDS is a version of Sharir\&Pnueli's functional approach.}
+\mtodo{I also removed the comparison of IFDS with other algorithms. I'm not pointing out the benefits of IFDS any more, so we might fail to show the importance of the algorithm.}
 
@@
 Each flow function operates on a \textit{subset} of $D$ (for example, the set of variables in the program) which makes the domain of the flow functions the power set of $D$.
-We describe the IFDS restrictions in detail in Section~\ref{sec:suitableifds}.
 
-The IDE framework is an expressive extension to IFDS that was created by the same authors in 1996.
-The problems that IDE can solve include, but are not limited to, IFDS problems.
-Just as the IFDS algorithm, the IDE algorithm is suitable for data-flow analyses that can be encoded with inter-procedural, distributive flow functions.
-However, in IDE, the domain of the flow functions is not restricted to sets $D$ of data-flow facts.
-The IDE domain of a flow function consists of \textit{environments} that map data-flow facts from the set $D$ to lattice elements.
+\commentout{The purpose of the IFDS framework is to solve a special subset of inter-procedural, flow-sensitive, context-sensitive data-flow-analysis problems.
+The main idea of IFDS is to encode the data-flow analysis problem into a graph-reachability problem.}
 
-As an example, in a constant propagation problem, an IDE environment would map each variable to the (possibly) constant value that it is bound to.
-To illustrate the distinction between IFDS and IDE we could say that IFDS can find out which variables in a program are constants, whereas IDE can additionally retrieve the values of the constant variables.
-
-\subsection{IFDS}\label{sec:bgifds}
-The purpose of the IFDS framework is to solve a special subset of inter-procedural, flow-sensitive, context-sensitive data-flow-analysis problems.
-The main idea of IFDS is to encode the data-flow analysis problem into a graph-reachability problem.
+Given a data-flow problem that satisfies the restrictions of IFDS, the algorithm provides a \textit{context-sensitive} \mtodo{Provide reference explaining context sensitivity?} solution in polynomial time.
+Compared to IFDS, most data-flow analyses are either general but do not run in polynomial time~\cite{knoop1992interprocedural,pnueli1981two} or handle a very specific set of problems~\cite{knoop1993efficient}.
 
 \subsubsection{Data-Flow Problems Suitable for IFDS}\label{sec:suitableifds}
-In this section we describe the data-flow problems that can be solved by an IFDS analysis. We will start with an intuitive definition and later on formalize the notion of an IFDS-suitable problem.
+\commentout{In this section we describe the data-flow problems that can be solved by an IFDS analysis.
+We will start with an intuitive definition and later on formalize the notion of an IFDS-suitable problem.}
 
@@
 For example, a taint-analysis problem asks, for each variable $v$ in the program, ``is $v$ secret at a given program point?''.
-An available-expressions problem asks, for each expression $e$, ``does $e$ have to be recomputed at a given program point?''.
+\commentout{An available-expressions problem asks, for each expression $e$, ``does $e$ have to be recomputed at a given program point?''.}
 
@@
 \subsubsection{Overview of the IFDS Algorithm}\label{sec:overviewifds}
-Formally, given an IFDS problem, for each node $n\in N^*$ the IFDS algorithm computes the \textit{meet-over-all-valid-paths} solution
+Given an IFDS problem, for each node $n\in N^*$ the IFDS algorithm computes the \textit{meet-over-all-valid-paths} solution
 \begin{equation}
@@
 \begin{align}
-  R_{f_1}\circ R_{f_2}=R_{f_1\circ f_2}\,,
-\intertext{and}
+  R_{f_1}\circ R_{f_2}=R_{f_1\circ f_2}\,,\qquad
+\text{and}\qquad
   R_{f_1}\sqcap R_{f_2}=R_{f_1\sqcap f_2}\,.
@@
 
-\begin{mdelete}\mtodo{We never use the interpretation function}
+\mtodo{We never use the interpretation function, so I deleted it, too}
+\commentout{
 To convert a representation relation $R_f$ back into the original flow function $f$, we can use the \textit{interpretation} function $\denote {R_f}$:
@@
 \end{align}
-\end{mdelete}
+}
 
-We presented an overview of the IFDS analysis. IFDS problems are transformed into IDE problems by the correlated-calls analysis. The IDE analysis is described in the next section.
+We presented an overview of the IFDS analysis. IFDS problems are transformed into IDE problems by the correlated-calls analysis. The IDE framework is described in the next section.
 
@@
 It turns out that problems with such questions can often be solved by the IDE algorithm.
+
+The IDE framework is an expressive extension to IFDS that was created by the same authors in 1996.
+The problems that IDE can solve include, but are not limited to, IFDS problems.
+Just as the IFDS algorithm, the IDE algorithm is suitable for data-flow analyses that can be encoded with inter-procedural, distributive flow functions.
+However, in IDE, the domain of the flow functions is not restricted to sets $D$ of data-flow facts.
+The IDE domain of a flow function consists of \textit{environments} that map data-flow facts from the set $D$ to lattice elements.
+
+As an example, in a constant propagation problem, an IDE environment would map each variable to the (possibly) constant value that it is bound to.
+To illustrate the distinction between IFDS and IDE we could say that IFDS can find out which variables in a program are constants, whereas IDE can additionally retrieve the values of the constant variables.
 

### 2014-12-08 content/background.tex
rewriting ide algorithm

@@
 The IDE framework is an expressive extension to IFDS that was created by the same authors in 1996.
-The problems that IDE can solve include, but are not limited to, IFDS problems.
+The problems that IDE can solve include, but are not limited to, IFDS problems~\cite{reps1995precise}.
 Just as the IFDS algorithm, the IDE algorithm is suitable for data-flow analyses that can be encoded with inter-procedural, distributive flow functions.
@@
 To illustrate the distinction between IFDS and IDE we could say that IFDS can find out which variables in a program are constants, whereas IDE can additionally retrieve the values of the constant variables.
-
 Instead of just telling us whether a fact holds or not, the IDE analysis can provide us with additional information about facts.
@@
 
+\begin{mdelete}
 For example, using the IDE analysis, we can encode a restricted version of a constant-propagation analysis\footnote{%
@@
 Furthermore, the value of the constant can be inferred from the environment for the corresponding node and is equal to $\textsf{Env}(d)$.
+\end{mdelete}
 
@@
 is the top element in the environment lattice~$\mathsf{Env}(D,\,L)$.
-
+\commentout{
 The IDE analysis is a generalization of the IFDS analysis: every IFDS problem can be converted into an equivalent IDE problem~\cite{reps1995precise}.
@@
 The conversion between IFDS and IDE problems is discussed in detail in Section~\ref{seq:transIfdsIde}.
+}
 
@@
 
-If an IDE problem is equivalent to an IFDS problem, the edges of the exploded supergraph are the same for both problems.
+For instance, if an IDE problem is equivalent to an IFDS problem, the edges of the exploded supergraph are the same for both problems.
 In the IDE problem, the edges of the exploded supergraph are labeled with identity micro functions.

### 2014-12-08 content/background.tex
decreasing figure sizes

@@
 
+\mtodo{I think the rest of this section will not make sense to anyone who does not already understand it.
+Should I try to replace it with one paragraph that tries to give an intuitive understanding of what the IDE algorithm is doing?}
 The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each inter-procedurally realizable path

### 2014-12-08 content/intro.tex
decreasing figure sizes

@@
     \node [problem] (ifds) {IFDS problem};
-    \node [problem] (equiv) [above right=0.9cm and .7\dist of ifds.east] {Equivalent IDE problem};
-    \node [problem] (ccide)[below=3cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
+    \node [problem] (equiv) [above right=0.3cm and .7\dist of ifds.east] {Equivalent IDE problem};
+    \node [problem] (ccide)[below=1.6cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
     \node [result] (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
-    \node [result] (ccres) [below=3cm of equivres.west,anchor=west] {Correlated-calls result};
+    \node [result] (ccres) [below=1.6cm of equivres.west,anchor=west] {Correlated-calls result};
     \node [result] (ifdsres) [right=\dist of equivres.east] {IFDS result};
@@
     \path[->] (ccres) edge node[above] {$\backCC$} (improved);
-    \path[->] (ccres) edge[out=30,in=240] node[above] {$\backEq$} (ifdsres);
-    \path[->] (ifds) edge[out=40,in=190] node[above] {$\transEq$} (equiv);
-    \path[->] (ifds) edge[out=-60,in=165] node[above] {$\transCC$} (ccide);
+    \path[->] (ccres) edge[out=25,in=210] node[above] {$\backEq$} (ifdsres);
+    \path[->] (ifds) edge[out=40,in=179] node[above] {$\transEq$} (equiv);
+    \path[->] (ifds) edge[out=-40,in=173] node[below] {$\transCC$} (ccide);
     \path[->] (equiv) edge node[above]{$\result$} (equivres);

### 2014-12-08 content/background.tex
removing some comments

@@
 \begin{example}
-  The exploded supergraph for Listing~\ref{list:ccexample} is shown in Figure~\ref{fig:cc_edgefn_example}.
+  The exploded supergraph for Listing~\ref{list:ccexample} is shown in Figure~\ref{fig:cc_edgefn_example}.\mtodo{Tell the reader here to ignore the labels on the edges of the graph?}
   We can see that there is a realizable path

### 2014-12-08 content/impl.tex
removed old comment
removing proof
removing some comments

@@
   \end{figure}
+\mtodo{In Figure~\ref{fig:cc_edgefn_example}, should we say that $\psi$ corresponds to the function's return value?}
 \otodo{we agreed to move this figure to the initial example section}
   \mtodo{Move Figure~\ref{fig:cc_edgefn_example} up to where it's mentioned first? If yes, the caption won't make sense.}
-  \otodo{Can we combine the IDE Figure\ref{fig:cc_edgefn_example} with the IFDS Figure 4?
-It should be the same figure, just that Figure\ref{fig:cc_edgefn_example} has labels on the edges.
-We can initially tell the reader to ignore the labels until later.}
 
@@
 
-\todo{What does the notation $N^*$ and $N^\#$ mean? What is the difference between the two?}
-
 For each program point $n$, the result of an IFDS analysis gives
@@
 \end{lemma}
-\otodo{We agreed to move the proofs to the appendix.}
-\begin{proof}
-  The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
-  \begin{align*}
-    \backCC\left(\result(\transCC_R(P))\right)(n)&=\{(n',\,D_n'^\Subset(\result(\transCC_R(P))))\ |\ n\in N^*\}(n)\\
-      &=D_n^\Subset(\result(\transCC_R(P)))\\
-      &\subseteq\mvp F(n)\\
-      &=\result_\text{IFDS}(P)(n)\,.\qedhere
-  \end{align*}
-\end{proof}
 

### 2014-12-08 content/related.tex
removing some comments

@@
 \section{Related Work}
-\otodo{should we move Related Work to near the end of the paper?}
 IFDS is a version of the functional approach to data-flow analysis developed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.

### 2014-12-08 content/impl.tex
uncomment labeled-expl-sup edge meaning
start and end node notation

@@
 \begin{itemize}
-%	\item the fact that $d_1$ holds at node $n_1$ implies that $d_2$ holds at $n_2$;
+	\item the fact that $d_1$ holds at node $n_1$ implies that $d_2$ holds at $n_2$;
   \item if at node $n_1$ the fact $d_1$ was mapped to a lattice element $l_1$ by an environment $Env(D,\,L)$, then the fact $d_2$ at node $n_2$ should be mapped to $f(l_1)$.
@@
 Let $G^\#$ be the exploded supergraph of an IFDS problem. A \emph{transformation}
-$\mathcal T:\ (G^\#)\to (G^\#,\,\edgefn)$
-converts it into an equivalent IDE problem. We consider two transformations:
+$\mathcal T:\ (G^\#)\to (G^\#,\,(\top,\,\bot),\,\edgefn)$
+converts it into an equivalent IDE problem with a two-point lattice. We consider two transformations:
 \begin{itemize}
@@
                 if $e$ is a call-start edge, $r.c()$ is
-                the call site at $n_1(e)$, $f$ is the called
+                the call site at $\src e$, $f$ is the called
                 procedure with signature $s_\mathcal F$,
@@
                 corresponding to the return node
-                at $n_2(e)$,
+                at $\target e$,
                 $f$ is the called method with
@@
             m\left[r\to \bot_T\right],
-            &\text{\parbox{75mm}{if $n_1(e)$ contains an assignment
+            &\text{\parbox{75mm}{if $\src e$ contains an assignment
                     for $r\in S$;}}\\

### 2014-12-08 content/example.tex
rewritten the introduction

--- 2014-12-05 content/intro.tex
@@
-\section{Introduction}
-\otodo{This section should be shrunk a lot (not completely deleted)}
-\begin{odelete}
-Static program analysis aims to discover properties of computer programs without running them.
-Static analysis has applications in compiler optimization, development of programming tools, and computer security, among others.
-As an example, we might want to analyze a program to know which variables are constants. 
-We could then write a compiler optimization that ensures that the values of those variables are computed only once.
-Alternatively, we could use the information about constant variables in an integrated development environment; for instance, to notify the user when an if-expression executes only one of its branches because its test condition has a constant value.
+\section{Motivating Example}
+  \label{sec:MotivatingExample}
 
-There are demonstrable limits on what information we can obtain about a program without running it.
-Rice's theorem states that verifying any non-trivial property of a program is an undecidable problem~\cite{rice1953classes}.
-However, it is sometimes possible to design an algorithm that \textit{over}- or \textit{underapproximates} the solution that we are seeking.
-
-\textit{Data-flow analysis} is an area of program analysis whose goal is to compute approximations of certain information (for example, which variables must be constants) for each program point.
-
-Other examples of data-flow analyses are \textit{reaching definitions} (finding out up to which instruction a given assignment of a variable must be valid) and \textit{available expressions} (retrieving the expressions in the program that do not need to be recomputed at a given program point).
-
-Another example of a data-flow analysis is \textit{taint analysis}~\cite{tripp2009taj}.
-Taint analysis discovers if ``secret'' values, like passwords or other confidential user information, can leak to an external observer.
-Methods that generate secret values, e.g.
-those that read user input, are called \textit{sources}.
-Methods that can leak information, e.g.
-those that write data to a file or send data through a network, are called \textit{sinks}.
-The goal of taint analysis is to find out whether data can propagate from sources to sinks.
-
-An important property of a data-flow analysis is \textit{precision}.
-Precision reflects how closely a data-flow-analysis result over- or underapproximates the information we are interested in.
-In the case of taint analysis, let $T$ be the number of sinks that the analysis considers to leak secret information, and $R$ the real number of potential information leaks.
-The smaller the difference between $T$ and $R$, the greater the precision of the taint analysis.
-
-Data-flow analyses operate on \textit{control-flow graphs} that model the order in which the instructions of a program are executed.
-A data-flow-analysis problem defines \textit{flow functions} that represent how data is propagated along the edges of the control-flow graph.
-The \textit{confluence operator} specifies how the data that has been computed along different paths should be merged when the paths join.
-
-Since a control-flow graph is an overapproximation of the possible flows of control in concrete executions of a program, the graph may contain \textit{infeasible} paths that cannot occur at runtime.
-
-One way to improve the precision of a data-flow analysis is to detect and eliminate infeasible paths.
-
-Our goal is to improve the precision of solutions to problems that can be solved by the \textit{Inter-procedural Finite Distributive Subset} (IFDS) algorithm~\cite{reps1995precise}.
-The IFDS algorithm is a general data-flow algorithm that can compute solutions to various data-flow problems, like reaching definitions, available expressions, and taint analysis.
-
-We improve the precision of IFDS problem solutions by eliminating infeasible paths that occur in object-oriented programs in the presence of \textit{correlated method calls}~--- polymorphic calls that are invoked on the same object~\cite{DBLP:journals/scp/Tip15}.
-\end{odelete}
-
-\section{Motivating Example}
+\ftodo{This section is current under revision. Please do not edit..}
 
@@
 
+\commentout{
 Our technique for improving the precision of an IFDS result is based on transforming the original IFDS problem into a more expressive \textit{Inter-procedural Distributive Environment} (IDE) problem.
@@
 
-\begin{figure}
-  \centering
-    \tikzset{
-  ashadow/.style={opacity=.25, shadow xshift=0.07, shadow yshift=-0.07},
-}
-  \tikzstyle{problem}=[fill=greyblue,text width=2.3cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
-  \tikzstyle{result}=[fill=bisque,text width=1.8cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
-\begin{tikzpicture}
-    \node [problem] (ifds) {IFDS problem};
-    \node [problem] (equiv) [above right=0.9cm and .7\dist of ifds.east] {Equivalent IDE problem};
-    \node [problem] (ccide)[below=3cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
-    \node [result] (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
-    \node [result] (ccres) [below=3cm of equivres.west,anchor=west] {Correlated-calls result};
-    \node [result] (ifdsres) [right=\dist of equivres.east] {IFDS result};
-    \node [result] (improved) [right=\dist of ccres.east] {Improved IFDS result};
-    \path[->] (equivres) edge node[above]{$\backEq$} (ifdsres);
-    \path[->] (ccres) edge node[above] {$\backCC$} (improved);
-    \path[->] (ccres) edge[out=30,in=240] node[above] {$\backEq$} (ifdsres);
-    \path[->] (ifds) edge[out=40,in=190] node[above] {$\transEq$} (equiv);
-    \path[->] (ifds) edge[out=-60,in=165] node[above] {$\transCC$} (ccide);
-    \path[->] (equiv) edge node[above]{$\result$} (equivres);
-    \path[->] (ccide) edge node[above]{$\result$} (ccres);
-\end{tikzpicture}
-  \caption{Transformations between IFDS and IDE problems and their results}%
-  \label{fig:transformations}%
-\end{figure}
-
   We prove that the solution to an IDE problem that considers correlated calls is more precise than the solution to the original IFDS problem.
@@
 The proofs for the lemmas in the paper are provided in the Appendix.\mtodo{Reference appendix like this?}
+}

### 2014-12-08 content/intro.tex
rewritten the introduction

--- 2014-12-05 content/intro.tex
@@
 \section{Introduction}
-\otodo{This section should be shrunk a lot (not completely deleted)}
-\begin{odelete}
+
+Data-flow analysis computes an approximation of how values may flow  
+through a program, and has applications in compiler optimization, 
+programming tools, and computer security, and many other areas.
+Data-flow analyses operate on \textit{control-flow graphs} (CFGs) that model 
+the order in which the instructions of a program are executed. This is
+typically done by associating \textit{flow functions} that represent how 
+data is propagated with the edges of the control-flow graph.  A 
+\textit{confluence operator} specifies how the data facts that have been 
+computed along different paths should be merged when the paths join.
+
+Since a control-flow graph is an over-approximation of the possible flows 
+of control in concrete executions of a program, it may contain \textit{infeasible} 
+paths that cannot occur at runtime. The precision of a data-flow analysis algorithm
+depends critically on its ability to detect and disregard such infeasible paths.
+The popular \textit{Interprocedural Finite Distributive Subset} (IFDS) algorithm 
+by  Reps, Horwitz, and Sagiv \cite{reps1995precise} is a general data-flow analysis
+algorithm for computing solutions to finite distributive data-flow problems such 
+as reaching definitions, available expressions, and taint analysis. A distinguishing 
+characteristic of IFDS is that it avoids infeasible interprocedural paths in which calls 
+and returns to/from functions are not properly matched. Sagiv, Reps, and Horwitz
+also presented the \textit{Interprocedural Distributive Environment} (IDE) algorithm
+\cite{sagiv1996precise} that similarly only considers properly matched call/return
+edges, but that supports a broader range of dataflow problems by expanding the 
+domain of flow functions to \textit{environments} that go beyond the data-flow facts 
+considered by IFDS.
+
+This paper presents an approach to dataflow analysis that avoids a type
+of infeasible path that arises in object-oriented programs when two or more
+methods are dynamically dispatched on the same receiver object. In such cases, if the
+method calls are polymorphic (i.e., if they dispatch to different method definitions 
+depending on the type of the receiver expression at run time), then their dispatch 
+behaviors will be correlated. A recent paper \cite{DBLP:journals/scp/Tip15} identified
+this problem but did not present a concrete solution or algorithm, and we are not aware 
+of any existing dataflow analysis that is capable of avoiding infeasible paths that arise 
+in the presence of correlated method calls.
+
+\input{figures/fig-transformation}
+
+The approach taken in our work is to transform a standard IFDS problem into an
+IDE problem that precisely accounts for infeasible paths due to correlated calls. 
+The results of this IDE problem can be mapped back to the dataflow domain of the 
+original IFDS problem.
+
+We present a formalization of the transformation and prove its correctness
+as follows. First, we derive an ``Equivalence IDE problem'' from the original 
+IFDS problem by associating the identity environment functions with all edges,
+and show that the solution to this Equivalence IDE problem can be mapped back
+to the solution of the original IFDS problem. Then, we derive a ``Correlated Calls 
+IDE Problem' from the original IFDS problem and show how a solution to this problem 
+can be mapped to the solution to the original IFDS problem, but also how an
+more precise IFDS result can be derived from it. 
+We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
+This is illustrated schematically
+in Figure~\ref{fig:transformations}%
+\footnote{ 
+  The labels $\result$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$ on edges in 
+  Figure~\ref{fig:transformations} reflect a number of mappings and projections 
+  that will be defined in Section~\TODO{ref} and that can be ignored here.
+}.  
+\ftodo{would it make sense to add an edge in Figure~\ref{fig:transformations} from the IFDS problem to the IFDS result?}
+
+We implemented the correlated-calls transformation and the IDE algorithm in Scala,
+on top of the WALA framework for static analysis of JVM bytecode~\cite{fink2012wala}.
+We also report on preliminary experiments in which our correlated-calls transformation
+is applied to an IFDS formulation of a simple taint analysis. Our results show that
+solving the resulting IDE problem avoids infeasible paths due to correlated calls as
+expected.  
+\mtodo{As discussed on the phone, we want to talk more about the results here.}
+
+In summary, the contributions of this paper are as follows:
+\begin{itemize}
+  \item
+    We present a general approach for transforming IFDS problems into corresponding
+    IDE problems that avoid infeasible paths due to correlated method calls and
+    prove its correctness. 
+  \item
+    We implemented the approach in Scala, on top of the WALA program analysis framework
+    and report on preliminary experiments. 
+\end{itemize}
+
+The remainder of this paper is organized as follows.
+%
+Section~\ref{sec:MotivatingExample} presents a motivating example.
+%
+Section~\ref{sec:bg} reviews the IFDS and IDE algorithms.
+%
+Section~\ref{sec:ccdatastr} presents the correlated-calls transformation
+and a proof of its correctness.
+%
+The implementation of our approach and preliminary experiments are discussed
+in Section~\ref{chapter:eval}.
+%
+Related work is discussed in Section~\TODO{ref}.
+%
+Finally, conclusions and directions for future work are presented in Section~\TODO{ref}.
+
+\commentout{
 Static program analysis aims to discover properties of computer programs without running them.
@@
 We improve the precision of IFDS problem solutions by eliminating infeasible paths that occur in object-oriented programs in the presence of \textit{correlated method calls}~--- polymorphic calls that are invoked on the same object~\cite{DBLP:journals/scp/Tip15}.
-\end{odelete}
-
-\section{Motivating Example}
-
-Consider a call site~$r.m()$ in an object-oriented programming language, where the variable~$r$ is the \textit{receiver} variable of the call site and $m$ is the name of the invoked method\footnote{We assume an internal representation of the program in which for each call site $e_r.m()$, the expression~$e_r$ has been evaluated to the variable~$r$.}.
-In the rest of the paper, we use the general term \textit{receiver} to mean a receiver variable.
-At runtime, the actual method that will be invoked by the call site depends on the runtime type of the object referenced by $r$.
-If the call site $r.m()$ can be associated with more than one method at compile time, we will say that the call site is \textit{polymorphic}.
-
-For example, in Listing~\ref{list:ccexample}, it is not possible to infer statically whether the runtime type of the variable \verb'a' in the \texttt{main} method is \verb'A' or \verb'B'.
-The call \verb'a.foo()' can be dispatched to either \verb'A.foo' or \verb'B.foo', and \verb'a.bar(v)' can be dispatched to either \verb'A.bar' or \verb'B.bar'.
-A concrete execution path for the main method might therefore go through \verb'A.foo' and \verb'A.bar', or through \verb'B.foo' and \verb'B.bar'.
-However, there cannot be an execution path through \verb'A.foo' and \verb'B.bar' or through \verb'B.foo' and \verb'A.bar'.
-
-\begin{figure}
-  \centering
-  \begin{minipage}{\textwidth}
-    \inputMinted{java}{ccexample.java}
-  \end{minipage}
-  \caption{Example program containing correlated calls}
-  \label{list:ccexample}
-\end{figure}
-
-We call the invocations to methods \verb'foo' and \verb'bar' \textit{correlated}.
-More generally, correlated calls occur when more than one polymorphic call is invoked on the same receiver variable.
-
-Suppose we wanted to perform a taint analysis on the program in Listing~\ref{list:ccexample}.
-Most dataflow-analysis algorithms, including IFDS, would conservatively assume that the call \verb'a.bar' could be dispatched to both \verb'A.bar' and \verb'B.bar', independently of what \verb'a.foo' had been dispatched to in the previous line.
-
-As a result, 
-such an analysis would consider a path through \verb'A.foo' and \verb'B.bar' feasible.
-This means that the variable \verb'v' would be considered secret.
-We would conclude that a secret value is passed to \verb'B.bar' and printed to the user.
-In other words, we would consider the program to leak secret information, which it does not do in any concrete execution.
-
-Our technique for improving the precision of an IFDS result is based on transforming the original IFDS problem into a more expressive \textit{Inter-procedural Distributive Environment} (IDE) problem.
-IDE problems can be solved with the IDE algorithm which is a generalization of IFDS~\cite{sagiv1996precise}.
-The IDE algorithm can, for instance, solve certain versions of the constant propagation problem that IFDS cannot.
-
-To improve the precision of IFDS results, given an IFDS problem $P$, we convert it into an IDE problem $Q$ that accounts for correlated calls.
-We then use the IDE algorithm to obtain a solution to $Q$.
-Finally, we convert the IDE result into a IFDS result.
-In the presence of correlated calls, the obtained IFDS result can be more precise than the solution that the IFDS algorithm would compute for $P$.
-
-The goal of the correlated-calls analysis presented in this work is to modify the output of an IFDS analysis to account for correlated calls.
-Specifically, the correlated-calls analysis improves the precision of IFDS problem results by eliminating infeasible execution paths caused by correlated calls.
-This is done by converting the input-IFDS problem to an IDE problem that detects infeasible paths, and converting the IDE result back to a more precise IFDS result.
-
-The contributions of this work are:
-\begin{itemize}
-  \item A transformation from IFDS to IDE problems that considers correlated calls.
-  \item An implementation in Scala of the correlated-calls transformation and the IDE algorithm which is based on the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
-\end{itemize}\mtodo{Reference the figure here.}
-
-\begin{figure}
-  \centering
-    \tikzset{
-  ashadow/.style={opacity=.25, shadow xshift=0.07, shadow yshift=-0.07},
 }
-  \tikzstyle{problem}=[fill=greyblue,text width=2.3cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
-  \tikzstyle{result}=[fill=bisque,text width=1.8cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
-\begin{tikzpicture}
-    \node [problem] (ifds) {IFDS problem};
-    \node [problem] (equiv) [above right=0.9cm and .7\dist of ifds.east] {Equivalent IDE problem};
-    \node [problem] (ccide)[below=3cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
-    \node [result] (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
-    \node [result] (ccres) [below=3cm of equivres.west,anchor=west] {Correlated-calls result};
-    \node [result] (ifdsres) [right=\dist of equivres.east] {IFDS result};
-    \node [result] (improved) [right=\dist of ccres.east] {Improved IFDS result};
-    \path[->] (equivres) edge node[above]{$\backEq$} (ifdsres);
-    \path[->] (ccres) edge node[above] {$\backCC$} (improved);
-    \path[->] (ccres) edge[out=30,in=240] node[above] {$\backEq$} (ifdsres);
-    \path[->] (ifds) edge[out=40,in=190] node[above] {$\transEq$} (equiv);
-    \path[->] (ifds) edge[out=-60,in=165] node[above] {$\transCC$} (ccide);
-    \path[->] (equiv) edge node[above]{$\result$} (equivres);
-    \path[->] (ccide) edge node[above]{$\result$} (ccres);
-\end{tikzpicture}
-  \caption{Transformations between IFDS and IDE problems and their results}%
-  \label{fig:transformations}%
-\end{figure}
-
-  We prove that the solution to an IDE problem that considers correlated calls is more precise than the solution to the original IFDS problem.
-  We also show that the correlated-calls analysis is sound, i.e.
-that it never considers concrete execution paths as infeasible.\mtodo{As discussed on the phone, we want to talk more about the results here.}
-
- Finally, we evaluate the effectiveness of the correlated-calls analysis using an implementation of taint analysis as the source IFDS problem.
-
-The remainder of this paper is organized as follows.
-In the next section, we describe the IFDS and IDE analyses in detail.
-In Section~\ref{chapter:cca} we present the correlated-calls analysis as a transformation of IFDS problems into a special kind of IDE problem.
-Section~\ref{sec:ccdatastr} describes an efficient representation of the data structures that are required to define a correlated-calls IDE transformation.
-In Section~\ref{chapter:eval} we address some implementation aspects of the correlated-calls analysis and present an evaluation of its results.
-Section~\ref{chapter:concl} contains concluding remarks.
-The proofs for the lemmas in the paper are provided in the Appendix.\mtodo{Reference appendix like this?}

### 2014-12-08 figures/fig-transformation.tex
rewritten the introduction

\begin{figure}
  \centering
    \tikzset{
  ashadow/.style={opacity=.25, shadow xshift=0.07, shadow yshift=-0.07},
}
  \tikzstyle{problem}=[fill=greyblue,text width=2.3cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
  \tikzstyle{result}=[fill=bisque,text width=1.8cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
\begin{tikzpicture}
    \node [problem] (ifds) {IFDS problem};
    \node [problem] (equiv) [above right=0.3cm and .7\dist of ifds.east] {Equivalent IDE problem};
    \node [problem] (ccide)[below=1.6cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
    \node [result] (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
    \node [result] (ccres) [below=1.6cm of equivres.west,anchor=west] {Correlated-calls result};
    \node [result] (ifdsres) [right=\dist of equivres.east] {IFDS result};
    \node [result] (improved) [right=\dist of ccres.east] {Improved IFDS result};
    \path[->] (equivres) edge node[above]{$\backEq$} (ifdsres);
    \path[->] (ccres) edge node[above] {$\backCC$} (improved);
    \path[->] (ccres) edge[out=25,in=210] node[above] {$\backEq$} (ifdsres);
    \path[->] (ifds) edge[out=40,in=179] node[above] {$\transEq$} (equiv);
    \path[->] (ifds) edge[out=-40,in=173] node[below] {$\transCC$} (ccide);
    \path[->] (equiv) edge node[above]{$\result$} (equivres);
    \path[->] (ccide) edge node[above]{$\result$} (ccres);
\end{tikzpicture}
  \caption{Transformations between IFDS and IDE problems and their results}%
  \label{fig:transformations}%
\end{figure}

### 2014-12-09 content/impl.tex
add text from section 5 about implementation of micro-functions

@@
 
-The representation of a micro-function is a map from receivers to pairs $\setpair{I}{U}$,
-where we require $U \subseteq I$.
-The meaning of such a map $\lambda r\,.\,\setpair{I_r}{U_r}$ is the micro-function
-$\lambda m\,.\,\lambda r\,.\,(m(r)\cap I_r) \cup U_r$. All of the micro-functions
-in definition \ref{def:microfn} can be represented in this form. \otodo{Say
-    how application, comparison, composition, and meet are implemented. Decide
-    how much detail and how much proof to give. Also need to introduce normalization.}
+The representation of a micro-function is a map from receivers to pairs of sets of
+types $I(r)$ and $U(r)$, where $U(r)$ is required to be a subset of $I(r)$. We use the notation
+$\setpair{I}{U}$ to represent such a map, and $I(r)$ and $U(r)$ to look up the
+sets corresponding to a particular receiver $r$. We define the meaning $\denote{\setpair{I}{U}}$
+of a representation $\setpair{I}{U}$ as follows: $\denote{\setpair{I}{U}} = \lambda m\,.\,\lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
+In words, the micro-function represented by $\setpair{I}{U}$ takes an existing map $m$
+from receivers to sets of types, and returns a map that maps each receiver $r$ to
+the set $m(r)$ given by the original map $m$ intersected with $I(r)$ and unioned
+with $U(r)$.
+
+All of the basic micro-functions defined in Definition~\ref{def:microfn} can be expressed
+in this representation.
+
+The implementation of function application follows directly from the definition of
+the representation: $\setpair{I}{U}(m) = \lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
+
+To compare two micro-functions for equality, it suffices to compare the corresponding
+sets $I(r)$ and $U(r)$ for all receivers $r$. The following lemma shows that this
+implementation of comparison corresponds to equality of the represented micro-functions:
+\begin{lemma}\label{lem:equal}
+    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
+    \[
+        \forall r\,.\,I(r) = I'(r) \land U(r) = U'(r)
+        \iff
+        \denote{\setpair{I}{U}} = \denote{\setpair{I'}{U'}}
+    \] 
+\end{lemma}
+\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}
+
+\otodo{The normalization function $\mathcal N$ was only needed in composition. I therefore
+    ``inlined'' it into composition to save space. This makes composition a bit harder to intuitively
+    verify, but saves complexity here. The verification can be in the proof in the supplementary appendix.}
+The composition of two micro-function representations is defined as follows:
+$\setpair{I}{U} \circ \setpair{I'}{U'} = \setpair{\lambda r\,.\,(I(r) \cap I'(r))\cup U(r)}{\lambda r\,.\,(I(r)\cap U'(r))\cup U(r)}$.
+The following lemma shows that this implementation corresponds to the composition
+of the denoted functions:
+\begin{lemma}\label{lem:equal}
+    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
+    \[
+        \denote{\setpair{I}{U}} \circ \denote{\setpair{I'}{U'}}
+        = 
+        \denote{\setpair{I}{U}} \circ \denote{\setpair{I'}{U'}}
+    \]
+\end{lemma}
+\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}
+
+The meet of two micro-function representations is defined as follows:
+$\setpair{I}{U} \sqcap \setpair{I'}{U'} = \setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}$.
+The following lemma shows that this implementation corresponds to the meet
+of the denoted functions:
+\begin{lemma}\label{lem:equal}
+    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
+    \[
+        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
+        = 
+        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
+    \]
+\end{lemma}
+\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}
+
+\otodo{Sagiv et al. define a notion of an ``efficient'' implementation of micro-functions.
+    If the micro-functions are ``efficient'', then the asymptotic complexity bounds proven by
+    Sagiv hold. Our implementation is ``efficient'' if we assume that the number of correlated
+    receivers is a constant independent of the size of the program. That seems a stretch. If
+    it's linear in the size of the program, then we would need to add a factor to their complexity
+    bounds. Their bound is $O(ED^3)$, while ours would be $O(ED^3R)$. But then we can't directly use their complexity proof; we would have to adapt it.
+    I'm leaning towards leaving out any mention of ``efficient'' implementation.}
 

### 2014-12-09 content/intro.tex

@@
 to the solution of the original IFDS problem. Then, we derive a ``Correlated Calls 
-IDE Problem' from the original IFDS problem and show how a solution to this problem 
-can be mapped to the solution to the original IFDS problem, but also how an
+IDE Problem'' from the original IFDS problem and show how a solution to this problem 
+can be mapped to the solution to the original IFDS problem, but also how a
 more precise IFDS result can be derived from it. 
+\otodo{Do we need to mention the imprecise map from the CC-IDE result to the IFDS result? It
+doesn't really seem relevant, and could be confusing.}
 We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.

### 2014-12-09 content/intro.tex
comments

@@
 programming tools, and computer security, and many other areas.
-Data-flow analyses operate on \textit{control-flow graphs} (CFGs) that model 
+Data-flow analyses operate on \textit{control-flow graphs} (CFGs)%
+\mtodo{If we introduce this abbreviation, should we replace the uses of
+``control-flow graph'' with ``CFG'' in the paper?}
+that model 
 the order in which the instructions of a program are executed. This is
@@
 We present a formalization of the transformation and prove its correctness
-as follows. First, we derive an ``Equivalence IDE problem'' from the original 
+as follows. First, we derive an ``Equivalence IDE problem''%
+\mtodo{The IDE paper already states that each IFDS problem can be solved with IDE.
+I wonder if this sounds like the equivalence transformation was our contribution.
+We just use the equivalence transformation to explain the CC transformation, and for the
+proofs.
+}
+from the original 
 IFDS problem by associating the identity environment functions with all edges,
@@
 expected.
-\mtodo{As discussed on the phone, we want to talk more about the results here.}
 

### 2014-12-09 content/background.tex
start and end node notation
reduce/rework general and IFDS part of background section

@@
 \section{Background}\label{sec:bg}
-The purpose of the correlated-calls analysis is to solve IFDS problems more precisely than using the standard IFDS algorithm by ruling out some infeasible paths.
+%The purpose of the correlated-calls analysis is to solve IFDS problems more precisely than using the standard IFDS algorithm by ruling out some infeasible paths.
 The correlated-calls analysis works by transforming an IFDS problem to an IDE problem, solving the IDE problem, and transforming the IDE result to a solution to the original IFDS problem.
-This section describes the general ideas underlying IFDS and IDE.
+This section defines basic terminology and presents the IFDS and IDE algorithms.
 
 \subsection{Terminology and Notation}
-We will start by introducing several concepts used by the IFDS and IDE analyses.
+%We will start by introducing several concepts used by the IFDS and IDE analyses.
+The \textit{control-flow graph} of a procedure is a directed graph whose nodes are instructions, and which contains an edge from $n_1$ to $n_2$ whenever
+$n_2$ may execute immediately after $n_1$. A control-flow graph has a distinguished \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$.
+%and edges represent transfer of control between the instructions during an execution of the program. 
+%A control-flow graph has a unique start node, $\startmain$, which is the node corresponding to the program entrypoint.
+%An \textit{intra-procedural} path is a path in a control-flow graph whose nodes are in the same procedure.
+By contrast, an \textit{inter-procedural path} is one that contains nodes from different procedures.
+The \textit{control-flow supergraph} of a program contains the control-flow graphs of all of the procedures as
+subgraphs. In addition, for each call instruction $c$, the supergraph contains a \textit{call-to-start} edge to the start node of every procedure that
+may be called from $c$, and an \textit{end-to-return} edge from the end node of the procedure back to the call instruction.
+\otodo{do we really need to extra "return nodes" that the IFDS/IDE papers add?}
+%is a control-flow graph
+%in which each procedure $p$ is augmented with an additional \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$, and for each call $c_q$ to a procedure $q$, there is a \textit{call node} \textsf{call}$_{c_q}$ and subsequent \textit{return node} \textsf{return}$_{c_q}$.
 
-A \textit{control-flow graph} is a directed graph in which nodes correspond to instructions and edges represent transfer of control between the instructions during an execution of the program. 
-A control-flow graph has a unique start node, $\startmain$, which is the node corresponding to the program entrypoint.
+%A control-flow supergraph allows us to model the control flow in inter-procedural paths.
+ %The flow from the caller to the callee is represented using an edge \[(\textsf{call}_{c_q},\,\textsf{start}_q)\,.\] The control flow from the callee back to the caller goes through an edge \[(\textsf{end}_q,\,\textsf{return}_{c_q})\,.\]
 
-An \textit{intra-procedural} path is a path in a control-flow graph whose nodes are in the same procedure.
-By contrast, an \textit{inter-procedural path} is one that contains nodes from different procedures.
+A call site is \textit{monomorphic} if it always calls the same procedure. In an object-oriented language, 
+a call site $r.m(\ldots)$ can dynamically dispatch to multiple methods depending on the runtime
+type of the object pointed to by the receiver $r$.
+A call site that calls multiple procedures is called
+\textit{polymorphic}.
+We define a function $\textsf{lookup}$ to specify the dynamic dispatch: 
+if $s$ is the signature of $m$ and $t$ is the runtime type of the object
+pointed to by $r$, $\textsf{lookup}(s,t)$ gives the procedure that will
+be invoked by the call $r.m(\ldots)$. We also define a kind of inverse $\tau$
+of $\textsf{lookup}$: given a signature $s$ and a specific invoked procedure
+$f$, $\tau(s,f)$ gives the set of all runtime types of $r$ that cause $r.m(\ldots)$
+to dispatch to $f$: $\tau(s,f) = \{t\mid \textsf{lookup}(s,t)=f\}$.
 
-A \textit{control-flow supergraph} is a control-flow graph
-in which each procedure $p$ is augmented with an additional \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$, and for each call $c_q$ to a procedure $q$, there is a \textit{call node} \textsf{call}$_{c_q}$ and subsequent \textit{return node} \textsf{return}$_{c_q}$.
-
-A control-flow supergraph allows us to model the control flow in inter-procedural paths.
- The flow from the caller to the callee is represented using an edge \[(\textsf{call}_{c_q},\,\textsf{start}_q)\,.\] The control flow from the callee back to the caller goes through an edge \[(\textsf{end}_q,\,\textsf{return}_{c_q})\,.\]
+\otodo{do we ever use $\src$ and $\target$?}
+We denote the source and end nodes of a graph edge $e$ as $\src e$ and $\target e$.
 
@@
 
-A \textit{flow-sensitive} data-flow analysis is one that takes the order of program instructions into account.
+%A \textit{flow-sensitive} data-flow analysis is one that takes the order of program instructions into account.
 
-Let each call node in a program be labeled with a distinct opening parenthesis and the corresponding return node with the matching closing parenthesis.
+A path through the control-flow supergraph is \textit{valid} if every end-to-return edge on the path returns
+to the site of the most recent unmatched call. The set of all valid paths from the program entry point to
+a node $n$ is denoted $\ivp(n)$.
+\otodo{Should we give a formal definition?}
+
+%Let each call node in a program be labeled with a distinct opening parenthesis and the corresponding return node with the matching closing parenthesis.
 For a given path $p$, let $s$ be the string that is obtained by concatenating the labels of the nodes in $p$.
-Then $p$ is \textit{valid} if $s$ belongs to the language of substrings of balanced parentheses.
+%Then $p$ is \textit{valid} if $s$ belongs to the language of substrings of balanced parentheses.
 The set of all inter-procedurally valid paths from the start node to a node $n$ is denoted as $\ivp(n)$.
@@
 
-A \textit{context-sensitive} data-flow analysis is an analysis that considers only inter-procedurally valid paths.
+%A \textit{context-sensitive} data-flow analysis is an analysis that considers only inter-procedurally valid paths.
 
+\commentout{
 \begin{mdelete}
@@
 \end{mdelete}
+}
 
-A \textit{lattice} is a partially ordered set in which each subset has a least upper bound and a greatest lower bound.
+\otodo{The definitions that Marianna had were for \emph{complete}
+lattices/semilattices. All of the lattices in the context of IFDS/IDE
+are/must be complete. I'll just say that here.}
+A \textit{complete lattice} is a partially ordered set $(S,\sqsubseteq)$ in which every subset has a least upper bound and a greatest lower bound.
+A \textit{complete meet semilattice} is a partially ordered set in which every subset need only have a greatest lower bound.
+The symbols $\bot$ and $\top$ are used to denote the greatest lower bound of $S$ and of the empty set, respectively.
+Since all of the (semi)lattices discussed in this paper are required to be complete, we will henceforth leave out the
+\textit{complete} qualifier.
 
-A \textit{meet semilattice} $L=(S,\,\sqcap)$ is defined by a set $S$ and a meet operation $\sqcap$ that is  associative, commutative, and idempotent.
-  The meet operation induces a partial order $(S,\,\sqsubseteq)$ where every subset contains  a greatest lower bound: For all $x,\,y\in S$, $x\sqsubseteq y$ if $x\sqcap y=x$.
+%A \textit{meet semilattice} $L=(S,\,\sqcap)$ is defined by a set $S$ and a meet operation $\sqcap$ that is  associative, commutative, and idempotent.
+  %The meet operation induces a partial order $(S,\,\sqsubseteq)$ where every subset contains  a greatest lower bound: For all $x,\,y\in S$, $x\sqsubseteq y$ if $x\sqcap y=x$.
 The greatest lower bound, or top element, of the semilattice is denoted as $\top$.
-  If $k$ is the length of the longest chains of elements in the semilattice, then the \textit{height} of the semilattice is~$k-1$.
+  %If $k$ is the length of the longest chains of elements in the semilattice, then the \textit{height} of the semilattice is~$k-1$.
 
-Finally, we introduce the notion of \textit{distributivity}. Given a set $D$, a function $f:2^D\to2^D$ is distributive if $\forall x_1,\,x_2\in 2^D$,
-\begin{equation}
-  f(x_1\cup x_2)=f(x_1)\cup f(x_2).
-\end{equation}
+In this paper, we denote a map $m$ as a set of pairs of keys and values, in which each key appears at most once.
+For any map $m$,  $m(k)$ is the value paired with the key $k$ in $m$. We denote by $m[x\to y]$ a map that maps $x$ to $y$, and every other key $k$ to $m(k)$.
+%To avoid excessive parentheses, we write $\left(m[x_1\to y_1]\right)[x_2\to y_2]$ as $m[x_1\to y_1][x_2\to y_2]$.
 
-In this work, we will denote a map from a set of keys $K$ to values from set $V$ as
-\begin{equation}
-  \{(k,\,v)\,|\,k\in K,\,v\in V\}.
-\end{equation}
-For an arbitrary map $m$,  $m(x)$ is the value to which $x$ is mapped in $m$. We denote by $m[x\to y]$ a map identical to $m$, except that the element $x$ is mapped to $y$.
-To avoid excessive parentheses, we write $\left(m[x_1\to y_1]\right)[x_2\to y_2]$ as $m[x_1\to y_1][x_2\to y_2]$.
+%We will denote the identity function $\lambda x\,.x$ by $\textsf{id}$.
+%We will use a typed version of this function in various contexts, where the type of $x$ will vary with
+%the context.
 
-We will denote the identity function $\lambda x\,.x$ by $\textsf{id}$.
-We will use a typed version of this function in various contexts, where the type of $x$ will vary with
-the context.
+%OL: we can just as easily write the identity explicitly as \x.x throughout.
 
 \subsection{IFDS}\label{sec:bgifds}
-The IFDS framework is a precise and efficient algorithm for data-flow analysis.
-IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}\mtodo{
-The four references take away space in the References section. Remove some of them?
-}. 
+The IFDS framework~\cite{reps1995precise} is a precise and efficient algorithm for data-flow analysis
+%. IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and
+that has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
+%\mtodo{ The four references take away space in the References section. Remove some of them?  }
+The IFDS framework is an instance of the \textit{functional approach} to data-flow analysis~\cite{pnueli1981two}
+because it constructs summaries of the effects of called procedures.
 \commentout{The IFDS analysis is a version of the classic \textit{functional approach} to data-flow analysis proposed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.}
@@
 \mtodo{I also removed the comparison of IFDS with other algorithms. I'm not pointing out the benefits of IFDS any more, so we might fail to show the importance of the algorithm.}
+The IFDS framework is applicable to \textit{inter-procedural} data flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
+and whose data-flow functions are \textit{distributive}.
+A function $f$ is distributive if 
+$f(x_1\sqcap x_2)=f(x_1)\sqcap f(x_2)$.
 
-The IFDS algorithm is applicable to problems which can be expressed with data-flow functions that satisfy certain restrictions.
+%The IFDS algorithm is applicable to problems which can be expressed with data-flow functions that satisfy certain restrictions.
 \textit{Inter-procedural} flow functions specify how data flows from the invocation of a procedure to its start, and from the procedure's end back to its call site.
@@
 
-Given a data-flow problem that satisfies the restrictions of IFDS, the algorithm provides a \textit{context-sensitive} \mtodo{Provide reference explaining context sensitivity?} solution in polynomial time.
-Compared to IFDS, most data-flow analyses are either general but do not run in polynomial time~\cite{knoop1992interprocedural,pnueli1981two} or handle a very specific set of problems~\cite{knoop1993efficient}.
+The IFDS algorithm is notable because it computes a meet over valid paths solution in polynomial time.
+Most other interprocedural analysis algorithms are either imprecise due to invalid paths,
+general but do not run in polynomial time~\cite{knoop1992interprocedural,pnueli1981two}, or handle a very specific set of problems~\cite{knoop1993efficient}.
 
-\subsubsection{Data-Flow Problems Suitable for IFDS}\label{sec:suitableifds}
+%\subsubsection{Data-Flow Problems Suitable for IFDS}\label{sec:suitableifds}
 \commentout{In this section we describe the data-flow problems that can be solved by an IFDS analysis.
@@
 
-Informally, an IFDS analysis can only solve decision problems.
+%Informally, an IFDS analysis can only solve decision problems.
 An IFDS analysis answers questions of the following kind: ``is property $X$ true at program point~$Y$?''.
@@
 
-Formally, a data-flow analysis problem is suitable for an IFDS analysis if it can be encoded as an IFDS problem
-\begin{equation}
-  (G^*,\,D,\,F,\,M_F,\,\sqcap)\,,
-\end{equation} where $G^*=(N^*,\,E^*)$ is the supergraph of the input program with nodes $N^*$ and edges $E^*$, $D$ is a finite set of \textit{data-flow facts}, $F$ is a set of distributive dataflow functions of type $2^D\to2^D$, $M_F:\,E^*\to F$ is a function that maps supergraph edges to dataflow functions, and $M_F$ is extended to paths by composition\footnote{%
+The input to the IFDS algorithm is specified as
+%Formally, a data-flow analysis problem is suitable for an IFDS analysis if it can be encoded as an IFDS problem
+  $(G^*,\,D,\,F,\,M_F,\,\sqcap)$,
+where $G^*=(N^*,\,E^*)$ is the supergraph of the input program with nodes $N^*$ and edges $E^*$,
+$D$ is a finite set of \textit{data-flow facts},
+$F$ is a set of distributive dataflow functions of type $2^D\to2^D$,
+$M_F:\,E^*\to F$ assigns a dataflow function to each supergraph edge,
+and $\sqcap$ is the \textit{meet operator} on the powerset $2^D$, either union or intersection.
+In our presentation, the meet will always be union, but all of the results apply dually when the
+meet is intersection.
+
+The output of the IFDS algorithm is, for each node $n$ in the supergraph, the \textit{meet-over-all-valid-paths} solution
+ $\mvp{F}(n)=\bigsqcap_{q\in\ivp(n)}M_F(q)(\top)$, where $M_F$ is extended from edges to paths by composition.
+
+\commentout{
+is a function that maps supergraph edges to dataflow functions, and $M_F$ is extended to paths by composition\footnote{%
   Let $A$ be a set and $f:\,E^*\to(A\to A)$ a function from supergraph edges to functions on $A$.
@@
 }. The \textit{meet operator} $\sqcap$ is either union or intersection.
+}
 
-Without loss of generality, we will take meet to denote union.
+%Without loss of generality, we will take meet to denote union.
 It can be shown that any problem where meet is defined as intersection can be reformulated into an equivalent one where meet is defined as union~\cite{reps1995precise}.
@@
 \subsubsection{Overview of the IFDS Algorithm}\label{sec:overviewifds}
-Given an IFDS problem, for each node $n\in N^*$ the IFDS algorithm computes the \textit{meet-over-all-valid-paths} solution
-\begin{equation}
- \mvp{F}(n)=\bigsqcap_{q\in\ivp(n)}M_F(q)(\varnothing)\,.
-\end{equation}
+The key idea behind the IFDS algorithm is that it is possible to represent any distributive
+function $f$ from $2^D$ to $2^D$ by a \textit{representation relation} $R_f \subseteq 
+(D \cup \{0\})
+\times
+(D \cup \{0\})$. The representation relation can be visualized as a bipartite graph
+with edges from one instance of $D \cup \{0\}$ to another instance of $D \cup \{0\}$.
+The IFDS algorithm uses such graphs to efficiently represent both the input dataflow functions
+and the summary functions that it computes for called procedures.
+Specifically, the representation relation $R_f$ of a function $f$ is defined as:
+\[
+R_f=\{(\mathbf0,\,\mathbf0)\}\cup
+      \{(\mathbf0,\,d_j)\,|\,d_j\in f(\varnothing)\}\cup
+      \{(d_i,\,d_j)\,|\,d_j\in f(\{d_i\}) \setminus f(\varnothing)\}.
+\]
+%Each pair $(d_i,\,d_j)\in R_f$ corresponds to an edge $((n_1,\,d_i),\,(n_2,\,d_j))$ in the exploded supergraph.
 
+\commentout{
+Note that $R_f$ constructs pairs of dataflow facts so that
+\begin{itemize}
+  \item there is always an edge $(\mathbf0,\,\mathbf0)$ corresponding to the control-flow-graph edge;
+  \item if there is an edge $(\mathbf0,\,d_j)$, then there is no other edge leading to $d_j$; in particular, there is never an edge $(d_i,\,\mathbf0)$ where $d_i\ne\mathbf0$.
+\end{itemize}
+}
+
+\begin{example}\label{ex:flowfun}
+    Given $D=\{u,\,v,\,w\}$ and $f(S) = S\setminus\{v\} \cup \{u\}$,
+    the representation relation 
+  %The representation relation $R_f$ for a set of data-flow facts 
+  %and dataflow function $f=\lambda S\,.\,S\setminus\{v\}\cup\{u\}$ looks as follows:
+  $
+    R_f=\{(\mathbf0,\,\mathbf0),\,(\mathbf0,\,u),\,(w,\,w)\}
+$, which can be visualized with the following graph:
+   \begin{center}
+    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
+\begin{tikzpicture}[>=stealth,on grid, auto]
+    \node [n,label=$\mathbf{0}$] (zero){};
+    \node [n,] (zero_) [below=\edge of zero] {};
+    \node [n,label=$u$] (u) [right=\nd of zero] {};
+    \node [n,] (u_) [below=\edge of u] {};
+    \node [n,label=$v$] (v) [right=\nd of u] {};
+    \node [n,] (v_) [below=\edge of v] {};
+    \node [n,label=$w$] (w) [right=\nd of v] {};
+    \node [n,] (w_) [below=\edge of w] {};
+    \path[->](zero) edge (zero_);
+    \path[->](zero) edge (u_);
+    \path[->](w) edge (w_);
+  \end{tikzpicture}
+  \end{center}
+\end{example}
+
+The representation relation decomposes a flow function into functions
+(edges) that operate on each fact individually. This is possible due
+to distributivity: applying the flow function to a set of facts is
+equivalent to applying it on each fact individually and
+taking the union of the results.
+
+The meet of two functions can be computed as simply the union of their representation
+functions: $R_{f\sqcap f'} = R_f \cup R_{f'}$. The composition of two functions can be
+computed by combining their representation graphs, merging the range nodes of the
+first function with the corresponding domain nodes of the second function, and finding
+paths in the resulting graph.
+
+\commentout{
+The representation relation allows us to compactly represent the composition and meet operations which are required for the IFDS algorithm.
+
+For two representation relations $R_{f_1},\,R_{f_2}$, the composition and meet operations are defined as follows:
+\begin{align}
+  R_{f_1}\circ R_{f_2}&=\{(d_1,\,d_3)\ |\ \exists d_2:\ (d_1,\,d_2)\in R_{f_1},\,(d_2,\,d_3)\in R_{f_2}\}\,.
+\intertext{and}
+  R_{f_1}\sqcap R_{f_2}&=R_{f_1}\cup R_{f_2}\,.
+\end{align}
+
+The representation relation distributes over composition and meet:
+\begin{align}
+  R_{f_1}\circ R_{f_2}=R_{f_1\circ f_2}\,,\qquad
+\text{and}\qquad
+  R_{f_1}\sqcap R_{f_2}=R_{f_1\sqcap f_2}\,.
+\end{align}
+}
+
+%On the exploded graph, the composition of two functions is represented by the paths that are formed when the exploded-graph edges are combined.
+\otodo{The example used to say $R_f \circ R_g$, but I believe it showed $R_g \circ R_f$. I fixed it, but please check that this is correct.}
+
+\begin{example}
+    If $g(S)=S\setminus\{w\}$ and $f(S) = S\setminus\{v\} \cup \{u\}$, then
+    $
+    R_g\circ R_f=\{(\mathbf0,\,\mathbf0),\,(\mathbf0,\,u)\},
+    $
+  as illustrated in the following graph:
+    \begin{center}
+    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
+\begin{tikzpicture}[>=stealth,on grid, auto]
+    \node [n,label=$\mathbf{0}$] (zero){};
+    \node [n] (zero_) [below=\edge of zero] {};
+    \node [n,label=$u$] (u) [right=\nd of zero] {};
+    \node [n] (u_) [below=\edge of u] {};
+    \node [n,label=$v$] (v) [right=\nd of u] {};
+    \node [n] (v_) [below=\edge of v] {};
+    \node [n,label=$w$] (w) [right=\nd of v] {};
+    \node [n] (w_) [below=\edge of w] {};
+    \node [n] (zero__) [below=\edge of zero_] {};
+    \node [n] (u__) [below=\edge of u_] {};
+    \node [n] (v__) [below=\edge of v_] {};
+    \node [n] (w__) [below=\edge of w_] {};
+
+    \path[->](zero) edge node[left] {$R_f$} (zero_);
+    \path[->](zero) edge (u_);
+    \path[->](w) edge (w_);
+    \path[->](zero_) edge node[left] {$R_g$} (zero__);
+    \path[->](u_) edge (u__);
+    \path[->](v_) edge (v__);
+
+    \node [n,label=$\mathbf{0}$] (zeroC) [below right= .5\edge and 3.5\dist of w] {};
+    \node [n] (zeroC_) [below=\edge of zeroC] {};
+    \node [n,label=$u$] (uC) [right=\nd of zeroC] {};
+    \node [n] (uC_) [below=\edge of uC] {};
+    \node [n,label=$v$] (vC) [right=\nd of uC] {};
+    \node [n] (vC_) [below=\edge of vC] {};
+    \node [n,label=$w$] (wC) [right=\nd of vC] {};
+    \node [n] (wC_) [below=\edge of wC] {};
+
+    \path[->](zeroC) edge node[left] {$R_g\circ R_f$} (zeroC_);
+    \path[->](zeroC) edge (uC_);
+  \end{tikzpicture}
+  \end{center}
+\end{example}
+
+Composition of two distributive
+functions $f$ and $f'$ corresponds to finding reachable nodes in a graph composed from their representation
+relations $R_f$ and $R_{f'}$. Therefore, evaluating the composed dataflow function for a control
+flow path corresponds to finding reachable nodes in a graph composed from the representation relations
+of the dataflow functions for individual instructions.
+
+It is this graph of representation relations that the IFDS algorithm operates on.
+In this graph, called the \textit{exploded supergraph}, each node is a pair $(n,d)$, where
+$n\in N^*$ is a node of the control-flow supergraph and $d$ is an element of $D\cup\{0\}$.
+For each edge $(n \to n') \in E^*$, the exploded supergraph contains a set of edges
+$(n,d_i) \to (n',d_j)$, which form the representation relation of the dataflow function
+$M_F(n \to n')$. The IFDS algorithm finds all exploded supergraph edges that are reachable by
+\textit{realizable} paths in the exploded supergraph. A path
+is \textit{realizable} if its projection to the (non-exploded) supergraph is a valid
+path (i.e. if it is of the form $(n_0, d_0) \to (n_1,d_1) \to \cdots \to (n_m,d_m)$
+and $n_0 \to n_1 \to \cdots \to n_m$ is a valid path).
+
+\commentout{
 To compute the meet-over-all-valid-paths solution, each node in the control-flow supergraph is paired with a \textit{fact} $d\in D\cup\{\mathbf0\},\,\mathbf0\notin D$, yielding the nodes $N^\#$ of the \textit{exploded supergraph} $G^\#=(N^\#,\,E^\#)$.
@@
 \end{example}}
+}
 \begin{example}
@@
 
-%\subsubsection{Flow Functions}\label{sec:flowfunifds}
-The flow functions $F\subseteq 2^D\to2^D$ allow us to establish the edges in the exploded supergraph.
-
-Given a control-flow-graph edge $e=(n_1,\,n_2)\in E^*$ and a distributive dataflow function $f=M(e)$, the \textit{representation relation} $R_f:\,(D\cup\{\mathbf0\})\times (D\cup\{\mathbf0\})$ of $f$ is defined as
-\[
-  R_f=\{(\mathbf0,\,\mathbf0)\}\cup
-      \{(\mathbf0,\,d_j)\,|\,d_j\in f(\varnothing)\}\cup
-      \{(d_i,\,d_j)\,|\,d_j\in f(\{d_i\}),\,d_j\notin f(\varnothing)\}.
-\]
-Each pair $(d_i,\,d_j)\in R_f$ corresponds to an edge $((n_1,\,d_i),\,(n_2,\,d_j))$ in the exploded supergraph.
-
-Note that $R_f$ constructs pairs of dataflow facts so that
-\begin{itemize}
-  \item there is always an edge $(\mathbf0,\,\mathbf0)$ corresponding to the control-flow-graph edge;
-  \item if there is an edge $(\mathbf0,\,d_j)$, then there is no other edge leading to $d_j$; in particular, there is never an edge $(d_i,\,\mathbf0)$ where $d_i\ne\mathbf0$.
-\end{itemize}
-
-\begin{example}\label{ex:flowfun}
-  The representation relation $R_f$ for a set of data-flow facts $D=\{u,\,v,\,w\}$ and dataflow function $f=\lambda S\,.\,S\setminus\{v\}\cup\{u\}$ looks as follows:
-  \[
-    R_f=\{(\mathbf0,\,\mathbf0),\,(\mathbf0,\,u),\,(w,\,w)\}.
-  \]
-
-The corresponding exploded-graph edges are shown below.
-   \begin{center}
-    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
-\begin{tikzpicture}[>=stealth,on grid, auto]
-    \node [n,label=$\mathbf{0}$] (zero){};
-    \node [n,] (zero_) [below=\edge of zero] {};
-    \node [n,label=$u$] (u) [right=\nd of zero] {};
-    \node [n,] (u_) [below=\edge of u] {};
-    \node [n,label=$v$] (v) [right=\nd of u] {};
-    \node [n,] (v_) [below=\edge of v] {};
-    \node [n,label=$w$] (w) [right=\nd of v] {};
-    \node [n,] (w_) [below=\edge of w] {};
-    \path[->](zero) edge (zero_);
-    \path[->](zero) edge (u_);
-    \path[->](w) edge (w_);
-  \end{tikzpicture}
-  \end{center}
-\end{example}
-
-The representation relation lets us decompose a flow function into functions that operate on each fact individually.
-This is possible due to distributivity: we can apply the flow function on each single fact and take the union of the results, rather than applying the function to the union of the facts.
-
-The representation relation allows us to compactly represent the composition and meet operations which are required for the IFDS algorithm.
-
-For two representation relations $R_{f_1},\,R_{f_2}$, the composition and meet operations are defined as follows:
-\begin{align}
-  R_{f_1}\circ R_{f_2}&=\{(d_1,\,d_3)\ |\ \exists d_2:\ (d_1,\,d_2)\in R_{f_1},\,(d_2,\,d_3)\in R_{f_2}\}\,.
-\intertext{and}
-  R_{f_1}\sqcap R_{f_2}&=R_{f_1}\cup R_{f_2}\,.
-\end{align}
-
-The representation relation distributes over composition and meet:
-\begin{align}
-  R_{f_1}\circ R_{f_2}=R_{f_1\circ f_2}\,,\qquad
-\text{and}\qquad
-  R_{f_1}\sqcap R_{f_2}=R_{f_1\sqcap f_2}\,.
-\end{align}
-
-On the exploded graph, the composition of two functions is represented by the paths that are formed when the exploded-graph edges are combined.
-
-\begin{example}
-  If $g=\lambda S\,.\,S\setminus\{w\}$ and $f$ is defined as in example~\ref{ex:flowfun}, then
-  \[
-    R_f\circ R_g=\{(\mathbf0,\,\mathbf0),\,(\mathbf0,\,u)\},
-  \]
-  as illustrated by the corresponding exploded graph edges:
-    \begin{center}
-    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
-\begin{tikzpicture}[>=stealth,on grid, auto]
-    \node [n,label=$\mathbf{0}$] (zero){};
-    \node [n] (zero_) [below=\edge of zero] {};
-    \node [n,label=$u$] (u) [right=\nd of zero] {};
-    \node [n] (u_) [below=\edge of u] {};
-    \node [n,label=$v$] (v) [right=\nd of u] {};
-    \node [n] (v_) [below=\edge of v] {};
-    \node [n,label=$w$] (w) [right=\nd of v] {};
-    \node [n] (w_) [below=\edge of w] {};
-    \node [n] (zero__) [below=\edge of zero_] {};
-    \node [n] (u__) [below=\edge of u_] {};
-    \node [n] (v__) [below=\edge of v_] {};
-    \node [n] (w__) [below=\edge of w_] {};
-
-    \path[->](zero) edge node[left] {$R_f$} (zero_);
-    \path[->](zero) edge (u_);
-    \path[->](w) edge (w_);
-    \path[->](zero_) edge node[left] {$R_g$} (zero__);
-    \path[->](u_) edge (u__);
-    \path[->](v_) edge (v__);
-
-    \node [n,label=$\mathbf{0}$] (zeroC) [below right= .5\edge and 3.5\dist of w] {};
-    \node [n] (zeroC_) [below=\edge of zeroC] {};
-    \node [n,label=$u$] (uC) [right=\nd of zeroC] {};
-    \node [n] (uC_) [below=\edge of uC] {};
-    \node [n,label=$v$] (vC) [right=\nd of uC] {};
-    \node [n] (vC_) [below=\edge of vC] {};
-    \node [n,label=$w$] (wC) [right=\nd of vC] {};
-    \node [n] (wC_) [below=\edge of wC] {};
-
-    \path[->](zeroC) edge node[left] {$R_f\circ R_g$} (zeroC_);
-    \path[->](zeroC) edge (uC_);
-  \end{tikzpicture}
-  \end{center}
-\end{example}
-
 \mtodo{We never use the interpretation function, so I deleted it, too}
@@
 
-We presented an overview of the IFDS analysis. IFDS problems are transformed into IDE problems by the correlated-calls analysis. The IDE framework is described in the next section.
+A practical implementation of the IFDS algorithm generally takes as input a representation of the
+exploded supergraph edges $E^\sharp$ instead of explicit dataflow functions $M_F$. This is convenient because
+the two are equivalent in expressiveness, and because the IFDS algorithm works internally with the exploded
+supergraph. More specifically, the input generally provides a function with signature
+$f: N^* \times D \times N^* \to 2^D$. Given a (non-exploded) supergraph edge $n \to n'$ and a dataflow fact $d$,
+$f(n,d,n')$ returns the set of all $d'$ such that the exploded supergraph contains the edge $(n,d) \to (n',d')$.
+For convenience, the function $f$ can be split up into separate functions that handle the cases when
+the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.
+
+%We presented an overview of the IFDS analysis. IFDS problems are transformed into IDE problems by the correlated-calls analysis. The IDE framework is described in the next section.
 

### 2014-12-09 content/intro.tex
related work

@@
 programming tools, and computer security, and many other areas.
-Data-flow analyses operate on \textit{control-flow graphs} (CFGs)%
+Data-flow analyses operate on \textit{control-flow graphs} (CFGs)
 \mtodo{If we introduce this abbreviation, should we replace the uses of
@@
 algorithm for computing solutions to finite distributive data-flow problems such 
-as reaching definitions, available expressions, and taint analysis. A distinguishing 
+as reaching definitions, available expressions, and taint analysis.
+\mtodo{Should we include any references here for people who don't know what these analyses refer to?}
+\mtodo{We should define somewhere what taint analysis is, since it's currently
+commented out.}
+A distinguishing 
 characteristic of IFDS is that it avoids infeasible interprocedural paths in which calls 

### 2014-12-09 content/related.tex
related work

@@
 IFDS is a version of the functional approach to data-flow analysis developed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.
+\commentout{
 Their algorithm is based on computing \textit{summary functions} that return the data-flow value at the end of a procedure, given the data-flow value at the start of the procedure.
@@
 However, the IFDS algorithm is more general than Sharir's and Pnueli's algorithm in that it can handle programs containing local variables and parameters in recursive methods.
+}
+IFDS has been used to encode a variety of data-flow problems, for~example, typestate analysis%
+\commentout{(determining which operations can be performed on an object at a given program point)}~\cite{naeem2008typestate,DBLP:conf/pldi/ZhangMGNY14} or shape analysis%
+\commentout{(detecting errors and validating properties of programs at compile time)}
+~\cite{DBLP:conf/birthday/KreikerRRSWY13}.
+IFDS has been broadly used~\cite{DBLP:conf/pldi/ArztRFBBKTOM14,tripp2009taj} and extended~\cite{DBLP:conf/sigsoft/LerchHBM14} to solve taint-analysis problems.
 
-IFDS has been used to encode a variety of data-flow problems.
-More complex examples of applications include typestate analysis (determining which operations can be performed on an object at a given program point)~\cite{naeem2008typestate} or shape analysis (detecting errors and validating properties of programs at compile time)~\cite{DBLP:conf/birthday/KreikerRRSWY13}.
+IFDS is implemented for two popular static-analysis frameworks for Java bytecode, the T.J.~Watson Libraries for~Analysis (WALA)~\cite{fink2012wala} and Heros~\cite{bodden2012inter}.
 
-IFDS is implemented for two popular static-analysis frameworks, the T.J. Watson Libraries for Analysis (WALA)~\cite{fink2012wala} and Soot~\cite{vallee1999soot}.
-
+\commentout{
 WALA is a framework for static analysis on Java bytecode developed by the IBM T.J.~Watson Research Center.
@@
 SSA can make dataflow analysis simpler and more efficient~\cite{appel1998ssa}.
+}
 
-Work on improving the IFDS algorithm includes Practical Extensions by~N.\,Naeem and O.\,Lhot\'ak~\cite{naeem2010pei}.
-Their paper presents four extensions to the IFDS algorithm.
-Two of the extensions improve the efficiency of the IFDS analysis for certain classes of IFDS problems.
-Another extension widens the class of problems applicable for the IFDS analysis.
-However, those extensions do not affect the precision of IFDS problems.
+Work on improving the IFDS algorithm includes the Practical Extensions to the IFDS algorithm~\cite{naeem2010pei}.
+\commentout{The paper presents four extensions to the IFDS algorithm.}
+Two of the four extensions improve the efficiency of the IFDS analysis for certain classes of IFDS problems. Another extension widens the class of problems applicable for the IFDS analysis. 
+\commentout{However, those extensions do not affect the precision of IFDS problems.}
 Our analysis, in contrast, does not improve the efficiency or generality of IFDS, but it allows us to solve IFDS problems more precisely.
-
 The fourth extension is targeted towards programs that are represented in SSA form.
@@
 
+\commentout{
 The correlated-calls analysis improves the precision of a data-flow analysis by eliminating a special type of infeasible paths.
 This is similar to the idea of context-sensitive analysis: just as a context-sensitive analysis eliminates infeasible paths from the end of a procedure to the call sites that do not match the given procedure call, the correlated-calls analysis eliminates infeasible paths caused by correlated method calls.
+}
 

### 2014-12-09 content/impl.tex

@@
 
+  \commentout{
 \otodo{The following definitions are very general, and not related to the transformation.
@@
   If the call site is polymorphic, then $\tau(s_\mathcal F,\,f)\subset T'$, since some types $t\in T'$ cause dispatch to a method other than $f$.
+  }
 
@@
 \subsection{Defining IFDS and IDE Problems}
-In Section~\ref{sec:bg}, we defined what IFDS and IDE problems are, their applications, and their constraints. In this section, we describe how to create instances of IFDS and IDE problems.
+%In Section~\ref{sec:bg}, we defined what IFDS and IDE problems are, their applications, and their constraints. In this section, we describe how to create instances of IFDS and IDE problems.
 
+\commentout{
 \subsubsection{Defining an IFDS Problem}\label{sec:ifdsdef}
@@
 Then there is an edge $(n_1,\,d_1),\,(n_2,\,d_2)\in E^\#$.
+}
 
@@
 %Let $P=(G^\#)$ be an IFDS problem and $Q=(G^\#,\,\edgefn)$ an IDE problem obtained by a conversion from $P$.
-\otodo{Here, you defined the output of a transformation as just G\# and an edge function. Later, you also include the lattice. Should we include the lattice here?}
 Let $G^\#$ be the exploded supergraph of an IFDS problem. A \emph{transformation}
-$\mathcal T:\ (G^\#)\to (G^\#,\,(\top,\,\bot),\,\edgefn)$
-converts it into an equivalent IDE problem with a two-point lattice. We consider two transformations:
+$\mathcal T:\ (G^\#)\to (G^\#,\,L,\,\edgefn)$
+converts it into an equivalent IDE problem. We consider two transformations:
 \begin{itemize}

### 2014-12-10 content/background.tex
complete pass squeezing background on IDE algorithm

@@
 the two are equivalent in expressiveness, and because the IFDS algorithm works internally with the exploded
-supergraph. More specifically, the input generally provides a function with signature
+supergraph. More specifically, the input generally provides a function
 $f: N^* \times D \times N^* \to 2^D$. Given a (non-exploded) supergraph edge $n \to n'$ and a dataflow fact $d$,
@@
 \subsection{IDE}\label{sec:bgide}
+\commentout{
 There exists an entire class of data-flow problems that cannot be formulated as IFDS problems.
@@
 Additionally, for each program point, the algorithm computes an \textit{environment} $\textsf{Env}(D,\,L)$, where data-flow facts are mapped to values of a lattice $L$.
+}
 
+The IDE algorithm~\cite{sagiv1996precise} extends IFDS to
+\textit{inter-procedural} \textit{distributive} \textit{environment}
+problems. An \textit{environment} problem is an analysis whose dataflow
+lattice is the lattice $\textsf{Env}(D,L)$ of maps from a finite set $D$ to a meet semilattice
+$L$ of finite height, ordered pointwise. Like IFDS, IDE requires the dataflow functions to be distributive.
+
+\commentout{
 \begin{mdelete}
@@
 \end{mdelete}
+}
 
-Formally, an IDE problem is defined as a four-tuple
-\begin{equation}
-  (G^*,\,D,\,L,\,M_\textsf{Env})\,,
-\end{equation}
-where $G^*$ is a control-flow supergraph, $D$ is a set of data-flow facts, and $L$ is a meet semilattice
-with finite height. 
-Finally, $M_\textsf{Env}:\,E^*\to(\textsf{Env}(D,\,L)\to \textsf{Env}(D,\,L))$ is a function from the edges of the control-flow supergraph to distributive \textit{environment transformers}.
-$M_\textsf{Env}$ is extended to paths by composition.
+The input to the IDE algorithm is
+  $(G^*,\,D,\,L,\,M_\textsf{Env})$
+where $G^*$ is a control-flow supergraph,
+$D$ is a set of data-flow facts,
+$L$ is a meet semilattice of finite height,
+and $M_\textsf{Env}:\,E^*\to(\textsf{Env}(D,\,L)\to \textsf{Env}(D,\,L))$ assigns a dataflow function
+to each supergraph edge.
 
-Given an IDE problem, for each node $n\in N^*$ and fact $d\in D$, the IDE algorithm computes the meet-over-all-valid-paths solution
-\begin{equation}\label{eq:mvpdef}
-  \mvp{\textsf{Env}}(n,\,d)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\Omega)(d)\,,
-\end{equation}
-where $M_\textsf{Env}$ is extended to paths by composition and
+The output of the IDE algorithm is, for each node $n$ in the supergraph,
+the \textit{meet-over-all-valid-paths} solution
+  $\mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top)$,
+where $M_\textsf{Env}$ is extended from edges to paths by composition.
+
+\commentout{
+and
 \begin{equation}
@@
 is the top element in the environment lattice~$\mathsf{Env}(D,\,L)$.
+}
+
 \commentout{
@@
 
+\commentout{
 \subsubsection{Environment Transformers}
@@
 for all $l\in L$.
+}
 
-In IDE problems, the auxiliary fact analogous to $\mathbf0$ in IFDS is denoted as $\Lambda$.
+%In IDE problems, the auxiliary fact analogous to $\mathbf0$ in IFDS is denoted as $\Lambda$.
 
@@
 
+\commentout{
 In this way, each edge in the exploded graph is labeled with a micro function.
 The mapping from exploded-graph edges to the corresponding micro functions is stored in \textit{edge functions},  denoted as \textsf{EdgeFn}$:\,E^\#\to(L\to L)$.
+}
 
 \subsubsection{Overview of the IDE Algorithm}\label{sec:ideoverview}
+Just as any distributive function from $2^D$ to $2^D$ can be represented with a
+representation relation, it is also possible to represent any distributive functions from
+$\textsf{Env}(D,L)$
+to
+$\textsf{Env}(D,L)$
+with a \textit{pointwise representation}. A pointwise representation is a bipartite graph
+with the same nodes~\footnote{The IDE literature uses the symbol $\Lambda$ for the node that
+    is denoted $\mathbf0$ in the IFDS literature.}
+and edges as a representation relation, except that each edge is labelled
+with a \textit{micro-function}, which is a function from $L$ to $L$. 
+\commentout{
+The pointwise representation of an environment transformer 
+$t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
+is defined as
+\newcommand{\microedge}[3]{#1\xrightarrow{#3}#2}
+\begin{align*}
+    R_t =& \{ \microedge{\Lambda}{\Lambda}{\lambda l.l} \} \cup
+    \{\microedge{\Lambda}{d_j}{\lambda l.t(\Omega)(d_j)} \mid d_j \in D\}\\
+    &\cup
+    \{\microedge{d_i}{d_j}{\lambda l.t(\Omega[d_i\to l])(d_j)} \mid d_i, d_j \in D\}.
+\end{align*}
+}
+Let $\Omega = \lambda d.\top$ be the environment that maps every element of $D$ to $\top$.
+Thanks to distributivity, every environment transformer 
+$t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
+can be decomposed into its effect on $\Omega$ and on a set of environments $\Omega[d_i\to l]$
+that map every element except one ($d_i$) to $\top$:
+\[
+    t(m)(d_j) = \lambda l. t(\Omega)(d_j) \sqcap \bigsqcap_{d_i\in D} \lambda l. t(\Omega[d_i\to l])(d_j).
+\]
+The functions $\lambda l. \cdots$ in this decomposition are the micro-functions that
+appear on the edges of the pointwise representation edges from $\Lambda$ to each $d_j$ and from
+each $d_i$ to each $d_j$.%
+\footnote{The IDE paper defines a more complicated but equivalent set of micro-functions
+that eliminate some duplication of computation.}
+The absence of an edge in the pointwise representation from some $d_i$ to some $d_j$ is
+equivalent to an edge with micro-function $\lambda l.\top$.
+
+\otodo{Discuss the micro-functions in the example exploded supergraph in Figure 3.}
+
+The meet of two environment transformers $t_1, t_2$ can be computed by taking the union of the edges
+in their pointwise representations. When the same edge appears in the pointwise representations of
+both $t_1$ and $t_2$, the micro-function for that edge in $t_1 \sqcap t_2$ is the meet of the
+micro-functions for that same edge in $t_1$ and in $t_2$.
+
+The composition of two environment transformers can be computed by combining their pointwise
+representation graphs in the same way as IFDS representation relations, and 
+computing the composition of the micro-functions appearing along each path in the resulting graph.
+
+The IDE algorithm operates on the same exploded supergraph as the IFDS algorithm
+(except that the edges are labelled with micro-functions). For each pair $(n,d)$ of
+node and fact, the algorithm computes a micro-function equal to the meet of the micro-functions
+of all the realizable paths from the program entry point to the pair.
+
+In order to do this efficiently, the IDE algorithm requires a representation of micro-functions
+that is general enough to express the basic micro-functions of the dataflow functions for individual
+instructions, and that supports computing the meet and composition of micro-functions.
+
+Similar to the IFDS algorithm, a practical implementation of the IDE algorithm requires
+the input dataflow functions to be provided in their pointwise representation
+as exploded supergraph edges labelled with micro-functions. Specifically,
+the input is generally provided as a function $f: N^* \times D \times N^* \to (D \to F)$,
+where $F$ is the set of representations of micro-functions from $L$ to $L$.
+Given a (non-exploded) supergraph edge $n \to n'$ and a dataflow fact $d$,
+$f(n,d,n')$ returns a map that gives for each fact $d'$ the micro-function $f$
+that appears on the exploded supergraph edge $(n,d) \to (n',d')$.
+Like in the IFDS algorithm, the function $f$ can be split up into separate functions that handle the cases when
+the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.
+
+\otodo{In the next section, we talk about \textsf{EdgeFn}, which is inconsistent with how
+    we define the functions to be implemented here. We need to make the two sections consistent,
+    one way or the other.}
+
+\commentout{
 Given a labeled exploded supergraph, the IDE algorithm computes the environments for all nodes in the control-flow graph.
@@
 The next section describes how this is done.
+}

### 2014-12-10 content/background.tex
comments

@@
 the input dataflow functions to be provided in their pointwise representation
-as exploded supergraph edges labelled with micro-functions. Specifically,
+as exploded supergraph edges labelled with micro-functions.
+\mtodo{Should we cite the ``Practical extensions'' paper here that talks about the on-demand IFDS algorithm?}
+Specifically,
 the input is generally provided as a function $f: N^* \times D \times N^* \to (D \to F)$,

### 2014-12-10 content/impl.tex
complete pass squeezing background on IDE algorithm
comments

@@
 
+\commentout{
 \otodo{incorporate into previous section}
@@
 
-\commentout{
 \subsubsection{Defining an IFDS Problem}\label{sec:ifdsdef}
@@
 Then there is an edge $(n_1,\,d_1),\,(n_2,\,d_2)\in E^\#$.
-}
 
@@
 where each edge of the exploded supergraph corresponds to a micro function.
+}
 
@@
 where $d_1(e)$ is the source fact of an edge $e$ and $d_2(e)$ is its target fact. 
-At a ``diagonal'' edge from a $\Lambda$-fact to a non-$\Lambda$-fact
+At a~``diagonal'' edge from a $\Lambda$-fact to a non-$\Lambda$-fact
 $d$, the micro function returns $\bot$
 to make
-the fact $d$ reachable. All other micro-functions are the identity.
+the fact $d$ reachable. All other micro-functions are the identity\mtodo{``the identity function'' or is it okay ot just say ``the identity''?}.
 The equivalence transformation is thus defined as:
@@
 where $R$ is the set of receivers and $T$ is the set of all types.
-For each receiver $r$, the map gives an overapproximation of the possible
+For each receiver~$r$, the map gives an overapproximation of the possible
 runtime types of $r$.
@@
 a set of facts $d$ that may be reached at $n$. The result of an IDE analysis
-pairs each such fact $d$ with a lattice element $\ell$. Formally,
+pairs each such fact~$d$ with a lattice element $\ell$. Formally,
 for an IFDS problem $P$, the result $\result_{\text{IFDS}}$ has type
@@
     \]
-\end{lemma}
+\end{lemma}\mtodo{Should one of the sides of the equation be $\denote{\dots\circ\dots}$? Same for next lemma.}
 \otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}

### 2014-12-10 content/background.tex
remove obsolete comments

@@
 This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.}
-\mtodo{I'm not saying any more that IFDS is a version of Sharir\&Pnueli's functional approach.}
-\mtodo{I also removed the comparison of IFDS with other algorithms. I'm not pointing out the benefits of IFDS any more, so we might fail to show the importance of the algorithm.}
 The IFDS framework is applicable to \textit{inter-procedural} data flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
@@
 
-\mtodo{We never use the interpretation function, so I deleted it, too}
 \commentout{

### 2014-12-11 content/impl.tex
fix composition and meet lemmas
supergraph figure

@@
-\begin{figure}%
-  \centering
-    \tikzstyle{supergraph}=[
-      fill=greyblue,
-      rounded corners,
-      font=\footnotesize,
-      align=right,
-      text=charcoal,
-      drop shadow={ashadow, color=greyblue}
-    ]
-    \tikzstyle{supergraph_y}=[
-      fill=bisque,
-      rounded corners,
-      font=\footnotesize,
-      align=left,
-      text=charcoal,
-      drop shadow={ashadow, color=greyblue}
-    ]
-    \tikzstyle{supergraph_f}=[
-      fill=lightsalmonpink,
-      rounded corners,
-      font=\footnotesize,
-      align=left,
-      text=charcoal,
-      drop shadow={ashadow, color=greyblue}
-    ]
-    \tikzstyle{description}=[fill=white]
-    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
-    \tikzstyle{arrowtext}=[font=\tiny,color=black,above]
+\input{figures/fig-cc_edge_fn_example}
 
-\hspace*{-10pt}
-\begin{tikzpicture}
-\scalebox{.8}{
-% main method nodes
-    \node [supergraph] (st_main) {\textsf{start}$_{\texttt{main}}$};
-    \node [supergraph] (asgn_a) [below = \dist of st_main.south east, anchor=east] {\texttt{a = args==null\,?}\\\texttt{new\,A()\,:\,new\,B()}};
-    \node [supergraph] (call_foo) [below = \dist of asgn_a.south east, anchor=east] {\textsf{call}$_\texttt{foo}$};
-    \node [supergraph] (return_foo) [below = \dist of call_foo.south east,anchor=east] {\textsf{return}$_\texttt{foo}$\\\texttt{v = a.foo()}};
-    \node [supergraph] (call_bar) [below = \dist of return_foo.south east, anchor=east] {\textsf{call}$_\texttt{bar}$};
-    \node [supergraph] (return_bar) [below = \dist of call_bar.south east, anchor=east] {\textsf{return}$_\texttt{bar}$};
-    \node [supergraph] (end_main) [below = \dist of return_bar.south east, anchor=east] {\textsf{end}$_{\texttt{main}}$};
-
-    \node [n,label=$\Lambda$] (st_main_z) [right=\nd of st_main.east] {};
-    \node [n,label=\texttt{v}] (st_main_v) [right=\nd of st_main_z] {};
-    \node [n] (asgn_a_z) [right=\nd of asgn_a.east] {};
-    \node [n] (call_foo_z) [right=\nd of call_foo.east] {};
-    \node [n] (return_foo_z) [right=\nd of return_foo.east] {};
-    \node [n] (call_bar_z) [right=\nd of call_bar.east] {};
-    \node [n] (return_bar_z) [right=\nd of return_bar.east] {};
-    \node [n] (end_main_z) [right=\nd of end_main.east] {};
-    \node [n] (asgn_a_v) [right=\nd of asgn_a_z] {};
-    \node [n] (call_foo_v) [right=\nd of call_foo_z] {};
-    \node [n] (return_foo_v) [right=\nd of return_foo_z] {};
-    \node [n] (call_bar_v) [right=\nd of call_bar_z] {};
-    \node [n] (return_bar_v) [right=\nd of return_bar_z] {};
-    \node [n] (end_main_v) [right=\nd of end_main_z] {};
-% main method edges
-    \path[->](st_main_z) edge (asgn_a_z);
-    \path[->](asgn_a_z) edge (call_foo_z);
-    \path[->](call_foo_z) edge (return_foo_z);
-    \path[->](return_foo_z) edge (call_bar_z);
-    \path[->](call_bar_z) edge (return_bar_z);
-    \path[->](return_bar_z) edge (end_main_z);  
-    \path[->](st_main_v) edge (asgn_a_v);
-    \path[->](asgn_a_v) edge (call_foo_v);
-    \path[->](call_foo_v) edge (return_foo_v);
-    \path[->](return_foo_v) edge (call_bar_v);
-    \path[->](call_bar_v) edge (return_bar_v);
-    \path[->](return_bar_v) edge (end_main_v);
-
-%A.foo method nodes
-    \node [supergraph_y] (st_a_foo) [right = 6*\dist of st_main] {\textsf{start}$_{\texttt{A.foo}}$};
-    \node [supergraph_y] (return_secret) [below = \dist of st_a_foo.south west, anchor=west] {\texttt{return secret()}};
-    \node [supergraph_y] (end_a_foo) [below = \dist of return_secret.south west,anchor = west] {\textsf{end}$_\texttt{A.foo}$};
-
-    \node [n,label=$\psi$] (st_a_foo_p) [left=\nd of st_a_foo.west] {};
-    \node [n] (return_secret_p) [left=\nd of return_secret.west] {};
-    \node [n] (end_a_foo_p) [left=\nd of end_a_foo.west] {};
-    \node [n,label=$\Lambda$] (st_a_foo_z) [left=\nd of st_a_foo_p] {};
-    \node [n] (return_secret_z) [left=\nd of return_secret_p] {};
-    \node [n] (end_a_foo_z) [left=\nd of end_a_foo_p] {};
-%A.foo method edges
-    \path[->](st_a_foo_z) edge (return_secret_z); 
-    \path[->](return_secret_z) edge node[arrowtext,near start,above right=0.4cm and -.15cm,rotate=-60]{$\lambda m.\botcc$} (end_a_foo_z); 
-    \path[->,dashed](call_foo_z) edge [out=38,in=238]  (st_a_foo_z);
-    \path[->,dashed](end_a_foo_z) edge [out=200,in=43] (return_foo_z);
-    \path[->,dashed](end_a_foo_p) edge  [out=200,in=43] node[arrowtext,below,rotate=30]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (return_foo_v);
-    \path[->](st_a_foo_p) edge (return_secret_p); 
-    \path[->](return_secret_p) edge (end_a_foo_p);
-    \path[->](return_secret_z) edge (end_a_foo_p);
-
-%A.bar method nodes
-    \node [supergraph_y] (st_a_bar) [right = 6*\dist of st_a_foo] {\textsf{start}$_{\texttt{A.bar}}$};
-    \node [supergraph_y] (end_a_bar) [below = \dist of st_a_bar.south west,anchor = west] {\textsf{end}$_\texttt{A.bar}$};
-
-    \node [n,label=\texttt{s}] (st_a_bar_s) [left=\nd of st_a_bar.west] {};
-    \node [n,label=$\Lambda$] (st_a_bar_z) [left=\nd of st_a_bar_s] {};
-    \node [n] (end_a_bar_s) [left=\nd of end_a_bar.west] {};    
-    \node [n] (end_a_bar_z) [left=\nd of end_a_bar_s] {};
-%A.bar method edges
-    \path[->](st_a_bar_z) edge (end_a_bar_z);
-    \path[->,dashed](call_bar_z) edge [out=20,in=229] (st_a_bar_z);
-    \path[->,dashed](end_a_bar_z) edge [out=220,in=35] (return_bar_z);
-    \path[->](st_a_bar_s) edge (end_a_bar_s);
-    \path[->,dashed](call_bar_v) edge [out=20,in=230] node[arrowtext,near end,above left=-.1cm and -.15cm,rotate=36]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (st_a_bar_s);
-
-%B.foo method nodes
-    \node [supergraph_f] (st_b_foo) [right = 6*\dist of call_bar] {\textsf{start}$_{\texttt{B.foo}}$};
-    \node [supergraph_f] (return_not_secret) [below = \dist of st_b_foo.south west, anchor=west] {\texttt{return "not secret"}};
-    \node [supergraph_f] (end_b_foo) [below = \dist of return_not_secret.south west,anchor = west] {\textsf{end}$_\texttt{B.foo}$};
-
-    \node [n,label=$\Lambda$] (st_b_foo_z) [left=\nd of st_b_foo.west] {};
-    \node [n] (return_not_secret_z) [left=\nd of return_not_secret.west] {};
-    \node [n] (end_b_foo_z) [left=\nd of end_b_foo.west] {};
-
-%B.foo method edges
-    \path[->](st_b_foo_z) edge (return_not_secret_z); 
-    \path[->](return_not_secret_z) edge (end_b_foo_z); 
-    \path[->,dashed](call_foo_z) edge [out=-60,in=160,color=lightsalmonpink] (st_b_foo_z);
-    \path[->,dashed](end_b_foo_z) edge [out=145,in=-65,color=lightsalmonpink] (return_foo_z);
-
-%B.bar method nodes
-    \node [supergraph_f] (st_b_bar) [right = 6*\dist of st_b_foo] {\textsf{start}$_{\texttt{B.bar}}$};
-    \node [supergraph_f] (print) [below = \dist of st_b_bar.south west,anchor = west] {\texttt{print(s)}};
-    \node [supergraph_f] (end_b_bar) [below = \dist of print.south west,anchor = west] {\textsf{end}$_\texttt{B.bar}$};
-
-    \node [n,label=\texttt{s}] (st_b_bar_s) [left=\nd of st_b_bar.west] {};
-    \node [n] (print_s) [left=\nd of print.west] {};
-    \node [n] (end_b_bar_s) [left=\nd of end_b_bar.west] {};
-    \node [n,label=$\Lambda$] (st_b_bar_z) [left=\nd of st_b_bar_s] {};
-    \node [n] (print_z) [left=\nd of print_s] {};
-    \node [n] (end_b_bar_z) [left=\nd of end_b_bar_s] {};
-%B.bar method edges
-    \path[->](st_b_bar_z) edge (print_z);
-    \path[->](print_z) edge (end_b_bar_z);
-    \path[->](st_b_bar_s) edge (print_s);
-    \path[->](print_s) edge (end_b_bar_s);
-    \path[->,dashed](call_bar_z) edge [out=40,in=140,color=lightsalmonpink] (st_b_bar_z);
-    \path[->,dashed](call_bar_v) edge [out=20,in=160,color=lightsalmonpink] node[arrowtext,above right=-.4cm and .4cm,rotate=-10]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$} (st_b_bar_s);
-    \path[->,dashed](end_b_bar_z) edge [out=210,in=-40,color=lightsalmonpink] (return_bar_z);    
-}
-\end{tikzpicture}
-\caption[An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}]{An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}.
-All non-labeled edges are implicitly labeled with identity functions $\id$.
-The variable corresponding to an initial secret value is denoted as $\psi$.}%
-  \label{fig:cc_edgefn_example}%  
-  \end{figure}
 \mtodo{In Figure~\ref{fig:cc_edgefn_example}, should we say that $\psi$ corresponds to the function's return value?}
@@
     \[
-        \denote{\setpair{I}{U}} \circ \denote{\setpair{I'}{U'}}
+        \denote{\setpair{I}{U} \circ \setpair{I'}{U'}}
         = 
@@
     \]
-\end{lemma}\mtodo{Should one of the sides of the equation be $\denote{\dots\circ\dots}$? Same for next lemma.}
+\end{lemma}
 \otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}
@@
     \[
-        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
+        \denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}
         = 

### 2014-12-11 content/intro.tex
supergraph figure

@@
 by  Reps, Horwitz, and Sagiv \cite{reps1995precise} is a general data-flow analysis
-algorithm for computing solutions to finite distributive data-flow problems such 
+algorithm for computing solutions to standard finite distributive data-flow problems such 
 as reaching definitions, available expressions, and taint analysis.
-\mtodo{Should we include any references here for people who don't know what these analyses refer to?}
 \mtodo{We should define somewhere what taint analysis is, since it's currently

### 2014-12-11 figures/fig-transformation.tex
title

@@
     \node [problem] (ifds) {IFDS problem};
-    \node [problem] (equiv) [above right=0.3cm and .7\dist of ifds.east] {Equivalent IDE problem};
-    \node [problem] (ccide)[below=1.6cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
+    \node [problem] (equiv) [above right=0.5cm and .7\dist of ifds.east] {Equivalent IDE problem};
+    \node [problem] (ccide)[below=2cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
     \node [result] (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
-    \node [result] (ccres) [below=1.6cm of equivres.west,anchor=west] {Correlated-calls result};
+    \node [result] (ccres) [below=2cm of equivres.west,anchor=west] {Correlated-calls result};
     \node [result] (ifdsres) [right=\dist of equivres.east] {IFDS result};
@@
     \path[->] (ccres) edge node[above] {$\backCC$} (improved);
-    \path[->] (ccres) edge[out=25,in=210] node[above] {$\backEq$} (ifdsres);
-    \path[->] (ifds) edge[out=40,in=179] node[above] {$\transEq$} (equiv);
+    %\path[->] (ccres) edge[out=25,in=210] node[above] {$\backEq$} (ifdsres);
+    \path[->] (ifds) edge[out=42,in=179] node[above] {$\transEq$} (equiv);
     \path[->] (ifds) edge[out=-40,in=173] node[below] {$\transCC$} (ccide);
@@
     \path[->] (ccide) edge node[above]{$\result$} (ccres);
+    \path[->,dashed] (ifds) edge[out=-3,in=205] node[above]{$\result_{\text{IFDS}}$} (ifdsres);
 \end{tikzpicture}

### 2014-12-11 figures/fig-cc_edge_fn_example.tex
figures

\begin{figure}%
  \centering
    \tikzstyle{supergraph}=[
      fill=greyblue,
      rounded corners,
      font=\footnotesize,
      align=right,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_y}=[
      fill=bisque,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_f}=[
      fill=lightsalmonpink,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{description}=[fill=white]
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
    \tikzstyle{arrowtext}=[font=\tiny,color=black,above]

\hspace*{-10pt}
\begin{tikzpicture}
\scalebox{.8}{
% main method nodes
    \node [supergraph] (st_main) {\textsf{start}$_{\texttt{main}}$};
    \node [supergraph] (asgn_a) [below = \dist of st_main.south east, anchor=east] {\texttt{a = args==null\,?}\\\texttt{new\,A()\,:\,new\,B()}};
    \node [supergraph] (call_foo) [below = \dist of asgn_a.south east, anchor=east] {\textsf{call}$_\texttt{foo}$};
    \node [supergraph] (return_foo) [below = \dist of call_foo.south east,anchor=east] {\textsf{return}$_\texttt{foo}$\\\texttt{v = a.foo()}};
    \node [supergraph] (call_bar) [below = \dist of return_foo.south east, anchor=east] {\textsf{call}$_\texttt{bar}$};
    \node [supergraph] (return_bar) [below = \dist of call_bar.south east, anchor=east] {\textsf{return}$_\texttt{bar}$};
    \node [supergraph] (end_main) [below = \dist of return_bar.south east, anchor=east] {\textsf{end}$_{\texttt{main}}$};

    \node [n,label=$\Lambda$] (st_main_z) [right=\nd of st_main.east] {};
    \node [n,label=\texttt{v}] (st_main_v) [right=\nd of st_main_z] {};
    \node [n] (asgn_a_z) [right=\nd of asgn_a.east] {};
    \node [n] (call_foo_z) [right=\nd of call_foo.east] {};
    \node [n] (return_foo_z) [right=\nd of return_foo.east] {};
    \node [n] (call_bar_z) [right=\nd of call_bar.east] {};
    \node [n] (return_bar_z) [right=\nd of return_bar.east] {};
    \node [n] (end_main_z) [right=\nd of end_main.east] {};
    \node [n] (asgn_a_v) [right=\nd of asgn_a_z] {};
    \node [n] (call_foo_v) [right=\nd of call_foo_z] {};
    \node [n] (return_foo_v) [right=\nd of return_foo_z] {};
    \node [n] (call_bar_v) [right=\nd of call_bar_z] {};
    \node [n] (return_bar_v) [right=\nd of return_bar_z] {};
    \node [n] (end_main_v) [right=\nd of end_main_z] {};
% main method edges
    \path[->](st_main_z) edge (asgn_a_z);
    \path[->](asgn_a_z) edge (call_foo_z);
    \path[->](call_foo_z) edge (return_foo_z);
    \path[->](return_foo_z) edge (call_bar_z);
    \path[->](call_bar_z) edge (return_bar_z);
    \path[->](return_bar_z) edge (end_main_z);  
    \path[->](st_main_v) edge (asgn_a_v);
    \path[->](asgn_a_v) edge (call_foo_v);
    \path[->](call_foo_v) edge (return_foo_v);
    \path[->](return_foo_v) edge (call_bar_v);
    \path[->](call_bar_v) edge (return_bar_v);
    \path[->](return_bar_v) edge (end_main_v);

%A.foo method nodes
    \node [supergraph_y] (st_a_foo) [right = 6*\dist of st_main] {\textsf{start}$_{\texttt{A.foo}}$};
    \node [supergraph_y] (return_secret) [below = \dist of st_a_foo.south west, anchor=west] {\texttt{return secret()}};
    \node [supergraph_y] (end_a_foo) [below = \dist of return_secret.south west,anchor = west] {\textsf{end}$_\texttt{A.foo}$};

    \node [n,label=$\psi$] (st_a_foo_p) [left=\nd of st_a_foo.west] {};
    \node [n] (return_secret_p) [left=\nd of return_secret.west] {};
    \node [n] (end_a_foo_p) [left=\nd of end_a_foo.west] {};
    \node [n,label=$\Lambda$] (st_a_foo_z) [left=\nd of st_a_foo_p] {};
    \node [n] (return_secret_z) [left=\nd of return_secret_p] {};
    \node [n] (end_a_foo_z) [left=\nd of end_a_foo_p] {};
%A.foo method edges
    \path[->](st_a_foo_z) edge (return_secret_z); 
    \path[->](return_secret_z) edge node[arrowtext,near start,above right=0.4cm and -.15cm,rotate=-60]{$\lambda m.\botcc$} (end_a_foo_z); 
    \path[->,dashed](call_foo_z) edge [out=38,in=238]  (st_a_foo_z);
    \path[->,dashed](end_a_foo_z) edge [out=200,in=43] (return_foo_z);
    \path[->,dashed](end_a_foo_p) edge  [out=200,in=43] node[arrowtext,below,rotate=30]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (return_foo_v);
    \path[->](st_a_foo_p) edge (return_secret_p); 
    \path[->](return_secret_p) edge (end_a_foo_p);
    \path[->](return_secret_z) edge (end_a_foo_p);

%A.bar method nodes
    \node [supergraph_y] (st_a_bar) [right = 6*\dist of st_a_foo] {\textsf{start}$_{\texttt{A.bar}}$};
    \node [supergraph_y] (end_a_bar) [below = \dist of st_a_bar.south west,anchor = west] {\textsf{end}$_\texttt{A.bar}$};

    \node [n,label=\texttt{s}] (st_a_bar_s) [left=\nd of st_a_bar.west] {};
    \node [n,label=$\Lambda$] (st_a_bar_z) [left=\nd of st_a_bar_s] {};
    \node [n] (end_a_bar_s) [left=\nd of end_a_bar.west] {};    
    \node [n] (end_a_bar_z) [left=\nd of end_a_bar_s] {};
%A.bar method edges
    \path[->](st_a_bar_z) edge (end_a_bar_z);
    \path[->,dashed](call_bar_z) edge [out=20,in=229] (st_a_bar_z);
    \path[->,dashed](end_a_bar_z) edge [out=220,in=35] (return_bar_z);
    \path[->](st_a_bar_s) edge (end_a_bar_s);
    \path[->,dashed](call_bar_v) edge [out=20,in=230] node[arrowtext,near end,above left=-.1cm and -.15cm,rotate=36]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (st_a_bar_s);

%B.foo method nodes
    \node [supergraph_f] (st_b_foo) [right = 6*\dist of call_bar] {\textsf{start}$_{\texttt{B.foo}}$};
    \node [supergraph_f] (return_not_secret) [below = \dist of st_b_foo.south west, anchor=west] {\texttt{return "not secret"}};
    \node [supergraph_f] (end_b_foo) [below = \dist of return_not_secret.south west,anchor = west] {\textsf{end}$_\texttt{B.foo}$};

    \node [n,label=$\Lambda$] (st_b_foo_z) [left=\nd of st_b_foo.west] {};
    \node [n] (return_not_secret_z) [left=\nd of return_not_secret.west] {};
    \node [n] (end_b_foo_z) [left=\nd of end_b_foo.west] {};

%B.foo method edges
    \path[->](st_b_foo_z) edge (return_not_secret_z); 
    \path[->](return_not_secret_z) edge (end_b_foo_z); 
    \path[->,dashed](call_foo_z) edge [out=-60,in=160,color=lightsalmonpink] (st_b_foo_z);
    \path[->,dashed](end_b_foo_z) edge [out=145,in=-65,color=lightsalmonpink] (return_foo_z);

%B.bar method nodes
    \node [supergraph_f] (st_b_bar) [right = 6*\dist of st_b_foo] {\textsf{start}$_{\texttt{B.bar}}$};
    \node [supergraph_f] (print) [below = \dist of st_b_bar.south west,anchor = west] {\texttt{print(s)}};
    \node [supergraph_f] (end_b_bar) [below = \dist of print.south west,anchor = west] {\textsf{end}$_\texttt{B.bar}$};

    \node [n,label=\texttt{s}] (st_b_bar_s) [left=\nd of st_b_bar.west] {};
    \node [n] (print_s) [left=\nd of print.west] {};
    \node [n] (end_b_bar_s) [left=\nd of end_b_bar.west] {};
    \node [n,label=$\Lambda$] (st_b_bar_z) [left=\nd of st_b_bar_s] {};
    \node [n] (print_z) [left=\nd of print_s] {};
    \node [n] (end_b_bar_z) [left=\nd of end_b_bar_s] {};
%B.bar method edges
    \path[->](st_b_bar_z) edge (print_z);
    \path[->](print_z) edge (end_b_bar_z);
    \path[->](st_b_bar_s) edge (print_s);
    \path[->](print_s) edge (end_b_bar_s);
    \path[->,dashed](call_bar_z) edge [out=40,in=140,color=lightsalmonpink] (st_b_bar_z);
    \path[->,dashed](call_bar_v) edge [out=20,in=160,color=lightsalmonpink] node[arrowtext,above right=-.4cm and .4cm,rotate=-10]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$} (st_b_bar_s);
    \path[->,dashed](end_b_bar_z) edge [out=210,in=-40,color=lightsalmonpink] (return_bar_z);    
}
\end{tikzpicture}
\caption[An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}]{An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}. All non-labeled edges are implicitly labeled with identity functions $\id$. The variable corresponding to an initial secret value is denoted as $\psi$.}%
  \label{fig:cc_edgefn_example}%  
  \end{figure}

### 2014-12-11 figures/fig-examplesupergraph.tex
figures

\begin{figure}%
  \centering
    \tikzstyle{supergraph}=[
      fill=greyblue,
      rounded corners,
      font=\footnotesize,
      align=right,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_y}=[
      fill=bisque,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_f}=[
      fill=lightsalmonpink,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{description}=[fill=white]
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
    \tikzstyle{arrowtext}=[font=\tiny,color=black,above]

\hspace*{-10pt}
\begin{tikzpicture}
\scalebox{.8}{
% main method nodes
    \node [supergraph] (st_main) {\textsf{start}$_{\texttt{main}}$};
    \node [supergraph] (asgn_a) [below = \dist of st_main.south] {\texttt{a = args==null\,?}\\\texttt{new\,A()\,:\,new\,B()}};
    \node [supergraph] (call_foo) [below = \dist of asgn_a.south] {\textsf{call}$_\texttt{foo}$};
    \node [supergraph] (return_foo) [below = \dist of call_foo.south] {\textsf{return}$_\texttt{foo}$\\\texttt{v = a.foo()}};
    \node [supergraph] (call_bar) [below = \dist of return_foo.south] {\textsf{call}$_\texttt{bar}$};
    \node [supergraph] (return_bar) [below = \dist of call_bar.south] {\textsf{return}$_\texttt{bar}$};
    \node [supergraph] (end_main) [below = \dist of return_bar.south] {\textsf{end}$_{\texttt{main}}$};

% main method edges 
    \path[->] (st_main) edge (asgn_a);
    \path[->] (asgn_a) edge (call_foo);
    \path[->] (call_foo) edge (return_foo);
    \path[->] (return_foo) edge (call_bar);
    \path[->] (call_bar) edge (return_bar);
    \path[->] (return_bar) edge (end_main);

%A.foo method nodes
    \node [supergraph_y] (st_a_foo) [right = 5*\dist of st_main] {\textsf{start}$_{\texttt{A.foo}}$};
    \node [supergraph_y] (return_secret) [below = \dist of st_a_foo.south] {\texttt{return secret()}};
    \node [supergraph_y] (end_a_foo) [below = \dist of return_secret.south] {\textsf{end}$_\texttt{A.foo}$};

%A.foo method edges
    \path[->] (st_a_foo) edge (return_secret);
    \path[->] (return_secret) edge (end_a_foo);

%A.bar method nodes
    \node [supergraph_y] (st_a_bar) [right = 5*\dist of st_a_foo] {\textsf{start}$_{\texttt{A.bar}}$};
    \node [supergraph_y] (end_a_bar) [below = \dist of st_a_bar.south] {\textsf{end}$_\texttt{A.bar}$};

%A.bar method edges
    \path[->] (st_a_bar) edge (end_a_bar);

%B.foo method nodes
    \node [supergraph_f] (st_b_foo) [right = 5*\dist of call_bar] {\textsf{start}$_{\texttt{B.foo}}$};
    \node [supergraph_f] (return_not_secret) [below = \dist of st_b_foo.south] {\texttt{return "not secret"}};
    \node [supergraph_f] (end_b_foo) [below = \dist of return_not_secret.south] {\textsf{end}$_\texttt{B.foo}$};

%B.foo method edges
  \path[->] (st_b_foo) edge (return_not_secret);
  \path[->] (return_not_secret) edge (end_b_foo);

%B.bar method nodes
    \node [supergraph_f] (st_b_bar) [right = 5*\dist of st_b_foo] {\textsf{start}$_{\texttt{B.bar}}$};
    \node [supergraph_f] (print) [below = \dist of st_b_bar.south] {\texttt{print(s)}};
    \node [supergraph_f] (end_b_bar) [below = \dist of print.south] {\textsf{end}$_\texttt{B.bar}$};

%B.bar method edges
  \path[->] (st_b_bar) edge (print);
  \path[->] (print) edge (end_b_bar);

%inter-procedural edges
  \path[->,dashed] (call_foo) edge[out=20,in=190] (st_a_foo);
  \path[->,dashed] (call_foo) edge[color=lightsalmonpink,out=-20,in=135] (st_b_foo);
  \path[->,dashed] (call_bar) edge[out=25,in=220] (st_a_bar);
  \path[->,dashed] (call_bar) edge[color=lightsalmonpink,out=18,in=160] (st_b_bar);
  \path[->,dashed] (end_a_foo) edge[out=220,in=15] (return_foo);
  \path[->,dashed] (end_b_foo) edge[color=lightsalmonpink,out=160,in=-60] (return_foo);
  \path[->,dashed] (end_a_bar) edge[out=210,in=40] (return_bar);
  \path[->,dashed] (end_b_bar) edge[color=lightsalmonpink,out=200,in=-40] (return_bar);

%arrow description
    \node [description] (intra_arrow_left) [above left = 2*\dist and 3.5*\dist of st_a_bar] {};
    \node [description] (intra_arrow_right) [right = \dist of intra_arrow_left] {};
    \node [description] (inter_arrow_left) [below = .5*\dist of intra_arrow_left] {};
    \node [description] (inter_arrow_right) [below = .5*\dist of intra_arrow_right] {};
    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intra-procedural edge} (intra_arrow_right);
    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{inter-procedural edge} (inter_arrow_right); 
}
\end{tikzpicture}
\caption{An example supergraph for Listing~\ref{list:ccexample}}%
  \label{fig:examplesupergraph}%
  \end{figure}

### 2014-12-11 figures/fig-transformation.tex
figures

@@
 }
-  \tikzstyle{problem}=[fill=greyblue,text width=2.3cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
-  \tikzstyle{result}=[fill=bisque,text width=1.8cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
+  \tikzstyle{problem}=[fill=greyblue,text width=2cm,rounded corners,font=\scriptsize,text=charcoal,drop shadow={ashadow, color=greyblue}]
+  \tikzstyle{result}=[fill=bisque,text width=1.5cm,rounded corners,font=\scriptsize,text=charcoal,drop shadow={ashadow, color=greyblue}]
 \begin{tikzpicture}
-    \node [problem] (ifds) {IFDS problem};
-    \node [problem] (equiv) [above right=0.5cm and .7\dist of ifds.east] {Equivalent IDE problem};
-    \node [problem] (ccide)[below=2cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
-    \node [result] (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
-    \node [result] (ccres) [below=2cm of equivres.west,anchor=west] {Correlated-calls result};
-    \node [result] (ifdsres) [right=\dist of equivres.east] {IFDS result};
-    \node [result] (improved) [right=\dist of ccres.east] {Improved IFDS result};
-    \path[->] (equivres) edge node[above]{$\backEq$} (ifdsres);
-    \path[->] (ccres) edge node[above] {$\backCC$} (improved);
-    %\path[->] (ccres) edge[out=25,in=210] node[above] {$\backEq$} (ifdsres);
-    \path[->] (ifds) edge[out=42,in=179] node[above] {$\transEq$} (equiv);
-    \path[->] (ifds) edge[out=-40,in=173] node[below] {$\transCC$} (ccide);
-    \path[->] (equiv) edge node[above]{$\result$} (equivres);
-    \path[->] (ccide) edge node[above]{$\result$} (ccres);
-    \path[->,dashed] (ifds) edge[out=-3,in=205] node[above]{$\result_{\text{IFDS}}$} (ifdsres);
+    \node [problem]
+      (ifds) {IFDS problem};
+    \node [problem]
+      (equiv) [above right=0.5cm and .7\dist of ifds.east] {Equivalent IDE problem};
+    \node [problem]
+      (ccide)[below=2cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
+    \node [result]
+      (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
+    \node [result]
+      (ccres) [below=2cm of equivres.west,anchor=west] {Correlated-calls result};
+    \node [result,text height=1.5cm,text width=2cm]
+      (ifdsres) [below right=0cm and \dist of equivres.east] {};
+    \node [below,font=\scriptsize] at (ifdsres.north) {IFDS result};
+    \node [rounded corners,font=\scriptsize,text width=1.5cm,fill=lightsalmonpink,text=charcoal]
+      (improved) [above right=.6cm and (\dist+.3cm) of ccres.east] {Improved IFDS result};
+
+    \path[->] (equivres) edge node[above,font=\scriptsize]{$\backEq$} (ifdsres);
+    \path[->] (ccres) edge node[above,font=\scriptsize] {$\backCC$} (improved);
+    %\path[->] (ccres) edge[out=25,in=210] node[above,font=\scriptsize] {$\backEq$} (ifdsres);
+    \path[->] (ifds) edge[out=43,in=183] node[above,font=\scriptsize] {$\transEq$} (equiv);
+    \path[->] (ifds) edge[out=-45,in=173] node[below,font=\scriptsize] {$\transCC$} (ccide);
+    \path[->] (equiv) edge node[above,font=\scriptsize]{$\result$} (equivres);
+    \path[->] (ccide) edge node[above,font=\scriptsize]{$\result$} (ccres);
+    \path[->,dashed] (ifds) edge[out=-3,in=183] node[above,font=\scriptsize]{$\result_{\text{IFDS}}$} (ifdsres);
 \end{tikzpicture}

### 2014-12-11 figures/fig-transformation.tex
angle
figure 1

@@
 }
-  \tikzstyle{problem}=[fill=greyblue,text width=2cm,rounded corners,font=\scriptsize,text=charcoal,drop shadow={ashadow, color=greyblue}]
+  \tikzstyle{problem}=[fill=greyblue,text width=1.6cm,rounded corners,font=\scriptsize,text=charcoal,drop shadow={ashadow, color=greyblue}]
   \tikzstyle{result}=[fill=bisque,text width=1.5cm,rounded corners,font=\scriptsize,text=charcoal,drop shadow={ashadow, color=greyblue}]
@@
     \node [result]
-      (ccres) [below=2cm of equivres.west,anchor=west] {Correlated-calls result};
+      (ccres) [below=2cm of equivres.west,anchor=west] {Correlated-calls IDE result};
     \node [result,text height=1.5cm,text width=2cm]
@@
 
-    \path[->] (equivres) edge node[above,font=\scriptsize]{$\backEq$} (ifdsres);
-    \path[->] (ccres) edge node[above,font=\scriptsize] {$\backCC$} (improved);
+    \path[->] (equivres) edge[out=0,in=150] node[above,font=\scriptsize]{$\backEq$} (ifdsres);
+    \path[->] (ccres) edge[out=0,in=230] node[above,font=\scriptsize] {$\backCC$} (improved);
     %\path[->] (ccres) edge[out=25,in=210] node[above,font=\scriptsize] {$\backEq$} (ifdsres);

### 2014-12-11 figures/fig-transformation.tex
figure

@@
 }
-  \tikzstyle{problem}=[fill=greyblue,text width=1.6cm,rounded corners,font=\scriptsize,text=charcoal,drop shadow={ashadow, color=greyblue}]
+  \tikzstyle{problem}=[fill=greyblue,text width=1.8cm,rounded corners,font=\scriptsize,text=charcoal,drop shadow={ashadow, color=greyblue}]
   \tikzstyle{result}=[fill=bisque,text width=1.5cm,rounded corners,font=\scriptsize,text=charcoal,drop shadow={ashadow, color=greyblue}]
@@
     \path[->] (equivres) edge[out=0,in=150] node[above,font=\scriptsize]{$\backEq$} (ifdsres);
-    \path[->] (ccres) edge[out=0,in=230] node[above,font=\scriptsize] {$\backCC$} (improved);
+    \path[->] (ccres) edge[out=0,in=230] node[above left,font=\scriptsize] {$\backCC$} (improved);
     %\path[->] (ccres) edge[out=25,in=210] node[above,font=\scriptsize] {$\backEq$} (ifdsres);

### 2014-12-11 content/background.tex
minor changes and comments in section 3

@@
 This section defines basic terminology and presents the IFDS and IDE algorithms.
+\ftodo{
+  Shall we add a sentence saying that readers familiar with these algorithms may skip this section?
+}
 
@@
 pointed to by $r$, $\textsf{lookup}(s,t)$ gives the procedure that will
-be invoked by the call $r.m(\ldots)$. We also define a kind of inverse $\tau$
+be invoked by the call $r.m(\ldots)$. We also define a function $\tau$
+that may be viewed as the inverse
 of $\textsf{lookup}$: given a signature $s$ and a specific invoked procedure
@@
 A path through the control-flow supergraph is \textit{valid} if every end-to-return edge on the path returns
-to the site of the most recent unmatched call. The set of all valid paths from the program entry point to
+to the site of the most recent unmatched call. 
+\ftodo{Can we explain/define the notion of the ``most recent unmatched call'' more precisely?}
+The set of all valid paths from the program entry point to
 a node $n$ is denoted $\ivp(n)$.
@@
 are/must be complete. I'll just say that here.}
+\ftodo{Would it make sense to first the define the notion of a lattice without referring to its completeness?
+       This could be followed by defining what it means for a (semi)lattice to be complete, and then we
+       could say that all lattices considered in this paper are complete, etc.}
+\ftodo{Can we define the symbols $\sqcup$ and $\sqcap$ for join and meet here?}
 A \textit{complete lattice} is a partially ordered set $(S,\sqsubseteq)$ in which every subset has a least upper bound and a greatest lower bound.
@@
 
-The IFDS algorithm is notable because it computes a meet over valid paths solution in polynomial time.
-Most other interprocedural analysis algorithms are either imprecise due to invalid paths,
-general but do not run in polynomial time~\cite{knoop1992interprocedural,pnueli1981two}, or handle a very specific set of problems~\cite{knoop1993efficient}.
+The IFDS algorithm is notable because it computes a meet-over-valid paths solution in polynomial time.
+Most other interprocedural analysis algorithms are either: 
+  (i) imprecise due to invalid paths,
+  (ii) general but do not run in polynomial time~\cite{knoop1992interprocedural,pnueli1981two}, or 
+  (iii) handle a very specific set of problems~\cite{knoop1993efficient}.
 
@@
 and $\sqcap$ is the \textit{meet operator} on the powerset $2^D$, either union or intersection.
-In our presentation, the meet will always be union, but all of the results apply dually when the
+In our presentation, the meet operator will always be union, but all of the results apply dually when the
 meet is intersection.
@@
 to distributivity: applying the flow function to a set of facts is
-equivalent to applying it on each fact individually and
+equivalent to applying it on each fact individually and then
 taking the union of the results.
@@
 is \textit{realizable} if its projection to the (non-exploded) supergraph is a valid
-path (i.e. if it is of the form $(n_0, d_0) \to (n_1,d_1) \to \cdots \to (n_m,d_m)$
-and $n_0 \to n_1 \to \cdots \to n_m$ is a valid path).
+path (i.e., if it is of the form $(n_0, d_0) \to (n_1,d_1) \to \cdots \to (n_m,d_m)$
+and where $n_0 \to n_1 \to \cdots \to n_m$ is a valid path).
 
@@
 Let $\Omega = \lambda d.\top$ be the environment that maps every element of $D$ to $\top$.
+\ftodo{
+   What is the relationship between $\Omega$ and $\Delta$?
+}
 Thanks to distributivity, every environment transformer 
@@
 Given a (non-exploded) supergraph edge $n \to n'$ and a dataflow fact $d$,
-$f(n,d,n')$ returns a map that gives for each fact $d'$ the micro-function $f$
+$f(n,d,n')$ returns a map that gives, for each fact $d'$, the micro-function $f$
 that appears on the exploded supergraph edge $(n,d) \to (n',d')$.
@@
 }
+
+\ftodo{Would it make sense to discuss an example of an IDE problem here?  Perhaps we can do this
+  without using much space by referring to an existing figure elsewhere in the paper?}

### 2014-12-11 content/appendix.tex
replacing R with R_IDE; introducing CFG abbreviation

@@
   \begin{align*}
-    \backCC\left(\result(\transCC_R(P))\right)(n)&=\{(n',\,D_n'^\Subset(\result(\transCC_R(P))))\ |\ n\in N^*\}(n)\\
-      &=D_n^\Subset(\result(\transCC_R(P)))\\
+    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)&=\{(n',\,D_n'^\Subset(\resultIDE(\transCC_R(P))))\ |\ n\in N^*\}(n)\\
+      &=D_n^\Subset(\resultIDE(\transCC_R(P)))\\
       &\subseteq\mvp F(n)\\
-      &=\result_\text{IFDS}(P)(n)\,.\qedhere
+      &=\resultIFDS(P)(n)\,.\qedhere
   \end{align*}
@@
 
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:sound}}] Let $\rho=\result(\transCC_R(P))$. Then
+\begin{proof}[\textbf{Proof of Lemma~\ref{lem:sound}}] Let $\rho=\resultIDE(\transCC_R(P))$. Then
   \begin{align*}
@@
   \begin{equation}
-    \result\left(\transCC_S(P)\right)(n,\,d)(r)=
-    \result(\transCC_{\{r\}}(P))(n,\,d)(r)\,.
+    \resultIDE\left(\transCC_S(P)\right)(n,\,d)(r)=
+    \resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r)\,.
   \end{equation}
@@
   \begin{align}
-    \result\left(\transCC_S(P)\right)(n,\,d)(r)
+    \resultIDE\left(\transCC_S(P)\right)(n,\,d)(r)
     &=\mvp{\textsf{Env}}(n,\,d)(r)\notag\\
@@
   \begin{align*}
-    \result\left(\transCC_S(P)\right)(n,\,d)(r)
+    \resultIDE\left(\transCC_S(P)\right)(n,\,d)(r)
     &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\\
-    &=\result\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)\,.\qedhere
+    &=\resultIDE\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)\,.\qedhere
   \end{align*}
@@
   \[
-    \result\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)=\top_T\,,
+    \resultIDE\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)=\top_T\,,
   \]
@@
   \[
-    \result\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
+    \resultIDE\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
   \]
@@
   \begin{align*}
-    \backCC(\result\left(\transCC_R(P)\right))
-    &=\left\{(n,\,D_n^\Subset(\result(\transCC_R(P))))\ |\ n\in N^*\right\}.
+    \backCC(\resultIDE\left(\transCC_R(P)\right))
+    &=\left\{(n,\,D_n^\Subset(\resultIDE(\transCC_R(P))))\ |\ n\in N^*\right\}.
   \end{align*}
@@
   \begin{align*}
-    D_n^\Subset&(\result(\transCC_R(P))))\\
-    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall r\in R:\ \left\{(r,\,\result(\transCC_{\{r\}}(P))(n,\,d)(r))\ |\ r\in R\right\}(r)\ne\top_T\right\}\\
-    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in R}:\ \result(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}.
+    D_n^\Subset&(\resultIDE(\transCC_R(P))))\\
+    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall r\in R:\ \left\{(r,\,\resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r))\ |\ r\in R\right\}(r)\ne\top_T\right\}\\
+    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in R}:\ \resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}.
   \end{align*}
 
-Since, according to Lemma~\ref{lem:ccrectop}, $\result(\transCC_{\{r\}}(P))(n,\,d)(r)$ can only be equal to $\top_T$ when $r\in\rcc$, we can conclude that
+Since, according to Lemma~\ref{lem:ccrectop}, $\resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r)$ can only be equal to $\top_T$ when $r\in\rcc$, we can conclude that
   \begin{align*}
-    D_n^\Subset&(\result(\transCC_R(P))))\\
-    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in\rcc}:\ \result(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}\\
-    &=D_n^\Subset(\result(\transCC_\rcc(P)))).
+    D_n^\Subset&(\resultIDE(\transCC_R(P))))\\
+    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in\rcc}:\ \resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}\\
+    &=D_n^\Subset(\resultIDE(\transCC_\rcc(P)))).
   \end{align*}
@@
   \begin{align*}
-    \backCC(\result\left(\transCC_R(P)\right))
-    &=\left\{(n,\,D_n^\Subset(\result(\transCC_\rcc(P))))\ |\ n\in N^*\right\}\\
-    &=\backCC(\result\left(\transCC_\rcc(P)\right))\,.\qedhere
+    \backCC(\resultIDE\left(\transCC_R(P)\right))
+    &=\left\{(n,\,D_n^\Subset(\resultIDE(\transCC_\rcc(P))))\ |\ n\in N^*\right\}\\
+    &=\backCC(\resultIDE\left(\transCC_\rcc(P)\right))\,.\qedhere
   \end{align*}

### 2014-12-11 content/background.tex
replacing R with R_IDE; introducing CFG abbreviation

--- 2014-12-10 content/background.tex
@@
 %We will start by introducing several concepts used by the IFDS and IDE analyses.
+\begin{mdelete}\mtodo{We already say (but less precisely) what a CFG is in the introduction.}
 The \textit{control-flow graph} of a procedure is a directed graph whose nodes are instructions, and which contains an edge from $n_1$ to $n_2$ whenever
-$n_2$ may execute immediately after $n_1$. A control-flow graph has a distinguished \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$.
+$n_2$ may execute immediately after $n_1$. A CFG has a distinguished \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$.
+\end{mdelete}
 %and edges represent transfer of control between the instructions during an execution of the program. 
@@
 By contrast, an \textit{inter-procedural path} is one that contains nodes from different procedures.
-The \textit{control-flow supergraph} of a program contains the control-flow graphs of all of the procedures as
+The \textit{control-flow supergraph} of a program contains the CFGs of all of the procedures as
 subgraphs. In addition, for each call instruction $c$, the supergraph contains a \textit{call-to-start} edge to the start node of every procedure that
@@
 \begin{itemize}
-  \item there is always an edge $(\mathbf0,\,\mathbf0)$ corresponding to the control-flow-graph edge;
+  \item there is always an edge $(\mathbf0,\,\mathbf0)$ corresponding to the CFG edge;
   \item if there is an edge $(\mathbf0,\,d_j)$, then there is no other edge leading to $d_j$; in particular, there is never an edge $(d_i,\,\mathbf0)$ where $d_i\ne\mathbf0$.
@@
 \subsubsection{Environment Transformers}
-For each node in the control-flow graph, the result of an IDE analysis computes an environment $\textsf{Env}(D,\,L)$, which is a map from data-flow facts to lattice elements.
+For each node in the CFG, the result of an IDE analysis computes an environment $\textsf{Env}(D,\,L)$, which is a map from data-flow facts to lattice elements.
 
@@
 \commentout{
-Given a labeled exploded supergraph, the IDE algorithm computes the environments for all nodes in the control-flow graph.
+Given a labeled exploded supergraph, the IDE algorithm computes the environments for all nodes in the CFG.
 

### 2014-12-11 content/impl.tex
replacing R with R_IDE; introducing CFG abbreviation

@@
 pairs each such fact~$d$ with a lattice element $\ell$. Formally,
-for an IFDS problem $P$, the result $\result_{\text{IFDS}}$ has type
-$N \to D$. Similarly, for an IFDS problem $Q$, the result $\result_{\text{IDE}}$
+for an IFDS problem $P$, the result $\resultIFDS$ has type
+$N \to D$. Similarly, for an IFDS problem $Q$, the result $\resultIDE$
 has type $N \to D \times L$.
@@
 The output of an IFDS analysis states whether a node is reachable in the exploded supergraph.
-This means that for an IFDS problem $P$, the IFDS-analysis result $\result_{\text{IFDS}}(P):\ N^*\to 2^D$ is a map from nodes of the control-flow supergraph to sets of facts:
+This means that for an IFDS problem $P$, the IFDS-analysis result $\resultIFDS(P):\ N^*\to 2^D$ is a map from nodes of the control-flow supergraph to sets of facts:
 \begin{equation}
-  \result_{\text{IFDS}}(P)=\{(n,\,\mvp F(n))\,|\,n\in N^*\}\,.
+  \resultIFDS(P)=\{(n,\,\mvp F(n))\,|\,n\in N^*\}\,.
 \end{equation}
@@
   \small\begin{align*}
-    \result_\text{IFDS}(\mathcal P)=\{&(\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\{\texttt a\}),
+    \resultIFDS(\mathcal P)=\{&(\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\{\texttt a\}),
       &(\highlight{\textsf{start}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
@@
  The IDE analysis associates a lattice element with each node in the exploded supergraph.
-For an IDE problem $Q$, the result $\result(Q):\ N^\#\to L$ maps nodes of the exploded supergraph to lattice elements (see~\eqref{eq:mvpdef}):
+For an IDE problem $Q$, the result $\resultIDE(Q):\ N^\#\to L$ maps nodes of the exploded supergraph to lattice elements (see~\eqref{eq:mvpdef}):
 \begin{equation}\label{eq:ideresult}
-  \result(Q)=\{((n,\,d),\,\mvp{\textsf{Env}}(n,\,d))\ |\ n\in N^*,\,d\in D\}\,.
+  \resultIDE(Q)=\{((n,\,d),\,\mvp{\textsf{Env}}(n,\,d))\ |\ n\in N^*,\,d\in D\}\,.
 \end{equation}
-In other words, for each fact $d\in D$ at a given node $n\in N^*$, $\result(Q)(n,\,d)$ returns a lattice element. If a fact $d\in D$ is unreachable, $\result(Q)(n,\,d)=\top$.
+In other words, for each fact $d\in D$ at a given node $n\in N^*$, $\resultIDE(Q)(n,\,d)$ returns a lattice element. If a fact $d\in D$ is unreachable, $\resultIDE(Q)(n,\,d)=\top$.
 
@@
 \begin{equation}
-  \resultEq=\result(\transEq(P))
+  \resultEq=\resultIDE(\transEq(P))
 \end{equation}
@@
     \small\begin{align*}
-    \result(\transEq(\mathcal P))=\{&((\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\texttt a),\,\bot),\\
+    \resultIDE(\transEq(\mathcal P))=\{&((\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\texttt a),\,\bot),\\
       &((\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
@@
     \end{align*}\normalsize
-  Suppose that for a pair $(n,\,d)$, where $n\in N^*$ and $d\in D$, there is no corresponding result in ~$\result_\text{IFDS}(\mathcal P)$ (see Example~\ref{ex:ifdsresult}).
-Then $(n,\,d)$ appears in $\result(\transEq(\mathcal P))$ as $((n,\,d),\,\top)$.
+  Suppose that for a pair $(n,\,d)$, where $n\in N^*$ and $d\in D$, there is no corresponding result in ~$\resultIFDS(\mathcal P)$ (see Example~\ref{ex:ifdsresult}).
+Then $(n,\,d)$ appears in $\resultIDE(\transEq(\mathcal P))$ as $((n,\,d),\,\top)$.
 \end{example}
@@
 \[
-  \rho=\result(\transEq(P)).
+  \rho=\resultIDE(\transEq(P)).
 \]
@@
 \begin{equation}
-  \backEq\left(\result(\transEq(P))\right)(n)=\result_{\text{IFDS}}(P)(n)\,.
+  \backEq\left(\resultIDE(\transEq(P))\right)(n)=\resultIFDS(P)(n)\,.
 \end{equation}
@@
 Let $P$ be an IFDS problem. 
-Let $E:\,N\times D$ be the domain of the IDE result $\result(Q)$.
-To convert $\result(\transCC_R(P))$ to an IFDS result, we need to map the control-flow-supergraph nodes $n\in N^*$ to the corresponding facts $d\in D$. 
-Unlike in~$\backEq$, we will only map each~$n$ to the facts~$d$ for~which~$\result(\transCC_R(P))(n,\,d)$ does not contain an~empty mapping for~any~receiver.
+Let $E:\,N\times D$ be the domain of the IDE result $\resultIDE(Q)$.
+To convert $\resultIDE(\transCC_R(P))$ to an IFDS result, we need to map the control-flow-supergraph nodes $n\in N^*$ to the corresponding facts $d\in D$. 
+Unlike in~$\backEq$, we will only map each~$n$ to the facts~$d$ for~which~$\resultIDE(\transCC_R(P))(n,\,d)$ does not contain an~empty mapping for~any~receiver.
 
-For a node $n\in N^*$ and a correlated-calls IDE problem result $\rho=\result(\transCC_S(P))$, let $D_n^\Subset(\rho)$ be a set of data-flow facts defined as
+For a node $n\in N^*$ and a correlated-calls IDE problem result $\rho=\resultIDE(\transCC_S(P))$, let $D_n^\Subset(\rho)$ be a set of data-flow facts defined as
 \begin{equation}\label{eq:dnq}
@@
 \begin{lemma}[Precision]\label{lem:subsetifds}
-    \otodo{Should we say $\result_{\text{IDE}}$ instead of $\result$ everywhere, to
-        be consistent with $\result_{\text{IFDS}}$?}
     For an IFDS problem $P$ and all ${n\in N^*}$,
     \begin{equation}\label{eq:correct}
-      \backCC\left(\result(\transCC_R(P))\right)(n)
+      \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
       \subseteq
-      \result_{\text{IFDS}}(P)(n)\,.
+      \resultIFDS(P)(n)\,.
     \end{equation}
@@
   \begin{equation}
-    d\in \backCC\left(\result(\transCC_R(P))\right)(n)\,.
+    d\in \backCC\left(\resultIDE(\transCC_R(P))\right)(n)\,.
   \end{equation}
@@
   \begin{equation}
-    \backCC\left(\result\left(\transCC_\rcc(P)\right)\right)=\backCC(\result\left(\transCC_R(P)\right))\,.
+    \backCC\left(\resultIDE\left(\transCC_\rcc(P)\right)\right)=\backCC(\resultIDE\left(\transCC_R(P)\right))\,.
   \end{equation}
@@
 To summarize, Lemma~\ref{lem:sound} shows that the result $\resultCC$ of a correlated-calls analysis is sound since it overapproximates the data flow of all possible concrete execution paths.
-We have also shown in Lemma~\ref{lem:subsetifds} that the correlated-calls analysis improves the precision of the original IFDS result $\result_\text{IFDS}$, because the correlated-calls result $\resultCC$ underapproximates an equivalence-IDE result $\resultEq=\result_\text{IFDS}$.
+We have also shown in Lemma~\ref{lem:subsetifds} that the correlated-calls analysis improves the precision of the original IFDS result $\resultIFDS$, because the correlated-calls result $\resultCC$ underapproximates an equivalence-IDE result $\resultEq$.
 Finally, we showed in Lemma~\ref{lem:onlycorrrec} that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result $\resultCC$ that is obtained when considering all receivers $R$.

### 2014-12-11 content/intro.tex
figure
replacing R with R_IDE; introducing CFG abbreviation

@@
 Data-flow analyses operate on \textit{control-flow graphs} (CFGs)
-\mtodo{If we introduce this abbreviation, should we replace the uses of
-``control-flow graph'' with ``CFG'' in the paper?}
 that model 
@@
 typically done by associating \textit{flow functions} that represent how 
-data is propagated with the edges of the control-flow graph.  A 
+data is propagated with the edges of the CFG.  A 
 \textit{confluence operator} specifies how the data facts that have been 
@@
 
-Since a control-flow graph is an over-approximation of the possible flows 
+Since a CFG is an over-approximation of the possible flows 
 of control in concrete executions of a program, it may contain \textit{infeasible} 
@@
 as reaching definitions, available expressions, and taint analysis.
-\mtodo{We should define somewhere what taint analysis is, since it's currently
-commented out.}
 A distinguishing 
@@
 We present a formalization of the transformation and prove its correctness
-as follows. First, we derive an ``Equivalence IDE problem''%
-\mtodo{The IDE paper already states that each IFDS problem can be solved with IDE.
-I wonder if this sounds like the equivalence transformation was our contribution.
-We just use the equivalence transformation to explain the CC transformation, and for the
-proofs.
-}
-from the original 
-IFDS problem by associating the identity environment functions with all edges,
-and show that the solution to this Equivalence IDE problem can be mapped back
-to the solution of the original IFDS problem. Then, we derive a ``Correlated Calls 
-IDE Problem'' from the original IFDS problem and show how a solution to this problem 
-can be mapped to the solution to the original IFDS problem, but also how a
-more precise IFDS result can be derived from it. 
-\otodo{Do we need to mention the imprecise map from the CC-IDE result to the IFDS result? It
-doesn't really seem relevant, and could be confusing.}
+as follows. 
+First, we derive an IDE problem that is equivalent to the original IFDS problem,
+as described by Reps et al.~\cite{sagiv1996precise}.
+Solving this ``Equivalence-IDE Problem'' with the IDE algorithm yields a result that
+is equivalent to the one obtained by applying the IFDS algorithm to the original IFDS problem.
+Then, we derive a ``Correlated Calls 
+IDE Problem'' from the original IFDS problem and show 
+that the solution to this problem, when converted to an IFDS result, is more precise
+than the original IFDS result.
 We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
@@
 \footnote{ 
-  The labels $\result$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$ on edges in 
+  The labels $\resultIDE$, $\resultIFDS$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$
+  on edges in 
   Figure~\ref{fig:transformations} reflect a number of mappings and projections 
   that will be defined in Section~\TODO{ref} and that can be ignored here.
-}.  
-\ftodo{would it make sense to add an edge in Figure~\ref{fig:transformations} from the IFDS problem to the IFDS result?}
+}.\mtodo{In the footnote, should we just say "the labels" since there are so many?}
 

### 2014-12-11 figures/fig-transformation.tex
replacing R with R_IDE; introducing CFG abbreviation

@@
     \node [problem]
-      (equiv) [above right=0.5cm and .7\dist of ifds.east] {Equivalent IDE problem};
+      (equiv) [above right=0.5cm and .7\dist of ifds.east] {Equivalence-IDE problem};
     \node [problem]
@@
     \path[->] (ifds) edge[out=-45,in=173] node[below,font=\scriptsize] {$\transCC$} (ccide);
-    \path[->] (equiv) edge node[above,font=\scriptsize]{$\result$} (equivres);
-    \path[->] (ccide) edge node[above,font=\scriptsize]{$\result$} (ccres);
-    \path[->,dashed] (ifds) edge[out=-3,in=183] node[above,font=\scriptsize]{$\result_{\text{IFDS}}$} (ifdsres);
+    \path[->] (equiv) edge node[above,font=\scriptsize]{$\resultIDE$} (equivres);
+    \path[->] (ccide) edge node[above,font=\scriptsize]{$\resultIDE$} (ccres);
+    \path[->,dashed] (ifds) edge[out=-3,in=183] node[above,font=\scriptsize]{$\resultIFDS$} (ifdsres);
 \end{tikzpicture}

### 2014-12-11 content/appendix.tex
part of the proofs

@@
 
-  According to~\eqref{eq:envTransToEdgeFnEdge},
+As shown in~Sagiv et al.~\cite{sagiv1996precise}, the relationship between environment transformers and edge functions can be described with the following equation.
+For an edge $(n_1,\,n_2)\in E^*$ an environment $\textsf{env}$ that maps $D$ to $L$, and a fact $d\in D$,
+\begin{align}\label{eq:envTransToEdgeFnEdge}
+  \menv&((n_1,\,n_2))(\textsf{env})(d)\notag\\
+  &=\edgefn((n_1,\,\Lambda),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,.
+\end{align}  
+Then, according to~\eqref{eq:envTransToEdgeFnEdge},\mtodo{Is it okay that in~\eqref{eq:envTransToEdgeFnEdge}, we use $\edgefn$, and below we use $\ccedgefn R$?}
   \begin{align*}
@@
 \subsection*{Correlated Call Receivers}
-This appendix contains the proof for Lemma~\ref{} which shows that in a correlated-calls analysis, it is enough to consider only correlated-call receivers~$\rcc$.
+We will now present the proof for Lemma~\ref{lem:onlycorrrec} which shows that in a correlated-calls analysis, it is enough to consider only correlated-call receivers~$\rcc$.
 
-The following Lemma shows that the types to which a given receiver is mapped in the result of the algorithm is not affected by other receivers and the types to which they are mapped.
+In this section, we will denote the set of realizable paths corresponding to a valid path $p$ and a fact $d$ as $\textsf{RP}(p,\,d)$.
+
+First, we introduce a Lemma showing that the types to which a given receiver is mapped in the result of the algorithm is not affected by other receivers and the types to which they are mapped.
 
@@
 \begin{proof}
-  According to~\eqref{eq:ideresult}, \eqref{eq:mvpdef}, and~\eqref{eq:envTransToEdgefn},
+ Recall from Section~\ref{sec:ideToIfds} that the result of an IDE analysis maps a lattice element to each node in the exploded supergraph.
+Specifically, for an IDE problem $Q$, the result $\resultIDE(Q):\ N^\#\to L$ maps nodes of the exploded supergraph to lattice elements:
+\begin{equation}\label{eq:ideresult}
+  \resultIDE(Q)=\{((n,\,d),\,\mvp{\textsf{Env}}(n,\,d))\ |\ n\in N^*,\,d\in D\}\,.
+\end{equation}
+Furthermore, recall from Section~\ref{sec:bgide} that
+\begin{equation}\label{eq:mvpdef}
+  \mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top)
+\end{equation}
+
+  According to~\eqref{eq:ideresult}, \eqref{eq:mvpdef}, and~\eqref{eq:envTransToEdgeFnEdge},
   \begin{align}

### 2014-12-11 content/background.tex
part of the proofs

@@
   $\mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top)$,
+  \mtodo{I like that the text is now very compact. But I wonder if some of the formulas should be put
+  on a separate line and enumerated. For example, I need to reference the definition of $\textsf{MVP}_{\textsf{Env}}$ in the
+  proof, but since it's embedded in the text, I'm repeating the formula in the appendix and reference the section. Is that fine?}
 where $M_\textsf{Env}$ is extended from edges to paths by composition.

### 2014-12-11 content/impl.tex
part of the proofs

@@
 
-\subsection{Converting IDE Results to IFDS Results}
+\subsection{Converting IDE Results to IFDS Results}\label{sec:ideToIfds}
 
@@
 for an IFDS problem $P$, the result $\resultIFDS$ has type
-$N \to D$. Similarly, for an IFDS problem $Q$, the result $\resultIDE$
+$N \to D$.\mtodo{Should it be $N^*$?} Similarly, for an IFDS problem $Q$, the result $\resultIDE$
 has type $N \to D \times L$.

### 2014-12-11 content/example.tex
supergraph figure
wrote new section 2

@@
 
-\ftodo{This section is current under revision. Please do not edit..}
+\newcommand{\code}[1]{\textsf{#1}}  
+\definecolor{sh_comment}{rgb}{0.12, 0.38, 0.18}
+\definecolor{sh_keyword}{rgb}{0.37, 0.08, 0.25}  % #5F1441
+\definecolor{sh_string}{rgb}{0.06, 0.10, 0.98} % #101AF9
+\definecolor{KWColor}{rgb}{0.5,0,0.67}
+\definecolor{CommentColor}{rgb}{0.15,0.5,0.15}
+\lstdefinelanguage{scala}[]{Java}{
+   morekeywords={trait,def,object,with,override,val,type,var} 
+}
+
+\lstdefinestyle{Eclipse}{
+  xleftmargin=0pt,
+  language = scala,
+  basicstyle=\sffamily\small,
+  stringstyle=\color{sh_string},
+  keywordstyle = \color{sh_keyword}\bfseries,  %}
+  lineskip=-0.0em,
+  commentstyle=\color{sh_comment}\itshape,  
+  escapeinside={/*@}{@*/},
+  numbersep=5pt,
+  captionpos=b,
+  xleftmargin=0.4cm, xrightmargin=0.5cm,
+   morekeywords={invokestatic,invokeinterface,invokevirtual,invokespecial},
+}
+
+\lstset{
+  showspaces=false,showtabs=false,tabsize=2,columns=flexible,
+  morekeywords={trait,def,object,with},
+  language={scala},
+  style=Eclipse,
+  numbers=left,
+  numberstyle=\scriptsize\color{CommentColor},
+  firstnumber=last,
+  showstringspaces=true
+}
+
+In this section, we illustrate our approach using a small motivating example that
+shows how our technique can be used to improve the precision of taint analysis.
+A taint analysis is a specialized dataflow analysis for computing how string values
+may flow from ``sources'', which are typically statements that read untrusted input, 
+to ``sinks'', which are typically securitive-sensitive operations such as calls to 
+a database. In previous research \TODO{cite}, taint analysis algorithms have been 
+formulated as IFDS problems.
+
+\begin{figure}
+  \centering
+
+  \begin{minipage}{\textwidth}
+    \inputMinted{java}{ccexample.java}
+  \end{minipage}
+    \vspace*{-4mm}
+  \caption{Example program containing correlated calls}
+  \label{list:ccexample}
+
+   \begin{minipage}{\textwidth}
+    \tikzstyle{supergraph}=[
+      fill=greyblue,
+      rounded corners,
+      font=\footnotesize,
+      align=right,
+      text=charcoal,
+      drop shadow={ashadow, color=greyblue}
+    ]
+    \tikzstyle{supergraph_y}=[
+      fill=bisque,
+      rounded corners,
+      font=\footnotesize,
+      align=left,
+      text=charcoal,
+      drop shadow={ashadow, color=greyblue}
+    ]
+    \tikzstyle{supergraph_f}=[
+      fill=lightsalmonpink,
+      rounded corners,
+      font=\footnotesize,
+      align=left,
+      text=charcoal,
+      drop shadow={ashadow, color=greyblue}
+    ]
+    \tikzstyle{description}=[fill=white]
+    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
+    \tikzstyle{arrowtext}=[font=\tiny,color=black,above]
+
+\hspace*{-10pt}
+\begin{tikzpicture}
+\scalebox{.8}{
+% main method nodes
+    \node [supergraph] (st_main) {\textsf{start}$_{\texttt{main}}$};
+    \node [supergraph] (asgn_a) [below = \dist of st_main.south] {\texttt{a = args==null\,?}\\\texttt{new\,A()\,:\,new\,B()}};
+    \node [supergraph] (call_foo) [below = \dist of asgn_a.south] {\textsf{call}$_\texttt{foo}$};
+    \node [supergraph] (return_foo) [below = \dist of call_foo.south] {\textsf{return}$_\texttt{foo}$\\\texttt{v = a.foo()}};
+    \node [supergraph] (call_bar) [below = \dist of return_foo.south] {\textsf{call}$_\texttt{bar}$};
+    \node [supergraph] (return_bar) [below = \dist of call_bar.south] {\textsf{return}$_\texttt{bar}$};
+    \node [supergraph] (end_main) [below = \dist of return_bar.south] {\textsf{end}$_{\texttt{main}}$};
+
+% main method edges 
+    \path[->,ultra thick] (st_main) edge (asgn_a);
+    \path[->,ultra thick] (asgn_a) edge (call_foo);
+    \path[->] (call_foo) edge (return_foo);
+    \path[->,ultra thick] (return_foo) edge (call_bar);
+    \path[->] (call_bar) edge (return_bar);
+    \path[->,ultra thick] (return_bar) edge (end_main);
+
+%A.foo method nodes
+    \node [supergraph_y] (st_a_foo) [right = 5*\dist of st_main] {\textsf{start}$_{\texttt{A.foo}}$};
+    \node [supergraph_y] (return_secret) [below = \dist of st_a_foo.south] {\texttt{return secret()}};
+    \node [supergraph_y] (end_a_foo) [below = \dist of return_secret.south] {\textsf{end}$_\texttt{A.foo}$};
+
+%A.foo method edges
+    \path[->] (st_a_foo) edge (return_secret);
+    \path[->] (return_secret) edge (end_a_foo);
+
+%A.bar method nodes
+    \node [supergraph_y] (st_a_bar) [right = 5*\dist of st_a_foo] {\textsf{start}$_{\texttt{A.bar}}$};
+    \node [supergraph_y] (end_a_bar) [below = \dist of st_a_bar.south] {\textsf{end}$_\texttt{A.bar}$};
+
+%A.bar method edges
+    \path[->] (st_a_bar) edge (end_a_bar);
+
+%B.foo method nodes
+    \node [supergraph_f] (st_b_foo) [right = 5*\dist of call_bar] {\textsf{start}$_{\texttt{B.foo}}$};
+    \node [supergraph_f] (return_not_secret) [below = \dist of st_b_foo.south] {\texttt{return "not secret"}};
+    \node [supergraph_f] (end_b_foo) [below = \dist of return_not_secret.south] {\textsf{end}$_\texttt{B.foo}$};
+
+%B.foo method edges
+  \path[->] (st_b_foo) edge (return_not_secret);
+  \path[->] (return_not_secret) edge (end_b_foo);
+
+%B.bar method nodes
+    \node [supergraph_f] (st_b_bar) [right = 5*\dist of st_b_foo] {\textsf{start}$_{\texttt{B.bar}}$};
+    \node [supergraph_f] (print) [below = \dist of st_b_bar.south] {\texttt{print(s)}};
+    \node [supergraph_f] (end_b_bar) [below = \dist of print.south] {\textsf{end}$_\texttt{B.bar}$};
+
+%B.bar method edges
+  \path[->] (st_b_bar) edge (print);
+  \path[->] (print) edge (end_b_bar);
+
+%inter-procedural edges
+  \path[->,dashed,ultra thick] (call_foo) edge[out=20,in=190] (st_a_foo);
+  \path[->,dashed] (call_foo) edge[color=lightsalmonpink,out=-20,in=135] (st_b_foo);
+  \path[->,dashed] (call_bar) edge[out=25,in=220] (st_a_bar);
+  \path[->,dashed,ultra thick] (call_bar) edge[color=lightsalmonpink,out=18,in=160] (st_b_bar);
+  \path[->,dashed,ultra thick] (end_a_foo) edge[out=220,in=15] (return_foo);
+  \path[->,dashed] (end_b_foo) edge[color=lightsalmonpink,out=160,in=-60] (return_foo);
+  \path[->,dashed] (end_a_bar) edge[out=210,in=40] (return_bar);
+  \path[->,dashed,ultra thick] (end_b_bar) edge[color=lightsalmonpink,out=200,in=-40] (return_bar);
+
+%arrow description
+    \node [description] (intra_arrow_left) [above left = 2*\dist and 3.5*\dist of st_a_bar] {};
+    \node [description] (intra_arrow_right) [right = \dist of intra_arrow_left] {};
+    \node [description] (inter_arrow_left) [below = .5*\dist of intra_arrow_left] {};
+    \node [description] (inter_arrow_right) [below = .5*\dist of intra_arrow_right] {};
+    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intra-procedural edge} (intra_arrow_right);
+    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{inter-procedural edge} (inter_arrow_right); 
+}
+\end{tikzpicture}
+   \end{minipage}
+   \vspace*{-25mm}
+  \caption{
+    Control flow supergraph for the example program of Figure~\ref{list:ccexample}.
+    An infeasible path is shown in bold. 
+  }%
+  \label{fig:examplesupergraph}%
+\end{figure}
+
+Figure~\ref{list:ccexample} shows a small Java program that we will use to illustrate
+how our technique can improve the precision of a simple taint analysis. The program
+declares a class \code{A} with a subclass \code{B},  where \code{A} defines methods 
+\code{foo()} and \code{bar()} that are overridden in \code{B}.  In order to keep the 
+example small and self-contained, it is assumed  that secret values are created by 
+an unspecified function \code{secret()}, which is called in method \code{A.foo()} on 
+line~\ref{line:Afoo}. Furthermore, it is assumed that any write to the standard output 
+stream via calls \code{System.out.println()} such as the one in method \code{B.bar()} 
+on line~\ref{line:Bbar} is a security-sensitive operation. Depending on the number of 
+arguments passed to the program, the \code{main()} method of the example program creates 
+either an \code{A}-object or a \code{B}-object on line~\ref{line:createObject}. The 
+program then calls \code{foo()} on this object on line~\ref{line:callfoo}, which is 
+followed by a call to \code{bar()} on the same object on line~\ref{line:callbar}.
+
+The specific question that we would like to answer for the example program of
+Figure~\ref{list:ccexample} is the following: Is it possible for the untrusted value 
+that is read on line~\ref{line:Afoo} to flow to the print statement on line~\ref{line:Bbar}? 
+%
+To determine whether such a flow of tainted data is possible, consider the control-flow
+supergraph for the example program that is shown in Figure~\ref{fig:examplesupergraph}.
+ The nodes in this graph correspond to statements, method entry points (start nodes) and 
+method exit points (end nodes). Note that for each method call, the graph contains a 
+distinct call-node and a return-node. Edges in the graph reflect intraprocedural control flow, 
+flow of control from a caller to a callee (edges from call-nodes to start-nodes), or
+flow of control from a callee back to a caller (edges from end-nodes to return-nodes).
+
+In the case of our example, the control flow within each of the methods is straightforward and
+all interesting issues arise from interprocedural control flow. In particular,
+note that, since the variable \code{a} may point to either an \code{A}-object or a \code{B}-object, 
+the call on line~\ref{line:callfoo} may dispatch to either \code{A.foo()} or to \code{B.foo()},
+and this is reflected by edges  
+  from the node labeled $\code{call}_\code{foo}$ to the nodes labeled
+  $\code{Start}_\code{A.foo()}$ and $\code{Start}_\code{B.foo()}$
+and by edges
+  from the nodes labeled $\code{End}_\code{A.foo}$ and $\code{End}_\code{B.foo}$ 
+  to the node labeled  $\code{return}_\code{foo}$.  
+Similarly, there are edges from the node labeled $\code{call}_\code{bar}$ to the nodes 
+$\code{Start}_\code{A.bar()}$ and $\code{Start}_\code{B.bar()}$, and 
+edges
+  from the nodes labeled $\code{End}_\code{A.bar}$ and $\code{End}_\code{B.bar}$ 
+  to the node labeled  $\code{return}_\code{bar}$.
+
+Informally speaking, an IFDS-based dataflow analysis propagates dataflow facts along the edges
+of a control flow supergraph such as the one in Figure~\ref{fig:examplesupergraph}. The
+IFDS algorithm was carefully designed to avoid infeasible paths that may arise in the
+presence of multiple calls to the same method. However, in this example all methods are
+called in exactly one place, so IFDS is unable to eliminate dataflow along any of the
+paths shown in the figure. As a result, an IFDS-based taint analysis such as the
+one of \TODO{cite} would report that the secret value read on line~\ref{line:Afoo}
+might flow to the print statement on line~\ref{line:Bbar}.
+
+As we discussed previously, the calls to \code{foo()} and \code{bar()} may dispatch
+to different implementations of these methods in classes \code{A} and \code{B}, 
+because the variable \code{a} that serves as the receiver for the call may be bound to
+ objects of type \code{A} or type \code{B} at run time. 
+However, consider the fact that the methods \code{foo()} and \code{bar()} are invoked
+on \textit{the same object}. This means that the behaviors of the two method calls
+are \textit{correlated}: if the call to \code{foo()} dispatches to \code{A.foo()},
+then the call to \code{bar()} must dispatch to \code{A.bar()}, and if the call
+to \code{foo()} dispatches to \code{B.foo()}, then the call to \code{bar()} must 
+dispatch to \code{B.bar()}.  Consequently, paths such as the one highlighted in
+Figure~\ref{fig:examplesupergraph} where the call to \code{foo()} dispatches 
+to \code{A.foo()} and where the call to \code{bar()} dispatches to \code{B.bar()}
+are infeasible.
+
+The main contribution of this paper is an algorithm for transforming an IFDS problem 
+into an IDE problem in which the feasibility of paths in the presence of 
+correlated is encoded into the environment functions. 
+Informally speaking, our approach associates with each edge in an (exploded) 
+interprocedural control flow graph a function that records the types of 
+variables that are used as the receiver of correlated method calls. Paths that 
+are composed of edges in which the same receiver expression has different types
+are infeasible, and the propagation of dataflow facts along such paths is
+prevented. Applying our technique to an IFDS-based taint analysis would enable
+the resulting IDE-based taint analysis to determine that no secret value can flow from
+line~\ref{line:Afoo} to the print statement on line~\ref{line:Bbar}.
+
+\commentout{
 
@@
 However, there cannot be an execution path through \verb'A.foo' and \verb'B.bar' or through \verb'B.foo' and \verb'A.bar'.
-
-\begin{figure}
-  \centering
-  \begin{minipage}{\textwidth}
-    \inputMinted{java}{ccexample.java}
-  \end{minipage}
-  \caption{Example program containing correlated calls}
-  \label{list:ccexample}
-\end{figure}
 
@@
 }
+}

### 2014-12-11 code/ccexample.java

@@ -1,25 +1,16 @@
 class A {
-  String foo {
-    return secret();
-  }
-  
-  void bar(String s) {}
+  String foo { return secret(); } /*@\label{line:Afoo}@*/
+  void bar(String s) {} /*@\label{line:Abar}@*/
 }
-
 class B extends A {
-  String foo {
-    return "not secret";
-  }
-  
-  void bar(String s) {
-    System.out.println(s);
-  }
+  String foo { return "not secret"; } /*@\label{line:Bfoo}@*/
+  void bar(String s) { System.out.println(s); } /*@\label{line:Bbar}@*/
 }
 
 class Main {
   public static void main(String[] args) {
-    A a = args == null ? new A() : new B();
-    String v = a.foo();
-    a.bar(v);
+    A a = (args == null) ? new A() : new B(); /*@\label{line:createObject}@*/
+    String v = a.foo(); /*@\label{line:callfoo}@*/
+    a.bar(v); /*@\label{line:callbar}@*/
   }
 }

### 2014-12-12 content/related.tex
pass through related work

@@
 \section{Related Work}
-IFDS is a version of the functional approach to data-flow analysis developed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.
+\otodo{Should we remove first initials in this section?}
+The IFDS algorithm is an instance of the functional approach to data-flow analysis developed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.
 \commentout{
@@
 }
-IFDS has been used to encode a variety of data-flow problems, for~example, typestate analysis%
-\commentout{(determining which operations can be performed on an object at a given program point)}~\cite{naeem2008typestate,DBLP:conf/pldi/ZhangMGNY14} or shape analysis%
-\commentout{(detecting errors and validating properties of programs at compile time)}
+IFDS has been used to encode a variety of data-flow problems such as typestate analysis%
+\commentout{(determining which operations can be performed on an object at a given program point)}~\cite{naeem2008typestate,DBLP:conf/pldi/ZhangMGNY14} and shape analysis%
+\commentout{(detecting errors and validating properties of programs at compile time)}%
 ~\cite{DBLP:conf/birthday/KreikerRRSWY13}.
@@
 
-IFDS is implemented for two popular static-analysis frameworks for Java bytecode, the T.J.~Watson Libraries for~Analysis (WALA)~\cite{fink2012wala} and Heros~\cite{bodden2012inter}.
+The IFDS algorithm is implemented in two popular static-analysis frameworks for Java bytecode, the T.~J.~Watson Libraries for~Analysis (WALA)~\cite{fink2012wala} and Heros~\cite{bodden2012inter}.
 
@@
 
+Several extensions of the IFDS algorithm have been proposed to improve its precision,
+efficiency, and expressiveness. N.~Naeem and O.~Lhot\'ak~\cite{naeem2010pei} propose
+four extensions: two to improve efficiency on certain kinds of IFDS problems,
+one to improve expressiveness to a wider range of IFDS problems, and one
+to improve precision when applying the IFDS algorithm to programs in SSA form.
+All of these extensions are orthogonal to and could be combined with the approach
+that we present in this paper. In contrast to these techniques, our approach targets
+analysis precision, not efficiency or expressiveness.
+
+\commentout{
 Work on improving the IFDS algorithm includes the Practical Extensions to the IFDS algorithm~\cite{naeem2010pei}.
@@
 Thus, an IFDS analysis could benefit from both precision improvements independently.
+}
 
-Another work on improving the efficiency of the IFDS algorithm is E.\,Bodden et~al.'s framework for the analysis of software products lines~\cite{bodden2013spl}.
-Their paper uses transformations from IFDS to IDE problems, a technique we also employ.
-Finally, J.\,Rodriguez and O.\,Lhot\'ak implemented a concurrent version of the IFDS algorithm using actors~\cite{rodriguez2010concurrent}.
-However, neither of those works is concerned with improving the precision of IFDS results.
+Two other extensions target efficiency. E.\,Bodden et~al.~\cite{bodden2013spl} presents a framework
+for applying IFDS analyses to software product lines. Their approach enables the analysis of
+all possible products derived from a product line in a single analysis pass. Like our approach,
+their approach transforms IFDS problems to IDE problems. The micro-functions keep track
+of the possible program variations specified by the product line.
+J.\,Rodriguez and O.\,Lhot\'ak evaluate a parallelized implementation of the IFDS algorithm using actors~\cite{rodriguez2010concurrent} that can take advantage of multiple processors.
+%However, neither of those works is concerned with improving the precision of IFDS results.
 
@@
 
+M.~Sridharan et~al.'s improvements to the precision of pointer analysis
+for JavaScript programs~\cite{DBLP:conf/ecoop/SridharanDCST12} also
+eliminate infeasible paths. However, instead of infeasible paths
+between dynamically dispatched method calls, their approach eliminates
+infeasible paths between reads and writes of different properties
+(the JavaScript analogue of fields) of an object. Unlike in more static languages,
+property names in JavaScript are first class values (strings). When a loop indexed by
+property names updates the properties of objects, the loop body is extracted into a function
+and analyzed context sensitively with a separate context for each property name.
+The approach differs from ours in that it targets points-to analysis rather
+than IFDS analyses, in that it targets infeasible paths due to different
+property names rather than different dynamically dispatched methods,
+and in that it employs context sensitivity to improve precision.
+
+\commentout{
 The idea of eliminating infeasible paths caused by correlated calls is similar to M.~Sridharan et~al.'s work on improving the precision of pointer analysis for JavaScript programs~\cite{DBLP:conf/ecoop/SridharanDCST12}.
@@
 \end{itemize}
+}

### 2014-12-12 content/background.tex
addressing comments

@@
        could say that all lattices considered in this paper are complete, etc.}
-\ftodo{Can we define the symbols $\sqcup$ and $\sqcap$ for join and meet here?}
-A \textit{complete lattice} is a partially ordered set $(S,\sqsubseteq)$ in which every subset has a least upper bound and a greatest lower bound.
+%\ftodo{Can we define the symbols $\sqcup$ and $\sqcap$ for join and meet here?}
+A \textit{complete lattice} is a partially ordered set $(S,\sqsubseteq)$ in which every subset has a least upper bound, called \textit{join} or $\sqcup$, and a greatest lower bound, called \textit{meet} or $\sqcap$.
 A \textit{complete meet semilattice} is a partially ordered set in which every subset need only have a greatest lower bound.
@@
 }
+\otodo{What do you mean by $\Delta$?}
 Thanks to distributivity, every environment transformer 
@@
   without using much space by referring to an existing figure elsewhere in the paper?}
+\otodo{I have the todo on the previous page to add text referring to the example in Figure 3.}

### 2014-12-12 content/appendix.tex
working on proofs

@@
 
-Finally, we present the proof for Lemma~\ref{lem:onlycorrec} which states that a correlated-calls analysis that considers all receivers computes the same result as an analysis that considers only correlated-call receivers.
+Finally, we present the proof for Lemma~\ref{lem:onlycorrrec} which states that a correlated-calls analysis that considers all receivers computes the same result as an analysis that considers only correlated-call receivers.
 
 \begin{proof}[\textbf{Proof of Lemma~\ref{lem:onlycorrrec}}]
-  From~\eqref{eq:ucc} we know that
+  From Section~\ref{sec:ideToIfds} we know that
+  \[
+    \backCC(\resultIDE\left(\transCC_R(P)\right))
+    =\lambda n.\{d\,|\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\topcc\}\,.
+  \]
+  We can rewrite this equation as follows:
+  \[
+    \backCC(\resultIDE\left(\transCC_R(P)\right))
+    =\lambda n.\{d\,|\,\forall r,\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\topcc\}\,.
+  \]
+
   \begin{align*}

### 2014-12-12 content/impl.tex
addressing comments
working on proofs

@@
 Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
-and $\top$ means unreachable. Therefore, a result $\rho$ of the equivalence IDE analysis
+and $\top$ means unreachable.
+\mtodo{Should it be $\topcc$ and $\botcc$?}
+Therefore, a result $\rho$ of the equivalence IDE analysis
 is converted to an IFDS result as follows:

### 2014-12-12 content/impl.tex
proof of Lemma 4

--- 2014-12-11 content/impl.tex
@@
 for an IFDS problem $P$, the result $\resultIFDS$ has type
-$N \to D$. Similarly, for an IFDS problem $Q$, the result $\resultIDE$
+$N \to D$.
+\mtodo{Should it be $N^*$ and $\resultIDE(Q)$?}
+Similarly, for an IFDS problem $Q$, the result $\resultIDE$
 has type $N \to D \times L$.
@@
 Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
-and $\top$ means unreachable. Therefore, a result $\rho$ of the equivalence IDE analysis
+and $\top$ means unreachable.
+Therefore, a result $\rho$ of the equivalence IDE analysis
 is converted to an IFDS result as follows:
 $\backEq(\rho) = \lambda n.\{d\mid\rho(n) = (d,\top)\}$.
+\mtodo{For the proofs, instead of talking about the transformation for an equivalence-IDE problem,
+we should talk about the equivalence transformation for any IDE problem. So we should define
+$\backEq(\rho) = \lambda n.\{d\mid\rho(n) = (d,\ell),\,\ell\ne\topcc\}$.}
 
@@
 converted to an IFDS result as follows:
-$\backCC(\rho) = \lambda n.\{d\mid\rho(n) = (d,\ell), \forall r\,.\, \ell(r) \neq \top\}$.
+$\backCC(\rho) = \lambda n.\{d\mid\rho(n) = (d,\ell), \forall r\,.\, \ell(r) \neq \top\}$.\mtodo{Should it be $\ell(r)\ne\top_T$?}
 
@@
 \subsection{Implementation of Correlated Calls Micro-Functions}
-\otodo{move material from following section here}
+%\otodo{move material from following section here}
 

### 2014-12-12 content/appendix.tex

@@
 \begin{proof}[\textbf{Proof of Lemma~\ref{lem:subsetifds}}]
+  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
+  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
+  \begin{equation}
+    \resultIFDS(P)=\lambda n\,.\,\mvp F(n).
+  \end{equation}
   The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
   \begin{align*}
-    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)&=\{(n',\,D_n'^\Subset(\resultIDE(\transCC_R(P))))\ |\ n\in N^*\}(n)\\
-      &=D_n^\Subset(\resultIDE(\transCC_R(P)))\\
-      &\subseteq\mvp F(n)\\
-      &=\resultIFDS(P)(n)\,.\qedhere
+    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
+    &=\left(\lambda n'\,.\,\left\{d\,|\,\resultIDE(\transCC_R(P))(n')=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\top_T\right\}\right)(n)\\
+    &=\left\{d\,|\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\top_T\right\}\\
+    &\subseteq\left\{d\,|\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\ell\ne\topcc\right\}\\
+    &=\backEq\left(\resultIDE(\transCC_R(P))(n)\right)\,.\qedhere
   \end{align*}

### 2014-12-12 content/appendix.tex
removing notion of set of functions with given signature; working on proofs

@@
   \begin{equation}
-    \resultIFDS(P)=\lambda n\,.\,\mvp F(n).
+    \resultIFDS(P)=\lambda n\,.\,\mvp F(n)\,.
   \end{equation}
@@
     \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
-    &=\left(\lambda n'\,.\,\left\{d\,|\,\resultIDE(\transCC_R(P))(n')=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\top_T\right\}\right)(n)\\
-    &=\left\{d\,|\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\top_T\right\}\\
-    &\subseteq\left\{d\,|\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\ell\ne\topcc\right\}\\
-    &=\backEq\left(\resultIDE(\transCC_R(P))(n)\right)\,.\qedhere
+    &=\left(\lambda n'\,.\,\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\right)(n)\\
+    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\\
+    &\subseteq\left\{d\,|\,\resultIDE(\transCC_R(P))(n)(d)\ne\topcc\right\}\\
+    &=\backEq\left(\resultIDE(\transCC_R(P))(n)\right).\qedhere
   \end{align*}
@@
       \end{enumerate}
-    \item\label{item:callstart} $e_k$ is a call-start edge with signature $s_\mathcal F$, and $f\in\mathcal F$ is the called procedure.
+    \item\label{item:callstart} $e_k$ is a call-start edge with signature $s$, and $f$ is the called procedure.
       Then
@@
           \efek
-          &=(\lambda m\,.\,m[r'\to m(r')\cap\tau(s_\mathcal F,\,f)])(\Delta)(r)\\
-          &=\Delta[r'\to\Delta(r')\cap\tau(s_\mathcal F,\,f)]\,,
+          &=(\lambda m\,.\,m[r'\to m(r')\cap\tau(s,\,f)])(\Delta)(r)\\
+          &=\Delta[r'\to\Delta(r')\cap\tau(s,\,f)]\,,
         \end{align*}
@@
       \begin{itemize}
-        \item If $r'=r$, then $\Delta(r')=\Delta(r)$ which contains $t$. Since $t\in\tau(s_\mathcal F,\,f)$, it follows that $t\in\Delta(r)\cap\tau(s_\mathcal F,\,f)$, and $t\in\efek$.
+        \item If $r'=r$, then $\Delta(r')=\Delta(r)$ which contains $t$. Since $t\in\tau(s,\,f)$, it follows that $t\in\Delta(r)\cap\tau(s,\,f)$, and $t\in\efek$.
          \item If $r'\ne r$, see~(\ref{item:defaultmap}).
        \end{itemize}
-    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_k\in R$ are the local variables in the callee method, $r'$ is the receiver of the call site corresponding to the return node $n_k$, and $f\in\mathcal F$ is the called method with signature~$s_\mathcal F$.
+    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_k\in R$ are the local variables in the callee method, $r'$ is the receiver of the call site corresponding to the return node $n_k$, and $f$ is the called method with signature~$s$.
       Then 
       \[
-        \varepsilon_R(e_k)=\lambda m\,.\,m[r'\to m(r')\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_k\to\bot_T].
+        \varepsilon_R(e_k)=\lambda m\,.\,m[r'\to m(r')\cap\tau(s,\,f)][r_1\to\bot_T]\dots[r_k\to\bot_T].
       \]
@@
 
-    Assume that $e_k$ is a end-return edge with a call on the receiver $r'\in R$ with a signature $s_\mathcal F$ to a function $f\in\mathcal F$.
+    Assume that $e_k$ is a end-return edge with a call on the receiver $r'\in R$ with a signature $s$ to a function $f$.
     \begin{align*}
       \ccedgefn R&(e_k)(\mpdkm)(r)\\
-      &=\left(\lambda m\,.\,m[r'\to m(r)\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(\mpdkm)(r)\\
-      &=\left(\mpdkm[r'\to \uptau\cap\tau(s_\mathcal F,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(r)\,,
+      &=\left(\lambda m\,.\,m[r'\to m(r)\cap\tau(s,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(\mpdkm)(r)\\
+      &=\left(\mpdkm[r'\to \uptau\cap\tau(s,\,f)][r_1\to\bot_T]\dots[r_l\to\bot_T]\right)(r)\,,
     \end{align*}
@@
 
-    Otherwise, if $r=r'$, then $\efek=\uptau\cap\tau(s_\mathcal F,\,f)$.
+    Otherwise, if $r=r'$, then $\efek=\uptau\cap\tau(s,\,f)$.
 
     According to Lemma~\ref{lem:sound1} and by the induction hypothesis, the runtime type $t$ of $r$ must be contained in $\mpdkm(r)=\uptau$.
-At the same time, by definition, $t$ is part of $\tau(s_\mathcal F,\,f)$.
-Therefore, $t\in\uptau\cap\tau(s_\mathcal F,\,f)\subseteq\efek$, which means that $\efek\ne\top_T$.
+At the same time, by definition, $t$ is part of $\tau(s,\,f)$.
+Therefore, $t\in\uptau\cap\tau(s,\,f)\subseteq\efek$, which means that $\efek\ne\top_T$.
 
@@
 
+For the following proofs, recall from Section~\ref{sec:ideToIfds} that the result of an IDE analysis maps a lattice element to each node in the exploded supergraph.
+Specifically, for an IDE problem $Q$, the result $\resultIDE(Q):\ N^*\to D\times L$ maps nodes of the supergraph to pairs of data-flow facts and lattice elements~\cite{sagiv1996precise}:
+\begin{equation}\label{eq:ideresult}
+  \resultIDE(Q)=\lambda n\,.\,\lambda d\,.\,\mvp{\textsf{Env}}(n,\,d))\,.
+\end{equation}
+
 Finally, we can prove the Soundness Lemma.
 
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:sound}}] Let $\rho=\resultIDE(\transCC_R(P))$. Then
+\begin{proof}[\textbf{Proof of Lemma~\ref{lem:sound}}] 
+According to~\eqref{eq:ideresult}, we can rewrite~\eqref{eq:transCcDef} as
+\begin{equation}\label{eq:transCcResultCc}
+  \backCC(\resultIDE(\transCC_R(P)))(n)
+  =\{d\,|\,\forall r\in R\,.\,\mvp{\textsf{Env}}(n,\,d))(r)\ne\top_T\}.
+\end{equation}
+\mtodo{TODO rest of proof!}
+Let $\rho=\resultIDE(\transCC_R(P))$. Then
   \begin{align*}
@@
   \begin{enumerate}
-    \item $e_k$ is a call-start edge, $r'.c()$ is the call site at $n_{k-1}$ with signature $s_\mathcal F$, $f\in\mathcal F$ is the called procedure, and $r'\in U$.
+    \item $e_k$ is a call-start edge, $r'.c()$ is the call site at $n_{k-1}$ with signature $s$, $f$ is the called procedure, and $r'\in U$.
     Then
     \[
-      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\delta(m)(r)\cap\tau(s_\mathcal F,\,f)]\,.
+      \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)[r'\to\delta(m)(r)\cap\tau(s,\,f)]\,.
     \]
@@
         \[
-          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\cap\tau(s_\mathcal F,\,f).
+          \ccedgefn U(q')(\topcc)(r)=\delta(\ccedgefn U(q)(\topcc))(r)\cap\tau(s,\,f).
         \]
@@
 If $d_{k-1}\ne\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\ccedgefn U(q)(\topcc)(r)=\uptau$.
-The set $\tau(s_\mathcal F,\,f)$ is the same for either case.
+The set $\tau(s,\,f)$ is the same for either case.
 
@@
     \end{enumerate}
-    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_l\in U$ are the local variables in the callee method, $r'.c()$ is the call corresponding to the return node at $n_k$, $f\in\mathcal F$ is the called method with signature $s_\mathcal F$, and $r'\in U$.
+    \item $e_k$ is an end-return edge, $r_1,\,\dots,\,r_l\in U$ are the local variables in the callee method, $r'.c()$ is the call corresponding to the return node at $n_k$, $f$ is the called method with signature $s$, and $r'\in U$.
     Then
@@
       \ccedgefn U(e_k)=\lambda m\,.\,\delta(m)
-      [r'\to\delta(m)(r)\cap\tau(s_\mathcal F,\,f)]
+      [r'\to\delta(m)(r)\cap\tau(s,\,f)]
       [r_1\to\bot_T]\ldots[r_l\to\bot_T]\,.
@@
   \begin{equation}
-    \resultIDE\left(\transCC_S(P)\right)(n,\,d)(r)=
-    \resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r)\,.
+    \resultIDE\left(\transCC_S(P)\right)(n)(d)(r)=
+    \resultIDE(\transCC_{\{r\}}(P))(n)(d)(r)\,.
   \end{equation}
 \end{lemma}
-\begin{proof}
- Recall from Section~\ref{sec:ideToIfds} that the result of an IDE analysis maps a lattice element to each node in the exploded supergraph.
-Specifically, for an IDE problem $Q$, the result $\resultIDE(Q):\ N^\#\to L$ maps nodes of the exploded supergraph to lattice elements:
-\begin{equation}\label{eq:ideresult}
-  \resultIDE(Q)=\{((n,\,d),\,\mvp{\textsf{Env}}(n,\,d))\ |\ n\in N^*,\,d\in D\}\,.
-\end{equation}
-Furthermore, recall from Section~\ref{sec:bgide} that
+\begin{proof} Recall from Section~\ref{sec:bgide} that
 \begin{equation}\label{eq:mvpdef}
@@
   \begin{align}
-    \resultIDE\left(\transCC_S(P)\right)(n,\,d)(r)
+    \resultIDE\left(\transCC_S(P)\right)(n)(d)(r)
     &=\mvp{\textsf{Env}}(n,\,d)(r)\notag\\
@@
   \begin{align*}
-    \resultIDE\left(\transCC_S(P)\right)(n,\,d)(r)
+    \resultIDE\left(\transCC_S(P)\right)(n)(d)(r)
     &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\\
-    &=\resultIDE\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)\,.\qedhere
+    &=\resultIDE\left(\transCC_{\{r\}}(P)\right)(n)(d)(r)\,.\qedhere
   \end{align*}
@@
 
-The next lemma shows that the set of types to which a receiver is mapped in a correlated-calls lattice element can be represented as an intersection of static-type function applications $\tau(s_{\mathcal F_i},\,f_i)$.
+The next lemma shows that the set of types to which a receiver is mapped in a correlated-calls lattice element can be represented as an intersection of static-type function applications $\tau(s_i,\,f_i)$.
 \begin{lemma}\label{lem:edgefnThroughTaus}
   For an IFDS problem $P$, a node $n\in N^*$, and fact $d\in D$, let $p\in\mathsf{RP}(n,\,d)$ be a realizable path and $r\in R$ a receiver.
-Then there exists a non-negative number $\gamma$ of calls on the receiver $r$ with signatures $s_{\mathcal F_\gamma}$ to the functions $f_\gamma\in\mathcal F_\gamma$, for which
+Then there exists a non-negative number $\gamma$ of calls on the receiver $r$ with signatures $s_\gamma$ to the functions~$f_\gamma$, for which
   \[
     \ccedgefn{\{r\}}(p)(\topcc)(r)=
-      \bigcap_{\gamma\ge0}\tau(s_{\mathcal F_\gamma},\,f_\gamma)\,.
+      \bigcap_{\gamma\ge0}\tau(s_\gamma,\,f_\gamma)\,.
   \]
@@
     \begin{cases}
-      \botcc[r\to\tau(s_\mathcal F,\,f)]&\text{if $(n_k,\,n_{k+1})$ is a call-start or end-return edge, and}\\&\text{the call site $r.c()$ with signature $s_\mathcal F$ to the function}\\
-      &\text{$f\in\mathcal F$ corresponds to the call-start or end-return edge,}\\
+      \botcc[r\to\tau(s,\,f)]&\text{if $(n_k,\,n_{k+1})$ is a call-start or end-return edge, and}\\&\text{the call site $r.c()$ with signature $s$ to the function}\\
+      &\text{$f$ corresponds to the call-start or end-return edge,}\\
       \botcc&\text{otherwise\footnotemark.}
@@
 
-If $\beta=\botcc[r\to\tau(s_\mathcal F,\,f)]$, then 
+If $\beta=\botcc[r\to\tau(s,\,f)]$, then 
 \[
-  \ccedgefn{\{r\}}(p)(\topcc)(r)=\tau(s_\mathcal F,\,f)\,,
+  \ccedgefn{\{r\}}(p)(\topcc)(r)=\tau(s,\,f)\,,
 \]
@@
   \ccedgefn{\{r\}}(e_{k+l+1})(\topcc)(r)&=\ccedgefn{\{r\}}(p)(\topcc)(r)\\
-  &=\bigcap_{N}\tau(s_{\mathcal F_N},\,f_N)\,,
+  &=\bigcap_{N}\tau(s_N,\,f_N)\,,
 \end{align*}
@@
 
-Suppose that $e_{k+l+1}$ is a call-start edge with a call on the receiver $r$ with signature $s_\mathcal G$ to a function $g\in\mathcal G$. Then, according to~\eqref{eq:varepsilon}, 
+Suppose that $e_{k+l+1}$ is a call-start edge with a call on the receiver $r$ with signature $s$ to a function $g$. Then, according to~\eqref{eq:varepsilon}, 
 \[
-  \ccedgefn{\{r\}}(e_{k+l+1})=\lambda m\,.\,m[r\to m(r)\cap\tau(s_\mathcal G,\,g)]\,.
+  \ccedgefn{\{r\}}(e_{k+l+1})=\lambda m\,.\,m[r\to m(r)\cap\tau(s,\,g)]\,.
 \]
@@
   \ccedgefn{\{r\}}&(p')(\topcc)(r)\\
-  &=\lambda m\,.\,m[r\to m(r)\cap\tau(s_\mathcal G,\,g)]\left(\ccedgefn{\{r\}}(p)(\topcc)\right)(r)\\
-  &=\ccedgefn{\{r\}}(p)(\topcc)(r)\cap\tau(s_\mathcal G,\,g)\\
-  &=\left(\bigcap_{N}\tau(s_{\mathcal F_N},\,f_N)\right)\cap\tau(s_\mathcal G,\,g)\,,
+  &=\lambda m\,.\,m[r\to m(r)\cap\tau(s,\,g)]\left(\ccedgefn{\{r\}}(p)(\topcc)\right)(r)\\
+  &=\ccedgefn{\{r\}}(p)(\topcc)(r)\cap\tau(s,\,g)\\
+  &=\left(\bigcap_{N}\tau(s_N,\,f_N)\right)\cap\tau(s,\,g)\,,
 \end{align*}
@@
 \begin{proof} 
+Observe that if there is a supergraph path from a method call with signature $s$ to the start of $f$, then the set $\tau(s,\,f)$ is always non-empty.
+  Let $r.c()$ be a call on a receiver $r\in R$ with a method signature $s$ to a function $f$.
+  If the call site is monomorphic, then $\tau(s,\,f)$ contains all types $T'\subseteq T$ that are compatible with the static type of $r$.
+  If the call site is polymorphic, then $\tau(s,\,f)\subset T'$, since some types $t\in T'$ cause dispatch to a method other than~$f$.
+
  According to Lemma~\ref{lem:edgefnThroughTaus},
@@
    \ccedgefn{\{r\}}(p)(\topcc)(r)=
-      \bigcap_{\gamma\ge0}\tau(s_{\mathcal F_\gamma},\,f_\gamma).
+      \bigcap_{\gamma\ge0}\tau(s_\gamma,\,f_\gamma).
  \]
 
- Let $\tau_i=\tau(s_{\mathcal F_i},\,f_i)$. 
- For a given $k$, let $r.m_k()$ be the call site corresponding to $\tau_k$, and $T'$ the set of types compatible with the static type of $r$.
- Recall from Section~\ref{sec:ef} that 
+Let $\tau_i=\tau(s_i,\,f_i)$. 
+ For a given $k$, let $r.m_k()$ be the call site corresponding to $\tau_k$, and $T'$ the set of types compatible with the static type of $r$. Then the following is true:
  \begin{itemize}
@@
   \[
-    \resultIDE\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)=\top_T\,,
+    \resultIDE\left(\transCC_{\{r\}}(P)\right)(n)(d)(r)=\top_T\,,
   \]
@@
   \[
-    \resultIDE\left(\transCC_{\{r\}}(P)\right)(n,\,d)(r)=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
+    \resultIDE\left(\transCC_{\{r\}}(P)\right)(n)(d)(r)=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
   \]
@@
 \begin{proof}[\textbf{Proof of Lemma~\ref{lem:onlycorrrec}}]
-  From Section~\ref{sec:ideToIfds} we know that
-  \[
+  By definition of $\backCC$,
+  \begin{align*}
     \backCC(\resultIDE\left(\transCC_R(P)\right))
-    =\lambda n.\{d\,|\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\topcc\}\,.
-  \]
-  We can rewrite this equation as follows:
-  \[
-    \backCC(\resultIDE\left(\transCC_R(P)\right))
-    =\lambda n.\{d\,|\,\forall r,\,\resultIDE(\transCC_R(P))(n)=(d,\,\ell),\,\forall r\,.\,\ell(r)\ne\topcc\}\,.
-  \]
+    &=\{d\,|\,\resultIDE(\transCC_R(P))(n)(d)=\ell,\,\forall r\,.\,\ell(r)\ne\top_T\}\\
+    &=\{d\,|\,\forall r\in R,\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\}.
+  \end{align*}
 
+  \commentout{
   \begin{align*}
@@
   \end{align*}
-
-Since, according to Lemma~\ref{lem:ccrectop}, $\resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r)$ can only be equal to $\top_T$ when $r\in\rcc$, we can conclude that
-  \begin{align*}
-    D_n^\Subset&(\resultIDE(\transCC_R(P))))\\
-    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in\rcc}:\ \resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}\\
-    &=D_n^\Subset(\resultIDE(\transCC_\rcc(P)))).
-  \end{align*}
-
-  Therefore,
+  }
+Since, according to Lemma~\ref{lem:ccrectop}, $\resultIDE(\transCC_{\{r\}}(P))(n)(d)(r)$ can only be equal to $\top_T$ when $r\in\rcc$, we can conclude that
   \begin{align*}
     \backCC(\resultIDE\left(\transCC_R(P)\right))
-    &=\left\{(n,\,D_n^\Subset(\resultIDE(\transCC_\rcc(P))))\ |\ n\in N^*\right\}\\
-    &=\backCC(\resultIDE\left(\transCC_\rcc(P)\right))\,.\qedhere
+    &=\{d\,|\,\bm{\forall r\in\rcc},\,\resultIDE(\transCC_{\bm\rcc}(P))(n)(d)(r)\ne\top_T\}\\
+    &=\backCC(\resultIDE\left(\transCC_\rcc(P)\right)).
+    \qedhere
   \end{align*}

### 2014-12-12 content/impl.tex
removing notion of set of functions with given signature; working on proofs

--- 2014-12-11 content/impl.tex
@@
         &\begin{cases}
-            m[r\to m(r)\cap \tau(s_\mathcal F,\,f)],
+            m[r\to m(r)\cap \tau(s,\,f)],
             &\text{\parbox{75mm}{
@@
                 the call site at $\src e$, $f$ is the called
-                procedure with signature $s_\mathcal F$,
+                procedure with signature $s$,
                 and $r\in S$;}}\\[3ex]
         \parbox{30mm}{\[\begin{array}{l}
-                m[r\to m(r)\cap \tau(s_\mathcal F,\,f)]\\
+                m[r\to m(r)\cap \tau(s,\,f)]\\
             [v_1\to\bot_T] \ldots [v_k\to\bot_T],
@@
                 $f$ is the called method with
-                signature $s_\mathcal F$,
+                signature $s$,
                 $v_1,\,\dots,\,v_k\in S$ are the local variables
@@
 
-\subsection{Converting IDE Results to IFDS Results}\label{sec:ideToIfds}
+\subsection{Converting IDE Results to IFDS Results}\label{sec:ideToIfds}\mtodo{I changed the formalisms in this section. Please see if you agree to these changes.}
 
@@
 for an IFDS problem $P$, the result $\resultIFDS$ has type
-$N \to D$.\mtodo{Should it be $N^*$?} Similarly, for an IFDS problem $Q$, the result $\resultIDE$
-has type $N \to D \times L$.
+$N^* \to D$.
+Similarly, for an IDE problem $Q$, the result $\resultIDE(Q)$
+has type $N \to (D \to L)$.
 
 Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
-and $\top$ means unreachable. Therefore, a result $\rho$ of the equivalence IDE analysis
+and $\top$ means unreachable.
+Therefore, a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
 is converted to an IFDS result as follows:
-$\backEq(\rho) = \lambda n.\{d\mid\rho(n) = (d,\top)\}$.
+\begin{equation}\label{eq:transEqDef}
+  \backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
+\end{equation}
 
@@
 to the empty set of possible types means that the corresponding data flow path is
-infeasible. Therefore, a result $\rho$ of the correlated-calls IDE analysis is
+infeasible. Therefore, a result $\rho=\resultIDE(\transCC S(P))$ of the correlated-calls IDE analysis is
 converted to an IFDS result as follows:
-$\backCC(\rho) = \lambda n.\{d\mid\rho(n) = (d,\ell), \forall r\,.\, \ell(r) \neq \top\}$.
+\begin{equation}\label{eq:transCcDef}
+  \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)\neq\top_T\}.
+\end{equation}
 

### 2014-12-12 content/related.tex
removing notion of set of functions with given signature; working on proofs

@@
 \otodo{Should we remove first initials in this section?}
-The IFDS algorithm is an instance of the functional approach to data-flow analysis developed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.
+The IFDS algorithm is an instance of the functional approach to data-flow analysis developed by Sharir and Pnueli~\cite{pnueli1981two}.
 \commentout{
@@
 
-The IFDS algorithm is implemented in two popular static-analysis frameworks for Java bytecode, the T.~J.~Watson Libraries for~Analysis (WALA)~\cite{fink2012wala} and Heros~\cite{bodden2012inter}.
+The IFDS algorithm is implemented in two popular static-analysis frameworks for Java bytecode, the T.J.~Watson Libraries for~Analysis (WALA)~\cite{fink2012wala} and Heros~\cite{bodden2012inter}.
 
@@
 Several extensions of the IFDS algorithm have been proposed to improve its precision,
-efficiency, and expressiveness. N.~Naeem and O.~Lhot\'ak~\cite{naeem2010pei} propose
+efficiency, and expressiveness. Naeem and Lhot\'ak~\cite{naeem2010pei} propose
 four extensions: two to improve efficiency on certain kinds of IFDS problems,
@@
 
-Two other extensions target efficiency. E.\,Bodden et~al.~\cite{bodden2013spl} presents a framework
+Two other extensions target efficiency. Bodden et~al.~\cite{bodden2013spl} presents a framework
 for applying IFDS analyses to software product lines. Their approach enables the analysis of
@@
 of the possible program variations specified by the product line.
-J.\,Rodriguez and O.\,Lhot\'ak evaluate a parallelized implementation of the IFDS algorithm using actors~\cite{rodriguez2010concurrent} that can take advantage of multiple processors.
+Rodriguez and Lhot\'ak evaluate a parallelized implementation of the IFDS algorithm using actors~\cite{rodriguez2010concurrent} that can take advantage of multiple processors.
 %However, neither of those works is concerned with improving the precision of IFDS results.
@@
 
-The idea of using correlated calls to remove infeasible paths in data-flow analyses of object-oriented programs was introduced by F.\,Tip~\cite{DBLP:journals/scp/Tip15}.
+The idea of using correlated calls to remove infeasible paths in data-flow analyses of object-oriented programs was introduced by Tip~\cite{DBLP:journals/scp/Tip15}.
 The possibility of using IDE to achieve this is mentioned, but not elaborated upon.
@@
 
-M.~Sridharan et~al.'s improvements to the precision of pointer analysis
+Sridharan et~al.'s improvements to the precision of pointer analysis
 for JavaScript programs~\cite{DBLP:conf/ecoop/SridharanDCST12} also

### 2014-12-12 content/example.tex

@@
 The main contribution of this paper is an algorithm for transforming an IFDS problem 
-into an IDE problem in which the feasibility of paths in the presence of 
-correlated is encoded into the environment functions. 
-Informally speaking, our approach associates with each edge in an (exploded) 
+into an IDE problem that expresses the feasibility of paths
+in light of correlated calls.
+Informally speaking, our approach associates with each edge in an
 interprocedural control flow graph a function that records the types of 

### 2014-12-12 content/impl.tex
removing resultCC and resultEq

@@
 
-To summarize, Lemma~\ref{lem:sound} shows that the result $\resultCC$ of a correlated-calls analysis is sound since it overapproximates the data flow of all possible concrete execution paths.
-We have also shown in Lemma~\ref{lem:subsetifds} that the correlated-calls analysis improves the precision of the original IFDS result $\resultIFDS$, because the correlated-calls result $\resultCC$ underapproximates an equivalence-IDE result $\resultEq$.
-Finally, we showed in Lemma~\ref{lem:onlycorrrec} that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result $\resultCC$ that is obtained when considering all receivers $R$.
+To summarize, Lemma~\ref{lem:sound} shows that the result of a correlated-calls analysis is sound since it overapproximates the data flow of all possible concrete execution paths.
+We have also shown in Lemma~\ref{lem:subsetifds} that for an IFDS problem $P$, the correlated-calls analysis improves the precision of the original IFDS result $\resultIFDS(P)$, because the correlated-calls result $\resultIDE(\transCC(P))$ underapproximates an equivalence-IDE result $\resultIDE(\transEq(P))$.
+Finally, we showed in Lemma~\ref{lem:onlycorrrec} that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result that is obtained when considering all receivers $R$.
 

### 2014-12-12 content/example.tex
moving figure to separate file

@@
 
-\begin{figure}
-  \centering
-
-  \begin{minipage}{\textwidth}
-    \inputMinted{java}{ccexample.java}
-  \end{minipage}
-    \vspace*{-4mm}
-  \caption{Example program containing correlated calls}
-  \label{list:ccexample}
-
-   \begin{minipage}{\textwidth}
-    \tikzstyle{supergraph}=[
-      fill=greyblue,
-      rounded corners,
-      font=\footnotesize,
-      align=right,
-      text=charcoal,
-      drop shadow={ashadow, color=greyblue}
-    ]
-    \tikzstyle{supergraph_y}=[
-      fill=bisque,
-      rounded corners,
-      font=\footnotesize,
-      align=left,
-      text=charcoal,
-      drop shadow={ashadow, color=greyblue}
-    ]
-    \tikzstyle{supergraph_f}=[
-      fill=lightsalmonpink,
-      rounded corners,
-      font=\footnotesize,
-      align=left,
-      text=charcoal,
-      drop shadow={ashadow, color=greyblue}
-    ]
-    \tikzstyle{description}=[fill=white]
-    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
-    \tikzstyle{arrowtext}=[font=\tiny,color=black,above]
-
-\hspace*{-10pt}
-\begin{tikzpicture}
-\scalebox{.8}{
-% main method nodes
-    \node [supergraph] (st_main) {\textsf{start}$_{\texttt{main}}$};
-    \node [supergraph] (asgn_a) [below = \dist of st_main.south] {\texttt{a = args==null\,?}\\\texttt{new\,A()\,:\,new\,B()}};
-    \node [supergraph] (call_foo) [below = \dist of asgn_a.south] {\textsf{call}$_\texttt{foo}$};
-    \node [supergraph] (return_foo) [below = \dist of call_foo.south] {\textsf{return}$_\texttt{foo}$\\\texttt{v = a.foo()}};
-    \node [supergraph] (call_bar) [below = \dist of return_foo.south] {\textsf{call}$_\texttt{bar}$};
-    \node [supergraph] (return_bar) [below = \dist of call_bar.south] {\textsf{return}$_\texttt{bar}$};
-    \node [supergraph] (end_main) [below = \dist of return_bar.south] {\textsf{end}$_{\texttt{main}}$};
-
-% main method edges 
-    \path[->,ultra thick] (st_main) edge (asgn_a);
-    \path[->,ultra thick] (asgn_a) edge (call_foo);
-    \path[->] (call_foo) edge (return_foo);
-    \path[->,ultra thick] (return_foo) edge (call_bar);
-    \path[->] (call_bar) edge (return_bar);
-    \path[->,ultra thick] (return_bar) edge (end_main);
-
-%A.foo method nodes
-    \node [supergraph_y] (st_a_foo) [right = 5*\dist of st_main] {\textsf{start}$_{\texttt{A.foo}}$};
-    \node [supergraph_y] (return_secret) [below = \dist of st_a_foo.south] {\texttt{return secret()}};
-    \node [supergraph_y] (end_a_foo) [below = \dist of return_secret.south] {\textsf{end}$_\texttt{A.foo}$};
-
-%A.foo method edges
-    \path[->] (st_a_foo) edge (return_secret);
-    \path[->] (return_secret) edge (end_a_foo);
-
-%A.bar method nodes
-    \node [supergraph_y] (st_a_bar) [right = 5*\dist of st_a_foo] {\textsf{start}$_{\texttt{A.bar}}$};
-    \node [supergraph_y] (end_a_bar) [below = \dist of st_a_bar.south] {\textsf{end}$_\texttt{A.bar}$};
-
-%A.bar method edges
-    \path[->] (st_a_bar) edge (end_a_bar);
-
-%B.foo method nodes
-    \node [supergraph_f] (st_b_foo) [right = 5*\dist of call_bar] {\textsf{start}$_{\texttt{B.foo}}$};
-    \node [supergraph_f] (return_not_secret) [below = \dist of st_b_foo.south] {\texttt{return "not secret"}};
-    \node [supergraph_f] (end_b_foo) [below = \dist of return_not_secret.south] {\textsf{end}$_\texttt{B.foo}$};
-
-%B.foo method edges
-  \path[->] (st_b_foo) edge (return_not_secret);
-  \path[->] (return_not_secret) edge (end_b_foo);
-
-%B.bar method nodes
-    \node [supergraph_f] (st_b_bar) [right = 5*\dist of st_b_foo] {\textsf{start}$_{\texttt{B.bar}}$};
-    \node [supergraph_f] (print) [below = \dist of st_b_bar.south] {\texttt{print(s)}};
-    \node [supergraph_f] (end_b_bar) [below = \dist of print.south] {\textsf{end}$_\texttt{B.bar}$};
-
-%B.bar method edges
-  \path[->] (st_b_bar) edge (print);
-  \path[->] (print) edge (end_b_bar);
-
-%inter-procedural edges
-  \path[->,dashed,ultra thick] (call_foo) edge[out=20,in=190] (st_a_foo);
-  \path[->,dashed] (call_foo) edge[color=lightsalmonpink,out=-20,in=135] (st_b_foo);
-  \path[->,dashed] (call_bar) edge[out=25,in=220] (st_a_bar);
-  \path[->,dashed,ultra thick] (call_bar) edge[color=lightsalmonpink,out=18,in=160] (st_b_bar);
-  \path[->,dashed,ultra thick] (end_a_foo) edge[out=220,in=15] (return_foo);
-  \path[->,dashed] (end_b_foo) edge[color=lightsalmonpink,out=160,in=-60] (return_foo);
-  \path[->,dashed] (end_a_bar) edge[out=210,in=40] (return_bar);
-  \path[->,dashed,ultra thick] (end_b_bar) edge[color=lightsalmonpink,out=200,in=-40] (return_bar);
-
-%arrow description
-    \node [description] (intra_arrow_left) [above left = 2*\dist and 3.5*\dist of st_a_bar] {};
-    \node [description] (intra_arrow_right) [right = \dist of intra_arrow_left] {};
-    \node [description] (inter_arrow_left) [below = .5*\dist of intra_arrow_left] {};
-    \node [description] (inter_arrow_right) [below = .5*\dist of intra_arrow_right] {};
-    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intra-procedural edge} (intra_arrow_right);
-    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{inter-procedural edge} (inter_arrow_right); 
-}
-\end{tikzpicture}
-   \end{minipage}
-   \vspace*{-25mm}
-  \caption{
-    Control flow supergraph for the example program of Figure~\ref{list:ccexample}.
-    An infeasible path is shown in bold. 
-  }%
-  \label{fig:examplesupergraph}%
-\end{figure}
+\input{figures/fig-examplesupergraph}
 

### 2014-12-12 figures/fig-examplesupergraph.tex
moving figure to separate file

@@
-\begin{figure}%
+\begin{figure}
   \centering
+
+  \begin{minipage}{\textwidth}
+    \inputMinted{java}{ccexample.java}
+  \end{minipage}
+    \vspace*{-4mm}
+  \caption{Example program containing correlated calls}
+  \label{list:ccexample}
+
+   \begin{minipage}{\textwidth}
     \tikzstyle{supergraph}=[
@@
 % main method edges 
-    \path[->] (st_main) edge (asgn_a);
-    \path[->] (asgn_a) edge (call_foo);
+    \path[->,ultra thick] (st_main) edge (asgn_a);
+    \path[->,ultra thick] (asgn_a) edge (call_foo);
     \path[->] (call_foo) edge (return_foo);
-    \path[->] (return_foo) edge (call_bar);
+    \path[->,ultra thick] (return_foo) edge (call_bar);
     \path[->] (call_bar) edge (return_bar);
-    \path[->] (return_bar) edge (end_main);
+    \path[->,ultra thick] (return_bar) edge (end_main);
 
@@
 %inter-procedural edges
-  \path[->,dashed] (call_foo) edge[out=20,in=190] (st_a_foo);
+  \path[->,dashed,ultra thick] (call_foo) edge[out=20,in=190] (st_a_foo);
   \path[->,dashed] (call_foo) edge[color=lightsalmonpink,out=-20,in=135] (st_b_foo);
   \path[->,dashed] (call_bar) edge[out=25,in=220] (st_a_bar);
-  \path[->,dashed] (call_bar) edge[color=lightsalmonpink,out=18,in=160] (st_b_bar);
-  \path[->,dashed] (end_a_foo) edge[out=220,in=15] (return_foo);
+  \path[->,dashed,ultra thick] (call_bar) edge[color=lightsalmonpink,out=18,in=160] (st_b_bar);
+  \path[->,dashed,ultra thick] (end_a_foo) edge[out=220,in=15] (return_foo);
   \path[->,dashed] (end_b_foo) edge[color=lightsalmonpink,out=160,in=-60] (return_foo);
   \path[->,dashed] (end_a_bar) edge[out=210,in=40] (return_bar);
-  \path[->,dashed] (end_b_bar) edge[color=lightsalmonpink,out=200,in=-40] (return_bar);
+  \path[->,dashed,ultra thick] (end_b_bar) edge[color=lightsalmonpink,out=200,in=-40] (return_bar);
 
@@
 \end{tikzpicture}
-\caption{An example supergraph for Listing~\ref{list:ccexample}}%
+   \end{minipage}
+   \vspace*{-25mm}
+  \caption{
+    Control flow supergraph for the example program of Figure~\ref{list:ccexample}.
+    An infeasible path is shown in bold. 
+  }%
   \label{fig:examplesupergraph}%

### 2014-12-12 content/example.tex
moving commands to command and color files

@@
   \label{sec:MotivatingExample}
-
-\newcommand{\code}[1]{\textsf{#1}}  
-\definecolor{sh_comment}{rgb}{0.12, 0.38, 0.18}
-\definecolor{sh_keyword}{rgb}{0.37, 0.08, 0.25}  % #5F1441
-\definecolor{sh_string}{rgb}{0.06, 0.10, 0.98} % #101AF9
-\definecolor{KWColor}{rgb}{0.5,0,0.67}
-\definecolor{CommentColor}{rgb}{0.15,0.5,0.15}
-\lstdefinelanguage{scala}[]{Java}{
-   morekeywords={trait,def,object,with,override,val,type,var} 
-}
-
-\lstdefinestyle{Eclipse}{
-  xleftmargin=0pt,
-  language = scala,
-  basicstyle=\sffamily\small,
-  stringstyle=\color{sh_string},
-  keywordstyle = \color{sh_keyword}\bfseries,  %}
-  lineskip=-0.0em,
-  commentstyle=\color{sh_comment}\itshape,  
-  escapeinside={/*@}{@*/},
-  numbersep=5pt,
-  captionpos=b,
-  xleftmargin=0.4cm, xrightmargin=0.5cm,
-   morekeywords={invokestatic,invokeinterface,invokevirtual,invokespecial},
-}
-
-\lstset{
-  showspaces=false,showtabs=false,tabsize=2,columns=flexible,
-  morekeywords={trait,def,object,with},
-  language={scala},
-  style=Eclipse,
-  numbers=left,
-  numberstyle=\scriptsize\color{CommentColor},
-  firstnumber=last,
-  showstringspaces=true
-}
 

### 2014-12-12 content/example.tex
highlight and font

@@
 and this is reflected by edges  
-  from the node labeled $\code{call}_\code{foo}$ to the nodes labeled
-  $\code{Start}_\code{A.foo()}$ and $\code{Start}_\code{B.foo()}$
+  from the node labeled $\highlight{\code{call}_\code{foo}}{greyblue}$ to the nodes labeled
+  $\highlight{\code{start}_\code{A.foo()}}{bisque}$ and $\highlight{\code{start}_\code{B.foo()}}{lightsalmonpink}$
 and by edges
-  from the nodes labeled $\code{End}_\code{A.foo}$ and $\code{End}_\code{B.foo}$ 
-  to the node labeled  $\code{return}_\code{foo}$.  
-Similarly, there are edges from the node labeled $\code{call}_\code{bar}$ to the nodes 
-$\code{Start}_\code{A.bar()}$ and $\code{Start}_\code{B.bar()}$, and 
+  from the nodes labeled $\highlight{\code{end}_\code{A.foo}}{bisque}$ and $\highlight{\code{end}_\code{B.foo}}{lightsalmonpink}$ 
+  to the node labeled  $\highlight{\code{return}_\code{foo}}{greyblue}$.  
+Similarly, there are edges from the node labeled $\highlight{\code{call}_\code{bar}}{greyblue}$ to the nodes 
+$\highlight{\code{start}_\code{A.bar()}}{bisque}$ and $\highlight{\code{start}_\code{B.bar()}}{lightsalmonpink}$, and 
 edges
-  from the nodes labeled $\code{End}_\code{A.bar}$ and $\code{End}_\code{B.bar}$ 
-  to the node labeled  $\code{return}_\code{bar}$.
+  from the nodes labeled $\highlight{\code{end}_\code{A.bar}}{bisque}$ and $\highlight{\code{end}_\code{B.bar}}{lightsalmonpink}$ 
+  to the node labeled  $\highlight{\code{return}_\code{bar}}{greyblue}$.
 
@@
 Informally speaking, our approach associates with each edge in an
-interprocedural control flow graph a function that records the types of 
+interprocedural CFG a function that records the types of 
 variables that are used as the receiver of correlated method calls. Paths that 
@@
 line~\ref{line:Afoo} to the print statement on line~\ref{line:Bbar}.
+\mtodo{Maybe emphasize that more generally, the program is not
+considered to leak secret information, and not mention the line numbers?}
 

### 2014-12-12 content/impl.tex
highlight and font

@@
 
-  Returning a secret value in method \verb'A.foo' creates a ``diagonal'' edge from the $\Lambda$-fact to the secret fact $\psi$. 
+  Returning a secret value in method \code{A.foo} creates a ``diagonal'' edge from the $\Lambda$-fact to the secret fact $\psi$. 
   The diagonal edge is labeled with the micro function $\lambda m\,.\,\botcc$. Thus, at the end node of the method, every receiver is mapped to the set of all types~$\bot_T$.
 
-On the end-return edge from \verb'A.foo' to \verb'main', the set of types for the receiver \verb'a' is restricted by the micro function $\lambda m\,.\,m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$ on the edge corresponding to the assignment of the return value $\psi$ to \verb'v'.
+On the end-return edge from \code{A.foo} to \code{main}, the set of types for the receiver \code{a} is restricted by the micro function $\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code A\}]$ on the edge corresponding to the assignment of the return value $\psi$ to \code v.
 
-Similarly, on the call-start edge from \verb'main' to \verb'B.bar', the possible types
-of the receiver \verb'a' are further restricted by the micro-function
-$\lambda m\,.\,m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$.
-on the edge that passes the argument \verb'v' to the parameter \verb's'.
+Similarly, on the call-start edge from \code{main} to \code{B.bar}, the possible types
+of the receiver \code{a} are further restricted by the micro-function
+$\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code B\}]$.
+on the edge that passes the argument \code{v} to the parameter \code{s}.
 
 The composition of these micro functions results in the empty set as the possible
-types of the receiver \verb'a', indicating that this data flow path that would
+types of the receiver \code{a}, indicating that this data flow path that would
 result in an information leak is actually infeasible.

### 2014-12-12 content/example.tex
comment

@@
 may flow from ``sources'', which are typically statements that read untrusted input, 
-to ``sinks'', which are typically securitive-sensitive operations such as calls to 
+to ``sinks'', which are typically securitive-sensitive
+\mtodo{Should it be ``security-sensitive''?}
+operations such as calls to 
 a database. In previous research \TODO{cite}, taint analysis algorithms have been 

### 2014-12-12 content/background.tex
applying comments

@@
 %We will start by introducing several concepts used by the IFDS and IDE analyses.
-\begin{mdelete}\mtodo{We already say (but less precisely) what a CFG is in the introduction.}
 The \textit{control-flow graph} of a procedure is a directed graph whose nodes are instructions, and which contains an edge from $n_1$ to $n_2$ whenever
 $n_2$ may execute immediately after $n_1$. A CFG has a distinguished \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$.
-\end{mdelete}
 %and edges represent transfer of control between the instructions during an execution of the program. 
@@
   $\mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top)$,
-  \mtodo{I like that the text is now very compact. But I wonder if some of the formulas should be put
-  on a separate line and enumerated. For example, I need to reference the definition of $\textsf{MVP}_{\textsf{Env}}$ in the
-  proof, but since it's embedded in the text, I'm repeating the formula in the appendix and reference the section. Is that fine?}
 where $M_\textsf{Env}$ is extended from edges to paths by composition.

### 2014-12-12 content/example.tex
applying comments

--- 2014-12-12 content/example.tex
@@
 may flow from ``sources'', which are typically statements that read untrusted input, 
-to ``sinks'', which are typically securitive-sensitive operations such as calls to 
+to ``sinks'', which are typically security-sensitive
+operations such as calls to 
 a database. In previous research \TODO{cite}, taint analysis algorithms have been 

### 2014-12-12 content/impl.tex
applying comments

@@
 
-\mtodo{In Figure~\ref{fig:cc_edgefn_example}, should we say that $\psi$ corresponds to the function's return value?}
 \otodo{we agreed to move this figure to the initial example section}
@@
 
-  Returning a secret value in method \code{A.foo} creates a ``diagonal'' edge from the $\Lambda$-fact to the secret fact $\psi$. 
+  Returning a secret value in method \code{A.foo} creates a ``diagonal'' edge from the $\Lambda$-fact to the method's return value $r$. 
   The diagonal edge is labeled with the micro function $\lambda m\,.\,\botcc$. Thus, at the end node of the method, every receiver is mapped to the set of all types~$\bot_T$.
 
-On the end-return edge from \code{A.foo} to \code{main}, the set of types for the receiver \code{a} is restricted by the micro function $\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code A\}]$ on the edge corresponding to the assignment of the return value $\psi$ to \code v.
+On the end-return edge from \code{A.foo} to \code{main}, the set of types for the receiver \code{a} is restricted by the micro function $\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code A\}]$ on the edge corresponding to the assignment of the return value $r$ to \code v.
 
@@
 
-\subsection{Converting IDE Results to IFDS Results}\label{sec:ideToIfds}\mtodo{I changed the formalisms in this section. Please see if you agree to these changes.}
+\subsection{Converting IDE Results to IFDS Results}\label{sec:ideToIfds}
 

### 2014-12-13 content/intro.tex
eliminate TODOs in introduction; improve formatting of title

@@
 \footnote{ 
-  The labels $\resultIDE$, $\resultIFDS$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$
+  The labels %$\resultIDE$, $\resultIFDS$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$
   on edges in 
   Figure~\ref{fig:transformations} reflect a number of mappings and projections 
-  that will be defined in Section~\TODO{ref} and that can be ignored here.
-}.\mtodo{In the footnote, should we just say "the labels" since there are so many?}
+  that will be defined in Section~\ref{sec:ccdatastr} and that can be ignored here.
+}.
 
@@
 %
-Related work is discussed in Section~\TODO{ref}.
+Related work is discussed in Section~\ref{sec:Related}.
 %
-Finally, conclusions and directions for future work are presented in Section~\TODO{ref}.
-
-\commentout{
-Static program analysis aims to discover properties of computer programs without running them.
-Static analysis has applications in compiler optimization, development of programming tools, and computer security, among others.
-As an example, we might want to analyze a program to know which variables are constants. 
-We could then write a compiler optimization that ensures that the values of those variables are computed only once.
-Alternatively, we could use the information about constant variables in an integrated development environment; for instance, to notify the user when an if-expression executes only one of its branches because its test condition has a constant value.
-
-There are demonstrable limits on what information we can obtain about a program without running it.
-Rice's theorem states that verifying any non-trivial property of a program is an undecidable problem~\cite{rice1953classes}.
-However, it is sometimes possible to design an algorithm that \textit{over}- or \textit{underapproximates} the solution that we are seeking.
-
-\textit{Data-flow analysis} is an area of program analysis whose goal is to compute approximations of certain information (for example, which variables must be constants) for each program point.
-
-Other examples of data-flow analyses are \textit{reaching definitions} (finding out up to which instruction a given assignment of a variable must be valid) and \textit{available expressions} (retrieving the expressions in the program that do not need to be recomputed at a given program point).
-
-Another example of a data-flow analysis is \textit{taint analysis}~\cite{tripp2009taj}.
-Taint analysis discovers if ``secret'' values, like passwords or other confidential user information, can leak to an external observer.
-Methods that generate secret values, e.g.
-those that read user input, are called \textit{sources}.
-Methods that can leak information, e.g.
-those that write data to a file or send data through a network, are called \textit{sinks}.
-The goal of taint analysis is to find out whether data can propagate from sources to sinks.
-
-An important property of a data-flow analysis is \textit{precision}.
-Precision reflects how closely a data-flow-analysis result over- or underapproximates the information we are interested in.
-In the case of taint analysis, let $T$ be the number of sinks that the analysis considers to leak secret information, and $R$ the real number of potential information leaks.
-The smaller the difference between $T$ and $R$, the greater the precision of the taint analysis.
-
-Data-flow analyses operate on \textit{control-flow graphs} that model the order in which the instructions of a program are executed.
-A data-flow-analysis problem defines \textit{flow functions} that represent how data is propagated along the edges of the control-flow graph.
-The \textit{confluence operator} specifies how the data that has been computed along different paths should be merged when the paths join.
-
-Since a control-flow graph is an overapproximation of the possible flows of control in concrete executions of a program, the graph may contain \textit{infeasible} paths that cannot occur at runtime.
-
-One way to improve the precision of a data-flow analysis is to detect and eliminate infeasible paths.
-
-Our goal is to improve the precision of solutions to problems that can be solved by the \textit{Inter-procedural Finite Distributive Subset} (IFDS) algorithm~\cite{reps1995precise}.
-The IFDS algorithm is a general data-flow algorithm that can compute solutions to various data-flow problems, like reaching definitions, available expressions, and taint analysis.
-
-We improve the precision of IFDS problem solutions by eliminating infeasible paths that occur in object-oriented programs in the presence of \textit{correlated method calls}~--- polymorphic calls that are invoked on the same object~\cite{DBLP:journals/scp/Tip15}.
-}
+Finally, conclusions and directions for future work are presented in Section~\ref{sec:Conclusions}.

### 2014-12-13 content/impl.tex
fix ref in intro & mention proofs in supplemental materials

@@
 
-\section{Correlated Calls Analysis}\label{chapter:cca}
+\section{Correlated Calls Analysis}\label{sec:cca}
 The correlated-calls analysis is defined as a transformation from an arbitrary IFDS problem to a corresponding IDE problem.

### 2014-12-13 content/intro.tex
fix ref in intro & mention proofs in supplemental materials

@@
   Figure~\ref{fig:transformations} reflect a number of mappings and projections 
-  that will be defined in Section~\ref{sec:ccdatastr} and that can be ignored here.
+  that will be defined in Section~\ref{sec:cca} and that can be ignored here.
 }.
@@
 Section~\ref{sec:ccdatastr} presents the correlated-calls transformation
-and a proof of its correctness.
+and sketches a proof of its correctness%
+\footnote{
+  Detailed proofs of our lemmas and theorems can be found in
+  the supplemental materials that are included with this submission.
+}.
 %

### 2014-12-13 content/example.tex
additions to section 2

@@
 operations such as calls to 
-a database. In previous research \TODO{cite}, taint analysis algorithms have been 
-formulated as IFDS problems.
+a database. In previous research \cite{DBLP:conf/issta/GuarnieriPTDTB11,DBLP:conf/pldi/ArztRFBBKTOM14}, 
+taint analysis algorithms have been formulated as IFDS problems.
 
@@
 called in exactly one place, so IFDS is unable to eliminate dataflow along any of the
-paths shown in the figure. As a result, an IFDS-based taint analysis such as the
-one of \TODO{cite} would report that the secret value read on line~\ref{line:Afoo}
+paths shown in the figure. As a result, IFDS-based taint analysis algorithms such as
+\cite{DBLP:conf/issta/GuarnieriPTDTB11,DBLP:conf/pldi/ArztRFBBKTOM14} would report 
+that the secret value read on line~\ref{line:Afoo}
 might flow to the print statement on line~\ref{line:Bbar}.
@@
 line~\ref{line:Afoo} to the print statement on line~\ref{line:Bbar}.
-\mtodo{Maybe emphasize that more generally, the program is not
-considered to leak secret information, and not mention the line numbers?}
 
-\commentout{
-
-Consider a call site~$r.m()$ in an object-oriented programming language, where the variable~$r$ is the \textit{receiver} variable of the call site and $m$ is the name of the invoked method\footnote{We assume an internal representation of the program in which for each call site $e_r.m()$, the expression~$e_r$ has been evaluated to the variable~$r$.}.
-In the rest of the paper, we use the general term \textit{receiver} to mean a receiver variable.
-At runtime, the actual method that will be invoked by the call site depends on the runtime type of the object referenced by $r$.
-If the call site $r.m()$ can be associated with more than one method at compile time, we will say that the call site is \textit{polymorphic}.
-
-For example, in Listing~\ref{list:ccexample}, it is not possible to infer statically whether the runtime type of the variable \verb'a' in the \texttt{main} method is \verb'A' or \verb'B'.
-The call \verb'a.foo()' can be dispatched to either \verb'A.foo' or \verb'B.foo', and \verb'a.bar(v)' can be dispatched to either \verb'A.bar' or \verb'B.bar'.
-A concrete execution path for the main method might therefore go through \verb'A.foo' and \verb'A.bar', or through \verb'B.foo' and \verb'B.bar'.
-However, there cannot be an execution path through \verb'A.foo' and \verb'B.bar' or through \verb'B.foo' and \verb'A.bar'.
-
-We call the invocations to methods \verb'foo' and \verb'bar' \textit{correlated}.
-More generally, correlated calls occur when more than one polymorphic call is invoked on the same receiver variable.
-
-Suppose we wanted to perform a taint analysis on the program in Listing~\ref{list:ccexample}.
-Most dataflow-analysis algorithms, including IFDS, would conservatively assume that the call \verb'a.bar' could be dispatched to both \verb'A.bar' and \verb'B.bar', independently of what \verb'a.foo' had been dispatched to in the previous line.
-
-As a result, 
-such an analysis would consider a path through \verb'A.foo' and \verb'B.bar' feasible.
-This means that the variable \verb'v' would be considered secret.
-We would conclude that a secret value is passed to \verb'B.bar' and printed to the user.
-In other words, we would consider the program to leak secret information, which it does not do in any concrete execution.
-
-\commentout{
-Our technique for improving the precision of an IFDS result is based on transforming the original IFDS problem into a more expressive \textit{Inter-procedural Distributive Environment} (IDE) problem.
-IDE problems can be solved with the IDE algorithm which is a generalization of IFDS~\cite{sagiv1996precise}.
-The IDE algorithm can, for instance, solve certain versions of the constant propagation problem that IFDS cannot.
-
-To improve the precision of IFDS results, given an IFDS problem $P$, we convert it into an IDE problem $Q$ that accounts for correlated calls.
-We then use the IDE algorithm to obtain a solution to $Q$.
-Finally, we convert the IDE result into a IFDS result.
-In the presence of correlated calls, the obtained IFDS result can be more precise than the solution that the IFDS algorithm would compute for $P$.
-
-The goal of the correlated-calls analysis presented in this work is to modify the output of an IFDS analysis to account for correlated calls.
-Specifically, the correlated-calls analysis improves the precision of IFDS problem results by eliminating infeasible execution paths caused by correlated calls.
-This is done by converting the input-IFDS problem to an IDE problem that detects infeasible paths, and converting the IDE result back to a more precise IFDS result.
-
-The contributions of this work are:
-\begin{itemize}
-  \item A transformation from IFDS to IDE problems that considers correlated calls.
-  \item An implementation in Scala of the correlated-calls transformation and the IDE algorithm which is based on the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
-\end{itemize}\mtodo{Reference the figure here.}
-
-  We prove that the solution to an IDE problem that considers correlated calls is more precise than the solution to the original IFDS problem.
-  We also show that the correlated-calls analysis is sound, i.e.
-that it never considers concrete execution paths as infeasible.\mtodo{As discussed on the phone, we want to talk more about the results here.}
-
- Finally, we evaluate the effectiveness of the correlated-calls analysis using an implementation of taint analysis as the source IFDS problem.
-
-The remainder of this paper is organized as follows.
-In the next section, we describe the IFDS and IDE analyses in detail.
-In Section~\ref{chapter:cca} we present the correlated-calls analysis as a transformation of IFDS problems into a special kind of IDE problem.
-Section~\ref{sec:ccdatastr} describes an efficient representation of the data structures that are required to define a correlated-calls IDE transformation.
-In Section~\ref{chapter:eval} we address some implementation aspects of the correlated-calls analysis and present an evaluation of its results.
-Section~\ref{chapter:concl} contains concluding remarks.
-The proofs for the lemmas in the paper are provided in the Appendix.\mtodo{Reference appendix like this?}
-}
-}
+In summary, the example discussed in this section shows how the precision of 
+IFDS-based taint analysis can be improved by taking into account how paths
+become infeasible in the presence of correlated calls. In particular, we have
+shown how a false positive reported by a standard IFDS-based algorithm is eliminated.
+While the discussion in this section has focused on the specific problem of taint analysis,
+we would like to emphasize that our technique generally applies to \textit{any}
+dataflow analysis problem that can be expressed in the IFDS framework. This includes
+many common analysis tasks such as \TODO{please add a few examples + citations}

### 2014-12-15 content/appendix.tex
proofs of Lemmas 1 and 2

@@
 For the following proofs, recall from Section~\ref{sec:ideToIfds} that the result of an IDE analysis maps a lattice element to each node in the exploded supergraph.
-Specifically, for an IDE problem $Q$, the result $\resultIDE(Q):\ N^*\to D\times L$ maps nodes of the supergraph to pairs of data-flow facts and lattice elements~\cite{sagiv1996precise}:
+Specifically, for an IDE problem $Q$, the result $\resultIDE(Q):\ N^*\to(D\to L)$ maps nodes of the supergraph to pairs of data-flow facts and lattice elements~\cite{sagiv1996precise}:
 \begin{equation}\label{eq:ideresult}
@@
 
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:normeq}}]
-    Let $\updfun f^*=\setpair I U$.
-    For any $\tau\in T,$
-    \[
-        \begin{aligned}
-            \denote{\mathcal N(\updfun f^*)}(\tau)
-            &=\denote{\mathcal N(\langle I,\ U\rangle)}(\tau)\\
-            &=\denote{\setpair{I\cup U}U}(\tau)\\
-            &=\tau\cap(I\cup U)\cup U\\
-            &=(\tau\cap I)\cup(\tau\cap U)\cup U\\
-            &=\tau\cap I\cup U\\
-            &=\denote{\setpair IU}(\tau)\\
-            &=\denote{\updfun f^*}(\tau)\,.
-        \end{aligned}
-    \]
-    Thus, $\denote{\mathcal N(\updfun f^*)}=\denote{\updfun f^*}$.
+\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalEq}}]
+First, we need to show that for all $r\in R$ and ${m\in R\to2^T}$, if $I(r)=I'(r)$ and $U(r)=U'(r)$, then $\denote{\setpair IU}(m)(r)=\denote{\setpair{I'}{U'}}(m)(r)$. Indeed, we can see that
+\begin{align*}
+  \denote{\setpair IU}(m)(r)
+  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I(r'))\cup U(r')\right)(m)(r)\\
+  &=(m(r)\cap I(r))\cup U(r)\\
+  &=(m(r)\cap I'(r))\cup U'(r)\\
+  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I'(r'))\cup U'(r')\right)(m)(r)\\
+  &=\denote{\setpair{I'}{U'}}(m)(r).
+\end{align*}
+
+For the other direction, we need to show that if for any $r\in R$ and ${m\in R\to2^T}$, $(m(r)\cap I(r))\cup U(r)=(m(r)\cap I'(r))\cup U'(r)$, then for all $r'\in R$, $I(r')=I'(r')$ and $U(r')=U'(r')$.
+
+To prove that $U(r')=U'(r')$, we will pick $m(r)=\varnothing$.
+Then by our assumption, for all $r$, $U(r)=U'(r)$, and hence $U(r')=U'(r')$.
+
+To prove that $I(r')=I'(r')$, let us pick $m=I$. Then the assumption
+is $I(r)\cup U(r)=(I(r)\cap I'(r))\cup U'(r)$. By our definition, $U(r)\subseteq I(r)$, and we just proved that $U(r')=U'(r)$. Theorefore, $I(r)=(I(r)\cap I'(r))\cup U'(r)$.
+Additionally, $U'(r)\subseteq I'(r)$ and $U'(r)\subseteq I(r)$ (because $U'(r)=U(r)\subseteq I(r)$). This means that $U'(r)\subseteq I(r)\cap I'(r)$. Therefore, $I(r)=I(r)\cap I'(r)$,
+and we can conclude that $I(r)=I'(r)$.
 \end{proof}
 
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:normuneq}}]
-    Let us show that there always exists a set $\tau\subseteq T$ such that $\denote{\setpair IU}(\tau)\ne\denote{\setpair{I'}{U'}}(\tau)$. There are two cases:
-    \begin{enumerate}
-        \item $U\ne U'$. Then for the empty set $\tau=\varnothing$,
-            \[
-                \denote{\setpair IU}(\tau)=\denote{\setpair IU}(\varnothing)=(\varnothing\cap I)\cup U=U\,,
-            \]
-            whereas 
-            \[ 
-                \denote{\setpair {I'}{U'}}(\tau)=\denote{\setpair {I'}{U'}}(\varnothing)=(\varnothing\cap I')\cup U'=U'.
-            \]
-            Hence, $\denote{\setpair IU}\ne\denote{\setpair {I'}{U'}}$.
-        \item $I\ne I'$. Then for the set of all types $\tau=T$,
-            \[
-                \denote{\setpair IU}(\tau)=\denote{\setpair IU}(T)=(T\cap I)\cup U=I\cup U\,.
-            \]
-            Since $\setpair IU$ is normalized, $U\subseteq I$, and
-            \[
-                I\cup U= I\,.
-            \]
-            At the same time,
-            \[
-                \denote{\setpair {I'}{U'}}(\tau)=\denote{\setpair {I'}{U'}}(T)=(T\cap I')\cup U'=I'\cup U'=I'\,.
-            \]
-            Since $I\ne I'$, it follows that $\denote{\setpair IU}\ne \denote{\setpair {I'}{U'}}$. \qedhere
-    \end{enumerate}
+\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalComp}}]
+For all $r\in R$ and $m\in R\to2^T$,
+\begin{align*}
+  &\denote{\setpair IU\circ\setpair{I'}{U'}}(m)(r)\\
+  &=\denote{\setpair{\lambda r'\,.\,(I(r')\cap I'(r'))\cup U(r')}
+                    {\lambda r'\,.\,(I(r')\cap U'(r'))\cup U(r')}}(m)(r)\\
+  &=(m(r)\cap(I(r)\cap I'(r))\cup U(r))\cup(I(r)\cap U'(r))\cup U(r)\\
+  &=(m(r)\cap I'(r))\cup I(r)\cup (U'(r)\cap I(r))\cup U(r)\\
+  &=(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
+  &=\left(\lambda r'.(((m(r')\cap I'(r'))\cup U'(r'))\cap I(r'))\cup U(r')\right)(r)\\
+  &=\left(\lambda m'.\lambda r'.(m'(r')\cap I(r'))\cup U(r')\right)
+    \left(\left(\lambda m'.\lambda r'.(m'(r')\cap I'(r'))\cup U'(r')\right)  (m)\right)(r)\\
+  &=\left(\denote{\setpair IU}\circ\denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
+\end{align*}
+\end{proof}
+
+\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalMeet}}]
 \end{proof}

### 2014-12-15 content/impl.tex
proofs of Lemmas 1 and 2

@@
 \otodo{we agreed to move this figure to the initial example section}
-  \mtodo{Move Figure~\ref{fig:cc_edgefn_example} up to where it's mentioned first? If yes, the caption won't make sense.}
 
@@
 The implementation of function application follows directly from the definition of
-the representation: $\setpair{I}{U}(m) = \lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
+the representation: $\setpair{I}{U}(m) = \lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.\mtodo{Should this be the denotation of $\setpair IU$?}
 
@@
 implementation of comparison corresponds to equality of the represented micro-functions:
-\begin{lemma}\label{lem:equal}
+\begin{lemma}\label{lem:equalEq}
     For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
@@
         \iff
-        \denote{\setpair{I}{U}} = \denote{\setpair{I'}{U'}}
+        \denote{\setpair{I}{U}} = \denote{\setpair{I'}{U'}}.
     \] 
@@
 of the denoted functions:
-\begin{lemma}\label{lem:equal}
+\begin{lemma}\label{lem:equalComp}
     For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
@@
         = 
-        \denote{\setpair{I}{U}} \circ \denote{\setpair{I'}{U'}}
+        \denote{\setpair{I}{U}} \circ \denote{\setpair{I'}{U'}}.
     \]
@@
 of the denoted functions:
-\begin{lemma}\label{lem:equal}
+\begin{lemma}\label{lem:equalMeet}
     For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
@@
         = 
-        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
+        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}.
     \]

### 2014-12-15 content/appendix.tex
proof for lemma 3
comment out efficiency proof
rearranging proofs

@@
 \section*{Appendix}
-In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:ccdatastr}.
+In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}.
+
+\subsection*{Representation of Micro Functions}
+We start by presenting the proofs to the lemmas about the representation of micro functions.
+
+\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalEq}}]
+First, we need to show that for all $r\in R$ and ${m\in R\to2^T}$, if $I(r)=I'(r)$ and $U(r)=U'(r)$, then $\denote{\setpair IU}(m)(r)=\denote{\setpair{I'}{U'}}(m)(r)$. Indeed, we can see that
+\begin{align*}
+  \denote{\setpair IU}(m)(r)
+  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I(r'))\cup U(r')\right)(m)(r)\\
+  &=(m(r)\cap I(r))\cup U(r)\\
+  &=(m(r)\cap I'(r))\cup U'(r)\\
+  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I'(r'))\cup U'(r')\right)(m)(r)\\
+  &=\denote{\setpair{I'}{U'}}(m)(r).
+\end{align*}
+
+For the other direction, we need to show that if for any $r\in R$ and ${m\in R\to2^T}$, $(m(r)\cap I(r))\cup U(r)=(m(r)\cap I'(r))\cup U'(r)$, then for all $r'\in R$, $I(r')=I'(r')$ and $U(r')=U'(r')$.
+
+To prove that $U(r')=U'(r')$, we will pick $m(r)=\varnothing$.
+Then by our assumption, for all $r$, $U(r)=U'(r)$, and hence $U(r')=U'(r')$.
+
+To prove that $I(r')=I'(r')$, let us pick $m=I$. Then the assumption
+is $I(r)\cup U(r)=(I(r)\cap I'(r))\cup U'(r)$. By our definition, $U(r)\subseteq I(r)$, and we just proved that $U(r')=U'(r)$. Theorefore, $I(r)=(I(r)\cap I'(r))\cup U'(r)$.
+Additionally, $U'(r)\subseteq I'(r)$ and $U'(r)\subseteq I(r)$ (because $U'(r)=U(r)\subseteq I(r)$). This means that $U'(r)\subseteq I(r)\cap I'(r)$. Therefore, $I(r)=I(r)\cap I'(r)$,
+and we can conclude that $I(r)=I'(r)$.
+\end{proof}
+
+\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalComp}}]
+For all $r\in R$ and $m\in R\to2^T$,
+\begin{align*}
+  &\denote{\setpair IU\circ\setpair{I'}{U'}}(m)(r)\\
+  &=\denote{\setpair{\lambda r'\,.\,(I(r')\cap I'(r'))\cup U(r')}
+                    {\lambda r'\,.\,(I(r')\cap U'(r'))\cup U(r')}}(m)(r)\\
+  &=(m(r)\cap(I(r)\cap I'(r))\cup U(r))\cup(I(r)\cap U'(r))\cup U(r)\\
+  &=(m(r)\cap I'(r))\cup I(r)\cup (U'(r)\cap I(r))\cup U(r)\\
+  &=(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
+  &=\left(\lambda r'.(((m(r')\cap I'(r'))\cup U'(r'))\cap I(r'))\cup U(r')\right)(r)\\
+  &=\left(\lambda m'.\lambda r'.(m'(r')\cap I(r'))\cup U(r')\right)
+    \left(\left(\lambda m'.\lambda r'.(m'(r')\cap I'(r'))\cup U'(r')\right)  (m)\right)(r)\\
+  &=\left(\denote{\setpair IU}\circ\denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
+\end{align*}
+\end{proof}
+
+\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalMeet}}]
+  For all $r\in R$ and $m\in R\to2^T$,
+\begin{align*}
+  &\left(\denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}\right)(m)(r)\\
+  &=(\denote{\setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}})(m)(r)\\
+  &=(m(r)\cap(I(r)\cup I'(r))\cup U(r)\cup U'(r)\\
+  &=(m(r)\cap I(r))\cup U(r)\cup(m(r)\cap I'(r))\cup U'(r)\\
+  &=\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)\\
+  &=\left(\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
+\end{align*}
+\end{proof}
+
+\commentout{
+\begin{proof}[\textbf{Proof of Lemma~\ref{lem:efficient}}]
+  \begin{enumerate}
+    \item The identity function is represented as
+      \[
+        \denote{\id}=\{(r,\,\langle \bot_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,;
+      \]
+      the top function is represented as
+      \[
+        \denote{\lambda m\,.\,\topcc}=\{(r,\,\langle \top_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,.
+      \]
+    \item Equations~\eqref{eq:compclosed} and~\eqref{eq:meetclosed} show that the representation of micro functions is closed under composition and meet.
+    \item To show that our representation for micro functions forms a lattice with finite height, let us first show that $\lcc_\rcc:\,\rcc\to2^T$ forms a lattice.
+Since $T$ is a finite set, $(2^T,\,\subseteq)$ is a finite-height lattice.
+$\rcc$ is a finite set.
+Hence, the mapping
+    \[
+      \rcc\mapsto2^T=\{(r,\,t)\,|\,r\in \rcc,\,t\in 2^T\}=\lcc_\rcc
+    \]        
+    also forms a finite-height lattice \cite{nielson1999principles}.
+
+    Furthermore, $\lcc_\rcc$ is a finite set. 
+    Every element of $\lcc_\rcc$ can be applied to $|\rcc|$ receivers, where each receiver is mapped to a set of types.
+There are $|\rcc|\cdot2^{|T|}$ different possibilities to form those mappings, so
+    \[
+      |\lcc_\rcc|=|\rcc|\cdot2^{|T|}.
+    \]
+    Therefore, $\lcc_\rcc\mapsto \lcc_\rcc$ also forms a finite-height lattice.
+    \item All operations can be computed in $O(\rcc\times T)$ time.
+Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
+    \item The space bound is $O(\rcc\times T)$.
+  \end{enumerate}
+\end{proof}
+}
 
@@
 
-We start by proving the Lemmas of Soundness and Precision of the correlated-calls analysis.
+In this part of the Appendix we prove the Lemmas of Soundness and Precision of the correlated-calls analysis.
 
@@
 \end{proof}
-
-\section*{Representation of Micro Functions}
-In this part of the appendix we present the proofs to the Lemmas related to the representation of micro functions with update maps.
-
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalEq}}]
-First, we need to show that for all $r\in R$ and ${m\in R\to2^T}$, if $I(r)=I'(r)$ and $U(r)=U'(r)$, then $\denote{\setpair IU}(m)(r)=\denote{\setpair{I'}{U'}}(m)(r)$. Indeed, we can see that
-\begin{align*}
-  \denote{\setpair IU}(m)(r)
-  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I(r'))\cup U(r')\right)(m)(r)\\
-  &=(m(r)\cap I(r))\cup U(r)\\
-  &=(m(r)\cap I'(r))\cup U'(r)\\
-  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I'(r'))\cup U'(r')\right)(m)(r)\\
-  &=\denote{\setpair{I'}{U'}}(m)(r).
-\end{align*}
-
-For the other direction, we need to show that if for any $r\in R$ and ${m\in R\to2^T}$, $(m(r)\cap I(r))\cup U(r)=(m(r)\cap I'(r))\cup U'(r)$, then for all $r'\in R$, $I(r')=I'(r')$ and $U(r')=U'(r')$.
-
-To prove that $U(r')=U'(r')$, we will pick $m(r)=\varnothing$.
-Then by our assumption, for all $r$, $U(r)=U'(r)$, and hence $U(r')=U'(r')$.
-
-To prove that $I(r')=I'(r')$, let us pick $m=I$. Then the assumption
-is $I(r)\cup U(r)=(I(r)\cap I'(r))\cup U'(r)$. By our definition, $U(r)\subseteq I(r)$, and we just proved that $U(r')=U'(r)$. Theorefore, $I(r)=(I(r)\cap I'(r))\cup U'(r)$.
-Additionally, $U'(r)\subseteq I'(r)$ and $U'(r)\subseteq I(r)$ (because $U'(r)=U(r)\subseteq I(r)$). This means that $U'(r)\subseteq I(r)\cap I'(r)$. Therefore, $I(r)=I(r)\cap I'(r)$,
-and we can conclude that $I(r)=I'(r)$.
-\end{proof}
-
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalComp}}]
-For all $r\in R$ and $m\in R\to2^T$,
-\begin{align*}
-  &\denote{\setpair IU\circ\setpair{I'}{U'}}(m)(r)\\
-  &=\denote{\setpair{\lambda r'\,.\,(I(r')\cap I'(r'))\cup U(r')}
-                    {\lambda r'\,.\,(I(r')\cap U'(r'))\cup U(r')}}(m)(r)\\
-  &=(m(r)\cap(I(r)\cap I'(r))\cup U(r))\cup(I(r)\cap U'(r))\cup U(r)\\
-  &=(m(r)\cap I'(r))\cup I(r)\cup (U'(r)\cap I(r))\cup U(r)\\
-  &=(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
-  &=\left(\lambda r'.(((m(r')\cap I'(r'))\cup U'(r'))\cap I(r'))\cup U(r')\right)(r)\\
-  &=\left(\lambda m'.\lambda r'.(m'(r')\cap I(r'))\cup U(r')\right)
-    \left(\left(\lambda m'.\lambda r'.(m'(r')\cap I'(r'))\cup U'(r')\right)  (m)\right)(r)\\
-  &=\left(\denote{\setpair IU}\circ\denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
-\end{align*}
-\end{proof}
-
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalMeet}}]
-\end{proof}
-
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:efficient}}]
-  \begin{enumerate}
-    \item The identity function is represented as
-      \[
-        \denote{\id}=\{(r,\,\langle \bot_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,;
-      \]
-      the top function is represented as
-      \[
-        \denote{\lambda m\,.\,\topcc}=\{(r,\,\langle \top_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,.
-      \]
-    \item Equations~\eqref{eq:compclosed} and~\eqref{eq:meetclosed} show that the representation of micro functions is closed under composition and meet.
-    \item To show that our representation for micro functions forms a lattice with finite height, let us first show that $\lcc_\rcc:\,\rcc\to2^T$ forms a lattice.
-Since $T$ is a finite set, $(2^T,\,\subseteq)$ is a finite-height lattice.
-$\rcc$ is a finite set.
-Hence, the mapping
-    \[
-      \rcc\mapsto2^T=\{(r,\,t)\,|\,r\in \rcc,\,t\in 2^T\}=\lcc_\rcc
-    \]        
-    also forms a finite-height lattice \cite{nielson1999principles}.
-
-    Furthermore, $\lcc_\rcc$ is a finite set. 
-    Every element of $\lcc_\rcc$ can be applied to $|\rcc|$ receivers, where each receiver is mapped to a set of types.
-There are $|\rcc|\cdot2^{|T|}$ different possibilities to form those mappings, so
-    \[
-      |\lcc_\rcc|=|\rcc|\cdot2^{|T|}.
-    \]
-    Therefore, $\lcc_\rcc\mapsto \lcc_\rcc$ also forms a finite-height lattice.
-    \item All operations can be computed in $O(\rcc\times T)$ time.
-Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
-    \item The space bound is $O(\rcc\times T)$.
-  \end{enumerate}
-\end{proof}

### 2014-12-15 content/impl.tex
proof for lemma 3
minor fix

@@
 to the empty set of possible types means that the corresponding data flow path is
-infeasible. Therefore, a result $\rho=\resultIDE(\transCC S(P))$ of the correlated-calls IDE analysis is
+infeasible. Therefore, a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
 converted to an IFDS result as follows:
@@
         = 
-        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}.
+        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}},
     \]
+    where
+    $\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
+     =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.\mtodo{I added the definition of the meet of two functions.}
 \end{lemma}

### 2014-12-15 content/background.tex
pass through section 3

@@
 This section defines basic terminology and presents the IFDS and IDE algorithms.
-\ftodo{
-  Shall we add a sentence saying that readers familiar with these algorithms may skip this section?
-}
+%\ftodo{
+  %Shall we add a sentence saying that readers familiar with these algorithms may skip this section?
+%}
 
@@
 %We will start by introducing several concepts used by the IFDS and IDE analyses.
+%\begin{mdelete}\mtodo{We already say (but less precisely) what a CFG is in the introduction.}
 The \textit{control-flow graph} of a procedure is a directed graph whose nodes are instructions, and which contains an edge from $n_1$ to $n_2$ whenever
 $n_2$ may execute immediately after $n_1$. A CFG has a distinguished \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$.
+Following the presentation of \cite{reps1995precise,sagiv1996precise}, we follow every
+call instruction with a no-op instruction, so that every \textit{call node} is immediately
+followed by a \textit{return node} in the CFG.
+%\end{mdelete}
 %and edges represent transfer of control between the instructions during an execution of the program. 
@@
 may be called from $c$, and an \textit{end-to-return} edge from the end node of the procedure back to the call instruction.
-\otodo{do we really need to extra "return nodes" that the IFDS/IDE papers add?}
+%\otodo{do we really need to extra "return nodes" that the IFDS/IDE papers add?}
 %is a control-flow graph
@@
 
-\otodo{do we ever use $\src$ and $\target$?}
+%\otodo{do we ever use $\src$ and $\target$?}
 We denote the source and end nodes of a graph edge $e$ as $\src e$ and $\target e$.
@@
 
-A path through the control-flow supergraph is \textit{valid} if every end-to-return edge on the path returns
-to the site of the most recent unmatched call. 
-\ftodo{Can we explain/define the notion of the ``most recent unmatched call'' more precisely?}
+A path through the control-flow supergraph is \textit{valid} if it follows the usual stack-based calling 
+discipline: every end-to-return edge on the path returns
+to the site of the most recent call that has not yet been matched by a return. 
+%\ftodo{Can we explain/define the notion of the ``most recent unmatched call'' more precisely?}
 The set of all valid paths from the program entry point to
 a node $n$ is denoted $\ivp(n)$.
-\otodo{Should we give a formal definition?}
+%\otodo{Should we give a formal definition?}
 
@@
 
-\otodo{The definitions that Marianna had were for \emph{complete}
-lattices/semilattices. All of the lattices in the context of IFDS/IDE
-are/must be complete. I'll just say that here.}
-\ftodo{Would it make sense to first the define the notion of a lattice without referring to its completeness?
-       This could be followed by defining what it means for a (semi)lattice to be complete, and then we
-       could say that all lattices considered in this paper are complete, etc.}
+%\otodo{The definitions that Marianna had were for \emph{complete}
+%lattices/semilattices. All of the lattices in the context of IFDS/IDE
+%are/must be complete. I'll just say that here.}
+%\ftodo{Would it make sense to first the define the notion of a lattice without referring to its completeness?
+       %This could be followed by defining what it means for a (semi)lattice to be complete, and then we
+       %could say that all lattices considered in this paper are complete, etc.}
 %\ftodo{Can we define the symbols $\sqcup$ and $\sqcap$ for join and meet here?}
-A \textit{complete lattice} is a partially ordered set $(S,\sqsubseteq)$ in which every subset has a least upper bound, called \textit{join} or $\sqcup$, and a greatest lower bound, called \textit{meet} or $\sqcap$.
-A \textit{complete meet semilattice} is a partially ordered set in which every subset need only have a greatest lower bound.
+A \textit{lattice}%
+\footnote{The definitions that we give here are of \textit{complete} lattices and semilattices.
+Since all of the (semi)lattices discussed in this paper are required to be complete, we omit the
+\textit{complete} qualifier.}
+is a partially ordered set $(S,\sqsubseteq)$ in which every subset has a least upper bound, called \textit{join} or $\sqcup$, and a greatest lower bound, called \textit{meet} or $\sqcap$.
+A \textit{meet semilattice} is a partially ordered set in which every subset need only have a greatest lower bound.
 The symbols $\bot$ and $\top$ are used to denote the greatest lower bound of $S$ and of the empty set, respectively.
-Since all of the (semi)lattices discussed in this paper are required to be complete, we will henceforth leave out the
-\textit{complete} qualifier.
 
@@
 %On the exploded graph, the composition of two functions is represented by the paths that are formed when the exploded-graph edges are combined.
-\otodo{The example used to say $R_f \circ R_g$, but I believe it showed $R_g \circ R_f$. I fixed it, but please check that this is correct.}
+%\otodo{The example used to say $R_f \circ R_g$, but I believe it showed $R_g \circ R_f$. I fixed it, but please check that this is correct.}
 
@@
 }
+
+\input{figures/fig-cc_edge_fn_example}
+%\mtodo{In Figure~\ref{fig:cc_edgefn_example}, should we say that $\psi$ corresponds to the function's return value?}
 \begin{example}
-  The exploded supergraph for Listing~\ref{list:ccexample} is shown in Figure~\ref{fig:cc_edgefn_example}.\mtodo{Tell the reader here to ignore the labels on the edges of the graph?}
+  The exploded supergraph for Listing~\ref{list:ccexample} is shown in Figure~\ref{fig:cc_edgefn_example}.
+  The labels on the edges will be explained in Section~\ref{sec:bgide}
   We can see that there is a realizable path
@@
 \begin{tikzpicture}[>=stealth,on grid, auto]
-    \node [n,label=$\Lambda$] (zero){};
+    \node [n,label=$\mathbf0$] (zero){};
     \node [n] (zero_) [below=\edge of zero] {};
@@
 with the same nodes~\footnote{The IDE literature uses the symbol $\Lambda$ for the node that
-    is denoted $\mathbf0$ in the IFDS literature.}
+    is denoted $\mathbf0$ in the IFDS literature. We use $\mathbf0$ throughout this paper for consistency.}
 and edges as a representation relation, except that each edge is labelled
@@
 \begin{align*}
-    R_t =& \{ \microedge{\Lambda}{\Lambda}{\lambda l.l} \} \cup
-    \{\microedge{\Lambda}{d_j}{\lambda l.t(\Omega)(d_j)} \mid d_j \in D\}\\
+    R_t =& \{ \microedge{\mathbf0}{\mathbf0}{\lambda l.l} \} \cup
+    \{\microedge{\mathbf0}{d_j}{\lambda l.t(\Omega)(d_j)} \mid d_j \in D\}\\
     &\cup
@@
 Let $\Omega = \lambda d.\top$ be the environment that maps every element of $D$ to $\top$.
-\ftodo{
-   What is the relationship between $\Omega$ and $\Delta$?
-}
-\otodo{What do you mean by $\Delta$?}
+%\ftodo{
+   %What is the relationship between $\Omega$ and $\Delta$?
+%}
+%\otodo{What do you mean by $\Delta$?}
 Thanks to distributivity, every environment transformer 
@@
 The functions $\lambda l. \cdots$ in this decomposition are the micro-functions that
-appear on the edges of the pointwise representation edges from $\Lambda$ to each $d_j$ and from
+appear on the edges of the pointwise representation edges from $\mathbf0$ to each $d_j$ and from
 each $d_i$ to each $d_j$.%
@@
 
-\otodo{Discuss the micro-functions in the example exploded supergraph in Figure 3.}
+%\otodo{Discuss the micro-functions in the example exploded supergraph in Figure 3.}
+\begin{example}
+    In the exploded supergraph in Figure~\ref{fig:cc_edgefn_example},
+    the micro-functions are shown as labels on the graph edges.
+    Every edge without an explicit label has the identity as its
+    micro-function. The micro-functions on the three edges from
+    the node \verb+return secret()+ to the node $\texttt{end}_\texttt{A.foo}$
+    together represent the environment transformer 
+    $\lambda e.e[\psi \to \lambda m.\bot \sqcap \lambda m.m]$.
+
+    To eliminate infeasible paths due to correlated calls, we encode the taint
+    analysis using environments $\textsf{Env}(D,L)$, where $D$ is the set of
+    variables and $L$ is a map from receiver variables to sets of possible
+    types. The interpretation of such an environment $e$ is that a given variable
+    $v \in D$ may contain a secret value in an exeuction in which the runtime
+    types of the objects pointed to be the receiver variables are in the sets
+    specified by $e(v)$.
+\end{example}
 
@@
 as exploded supergraph edges labelled with micro-functions.
-\mtodo{Should we cite the ``Practical extensions'' paper here that talks about the on-demand IFDS algorithm?}
+%\mtodo{Should we cite the ``Practical extensions'' paper here that talks about the on-demand IFDS algorithm?}
 Specifically,
@@
 \[
-  p=\left[(\startmain,\,\Lambda),\,(n_1,\,d_1),\,\dots,\,(n_k,\,d_k)\right]
+  p=\left[(\startmain,\,\mathbf0),\,(n_1,\,d_1),\,\dots,\,(n_k,\,d_k)\right]
 \]
@@
   f_p=\textsf{EdgeFn}((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))\,\circ\ldots\circ
-      \textsf{EdgeFn}(\startmain,\,\Lambda),\,(n_1,\,d_1))\,.
+      \textsf{EdgeFn}(\startmain,\,\mathbf0),\,(n_1,\,d_1))\,.
 \end{align}
@@
   without using much space by referring to an existing figure elsewhere in the paper?}
-\otodo{I have the todo on the previous page to add text referring to the example in Figure 3.}
+  \otodo{See Example 4 on the previous page.}

### 2014-12-15 content/datastr.tex
one more delete
pass through section 3

@@
   The edges of the exploded supergraph in Figure~\ref{fig:cc_edgefn_example} correspond to the edges of an IFDS taint analysis.
-We can see that there is a path from the node $(\highlight{\startmain}{greyblue},\,\Lambda)$ to $(\highlight{\texttt{print(s)}}{lightsalmonpink},\,\texttt s)$.
+We can see that there is a path from the node $(\highlight{\startmain}{greyblue},\,\mathbf0)$ to $(\highlight{\texttt{print(s)}}{lightsalmonpink},\,\texttt s)$.
 This means that the IFDS taint analysis considers \texttt s to be a secret value that is leaked at the print statement.
@@
 
+\begin{mdelete}
 \paragraph{Final Remarks}
@@
 The same argument applies to computing function meets.
+\end{mdelete}
 

### 2014-12-15 content/impl.tex
removing crossreferences, adding comment
pass through section 3

@@
-\input{figures/fig-cc_edge_fn_example}
-
-\otodo{we agreed to move this figure to the initial example section}
-
   \commentout{
@@
 to make
-the fact $d$ reachable. All other micro-functions are the identity\mtodo{``the identity function'' or is it okay ot just say ``the identity''?}.
+the fact $d$ reachable. All other micro-functions are the identity function.
+%\mtodo{``the identity function'' or is it okay ot just say ``the identity''?}.
 The equivalence transformation is thus defined as:
@@
 to the empty set of possible types means that the corresponding data flow path is
-infeasible. Therefore, a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
+infeasible. Therefore, a result $\rho=\resultIDE(\transCC S(P))$ of the correlated-calls IDE analysis is
 converted to an IFDS result as follows:

### 2014-12-15 content/related.tex
eliminate TODOs in introduction; improve formatting of title
pass through section 3

@@
 \section{Related Work}
-\otodo{Should we remove first initials in this section?}
+  \label{sec:Related}
+%\otodo{Should we remove first initials in this section?}
 The IFDS algorithm is an instance of the functional approach to data-flow analysis developed by Sharir and Pnueli~\cite{pnueli1981two}.

### 2014-12-15 content/impl.tex

@@
   \backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
-\end{equation}
+\end{equation}\mtodo{Another change was that Ondrej defined $\backEq$ as $\lambda n.\{d\mid\rho(n)(d)=\top\}$
+and that he defined $\backEq$ related to the equivalence transformation.}
 

### 2014-12-15 content/appendix.tex
minor fix
part of proof for lemma 5

@@
 \begin{align*}
-  &\left(\denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}\right)(m)(r)\\
+  \left(\denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}\right)&(m)(r)\\
   &=(\denote{\setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}})(m)(r)\\
@@
 We will denote the top element in the environment lattice as
-\begin{equation}
-  \Omega=\lambda d\,.\,\topcc\,.
-\end{equation}
+$\Omega=\lambda d\,.\,\topcc$.
 
@@
 According to~\eqref{eq:ideresult}, we can rewrite~\eqref{eq:transCcDef} as
-\begin{equation}\label{eq:transCcResultCc}
+\begin{align*}\label{eq:transCcResultCc}
   \backCC(\resultIDE(\transCC_R(P)))(n)
-  =\{d\,|\,\forall r\in R\,.\,\mvp{\textsf{Env}}(n,\,d))(r)\ne\top_T\}.
-\end{equation}
-\mtodo{TODO rest of proof!}
-Let $\rho=\resultIDE(\transCC_R(P))$. Then
-  \begin{align*}
-    \backCC(\rho)(n)
-    &=D_n^\Subset(\rho)\\
-    &=\left\{d'\ |\ 
-        d'\in\mvp F(n)\,\wedge\,\forall r\in R:\ \rho(n,\ d')(r)\ne\top_T\right\}.
+  &=\{d'\,|\,\forall r\in R\,.\,\mvp{\textsf{Env}}(n,\,d'))(r)\ne\top_T\}\\
+  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\menv(q)(\Omega)(d')(r)\ne\top_T\right\}\\
+  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d'}(r)\ne\top_T\right\}.
 \end{align*}
-  Since $\mvp F(n)=\bigsqcap_{q\in\ivp(n)}M_F(q)(\varnothing)$, and $p\in\ivp(n)$, it follows that
-    \begin{align*}
-      d&\in M_F(p)(\varnothing)\\&\subseteq\mvp F(n)\,.
-    \end{align*}
-  At the same time, for all receivers $r\in R$,
-  \begin{align*}
-    \rho(n,\,d)(r)
-    &=\left(\bigsqcap_{q\in\ivp(n)}\mpddef q d\right)(r)\\
-    &=\bigsqcap_{q\in\ivp(n)}\mpddef q d(r)\,.
-  \end{align*}
-  According to~Lemma~\ref{lem:sound3}, $\mpd(r)\ne\top_T$.
+  According to~Lemma~\ref{lem:sound3}, since $d\in M_F(p)(\varnothing)$, then $\mpd(r)\ne\top_T$.
   Since $p\in\ivp(n)$,

### 2014-12-15 content/background.tex
part of proof for lemma 5

--- 2014-12-12 content/background.tex
@@
 the \textit{meet-over-all-valid-paths} solution
-  $\mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top)$,
+  $\mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top)$,\mtodo{Should it be $\Omega$ instead of $\top$?}
 where $M_\textsf{Env}$ is extended from edges to paths by composition.

### 2014-12-15 figures/fig-cc_edge_fn_example.tex
applying comments

@@
-\begin{figure}%
+\begin{figure}[h!]%
   \centering
@@
 
-    \node [n,label=$\Lambda$] (st_main_z) [right=\nd of st_main.east] {};
+    \node [n,label=$\mathbf0$] (st_main_z) [right=\nd of st_main.east] {};
     \node [n,label=\texttt{v}] (st_main_v) [right=\nd of st_main_z] {};
@@
 
-    \node [n,label=$\psi$] (st_a_foo_p) [left=\nd of st_a_foo.west] {};
+    \node [n,label=$r$] (st_a_foo_p) [left=\nd of st_a_foo.west] {};
     \node [n] (return_secret_p) [left=\nd of return_secret.west] {};
     \node [n] (end_a_foo_p) [left=\nd of end_a_foo.west] {};
-    \node [n,label=$\Lambda$] (st_a_foo_z) [left=\nd of st_a_foo_p] {};
+    \node [n,label=$\mathbf0$] (st_a_foo_z) [left=\nd of st_a_foo_p] {};
     \node [n] (return_secret_z) [left=\nd of return_secret_p] {};
@@
     \node [n,label=\texttt{s}] (st_a_bar_s) [left=\nd of st_a_bar.west] {};
-    \node [n,label=$\Lambda$] (st_a_bar_z) [left=\nd of st_a_bar_s] {};
+    \node [n,label=$\mathbf0$] (st_a_bar_z) [left=\nd of st_a_bar_s] {};
     \node [n] (end_a_bar_s) [left=\nd of end_a_bar.west] {};    
@@
 
-    \node [n,label=$\Lambda$] (st_b_foo_z) [left=\nd of st_b_foo.west] {};
+    \node [n,label=$\mathbf0$] (st_b_foo_z) [left=\nd of st_b_foo.west] {};
     \node [n] (return_not_secret_z) [left=\nd of return_not_secret.west] {};
@@
     \node [n] (end_b_bar_s) [left=\nd of end_b_bar.west] {};
-    \node [n,label=$\Lambda$] (st_b_bar_z) [left=\nd of st_b_bar_s] {};
+    \node [n,label=$\mathbf0$] (st_b_bar_z) [left=\nd of st_b_bar_s] {};
     \node [n] (print_z) [left=\nd of print_s] {};
@@
 \end{tikzpicture}
-\caption[An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}]{An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}.
+\caption[An example program demonstrating correlated-call edge functions on the $\mathbf0$-node path for Listing~\ref{list:ccexample}]{An example program demonstrating correlated-call edge functions on the $\mathbf0$-node path for Listing~\ref{list:ccexample}.
 All non-labeled edges are implicitly labeled with identity functions $\id$.
-The variable corresponding to an initial secret value is denoted as $\psi$.}%
+The variable $\psi$ denotes the return value of the \texttt{A.foo} method.}%
   \label{fig:cc_edgefn_example}%  

### 2014-12-15 content/appendix.tex
todo comment
finished proof of lemma 5

@@
 \end{align*}
-  According to~Lemma~\ref{lem:sound3}, since $d\in M_F(p)(\varnothing)$, then $\mpd(r)\ne\top_T$.
-  Since $p\in\ivp(n)$,
-  \begin{align*}
-    \mpd(r)\subseteq\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)\,.
-  \end{align*}
-  From $\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)=\rho(n,\,d)(r)$ it follows that
-  $\mpd(r)\subseteq\rho(n,\,d)(r)$.
-  Therefore, $\rho(n,\,d)(r)\ne\top_T$, and $d\in D_n^\Subset(\rho)=\backCC(\rho)(n)$.
+  According to~Lemma~\ref{lem:sound3}, since $d\in M_F(p)(\varnothing)$, then for any $r\in R$, $\mpd(r)\ne\top_T$. 
+  Since $\mpd(r)$ is a non-empty set that is contained in $\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d}(r)$, it follows that $$\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d}(r)\ne\top_T.$$ Therefore, $d\in \backCC(\resultIDE(\transCC_R(P)))(n)$.
 \end{proof}

### 2014-12-16 content/background.tex
pass through section 4

--- 2014-12-15 content/background.tex
@@
 %\otodo{do we ever use $\src$ and $\target$?}
-We denote the source and end nodes of a graph edge $e$ as $\src e$ and $\target e$.
+%We denote the source and end nodes of a graph edge $e$ as $\src e$ and $\target e$.
 
@@
   The labels on the edges will be explained in Section~\ref{sec:bgide}
-  We can see that there is a realizable path
+  We can see that there is a realizable path, highlighted in bold,
   from the start node of the exploded graph to the variable \verb's' at~the~node~$\textsf{print(s)}$ in the \verb'B.bar' method. This means that at that node, \verb's' is considered secret.
@@
 the \textit{meet-over-all-valid-paths} solution
-  $\mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top)$,
-where $M_\textsf{Env}$ is extended from edges to paths by composition.
+$\mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top_\textsf{Env})$,
+%\mtodo{Should it be $\Omega$ instead of $\top$?}
+where $\top_\textsf{Env} = \lambda d.\top$ is the top element of the lattice of environments,
+and $M_\textsf{Env}$ is extended from edges to paths by composition.
 
@@
     R_t =& \{ \microedge{\mathbf0}{\mathbf0}{\lambda l.l} \} \cup
-    \{\microedge{\mathbf0}{d_j}{\lambda l.t(\Omega)(d_j)} \mid d_j \in D\}\\
+    \{\microedge{\mathbf0}{d_j}{\lambda l.t(\top_{\textsf{Env}})(d_j)} \mid d_j \in D\}\\
     &\cup
-    \{\microedge{d_i}{d_j}{\lambda l.t(\Omega[d_i\to l])(d_j)} \mid d_i, d_j \in D\}.
+    \{\microedge{d_i}{d_j}{\lambda l.t(\top_{\textsf{Env}}[d_i\to l])(d_j)} \mid d_i, d_j \in D\}.
 \end{align*}
 }
-Let $\Omega = \lambda d.\top$ be the environment that maps every element of $D$ to $\top$.
+%Let $\top_{\textsf{Env}} = \lambda d.\top$ be the environment that maps every element of $D$ to $\top$.
 %\ftodo{
@@
 $t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
-can be decomposed into its effect on $\Omega$ and on a set of environments $\Omega[d_i\to l]$
-that map every element except one ($d_i$) to $\top$:
+can be decomposed into its effect on $\top_{\textsf{Env}}$ and on a set of environments $\top_{\textsf{Env}}[d_i\to l]$
+that map every element to $\top$ except one ($d_i$):
 \[
-    t(m)(d_j) = \lambda l. t(\Omega)(d_j) \sqcap \bigsqcap_{d_i\in D} \lambda l. t(\Omega[d_i\to l])(d_j).
+    t(m)(d_j) = \lambda l. t(\top_{\textsf{Env}})(d_j) \sqcap \bigsqcap_{d_i\in D} \lambda l. t(\top_{\textsf{Env}}[d_i\to l])(d_j).
 \]

### 2014-12-16 content/impl.tex
pass through section 4

@@
   \menv&((n_1,\,n_2))(\textsf{env})(d)\notag\\
-  &=\edgefn((n_1,\,\Lambda),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,,
+  &=\edgefn((n_1,\,\mathbf0),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,,
 \end{align}
@@
 The correlated-calls analysis is defined as a transformation from an arbitrary IFDS problem to a corresponding IDE problem.
-The solution of the IDE problem is converted to a solution of the original IFDS problem.
+The solution of this IDE problem can be converted to a solution of the original IFDS problem.
 The converted IFDS result can be more precise than the original IFDS result because it avoids infeasible paths corresponding to correlated calls.
@@
 \begin{itemize}
-	\item an equivalence transformation $\transEq$ (pronounced ``t-equiv'') that generates IDE problems with the same precision as the original IFDS problem, and
-  \item a correlated-call transformation $\transCC$ (pronounced ``t-c-c'') that generates IDE problems that exclude infeasible paths.
+    \item an \textit{equivalence transformation} $\transEq$ (pronounced ``t-equiv'') that generates IDE problems with the same precision as the original IFDS problem, and
+    \item a \textit{correlated-calls transformation} $\transCC$ (pronounced ``t-c-c'') that generates IDE problems that exclude infeasible paths.
 \end{itemize}
@@
     \begin{cases}
-      \lambda e\,.\,\lambda m\,.\,\bot&\text{if $d_1(e)=\Lambda$ and $d_2(e)\ne\Lambda$;}\\
-      \lambda e\,.\,\id&\text{otherwise,}
+        \lambda e\,.\,\lambda m\,.\,\bot&\text{if $e=(n_1,\mathbf0)\to(n_2,d_2)$, where $d_2 \neq \mathbf0$;}\\
+      \lambda e\,.\,\id&\text{otherwise.}
     \end{cases}
 \end{equation}
-where $d_1(e)$ is the source fact of an edge $e$ and $d_2(e)$ is its target fact. 
-At a~``diagonal'' edge from a $\Lambda$-fact to a non-$\Lambda$-fact
+At a~``diagonal'' edge from a $\mathbf0$-fact to a non-$\mathbf0$-fact
 $d$, the micro function returns $\bot$
@@
 of a supergraph edge $e$ is defined as:
-                    \otodo{define $n_1(e)$ globally somewhere early on, and consider using a more decriptive name like src instead of $n_1$}
+                    %\otodo{define $n_1(e)$ globally somewhere early on, and consider using a more decriptive name like src instead of $n_1$}
   \begin{align}\label{eq:varepsilon}
@@
             &\text{\parbox{75mm}{
-                if $e$ is a call-start edge, $r.c()$ is
-                the call site at $\src e$, $f$ is the called
-                procedure with signature $s$,
+                    if $e$ is a call-start edge $r.c() \to \textsf{start}_f$ that calls
+                procedure $f$ with signature $s$,
                 and $r\in S$;}}\\[3ex]
@@
         \text{\parbox{75mm}{
-                if $e$ is an end-return edge,
-                $r.c()$ is the call
-                corresponding to the return node
-                at $\target e$,
-                $f$ is the called method with
-                signature $s$,
+                if $e$ is an end-return edge
+                $\textsf{end}_f \to \textsf{return}_{r.c()}$
+                from method $f$ with signature $s$ to the return node corresponding
+                to the call $r.c()$,
                 $v_1,\,\dots,\,v_k\in S$ are the local variables
@@
             m\left[r\to \bot_T\right],
-            &\text{\parbox{75mm}{if $\src e$ contains an assignment
-                    for $r\in S$;}}\\
+            &\text{\parbox{75mm}{if $e = n_1 \to n_2$ and $n_1$ contains an assignment
+                    to $r\in S$;}}\\
             m
@@
 the exploded supergraph. 
-Along a $\Lambda$-edge, the micro function is the identity. 
+Along a $\mathbf0$-edge, the micro function is the identity. 
 All other functions can be described with $\varepsilon_S$.
-On a ``diagonal'' edge from $\Lambda$ to a non-$\Lambda$ fact that corresponds
+On a ``diagonal'' edge from $\mathbf0$ to a non-$\mathbf0$ fact that corresponds
 to some data flow fact becoming reachable, $\varepsilon_S(e)$ is applied to the initial
@@
         \begin{cases}
-          \id  &\text{if $d_1=d_2=\Lambda$},\\
-          \lambda m\,.\,\varepsilon_S(e)(\botcc) &\text{if $d_1=\Lambda$ and $d_2\ne\Lambda$},\\
+          \id  &\text{if $d_1=d_2=\mathbf0$},\\
+          \lambda m\,.\,\varepsilon_S(e)(\botcc) &\text{if $d_1=\mathbf0$ and $d_2\ne\mathbf0$},\\
           \lambda m\,.\,\varepsilon_S(e)(m)  &\text{otherwise.}
@@
 \begin{example}
-  Consider the program from Listing~\ref{list:ccexample}, whose exploded supergraph appeared in Figure~\ref{fig:cc_edgefn_example}.
+  Consider the program from Figure~\ref{list:ccexample}, whose exploded supergraph appeared in Figure~\ref{fig:cc_edgefn_example}.
 
-  Returning a secret value in method \code{A.foo} creates a ``diagonal'' edge from the $\Lambda$-fact to the method's return value $r$. 
+  Returning a secret value in method \code{A.foo} creates a ``diagonal'' edge from the $\mathbf0$-fact to the method's return value $r$. 
   The diagonal edge is labeled with the micro function $\lambda m\,.\,\botcc$. Thus, at the end node of the method, every receiver is mapped to the set of all types~$\bot_T$.
@@
 
-Finally, the correlated-calls transformation is defined as
+Finally, the correlated-calls transformation is defined as\\
     $\transCC_S((G^\#))=\left(G^\#,\,\lcc_S,\,\ccedgefn S\right)$.
@@
 \begin{example}\label{ex:ifdsresult}
-  The solution to the taint-analysis IFDS problem $\mathcal P$ in Listing~\ref{list:examplejava} whose exploded supergraph is presented in Figure~\ref{fig:exampleexploded} looks as follows:
+  The solution to the taint-analysis IFDS problem $\mathcal P$ in Figure~\ref{list:examplejava} whose exploded supergraph is presented in Figure~\ref{fig:exampleexploded} looks as follows:
   \small\begin{align*}
@@
 The representation of a micro-function is a map from receivers to pairs of sets of
-types $I(r)$ and $U(r)$, where $U(r)$ is required to be a subset of $I(r)$. We use the notation
+types $I(r)$ and $U(r)$, where $U(r)$ is required to be a subset of $I(r)$. 
+Intuitively, the micro-function takes the existing set of possible types of the
+receiver $r$, intersects it with $I(r)$, then unions it with $U(r)$.
+We use the notation
 $\setpair{I}{U}$ to represent such a map, and $I(r)$ and $U(r)$ to look up the
@@
 \end{lemma}
+The proofs of all of the lemmas and theorems in the paper are provided in the supplemental
+material submitted with the paper.
 \otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}

### 2014-12-16 figures/fig-cc_edge_fn_example.tex
pass through section 4

@@
 % main method edges
-    \path[->](st_main_z) edge (asgn_a_z);
-    \path[->](asgn_a_z) edge (call_foo_z);
+    \path[->, ultra thick](st_main_z) edge (asgn_a_z);
+    \path[->, ultra thick](asgn_a_z) edge (call_foo_z);
     \path[->](call_foo_z) edge (return_foo_z);
@@
     \path[->](call_foo_v) edge (return_foo_v);
-    \path[->](return_foo_v) edge (call_bar_v);
+    \path[->, ultra thick](return_foo_v) edge (call_bar_v);
     \path[->](call_bar_v) edge (return_bar_v);
@@
 %A.foo method edges
-    \path[->](st_a_foo_z) edge (return_secret_z); 
+    \path[->, ultra thick](st_a_foo_z) edge (return_secret_z); 
     \path[->](return_secret_z) edge node[arrowtext,near start,above right=0.4cm and -.15cm,rotate=-60]{$\lambda m.\botcc$} (end_a_foo_z); 
-    \path[->,dashed](call_foo_z) edge [out=38,in=238]  (st_a_foo_z);
+    \path[->,dashed, ultra thick](call_foo_z) edge [out=38,in=238]  (st_a_foo_z);
     \path[->,dashed](end_a_foo_z) edge [out=200,in=43] (return_foo_z);
-    \path[->,dashed](end_a_foo_p) edge  [out=200,in=43] node[arrowtext,below,rotate=30]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (return_foo_v);
+    \path[->,dashed, ultra thick](end_a_foo_p) edge  [out=200,in=43] node[arrowtext,below,rotate=30]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (return_foo_v);
     \path[->](st_a_foo_p) edge (return_secret_p); 
     \path[->](return_secret_p) edge (end_a_foo_p);
-    \path[->](return_secret_z) edge (end_a_foo_p);
+    \path[->, ultra thick](return_secret_z) edge (end_a_foo_p);
 
@@
     \path[->](print_z) edge (end_b_bar_z);
-    \path[->](st_b_bar_s) edge (print_s);
+    \path[->, ultra thick](st_b_bar_s) edge (print_s);
     \path[->](print_s) edge (end_b_bar_s);
     \path[->,dashed](call_bar_z) edge [out=40,in=140,color=lightsalmonpink] (st_b_bar_z);
-    \path[->,dashed](call_bar_v) edge [out=20,in=160,color=lightsalmonpink] node[arrowtext,above right=-.4cm and .4cm,rotate=-10]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$} (st_b_bar_s);
+    \path[->,dashed, ultra thick](call_bar_v) edge [out=20,in=160,color=lightsalmonpink] node[arrowtext,above right=-.4cm and .4cm,rotate=-10]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$} (st_b_bar_s);
     \path[->,dashed](end_b_bar_z) edge [out=210,in=-40,color=lightsalmonpink] (return_bar_z);    

### 2014-12-16 content/appendix.tex
pass halfway through proofs

@@
 \subsection*{Representation of Micro Functions}
+\otodo{Repeat the lemmas here before each proof.}
 We start by presenting the proofs to the lemmas about the representation of micro functions.
@@
 \begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalEq}}]
+    OL: Can't we just say the following?
+    \begin{align*}
+        \denote{\setpair {I}{U}}\\
+       & = \lambda m. \lambda r. (m(r) \cap I(r))\cup U(r))\\
+       & = \lambda m. \lambda r. (m(r) \cap I'(r))\cup U'(r))\\
+       & = 
+        \denote{\setpair {I'}{U'}}\\
+    \end{align*}
+
 First, we need to show that for all $r\in R$ and ${m\in R\to2^T}$, if $I(r)=I'(r)$ and $U(r)=U'(r)$, then $\denote{\setpair IU}(m)(r)=\denote{\setpair{I'}{U'}}(m)(r)$. Indeed, we can see that
@@
 \end{align*}
+
+OL: Again, we can keep it simpler:
+For the other direction:
+\begin{align*}
+&&
+    \denote{\setpair{I}{U}} &= \denote{\setpair{I'}{U'}}\\
+&\implies &
+    \denote{\setpair{I}{U}}(\lambda r. \emptyset) &= \denote{\setpair{I'}{U'}}(\lambda r. \emptyset)\\
+&\implies &
+(\lambda m.\lambda r.(m(r)\cap I(r))\cup U(r))(\lambda r.\emptyset) &=
+(\lambda m.\lambda r.(m(r)\cap I'(r))\cup U'(r))(\lambda r.\emptyset) \\
+&\implies &
+\lambda r.(\emptyset \cap I(r))\cup U(r) &=
+\lambda r.(\emptyset \cap I'(r))\cup U'(r) \\
+&\implies &
+\lambda r.U(r) &=
+\lambda r.U'(r) \\
+&\implies &
+U &=
+U' \\
+\end{align*}
+Similarly:
+\begin{align*}
+&&
+    \denote{\setpair{I}{U}} &= \denote{\setpair{I'}{U'}}\\
+&\implies &
+\denote{\setpair{I}{U}}(I) &= \denote{\setpair{I'}{U'}}(I)\\
+&\implies &
+(\lambda m.\lambda r.(m(r)\cap I(r))\cup U(r))(I) &=
+(\lambda m.\lambda r.(m(r)\cap I'(r))\cup U'(r))(I) \\
+&\implies &
+\lambda r.(I(r) \cap I(r))\cup U(r) &=
+\lambda r.(I(r) \cap I'(r))\cup U'(r) \\
+&\implies &
+\lambda r.(I(r) \cap I(r)) &=
+\lambda r.(I(r) \cap I'(r)) \textrm{ since $\forall r.U(r) \subseteq I(r)$} \\
+&\implies \forall r.&
+I(r) &= I(r) \cap I'(r)\\
+&\implies \forall r.&
+I(r) &\subseteq I'(r)\\
+\end{align*}
+Symmetrically, we can also establish that $\forall r.I'(r) \subseteq I(r)$ by applying the functions to $I'$ instead of to $I$. Therefore, $I = I'$.
 
@@
 
+\otodo{The (m)(r) does not seem necessary. Can we replace $r'$ with $r$ and $m'$ with $m$?}
 \begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalComp}}]

### 2014-12-16 content/example.tex
implementation paragraph in section 4; stats table in section 2; removed section 5

@@
 many common analysis tasks such as \TODO{please add a few examples + citations}
+
+\subsection{Occurrences of Correlated Calls}
+How often do correlated calls occur in practice?
+To assess the benefit of the correlated-calls analysis, we counted the number of correlated calls that occurred programs of the Dacapo benchmarks~\cite{blackburn2006dacapo}, using the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
+Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis. The results are shown in Table~\ref{tab:dacapostat}.
+
+In the table, the number of all call sites in a program is denoted as $C$. 
+Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. 
+The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
+The last three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
+
+\begin{table}
+\caption{Frequencies of correlated-call occurrences in the Dacapo benchmarks}\label{tab:dacapostat}
+\centering
+%\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lrrrr
+>{\columncolor[HTML]{FFFFFF}}r 
+>{\columncolor[HTML]{FFFFFF}}l r@{}}
+\toprule
+\textbf{Benchmark}  &
+  \multicolumn{1}{c}{\textbf{$|C|$}} & 
+  \multicolumn{1}{c}{\textbf{$|C_P|$}} & 
+  \multicolumn{1}{c}{\textbf{$|C^\Subset|$}} & 
+  \multicolumn{1}{c}{\textbf{$|\rcc|$}} & 
+  {\textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C_P|}{|C|}$\end{tabular}}} & 
+  {\textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C^\Subset|}{|C_P|}$\end{tabular}}} & 
+  \textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C^\Subset|}{|\rcc|}$\end{tabular}} \\ \midrule
+\textbf{antlr}      & 7,610                             & 428                                   & 299                              & 70                                   & {\textbf{6\%}}                                                      & {\textbf{70\%}}                                                     & 4                                                                \\
+\textbf{bloat}      & 18,157                            & 933                                   & 429                              & 119                                  & {\textbf{5\%}}                                                      & {\textbf{46\%}}                                                     & 4                                                                \\
+\textbf{chart}      & 18,101                            & 466                                   & 195                              & 61                                   & {\textbf{3\%}}                                                      & {\textbf{42\%}}                                                     & 3                                                                \\
+\textbf{eclipse}    & 3,222                             & 100                                   & 35                               & 10                                   & {\textbf{3\%}}                                                      & {\textbf{35\%}}                                                     & 4                                                                \\
+\textbf{fop}        & 4,831                             & 129                                   & 40                               & 12                                   & {\textbf{3\%}}                                                      & {\textbf{31\%}}                                                     & 3                                                                \\
+\textbf{hsqldb}     & 3,573                             & 81                                    & 35                               & 10                                   & {\textbf{2\%}}                                                      & {\textbf{43\%}}                                                     & 4                                                                \\
+\textbf{jython}     & 12,149                            & 487                                   & 129                              & 54                                   & {\textbf{4\%}}                                                      & {\textbf{26\%}}                                                     & 2                                                                \\
+\textbf{luindex}    & 7,190                             & 188                                   & 79                               & 29                                   & {\textbf{3\%}}                                                      & {\textbf{42\%}}                                                     & 3                                                                \\
+\textbf{lusearch}   & 9,043                             & 350                                   & 126                              & 47                                   & {\textbf{4\%}}                                                      & {\textbf{36\%}}                                                     & 3                                                                \\
+\textbf{pmd}        & 10,972                            & 219                                   & 68                               & 23                                   & {\textbf{2\%}}                                                      & {\textbf{31\%}}                                                     & 3                                                                \\
+\textbf{xalan}      & 3,889                             & 110                                   & 35                               & 10                                   & {\textbf{3\%}}                                                      & {\textbf{32\%}}                                                     & 4                                                                \\
+\textbf{Geom.
+mean} & \textbf{7,572}                    & \textbf{240}                          & \textbf{91}                      & \textbf{29}                          & {\textbf{3\%}}                                                      & {\textbf{38\%}}                                                     & \textbf{3}                                                       \\ \bottomrule
+\end{tabular}
+%}
+\end{table}
+
+We can see that on average, 3\% of all call sites $C$ are polymorphic call sites $C_P$.
+\mtodo{Should we explain in a footnote why the number of polymorphic call sites is so low?}
+Out of those call sites, 38\% are correlated call sites $C^\Subset$. We also see that for one correlated-call receiver, there are on average three correlated calls.

### 2014-12-16 content/impl.tex
implementation paragraph in section 4; stats table in section 2; removed section 5

--- 2014-12-15 content/impl.tex
@@
 An efficient representation of those data structures for the correlated-calls analysis is presented in the next section.
+
+\subsection{Implementation of the Correlated-Calls Analysis}
+The correlated-calls analysis was implemented in the Scala programming language~\cite{odersky2004overview}. 
+We chose Java as the target language for client programs of the analysis.
+To retrieve information about an input program, such as its control-flow supergraph or the set of receivers and their types, we used the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
+
+Since WALA currently only contains an implementation of IFDS, we implemented IDE from scratch.
+Instead of using WALA's IFDS implementation, to run an IFDS problem, we converted it to an IDE problem and used our own IDE solver.
+
+We tested the implementation of the correlated-calls analysis using an IFDS taint-analysis implementation as a client analysis.
+We converted the IFDS taint analysis into an IDE problem with an implementation of $\transCC_\rcc$.
+
+We extensively tested the correlated-calls analysis to ensure that in the absence of correlated calls in an input program, the analysis produced the same results as an IFDS-equivalent analysis, and in the presence of correlated calls, the result was more precise.

### 2014-12-16 content/intro.tex
implementation paragraph in section 4; stats table in section 2; removed section 5

@@
 of infeasible path that arises in object-oriented programs when two or more
-methods are dynamically dispatched on the same receiver object. In such cases, if the
+methods are dynamically dispatched on the same receiver object.
+\mtodo{Should we define the term ``receiver''?}
+In such cases, if the
 method calls are polymorphic (i.e., if they dispatch to different method definitions 

### 2014-12-16 content/appendix.tex

@@
 \begin{proof}[\textbf{Proof of Lemma~\ref{lem:subsetifds}}]
+    \otodo{It's Section 3.2.}
   Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
@@
   \end{equation}
+  \otodo{Where do we mention $\backEq$ in this lemma?}
   The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
@@
 $\Omega=\lambda d\,.\,\topcc$.
+\otodo{I've been using $\top_\textsf{Env}$ for clarity.}
 

### 2014-12-16 content/background.tex
rewriting last paragraph of section 3

@@
 For convenience, the function $f$ can be split up into separate functions that handle the cases when
-the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.
+the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.\mtodo{Do we leave the start-to-return edge out as a special case of intraprocedural edge?}
 
@@
 Specifically,
-the input is generally provided as a function $f: N^* \times D \times N^* \to (D \to F)$,
+the input is generally provided as a function $f: (N^* \times D) \times (N^* \times D) \to F$,
 where $F$ is the set of representations of micro-functions from $L$ to $L$.
-Given a (non-exploded) supergraph edge $n \to n'$ and a dataflow fact $d$,
-$f(n,d,n')$ returns a map that gives, for each fact $d'$, the micro-function $f$
-that appears on the exploded supergraph edge $(n,d) \to (n',d')$.
-Like in the IFDS algorithm, the function $f$ can be split up into separate functions that handle the cases when
-the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.
+Given an exploded supergraph edge $e=(n,\,d) \to (n',\,d')$,
+$f((n,\,d),\,(n',\,d'))$ returns the micro-function that appears on the exploded supergraph edge $e$.
+Like in the IFDS algorithm, the function $f$ can be split up into separate functions that handle the cases when $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.
 

### 2014-12-16 content/appendix.tex
repeating lemmas in appendix

@@
 \subsection*{Representation of Micro Functions}
-\otodo{Repeat the lemmas here before each proof.}
 We start by presenting the proofs to the lemmas about the representation of micro functions.
 
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalEq}}]
+\equalEq*
+\begin{proof}
     OL: Can't we just say the following?
@@
 \otodo{The (m)(r) does not seem necessary. Can we replace $r'$ with $r$ and $m'$ with $m$?}
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalComp}}]
+\equalComp*
+\begin{proof}
 For all $r\in R$ and $m\in R\to2^T$,
@@
 
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalMeet}}]
+\equalMeet*
+\begin{proof}
   For all $r\in R$ and $m\in R\to2^T$,
@@
 
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:subsetifds}}]
+\precision*
+\begin{proof}
     \otodo{It's Section 3.2.}
@@
 
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:sound}}] 
+\sound*
+\begin{proof}
 According to~\eqref{eq:ideresult}, we can rewrite~\eqref{eq:transCcDef} as

### 2014-12-16 content/impl.tex
modifying implementation explanation
repeating lemmas in appendix

@@
 implementation of comparison corresponds to equality of the represented micro-functions:
-\begin{lemma}\label{lem:equalEq}
+\begin{restatable}{lemma}{equalEq}
+\label{lem:equalEq}
     For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
@@
     \] 
-\end{lemma}
+\end{restatable}
 The proofs of all of the lemmas and theorems in the paper are provided in the supplemental
@@
 of the denoted functions:
-\begin{lemma}\label{lem:equalComp}
+\begin{restatable}{lemma}{equalComp}\label{lem:equalComp}
     For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
@@
     \]
-\end{lemma}
+\end{restatable}
 \otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}
@@
 of the denoted functions:
-\begin{lemma}\label{lem:equalMeet}
+\begin{restatable}{lemma}{equalMeet}\label{lem:equalMeet}
+\label{lem:equalMeet}
     For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
@@
      =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.\mtodo{I added the definition of the meet of two functions.}
-\end{lemma}
+\end{restatable}
 \otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}
@@
 
-\begin{lemma}[Precision]\label{lem:subsetifds}
+\begin{restatable}[Precision]{lemma}{precision}\label{lem:subsetifds}
     For an IFDS problem $P$ and all ${n\in N^*}$,
@@
     \end{equation}
-\end{lemma}
+\end{restatable}
 
@@
 
-\begin{lemma}[Soundness]\label{lem:sound}
+\begin{restatable}[Soundness]{lemma}{sound}\label{lem:sound}
   Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, and let $d\in D$.
@@
   \end{equation}
-\end{lemma}
+\end{restatable}
 
@@
 To retrieve information about an input program, such as its control-flow supergraph or the set of receivers and their types, we used the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
-
 Since WALA currently only contains an implementation of IFDS, we implemented IDE from scratch.
@@
 We extensively tested the correlated-calls analysis to ensure that in the absence of correlated calls in an input program, the analysis produced the same results as an IFDS-equivalent analysis, and in the presence of correlated calls, the result was more precise.
+
+The artifact of our implementation can be used to solve any IFDS problem.
+In the presence of correlated calls, the result of the correlated-calls analysis can be more precise than the result obtained with an IFDS solver.

### 2014-12-16 content/appendix.tex
removing (m)(r) applications

@@
 \begin{proof}
-    OL: Can't we just say the following?
+   % OL: Can't we just say the following?
+   First, we need to show that for all $r\in R$, if $I(r)=I'(r)$ and $U(r)=U'(r)$, then $\denote{\setpair IU}=\denote{\setpair{I'}{U'}}$. Indeed, we can see that
     \begin{align*}
-        \denote{\setpair {I}{U}}\\
+        \denote{\setpair {I}{U}}
        & = \lambda m. \lambda r. (m(r) \cap I(r))\cup U(r))\\
@@
        & = 
-        \denote{\setpair {I'}{U'}}\\
+        \denote{\setpair {I'}{U'}}.
     \end{align*}
 
-First, we need to show that for all $r\in R$ and ${m\in R\to2^T}$, if $I(r)=I'(r)$ and $U(r)=U'(r)$, then $\denote{\setpair IU}(m)(r)=\denote{\setpair{I'}{U'}}(m)(r)$. Indeed, we can see that
-\begin{align*}
-  \denote{\setpair IU}(m)(r)
-  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I(r'))\cup U(r')\right)(m)(r)\\
-  &=(m(r)\cap I(r))\cup U(r)\\
-  &=(m(r)\cap I'(r))\cup U'(r)\\
-  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I'(r'))\cup U'(r')\right)(m)(r)\\
-  &=\denote{\setpair{I'}{U'}}(m)(r).
-\end{align*}
-
-OL: Again, we can keep it simpler:
+%OL: Again, we can keep it simpler:
 For the other direction:
@@
 \end{align*}
+\mtodo{I agree that this is much better than what I had. I think from $I(r) = I(r) \cap I'(r)$ we can conclude that $I(r)=I'(r)$.}
 Symmetrically, we can also establish that $\forall r.I'(r) \subseteq I(r)$ by applying the functions to $I'$ instead of to $I$. Therefore, $I = I'$.
-
-For the other direction, we need to show that if for any $r\in R$ and ${m\in R\to2^T}$, $(m(r)\cap I(r))\cup U(r)=(m(r)\cap I'(r))\cup U'(r)$, then for all $r'\in R$, $I(r')=I'(r')$ and $U(r')=U'(r')$.
-
-To prove that $U(r')=U'(r')$, we will pick $m(r)=\varnothing$.
-Then by our assumption, for all $r$, $U(r)=U'(r)$, and hence $U(r')=U'(r')$.
-
-To prove that $I(r')=I'(r')$, let us pick $m=I$. Then the assumption
-is $I(r)\cup U(r)=(I(r)\cap I'(r))\cup U'(r)$. By our definition, $U(r)\subseteq I(r)$, and we just proved that $U(r')=U'(r)$. Theorefore, $I(r)=(I(r)\cap I'(r))\cup U'(r)$.
-Additionally, $U'(r)\subseteq I'(r)$ and $U'(r)\subseteq I(r)$ (because $U'(r)=U(r)\subseteq I(r)$). This means that $U'(r)\subseteq I(r)\cap I'(r)$. Therefore, $I(r)=I(r)\cap I'(r)$,
-and we can conclude that $I(r)=I'(r)$.
 \end{proof}
 
+\equalComp*
 \otodo{The (m)(r) does not seem necessary. Can we replace $r'$ with $r$ and $m'$ with $m$?}
-\equalComp*
 \begin{proof}
-For all $r\in R$ and $m\in R\to2^T$,
 \begin{align*}
-  &\denote{\setpair IU\circ\setpair{I'}{U'}}(m)(r)\\
-  &=\denote{\setpair{\lambda r'\,.\,(I(r')\cap I'(r'))\cup U(r')}
-                    {\lambda r'\,.\,(I(r')\cap U'(r'))\cup U(r')}}(m)(r)\\
-  &=(m(r)\cap(I(r)\cap I'(r))\cup U(r))\cup(I(r)\cap U'(r))\cup U(r)\\
-  &=(m(r)\cap I'(r))\cup I(r)\cup (U'(r)\cap I(r))\cup U(r)\\
-  &=(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
-  &=\left(\lambda r'.(((m(r')\cap I'(r'))\cup U'(r'))\cap I(r'))\cup U(r')\right)(r)\\
-  &=\left(\lambda m'.\lambda r'.(m'(r')\cap I(r'))\cup U(r')\right)
-    \left(\left(\lambda m'.\lambda r'.(m'(r')\cap I'(r'))\cup U'(r')\right)  (m)\right)(r)\\
-  &=\left(\denote{\setpair IU}\circ\denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
+  &\denote{\setpair IU\circ\setpair{I'}{U'}}\\
+  =&\denote{\setpair{\lambda r\,.\,(I(r')\cap I'(r))\cup U(r)}
+                    {\lambda r\,.\,(I(r)\cap U'(r))\cup U(r)}}\\
+  =&\lambda m\,.\,\lambda r\,.\,(m(r)\cap(I(r)\cap I'(r))\cup U(r))\cup(I(r)\cap U'(r))\cup U(r)\\
+  =&\lambda m\,.\,\lambda r\,.\,(m(r)\cap I'(r))\cup I(r)\cup (U'(r)\cap I(r))\cup U(r)\\
+  =&\lambda m\,.\,\lambda r\,.\,(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
+  =&\lambda m\,.\,\lambda r\,.\,(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
+  =&\lambda m\,.\,\left(\lambda m'\,.\,\lambda r\,.\,(m'(r)\cap I(r))\cup U(r)\right)
+    \left(
+    \left(\lambda r\,.\,(m(r)\cap I'(r))\cup U'(r)\right)
+    \right)\\
+  =&\left(\lambda m\,.\,\lambda r\,.\,(m(r)\cap I(r))\cup U(r)\right)\circ
+    \left(\lambda m\,.\,\lambda r\,.\,(m(r)\cap I'(r))\cup U'(r)\right)\\
+  =&\denote{\setpair IU}\circ\denote{\setpair{I'}{U'}}.\qedhere
 \end{align*}
@@
 \begin{align*}
-  \left(\denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}\right)&(m)(r)\\
-  &=(\denote{\setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}})(m)(r)\\
-  &=(m(r)\cap(I(r)\cup I'(r))\cup U(r)\cup U'(r)\\
-  &=(m(r)\cap I(r))\cup U(r)\cup(m(r)\cap I'(r))\cup U'(r)\\
-  &=\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)\\
-  &=\left(\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
+  &\left(\denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}\right)(m)(r)\\
+  =&(\denote{\setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}})(m)(r)\\
+  =&(m(r)\cap(I(r)\cup I'(r))\cup U(r)\cup U'(r)\\
+  =&(m(r)\cap I(r))\cup U(r)\cup(m(r)\cap I'(r))\cup U'(r)\\
+  =&\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)\\
+  =&\left(\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
 \end{align*}

### 2014-12-16 content/appendix.tex
removing (m)(r) for lemma 3
replacing omega with top

@@
 \begin{proof}
-  For all $r\in R$ and $m\in R\to2^T$,
 \begin{align*}
-  &\left(\denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}\right)(m)(r)\\
-  =&(\denote{\setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}})(m)(r)\\
-  =&(m(r)\cap(I(r)\cup I'(r))\cup U(r)\cup U'(r)\\
-  =&(m(r)\cap I(r))\cup U(r)\cup(m(r)\cap I'(r))\cup U'(r)\\
-  =&\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)\\
-  =&\left(\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
+  &\denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}\\
+  =&\denote{\setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}}\\
+  =&\lambda m\,.\,\lambda r\,.\,(m(r)\cap(I(r)\cup I'(r))\cup U(r)\cup U'(r)\\
+  =&\lambda m\,.\,\lambda r\,.\,(m(r)\cap I(r))\cup U(r)\cup(m(r)\cap I'(r))\cup U'(r)\\
+  =&\lambda m\,.\,\lambda r\,.\,\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)\\
+  =&\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}.\qedhere
 \end{align*}
@@
     \otodo{It's Section 3.2.}
+    \mtodo{Section 3.2 talks about the IFDS algorithm, but it doesn't explicitly say how the result of an IFDS analysis looks like and doesn't introduce the notation $\resultIFDS$.}
   Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
@@
 
-We will denote the top element in the environment lattice as
-$\Omega=\lambda d\,.\,\topcc$.
+As previously we will denote the top element in the environment lattice as
+$\top_\textsf{Env}$.
 \otodo{I've been using $\top_\textsf{Env}$ for clarity.}
@@
 \begin{equation}
-  \mpd=\menv(p)(\Omega)(d)\,.
+  \mpd=\menv(p)(\top_\textsf{Env})(d)\,.
 \end{equation}
@@
     \mppd
-    &=\menv(p')(\Omega)(d)\\
-    &=\left(\menv(e_k)\circ\menv(e_{k-1})\circ\ldots\circ\menv(e_1)\right)(\Omega)(d)\\
-    &=\menv(e_k)\left(\menv(p)(\Omega)\right)(d)\,.
+    &=\menv(p')(\top_\textsf{Env})(d)\\
+    &=\left(\menv(e_k)\circ\menv(e_{k-1})\circ\ldots\circ\menv(e_1)\right)(\top_\textsf{Env})(d)\\
+    &=\menv(e_k)\left(\menv(p)(\top_\textsf{Env})\right)(d)\,.
   \end{align*}
@@
   \begin{align*}
-    &\menv(e_k)\left(\menv(p)(\Omega)\right)(d)(r)\\
+    &\menv(e_k)\left(\menv(p)(\top_\textsf{Env})\right)(d)(r)\\
       =&\bigg(\ccedgefn R((n_{k-1},\,\Lambda),\,(n_k,\,d))(\topcc)\sqcap\\
-       &\bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\Omega)(d'))\bigg)(r)\\
+       &\bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\top_\textsf{Env})(d'))\bigg)(r)\\
       \supseteq&
-        \bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\Omega)(d'))(r)\\
+        \bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\top_\textsf{Env})(d'))(r)\\
       \supseteq&\,\ccedgefn R((n_{k-1},\,d_{k-1}),\,(n_k,\,d))(\mpdkm)(r)\,.
@@
   &=\{d'\,|\,\forall r\in R\,.\,\mvp{\textsf{Env}}(n,\,d'))(r)\ne\top_T\}\\
-  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\menv(q)(\Omega)(d')(r)\ne\top_T\right\}\\
+  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\menv(q)(\top_\textsf{Env})(d')(r)\ne\top_T\right\}\\
   &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d'}(r)\ne\top_T\right\}.
@@
     &=\mvp{\textsf{Env}}(n,\,d)(r)\notag\\
-    &=\left(\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\Omega)(d)\right)(r)\notag\\
+    &=\left(\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top_\textsf{Env})(d)\right)(r)\notag\\
     &=\left(\bigsqcap_{q\in\ivp(n)}\bigsqcap_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)\right)(r)\notag\\

### 2014-12-16 content/appendix.tex
rearranging soundness and precision lemmas

@@
 
-\precision*
-\begin{proof}
-    \otodo{It's Section 3.2.}
-    \mtodo{Section 3.2 talks about the IFDS algorithm, but it doesn't explicitly say how the result of an IFDS analysis looks like and doesn't introduce the notation $\resultIFDS$.}
-  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
-  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
-  \begin{equation}
-    \resultIFDS(P)=\lambda n\,.\,\mvp F(n)\,.
-  \end{equation}
-  \otodo{Where do we mention $\backEq$ in this lemma?}
-  The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
-  \begin{align*}
-    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
-    &=\left(\lambda n'\,.\,\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\right)(n)\\
-    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\\
-    &\subseteq\left\{d\,|\,\resultIDE(\transCC_R(P))(n)(d)\ne\topcc\right\}\\
-    &=\backEq\left(\resultIDE(\transCC_R(P))(n)\right).\qedhere
-  \end{align*}
-\end{proof}
-
 To prove the Soundness Lemma, we first introduce Lemmas~\ref{lem:sound1} and~\ref{lem:sound3}.
 
-As previously we will denote the top element in the environment lattice as
-$\top_\textsf{Env}$.
-\otodo{I've been using $\top_\textsf{Env}$ for clarity.}
+As previously we will denote the top element in the environment lattice as~$\top_\textsf{Env}$.
+%\otodo{I've been using $\top_\textsf{Env}$ for clarity.}
 
@@
 
-Finally, we can prove the Soundness Lemma.
+We can now prove the Soundness Lemma.
 
@@
   Since $\mpd(r)$ is a non-empty set that is contained in $\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d}(r)$, it follows that $$\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d}(r)\ne\top_T.$$ Therefore, $d\in \backCC(\resultIDE(\transCC_R(P)))(n)$.
+\end{proof}
+
+\precision*
+\begin{proof}
+    \otodo{It's Section 3.2.}
+    \mtodo{Section 3.2 talks about the IFDS algorithm, but it doesn't explicitly say how the result of an IFDS analysis looks like and doesn't introduce the notation $\resultIFDS$.}
+  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
+  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
+  \begin{equation}
+    \resultIFDS(P)=\lambda n\,.\,\mvp F(n)\,.
+  \end{equation}
+  \otodo{Where do we mention $\backEq$ in this lemma?}
+  %The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
+  An IFDS result The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
+  \begin{align*}
+    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
+    &=\left(\lambda n'\,.\,\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\right)(n)\\
+    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\\
+    &\subseteq\left\{d\,|\,\resultIDE(\transCC_R(P))(n)(d)\ne\topcc\right\}\\
+    &=\backEq\left(\resultIDE(\transCC_R(P))(n)\right).\qedhere
+  \end{align*}
 \end{proof}

### 2014-12-16 content/impl.tex
rearranging soundness and precision lemmas

@@
 
-In the following lemma we show that the result of an IDE problem obtained through a correlated-calls transformation is a subset of the original IFDS result.
+In the following lemma we show that our analysis is sound, i.e. that the result of an IDE problem obtained through a correlated-calls transformation removes only facts that occur on infeasible paths.
+
+\begin{restatable}[Soundness]{lemma}{sound}\label{lem:sound}
+  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, and let $d\in D$.
+  If $d\in M_F(p)(\varnothing),$
+  then
+  \begin{equation}
+    d\in \backCC\left(\resultIDE(\transCC_R(P))\right)(n)\,.
+  \end{equation}
+\end{restatable}
+
+We next show that the result of an IDE problem obtained through a correlated-calls transformation is a subset of the original IFDS result.
 
@@
       \resultIFDS(P)(n)\,.
-    \end{equation}
-\end{restatable}
-
-We will next show that our analysis is sound, i.e. that the result of an IDE problem obtained through a correlated-calls transformation removes only facts that occur on infeasible paths.
-
-\begin{restatable}[Soundness]{lemma}{sound}\label{lem:sound}
-  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, and let $d\in D$.
-  If $d\in M_F(p)(\varnothing),$
-  then
-  \begin{equation}
-    d\in \backCC\left(\resultIDE(\transCC_R(P))\right)(n)\,.
     \end{equation}

### 2014-12-16 content/appendix.tex
changing proof of lemma 5

@@
 \begin{lemma}\label{lem:sound3}
-  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, $r\in R$ a receiver, and $d\in D$ a data-flow fact. Then if $d\in M_F(p)(\varnothing)$,
+  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, $r\in R$ a receiver, and $d\in D$ a data-flow fact. Then
   \begin{equation}
-    \mpd(r)\ne\top_T\,.
-  \end{equation}
+    d\in M_F(p)(\varnothing)\iff\mpd(r)\ne\top_T\,.
+  \end{equation}\mtodo{Prove other direction}
 \end{lemma}
@@
   \end{equation}
-  Assume the Lemma holds for that for a concrete execution path $$p=[\startmain,\,n_1,\,\dots,\,n_{k-1}]\,,$$ i.e. $\uptau\ne\top_T$ for an arbitrary $r\in R$ and $d_{k-1}\in D$.
+  Assume the Lemma holds for a concrete execution path $$p=[\startmain,\,n_1,\,\dots,\,n_{k-1}]\,,$$ i.e. $\uptau\ne\top_T$ for an arbitrary $r\in R$ and $d_{k-1}\in D$.
 
@@
   nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
-  \begin{equation}
-    \resultIFDS(P)=\lambda n\,.\,\mvp F(n)\,.
-  \end{equation}
-  \otodo{Where do we mention $\backEq$ in this lemma?}
-  %The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
-  An IFDS result The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
+  \begin{align*}
+    \resultIFDS(P)&=\lambda n\,.\,\mvp F(n)\\
+    &=\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top).
+  \end{align*}
+  At the same time,
   \begin{align*}
     \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
-    &=\left(\lambda n'\,.\,\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\right)(n)\\
-    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\\
-    &\subseteq\left\{d\,|\,\resultIDE(\transCC_R(P))(n)(d)\ne\topcc\right\}\\
-    &=\backEq\left(\resultIDE(\transCC_R(P))(n)\right).\qedhere
+    &=\left(\lambda n\,.\,\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\right\}\right)(n)\\
+    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\right\}\\
+    &=\left\{d\,|\,\forall r\in R\,.\,\bigsqcap_{q\in\textsf{VP}(n)}\xi(q,\,d)(r)\ne\top_T\right\}.
   \end{align*}
+  This means that for each $d\in\backCC(\resultIDE(\transCC R(P)))(n)$ and for each path $q\in\textsf{VP}(n)$, $\xi(q,\,d)\ne\top_T$.
+Therefore, according to~Lemma~\ref{lem:sound3}, for each $q$, $d\in M_F(q)(\top)$.
+It follows that $d\in\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top)=\resultIFDS(P)(n)$.
+  In other words, if $d\in\backCC(\resultIDE(\transCC R(P)))(n)$, then $d\in\resultIFDS(P)(n)$.
 \end{proof}

### 2014-12-16 content/appendix.tex
minor changes

@@
 \begin{proof}
-  By induction on the length of the execution trace.
+  We start by proving that if $d\in M_F(p)(\varnothing)$, then $\mpd(r)\ne\top_T$, by induction on the length of the execution trace.
 
@@
 
-    The same reasoning applies to the case where $e_k$ is a call-start edge.
+    The same reasoning applies to the case where $e_k$ is a call-start edge.\\
+
+    For the other direction, we will prove that if $\mpd(r)\ne\top_T$, then $d\in M_F(p)(\varnothing)$.
 \end{proof}
@@
     \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
-    &=\left(\lambda n\,.\,\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\right\}\right)(n)\\
     &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\right\}\\
@@
   \end{align*}
-  This means that for each $d\in\backCC(\resultIDE(\transCC R(P)))(n)$ and for each path $q\in\textsf{VP}(n)$, $\xi(q,\,d)\ne\top_T$.
-Therefore, according to~Lemma~\ref{lem:sound3}, for each $q$, $d\in M_F(q)(\top)$.
-It follows that $d\in\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top)=\resultIFDS(P)(n)$.
-  In other words, if $d\in\backCC(\resultIDE(\transCC R(P)))(n)$, then $d\in\resultIFDS(P)(n)$.
+  This means that for any given $d\in\backCC(\resultIDE(\transCC R(P)))(n)$ and path $q\in\textsf{VP}(n)$, $\xi(q,\,d)\ne\top_T$.
+Therefore, according to~Lemma~\ref{lem:sound3}, $d\in M_F(q)(\top)$.
+It follows that $d\in\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top)$, which is equal to $\resultIFDS(P)(n)$.
+  Hence, we have shown that if $d\in\backCC(\resultIDE(\transCC R(P)))(n)$, then $d\in\resultIFDS(P)(n)$.
 \end{proof}

### 2014-12-16 content/appendix.tex
proving other direction of lemma 8

@@
     d\in M_F(p)(\varnothing)\iff\mpd(r)\ne\top_T\,.
-  \end{equation}\mtodo{Prove other direction}
+  \end{equation}
 \end{lemma}
@@
 
-    For the other direction, we will prove that if $\mpd(r)\ne\top_T$, then $d\in M_F(p)(\varnothing)$.
+    For the other direction, we need to show that if $\mpd(r)\ne\top_T$, then $d\in M_F(p)(\varnothing)$.
+
+    The fact that $\mpd(r)\ne\top_T$ means that there exists a realizable path corresponding to the fact $d$ along path $p$, and, by definition, $d$ must be contained in $M_F(p)(\varnothing)$.\mtodo{Is this hand-wavy?}
 \end{proof}

### 2014-12-17 content/abstract.tex
new abstract

\begin{abstract}
    When two methods are invoked on the same object, the dispatch behaviors of these
    method calls will be correlated. If two correlated method calls are polymorphic 
    (i.e., they dispatch to different method definitions depending on the type of 
    the receiver object), a program's interprocedural control flow graph (ICFG)
    will contain infeasible paths. Existing algorithms for dataflow analysis 
    are unable to ignore such infeasible paths, giving rise to loss of precision.

	We show how infeasible paths due to correlated calls can be eliminated for 
	\textit{Interprocedural Finite Distributive Subset} (IFDS) problems, a large class 
	of data-flow analysis problems with broad applications. Our approach is to
	transform an IFDS problem into an \textit{Interprocedural Distributive 
	Environment} (IDE) problem, in which edge functions are designed in a
	way that enables us to ignore dataflow along infeasible paths. A solution
	to this IDE problem can be mapped back to the solution space of the original
	IFDS problem. We prove the correctness of our approach, and report on
	some preliminary experiments with our prototype implementation. 
\end{abstract}

### 2014-12-17 main.tex
started to move proofs to appendix; removing dependency on minted
add page numbers
restructuring
comments
todo list
rename todo list
rewritten the introduction
remove section 5
removing tdo files
title
eliminate TODOs in introduction; improve formatting of title
proofs of Lemmas 1 and 2
implementation paragraph in section 4; stats table in section 2; removed section 5
new abstract

@@
 
+\input{style/commands}
+
+\pagenumbering{gobble}
+\listoftodos[Overview of Comments]
+
 \mainmatter  % start of an individual contribution
 
-\title{Data Flow Analysis\\in the Presence of Correlated Calls}
+\title{Precise Data Flow Analysis\\in the Presence of Correlated Method Calls}
+\titlerunning{Data Flow Analysis in the Presence of Correlated Calls}
 
@@
 
-\pagenumbering{gobble}
+\pagenumbering{arabic}
 
@@
 
-\begin{abstract}
-We present a technique to improve the precision of data-flow analyses on object-oriented programs in the presence of 	\textit{correlated calls}.
-Two method calls are correlated if they are polymorphic and are invoked on the same object.
-Correlated calls are problematic because they can make  existing data-flow analyses consider certain infeasible data-flow paths as valid.
-This leads to loss in precision of the analysis solution.
-
-We show how infeasible paths can be eliminated for \textit{Inter-procedural Finite Distributive Subset} (IFDS) problems, a large class of data-flow analysis problems.
-We show how the precision of IFDS problems can be improved in the presence of correlated calls, by using the \textit{Inter-procedural Distributive Environment} (IDE) algorithm to eliminate infeasible paths.
-Using IDE, we eliminate the infeasible paths and obtain a more precise result for the original IFDS problem.
-
-Our analysis is implemented in Scala, using the WALA framework for static program analysis on Java bytecode.
-
-%\keywords{We would like to encourage you to list your keywords within
-%the abstract section}
-\end{abstract}
-
-\input{style/commands}
-
+\input{content/abstract}
 \input{content/intro}
+\input{content/example}
 \input{content/background}
 \input{content/impl}
-\input{content/datastr}
-\input{content/eval}
+%\input{content/datastr}
+%\input{content/eval}
+\input{content/related}
 \input{content/concl}
@@
 \bibliography{bib/ref}
+
+\input{content/appendix}
 \end{document}

### 2014-12-17 content/intro.tex
reworded last few paragraphs to deemphasize the implementation/evaluation

--- 2014-12-13 content/intro.tex
@@
 of infeasible path that arises in object-oriented programs when two or more
-methods are dynamically dispatched on the same receiver object. In such cases, if the
+methods are dynamically dispatched on the same receiver object.
+%\mtodo{Should we define the term ``receiver''?}
+In such cases, if the
 method calls are polymorphic (i.e., if they dispatch to different method definitions 
@@
 on top of the WALA framework for static analysis of JVM bytecode~\cite{fink2012wala}.
-We also report on preliminary experiments in which our correlated-calls transformation
-is applied to an IFDS formulation of a simple taint analysis. Our results show that
-solving the resulting IDE problem avoids infeasible paths due to correlated calls as
-expected.
+Our prototype implementation was tested extensively by using it to transform an IFDS-based 
+taint analysis into a more precise IDE-based taint analysis, and applying the latter
+to small example programs with correlated calls. Our prototype along with all tests
+will be made available to the artifact evaluation committee.
 
-In summary, the contributions of this paper are as follows:
-\begin{itemize}
-  \item
-    We present a general approach for transforming IFDS problems into corresponding
-    IDE problems that avoid infeasible paths due to correlated method calls and
-    prove its correctness. 
-  \item
-    We implemented the approach in Scala, on top of the WALA program analysis framework
-    and report on preliminary experiments. 
-\end{itemize}
+%We also report on preliminary experiments in which our correlated-calls transformation
+%is applied to an IFDS formulation of a simple taint analysis. Our results show that
+%solving the resulting IDE problem avoids infeasible paths due to correlated calls as
+%expected.
+%
+%In summary, the contributions of this paper are as follows:
+%\begin{itemize}
+%  \item
+%    We present a general approach for transforming IFDS problems into corresponding
+%    IDE problems that avoid infeasible paths due to correlated method calls and
+%    prove its correctness. 
+%  \item
+%    We implemented the approach in Scala, on top of the WALA program analysis framework
+%    and report on preliminary experiments. 
+%\end{itemize}
 
@@
 %
-Section~\ref{sec:ccdatastr} presents the correlated-calls transformation
+Section~\ref{sec:cca} presents the correlated-calls transformation
 and sketches a proof of its correctness%
@@
 %
-The implementation of our approach and preliminary experiments are discussed
-in Section~\ref{chapter:eval}.
-%
 Related work is discussed in Section~\ref{sec:Related}.

### 2014-12-17 content/example.tex
minor changes

@@
 dataflow analysis problem that can be expressed in the IFDS framework. This includes
-many common analysis tasks such as \TODO{please add a few examples + citations}
+many common analysis tasks such as reaching definitions, constant propagation, etc.
+\ftodo{Ondrej, can you give a few more/better examples?}
 
@@
 How often do correlated calls occur in practice?
-To assess the benefit of the correlated-calls analysis, we counted the number of correlated calls that occurred programs of the Dacapo benchmarks~\cite{blackburn2006dacapo}, using the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
+To assess the benefit of the correlated-calls analysis, we counted the number of correlated calls that occur in programs of the Dacapo benchmarks~\cite{blackburn2006dacapo}, using the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
 Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis. The results are shown in Table~\ref{tab:dacapostat}.
@@
 
-We can see that on average, 3\% of all call sites $C$ are polymorphic call sites $C_P$.
+In these programs, on average, only 3\% of all call sites $C$ are polymorphic call sites $C_P$.
 \mtodo{Should we explain in a footnote why the number of polymorphic call sites is so low?}
-Out of those call sites, 38\% are correlated call sites $C^\Subset$. We also see that for one correlated-call receiver, there are on average three correlated calls.
+However, it is worth noting that out of those call sites, a significant fraction (38\%) are correlated 
+call sites $C^\Subset$. We also see that, on average,  each correlated-call receiver is involved in three correlated calls.

### 2014-12-17 content/concl.tex
eliminate TODOs in introduction; improve formatting of title
rewrote conclusions

@@
-\section{Conclusions}\label{chapter:concl}
-We presented a technique to improve the precision of solutions to IFDS problems in the presence of correlated calls.
-Correlated calls occur when there are multiple polymorphic method invocations on the same receiver.
-Such method calls cause a data-flow analysis to consider infeasible paths, which makes the data-flow analysis less precise.
+\section{Conclusions}
+  \label{sec:Conclusions}
 
-Our method of eliminating infeasible paths caused by correlated calls works by transforming an existing IFDS problem into a specialized IDE problem.
-In this way, we are able to track the classes to which method invocations get dispatched.
-After solving the specialized IDE problem, we convert its result into an IFDS result that is potentially more precise than the solution to the original IFDS problem.
-The increase in precision can occur for programs that contain correlated calls.
-Specifically, if, on a certain data-flow path, there are two polymorphic method invocations on the same receiver that dispatch to incompatible classes, the IDE analysis will consider the path infeasible.
-
-We proved that the correlated-calls analysis is sound and that it improves the precision of IFDS results.
-
-Our Scala implementation of the correlated-calls analysis includes
-\begin{itemize}
-  \item an implementation of the IDE analysis, which is based on the WALA static program analysis framework;
-  \item a taint-analysis implementation as an IFDS problem instance;
-  \item a transformer of IFDS problems to equivalent IDE problems, and a second transformer that accounts for correlated calls.
-\end{itemize}
-
-We tested the correlated-calls analysis on our taint analysis implementation by comparing the number of secret values that were leaked when using an IFDS taint analysis and a taint analysis that accounts for correlated calls.
-We used the Dacapo benchmarks as input programs.
-Although the benchmarks contained a number of correlated calls, we were not able to improve the precision of the taint analysis, because the correlated calls did not occur on paths of secret information leaks.
-
-We are hopeful that other analyses can benefit from the extra information provided by the correlated-calls analysis, and plan to test this hypothesis in the future.
+Previous algorithms for dataflow analysis are unable to avoid propagating
+dataflow facts along infeasible paths that arise in the presence of
+correlated polymorphic method calls. 
+% 
+We present an approach for transforming an IFDS problem into an IDE problem
+in which path feasibility is encoded into the functions that are associated
+with edges in an exploded control-flow supergraph. The solution to this
+IDE problem can be mapped back to the solution space of the original IFDS
+problem, and is potentially more precise because the flow of data along
+infeasible paths is prevented. We present a formalization of the
+transformation and prove its correctness. We also briefly report on
+preliminary experiments with our prototype implementation. Full proof
+details are available as supplemental materials with this submission,
+and we plan to submit our implementation and experimental data to the
+artifact evaluation committee.

### 2014-12-17 content/example.tex
pass through abstract, introduction, example, conclusion

@@
 dataflow analysis problem that can be expressed in the IFDS framework. This includes
-many common analysis tasks such as reaching definitions, constant propagation, etc.
-\ftodo{Ondrej, can you give a few more/better examples?}
+many common analysis tasks such as reaching definitions, constant propagation, slicing,
+typestate analysis, pointer analysis, and lightweight
+shape analysis.
+%\ftodo{Ondrej, can you give a few more/better examples?}
 
@@
 The last three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
+In this context, we deem a call site to be polymorphic if its statically computed call graph
+contains edges from the call site to multiple target methods.
+We deem a call site to be a correlated call site if it is polymorphic and there is
+at least one other polymorphic call site on the same receiver.
 
@@
 
-In these programs, on average, only 3\% of all call sites $C$ are polymorphic call sites $C_P$.
-\mtodo{Should we explain in a footnote why the number of polymorphic call sites is so low?}
-However, it is worth noting that out of those call sites, a significant fraction (38\%) are correlated 
+In these programs, on average, 3\% of all call sites $C$ are polymorphic call sites $C_P$.
+%\mtodo{Should we explain in a footnote why the number of polymorphic call sites is so low?}
+%\otodo{We don't have an explanation.}
+Out of these polymorphic call sites, a significant fraction (38\%) are correlated 
 call sites $C^\Subset$. We also see that, on average,  each correlated-call receiver is involved in three correlated calls.

### 2014-12-17 content/impl.tex
moving comment
pass over section 4.6

@@
     $\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
-     =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.\mtodo{I added the definition of the meet of two functions.}
-\end{restatable}
+     =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.
+\end{restatable}\mtodo{I added the definition of the meet of two functions.}
 \otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}
@@
 The correlated-calls analysis was implemented in the Scala programming language~\cite{odersky2004overview}. 
-We chose Java as the target language for client programs of the analysis.
-To retrieve information about an input program, such as its control-flow supergraph or the set of receivers and their types, we used the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
+The input programs that we analyzed were written in Java. Our implementation analyzed the
+corresponding Java bytecode.
+To retrieve information about an input program, such as its control-flow supergraph or the set of receivers and their types, we used the WALA framework for static analysis~\cite{fink2012wala}.
 Since WALA currently only contains an implementation of IFDS, we implemented IDE from scratch.

### 2014-12-17 content/background.tex
pass through presentation of EdgeFn

--- 2014-12-16 content/background.tex
@@
 
+\commentout{
 A practical implementation of the IFDS algorithm generally takes as input a representation of the
@@
 For convenience, the function $f$ can be split up into separate functions that handle the cases when
-the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.
+the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.\mtodo{Do we leave the start-to-return edge out as a special case of intraprocedural edge?}
+}
 
@@
 
-Similar to the IFDS algorithm, a practical implementation of the IDE algorithm requires
+%Similar to the IFDS algorithm,
+A practical implementation of the IDE algorithm requires
 the input dataflow functions to be provided in their pointwise representation
@@
 Specifically,
-the input is generally provided as a function $f: N^* \times D \times N^* \to (D \to F)$,
+the input is generally provided as a function $\textsf{EdgeFn}: (N^* \times D) \times (N^* \times D) \to F$,
 where $F$ is the set of representations of micro-functions from $L$ to $L$.
-Given a (non-exploded) supergraph edge $n \to n'$ and a dataflow fact $d$,
-$f(n,d,n')$ returns a map that gives, for each fact $d'$, the micro-function $f$
-that appears on the exploded supergraph edge $(n,d) \to (n',d')$.
-Like in the IFDS algorithm, the function $f$ can be split up into separate functions that handle the cases when
-the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.
-
-\otodo{In the next section, we talk about \textsf{EdgeFn}, which is inconsistent with how
-    we define the functions to be implemented here. We need to make the two sections consistent,
-    one way or the other.}
+Given an exploded supergraph edge $e=(n,\,d) \to (n',\,d')$,
+$\textsf{EdgeFn}((n,\,d),\,(n',\,d'))$ returns the micro-function that appears on the exploded supergraph edge $e$.
+%Like in the IFDS algorithm,
+In an implementation, it can be convenient to split the function $\textsf{EdgeFn}$ into separate functions that handle the cases when $n\to n'$ is an intraprocedural edge, a call-to-return edge, a call-to-start edge, or an end-to-return edge.
 

### 2014-12-17 content/impl.tex
pass through comments in section 4

@@
 During an actual execution, every receiver $r$ points to an object of some
-runtime type. \otodo{What if $r$ points to null?} Therefore, a data flow fact
+runtime type. Therefore, a data flow fact
 is unreachable along any feasible path if its corresponding lattice element
@@
 and that he defined $\backEq$ related to the equivalence transformation.}
+\otodo{I don't understand this comment. What does it mean?}
 
@@
 The implementation of function application follows directly from the definition of
-the representation: $\setpair{I}{U}(m) = \lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.\mtodo{Should this be the denotation of $\setpair IU$?}
+the representation: $\setpair{I}{U}(m) = \lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
+%\mtodo{Should this be the denotation of $\setpair IU$?}
+%\otodo{No. It is an implementation of the apply operation.}
 
@@
 material submitted with the paper.
-\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}
 
-\otodo{The normalization function $\mathcal N$ was only needed in composition. I therefore
-    ``inlined'' it into composition to save space. This makes composition a bit harder to intuitively
-    verify, but saves complexity here. The verification can be in the proof in the supplementary appendix.}
 The composition of two micro-function representations is defined as follows:
@@
 \end{restatable}
-\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}
 
@@
      =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.
-\end{restatable}\mtodo{I added the definition of the meet of two functions.}
-\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}
+\end{restatable}%\mtodo{I added the definition of the meet of two functions.}
 
@@
 \subsection{Correlated-Call Receivers}\label{sec:ccreceivers}
-\otodo{should this be a section or subsection? should it be moved somewhere else (or maybe not included at all)?}
 We will now show that in a correlated-calls transformation, it is enough to consider only some of the receivers of set $R$.

### 2014-12-17 content/example.tex
add example from Scala library

@@
 call sites $C^\Subset$. We also see that, on average,  each correlated-call receiver is involved in three correlated calls.
+
+\subsection{An Example from the Scala Collections Library}
+The Scala collections library contains the trait \code{TraversableOnce} that is
+shared by both collections and iterators over them. The \code{toArray} method of this trait
+creates an array and copies the contents of the collection or iterator into it:
+%\begin{minted}{scala}
+\begin{verbatim}
+val result = new Array[B](this.size)
+this.copyToArray(result, 0)
+\end{verbatim}
+%\end{minted}
+\otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
+When \code{this} is an iterator rather than a collection, the call to \code{this.size}
+extracts all elements of the iterator to count them. At the call to \code{copyToArray},
+the iterator is already empty, so nothing is copied to the newly created array.
+One could design an IFDS analysis to detect this kind of bug.
+
+The implementation of \code{TraversableOnce.toArray} is actually correct because the above
+code is guarded with a test:
+\begin{verbatim}
+if(this.isTraversableAgain) ...
+\end{verbatim}
+When the \code{isTraversableAgain} method returns false, as it does for
+an iterator, the \code{toArray} method uses a different
+(less efficient) implementation. The bug report would therefore be a false positive. 
+The \code{isTraversableAgain} method is easy to analyze: it returns the constant
+true in a collection and the constant false in an iterator. However, in order
+to eliminate the false positive bug report, an analysis would need to rule out infeasible
+paths using correlated calls. Specifically, the following path triggers the bug, but
+is infeasible: first, call \code{isTraversableAgain} on a collection, returning
+true, then call \code{size} and \code{copyToArray} on an iterator. Our correlated
+calls analysis could determine that this path is infeasible because it calls the
+collection version of \code{isTraversableAgain} but the iterator versions of
+\code{size} and \code{copyToArray}.
+
+\commentout{
+    For reference, here is the full code of the method:
+
+def toArray[B >: A : ClassTag]: Array[B] = {
+    if (isTraversableAgain) {
+        val result = new Array[B](size)
+        copyToArray(result, 0)
+        result
+    }
+    else toBuffer.toArray
+}
+
+}

### 2014-12-17 content/appendix.tex
pass through appendix/proofs

@@
 \end{align*}
-\mtodo{I agree that this is much better than what I had. I think from $I(r) = I(r) \cap I'(r)$ we can conclude that $I(r)=I'(r)$.}
+%\mtodo{I agree that this is much better than what I had. I think from $I(r) = I(r) \cap I'(r)$ we can conclude that $I(r)=I'(r)$.}
+%\otodo{No. {1,2} = {1,2} \cap {1,2,3}, but {1,2} is not equal to {1,2,3}.}
 Symmetrically, we can also establish that $\forall r.I'(r) \subseteq I(r)$ by applying the functions to $I'$ instead of to $I$. Therefore, $I = I'$.
@@
 \equalComp*
-\otodo{The (m)(r) does not seem necessary. Can we replace $r'$ with $r$ and $m'$ with $m$?}
+%\otodo{The (m)(r) does not seem necessary. Can we replace $r'$ with $r$ and $m'$ with $m$?}
 \begin{proof}
@@
   =&\lambda m\,.\,\lambda r\,.\,(m(r)\cap I'(r))\cup I(r)\cup (U'(r)\cap I(r))\cup U(r)\\
-  =&\lambda m\,.\,\lambda r\,.\,(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
   =&\lambda m\,.\,\lambda r\,.\,(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
@@
     \begin{cases}
-      \id&\text{if $d_1=d_2=\Lambda$,}\\
+      \id&\text{if $d_1=d_2=\mathbf0$,}\\
       \lambda m\,.\,\varepsilon(e)(\delta(m))&\text{otherwise},
@@
     \delta(m)=\begin{cases}
-      \botcc&\text{if $d_1=\Lambda$}\\
+      \botcc&\text{if $d_1=\mathbf0$}\\
       m&\text{otherwise.}
@@
 
-  For each $i$, let $e_i$ be the edge $((n_{i-1},\,d_{i-1}),\,(n_i,\,d_i))$. Note that $$e_1=((\startmain,\,\Lambda),\,(n_1,\,d_1))\,.$$
+  For each $i$, let $e_i$ be the edge $((n_{i-1},\,d_{i-1}),\,(n_i,\,d_i))$. Note that $$e_1=((\startmain,\,\mathbf0),\,(n_1,\,d_1))\,.$$
 
@@
   \menv&((n_1,\,n_2))(\textsf{env})(d)\notag\\
-  &=\edgefn((n_1,\,\Lambda),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,.
+  &=\edgefn((n_1,\,\mathbf0),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,.
 \end{align}  
-Then, according to~\eqref{eq:envTransToEdgeFnEdge},\mtodo{Is it okay that in~\eqref{eq:envTransToEdgeFnEdge}, we use $\edgefn$, and below we use $\ccedgefn R$?}
+Then, according to~\eqref{eq:envTransToEdgeFnEdge},
+%\mtodo{Is it okay that in~\eqref{eq:envTransToEdgeFnEdge}, we use $\edgefn$, and below we use $\ccedgefn R$?}
+%\otodo{Yes, that's fine.}
   \begin{align*}
     &\menv(e_k)\left(\menv(p)(\top_\textsf{Env})\right)(d)(r)\\
-      =&\bigg(\ccedgefn R((n_{k-1},\,\Lambda),\,(n_k,\,d))(\topcc)\sqcap\\
+      =&\bigg(\ccedgefn R((n_{k-1},\,\mathbf0),\,(n_k,\,d))(\topcc)\sqcap\\
        &\bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\top_\textsf{Env})(d'))\bigg)(r)\\
@@
 
-  If $d_{k-1}=d_k=\Lambda$, then $d_k\notin M_F(p)(\varnothing)$, since it does not belong to the set $D$, and the Lemma trivially holds.
+  If $d_{k-1}=d_k=\mathbf0$, then $d_k\notin M_F(p)(\varnothing)$, since it does not belong to the set $D$, and the Lemma trivially holds.
 
@@
     Let $p=[\startmain]$.
-Since the only realizable path corresponding to $p$ is $[(\startmain,\,\Lambda)]$, there is no fact $d\in D$ such that $d\in M_F(p)(\varnothing)$, and the claim follows immediately.
+Since the only realizable path corresponding to $p$ is $[(\startmain,\,\mathbf0)]$, there is no fact $d\in D$ such that $d\in M_F(p)(\varnothing)$, and the claim follows immediately.
 
@@
 \begin{proof}
-    \otodo{It's Section 3.2.}
-    \mtodo{Section 3.2 talks about the IFDS algorithm, but it doesn't explicitly say how the result of an IFDS analysis looks like and doesn't introduce the notation $\resultIFDS$.}
+    %\otodo{It's Section 3.2.}
+    %\mtodo{Section 3.2 talks about the IFDS algorithm, but it doesn't explicitly say how the result of an IFDS analysis looks like and doesn't introduce the notation $\resultIFDS$.}
   Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
@@
 Let $N^*$ be the supergraph for $P$, $D$ the set of data-flow facts, $n\in N^*$ a node, and $p=[\startmain,\,\dots,\,n]$ a path in the supergraph.
-Let $d\in D\cup\{\Lambda\}$.
+Let $d\in D\cup\{\mathbf0\}$.
   Then for any realizable path $p'\in\textsf{RP}(p,\,d)$, set $S\subseteq R$, and receiver $r\in S$,
@@
 
-  \textit{Basis:} $p'=[(\startmain,\,\Lambda)]$. Then $\ccedgefn S(p')=\id=\ccedgefn{\{r\}}(p')$, and the Lemma follows directly.
+  \textit{Basis:} $p'=[(\startmain,\,\mathbf0)]$. Then $\ccedgefn S(p')=\id=\ccedgefn{\{r\}}(p')$, and the Lemma follows directly.
 
-  \textit{Induction hypothesis:} Suppose that for a path $q=[(\startmain,\,\Lambda),\,\dots,\,(n_{k-1},\,d_{k-1})]$, where $q\in\textsf{RP}(n,\,d)$, the Lemma holds, i.e.
+  \textit{Induction hypothesis:} Suppose that for a path $q=[(\startmain,\,\mathbf0),\,\dots,\,(n_{k-1},\,d_{k-1})]$, where $q\in\textsf{RP}(n,\,d)$, the Lemma holds, i.e.
 both edge functions map $r$ to the same set of types $\uptau$:
@@
 
-  \textit{Induction step:} Let $q'=[(\startmain,\,\Lambda),\,\dots,\,(n_{k-1},\,d_{k-1}),\,(n_k,\,d_k)]$ and the edge $e_k=((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))$.
+  \textit{Induction step:} Let $q'=[(\startmain,\,\mathbf0),\,\dots,\,(n_{k-1},\,d_{k-1}),\,(n_k,\,d_k)]$ and the edge $e_k=((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))$.
 
@@
 
-  If $d_{k-1}=d_k=\Lambda$, $\ccedgefn S(e_k)=\id=\ccedgefn{\{r\}}(e_k)$, and, due to~\eqref{eq:edgefnU},
+  If $d_{k-1}=d_k=\mathbf0$, $\ccedgefn S(e_k)=\id=\ccedgefn{\{r\}}(e_k)$, and, due to~\eqref{eq:edgefnU},
   \begin{align*}
@@
         \]
-        If $d_{k-1}=\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\botcc(r)=\bot_T$.
-If $d_{k-1}\ne\Lambda$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\ccedgefn U(q)(\topcc)(r)=\uptau$.
+        If $d_{k-1}=\mathbf0$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\botcc(r)=\bot_T$.
+If $d_{k-1}\ne\mathbf0$, then $\delta(\ccedgefn U(q)(\topcc))(r)=\ccedgefn U(q)(\topcc)(r)=\uptau$.
 The set $\tau(s,\,f)$ is the same for either case.
@@
 \begin{proof}
-  Let $p$ have the following form\footnote{It can be shown from the definition of a pointwise representation in~Sagiv et al.~\cite{sagiv1996precise} that in a realizable path, there is never an edge from a fact of the set $D$ to a $\Lambda$ fact.
-Therefore, we can represent $p$ as a sequence of nodes that has a prefix of $\Lambda$-fact nodes, after which all nodes are non-$\Lambda$ facts.}:
+  Let $p$ have the following form\footnote{It can be shown from the definition of a pointwise representation in~Sagiv et al.~\cite{sagiv1996precise} that in a realizable path, there is never an edge from a fact of the set $D$ to a $\mathbf0$ fact.
+Therefore, we can represent $p$ as a sequence of nodes that has a prefix of $\mathbf0$-fact nodes, after which all nodes are non-$\mathbf0$ facts.}:
   \[
-    p=[(\startmain,\,\Lambda),\,(n_1,\,\Lambda),\,\dots,\,(n_k,\,\Lambda),
+    p=[(\startmain,\,\mathbf0),\,(n_1,\,\mathbf0),\,\dots,\,(n_k,\,\mathbf0),
        (n_{k+1},\,d_{k+1}),\,\dots,\,(n_{k+l},\,d_{k+l})]\,,
   \]
-  where $l\ge1$ and the facts for all nodes up to $n_k$ are equal to $\Lambda$ and $d_{k+i}\in D$ for $0<i\le l$.
+  where $l\ge1$ and the facts for all nodes up to $n_k$ are equal to $\mathbf0$ and $d_{k+i}\in D$ for $0<i\le l$.
 
@@
   \]
-  \footnotetext{Since $d_k=\Lambda$ and $d_{k+1}\ne\Lambda$, the micro function for the edge $e_{k+1} $ is equal to $\lambda m\,.\,\varepsilon_{\{r\}}(e_{k+1})(\botcc)$.
+  \footnotetext{Since $d_k=\mathbf0$ and $d_{k+1}\ne\mathbf0$, the micro function for the edge $e_{k+1} $ is equal to $\lambda m\,.\,\varepsilon_{\{r\}}(e_{k+1})(\botcc)$.
 From the definition of $\varepsilon_S$~\eqref{eq:varepsilon} we can see that the only case where $\varepsilon_{\{r\}}(e_{k+1})(m)$ would not be equal to $\botcc$ is when $e_{k+1}$ is call-start or end-return edge.}
@@
 \textit{Induction hypothesis:}
-Assume that for a path $p=[(\startmain,\,\Lambda),\,\dots,\,(n_{k+l},\,d_{k+l})]$, the Lemma holds for $\gamma=N$, where $N\ge0$.
+Assume that for a path $p=[(\startmain,\,\mathbf0),\,\dots,\,(n_{k+l},\,d_{k+l})]$, the Lemma holds for $\gamma=N$, where $N\ge0$.
 
 \textit{Induction step:}
-Let $p'=[(\startmain,\,\Lambda),\,\dots,\,(n_{k+l},\,d_{k+l}),\,(n_{k+l+1},\,d_{k+l+1})]$.
+Let $p'=[(\startmain,\,\mathbf0),\,\dots,\,(n_{k+l},\,d_{k+l}),\,(n_{k+l+1},\,d_{k+l+1})]$.
 
@@
 
+\otodo{restate the lemma before the proof}
+
 \begin{proof}[\textbf{Proof of Lemma~\ref{lem:onlycorrrec}}]

### 2014-12-17 content/appendix.tex
.

@@
 
-    The fact that $\mpd(r)\ne\top_T$ means that there exists a realizable path corresponding to the fact $d$ along path $p$, and, by definition, $d$ must be contained in $M_F(p)(\varnothing)$.\mtodo{Is this hand-wavy?}
+    The fact that $\mpd(r)\ne\top_T$ means that there exists a realizable path corresponding to the fact $d$ along path $p$, and, by definition, $d$ must be contained in $M_F(p)(\varnothing)$.
+    %\mtodo{Is this hand-wavy?}
+    %\otodo{No, I think it's fine.}
 \end{proof}

### 2014-12-17 content/example.tex
highlight
isTraversable highlight

@@
 creates an array and copies the contents of the collection or iterator into it:
-%\begin{minted}{scala}
-\begin{verbatim}
-val result = new Array[B](this.size)
-this.copyToArray(result, 0)
-\end{verbatim}
-%\end{minted}
+\inputMinted{java}{collectionsExample.java}
 \otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
@@
 code is guarded with a test:
-\begin{verbatim}
-if(this.isTraversableAgain) ...
-\end{verbatim}
+\inputMinted{java}{isTraversable.java}
 When the \code{isTraversableAgain} method returns false, as it does for

### 2014-12-17 content/example.tex
remove finished todos

@@
 \inputMinted{java}{collectionsExample.java}
-\otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
+%\otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
 When \code{this} is an iterator rather than a collection, the call to \code{this.size}

### 2014-12-17 content/concl.tex
rephrasing

@@
 IDE problem can be mapped back to the solution space of the original IFDS
-problem, and is potentially more precise because the flow of data along
+problem, and is more precise for some client programs because the flow of data along
 infeasible paths is prevented. We present a formalization of the

### 2014-12-17 content/example.tex
change titles of section 2 and 3
minor tweaks and comments on section 2.2

@@
-\section{Motivating Example}
+\section{Background and Motivation}
   \label{sec:MotivatingExample}
@@
 The Scala collections library contains the trait \code{TraversableOnce} that is
-shared by both collections and iterators over them. The \code{toArray} method of this trait
+shared by both collections and iterators over them. 
+\ftodo{
+  I think it would be helpful to show a little more of the code of the trait here,
+  such as the trait declaration and the signature of the toArray method containing the
+  correlated calls. You can abbreviate everything else with ...
+}
+The \code{toArray} method of this trait
 creates an array and copies the contents of the collection or iterator into it:
@@
 %\otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
-When \code{this} is an iterator rather than a collection, the call to \code{this.size}
-extracts all elements of the iterator to count them. At the call to \code{copyToArray},
+When \code{this} refers to an iterator rather than a collection, the call to \code{this.size}
+extracts all elements of the iterator to count them.
+\ftodo{
+  Would it make sense to show the code for the size method, and refer to the line numbers
+  of that method in the above sentence?  
+}
+ At the call to \code{copyToArray},
 the iterator is already empty, so nothing is copied to the newly created array.
+\ftodo{
+Would it make sense to show the code for copyToArray here?
+}
 One could design an IFDS analysis to detect this kind of bug.
 
-The implementation of \code{TraversableOnce.toArray} is actually correct because the above
+However, the implementation of \code{TraversableOnce.toArray} is actually correct because the above
 code is guarded with a test:
 \inputMinted{java}{isTraversable.java}
+\ftodo{
+  It is confusing that this code fragment is labeled with line number 19 although it presumably
+  occurs in the code before the previously discussed two lines. I think it is better to show
+  all of the code at once, in a figure, and include at least the headers of all the methods mentioned
+  here.
+}
 When the \code{isTraversableAgain} method returns false, as it does for
@@
 \code{size} and \code{copyToArray}.
+\ftodo{Would it be helpful to create a diagram of the relevant fragments of the supergraph,
+with the infeasible path in bold?}
 

### 2014-12-17 content/impl.tex
restating lemma
sorting citations; adding efficiency lemma and proof

@@
 
+\subsection{Efficiency}
 \otodo{Sagiv et al. define a notion of an ``efficient'' implementation of micro-functions.
@@
     I'm leaning towards leaving out any mention of ``efficient'' implementation.}
+As defined in~Sagiv et al.~\cite{sagiv1996precise}, a representation of micro functions is efficient if the following conditions hold:
+\begin{enumerate}
+	\item There is a representation for the identity and top functions.
+  \item The representation is closed under the meet and composition operations.
+  \item The micro functions form a finite-height lattice.
+  \item The apply, meet, composition, and equality-check operations can be computed in constant time.
+  \item There is a constant bound on the storage space for a micro function representation.
+\end{enumerate}
+\begin{restatable}{lemma}{efficient}\label{lem:efficient}
+  The correlated-call representation of a micro function is efficient.
+\end{restatable}
 
@@
 
-\begin{lemma}\label{lem:onlycorrrec}
+\begin{restatable}{lemma}{onlycorrrec}\label{lem:onlycorrrec}
   Let $P$ be an IFDS problem. Then

### 2014-12-17 content/appendix.tex
restating lemma
remove finished todos
sorting citations; adding efficiency lemma and proof
reformulating proof

@@
 \end{align*}
+\end{proof}
+
+\efficient*
+\begin{proof}
+\leavevmode
+  \begin{enumerate}
+    \item The identity function is represented as $\lambda r\,.\,\setpair{\bot_T}{\top_T}$. 
+    The top function is represented as $\lambda r\,.\,\setpair{\top_T}{\top_T}$.
+    \item Lemmas~\ref{lem:equalComp} and \ref{lem:equalMeet} show that the representation of micro functions is closed under composition and meet.
+    \item To show that our representation for micro functions forms a lattice with finite height, let us first show that $\lcc_\rcc:\,\rcc\to2^T$ forms a lattice.
+Since $T$ is a finite set, $(2^T,\,\subseteq)$ is a finite-height lattice.
+$\rcc$ is a finite set.
+Hence, the mapping
+    \[
+      \rcc\mapsto2^T=\{(r,\,t)\,|\,r\in \rcc,\,t\in 2^T\}=\lcc_\rcc
+    \]        
+    also forms a finite-height lattice \cite{nielson1999principles}.
+
+    Furthermore, $\lcc_\rcc$ is a finite set. 
+    Every element of $\lcc_\rcc$ can be applied to $|\rcc|$ receivers, where each receiver is mapped to a set of types.
+There are $|\rcc|\cdot2^{|T|}$ different possibilities to form those mappings, so
+    \[
+      |\lcc_\rcc|=|\rcc|\cdot2^{|T|}.
+    \]
+    Therefore, $\lcc_\rcc\mapsto \lcc_\rcc$ also forms a finite-height lattice.
+    \item All operations can be computed in $O(\rcc\times T)$ time.
+Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
+    \item The space bound is $O(\rcc\times T)$.\qedhere
+  \end{enumerate}
 \end{proof}
@@
 
-\otodo{restate the lemma before the proof}
-
+%\otodo{restate the lemma before the proof}
+\onlycorrrec*
 \begin{proof}[\textbf{Proof of Lemma~\ref{lem:onlycorrrec}}]

### 2014-12-17 content/example.tex
scala instead of java

--- 2014-12-17 content/example.tex
@@
 creates an array and copies the contents of the collection or iterator into it:
-\inputMinted{java}{collectionsExample.java}
+\inputMinted{scala}{collectionsExample.scala}
 \otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
@@
 code is guarded with a test:
-\inputMinted{java}{isTraversable.java}
+\inputMinted{scala}{isTraversable.scala}
 When the \code{isTraversableAgain} method returns false, as it does for

### 2014-12-17 content/abstract.tex
pass through abstract, introduction, example, conclusion
spell check

@@
 \begin{abstract}
-    When two methods are invoked on the same object, the dispatch behaviors of these
+    When two methods are invoked on the same object, the dispatch behaviours of these
     method calls will be correlated. If two correlated method calls are polymorphic 
@@
 	to this IDE problem can be mapped back to the solution space of the original
-	IFDS problem. We prove the correctness of our approach, and report on
-	some preliminary experiments with our prototype implementation. 
+	IFDS problem.
+        We formalize the approach, prove it correct, and report on an implementation
+        in the WALA analysis framework.
 \end{abstract}

### 2014-12-17 content/background.tex
remove completed comment
spell check

@@
-\section{Background}\label{sec:bg}
+\section{IFDS and IDE}\label{sec:bg}
 %The purpose of the correlated-calls analysis is to solve IFDS problems more precisely than using the standard IFDS algorithm by ruling out some infeasible paths.
@@
 $M_F:\,E^*\to F$ assigns a dataflow function to each supergraph edge,
-and $\sqcap$ is the \textit{meet operator} on the powerset $2^D$, either union or intersection.
+and $\sqcap$ is the \textit{meet operator} on the power set $2^D$, either union or intersection.
 In our presentation, the meet operator will always be union, but all of the results apply dually when the
@@
     types. The interpretation of such an environment $e$ is that a given variable
-    $v \in D$ may contain a secret value in an exeuction in which the runtime
+    $v \in D$ may contain a secret value in an execution in which the runtime
     types of the objects pointed to be the receiver variables are in the sets
@@
 
+\commentout{
 \ftodo{Would it make sense to discuss an example of an IDE problem here?  Perhaps we can do this
@@
   \otodo{See Example 4 on the previous page.}
+  \otodo{Now done in Example 5.}
+}

### 2014-12-17 content/example.tex
spell check

--- 2014-12-17 content/example.tex
@@
 However, consider the fact that the methods \code{foo()} and \code{bar()} are invoked
-on \textit{the same object}. This means that the behaviors of the two method calls
+on \textit{the same object}. This means that the behaviours of the two method calls
 are \textit{correlated}: if the call to \code{foo()} dispatches to \code{A.foo()},
@@
 creates an array and copies the contents of the collection or iterator into it:
-\inputMinted{java}{collectionsExample.java}
+\inputMinted{scala}{collectionsExample.scala}
 %\otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
@@
 code is guarded with a test:
-\inputMinted{java}{isTraversable.java}
+\inputMinted{scala}{isTraversable.scala}
 \ftodo{

### 2014-12-17 content/intro.tex
spell check

@@
 depending on the type of the receiver expression at run time), then their dispatch 
-behaviors will be correlated. A recent paper \cite{DBLP:journals/scp/Tip15} identified
+behaviours will be correlated. A recent paper \cite{DBLP:journals/scp/Tip15} identified
 this problem but did not present a concrete solution or algorithm, and we are not aware 

### 2014-12-17 content/background.tex
inter- and intra-procedural to interprocedural and intraprocedural

--- 2014-12-17 content/background.tex
@@
 %A control-flow graph has a unique start node, $\startmain$, which is the node corresponding to the program entrypoint.
-%An \textit{intra-procedural} path is a path in a control-flow graph whose nodes are in the same procedure.
-By contrast, an \textit{inter-procedural path} is one that contains nodes from different procedures.
+%An \textit{intraprocedural} path is a path in a control-flow graph whose nodes are in the same procedure.
+By contrast, an \textit{interprocedural path} is one that contains nodes from different procedures.
 The \textit{control-flow supergraph} of a program contains the CFGs of all of the procedures as
@@
 
-%A control-flow supergraph allows us to model the control flow in inter-procedural paths.
+%A control-flow supergraph allows us to model the control flow in interprocedural paths.
  %The flow from the caller to the callee is represented using an edge \[(\textsf{call}_{c_q},\,\textsf{start}_q)\,.\] The control flow from the callee back to the caller goes through an edge \[(\textsf{end}_q,\,\textsf{return}_{c_q})\,.\]
@@
     \node [description] (inter_arrow_right) [below = .5*\dist of intra_arrow_right] {};
-    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intra-procedural edge} (intra_arrow_right);
-    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{inter-procedural edge} (inter_arrow_right);
+    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intraprocedural edge} (intra_arrow_right);
+    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{interprocedural edge} (inter_arrow_right);
 \end{tikzpicture}
@@
 %Then $p$ is \textit{valid} if $s$ belongs to the language of substrings of balanced parentheses.
-The set of all inter-procedurally valid paths from the start node to a node $n$ is denoted as $\ivp(n)$.
+The set of all interprocedurally valid paths from the start node to a node $n$ is denoted as $\ivp(n)$.
 The set $\ivp(n)$ is a conservative approximation of all concrete execution paths from the start node to $n$.
 
-%A \textit{context-sensitive} data-flow analysis is an analysis that considers only inter-procedurally valid paths.
+%A \textit{context-sensitive} data-flow analysis is an analysis that considers only interprocedurally valid paths.
 
@@
 
-However, the graph also contains an inter-procedurally invalid path
+However, the graph also contains an interprocedurally invalid path
   \[
@@
 This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.}
-The IFDS framework is applicable to \textit{inter-procedural} data flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
+The IFDS framework is applicable to \textit{interprocedural} data flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
 and whose data-flow functions are \textit{distributive}.
@@
 %The IFDS algorithm is applicable to problems which can be expressed with data-flow functions that satisfy certain restrictions.
-\textit{Inter-procedural} flow functions specify how data flows from the invocation of a procedure to its start, and from the procedure's end back to its call site.
+\textit{Interprocedural} flow functions specify how data flows from the invocation of a procedure to its start, and from the procedure's end back to its call site.
 \textit{Distributive} flow functions are those that distribute over the confluence operator.
@@
 
-\commentout{The purpose of the IFDS framework is to solve a special subset of inter-procedural, flow-sensitive, context-sensitive data-flow-analysis problems.
+\commentout{The purpose of the IFDS framework is to solve a special subset of interprocedural, flow-sensitive, context-sensitive data-flow-analysis problems.
 The main idea of IFDS is to encode the data-flow analysis problem into a graph-reachability problem.}
@@
 The flow functions $F$ define the edges of the exploded supergraph.
-Using the flow functions, the IFDS algorithm computes the inter-procedurally \textit{realizable} paths from the start to the rest of the exploded graph's nodes.
+Using the flow functions, the IFDS algorithm computes the interprocedurally \textit{realizable} paths from the start to the rest of the exploded graph's nodes.
 A realizable path is a valid path in the exploded supergraph that starts with the entry node $\startmain$.
@@
 The problems that IDE can solve include, but are not limited to, IFDS problems~\cite{reps1995precise}.
-Just as the IFDS algorithm, the IDE algorithm is suitable for data-flow analyses that can be encoded with inter-procedural, distributive flow functions.
+Just as the IFDS algorithm, the IDE algorithm is suitable for data-flow analyses that can be encoded with interprocedural, distributive flow functions.
 However, in IDE, the domain of the flow functions is not restricted to sets $D$ of data-flow facts.
@@
 The IDE algorithm~\cite{sagiv1996precise} extends IFDS to
-\textit{inter-procedural} \textit{distributive} \textit{environment}
+\textit{interprocedural} \textit{distributive} \textit{environment}
 problems. An \textit{environment} problem is an analysis whose dataflow
@@
 Should I try to replace it with one paragraph that tries to give an intuitive understanding of what the IDE algorithm is doing?}
-The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each inter-procedurally realizable path
+The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each interprocedurally realizable path
 \[

### 2014-12-17 content/eval.tex
pass through section 3
inter- and intra-procedural to interprocedural and intraprocedural

@@
 
+\commentout{
 \begin{odelete}
@@
 \begin{itemize}
-  \item \textsf{call-start}, for inter-procedural edges from a call node to the start node of the target method;
-  \item \textsf{call-return}, for intra-procedural edges from a call node to its return node;
-  \item \textsf{end-return}, for inter-procedural edges from the end node of a method to the return node of the callee;
-  \item \textsf{default}, for all other intra-procedural edges.
+  \item \textsf{call-start}, for interprocedural edges from a call node to the start node of the target method;
+  \item \textsf{call-return}, for intraprocedural edges from a call node to its return node;
+  \item \textsf{end-return}, for interprocedural edges from the end node of a method to the return node of the callee;
+  \item \textsf{default}, for all other intraprocedural edges.
 \end{itemize}
 \end{odelete}
+}
 
@@
 \end{align*}
-where $\epsilon$ is the bottom function on an edge from a $\Lambda$-fact to a non-$\Lambda$-fact, and the identity function otherwise:
+where $\epsilon$ is the bottom function on an edge from a $\mathbf0$-fact to a non-$\mathbf0$-fact, and the identity function otherwise:
 \[
   \epsilon(d_1,\,d_2)=\begin{cases}
-    \lambda l\,.\,\bot&\text{if $d_1=\Lambda$ and $d_2\ne\Lambda$;}\\
+    \lambda l\,.\,\bot&\text{if $d_1=\mathbf0$ and $d_2\ne\mathbf0$;}\\
     \id&\text{otherwise.}
@@
 
-We tested the propagation of constants on different intra- and inter-procedural data-flow paths, in parameter passing,
+We tested the propagation of constants on different intra- and interprocedural data-flow paths, in parameter passing,
 and in conditional branches. Each regression test contained assertions of the form ``at the end of method $m$, variable with name $x$ should be (not) constant''.
@@
   \end{minipage}
-  \caption{Inter-procedurally-correlated calls}
+  \caption{Interprocedurally-correlated calls}
   \label{list:interProcRec}
@@
 
-Another constraint of the algorithm is that it only accounts for intra-procedurally-correlated receivers, or receivers on which correlated calls occur within one method.
+Another constraint of the algorithm is that it only accounts for intraprocedurally-correlated receivers, or receivers on which correlated calls occur within one method.
 For example, in Listing~\ref{list:interProcRec}, \verb'a' is a correlated-call receiver, since there are two polymorphic method invocations on \verb'a'.

### 2014-12-18 content/impl.tex
inter- and intra-procedural to interprocedural and intraprocedural
edit efficiency subsection

@@
 \end{equation}
-where $n\in N^*$, $d\in D$, $p\in\ivp(n)$, and $\mathsf{RP}$ is the set of all inter-procedurally realizable paths.
+where $n\in N^*$, $d\in D$, $p\in\ivp(n)$, and $\mathsf{RP}$ is the set of all interprocedurally realizable paths.
 
@@
   \backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
-\end{equation}\mtodo{Another change was that Ondrej defined $\backEq$ as $\lambda n.\{d\mid\rho(n)(d)=\top\}$
-and that he defined $\backEq$ related to the equivalence transformation.}
-\otodo{I don't understand this comment. What does it mean?}
+\end{equation}
+%\mtodo{Another change was that Ondrej defined $\backEq$ as $\lambda n.\{d\mid\rho(n)(d)=\top\}$
+%and that he defined $\backEq$ related to the equivalence transformation.}
+%\otodo{I don't understand this comment. What does it mean?}
 
@@
 \begin{equation}\label{eq:transCcDef}
-  \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)\neq\top_T\}.
+    \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.
 \end{equation}
+\otodo{In Equation (5), I changed $\rho(n)(d)$ to $\rho(n)(d)(r)$, because I think
+    the original was incorrect. Marianna, please check that this correction is correct.}
 
@@
 
-\subsection{Efficiency}
-\otodo{Sagiv et al. define a notion of an ``efficient'' implementation of micro-functions.
-    If the micro-functions are ``efficient'', then the asymptotic complexity bounds proven by
-    Sagiv hold. Our implementation is ``efficient'' if we assume that the number of correlated
-    receivers is a constant independent of the size of the program. That seems a stretch. If
-    it's linear in the size of the program, then we would need to add a factor to their complexity
-    bounds. Their bound is $O(ED^3)$, while ours would be $O(ED^3R)$. But then we can't directly use their complexity proof; we would have to adapt it.
-    I'm leaning towards leaving out any mention of ``efficient'' implementation.}
-As defined in~Sagiv et al.~\cite{sagiv1996precise}, a representation of micro functions is efficient if the following conditions hold:
-\begin{enumerate}
-	\item There is a representation for the identity and top functions.
-  \item The representation is closed under the meet and composition operations.
-  \item The micro functions form a finite-height lattice.
-  \item The apply, meet, composition, and equality-check operations can be computed in constant time.
-  \item There is a constant bound on the storage space for a micro function representation.
-\end{enumerate}
-\begin{restatable}{lemma}{efficient}\label{lem:efficient}
-  The correlated-call representation of a micro function is efficient.
-\end{restatable}
-
 \subsection{Theoretical Results}
@@
 
+\subsection{Efficiency}
+\commentout{
+\otodo{Sagiv et al. define a notion of an ``efficient'' implementation of micro-functions.
+    If the micro-functions are ``efficient'', then the asymptotic complexity bounds proven by
+    Sagiv hold. Our implementation is ``efficient'' if we assume that the number of correlated
+    receivers is a constant independent of the size of the program. That seems a stretch. If
+    it's linear in the size of the program, then we would need to add a factor to their complexity
+    bounds. Their bound is $O(ED^3)$, while ours would be $O(ED^3R)$. But then we can't directly use their complexity proof; we would have to adapt it.
+    I'm leaning towards leaving out any mention of ``efficient'' implementation.}
+}
+
+Both the IFDS and IDE algorithms have been proven
+to run in $O(ED^3)$ time~\cite{reps1995precise,sagiv1996precise},
+where $E$ is the number of edges in the (non-exploded) supergraph, and $D$ is the size
+of the set of facts.
+The complexity proof for the IDE algorithm requires the implementation of the micro-functions
+to be \textit{efficient} according to the following criteria:
+\begin{enumerate}
+	\item There is a representation for the identity and top functions.
+  \item The representation is closed under the meet and composition operations.
+  \item The micro functions form a finite-height lattice.
+  \item The apply, meet, composition, and equality-check operations can be computed in constant time.
+  \item There is a constant bound on the storage space for a micro function representation.
+\end{enumerate}
+We prove that the micro-functions for the correlated-call analysis satisfy these
+criteria if we consider the number of correlated-call receivers $R$ and the
+number of run-time types $T$ constant
+(i.e. the operations on micro-functions are allowed to use time that is $O(RT)$,
+but constant with respect to $E$ and $D$).
+
+\begin{restatable}{lemma}{efficient}\label{lem:efficient}
+  The correlated-call representation of a micro function is efficient if the number of
+  correlated-call receivers $R$ and the number of run-time types $T$ are considered constant.
+\end{restatable}
+
+From this lemma, we conclude that the correlated-calls analysis runs in time
+$O(ED^3RT)$. In other words, the asymptotic cost of the added precision of
+the correlated-calls analysis is increased by a factor of $O(RT)$ compared
+to the original IFDS analysis.
+
 \subsection{Implementation of the Correlated-Calls Analysis}

### 2014-12-18 content/example.tex
remove line numbers from short code snippets

@@
 creates an array and copies the contents of the collection or iterator into it:
-\inputMinted{scala}{collectionsExample.scala}
+\inputMintedNoLNs{scala}{collectionsExample.scala}
 %\otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
@@
 code is guarded with a test:
-\inputMinted{scala}{isTraversable.scala}
+\inputMintedNoLNs{scala}{isTraversable.scala}
+\commentout{
 \ftodo{
@@
   here.
+}
 }

### 2014-12-18 content/impl.tex
add missing comma

@@
 number of run-time types $T$ constant
-(i.e. the operations on micro-functions are allowed to use time that is $O(RT)$,
+(i.e., the operations on micro-functions are allowed to use time that is $O(RT)$,
 but constant with respect to $E$ and $D$).

### 2014-12-18 content/impl.tex
remove comment

--- 2014-12-17 content/impl.tex
@@
   \backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
-\end{equation}\mtodo{Another change was that Ondrej defined $\backEq$ as $\lambda n.\{d\mid\rho(n)(d)=\top\}$
-and that he defined $\backEq$ related to the equivalence transformation.}
-\otodo{I don't understand this comment. What does it mean?}
+\end{equation}
+%\mtodo{Another change was that Ondrej defined $\backEq$ as $\lambda n.\{d\mid\rho(n)(d)=\top\}$ and that he defined $\backEq$ related to the equivalence transformation.}
+%\otodo{I don't understand this comment. What does it mean?}
 

### 2014-12-18 content/example.tex
add full code for TraversableOnce

@@
 shared by both collections and iterators over them. 
-\ftodo{
+\commentout\ftodo{
   I think it would be helpful to show a little more of the code of the trait here,
@@
 extracts all elements of the iterator to count them.
-\ftodo{
+\commentout\ftodo{
   Would it make sense to show the code for the size method, and refer to the line numbers
@@
 the iterator is already empty, so nothing is copied to the newly created array.
-\ftodo{
+\commentout\ftodo{
 Would it make sense to show the code for copyToArray here?
@@
 \code{size} and \code{copyToArray}.
-\ftodo{Would it be helpful to create a diagram of the relevant fragments of the supergraph,
+\commentout\ftodo{Would it be helpful to create a diagram of the relevant fragments of the supergraph,
 with the infeasible path in bold?}
@@
 }
+
+The relevant code from \textsf{TraversableOnce} and other related traits is shown
+in Figure~\ref{fig:traversableonce}.
+
+\begin{figure}
+\inputMinted{scala}{TraversableOnce.scala}
+\caption{Relevant code from \textsf{TraversableOnce} and related traits.}
+\label{fig:traversableonce}
+\end{figure}

### 2014-12-18 content/impl.tex
rcc instead of R

--- 2014-12-18 content/impl.tex
@@
 \end{equation}
-%\mtodo{Another change was that Ondrej defined $\backEq$ as $\lambda n.\{d\mid\rho(n)(d)=\top\}$
-%and that he defined $\backEq$ related to the equivalence transformation.}
+
 %\otodo{I don't understand this comment. What does it mean?}
@@
   The correlated-call representation of a micro function is efficient if the number of
-  correlated-call receivers $R$ and the number of run-time types $T$ are considered constant.
+  correlated-call receivers $\rcc$ and the number of run-time types $T$ are considered constant.
 \end{restatable}
@@
 From this lemma, we conclude that the correlated-calls analysis runs in time
-$O(ED^3RT)$. In other words, the asymptotic cost of the added precision of
-the correlated-calls analysis is increased by a factor of $O(RT)$ compared
+$O(ED^3\rcc T)$. In other words, the asymptotic cost of the added precision of
+the correlated-calls analysis is increased by a factor of $O(\rcc T)$ compared
 to the original IFDS analysis.

### 2014-12-18 content/appendix.tex
hyphens

@@
 
-\subsection*{Correlated Call Receivers}
+\subsection*{Correlated-Call Receivers}
 We will now present the proof for Lemma~\ref{lem:onlycorrrec} which shows that in a correlated-calls analysis, it is enough to consider only correlated-call receivers~$\rcc$.

### 2014-12-18 content/impl.tex
uncommenting Ondrejs comment
hyphens

@@
 \end{equation}
-\otodo{In Equation (5), I changed $\rho(n)(d)$ to $\rho(n)(d)(r)$, because I think
-    the original was incorrect. Marianna, please check that this correction is correct.}
+%\otodo{In Equation (5), I changed $\rho(n)(d)$ to $\rho(n)(d)(r)$, because I think
+%    the original was incorrect. Marianna, please check that this correction is correct.}
 
@@
 We will show that IDE problems obtained through ordinary and reduced correlated-calls transformations yield the same results.
-In other words, we show that if a correlated calls analysis considers only correlated-call receivers, no precision is lost.
+In other words, we show that if a correlated-calls analysis considers only correlated-call receivers, no precision is lost.
 

### 2014-12-18 content/intro.tex
hyphens

@@
 is equivalent to the one obtained by applying the IFDS algorithm to the original IFDS problem.
-Then, we derive a ``Correlated Calls 
+Then, we derive a ``Correlated-Calls 
 IDE Problem'' from the original IFDS problem and show 

### 2014-12-18 content/example.tex
uncommenting part of the comments

@@
 shared by both collections and iterators over them. 
-\commentout\ftodo{
-  I think it would be helpful to show a little more of the code of the trait here,
-  such as the trait declaration and the signature of the toArray method containing the
-  correlated calls. You can abbreviate everything else with ...
-}
+%\ftodo{
+%  I think it would be helpful to show a little more of the code of the trait here,
+%  such as the trait declaration and the signature of the toArray method containing the
+%  correlated calls. You can abbreviate everything else with ...
+%}
 The \code{toArray} method of this trait
@@
 extracts all elements of the iterator to count them.
-\commentout\ftodo{
-  Would it make sense to show the code for the size method, and refer to the line numbers
-  of that method in the above sentence?  
-}
+%\ftodo{
+%  Would it make sense to show the code for the size method, and refer to the line numbers
+%  of that method in the above sentence?  
+%}
  At the call to \code{copyToArray},
 the iterator is already empty, so nothing is copied to the newly created array.
-\commentout\ftodo{
-Would it make sense to show the code for copyToArray here?
-}
+%\ftodo{
+%Would it make sense to show the code for copyToArray here?
+%}
 One could design an IFDS analysis to detect this kind of bug.
@@
 \inputMintedNoLNs{scala}{isTraversable.scala}
-\commentout{
-\ftodo{
-  It is confusing that this code fragment is labeled with line number 19 although it presumably
-  occurs in the code before the previously discussed two lines. I think it is better to show
-  all of the code at once, in a figure, and include at least the headers of all the methods mentioned
-  here.
-}
-}
+%\ftodo{It is confusing that this code fragment is labeled with line number 19 although it presumably
+%  occurs in the code before the previously discussed two lines. I think it is better to show
+%  all of the code at once, in a figure, and include at least the headers of all the methods mentioned
+%  here.}
 When the \code{isTraversableAgain} method returns false, as it does for
@@
 \code{size} and \code{copyToArray}.
-\commentout\ftodo{Would it be helpful to create a diagram of the relevant fragments of the supergraph,
-with the infeasible path in bold?}
+%\ftodo{Would it be helpful to create a diagram of the relevant fragments of the supergraph,
+%with the infeasible path in bold?}
 

### 2014-12-18 content/impl.tex
uncommenting part of the comments

@@
   \commentout{
-\otodo{The following definitions are very general, and not related to the transformation.
-    Can we move them somewhere earlier?}
+%\otodo{The following definitions are very general, and not related to the transformation. Can we move them somewhere earlier?}
 \paragraph{Edge Functions}\label{sec:ef}
@@
 \commentout{
-\otodo{incorporate into previous section}
+%\otodo{incorporate into previous section}
 \subsection{Defining IFDS and IDE Problems}
@@
 \subsection{Efficiency}
-\commentout{
-\otodo{Sagiv et al. define a notion of an ``efficient'' implementation of micro-functions.
-    If the micro-functions are ``efficient'', then the asymptotic complexity bounds proven by
-    Sagiv hold. Our implementation is ``efficient'' if we assume that the number of correlated
-    receivers is a constant independent of the size of the program. That seems a stretch. If
-    it's linear in the size of the program, then we would need to add a factor to their complexity
-    bounds. Their bound is $O(ED^3)$, while ours would be $O(ED^3R)$. But then we can't directly use their complexity proof; we would have to adapt it.
-    I'm leaning towards leaving out any mention of ``efficient'' implementation.}
-}
+%\otodo{Sagiv et al. define a notion of an ``efficient'' implementation of micro-functions.
+%    If the micro-functions are ``efficient'', then the asymptotic complexity bounds proven by
+%    Sagiv hold. Our implementation is ``efficient'' if we assume that the number of correlated
+%    receivers is a constant independent of the size of the program. That seems a stretch. If
+%    it's linear in the size of the program, then we would need to add a factor to their complexity
+%    bounds. Their bound is $O(ED^3)$, while ours would be $O(ED^3R)$. But then we can't directly use their complexity proof; we would have to adapt it.
+%    I'm leaning towards leaving out any mention of ``efficient'' implementation.}
 

### 2014-12-18 content/background.tex
uncommenting rest of comments

@@
   Consider the program in Listing~\ref{list:examplejava}. The supergraph corresponding to that program is shown in Figure~\ref{fig:examplesupergraph}.
-  \otodo{Can we merge the examples from Figures 1 and 2 into a single example program?}
-\otodo{I think we can remove the supergraph Figure 3.}
+  %\otodo{Can we merge the examples from Figures 1 and 2 into a single example program?}
+%\otodo{I think we can remove the supergraph Figure 3.}
 \begin{figure}
@@
   is $\{\}$, which indicates that $p_1$ is valid. Every prefix of $p_1$ is also a valid path.
-
-\mtodo{The figure that we deleted was constructed so that there would be a realizable and a non-realizable path. Now that we deleted that figure, let's delete this example as well.}
 
@@
 For convenience, the function $f$ can be split up into separate functions that handle the cases when
-the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.\mtodo{Do we leave the start-to-return edge out as a special case of intraprocedural edge?}
+the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.
+%\mtodo{Do we leave the start-to-return edge out as a special case of intraprocedural edge?}
 }
@@
 
-\mtodo{I think the rest of this section will not make sense to anyone who does not already understand it.
-Should I try to replace it with one paragraph that tries to give an intuitive understanding of what the IDE algorithm is doing?}
 The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each interprocedurally realizable path
@@
 
-\commentout{
-\ftodo{Would it make sense to discuss an example of an IDE problem here?  Perhaps we can do this
-  without using much space by referring to an existing figure elsewhere in the paper?}
-  \otodo{See Example 4 on the previous page.}
-  \otodo{Now done in Example 5.}
-}
+%\ftodo{Would it make sense to discuss an example of an IDE problem here?  Perhaps we can do this
+%  without using much space by referring to an existing figure elsewhere in the paper?}
+%  \otodo{See Example 4 on the previous page.}
+%  \otodo{Now done in Example 5.}

### 2014-12-18 content/abstract.tex
remove abbreviation

@@
     (i.e., they dispatch to different method definitions depending on the type of 
-    the receiver object), a program's interprocedural control flow graph (ICFG)
+    the receiver object), a program's interprocedural control flow graph
     will contain infeasible paths. Existing algorithms for dataflow analysis 

### 2014-12-18 content/appendix.tex
spacing

@@
     \]        
-    also forms a finite-height lattice \cite{nielson1999principles}.
+    also forms a finite-height lattice~\cite{nielson1999principles}.
 
@@
 \end{proof}
-
-\commentout{
-\begin{proof}[\textbf{Proof of Lemma~\ref{lem:efficient}}]
-  \begin{enumerate}
-    \item The identity function is represented as
-      \[
-        \denote{\id}=\{(r,\,\langle \bot_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,;
-      \]
-      the top function is represented as
-      \[
-        \denote{\lambda m\,.\,\topcc}=\{(r,\,\langle \top_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,.
-      \]
-    \item Equations~\eqref{eq:compclosed} and~\eqref{eq:meetclosed} show that the representation of micro functions is closed under composition and meet.
-    \item To show that our representation for micro functions forms a lattice with finite height, let us first show that $\lcc_\rcc:\,\rcc\to2^T$ forms a lattice.
-Since $T$ is a finite set, $(2^T,\,\subseteq)$ is a finite-height lattice.
-$\rcc$ is a finite set.
-Hence, the mapping
-    \[
-      \rcc\mapsto2^T=\{(r,\,t)\,|\,r\in \rcc,\,t\in 2^T\}=\lcc_\rcc
-    \]        
-    also forms a finite-height lattice \cite{nielson1999principles}.
-
-    Furthermore, $\lcc_\rcc$ is a finite set. 
-    Every element of $\lcc_\rcc$ can be applied to $|\rcc|$ receivers, where each receiver is mapped to a set of types.
-There are $|\rcc|\cdot2^{|T|}$ different possibilities to form those mappings, so
-    \[
-      |\lcc_\rcc|=|\rcc|\cdot2^{|T|}.
-    \]
-    Therefore, $\lcc_\rcc\mapsto \lcc_\rcc$ also forms a finite-height lattice.
-    \item All operations can be computed in $O(\rcc\times T)$ time.
-Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
-    \item The space bound is $O(\rcc\times T)$.
-  \end{enumerate}
-\end{proof}
-}
 

### 2014-12-18 content/background.tex
spacing

@@
 $n_2$ may execute immediately after $n_1$. A CFG has a distinguished \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$.
-Following the presentation of \cite{reps1995precise,sagiv1996precise}, we follow every
+Following the presentation of Reps~et~al.~\cite{reps1995precise,sagiv1996precise}, we follow every
 call instruction with a no-op instruction, so that every \textit{call node} is immediately

### 2014-12-18 content/example.tex
spacing

@@
 operations such as calls to 
-a database. In previous research \cite{DBLP:conf/issta/GuarnieriPTDTB11,DBLP:conf/pldi/ArztRFBBKTOM14}, 
+a database. In previous research~\cite{DBLP:conf/issta/GuarnieriPTDTB11,DBLP:conf/pldi/ArztRFBBKTOM14}, 
 taint analysis algorithms have been formulated as IFDS problems.

### 2014-12-18 content/intro.tex
spacing

@@
 The popular \textit{Interprocedural Finite Distributive Subset} (IFDS) algorithm 
-by  Reps, Horwitz, and Sagiv \cite{reps1995precise} is a general data-flow analysis
+by  Reps, Horwitz, and Sagiv~\cite{reps1995precise} is a general data-flow analysis
 algorithm for computing solutions to standard finite distributive data-flow problems such 
@@
 depending on the type of the receiver expression at run time), then their dispatch 
-behaviours will be correlated. A recent paper \cite{DBLP:journals/scp/Tip15} identified
+behaviours will be correlated. A recent paper~\cite{DBLP:journals/scp/Tip15} identified
 this problem but did not present a concrete solution or algorithm, and we are not aware 

### 2014-12-18 content/example.tex
data-flow

@@
 shows how our technique can be used to improve the precision of taint analysis.
-A taint analysis is a specialized dataflow analysis for computing how string values
+A taint analysis is a specialized data-flow analysis for computing how string values
 may flow from ``sources'', which are typically statements that read untrusted input, 
@@
 
-Informally speaking, an IFDS-based dataflow analysis propagates dataflow facts along the edges
+Informally speaking, an IFDS-based data-flow analysis propagates data-flow facts along the edges
 of a control flow supergraph such as the one in Figure~\ref{fig:examplesupergraph}. The
@@
 presence of multiple calls to the same method. However, in this example all methods are
-called in exactly one place, so IFDS is unable to eliminate dataflow along any of the
+called in exactly one place, so IFDS is unable to eliminate data flow along any of the
 paths shown in the figure. As a result, IFDS-based taint analysis algorithms such as
@@
 are composed of edges in which the same receiver expression has different types
-are infeasible, and the propagation of dataflow facts along such paths is
+are infeasible, and the propagation of data-flow facts along such paths is
 prevented. Applying our technique to an IFDS-based taint analysis would enable
@@
 we would like to emphasize that our technique generally applies to \textit{any}
-dataflow analysis problem that can be expressed in the IFDS framework. This includes
+data-flow-analysis problem that can be expressed in the IFDS framework. This includes
 many common analysis tasks such as reaching definitions, constant propagation, slicing,

### 2014-12-20 content/example.tex
loc and classes to table
explanations; modifying table more

@@
 In the table, the number of all call sites in a program is denoted as $C$. 
-Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. 
+Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. The~number of classes~$T$ and the number of lines of code are shown in the last two columns.
 The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
-The last three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
+The next three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
 In this context, we deem a call site to be polymorphic if its statically computed call graph
@@
 
-\begin{table}
-\caption{Frequencies of correlated-call occurrences in the Dacapo benchmarks}\label{tab:dacapostat}
-\centering
-%\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lrrrr
->{\columncolor[HTML]{FFFFFF}}r 
->{\columncolor[HTML]{FFFFFF}}l r@{}}
-\toprule
-\textbf{Benchmark}  &
-  \multicolumn{1}{c}{\textbf{$|C|$}} & 
-  \multicolumn{1}{c}{\textbf{$|C_P|$}} & 
-  \multicolumn{1}{c}{\textbf{$|C^\Subset|$}} & 
-  \multicolumn{1}{c}{\textbf{$|\rcc|$}} & 
-  {\textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C_P|}{|C|}$\end{tabular}}} & 
-  {\textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C^\Subset|}{|C_P|}$\end{tabular}}} & 
-  \textbf{\begin{tabular}[c]{@{}l@{}}$\cfrac{|C^\Subset|}{|\rcc|}$\end{tabular}} \\ \midrule
-\textbf{antlr}      & 7,610                             & 428                                   & 299                              & 70                                   & {\textbf{6\%}}                                                      & {\textbf{70\%}}                                                     & 4                                                                \\
-\textbf{bloat}      & 18,157                            & 933                                   & 429                              & 119                                  & {\textbf{5\%}}                                                      & {\textbf{46\%}}                                                     & 4                                                                \\
-\textbf{chart}      & 18,101                            & 466                                   & 195                              & 61                                   & {\textbf{3\%}}                                                      & {\textbf{42\%}}                                                     & 3                                                                \\
-\textbf{eclipse}    & 3,222                             & 100                                   & 35                               & 10                                   & {\textbf{3\%}}                                                      & {\textbf{35\%}}                                                     & 4                                                                \\
-\textbf{fop}        & 4,831                             & 129                                   & 40                               & 12                                   & {\textbf{3\%}}                                                      & {\textbf{31\%}}                                                     & 3                                                                \\
-\textbf{hsqldb}     & 3,573                             & 81                                    & 35                               & 10                                   & {\textbf{2\%}}                                                      & {\textbf{43\%}}                                                     & 4                                                                \\
-\textbf{jython}     & 12,149                            & 487                                   & 129                              & 54                                   & {\textbf{4\%}}                                                      & {\textbf{26\%}}                                                     & 2                                                                \\
-\textbf{luindex}    & 7,190                             & 188                                   & 79                               & 29                                   & {\textbf{3\%}}                                                      & {\textbf{42\%}}                                                     & 3                                                                \\
-\textbf{lusearch}   & 9,043                             & 350                                   & 126                              & 47                                   & {\textbf{4\%}}                                                      & {\textbf{36\%}}                                                     & 3                                                                \\
-\textbf{pmd}        & 10,972                            & 219                                   & 68                               & 23                                   & {\textbf{2\%}}                                                      & {\textbf{31\%}}                                                     & 3                                                                \\
-\textbf{xalan}      & 3,889                             & 110                                   & 35                               & 10                                   & {\textbf{3\%}}                                                      & {\textbf{32\%}}                                                     & 4                                                                \\
-\textbf{Geom.
-mean} & \textbf{7,572}                    & \textbf{240}                          & \textbf{91}                      & \textbf{29}                          & {\textbf{3\%}}                                                      & {\textbf{38\%}}                                                     & \textbf{3}                                                       \\ \bottomrule
-\end{tabular}
-%}
-\end{table}
+\input{tables/stats}
 

### 2015-03-05 ecoop/content/appendix.tex
directories for conferences

--- 2014-12-18 content/appendix.tex
@@
 \begin{lemma}\label{lem:ccrectop}
-   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a dataflow fact such that there exists a realizable path $p\in\textsf{RP}(n,\,d)$. Let $T$ be the set of all types in the program.
+   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a data-flow fact such that there exists a realizable path $p\in\textsf{RP}(n,\,d)$. Let $T$ be the set of all types in the program.
    If there exists a receiver $r\in R$ such that
@@
 \begin{lemma}\label{lem:ccrectop}
-   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a dataflow fact such there exists a realizable path $p\in\textsf{RP}(n,\,d)$.
+   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a data-flow fact such there exists a realizable path $p\in\textsf{RP}(n,\,d)$.
    Then, if there exists a receiver $r\in R$, such that

### 2015-03-05 ecoop/content/impl.tex
directories for conferences

--- 2014-12-18 content/impl.tex
@@
 \]
-where $G^*=(N^*,\,E^*)$ is the control-flow supergraph of the program, $D$ is the set of dataflow facts, $F\subseteq2^D\to2^D$ is a set of distributive dataflow functions, and the function $$M_F:\,E^*\to(2^D\to2^D)$$ maps the supergraph edges to dataflow functions, and is extended to paths by composition.
+where $G^*=(N^*,\,E^*)$ is the control-flow supergraph of the program, $D$ is the set of data-flow facts, $F\subseteq2^D\to2^D$ is a set of distributive data-flow functions, and the function $$M_F:\,E^*\to(2^D\to2^D)$$ maps the supergraph edges to data-flow functions, and is extended to paths by composition.
 
@@
 where $G^*$ and $D$ are defined in the same way as for IFDS.
-$L$ is a finite-height lattice that represents the values to which dataflow facts are mapped in an IDE problem.
-An environment $Env(D, L)$ maps dataflow facts to lattice elements.
+$L$ is a finite-height lattice that represents the values to which data-flow facts are mapped in an IDE problem.
+An environment $Env(D, L)$ maps data-flow facts to lattice elements.
 Finally, the map $$M_{\textsf{Env}}:\,E^*\to(\textsf{Env}(D, L)\to \textsf{Env}(D, L))$$ is a function from the control-flow-supergraph edges to environment transformers, extended to paths by composition.
@@
 During an actual execution, every receiver $r$ points to an object of some
-runtime type. Therefore, a data flow fact
+runtime type. Therefore, a data-flow fact
 is unreachable along any feasible path if its corresponding lattice element
@@
 On a ``diagonal'' edge from $\mathbf0$ to a non-$\mathbf0$ fact that corresponds
-to some data flow fact becoming reachable, $\varepsilon_S(e)$ is applied to the initial
+to some data-flow fact becoming reachable, $\varepsilon_S(e)$ is applied to the initial
 map $\botcc$ that conservatively allows every receiver to point to an object of any type.
@@
 The composition of these micro functions results in the empty set as the possible
-types of the receiver \code{a}, indicating that this data flow path that would
+types of the receiver \code{a}, indicating that this data-flow path that would
 result in an information leak is actually infeasible.
@@
 In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
-to the empty set of possible types means that the corresponding data flow path is
+to the empty set of possible types means that the corresponding data-flow path is
 infeasible. Therefore, a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is

### 2015-03-05 ecoop/content/intro.tex
directories for conferences

--- 2014-12-18 content/intro.tex
@@
 \cite{sagiv1996precise} that similarly only considers properly matched call/return
-edges, but that supports a broader range of dataflow problems by expanding the 
+edges, but that supports a broader range of data-flow problems by expanding the 
 domain of flow functions to \textit{environments} that go beyond the data-flow facts 
@@
 
-This paper presents an approach to dataflow analysis that avoids a type
+This paper presents an approach to data-flow analysis that avoids a type
 of infeasible path that arises in object-oriented programs when two or more
@@
 this problem but did not present a concrete solution or algorithm, and we are not aware 
-of any existing dataflow analysis that is capable of avoiding infeasible paths that arise 
+of any existing data-flow analysis that is capable of avoiding infeasible paths that arise 
 in the presence of correlated method calls.
@@
 IDE problem that precisely accounts for infeasible paths due to correlated calls. 
-The results of this IDE problem can be mapped back to the dataflow domain of the 
+The results of this IDE problem can be mapped back to the data-flow domain of the 
 original IFDS problem.

### 2015-03-05 ecoop/figures/fig-examplesupergraph.tex
directories for conferences

--- 2014-12-12 figures/fig-examplesupergraph.tex
@@
 
-%inter-procedural edges
+%interprocedural edges
   \path[->,dashed,ultra thick] (call_foo) edge[out=20,in=190] (st_a_foo);
@@
     \node [description] (inter_arrow_right) [below = .5*\dist of intra_arrow_right] {};
-    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intra-procedural edge} (intra_arrow_right);
-    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{inter-procedural edge} (inter_arrow_right); 
+    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intraprocedural edge} (intra_arrow_right);
+    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{interprocedural edge} (inter_arrow_right); 
 }

### 2015-03-05 oopsla/content/abstract.tex
directories for conferences

--- 2014-12-18 content/abstract.tex
@@
     the receiver object), a program's interprocedural control flow graph
-    will contain infeasible paths. Existing algorithms for dataflow analysis 
+    will contain infeasible paths. Existing algorithms for data-flow analysis 
     are unable to ignore such infeasible paths, giving rise to loss of precision.
@@
 	Environment} (IDE) problem, in which edge functions are designed in a
-	way that enables us to ignore dataflow along infeasible paths. A solution
+	way that enables us to ignore data flow along infeasible paths. A solution
 	to this IDE problem can be mapped back to the solution space of the original

### 2015-03-05 oopsla/content/related.tex
directories for conferences

--- 2014-12-15 content/related.tex
@@
 SSA form is a representation of the program in which each variable has only one definition (assignment).
-SSA can make dataflow analysis simpler and more efficient~\cite{appel1998ssa}.
+SSA can make data-flow analysis simpler and more efficient~\cite{appel1998ssa}.
 }
@@
 Sridharan et~al.'s improvements to the precision of pointer analysis
-for JavaScript programs~\cite{DBLP:conf/ecoop/SridharanDCST12} also
+for Ja\-va\-Script programs~\cite{DBLP:conf/ecoop/SridharanDCST12} also
 eliminate infeasible paths. However, instead of infeasible paths

### 2015-03-05 oopsla/figures/fig-cc_edge_fn_example.tex
directories for conferences

--- 2014-12-16 figures/fig-cc_edge_fn_example.tex
@@
     \path[->, ultra thick](st_a_foo_z) edge (return_secret_z); 
-    \path[->](return_secret_z) edge node[arrowtext,near start,above right=0.4cm and -.15cm,rotate=-60]{$\lambda m.\botcc$} (end_a_foo_z); 
+    \path[->](return_secret_z) edge node[arrowtext,near start,above right=0.4cm and -.1cm,rotate=-60]{$\lambda m.\botcc$} (end_a_foo_z); 
     \path[->,dashed, ultra thick](call_foo_z) edge [out=38,in=238]  (st_a_foo_z);
     \path[->,dashed](end_a_foo_z) edge [out=200,in=43] (return_foo_z);
-    \path[->,dashed, ultra thick](end_a_foo_p) edge  [out=200,in=43] node[arrowtext,below,rotate=30]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (return_foo_v);
+    \path[->,dashed, ultra thick](end_a_foo_p) edge  [out=200,in=43,] node[arrowtext,rotate=28,below=.1cm]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (return_foo_v);
     \path[->](st_a_foo_p) edge (return_secret_p); 
@@
     \path[->](st_a_bar_s) edge (end_a_bar_s);
-    \path[->,dashed](call_bar_v) edge [out=20,in=230] node[arrowtext,near end,above left=-.1cm and -.15cm,rotate=36]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (st_a_bar_s);
+    \path[->,dashed](call_bar_v) edge [out=20,in=230] node[arrowtext,near end,above left=-.1cm and -.15cm,rotate=34]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (st_a_bar_s);
 
@@
 All non-labeled edges are implicitly labeled with identity functions $\id$.
-The variable $\psi$ denotes the return value of the \texttt{A.foo} method.}%
+The variable $r$ denotes the return value of the \texttt{A.foo} method.}%
   \label{fig:cc_edgefn_example}%  

### 2015-03-05 oopsla/code/collectionsExample.scala

@@ -1,0 +1,2 @@
+val result = new Array[B](this.size)
+this.copyToArray(result, 0)

### 2015-03-05 oopsla/code/constprop.java

@@ -1,0 +1,4 @@
+int u = 1;
+int v = u + 2;
+int w = u + v;
+u = 5;

### 2015-03-05 oopsla/code/interprocRec.java

@@ -1,0 +1,32 @@
+  class A {
+   
+    String string; 
+  
+    public static void main(String[] args) {
+      A a = args == null ? new A() : new B();
+      a.setString();
+      propagate(a);
+    }  
+     
+    static void propagate(A a) {
+      a.printString();
+    }
+    
+    void setString() {
+      string = secret();
+    }
+    
+    void printString() {
+      System.out.println("not secret");
+    }
+  }
+  
+  class B extends A {
+    void setString() {
+      string = "not secret";
+    }
+    
+    void printString() {
+      System.out.println(a);
+    }
+  }

### 2015-03-05 ecoop/code/TraversableOnce.scala
rename folders

@@ -1,45 +1,0 @@
-trait GenTraversableOnce[+A] extends Any {
-  ...
-  def isTraversableAgain: Boolean
-  ...
-}
-
-trait TraversableOnce[+A] extends Any with GenTraversableOnce[A] {
-  ...
-  def size: Int = {
-    var result = 0
-    for (x <- self) result += 1
-    result
-  }
-  ...
-  def toArray[B >: A : ClassTag]: Array[B] = {
-    if (this.isTraversableAgain) {
-      val result = new Array[B](this.size)
-      this.copyToArray(result, 0)
-      result
-    }
-    else this.toBuffer.toArray
-  }
-  ...
-}
-
-trait Iterator[+A] extends TraversableOnce[A] {
-  ...
-  def isTraversableAgain = false
-  ...
-}
-
-/** A template trait for traversable collections of type `Traversable[A]`.
-    ...
- */
-trait TraversableLike[+A, +Repr] extends Any
-                                    with HasNewBuilder[A, Repr]
-                                    with FilterMonadic[A, Repr]
-                                    with TraversableOnce[A]
-                                    with GenTraversableLike[A, Repr]
-                                    with Parallelizable[A, ParIterable[A]]
-{
-  ...
-  final def isTraversableAgain: Boolean = true
-  ...
-}

### 2015-03-05 ecoop/code/assertions.java

@@ -1,16 +1,0 @@
-  public static void main(String[] args) {
-    String n = "not secret";
-    notSecret(n);  // assert that n is not secret
-    String s1 = f(n);
-    isSecret(s1);
-    String s2 = f(secret());
-  }
-
-  static String f(String str) {
-    isSecret(str);
-    return str;
-  }
-  
-  public static String secret() {  // the secret source
-    return "secret";
-  }

### 2015-03-05 ecoop/code/ccexample.java

@@ -1,16 +1,0 @@
-class A {
-  String foo { return secret(); } /*@\label{line:Afoo}@*/
-  void bar(String s) {} /*@\label{line:Abar}@*/
-}
-class B extends A {
-  String foo { return "not secret"; } /*@\label{line:Bfoo}@*/
-  void bar(String s) { System.out.println(s); } /*@\label{line:Bbar}@*/
-}
-
-class Main {
-  public static void main(String[] args) {
-    A a = (args == null) ? new A() : new B(); /*@\label{line:createObject}@*/
-    String v = a.foo(); /*@\label{line:callfoo}@*/
-    a.bar(v); /*@\label{line:callbar}@*/
-  }
-}

### 2015-03-05 ecoop/code/constprop.java

@@ -1,4 +1,0 @@
-int u = 1;
-int v = u + 2;
-int w = u + v;
-u = 5;

### 2015-03-05 ecoop/code/correct.java

@@ -1,4 +1,0 @@
-  int a = 1;
-  int b = a;
-  int c = a + b;
-  int d = a + 2;

### 2015-03-05 ecoop/code/examplesupergraph.java

@@ -1,20 +1,0 @@
-class Main {
-  public static void main(String[] args) {
-    String a = secret();
-    String b = A.f(a);
-  }
-
-  static String secret() {
-    return "secret";
-  }
-}
-
-class A {  
-  static String f(String s) {
-    if (s == null) {
-     String r = f("not secret");
-     return r;    
-    }
-    return s;
-  }
-}

### 2015-03-05 ecoop/code/interprocRec.java

@@ -1,32 +1,0 @@
-  class A {
-   
-    String string; 
-  
-    public static void main(String[] args) {
-      A a = args == null ? new A() : new B();
-      a.setString();
-      propagate(a);
-    }  
-     
-    static void propagate(A a) {
-      a.printString();
-    }
-    
-    void setString() {
-      string = secret();
-    }
-    
-    void printString() {
-      System.out.println("not secret");
-    }
-  }
-  
-  class B extends A {
-    void setString() {
-      string = "not secret";
-    }
-    
-    void printString() {
-      System.out.println(a);
-    }
-  }

### 2015-03-05 oopsla/code/collectionsExample.scala

@@ -1,2 +1,0 @@
-val result = new Array[B](this.size)
-this.copyToArray(result, 0)

### 2015-03-05 oopsla/code/isTraversable.scala

@@ -1,1 +1,0 @@
-if(this.isTraversableAgain) ...

### 2015-03-05 oopsla2015/content/background.tex
rename folders

--- 2014-12-18 content/background.tex
@@
 This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.}
-The IFDS framework is applicable to \textit{interprocedural} data flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
+The IFDS framework is applicable to \textit{interprocedural} data-flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
 and whose data-flow functions are \textit{distributive}.
@@
 $D$ is a finite set of \textit{data-flow facts},
-$F$ is a set of distributive dataflow functions of type $2^D\to2^D$,
-$M_F:\,E^*\to F$ assigns a dataflow function to each supergraph edge,
+$F$ is a set of distributive data-flow functions of type $2^D\to2^D$,
+$M_F:\,E^*\to F$ assigns a data-flow function to each supergraph edge,
 and $\sqcap$ is the \textit{meet operator} on the powerset $2^D$, either union or intersection.
@@
 \commentout{
-is a function that maps supergraph edges to dataflow functions, and $M_F$ is extended to paths by composition\footnote{%
+is a function that maps supergraph edges to data-flow functions, and $M_F$ is extended to paths by composition\footnote{%
   Let $A$ be a set and $f:\,E^*\to(A\to A)$ a function from supergraph edges to functions on $A$.
@@
 with edges from one instance of $D \cup \{0\}$ to another instance of $D \cup \{0\}$.
-The IFDS algorithm uses such graphs to efficiently represent both the input dataflow functions
+The IFDS algorithm uses such graphs to efficiently represent both the input data-flow functions
 and the summary functions that it computes for called procedures.
@@
 \commentout{
-Note that $R_f$ constructs pairs of dataflow facts so that
+Note that $R_f$ constructs pairs of data-flow facts so that
 \begin{itemize}
@@
   %The representation relation $R_f$ for a set of data-flow facts 
-  %and dataflow function $f=\lambda S\,.\,S\setminus\{v\}\cup\{u\}$ looks as follows:
+  %and data-flow function $f=\lambda S\,.\,S\setminus\{v\}\cup\{u\}$ looks as follows:
   $
@@
 functions $f$ and $f'$ corresponds to finding reachable nodes in a graph composed from their representation
-relations $R_f$ and $R_{f'}$. Therefore, evaluating the composed dataflow function for a control
+relations $R_f$ and $R_{f'}$. Therefore, evaluating the composed data-flow function for a control
 flow path corresponds to finding reachable nodes in a graph composed from the representation relations
-of the dataflow functions for individual instructions.
+of the data-flow functions for individual instructions.
 
@@
 For each edge $(n \to n') \in E^*$, the exploded supergraph contains a set of edges
-$(n,d_i) \to (n',d_j)$, which form the representation relation of the dataflow function
+$(n,d_i) \to (n',d_j)$, which form the representation relation of the data-flow function
 $M_F(n \to n')$. The IFDS algorithm finds all exploded supergraph edges that are reachable by
@@
 A practical implementation of the IFDS algorithm generally takes as input a representation of the
-exploded supergraph edges $E^\sharp$ instead of explicit dataflow functions $M_F$. This is convenient because
+exploded supergraph edges $E^\sharp$ instead of explicit data-flow functions $M_F$. This is convenient because
 the two are equivalent in expressiveness, and because the IFDS algorithm works internally with the exploded
 supergraph. More specifically, the input generally provides a function
-$f: N^* \times D \times N^* \to 2^D$. Given a (non-exploded) supergraph edge $n \to n'$ and a dataflow fact $d$,
+$f: N^* \times D \times N^* \to 2^D$. Given a (non-exploded) supergraph edge $n \to n'$ and a data-flow fact $d$,
 $f(n,d,n')$ returns the set of all $d'$ such that the exploded supergraph contains the edge $(n,d) \to (n',d')$.
@@
 \textit{interprocedural} \textit{distributive} \textit{environment}
-problems. An \textit{environment} problem is an analysis whose dataflow
+problems. An \textit{environment} problem is an analysis whose data-flow
 lattice is the lattice $\textsf{Env}(D,L)$ of maps from a finite set $D$ to a meet semilattice
-$L$ of finite height, ordered pointwise. Like IFDS, IDE requires the dataflow functions to be distributive.
+$L$ of finite height, ordered pointwise. Like IFDS, IDE requires the data-flow functions to be distributive.
 
@@
 $L$ is a meet semilattice of finite height,
-and $M_\textsf{Env}:\,E^*\to(\textsf{Env}(D,\,L)\to \textsf{Env}(D,\,L))$ assigns a dataflow function
+and $M_\textsf{Env}:\,E^*\to(\textsf{Env}(D,\,L)\to \textsf{Env}(D,\,L))$ assigns a data-flow function
 to each supergraph edge.
@@
 In order to do this efficiently, the IDE algorithm requires a representation of micro-functions
-that is general enough to express the basic micro-functions of the dataflow functions for individual
+that is general enough to express the basic micro-functions of the data-flow functions for individual
 instructions, and that supports computing the meet and composition of micro-functions.
@@
 A practical implementation of the IDE algorithm requires
-the input dataflow functions to be provided in their pointwise representation
+the input data-flow functions to be provided in their pointwise representation
 as exploded supergraph edges labelled with micro-functions.

### 2015-03-05 oopsla2015/code/ccexample.java

@@ -1,0 +1,16 @@
+class A {
+  String foo { return secret(); } /*@\label{line:Afoo}@*/
+  void bar(String s) {} /*@\label{line:Abar}@*/
+}
+class B extends A {
+  String foo { return "not secret"; } /*@\label{line:Bfoo}@*/
+  void bar(String s) { System.out.println(s); } /*@\label{line:Bbar}@*/
+}
+
+class Main {
+  public static void main(String[] args) {
+    A a = (args == null) ? new A() : new B(); /*@\label{line:createObject}@*/
+    String v = a.foo(); /*@\label{line:callfoo}@*/
+    a.bar(v); /*@\label{line:callbar}@*/
+  }
+}

### 2015-03-05 oopsla2015/code/examplesupergraph.java

@@ -1,0 +1,20 @@
+class Main {
+  public static void main(String[] args) {
+    String a = secret();
+    String b = A.f(a);
+  }
+
+  static String secret() {
+    return "secret";
+  }
+}
+
+class A {  
+  static String f(String s) {
+    if (s == null) {
+     String r = f("not secret");
+     return r;    
+    }
+    return s;
+  }
+}

### 2015-03-05 ecoop2014/reviews/response.txt
reviews

esponse by Marianna Rapoport <mrapoport@uwaterloo.ca>
   Paper #25: Precise Data Flow Analysis in the Presence of Correlated
              Method Calls
---------------------------------------------------------------------------
Reviewers C and D correctly point out that our primary contributions are
theoretical: the transformation of an IFDS problem to an IDE problem
that provides more precise results for the original IFDS problem, and
the proofs that the result of this approach is both sound and fully
eliminates flow along infeasible paths due to correlated calls.

Reviewers B and C ask about object sensitivity. Object-sensitive
points-to analysis is orthogonal to our work because it analyzes the
flow of data (pointers), while we analyze control flow paths instead.
Also, object-sensitive points-to analysis is flow-insensitive, while
IFDS/IDE are flow-sensitive, and our transformation only makes sense
in a flow-sensitive setting (since a flow-insensitive analysis already
introduces many more infeasible control flow paths).

It would be possible to simulate the effect of our correlated calls
transformation in the following way inspired by object-sensitive
points-to analysis: we could re-analyze each method in a number
of contexts. There would be a separate context for every possible
assignment of concrete types to all of the pointers in the method that
are used as receivers at a call site. The number of such contexts for
each method would be O(R^T), where R is the number of receiver pointers
in the method and T is the number of possible concrete types that could
be assigned to a receiver pointer. Our approach computes equally precise
analysis results but avoids this exponential cost.

Reviewer C says it would be of interest to know how many calls share the
same base variable on average. The average number of polymorphic calls per
receiver is included in Table 1, and is equal to 3. The frequency of
 situations where more than two polymorphic calls are invoked on the same
receiver, compared to all calls in the program, is reflected by the number
of correlated calls over polymorphic calls, which is 39%, and number of
polymorphic calls over all calls, which is 3%.

Reviewer B asks about the inclusion of our IDE implementation in WALA.
We have been in discussion about this with the key WALA developers since
the summer, and we have already begun the process of contributing our
IDE implementation (and correlated calls transformation) to WALA so that
it will be available to all WALA users.

We agree with reviewer D that the asymptotic complexity is O(ED^3RT) and will present it more explicitly in the final version.

Reviewer A asks why we do not just use IDE directly. The IFDS and
IDE algorithms solve two distinct classes of problems. Our approach
is aimed at IFDS problems rather than IDE problems. Given an IFDS
problem, our approach results in an IFDS solution that is more precise
than if the same IFDS problem had been solved directly with the IFDS
algorithm. As future work, we could look at adapting our approach to IDE
problems: we could take an initial IDE problem, convert it to a larger
and more complex IDE problem, so that the solution of the larger IDE
problem generates a more precise solution to the original IDE problem by
removing infeasible paths due to correlated calls.

### 2015-03-05 ecoop2014/reviews/response.txt
fixing reviews

@@
-esponse by Marianna Rapoport <mrapoport@uwaterloo.ca>
+===========================================================================
+          Response by Marianna Rapoport <mrapoport@uwaterloo.ca>
    Paper #25: Precise Data Flow Analysis in the Presence of Correlated

### 2015-03-07 sas2015/content/concl.tex
directory for sas

--- 2014-12-17 content/concl.tex
@@
 
-Previous algorithms for dataflow analysis are unable to avoid propagating
-dataflow facts along infeasible paths that arise in the presence of
+Previous algorithms for data-flow analysis are unable to avoid propagating
+data-flow facts along infeasible paths that arise in the presence of
 correlated polymorphic method calls. 

### 2015-03-07 sas2015/code/TraversableOnce.scala

@@ -1,0 +1,45 @@
+trait GenTraversableOnce[+A] extends Any {
+  ...
+  def isTraversableAgain: Boolean
+  ...
+}
+
+trait TraversableOnce[+A] extends Any with GenTraversableOnce[A] {
+  ...
+  def size: Int = {
+    var result = 0
+    for (x <- self) result += 1
+    result
+  }
+  ...
+  def toArray[B >: A : ClassTag]: Array[B] = {
+    if (this.isTraversableAgain) {
+      val result = new Array[B](this.size)
+      this.copyToArray(result, 0)
+      result
+    }
+    else this.toBuffer.toArray
+  }
+  ...
+}
+
+trait Iterator[+A] extends TraversableOnce[A] {
+  ...
+  def isTraversableAgain = false
+  ...
+}
+
+/** A template trait for traversable collections of type `Traversable[A]`.
+    ...
+ */
+trait TraversableLike[+A, +Repr] extends Any
+                                    with HasNewBuilder[A, Repr]
+                                    with FilterMonadic[A, Repr]
+                                    with TraversableOnce[A]
+                                    with GenTraversableLike[A, Repr]
+                                    with Parallelizable[A, ParIterable[A]]
+{
+  ...
+  final def isTraversableAgain: Boolean = true
+  ...
+}

### 2015-03-07 sas2015/code/assertions.java

@@ -1,0 +1,16 @@
+  public static void main(String[] args) {
+    String n = "not secret";
+    notSecret(n);  // assert that n is not secret
+    String s1 = f(n);
+    isSecret(s1);
+    String s2 = f(secret());
+  }
+
+  static String f(String str) {
+    isSecret(str);
+    return str;
+  }
+  
+  public static String secret() {  // the secret source
+    return "secret";
+  }

### 2015-03-07 sas2015/code/isTraversable.scala

@@ -1,0 +1,1 @@
+if(this.isTraversableAgain) ...

### 2015-03-08 sas2015/content/impl.tex
address reviewer concerns about presentation of efficiency

--- 2015-03-05 ecoop/content/impl.tex
@@
 of the set of facts.
-The complexity proof for the IDE algorithm requires the implementation of the micro-functions
+The IDE algorithm may evaluate micro-functions up to $O(ED^3)$ times,
+so this running time must be multiplied by the cost of evaluating a
+micro-function. We show that the micro-functions in the correlated-calls
+IDE analysis can be evaluated in time $O(\rcc T)$, where $\rcc$ is the number
+of correlated-call receivers $\rcc$ and the $T$ is the number of run-time
+types. Therefore, the overall worst-case cost of the correlated-calls IDE analysis
+is $O(ED^3\rcc T)$.
+
+Specifically, the complexity proof for the IDE algorithm requires the implementation of the micro-functions
 to be \textit{efficient} according to the following criteria:
@@
   \item The micro functions form a finite-height lattice.
-  \item The apply, meet, composition, and equality-check operations can be computed in constant time.
+  \item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
   \item There is a constant bound on the storage space for a micro function representation.
 \end{enumerate}
-We prove that the micro-functions for the correlated-call analysis satisfy these
-criteria if we consider the number of correlated-call receivers $R$ and the
-number of run-time types $T$ constant
-(i.e., the operations on micro-functions are allowed to use time that is $O(RT)$,
-but constant with respect to $E$ and $D$).
-
+We prove these conditions with the following lemma:
 \begin{restatable}{lemma}{efficient}\label{lem:efficient}
-  The correlated-call representation of a micro function is efficient if the number of
-  correlated-call receivers $\rcc$ and the number of run-time types $T$ are considered constant.
+  The correlated-call representation of a micro function is efficient and the required operations
+  on micro-functions can be computed in time $O(\rcc T)$.
 \end{restatable}
 
-From this lemma, we conclude that the correlated-calls analysis runs in time
-$O(ED^3\rcc T)$. In other words, the asymptotic cost of the added precision of
-the correlated-calls analysis is increased by a factor of $O(\rcc T)$ compared
-to the original IFDS analysis.
+%From this lemma, we conclude that the correlated-calls analysis runs in time
+%$O(ED^3\rcc T)$. In other words, the asymptotic cost of the added precision of
+%the correlated-calls analysis is increased by a factor of $O(\rcc T)$ compared
+%to the original IFDS analysis.
 

### 2015-03-08 sas2015/content/related.tex
expand related work to discuss object sensitivity and context sensitivity

--- 2015-03-05 oopsla/content/related.tex
@@
 }
+
+Our approach superficially resembles, but is orthogonal, to context
+sensitivity, including such variations as object sensitivity~\cite{DBLP:conf/issta/MilanovaRR02,DBLP:journals/tosem/MilanovaRR05}.
+Context-sensitive
+points-to analysis is orthogonal to our work because it analyzes the
+flow of data (pointers), while we analyze control flow paths instead.
+Also, object-sensitive points-to analysis is flow-insensitive, while
+the IFDS and IDE algorithms are flow-sensitive, and our transformation only makes sense
+in a flow-sensitive setting (since a flow-insensitive analysis already
+introduces many more infeasible control flow paths).
+
+It would be possible to simulate the effect of our correlated calls
+transformation in the following way inspired by context-sensitivity:
+we could re-analyze each method in a number
+of contexts. There would be a separate context for every possible
+assignment of concrete types to all of the pointers in the method that
+are used as receivers at a call site. The number of such contexts for
+each method would be $O(R^T)$, where $R$ is the number of receiver pointers
+in the method and $T$ is the number of possible concrete types that could
+be assigned to a receiver pointer. Our approach computes equally precise
+analysis results but avoids this exponential cost.

### 2015-03-08 sas2015/content/concl.tex
add future work of adapting to IDE input problems

@@
 artifact evaluation committee.
+
+As future work, it is possible to adapt our approach to work on IDE
+problems in addition to IFDS problems. We would take an initial IDE
+problem, convert it to a larger and more complex IDE problem, such
+that the solution of the larger IDE problem generates a more precise
+solution to the original IDE problem by removing infeasible paths due to
+correlated calls.

### 2015-03-08 sas2015/content/abstract.tex
minor tweaks

--- 2015-03-05 oopsla/content/abstract.tex
@@
 	transform an IFDS problem into an \textit{Interprocedural Distributive 
-	Environment} (IDE) problem, in which edge functions are designed in a
-	way that enables us to ignore data flow along infeasible paths. A solution
+	Environment} (IDE) problem, in which edge functions ``filter out'' data flow 
+	along infeasible paths. A solution
 	to this IDE problem can be mapped back to the solution space of the original

### 2015-03-08 sas2015/content/background.tex
minor tweaks

--- 2015-03-05 oopsla2015/content/background.tex
@@
 %\begin{mdelete}\mtodo{We already say (but less precisely) what a CFG is in the introduction.}
-The \textit{control-flow graph} of a procedure is a directed graph whose nodes are instructions, and which contains an edge from $n_1$ to $n_2$ whenever
+The \textit{control-flow graph} of a procedure is a directed graph whose nodes are instructions, which contains an edge from $n_1$ to $n_2$ whenever
 $n_2$ may execute immediately after $n_1$. A CFG has a distinguished \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$.
@@
 
-A path through the control-flow supergraph is \textit{valid} if it follows the usual stack-based calling 
+A path in the control-flow supergraph is \textit{valid} if it follows the usual stack-based calling 
 discipline: every end-to-return edge on the path returns
@@
 is a partially ordered set $(S,\sqsubseteq)$ in which every subset has a least upper bound, called \textit{join} or $\sqcup$, and a greatest lower bound, called \textit{meet} or $\sqcap$.
-A \textit{meet semilattice} is a partially ordered set in which every subset need only have a greatest lower bound.
+A \textit{meet semilattice} is a partially ordered set in which every subset only has a greatest lower bound.
 The symbols $\bot$ and $\top$ are used to denote the greatest lower bound of $S$ and of the empty set, respectively.
@@
 Context-sensitivity, however, allows an analysis to compute the data-flow result for a given procedure as a \textit{function} of the data-flow value at the start of the procedure.
-In other words, the analysis result for a procedure varies depending on where the procedure was called from.
+The analysis result for a procedure varies depending on where the procedure was called from.
 This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.}
@@
     R_f=\{(\mathbf0,\,\mathbf0),\,(\mathbf0,\,u),\,(w,\,w)\}
-$, which can be visualized with the following graph:
+$, which is depicted by the following graph:
    \begin{center}
@@
   We can see that there is a realizable path, highlighted in bold,
-  from the start node of the exploded graph to the variable \verb's' at~the~node~$\textsf{print(s)}$ in the \verb'B.bar' method. This means that at that node, \verb's' is considered secret.
+  from the start node of the exploded graph to the variable \verb's' at~the~node~$\textsf{print(s)}$ in the \verb'B.bar' method. This means that \verb's' is considered secret at that node.
 
@@
 The composition of two environment transformers can be computed by combining their pointwise
-representation graphs in the same way as IFDS representation relations, and 
+representation graphs in the same fashion as IFDS representation relations, and 
 computing the composition of the micro-functions appearing along each path in the resulting graph.

### 2015-03-08 sas2015/content/example.tex
minor tweaks

--- 2014-12-20 content/example.tex
@@
 In this section, we illustrate our approach using a small motivating example that
-shows how our technique can be used to improve the precision of taint analysis.
+shows how our technique improves the precision of taint analysis.
 A taint analysis is a specialized data-flow analysis for computing how string values
@@
 Figure~\ref{list:ccexample} shows a small Java program that we will use to illustrate
-how our technique can improve the precision of a simple taint analysis. The program
+how our technique improves the precision of a simple taint analysis. The program
 declares a class \code{A} with a subclass \code{B},  where \code{A} defines methods 
@@
 
-Informally speaking, an IFDS-based data-flow analysis propagates data-flow facts along the edges
+An IFDS-based data-flow analysis propagates data-flow facts along the edges
 of a control flow supergraph such as the one in Figure~\ref{fig:examplesupergraph}. The
@@
 in light of correlated calls.
-Informally speaking, our approach associates with each edge in an
+Our approach associates with each edge in an
 interprocedural CFG a function that records the types of 
@@
 %\otodo{We don't have an explanation.}
-Out of these polymorphic call sites, a significant fraction (38\%) are correlated 
+Out of these polymorphic call sites, a significant fraction (39\%) are correlated 
 call sites $C^\Subset$. We also see that, on average,  each correlated-call receiver is involved in three correlated calls.

### 2015-03-08 sas2015/content/intro.tex
minor tweaks

--- 2015-03-05 ecoop/content/intro.tex
@@
 of any existing data-flow analysis that is capable of avoiding infeasible paths that arise 
-in the presence of correlated method calls.
+in the presence of correlated method calls (see Section~\ref{sec:Related} for a discussion
+of related work).
 

### 2015-03-08 sas2015/content/example.tex
minor edits of Frank's minor edits

@@
 of a control flow supergraph such as the one in Figure~\ref{fig:examplesupergraph}. The
-IFDS algorithm was carefully designed to avoid infeasible paths that may arise in the
-presence of multiple calls to the same method. However, in this example all methods are
+IFDS algorithm already avoids flow along infeasible paths from one call site, through a target method,
+and returning to a different call site of the target method.
+However, in this example all methods are
 called in exactly one place, so IFDS is unable to eliminate data flow along any of the

### 2015-03-08 sas2015/content/appendix.tex
address reviewer concerns about presentation of efficiency
move TraversableOnce code to appendix

--- 2015-03-05 ecoop/content/appendix.tex
@@
-\section*{Appendix}
+\section{TraversableOnce Trait from Scala Standard Library}
+
+\begin{figure}
+\inputMinted{scala}{TraversableOnce.scala}
+\caption{Relevant code from \textsf{TraversableOnce} and related traits.}
+\label{fig:traversableonce}
+\end{figure}
+
+\section{Proofs}
 In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}.
@@
     \item All operations can be computed in $O(\rcc\times T)$ time.
-Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
+%Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
     \item The space bound is $O(\rcc\times T)$.\qedhere

### 2015-03-08 sas2015/content/example.tex
move TraversableOnce code to appendix

@@
 The relevant code from \textsf{TraversableOnce} and other related traits is shown
-in Figure~\ref{fig:traversableonce}.
-
-\begin{figure}
-\inputMinted{scala}{TraversableOnce.scala}
-\caption{Relevant code from \textsf{TraversableOnce} and related traits.}
-\label{fig:traversableonce}
-\end{figure}
+in Figure~\ref{fig:traversableonce} in the appendix.

### 2015-03-08 sas2015/content/intro.tex
removed fig 1

@@
 
-\input{figures/fig-transformation}
+%\input{figures/fig-transformation}
 
@@
 We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
-This is illustrated schematically
-in Figure~\ref{fig:transformations}%
-\footnote{ 
-  The labels %$\resultIDE$, $\resultIFDS$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$
-  on edges in 
-  Figure~\ref{fig:transformations} reflect a number of mappings and projections 
-  that will be defined in Section~\ref{sec:cca} and that can be ignored here.
-}.
+%This is illustrated schematically
+%in Figure~\ref{fig:transformations}%
+%\footnote{ 
+%  The labels %$\resultIDE$, $\resultIFDS$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$
+%  on edges in 
+%  Figure~\ref{fig:transformations} reflect a number of mappings and %projections 
+%  that will be defined in Section~\ref{sec:cca} and that can be %ignored here.
+%}.
 

### 2015-03-08 sas2015/content/background.tex
moving and resizing figures

@@
 \]
-%Each pair $(d_i,\,d_j)\in R_f$ corresponds to an edge $((n_1,\,d_i),\,(n_2,\,d_j))$ in the exploded supergraph.
-
-\commentout{
-Note that $R_f$ constructs pairs of data-flow facts so that
-\begin{itemize}
-  \item there is always an edge $(\mathbf0,\,\mathbf0)$ corresponding to the CFG edge;
-  \item if there is an edge $(\mathbf0,\,d_j)$, then there is no other edge leading to $d_j$; in particular, there is never an edge $(d_i,\,\mathbf0)$ where $d_i\ne\mathbf0$.
-\end{itemize}
-}
-
+\begin{floatingfigure}[lrp]{3.5cm}
+\input{figures/ex1minigraph} 
+\end{floatingfigure}
 \begin{example}\label{ex:flowfun}
 Given $D=\{u,\,v,\,w\}$ and $f(S) = S\setminus\{v\} \cup \{u\}$,
-    the representation relation 
-  %The representation relation $R_f$ for a set of data-flow facts 
-  %and data-flow function $f=\lambda S\,.\,S\setminus\{v\}\cup\{u\}$ looks as follows:
+    the representation
+ relation 
   $
     R_f=\{(\mathbf0,\,\mathbf0),\,(\mathbf0,\,u),\,(w,\,w)\}
-$, which is depicted by the following graph:
-   \begin{center}
-    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
-\begin{tikzpicture}[>=stealth,on grid, auto]
-    \node [n,label=$\mathbf{0}$] (zero){};
-    \node [n,] (zero_) [below=\edge of zero] {};
-    \node [n,label=$u$] (u) [right=\nd of zero] {};
-    \node [n,] (u_) [below=\edge of u] {};
-    \node [n,label=$v$] (v) [right=\nd of u] {};
-    \node [n,] (v_) [below=\edge of v] {};
-    \node [n,label=$w$] (w) [right=\nd of v] {};
-    \node [n,] (w_) [below=\edge of w] {};
-    \path[->](zero) edge (zero_);
-    \path[->](zero) edge (u_);
-    \path[->](w) edge (w_);
-  \end{tikzpicture}
-  \end{center}
+$, which is depicted on the graph below.
 \end{example}
@@
     $
-  as illustrated in the following graph:
-    \begin{center}
-    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
-\begin{tikzpicture}[>=stealth,on grid, auto]
-    \node [n,label=$\mathbf{0}$] (zero){};
-    \node [n] (zero_) [below=\edge of zero] {};
-    \node [n,label=$u$] (u) [right=\nd of zero] {};
-    \node [n] (u_) [below=\edge of u] {};
-    \node [n,label=$v$] (v) [right=\nd of u] {};
-    \node [n] (v_) [below=\edge of v] {};
-    \node [n,label=$w$] (w) [right=\nd of v] {};
-    \node [n] (w_) [below=\edge of w] {};
-    \node [n] (zero__) [below=\edge of zero_] {};
-    \node [n] (u__) [below=\edge of u_] {};
-    \node [n] (v__) [below=\edge of v_] {};
-    \node [n] (w__) [below=\edge of w_] {};
-
-    \path[->](zero) edge node[left] {$R_f$} (zero_);
-    \path[->](zero) edge (u_);
-    \path[->](w) edge (w_);
-    \path[->](zero_) edge node[left] {$R_g$} (zero__);
-    \path[->](u_) edge (u__);
-    \path[->](v_) edge (v__);
-
-    \node [n,label=$\mathbf{0}$] (zeroC) [below right= .5\edge and 3.5\dist of w] {};
-    \node [n] (zeroC_) [below=\edge of zeroC] {};
-    \node [n,label=$u$] (uC) [right=\nd of zeroC] {};
-    \node [n] (uC_) [below=\edge of uC] {};
-    \node [n,label=$v$] (vC) [right=\nd of uC] {};
-    \node [n] (vC_) [below=\edge of vC] {};
-    \node [n,label=$w$] (wC) [right=\nd of vC] {};
-    \node [n] (wC_) [below=\edge of wC] {};
-
-    \path[->](zeroC) edge node[left] {$R_g\circ R_f$} (zeroC_);
-    \path[->](zeroC) edge (uC_);
-  \end{tikzpicture}
-  \end{center}
+  as illustrated in the graphs below.
+\begin{floatingfigure}[lrp]{3.5cm}
+  \input{figures/ex2minigraph}
+\end{floatingfigure}
 \end{example}
@@
 
-\input{figures/fig-cc_edge_fn_example}
 %\mtodo{In Figure~\ref{fig:cc_edgefn_example}, should we say that $\psi$ corresponds to the function's return value?}

### 2015-03-08 sas2015/figures/fig-examplesupergraph.tex
moving and resizing figures

--- 2015-03-05 ecoop/figures/fig-examplesupergraph.tex
@@
 \begin{figure}
-  \centering
-
-  \begin{minipage}{\textwidth}
+  \begin{minipage}{.5\textwidth}
     \inputMinted{java}{ccexample.java}
+%    \vspace*{-4mm}
+    \caption{Example program containing\\ correlated calls}
+  \label{list:ccexample}
   \end{minipage}
-    \vspace*{-4mm}
-  \caption{Example program containing correlated calls}
-  \label{list:ccexample}
-
-   \begin{minipage}{\textwidth}
+   \begin{minipage}{.5\textwidth}
     \tikzstyle{supergraph}=[
@@
 
-\hspace*{-10pt}
+\hspace*{-20pt}
 \begin{tikzpicture}
@@
 %interprocedural edges
-  \path[->,dashed,ultra thick] (call_foo) edge[out=20,in=190] (st_a_foo);
+  \path[->,dashed,ultra thick] (call_foo) edge[out=-5,in=198] (st_a_foo);
   \path[->,dashed] (call_foo) edge[color=lightsalmonpink,out=-20,in=135] (st_b_foo);
@@
   \path[->,dashed,ultra thick] (end_a_foo) edge[out=220,in=15] (return_foo);
-  \path[->,dashed] (end_b_foo) edge[color=lightsalmonpink,out=160,in=-60] (return_foo);
+  \path[->,dashed] (end_b_foo) edge[color=lightsalmonpink,out=180,in=-50] (return_foo);
   \path[->,dashed] (end_a_bar) edge[out=210,in=40] (return_bar);
-  \path[->,dashed,ultra thick] (end_b_bar) edge[color=lightsalmonpink,out=200,in=-40] (return_bar);
+  \path[->,dashed,ultra thick] (end_b_bar) edge[color=lightsalmonpink,out=190,in=-40] (return_bar);
 
@@
     \node [description] (inter_arrow_right) [below = .5*\dist of intra_arrow_right] {};
-    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intraprocedural edge} (intra_arrow_right);
-    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{interprocedural edge} (inter_arrow_right); 
+
+%    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intraprocedural edge} (intra_arrow_right);
+%    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{interprocedural edge} (inter_arrow_right); 
 }
 \end{tikzpicture}
-   \end{minipage}
-   \vspace*{-25mm}
+\vspace*{-18mm}
   \caption{
     Control flow supergraph for the example program of Figure~\ref{list:ccexample}.
+    Dashed lines depict interprocedural edges.
     An infeasible path is shown in bold. 
@@
   \label{fig:examplesupergraph}%
+\end{minipage}
+
+\begin{minipage}{\textwidth}
+\input{figures/fig-cc_edge_fn_example}
+\end{minipage}
 \end{figure}

### 2015-03-08 sas2015/content/appendix.tex
moving code to appendix

@@
-\section{TraversableOnce Trait from Scala Standard Library}
-
-\begin{figure}
-\inputMinted{scala}{TraversableOnce.scala}
-\caption{Relevant code from \textsf{TraversableOnce} and related traits.}
-\label{fig:traversableonce}
-\end{figure}
-
-\section{Proofs}
-In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}.
+\section*{Appendix}
+In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca} and the code discussed in Section~\ref{sec:collex}.
 
@@
 \end{proof}
+
+\begin{figure}
+\inputMinted{scala}{TraversableOnce.scala}
+\caption{Relevant code from \textsf{TraversableOnce} and related traits.}
+\label{fig:traversableonce}
+\end{figure}

### 2015-03-08 sas2015/content/background.tex
moving code to appendix

@@
 %We denote the source and end nodes of a graph edge $e$ as $\src e$ and $\target e$.
-
-\commentout{
-\begin{example}
-  Consider the program in Listing~\ref{list:examplejava}. The supergraph corresponding to that program is shown in Figure~\ref{fig:examplesupergraph}.
-  %\otodo{Can we merge the examples from Figures 1 and 2 into a single example program?}
-%\otodo{I think we can remove the supergraph Figure 3.}
-\begin{figure}
-  \centering
-  \begin{minipage}{\textwidth}
-    \inputMinted{java}{examplesupergraph.java}
-  \end{minipage}
-  \caption{An example Java program}
-  \label{list:examplejava}
-\end{figure}
-
-  \begin{figure}%
-  \centering
-  \scalebox{.9}{
-      \tikzset{
-        ashadow/.style={
-          opacity=.25,
-          shadow xshift=0.07,
-          shadow yshift=-0.07
-        },
-      }
-    \tikzstyle{supergraph}=[
-      fill=greyblue,
-      rounded corners,
-      font=\small,
-      align=center,
-      text=charcoal,
-      drop shadow={ashadow, color=greyblue}
-    ]
-    \tikzstyle{supergraph_s}=[
-      fill=bisque,
-      rounded corners,
-      font=\small,
-      align=center,
-      text=charcoal,
-      drop shadow={ashadow, color=greyblue}
-    ]
-    \tikzstyle{supergraph_f}=[
-      fill=lightsalmonpink,
-      rounded corners,
-      font=\small,
-      align=center,
-      text=charcoal,
-      drop shadow={ashadow, color=greyblue}
-    ]
-    \tikzstyle{description}=[fill=white]
-\begin{tikzpicture}
-
-% main method nodes
-    \node [supergraph] (st_main) {\textsf{start}$_{\texttt{main}}$};
-    \node [supergraph] (call_secret) [below = \dist of st_main.south] {\textsf{call}$_\texttt{secret}$};
-    \node [supergraph] (return_secret) [below = \dist of call_secret.south] {\textsf{return}$_\texttt{secret}$\\\texttt{a = secret()}};
-    \node [supergraph] (call_f_main) [below = \dist of return_secret.south] {\textsf{call}$_\texttt{A.f}$};
-    \node [supergraph] (return_f_main) [below = \dist of call_f_main.south] {\textsf{return}$_\texttt{A.f}$\\\texttt{b = f(a)}};
-    \node [supergraph] (end_main) [below = \dist of return_f_main.south] {\textsf{end}$_{\texttt{main}}$};
-% main method edges
-    \path[->] (st_main) edge (call_secret);
-    \path[->] (call_secret) edge (return_secret);
-    \path[->] (return_secret) edge (call_f_main);
-    \path[->] (call_f_main) edge (return_f_main);
-    \path[->] (return_f_main) edge (end_main);
-
-%secret method nodes
-    \node [supergraph_s] (st_secret) [above right = 2*\dist and 6*\dist of st_main] {\textsf{start}$_{\texttt{secret}}$};
-    \node [supergraph_s] (return_secret_string) [below = \dist of st_secret.south] {\texttt{return "secret"}};
-    \node [supergraph_s] (end_secret) [below = \dist of return_secret_string.south] {\textsf{end}$_\texttt{secret}$};
-%secret method edges
-    \path[dashed,->] (call_secret) edge[out=20,in=130,->] (st_secret);
-    \path[->] (st_secret) edge (return_secret_string);
-    \path[->] (return_secret_string) edge (end_secret);
-    \path[dashed,->] (end_secret) edge[out=240,in=5] (return_secret);
-
-%f method nodes
-    \node [supergraph_f] (st_f) [below right = 2*\dist and \dist of end_secret.south] {\textsf{start}$_\texttt f$};
-    \node [supergraph_f] (if) [below = \dist of st_f.south] {\texttt{if (s == null)}};
-    \node [supergraph_f] (return_x) [below right = \dist and 2*\dist of if.south] {\texttt{return s}};
-    \node [supergraph_f] (call_f_f) [below left = \dist and 2*\dist of if.south] {\textsf{call}$_\texttt{f}$};
-    \node [supergraph_f] (return_f_f) [below = \dist of call_f_f.south] {\textsf{return}$_\texttt{f}$\\\texttt{r = f("not secret")}};
-    \node [supergraph_f] (return_r) [below = \dist of return_f_f.south] {\texttt{return r}};
-    \node [supergraph_f] (end_f) [below right = \dist and 2*\dist of return_r.south] {\textsf{end}$_\texttt f$};
-%f method edges
-    \path[dashed,->] (call_f_main) edge[out=0,in=160] (st_f);
-    \draw[->] (st_f) edge (if);
-    \draw[->] (if) edge [out=210,in=45] (call_f_f);
-    \draw[->] (call_f_f) edge (return_f_f);
-    \draw[dashed,->] (call_f_f) [out=170,in=200] edge (st_f);
-    \draw[->] (return_f_f) edge (return_r);
-    \draw[->] (return_r) edge [out=-80,in=175] (end_f);
-    \draw[->] (if) edge [out=330,in=135] (return_x);
-    \draw[->] (return_x) edge [out=270,in=10] (end_f);
-    \draw[dashed,->] (end_f) edge [out=200,in=180] (return_f_f);
-    \draw[dashed,->] (end_f) edge [out=215,in=-50] (return_f_main);
-
-%arrow description
-    \node [description] (intra_arrow_left) [above right = \dist and 2*\dist of st_secret] {};
-    \node [description] (intra_arrow_right) [right = \dist of intra_arrow_left] {};
-    \node [description] (inter_arrow_left) [below = .5*\dist of intra_arrow_left] {};
-    \node [description] (inter_arrow_right) [below = .5*\dist of intra_arrow_right] {};
-    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intraprocedural edge} (intra_arrow_right);
-    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{interprocedural edge} (inter_arrow_right);
-\end{tikzpicture}
-}
-  \caption{An example supergraph for Listing~\ref{list:examplejava}}%
-  \label{fig:examplesupergraph}%
-  \end{figure}
-\end{example}
-}
 

### 2015-03-08 sas2015/content/example.tex
moving and resizing figures
moving code to appendix

--- 2015-03-08 sas2015/content/example.tex
@@
 
-\subsection{An Example from the Scala Collections Library}
+\subsection{An Example from the Scala Collections Library}\label{sec:collex}
 The Scala collections library contains the trait \code{TraversableOnce} that is
@@
 The relevant code from \textsf{TraversableOnce} and other related traits is shown
-in Figure~\ref{fig:traversableonce}.
-
-\begin{figure}
-\inputMinted{scala}{TraversableOnce.scala}
-\caption{Relevant code from \textsf{TraversableOnce} and related traits.}
-\label{fig:traversableonce}
-\end{figure}
+in Figure~\ref{fig:traversableonce} in the Appendix.

### 2015-03-08 sas2015/content/appendix.tex
moving table to appendix

@@
 \section*{Appendix}
-In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca} and the code discussed in Section~\ref{sec:collex}.
+In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}, the table illustrating frequencies of correlated calls from Section~\ref{}, and the code discussed in Section~\ref{sec:collex}.
 
@@
 \end{figure}
+
+\subsection{Correlated Calls Occurrences}
+Table~\ref{tab:dacapostat} shows how often correlated calls occur in practice. The number of all call sites in a program is denoted as $C$. 
+Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. The~number of classes~$T$ and the number of lines of code are shown in the last two columns.
+The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
+The next three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
+In this context, we deem a call site to be polymorphic if its statically computed call graph
+contains edges from the call site to multiple target methods.
+We deem a call site to be a correlated call site if it is polymorphic and there is
+at least one other polymorphic call site on the same receiver.
+\input{tables/stats}

### 2015-03-08 sas2015/content/example.tex
moving table to appendix

@@
 To assess the benefit of the correlated-calls analysis, we counted the number of correlated calls that occur in programs of the Dacapo benchmarks~\cite{blackburn2006dacapo}, using the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
-Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis. The results are shown in Table~\ref{tab:dacapostat}.
-
-In the table, the number of all call sites in a program is denoted as $C$. 
-Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. The~number of classes~$T$ and the number of lines of code are shown in the last two columns.
-The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
-The next three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
-In this context, we deem a call site to be polymorphic if its statically computed call graph
-contains edges from the call site to multiple target methods.
-We deem a call site to be a correlated call site if it is polymorphic and there is
-at least one other polymorphic call site on the same receiver.
-
-\input{tables/stats}
+Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis.
+The results are shown in Table~\ref{tab:dacapostat} in the Appendix.
 

### 2015-03-08 sas2015/content/background.tex
removing some old comments

@@
 
-\commentout{
-To compute the meet-over-all-valid-paths solution, each node in the control-flow supergraph is paired with a \textit{fact} $d\in D\cup\{\mathbf0\},\,\mathbf0\notin D$, yielding the nodes $N^\#$ of the \textit{exploded supergraph} $G^\#=(N^\#,\,E^\#)$.
-Roughly, for each node in the program, a fact denotes a binary property whose value (true or false) we want to find out.
-The start node of the exploded supergraph is the node $(\startmain,\,\mathbf0)$.
-
-The flow functions $F$ define the edges of the exploded supergraph.
-Using the flow functions, the IFDS algorithm computes the interprocedurally \textit{realizable} paths from the start to the rest of the exploded graph's nodes.
-A realizable path is a valid path in the exploded supergraph that starts with the entry node $\startmain$.
-
-If there is a realizable path from the node $(\startmain,\,\mathbf0)$ to a given node $(n,\,d),\,d\ne\mathbf0$, then the fact $d$ is considered to hold at node $n$.
-A path to a node $(n,\,\mathbf0)$ means that in the control-flow supergraph, there is a path from $\startmain$ to $n$.
-
-In this way, the IFDS algorithm reduces the input data-flow problem to a graph-reachability problem.
-\begin{example}
-  In a taint analysis, $D$ is the set of variables in the program.
-If a fact $d\in D$ is reachable at a given node, then the variable is considered secret at that node.
-Otherwise, it is considered not secret.
-The question ``is $d$ secret at node $n$?'' becomes ``is there a realizable path from (\textsf{start}$_\texttt{main}$,\,\textbf{0}) to $(n,\,d)$?''.
-\end{example}
-\commentout{\begin{example} 
-  In an available-expressions analysis, $D$ is the set of all expressions in the program.
-If an expression $d\in D$ is reachable at a certain node, it means that it does not need to be recomputed at that node.
-\end{example}}
-}
-
-%\mtodo{In Figure~\ref{fig:cc_edgefn_example}, should we say that $\psi$ corresponds to the function's return value?}
 \begin{example}
@@
   from the start node of the exploded graph to the variable \verb's' at~the~node~$\textsf{print(s)}$ in the \verb'B.bar' method. This means that \verb's' is considered secret at that node.
-
-\commentout{  
-    \begin{figure}%
-      \hspace*{-30pt}
-\scalebox{.9}{
-      \tikzset{
-        ashadow/.style={
-          opacity=.25,
-          shadow xshift=0.07,
-          shadow yshift=-0.07
-        },
-      }
-    \tikzstyle{supergraph}=[
-      fill=greyblue,
-      rounded corners,
-      font=\small,
-      align=right,
-      text=charcoal,
-      drop shadow={ashadow, color=greyblue}
-    ]
-    \tikzstyle{supergraph_s}=[
-      fill=bisque,
-      rounded corners,
-      font=\small,
-      align=left,
-      text=charcoal,
-      drop shadow={ashadow, color=greyblue}
-    ]
-    \tikzstyle{supergraph_f}=[
-      fill=lightsalmonpink,
-      rounded corners,
-      font=\small,
-      align=left,
-      text=charcoal,
-      drop shadow={ashadow, color=greyblue}
-    ]
-    \tikzstyle{description}=[fill=white]
-    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
-
-\begin{tikzpicture}[>=stealth,on grid, auto]
-
-% main method nodes
-    \node [supergraph] (st_main) {\textsf{start}$_{\texttt{main}}$};
-    \node [supergraph] (call_secret) [below = \dist of st_main.south east, anchor=east] {\textsf{call}$_\texttt{secret}$};
-    \node [supergraph] (return_secret) [below = \dist of call_secret.south east,anchor=east] {\textsf{return}$_\texttt{secret}$\\\texttt{a = secret()}};
-    \node [supergraph] (call_f_main) [below = \dist of return_secret.south east, anchor=east] {\textsf{call}$_\texttt{A.f}$};
-    \node [supergraph] (return_f_main) [below = \dist of call_f_main.south east, anchor=east] {\textsf{return}$_\texttt{A.f}$\\\texttt{b = f(a)}};
-    \node [supergraph] (end_main) [below = \dist of return_f_main.south east, anchor=east] {\textsf{end}$_{\texttt{main}}$};
-
-    \node [n,label=$\mathbf{0}$] (st_main_z) [right=\ndd of st_main.east] {};
-    \node [n,label=\texttt{a}] (st_main_x) [right=\ndd of st_main_z] {};
-    \node [n,label=\texttt{b}] (st_main_y) [right=\ndd of st_main_x] {};
-
-    \node [n] (call_secret_z) [right=\ndd of call_secret.east] {};
-    \node [n] (call_secret_x) [right=\ndd of call_secret_z] {};
-    \node [n] (call_secret_y) [right=\ndd of call_secret_x] {};
-
-    \node [n] (return_secret_z) [right=\ndd of return_secret.east] {};
-    \node [n] (return_secret_x) [right=\ndd of return_secret_z] {};
-    \node [n] (return_secret_y) [right=\ndd of return_secret_x] {};
-
-    \node [n] (call_f_main_z) [right=\ndd of call_f_main.east] {};
-    \node [n] (call_f_main_x) [right=\ndd of call_f_main_z] {};
-    \node [n] (call_f_main_y) [right=\ndd of call_f_main_x] {};
-
-    \node [n] (return_f_main_z) [right=\ndd of return_f_main.east] {};
-    \node [n] (return_f_main_x) [right=\ndd of return_f_main_z] {};
-    \node [n] (return_f_main_y) [right=\ndd of return_f_main_x] {};
-
-    \node [n] (end_main_z) [right=\ndd of end_main.east] {};
-    \node [n] (end_main_x) [right=\ndd of end_main_z] {};
-    \node [n] (end_main_y) [right=\ndd of end_main_x] {};
-% main method edges
-    \path[->](st_main_z) edge (call_secret_z);
-    \path[->](call_secret_z) edge (return_secret_z);
-    \path[->](return_secret_z) edge (call_f_main_z);
-    \path[->](call_f_main_z) edge (return_f_main_z);
-    \path[->](return_f_main_z) edge (end_main_z);  
-    \path[->](return_f_main_y) edge (end_main_y);
-
-%secret method nodes
-    \node [supergraph_s] (st_secret) [above right = 2*\dist and 6*\dist of st_main] {\textsf{start}$_{\texttt{secret}}$};
-    \node [supergraph_s] (return_secret_string) [below = \dist of st_secret.south west, anchor=west] {\texttt{return "secret"}};
-    \node [supergraph_s] (end_secret) [below = \dist of return_secret_string.south west,anchor = west] {\textsf{end}$_\texttt{secret}$};
-
-    \node [n,label=$\mathbf{0}$] (st_secret_z) [left=\ndd of st_secret.west] {};
-    \node [n] (return_secret_string_z) [left=\ndd of return_secret_string.west] {};
-    \node [n] (end_secret_z) [left=\ndd of end_secret.west] {};
-%secret method edges
-    \path[->](st_secret_z) edge (return_secret_string_z); 
-    \path[->](return_secret_string_z) edge (end_secret_z); 
-    \path[->,dashed](call_secret_z) edge [out=30,in=180] (st_secret_z);
-    \path[->,dashed](end_secret_z) edge [out=240,in=40] (return_secret_z);
-    \path[->,dashed](end_secret_z) edge [out=260,in=30] (return_secret_x);
-    \path[->](return_secret_x) edge (call_f_main_x);
-    \path[->](call_f_main_x) edge (return_f_main_x);
-    \path[->](return_f_main_x) edge (end_main_x);
-
-%f method nodes
-    \node [supergraph_f] (st_f) [below=2*\dist of end_secret.south west,anchor=west] {\textsf{start}$_\texttt f$};
-    \node [supergraph_f] (if) [below = \dist of st_f.south west,anchor=west] {\texttt{if (s == null)}};
-    \node [supergraph_f] (return_x) [below right = \dist and 2.5*\dist of if.south] {\texttt{return s}};
-    \node [supergraph_f] (call_f_f) [below=\dist of if.south west,anchor=west] {\textsf{call}$_\texttt{f}$};
-    \node [supergraph_f] (return_f_f) [below = \dist of call_f_f.south west,anchor=west] {\textsf{return}$_\texttt{f}$\\\texttt{r = f("not secret")}};
-    \node [supergraph_f] (return_r) [below = \dist of return_f_f.south west,anchor=west] {\texttt{return r}};
-    \node [supergraph_f] (end_f) [below=\dist of return_r.south west,anchor=west] {\textsf{end}$_\texttt f$};
-
-     \node [n,label=\texttt{s}] (st_f_s) [left=\ndd of st_f.west] {}; 
-     \node [n,label=\texttt{r}] (st_f_r) [left=\ndd of st_f_s] {};
-     \node [n,label=$\mathbf{0}$] (st_f_z) [left=\ndd of st_f_r] {};
-
-     \node [n] (if_s) [left=\ndd of if.west] {};
-     \node [n] (if_r) [left=\ndd of if_s] {};
-     \node [n] (if_z) [left=\ndd of if_r] {};
-
-     \node [n] (call_f_f_s) [left=\ndd of call_f_f.west] {};
-     \node [n] (call_f_f_r) [left=\ndd of call_f_f_s] {};
-     \node [n] (call_f_f_z) [left=\ndd of call_f_f_r] {};
-
-     \node [n] (return_f_f_s) [left=\ndd of return_f_f.west] {};
-     \node [n] (return_f_f_r) [left=\ndd of return_f_f_s] {};
-     \node [n] (return_f_f_z) [left=\ndd of return_f_f_r] {};
-
-     \node [n] (return_r_s) [left=\ndd of return_r.west] {};
-     \node [n] (return_r_r) [left=\ndd of return_r_s] {};
-     \node [n] (return_r_z) [left=\ndd of return_r_r] {};
-
-     \node [n] (end_f_s) [left=\ndd of end_f.west] {};
-     \node [n] (end_f_r) [left=\ndd of end_f_s] {};
-     \node [n] (end_f_z) [left=\ndd of end_f_r] {};
-
-     \node [n,label=$\mathbf0$] (return_x_z) [right=\ndd of return_x.east] {};
-     \node [n,label=\texttt{r}] (return_x_r) [right=\ndd of return_x_z] {};
-     \node [n,label=\texttt{s}] (return_x_s) [right=\ndd of return_x_r] {};
-%f method edges
-    \path[->](st_f_z) edge (if_z);
-    \path[->](if_z) edge (call_f_f_z);
-    \path[->](call_f_f_z) edge (return_r_z);  
-    \path[->](return_r_z) edge (end_f_z);
-    \path[->](if_z) edge [out=-43,in=127] (return_x_z);
-    \path[->](return_x_z) edge [out=270,in=25] (end_f_z);
-    \path[->](st_f_s) edge (if_s);
-    \path[->](if_s) edge (call_f_f_s);
-    \path[->](call_f_f_s) edge (return_r_s);  
-    \path[->](return_r_s) edge (end_f_s);
-    \path[->](if_s) edge [out=-30,in=110] (return_x_s);
-    \path[->](return_x_s) edge [out=270,in=25] (end_f_s);
-    \path[->](return_f_f_r) edge (return_r_r);
-    \path[->](return_r_r) edge (end_f_r);
-    \path[->,dashed](call_f_main_z) edge [out=20,in=160] (st_f_z);
-    \path[->,dashed](end_f_z) edge [out=150,in=-20] (return_f_main_z);
-    \path[->,dashed](call_f_f_z) edge [out=110,in=250] (st_f_z);
-    \path[->,dashed](end_f_z) edge [out=110,in=250] (return_f_f_z);
-    \path[->,dashed](call_f_main_x) edge [out=32,in=112] (st_f_s);
-    \path[->,dashed](end_f_s) edge [out=155,in=-40] (return_f_main_y);
-    \path[->,dashed](end_f_s) edge [out=120,in=-50] (return_f_f_r);
-    \path[->,dashed](end_f_r) edge [out=110,in=250] (return_f_f_r);
-    \path[->,dashed](end_f_r) edge [out=150,in=-50] (return_f_main_y);
-\end{tikzpicture}
-}
-  \caption{The exploded supergraph corresponding to a taint analysis for the input program in Listing~\ref{list:examplejava}}%
-  \label{fig:exampleexploded}%
-  \end{figure}
-}
 \end{example}
 
-\commentout{
-To convert a representation relation $R_f$ back into the original flow function $f$, we can use the \textit{interpretation} function $\denote {R_f}$:
-\begin{align}
-  f&=\denote{R_f}\notag\\
-  &=\lambda D_1\,.\,\left(\left\{d_2\ |\ \exists d_1\in D_1:\,(d_1,\,d_2)\in R_f\right\}\cup\{d_2\ |\ (\mathbf0,\,d_2)\in R_f\}\right)
-  \setminus\{\mathbf0\}\,.
-\end{align}
-}
-
-\commentout{
-A practical implementation of the IFDS algorithm generally takes as input a representation of the
-exploded supergraph edges $E^\sharp$ instead of explicit data-flow functions $M_F$. This is convenient because
-the two are equivalent in expressiveness, and because the IFDS algorithm works internally with the exploded
-supergraph. More specifically, the input generally provides a function
-$f: N^* \times D \times N^* \to 2^D$. Given a (non-exploded) supergraph edge $n \to n'$ and a data-flow fact $d$,
-$f(n,d,n')$ returns the set of all $d'$ such that the exploded supergraph contains the edge $(n,d) \to (n',d')$.
-For convenience, the function $f$ can be split up into separate functions that handle the cases when
-the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.
-%\mtodo{Do we leave the start-to-return edge out as a special case of intraprocedural edge?}
-}
-
-%We presented an overview of the IFDS analysis. IFDS problems are transformed into IDE problems by the correlated-calls analysis. The IDE framework is described in the next section.
-
 \subsection{IDE}\label{sec:bgide}
-\commentout{
-There exists an entire class of data-flow problems that cannot be formulated as IFDS problems.
-Informally, the problems cannot be formulated as decision problems.
-For instance, a constant-propagation problem asks, for each variable $v$ in the program, ``if $v$ is a constant at a given program point, what is $v$'s value?''.
-The questions asked by constant propagation are of the form ``if property $X$ \textit{($v$ being a constant)} is true at program point~$Y$, what is the value of some property~$Z$ \textit{(the value of the constant)} corresponding to~$X$?''.
-It turns out that problems with such questions can often be solved by the IDE algorithm.
-
-The IDE framework is an expressive extension to IFDS that was created by the same authors in 1996.
-The problems that IDE can solve include, but are not limited to, IFDS problems~\cite{reps1995precise}.
-Just as the IFDS algorithm, the IDE algorithm is suitable for data-flow analyses that can be encoded with interprocedural, distributive flow functions.
-However, in IDE, the domain of the flow functions is not restricted to sets $D$ of data-flow facts.
-The IDE domain of a flow function consists of \textit{environments} that map data-flow facts from the set $D$ to lattice elements.
-
-As an example, in a constant propagation problem, an IDE environment would map each variable to the (possibly) constant value that it is bound to.
-To illustrate the distinction between IFDS and IDE we could say that IFDS can find out which variables in a program are constants, whereas IDE can additionally retrieve the values of the constant variables.
-Instead of just telling us whether a fact holds or not, the IDE analysis can provide us with additional information about facts.
-
-Just as in the IFDS analysis, the IDE algorithm reduces a data-flow problem to a graph-reachability problem.
-Additionally, for each program point, the algorithm computes an \textit{environment} $\textsf{Env}(D,\,L)$, where data-flow facts are mapped to values of a lattice $L$.
-}
 
@@
 $L$ of finite height, ordered pointwise. Like IFDS, IDE requires the data-flow functions to be distributive.
-
-\commentout{
-\begin{mdelete}
-For example, using the IDE analysis, we can encode a restricted version of a constant-propagation analysis\footnote{%
-  In the general case, constant propagation cannot be encoded with distributive flow functions and is therefore not suitable for an IDE analysis~\cite{muller2001complexity}.
-}. The data-flow facts  correspond to program variables, and the lattice incorporates all possible values for constants. 
-If a fact $d$ in the exploded supergraph is reachable at node $n$, and $\textsf{Env}(d)\notin\{\bot,\,\top\}$, it means that the variable associated with $d$ is a constant.
-Furthermore, the value of the constant can be inferred from the environment for the corresponding node and is equal to $\textsf{Env}(d)$.
-\end{mdelete}
-}
 
@@
 
-\commentout{
-and
-\begin{equation}
-  \Omega=\lambda d\,.\,\top
-\end{equation}
-is the top element in the environment lattice~$\mathsf{Env}(D,\,L)$.
-}
-
-\commentout{
-The IDE analysis is a generalization of the IFDS analysis: every IFDS problem can be converted into an equivalent IDE problem~\cite{reps1995precise}.
-The equivalent problem can be solved by the IDE algorithm, and the result converted into an IFDS result.
-In~an~IFDS-equivalent IDE problem, the~graph~$G^*$ and the~set~$D$ of~data-flow facts remain the~same.
-The $L$ lattice is a two-point lattice: if a fact is mapped to the top (bottom) element, then it is reachable (unreachable).
-The conversion between IFDS and IDE problems is discussed in detail in Section~\ref{seq:transIfdsIde}.
-}
-
-\commentout{
-\subsubsection{Environment Transformers}
-For each node in the CFG, the result of an IDE analysis computes an environment $\textsf{Env}(D,\,L)$, which is a map from data-flow facts to lattice elements.
-
-Instead of flow functions that show how to propagate facts, the IDE framework uses distributive environment transformers to propagate environments.
-For each edge $(n_1,\,n_2)$ in the control-flow supergraph, an environment transformer indicates how the environment at node $n_1$ is modified at node $n_2$.
-
-From Section~\ref{sec:overviewifds} we know that flow functions can be represented with exploded-graph edges.
-To represent environment transformers, we will construct \textit{labeled} exploded-graph edges, where each edge is associated with a distributive \textit{micro function}%
-\footnote{See~Sagiv et al.~\cite{sagiv1996precise} for a formal definition of the representation relation for environment transformers.}
-$f:\,L\to L$. A~micro function shows how to change a lattice element for a given node and fact.
-
-For instance, if an IDE problem is equivalent to an IFDS problem, the edges of the exploded supergraph are the same for both problems.
-In the IDE problem, the edges of the exploded supergraph are labeled with identity micro functions.
-
-We extend the meet operator to work on micro functions by defining
-\begin{equation}
-  (f_1\sqcap f_2)(l)=f_1(l)\sqcap f_2(l)
-\end{equation}
-for all $l\in L$.
-}
-
-%In IDE problems, the auxiliary fact analogous to $\mathbf0$ in IFDS is denoted as $\Lambda$.
-
-\commentout{
-\begin{mdelete}
-\begin{example}\label{ex:constprop}
-  One version of the constant propagation analysis that can be encoded with IDE is \textit{linear constant propagation}.
-A linear constant propagation analysis can detect constants of the form $a\cdot x+b$, where $a$ and $b$ are integers and $x$ is a variable.
-In particular, a variable can only be considered constant if it depends on at most one other constant variable: even if $y$ and $z$ are variables that are considered constant, the variable $x=y+z$ will be considered not constant.
-If we encoded the analysis in a way to handle non-linear constant assignments, we would have to use non-distributive flow functions, which would violate the requirements of the IDE algorithm.
-
-  For linear constant propagation, the $L$ lattice consists of the set of integers $\mathbb Z$, a top element denoting ``not a constant'', and a bottom element denoting an unknown value.
-  The meet of two lattice elements is defined as follows: for any lattice element $l\in L$,
-  \[
-    \top\sqcap l=\top\qquad\text{and}\qquad\bot\sqcap l=l.
-  \]
-  For two lattice elements $l_1,\,l_2\in\mathbb Z$, $$l_1\sqcap l_2=\top.$$
-
-  We define the addition and multiplication operations on lattice elements $l\in L$ and integers $c\in\mathbb Z$ as follows:
-  \[
-    l+c=\begin{cases}
-      \bot&\text{if }l=\bot;\\
-      \top&\text{if }l=\top;\\
-      l+c&\text{otherwise.}
-    \end{cases}
-    \qquad
-    c\cdot l=\begin{cases}
-      \bot&\text{if }l=\bot;\\
-      \top&\text{if }l=\top;\\
-      c\cdot l&\text{otherwise.}
-    \end{cases}
-  \]
-   Let the function $M$ that maps supergraph edges to environment transformers be defined in the following way:
-  \[
-    M=\lambda((n_1,\,n_2))\,.\,
-    \begin{cases}
-      \lambda\textsf{env}\,.\,\textsf{env}[x\to a\cdot\textsf{env}(y)+c\,]
-        &\text{if $n_1$ contains an assignment}\\&\text{$x=a\cdot y+c$, where $y$ is a variable}\\&\text{and $a,\,c$ are constants;}\\
-      \id
-        &\text{otherwise.}
-    \end{cases}
-  \]
-  Here, we denote with $\textsf{env}[x\to a]$ an environment \textsf{env} in which the key $x$ is mapped to $a$, and all other keys $y\ne x$ are mapped to their old values $\textsf{env}(y)$.
-  When $M$ is applied to an edge whose source node contains an assignment for a variable $x$, $M$ returns an environment transformer that updates the argument environment with a new value for $x$.
-
-  Consider the following program:
-
-\inputMinted{java}{constprop.java}
-  For the edges $e_1,\,e_2,\,e_3$, and $e_4$ that start at the first, second, third, and fourth instruction, $M$ creates the following environment transformers:
-  \begin{align*}
-    M(e_1)
-    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt u\to 1]\\
-    M(e_2)
-    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt v\to\textsf{env}(\texttt u)+2]\\
-    M(e_3)
-    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt w\to\top]\\
-    M(e_4)
-    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt u\to 5].
-  \end{align*}
-
-  The corresponding labeled exploded supergraph is shown in Figure~\ref{fig:constprop}.
-
-  The result of the analysis yields a map from nodes to environments.
-Each environment maps variables to elements of the constant-propagation lattice.
-The environment at the last node will look as follows:
-  \[
-    \{(\texttt u,\,5),\ (\texttt v,\,3),\ (\texttt w,\,\top)\}.
-  \]
-\end{example}
-
-\begin{figure}
-  \centering
-    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt,sm]
-    \tikzstyle{sm}=[font=\footnotesize]
-\begin{tikzpicture}[>=stealth,on grid, auto]
-    \node [n,label=$\mathbf0$] (zero){};
-    \node [n] (zero_) [below=\edge of zero] {};
-    \node [n,label={\texttt u}] (u) [right=\dist of zero] {};
-    \node [n] (u_) [below=\edge of u] {};
-    \node [n,label={\texttt v}] (v) [right=\dist of u] {};
-    \node [n] (v_) [below=\edge of v] {};
-    \node [n,label=\texttt{w}] (w) [right=\dist of v] {};
-    \node [n] (w_) [below=\edge of w] {};
-    \node [n] (zero__) [below=\edge of zero_]{};
-    \node [n] (u__) [below=\edge of u_]{};
-    \node [n] (v__) [below=\edge of v_]{};
-    \node [n] (w__) [below=\edge of w_]{};
-    \node [n] (zero___) [below=\edge of zero__]{};
-    \node [n] (u___) [below=\edge of u__]{};
-    \node [n] (v___) [below=\edge of v__)]{};
-    \node [n] (w___) [below=\edge of w__]{};  
-    \node [n] (zero____) [below=\edge of zero___]{};
-    \node [n] (u____) [below=\edge of u___]{};
-    \node [n] (v____) [below=\edge of v___)]{};
-    \node [n] (w____) [below=\edge of w___]{};
-
-    \path[->](zero) edge node[left,sm]{$\id$} (zero_);
-    \path[->](zero) edge node[right,sm]{$\lambda l.1$} (u_);
-    \path[->](zero_) edge node[left,sm]{$\id$} (zero__);
-    \path[->](u_) edge node[right,sm]{$\lambda l.l+2$} (v__);
-    \path[->](u_) edge node[left,sm]{$\id$} (u__);
-    \path[->](zero__) edge node[left,sm]{$\id$} (zero___);
-    \path[->](u__) edge node[left,sm]{$\id$} (u___);
-    \path[->](v__) edge node[left,sm]{$\id$} (v___);
-
-    \path[->,dashed,color=gray](v) edge node[left,sm]{$\id$} (v_);
-    \path[->,dashed,color=gray](w) edge node[left,sm]{$\id$} (w_);
-    \path[->,dashed,color=gray](w_) edge node[right,sm]{$\id$} (w__);
-
-    \path[->] (zero___) edge node[left,sm]{$\id$} (zero____);
-    \path[->] (u___) edge node[left,sm]{$\lambda l.5$} (u____);
-    \path[->] (v___) edge node[left,sm]{$\id$} (v____);
-    \path[->,dashed,color=gray] (w___) edge node[left,sm]{$\id$} (w____);
-  \end{tikzpicture}
-  \caption[A labeled exploded supergraph for a constant-propagation analysis described in Example~\ref{ex:constprop}]{A labeled exploded supergraph for a constant-propagation analysis described in Example~\ref{ex:constprop}.
-The dashed edges are edges not reachable from the entry node.}%
-  \label{fig:constprop}%
-  \end{figure}
-\end{mdelete}
-}
-
-\commentout{
-In this way, each edge in the exploded graph is labeled with a micro function.
-The mapping from exploded-graph edges to the corresponding micro functions is stored in \textit{edge functions},  denoted as \textsf{EdgeFn}$:\,E^\#\to(L\to L)$.
-}
-
 \subsubsection{Overview of the IDE Algorithm}\label{sec:ideoverview}
@@
 with a \textit{micro-function}, which is a function from $L$ to $L$.
-\commentout{
-The pointwise representation of an environment transformer 
-$t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
-is defined as
-\newcommand{\microedge}[3]{#1\xrightarrow{#3}#2}
-\begin{align*}
-    R_t =& \{ \microedge{\mathbf0}{\mathbf0}{\lambda l.l} \} \cup
-    \{\microedge{\mathbf0}{d_j}{\lambda l.t(\top_{\textsf{Env}})(d_j)} \mid d_j \in D\}\\
-    &\cup
-    \{\microedge{d_i}{d_j}{\lambda l.t(\top_{\textsf{Env}}[d_i\to l])(d_j)} \mid d_i, d_j \in D\}.
-\end{align*}
-}
-%Let $\top_{\textsf{Env}} = \lambda d.\top$ be the environment that maps every element of $D$ to $\top$.
-%\ftodo{
-   %What is the relationship between $\Omega$ and $\Delta$?
-%}
-%\otodo{What do you mean by $\Delta$?}
+
 Thanks to distributivity, every environment transformer 
@@
 
-%Similar to the IFDS algorithm,
 A practical implementation of the IDE algorithm requires
@@
 In an implementation, it can be convenient to split the function $\textsf{EdgeFn}$ into separate functions that handle the cases when $n\to n'$ is an intraprocedural edge, a call-to-return edge, a call-to-start edge, or an end-to-return edge.
-
-\commentout{
-Given a labeled exploded supergraph, the IDE algorithm computes the environments for all nodes in the CFG.
-
-The algorithm first computes the lattice elements $l_{n,\,d}$ that correspond to each reachable node $(n,\,d)$ in the exploded supergraph.
-The union of the exploded nodes $(n,\,d)$ for a given control-flow node $n$, mapped to the corresponding lattice elements $l_{n,\,d}$, form the environment $\textsf{Env}_n$  for that node:
-\begin{equation}
-  \textsf{Env}_n=\left\{(d,\,l_{n,\,d})\ |\ (n,\,d)\in N^\#\right\}\,.
-\end{equation}
-
-The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each interprocedurally realizable path
-\[
-  p=\left[(\startmain,\,\mathbf0),\,(n_1,\,d_1),\,\dots,\,(n_k,\,d_k)\right]
-\]
- that starts with the entrypoint of the exploded supergraph, we compute the micro function $f_p$ that corresponds to $p$.
-The micro function consists of the composition of all individual micro functions with which the edges of $p$ are labeled:
-\begin{align}
-  f_p=\textsf{EdgeFn}((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))\,\circ\ldots\circ
-      \textsf{EdgeFn}(\startmain,\,\mathbf0),\,(n_1,\,d_1))\,.
-\end{align}
-
-Let the lattice element that $(n,\,d)$ is mapped to according to path $p$ be denoted as $l_{n,\,d}^p$.
-As shown in~Sagiv et al.~\cite{sagiv1996precise}, the lattice element can be obtained by applying $f_p$ to the bottom element:
-\begin{equation}
- l^p_{n,\,d}=f_p(\bot)\,.
-\end{equation}
-
-Let $Q$ be the set of paths that start at the entry point and end at the given node $(n,\,d)$.
-The lattice element $l_{n,\,d}$ is the meet of the lattice elements corresponding to all the paths in $Q$:
-\[
-  l_{n,\,d}=\bigsqcap_{q\in Q}l^q_{n,\,d}\,.
-\]
-
-This is a general outline of the IDE analysis. We use the IDE framework to improve the precision of IFDS problems in the presence of correlated calls.
-The next section describes how this is done.
-}
-
-%\ftodo{Would it make sense to discuss an example of an IDE problem here?  Perhaps we can do this
-%  without using much space by referring to an existing figure elsewhere in the paper?}
-%  \otodo{See Example 4 on the previous page.}
-%  \otodo{Now done in Example 5.}

### 2015-03-08 sas2015/content/background.tex
removing some old comments

@@
 a node $n$ is denoted $\ivp(n)$.
-%\otodo{Should we give a formal definition?}
 
-%Let each call node in a program be labeled with a distinct opening parenthesis and the corresponding return node with the matching closing parenthesis.
-For a given path $p$, let $s$ be the string that is obtained by concatenating the labels of the nodes in $p$.
-%Then $p$ is \textit{valid} if $s$ belongs to the language of substrings of balanced parentheses.
-The set of all interprocedurally valid paths from the start node to a node $n$ is denoted as $\ivp(n)$.
-The set $\ivp(n)$ is a conservative approximation of all concrete execution paths from the start node to $n$.
-
-%A \textit{context-sensitive} data-flow analysis is an analysis that considers only interprocedurally valid paths.
-
-\commentout{
-\begin{mdelete}
-\begin{example}
-  In the supergraph in Figure~\ref{fig:examplesupergraph}, let us assign $\{,\,\}$ parentheses to $\textsf{call}_\texttt{A.f}$ and $\textsf{return}_\texttt{A.f}$, and $\langle,\,\rangle$ parentheses to $\textsf{call}_\texttt{f}$ and $\textsf{return}_\texttt{f}$.
-  Then the string corresponding to the path 
-  \[
-    p_1=\left[\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,
-          \highlight{\textsf{start}_\texttt{f}}{lightsalmonpink},\,
-          \highlight{\texttt{if (s == null)}}{lightsalmonpink},\,
-          \highlight{\texttt{return s}}{lightsalmonpink},\,
-          \highlight{\textsf{end}_\texttt{f}}{lightsalmonpink},\,
-          \highlight{\textsf{return}_\texttt{A.f}}{greyblue}
-    \right]
-  \]
-  is $\{\}$, which indicates that $p_1$ is valid. Every prefix of $p_1$ is also a valid path.
-
-However, the graph also contains an interprocedurally invalid path
-  \[
-    p_2=\left[\highlight{\textsf{call}_\texttt{f}}{lightsalmonpink},\,
-          \highlight{\textsf{start}_\texttt{f}}{lightsalmonpink},\,
-          \highlight{\texttt{if (s == null)}}{lightsalmonpink},\,
-          \highlight{\texttt{return s}}{lightsalmonpink},\,
-          \highlight{\textsf{end}_\texttt{f}}{lightsalmonpink},\,
-          \highlight{\textsf{return}_\texttt{A.f}}{greyblue}
-    \right]
-  \]
-  with corresponding string $\langle\}$.
-\end{example}
-\end{mdelete}
-}
-
-%\otodo{The definitions that Marianna had were for \emph{complete}
-%lattices/semilattices. All of the lattices in the context of IFDS/IDE
-%are/must be complete. I'll just say that here.}
-%\ftodo{Would it make sense to first the define the notion of a lattice without referring to its completeness?
-       %This could be followed by defining what it means for a (semi)lattice to be complete, and then we
-       %could say that all lattices considered in this paper are complete, etc.}
-%\ftodo{Can we define the symbols $\sqcup$ and $\sqcap$ for join and meet here?}
 A \textit{lattice}%
@@
 
-%A \textit{meet semilattice} $L=(S,\,\sqcap)$ is defined by a set $S$ and a meet operation $\sqcap$ that is  associative, commutative, and idempotent.
-  %The meet operation induces a partial order $(S,\,\sqsubseteq)$ where every subset contains  a greatest lower bound: For all $x,\,y\in S$, $x\sqsubseteq y$ if $x\sqcap y=x$.
-The greatest lower bound, or top element, of the semilattice is denoted as $\top$.
-  %If $k$ is the length of the longest chains of elements in the semilattice, then the \textit{height} of the semilattice is~$k-1$.
-
 In this paper, we denote a map $m$ as a set of pairs of keys and values, in which each key appears at most once.
 For any map $m$,  $m(k)$ is the value paired with the key $k$ in $m$. We denote by $m[x\to y]$ a map that maps $x$ to $y$, and every other key $k$ to $m(k)$.
-%To avoid excessive parentheses, we write $\left(m[x_1\to y_1]\right)[x_2\to y_2]$ as $m[x_1\to y_1][x_2\to y_2]$.
-
-%We will denote the identity function $\lambda x\,.x$ by $\textsf{id}$.
-%We will use a typed version of this function in various contexts, where the type of $x$ will vary with
-%the context.
-
-%OL: we can just as easily write the identity explicitly as \x.x throughout.
 
@@
 because it constructs summaries of the effects of called procedures.
-\commentout{The IFDS analysis is a version of the classic \textit{functional approach} to data-flow analysis proposed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.}
-\commentout{In other data-flow algorithms not based on the functional approach, the result of the analysis at the entry of a procedure ``merges'' the incoming data obtained from all callers of the procedure.
-As a consequence, there is one global data-flow result computed at the end of the procedure.
-Context-sensitivity, however, allows an analysis to compute the data-flow result for a given procedure as a \textit{function} of the data-flow value at the start of the procedure.
-The analysis result for a procedure varies depending on where the procedure was called from.
-This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.}
 The IFDS framework is applicable to \textit{interprocedural} data-flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
@@
 $f(x_1\sqcap x_2)=f(x_1)\sqcap f(x_2)$.
-
-%The IFDS algorithm is applicable to problems which can be expressed with data-flow functions that satisfy certain restrictions.
-\textit{Interprocedural} flow functions specify how data flows from the invocation of a procedure to its start, and from the procedure's end back to its call site.
-\textit{Distributive} flow functions are those that distribute over the confluence operator.
-In the context of IFDS, the confluence operator is called meet, and it can be either union or intersection.
-The data-flow facts on which the analysis operates must be a \textit{finite} set $D$.
-Each flow function operates on a \textit{subset} of $D$ (for example, the set of variables in the program) which makes the domain of the flow functions the power set of $D$.
-
-\commentout{The purpose of the IFDS framework is to solve a special subset of interprocedural, flow-sensitive, context-sensitive data-flow-analysis problems.
-The main idea of IFDS is to encode the data-flow analysis problem into a graph-reachability problem.}
 
@@
   (iii) handle a very specific set of problems~\cite{knoop1993efficient}.
-
-%\subsubsection{Data-Flow Problems Suitable for IFDS}\label{sec:suitableifds}
-\commentout{In this section we describe the data-flow problems that can be solved by an IFDS analysis.
-We will start with an intuitive definition and later on formalize the notion of an IFDS-suitable problem.}
-
-%Informally, an IFDS analysis can only solve decision problems.
-An IFDS analysis answers questions of the following kind: ``is property $X$ true at program point~$Y$?''.
-For example, a taint-analysis problem asks, for each variable $v$ in the program, ``is $v$ secret at a given program point?''.
-\commentout{An available-expressions problem asks, for each expression $e$, ``does $e$ have to be recomputed at a given program point?''.}
 
@@
  $\mvp{F}(n)=\bigsqcap_{q\in\ivp(n)}M_F(q)(\top)$, where $M_F$ is extended from edges to paths by composition.
-
-\commentout{
-is a function that maps supergraph edges to data-flow functions, and $M_F$ is extended to paths by composition\footnote{%
-  Let $A$ be a set and $f:\,E^*\to(A\to A)$ a function from supergraph edges to functions on $A$.
-  We say that $f$ is extended to  paths by composition to denote that for a path $q$ consisting of the edges $e_1,\,\dots,\,e_k$, $f(q)=f(e_k)\circ\ldots\circ f(e_1)\circ\id$.
-}. The \textit{meet operator} $\sqcap$ is either union or intersection.
-}
-
-%Without loss of generality, we will take meet to denote union.
-It can be shown that any problem where meet is defined as intersection can be reformulated into an equivalent one where meet is defined as union~\cite{reps1995precise}.
 
@@
 paths in the resulting graph.
-
-\commentout{
-The representation relation allows us to compactly represent the composition and meet operations which are required for the IFDS algorithm.
-
-For two representation relations $R_{f_1},\,R_{f_2}$, the composition and meet operations are defined as follows:
-\begin{align}
-  R_{f_1}\circ R_{f_2}&=\{(d_1,\,d_3)\ |\ \exists d_2:\ (d_1,\,d_2)\in R_{f_1},\,(d_2,\,d_3)\in R_{f_2}\}\,.
-\intertext{and}
-  R_{f_1}\sqcap R_{f_2}&=R_{f_1}\cup R_{f_2}\,.
-\end{align}
-
-The representation relation distributes over composition and meet:
-\begin{align}
-  R_{f_1}\circ R_{f_2}=R_{f_1\circ f_2}\,,\qquad
-\text{and}\qquad
-  R_{f_1}\sqcap R_{f_2}=R_{f_1\sqcap f_2}\,.
-\end{align}
-}
-
-%On the exploded graph, the composition of two functions is represented by the paths that are formed when the exploded-graph edges are combined.
-%\otodo{The example used to say $R_f \circ R_g$, but I believe it showed $R_g \circ R_f$. I fixed it, but please check that this is correct.}
 
@@
 
-%\otodo{Discuss the micro-functions in the example exploded supergraph in Figure 3.}
 \begin{example}

### 2015-03-08 sas2015/content/example.tex
minor changes

@@
 shape analysis.
-%\ftodo{Ondrej, can you give a few more/better examples?}
 
-\subsection{Occurrences of Correlated Calls}
+\subsection{Occurrences of Correlated Calls}\vspace{-.5mm}
 How often do correlated calls occur in practice?
@@
 shared by both collections and iterators over them. 
-%\ftodo{
-%  I think it would be helpful to show a little more of the code of the trait here,
-%  such as the trait declaration and the signature of the toArray method containing the
-%  correlated calls. You can abbreviate everything else with ...
-%}
 The \code{toArray} method of this trait
@@
 extracts all elements of the iterator to count them.
-%\ftodo{
-%  Would it make sense to show the code for the size method, and refer to the line numbers
-%  of that method in the above sentence?  
-%}
  At the call to \code{copyToArray},
 the iterator is already empty, so nothing is copied to the newly created array.
-%\ftodo{
-%Would it make sense to show the code for copyToArray here?
-%}
 One could design an IFDS analysis to detect this kind of bug.
@@
 However, the implementation of \code{TraversableOnce.toArray} is actually correct because the above
-code is guarded with a test:
-\inputMintedNoLNs{scala}{isTraversable.scala}
-%\ftodo{It is confusing that this code fragment is labeled with line number 19 although it presumably
-%  occurs in the code before the previously discussed two lines. I think it is better to show
-%  all of the code at once, in a figure, and include at least the headers of all the methods mentioned
-%  here.}
+code is guarded with a test: \code{if (this.isTraversableAgain) ...}
+%\inputMintedNoLNs{scala}{isTraversable.scala}
 When the \code{isTraversableAgain} method returns false, as it does for
@@
 \code{size} and \code{copyToArray}.
-%\ftodo{Would it be helpful to create a diagram of the relevant fragments of the supergraph,
-%with the infeasible path in bold?}
-
-\commentout{
-    For reference, here is the full code of the method:
-
-def toArray[B >: A : ClassTag]: Array[B] = {
-    if (isTraversableAgain) {
-        val result = new Array[B](size)
-        copyToArray(result, 0)
-        result
-    }
-    else toBuffer.toArray
-}
-
-}
 

### 2015-03-08 sas2015/content/impl.tex
minor changes

@@
   then
-  \begin{equation}
+  $
     d\in \backCC\left(\resultIDE(\transCC_R(P))\right)(n)\,.
-  \end{equation}
+  $
 \end{restatable}
@@
 \begin{restatable}[Precision]{lemma}{precision}\label{lem:subsetifds}
-    For an IFDS problem $P$ and all ${n\in N^*}$,
-    \begin{equation}\label{eq:correct}
+    For an IFDS problem $P$ and all ${n\in N^*}$,\\
+    $
       \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
@@
       \resultIFDS(P)(n)\,.
-    \end{equation}
+    $
 \end{restatable}
@@
 
+Let $P$ be an IFDS problemm.
 \begin{restatable}{lemma}{onlycorrrec}\label{lem:onlycorrrec}
-  Let $P$ be an IFDS problem. Then
-  \begin{equation}
+  $
     \backCC\left(\resultIDE\left(\transCC_\rcc(P)\right)\right)=\backCC(\resultIDE\left(\transCC_R(P)\right))\,.
-  \end{equation}
+  $
 \end{restatable}

### 2015-03-08 sas2015/content/related.tex
minor changes

@@
 for Ja\-va\-Script programs~\cite{DBLP:conf/ecoop/SridharanDCST12} also
-eliminate infeasible paths. However, instead of infeasible paths
+eliminate infeasible paths. Instead of infeasible paths
 between dynamically dispatched method calls, their approach eliminates
-infeasible paths between reads and writes of different properties
-(the JavaScript analogue of fields) of an object. Unlike in more static languages,
-property names in JavaScript are first class values (strings). When a loop indexed by
-property names updates the properties of objects, the loop body is extracted into a function
-and analyzed context sensitively with a separate context for each property name.
+infeasible paths between reads and writes of different members
+%(the JavaScript analogue of fields) 
+of an object. 
+%Unlike in more static languages,
+%property names in JavaScript are first class values (strings). When a loop indexed by
+%property names updates the properties of objects, the loop body is extracted into a function
+%and analyzed context sensitively with a separate context for each property name.
 The approach differs from ours in that it targets points-to analysis rather

### 2015-03-08 sas2015/content/example.tex
removing stuff

@@
 declares a class \code{A} with a subclass \code{B},  where \code{A} defines methods 
-\code{foo()} and \code{bar()} that are overridden in \code{B}.  In order to keep the 
-example small and self-contained, it is assumed  that secret values are created by 
-an unspecified function \code{secret()}, which is called in method \code{A.foo()} on 
-line~\ref{line:Afoo}. Furthermore, it is assumed that any write to the standard output 
+\code{foo()} and \code{bar()} that are overridden in \code{B}.  
+%In order to keep the example small and self-contained, 
+It is assumed  that secret values are created by 
+an unspecified function \code{secret()}, which is called in method \code{A.foo()}%
+%  on line~\ref{line:Afoo}
+. Furthermore, it is assumed that any write to the standard output 
 stream via calls \code{System.out.println()} such as the one in method \code{B.bar()} 
-on line~\ref{line:Bbar} is a security-sensitive operation. Depending on the number of 
+%on line~\ref{line:Bbar} 
+is a security-sensitive operation. Depending on the number of 
 arguments passed to the program, the \code{main()} method of the example program creates 
-either an \code{A}-object or a \code{B}-object on line~\ref{line:createObject}. The 
-program then calls \code{foo()} on this object on line~\ref{line:callfoo}, which is 
-followed by a call to \code{bar()} on the same object on line~\ref{line:callbar}.
+either an \code{A}-object or a \code{B}-object%
+%on line~\ref{line:createObject}
+. The 
+program then calls \code{foo()} on this object
+on line~\ref{line:callfoo}, which is 
+followed by a call to \code{bar()} on the same object%
+%on line~\ref{line:callbar}
+.
 
@@
 Figure~\ref{list:ccexample} is the following: Is it possible for the untrusted value 
-that is read on line~\ref{line:Afoo} to flow to the print statement on line~\ref{line:Bbar}? 
-%
+that is read on line~\ref{line:Afoo} to flow to the print statement% %on line~\ref{line:Bbar}
+?
 To determine whether such a flow of tainted data is possible, consider the control-flow

### 2015-03-08 sas2015/content/intro.tex
commiting introduction changes

@@
 of any existing data-flow analysis that is capable of avoiding infeasible paths that arise 
-in the presence of correlated method calls (see Section~\ref{sec:Related} for a discussion
-of related work).
+in the presence of correlated method calls.
+% (see Section~\ref{sec:Related} for a discussion
+%of related work).
 

### 2015-03-08 sas2015/content/appendix.tex

@@
-\section*{Appendix}
+\section{TraversableOnce Trait from Scala Standard Library}
+
 In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}, the table illustrating frequencies of correlated calls from Section~\ref{}, and the code discussed in Section~\ref{sec:collex}.
+\begin{figure}
+\inputMinted{scala}{TraversableOnce.scala}
+\caption{Relevant code from \textsf{TraversableOnce} and related traits.}
+\label{fig:traversableonce}
+\end{figure}
+
+\section{Proofs}
 

### 2015-03-08 sas2015/content/example.tex

@@
-\section{Background and Motivation}
+\section{Motivation}
   \label{sec:MotivatingExample}
 
-In this section, we illustrate our approach using a small motivating example that
-shows how our technique improves the precision of taint analysis.
-A taint analysis is a specialized data-flow analysis for computing how string values
+We illustrate our approach using a small example that
+applies our technique to improve the precision of taint analysis.
+A taint analysis computes how string values
 may flow from ``sources'', which are typically statements that read untrusted input, 
@@
 
-Figure~\ref{list:ccexample} shows a small Java program that we will use to illustrate
-how our technique improves the precision of a simple taint analysis. The program
+Figure~\ref{list:ccexample} shows a small Java program.
+%that we will use to illustrate
+%how our technique improves the precision of a simple taint analysis.
+The program
 declares a class \code{A} with a subclass \code{B},  where \code{A} defines methods 
 \code{foo()} and \code{bar()} that are overridden in \code{B}.  
-%In order to keep the example small and self-contained, 
-It is assumed  that secret values are created by 
-an unspecified function \code{secret()}, which is called in method \code{A.foo()}%
-%  on line~\ref{line:Afoo}
-. Furthermore, it is assumed that any write to the standard output 
-stream via calls \code{System.out.println()} such as the one in method \code{B.bar()} 
+%To keep the 
+%example small and self-contained, it is 
+We assume  that secret values are created by 
+an unspecified function \code{secret()}, which is called in \code{A.foo()} on 
+line~\ref{line:Afoo}. 
+%Furthermore, it is assumed that 
+Any write to standard output 
+%via calls \code{System.out.println()} such as the one in method \code{B.bar()} 
 %on line~\ref{line:Bbar} 
-is a security-sensitive operation. Depending on the number of 
+is assumed to be a sink (e.g. the call to \code{System.out.println()} in code{B.bar()}.
+%a security-sensitive operation.
+Depending on the number of 
 arguments passed to the program, the \code{main()} method of the example program creates 
@@
 
-The specific question that we would like to answer for the example program of
-Figure~\ref{list:ccexample} is the following: Is it possible for the untrusted value 
+%The specific question that we would like to answer for the example program of
+%Figure~\ref{list:ccexample} is the following:
+We wish to answer the following question: Is it possible for the untrusted value 
 that is read on line~\ref{line:Afoo} to flow to the print statement% %on line~\ref{line:Bbar}
 ?
-To determine whether such a flow of tainted data is possible, consider the control-flow
+%To determine whether such a flow of tainted data is possible,
+Consider the control-flow
 supergraph for the example program that is shown in Figure~\ref{fig:examplesupergraph}.
  The nodes in this graph correspond to statements, method entry points (start nodes) and 
-method exit points (end nodes). Note that for each method call, the graph contains a 
+method exit points (end nodes). For each method call, the graph contains a 
 distinct call-node and a return-node. Edges in the graph reflect intraprocedural control flow, 
@@
 
-In the case of our example, the control flow within each of the methods is straightforward and
+In our example, the control flow within each method is straightforward and
 all interesting issues arise from interprocedural control flow. In particular,
-note that, since the variable \code{a} may point to either an \code{A}-object or a \code{B}-object, 
+since the variable \code{a} may point to either an \code{A}-object or a \code{B}-object, 
 the call on line~\ref{line:callfoo} may dispatch to either \code{A.foo()} or to \code{B.foo()},
@@
 
-An IFDS-based data-flow analysis propagates data-flow facts along the edges
+An IFDS analysis propagates data-flow facts along the edges
 of a control flow supergraph such as the one in Figure~\ref{fig:examplesupergraph}. The
-IFDS algorithm was carefully designed to avoid infeasible paths that may arise in the
-presence of multiple calls to the same method. However, in this example all methods are
+IFDS algorithm already avoids flow along infeasible paths from one call site, through a target method,
+and returning to a different call site of the target method.
+However, in this example, all methods are
 called in exactly one place, so IFDS is unable to eliminate data flow along any of the
@@
 As we discussed previously, the calls to \code{foo()} and \code{bar()} may dispatch
-to different implementations of these methods in classes \code{A} and \code{B}, 
-because the variable \code{a} that serves as the receiver for the call may be bound to
- objects of type \code{A} or type \code{B} at run time. 
-However, consider the fact that the methods \code{foo()} and \code{bar()} are invoked
-on \textit{the same object}. This means that the behaviours of the two method calls
+to the implementations in classes \code{A} and \code{B}, 
+because the receiver variable \code{a} may be bound to
+ objects of type \code{A} or \code{B} at run time. 
+However, the methods \code{foo()} and \code{bar()} are invoked
+on \textit{the same object}. Thus the behaviours of the method calls
 are \textit{correlated}: if the call to \code{foo()} dispatches to \code{A.foo()},
-then the call to \code{bar()} must dispatch to \code{A.bar()}, and if the call
-to \code{foo()} dispatches to \code{B.foo()}, then the call to \code{bar()} must 
-dispatch to \code{B.bar()}.  Consequently, paths such as the one highlighted in
-Figure~\ref{fig:examplesupergraph} where the call to \code{foo()} dispatches 
-to \code{A.foo()} and where the call to \code{bar()} dispatches to \code{B.bar()}
+then the call to \code{bar()} must dispatch to \code{A.bar()}, and analogously
+for \code{B.foo()} and \code{B.bar()}.
+Consequently, paths such as the one highlighted in
+Figure~\ref{fig:examplesupergraph} where the calls dispatch to
+\code{A.foo()} and \code{B.bar()}
 are infeasible.
 
-The main contribution of this paper is an algorithm for transforming an IFDS problem 
+Our main contribution is an algorithm for transforming an IFDS problem 
 into an IDE problem that expresses the feasibility of paths
 in light of correlated calls.
-Our approach associates with each edge in an
-interprocedural CFG a function that records the types of 
+The approach associates with each interprocedural CFG edge 
+a function that records the types of 
 variables that are used as the receiver of correlated method calls. Paths that 
@@
 
+\commentout{
 In summary, the example discussed in this section shows how the precision of 
@@
 shown how a false positive reported by a standard IFDS-based algorithm is eliminated.
+}
 While the discussion in this section has focused on the specific problem of taint analysis,
-we would like to emphasize that our technique generally applies to \textit{any}
+our technique generally applies to \textit{any}
 data-flow-analysis problem that can be expressed in the IFDS framework. This includes
@@
 \code{size} and \code{copyToArray}.
-
 The relevant code from \textsf{TraversableOnce} and other related traits is shown

### 2015-03-08 sas2015/content/impl.tex

@@
 \label{lem:equalEq}
-    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
-    \[
+    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,\\
+    $
         \forall r\,.\,I(r) = I'(r) \land U(r) = U'(r)
@@
         \denote{\setpair{I}{U}} = \denote{\setpair{I'}{U'}}.
-    \] 
+    $
 \end{restatable}
@@
 \label{lem:equalMeet}
-    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
-    \[
+    Let $\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
+     =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.
+    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,\\
+    $
         \denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}
@@
         \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}},
-    \]
-    where
-    $\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
-     =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.
+    $.
 \end{restatable}%\mtodo{I added the definition of the meet of two functions.}

### 2015-03-08 sas2015/figures/fig-cc_edge_fn_example.tex

--- 2015-03-05 oopsla/figures/fig-cc_edge_fn_example.tex
@@
-\begin{figure}[h!]%
+%\begin{figure}[h!]%
+\vspace{2cm}
   \centering
@@
     \node [supergraph] (st_main) {\textsf{start}$_{\texttt{main}}$};
-    \node [supergraph] (asgn_a) [below = \dist of st_main.south east, anchor=east] {\texttt{a = args==null\,?}\\\texttt{new\,A()\,:\,new\,B()}};
-    \node [supergraph] (call_foo) [below = \dist of asgn_a.south east, anchor=east] {\textsf{call}$_\texttt{foo}$};
-    \node [supergraph] (return_foo) [below = \dist of call_foo.south east,anchor=east] {\textsf{return}$_\texttt{foo}$\\\texttt{v = a.foo()}};
-    \node [supergraph] (call_bar) [below = \dist of return_foo.south east, anchor=east] {\textsf{call}$_\texttt{bar}$};
-    \node [supergraph] (return_bar) [below = \dist of call_bar.south east, anchor=east] {\textsf{return}$_\texttt{bar}$};
-    \node [supergraph] (end_main) [below = \dist of return_bar.south east, anchor=east] {\textsf{end}$_{\texttt{main}}$};
+    \node [supergraph] (asgn_a) [below = \distt of st_main.south east, anchor=east] {\texttt{a = args==null\,?}\\\texttt{new\,A()\,:\,new\,B()}};
+    \node [supergraph] (call_foo) [below = \distt of asgn_a.south east, anchor=east] {\textsf{call}$_\texttt{foo}$};
+    \node [supergraph] (return_foo) [below = \distt of call_foo.south east,anchor=east] {\textsf{return}$_\texttt{foo}$\\\texttt{v = a.foo()}};
+    \node [supergraph] (call_bar) [below = \distt of return_foo.south east, anchor=east] {\textsf{call}$_\texttt{bar}$};
+    \node [supergraph] (return_bar) [below = \distt of call_bar.south east, anchor=east] {\textsf{return}$_\texttt{bar}$};
+    \node [supergraph] (end_main) [below = \distt of return_bar.south east, anchor=east] {\textsf{end}$_{\texttt{main}}$};
 
@@
 %A.foo method nodes
-    \node [supergraph_y] (st_a_foo) [right = 6*\dist of st_main] {\textsf{start}$_{\texttt{A.foo}}$};
-    \node [supergraph_y] (return_secret) [below = \dist of st_a_foo.south west, anchor=west] {\texttt{return secret()}};
-    \node [supergraph_y] (end_a_foo) [below = \dist of return_secret.south west,anchor = west] {\textsf{end}$_\texttt{A.foo}$};
+    \node [supergraph_y] (st_a_foo) [right = 6*\disth of st_main] {\textsf{start}$_{\texttt{A.foo}}$};
+    \node [supergraph_y] (return_secret) [below = \distt of st_a_foo.south west, anchor=west] {\texttt{return secret()}};
+    \node [supergraph_y] (end_a_foo) [below = \distt of return_secret.south west,anchor = west] {\textsf{end}$_\texttt{A.foo}$};
 
@@
 %A.bar method nodes
-    \node [supergraph_y] (st_a_bar) [right = 6*\dist of st_a_foo] {\textsf{start}$_{\texttt{A.bar}}$};
-    \node [supergraph_y] (end_a_bar) [below = \dist of st_a_bar.south west,anchor = west] {\textsf{end}$_\texttt{A.bar}$};
+    \node [supergraph_y] (st_a_bar) [right = 6*\disth of st_a_foo] {\textsf{start}$_{\texttt{A.bar}}$};
+    \node [supergraph_y] (end_a_bar) [below = \distt of st_a_bar.south west,anchor = west] {\textsf{end}$_\texttt{A.bar}$};
 
@@
 %B.foo method nodes
-    \node [supergraph_f] (st_b_foo) [right = 6*\dist of call_bar] {\textsf{start}$_{\texttt{B.foo}}$};
-    \node [supergraph_f] (return_not_secret) [below = \dist of st_b_foo.south west, anchor=west] {\texttt{return "not secret"}};
-    \node [supergraph_f] (end_b_foo) [below = \dist of return_not_secret.south west,anchor = west] {\textsf{end}$_\texttt{B.foo}$};
+    \node [supergraph_f] (st_b_foo) [right = 6*\disth of call_bar] {\textsf{start}$_{\texttt{B.foo}}$};
+    \node [supergraph_f] (return_not_secret) [below = \distt of st_b_foo.south west, anchor=west] {\texttt{return "not secret"}};
+    \node [supergraph_f] (end_b_foo) [below = \distt of return_not_secret.south west,anchor = west] {\textsf{end}$_\texttt{B.foo}$};
 
@@
 %B.bar method nodes
-    \node [supergraph_f] (st_b_bar) [right = 6*\dist of st_b_foo] {\textsf{start}$_{\texttt{B.bar}}$};
-    \node [supergraph_f] (print) [below = \dist of st_b_bar.south west,anchor = west] {\texttt{print(s)}};
-    \node [supergraph_f] (end_b_bar) [below = \dist of print.south west,anchor = west] {\textsf{end}$_\texttt{B.bar}$};
+    \node [supergraph_f] (st_b_bar) [right = 6*\disth of st_b_foo] {\textsf{start}$_{\texttt{B.bar}}$};
+    \node [supergraph_f] (print) [below = \distt of st_b_bar.south west,anchor = west] {\texttt{print(s)}};
+    \node [supergraph_f] (end_b_bar) [below = \distt of print.south west,anchor = west] {\textsf{end}$_\texttt{B.bar}$};
 
@@
     \path[->,dashed, ultra thick](call_bar_v) edge [out=20,in=160,color=lightsalmonpink] node[arrowtext,above right=-.4cm and .4cm,rotate=-10]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$} (st_b_bar_s);
-    \path[->,dashed](end_b_bar_z) edge [out=210,in=-40,color=lightsalmonpink] (return_bar_z);    
+    \path[->,dashed](end_b_bar_z) edge [out=190,in=-40,color=lightsalmonpink] (return_bar_z);    
 }
 \end{tikzpicture}
+\vspace{-27mm}
 \caption[An example program demonstrating correlated-call edge functions on the $\mathbf0$-node path for Listing~\ref{list:ccexample}]{An example program demonstrating correlated-call edge functions on the $\mathbf0$-node path for Listing~\ref{list:ccexample}.
@@
   \label{fig:cc_edgefn_example}%  
-  \end{figure}
+%  \end{figure}

### 2015-03-08 sas2015/content/appendix.tex
applying ondrej's corrections

--- 2015-03-08 sas2015/content/appendix.tex
@@
 \section*{Appendix}
-In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}, the table illustrating frequencies of correlated calls from Section~\ref{}, and the code discussed in Section~\ref{sec:collex}.
+In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}, the table illustrating frequencies of correlated calls from Section~\ref{sec:occur}, and the code discussed in Section~\ref{sec:collex}.
 
-\subsection*{Representation of Micro Functions}
+\subsection*{Correlated Calls Occurrences}
+Table~\ref{tab:dacapostat} shows how often correlated calls occur in practice. The number of all call sites in a program is denoted as $C$. 
+Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. The~number of classes~$T$ and the number of lines of code are shown in the last two columns.
+The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
+The next three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
+In this context, we deem a call site to be polymorphic if its statically computed call graph
+contains edges from the call site to multiple target methods.
+We deem a call site to be a correlated call site if it is polymorphic and there is
+at least one other polymorphic call site on the same receiver.
+\input{tables/stats}
+
+\subsection*{\code{TraversableOnce} Trait from Scala Standard Library}
+Figure~\ref{fig:traversableonce} presents the code from Scala's \code{TraversableOnce} trait discussed in Section~ref{sec:collex}.
+
+\begin{figure}
+\inputMinted{scala}{TraversableOnce.scala}
+\caption{Relevant code from \textsf{TraversableOnce} and related traits.}
+\label{fig:traversableonce}
+\end{figure}
+
+\subsection*{Proofs}
+
+\subsubsection*{Representation of Micro Functions}
 We start by presenting the proofs to the lemmas about the representation of micro functions.
@@
 
-\subsection*{Soundness and Precision}
+\subsubsection*{Soundness and Precision}
 
@@
 
-\subsection*{Correlated-Call Receivers}
+\subsubsection*{Correlated-Call Receivers}
 We will now present the proof for Lemma~\ref{lem:onlycorrrec} which shows that in a correlated-calls analysis, it is enough to consider only correlated-call receivers~$\rcc$.
@@
 \end{proof}
-
-\begin{figure}
-\inputMinted{scala}{TraversableOnce.scala}
-\caption{Relevant code from \textsf{TraversableOnce} and related traits.}
-\label{fig:traversableonce}
-\end{figure}
-
-\subsection{Correlated Calls Occurrences}
-Table~\ref{tab:dacapostat} shows how often correlated calls occur in practice. The number of all call sites in a program is denoted as $C$. 
-Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. The~number of classes~$T$ and the number of lines of code are shown in the last two columns.
-The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
-The next three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
-In this context, we deem a call site to be polymorphic if its statically computed call graph
-contains edges from the call site to multiple target methods.
-We deem a call site to be a correlated call site if it is polymorphic and there is
-at least one other polymorphic call site on the same receiver.
-\input{tables/stats}

### 2015-03-08 sas2015/content/background.tex
removing some old comments
applying ondrej's corrections

@@
 followed by a \textit{return node} in the CFG.
-%\end{mdelete}
-%and edges represent transfer of control between the instructions during an execution of the program. 
-%A control-flow graph has a unique start node, $\startmain$, which is the node corresponding to the program entrypoint.
-%An \textit{intraprocedural} path is a path in a control-flow graph whose nodes are in the same procedure.
-By contrast, an \textit{interprocedural path} is one that contains nodes from different procedures.
 The \textit{control-flow supergraph} of a program contains the CFGs of all of the procedures as
@@
 may be called from $c$, and an \textit{end-to-return} edge from the end node of the procedure back to the call instruction.
-%\otodo{do we really need to extra "return nodes" that the IFDS/IDE papers add?}
-%is a control-flow graph
-%in which each procedure $p$ is augmented with an additional \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$, and for each call $c_q$ to a procedure $q$, there is a \textit{call node} \textsf{call}$_{c_q}$ and subsequent \textit{return node} \textsf{return}$_{c_q}$.
-
-%A control-flow supergraph allows us to model the control flow in interprocedural paths.
- %The flow from the caller to the callee is represented using an edge \[(\textsf{call}_{c_q},\,\textsf{start}_q)\,.\] The control flow from the callee back to the caller goes through an edge \[(\textsf{end}_q,\,\textsf{return}_{c_q})\,.\]
 
@@
 to dispatch to $f$: $\tau(s,f) = \{t\mid \textsf{lookup}(s,t)=f\}$.
-
-%\otodo{do we ever use $\src$ and $\target$?}
-%We denote the source and end nodes of a graph edge $e$ as $\src e$ and $\target e$.
-
-%A \textit{flow-sensitive} data-flow analysis is one that takes the order of program instructions into account.
 
@@
 that has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
-%\mtodo{ The four references take away space in the References section. Remove some of them?  }
 The IFDS framework is an instance of the \textit{functional approach} to data-flow analysis~\cite{pnueli1981two}
@@
 \]
-\begin{floatingfigure}[lrp]{3.5cm}
-\input{figures/ex1minigraph} 
-\end{floatingfigure}
 \begin{example}\label{ex:flowfun}
@@
     R_f=\{(\mathbf0,\,\mathbf0),\,(\mathbf0,\,u),\,(w,\,w)\}
-$, which is depicted on the graph below.
+$, which is depicted in Figure~\ref{fig:minigraph1}.
 \end{example}
@@
 paths in the resulting graph.
+  \input{figures/ex2minigraph}
 
@@
     $
-  as illustrated in the graphs below.
-\begin{floatingfigure}[lrp]{3.5cm}
-  \input{figures/ex2minigraph}
-\end{floatingfigure}
+  as illustrated in Figure~\ref{fig:minigraph2}.
 \end{example}

### 2015-03-08 sas2015/content/impl.tex
applying ondrej's corrections

--- 2015-03-08 sas2015/content/impl.tex
@@
 
-Finally, the correlated-calls transformation is defined as\\
-    $\transCC_S((G^\#))=\left(G^\#,\,\lcc_S,\,\ccedgefn S\right)$.
+Finally, the correlated-calls transformation is defined as
+    \begin{equation}
+      \transCC_S((G^\#))=\left(G^\#,\,\lcc_S,\,\ccedgefn S\right).
+    \end{equation}
 
@@
     For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
-    \[
+    \begin{equation}
         \forall r\,.\,I(r) = I'(r) \land U(r) = U'(r)
@@
         \denote{\setpair{I}{U}} = \denote{\setpair{I'}{U'}}.
-    \] 
+    \end{equation}
 \end{restatable}
@@
 
-The composition of two micro-function representations is defined as follows:
-$\setpair{I}{U} \circ \setpair{I'}{U'} = \setpair{\lambda r\,.\,(I(r) \cap I'(r))\cup U(r)}{\lambda r\,.\,(I(r)\cap U'(r))\cup U(r)}$.
 The following lemma shows that this implementation corresponds to the composition
-of the denoted functions:
+of the denoted functions.
 \begin{restatable}{lemma}{equalComp}\label{lem:equalComp}
@@
         = 
-        \denote{\setpair{I}{U}} \circ \denote{\setpair{I'}{U'}}.
+        \denote{\setpair{I}{U}} \circ \denote{\setpair{I'}{U'}},
     \]
+    where the composition of two micro-function representations is defined as follows:
+$$\setpair{I}{U} \circ \setpair{I'}{U'} = \setpair{\lambda r\,.\,(I(r) \cap I'(r))\cup U(r)}{\lambda r\,.\,(I(r)\cap U'(r))\cup U(r)}.$$
 \end{restatable}
 
-The meet of two micro-function representations is defined as follows:
-$\setpair{I}{U} \sqcap \setpair{I'}{U'} = \setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}$.
 The following lemma shows that this implementation corresponds to the meet
@@
 \label{lem:equalMeet}
+    Let $\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
+     =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.
     For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
-    \[
+    \begin{equation}
         \denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}
@@
         \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}},
-    \]
-    where
-    $\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
-     =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.
-\end{restatable}%\mtodo{I added the definition of the meet of two functions.}
+    \end{equation}
+    where the meet of two micro-function representations is defined as follows:
+$$\setpair{I}{U} \sqcap \setpair{I'}{U'} = \setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}.$$
+\end{restatable}
 
@@
     For an IFDS problem $P$ and all ${n\in N^*}$,
-    \begin{equation}\label{eq:correct}
+    \begin{equation}
       \backCC\left(\resultIDE(\transCC_R(P))\right)(n)

### 2015-03-09 sas2015/content/concl.tex
squishing (mainly) of introduction

@@
 preliminary experiments with our prototype implementation. Full proof
-details are available as supplemental materials with this submission,
+details are available in the Appendix,
 and we plan to submit our implementation and experimental data to the

### 2015-03-09 sas2015/content/example.tex
applying ondrej's corrections
squishing (mainly) of introduction

@@
 
-\subsection{Occurrences of Correlated Calls}\vspace{-.5mm}
+\subsection{Occurrences of Correlated Calls}\label{sec:occur}\vspace{-.5mm}
 How often do correlated calls occur in practice?
-To assess the benefit of the correlated-calls analysis, we counted the number of correlated calls that occur in programs of the Dacapo benchmarks~\cite{blackburn2006dacapo}, using the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
+To assess the benefit of the correlated-calls analysis, we counted the number of correlated calls that occur in programs of the Dacapo benchmarks~\cite{blackburn2006dacapo}, using the WALA framework~\cite{fink2012wala}.
 Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis.

### 2015-03-09 sas2015/content/impl.tex
squishing (mainly) of introduction

@@
 \end{restatable}
-The proofs of all of the lemmas and theorems in the paper are provided in the supplemental
-material submitted with the paper.
+The proofs of all of the lemmas and theorems are in the Appendix.
 
@@
 corresponding Java bytecode.
-To retrieve information about an input program, such as its control-flow supergraph or the set of receivers and their types, we used the WALA framework for static analysis~\cite{fink2012wala}.
+To retrieve information about an input program, such as its control-flow supergraph or the set of receivers and their types, we used the WALA framework~\cite{fink2012wala}.
 Since WALA currently only contains an implementation of IFDS, we implemented IDE from scratch.

### 2015-03-09 sas2015/content/intro.tex
tweaks
squishing (mainly) of introduction

@@
 
+\commentout{
 Data-flow analysis computes an approximation of how values may flow  
@@
 computed along different paths should be merged when the paths join.
+}
 
-Since a CFG is an over-approximation of the possible flows 
-of control in concrete executions of a program, it may contain \textit{infeasible} 
+%Since a CFG is an over-approximation of the possible flows 
+A control-flow graph (CFG) is an over-approximation of the possible flows 
+of control in concrete executions of a program. It may contain \textit{infeasible} 
 paths that cannot occur at runtime. The precision of a data-flow analysis algorithm
-depends critically on its ability to detect and disregard such infeasible paths.
-The popular \textit{Interprocedural Finite Distributive Subset} (IFDS) algorithm 
-by  Reps, Horwitz, and Sagiv~\cite{reps1995precise} is a general data-flow analysis
-algorithm for computing solutions to standard finite distributive data-flow problems such 
-as reaching definitions, available expressions, and taint analysis.
-A distinguishing 
-characteristic of IFDS is that it avoids infeasible interprocedural paths in which calls 
-and returns to/from functions are not properly matched. Sagiv, Reps, and Horwitz
-also presented the \textit{Interprocedural Distributive Environment} (IDE) algorithm
-\cite{sagiv1996precise} that similarly only considers properly matched call/return
-edges, but that supports a broader range of data-flow problems by expanding the 
-domain of flow functions to \textit{environments} that go beyond the data-flow facts 
-considered by IFDS.
+depends on its ability to detect and disregard such infeasible paths.
+The \textit{Interprocedural Finite Distributive Subset} (IFDS) algorithm~\cite{reps1995precise}
+is one general data-flow analysis algorithm that 
+%by  Reps, Horwitz, and Sagiv
+%is a general data-flow analysis
+%algorithm
+%for computing solutions to finite distributive data-flow problems such 
+%that can be instantiated to solve problems such
+%as reaching definitions, available expressions, and taint analysis.
+%A distinguishing 
+%characteristic of IFDS is that it
+avoids infeasible interprocedural paths in which calls 
+and returns to/from functions are not properly matched. %Sagiv, Reps, and Horwitz
+%also presented
+The \textit{Interprocedural Distributive Environment} (IDE) algorithm~\cite{sagiv1996precise}
+has the same property, but
+%that similarly only considers properly matched call/return
+%edges, but that 
+supports a broader range of data-flow problems.
+%by expanding the 
+%domain of flow functions to \textit{environments} that go beyond the data-flow facts 
+%considered by IFDS.
 
@@
 %\mtodo{Should we define the term ``receiver''?}
-In such cases, if the
-method calls are polymorphic (i.e., if they dispatch to different method definitions 
-depending on the type of the receiver expression at run time), then their dispatch 
-behaviours will be correlated. A recent paper~\cite{DBLP:journals/scp/Tip15} identified
-this problem but did not present a concrete solution or algorithm, and we are not aware 
-of any existing data-flow analysis that is capable of avoiding infeasible paths that arise 
-in the presence of correlated method calls.
+%In such cases,
+If the
+method calls are polymorphic
+(i.e. the method invoked depends on the run-time type of the receiver),
+%(i.e., if they dispatch to different method definitions 
+%depending on the type of the receiver expression at run time),
+then their dispatch 
+behaviours are correlated, and some of the paths between them are infeasible. A recent paper~\cite{DBLP:journals/scp/Tip15} made this observation
+but did not present any concrete algorithm to take advantage of it.
+%, and we are not aware 
+%of any existing data-flow analysis that is capable of avoiding infeasible paths that arise 
+%in the presence of correlated method calls.
 % (see Section~\ref{sec:Related} for a discussion
@@
 
-The approach taken in our work is to transform a standard IFDS problem into an
+%The approach taken in our work is to 
+Our approach transforms an IFDS problem into an
 IDE problem that precisely accounts for infeasible paths due to correlated calls. 
 The results of this IDE problem can be mapped back to the data-flow domain of the 
-original IFDS problem.
-
-We present a formalization of the transformation and prove its correctness
-as follows. 
-First, we derive an IDE problem that is equivalent to the original IFDS problem,
-as described by Reps et al.~\cite{sagiv1996precise}.
-Solving this ``Equivalence-IDE Problem'' with the IDE algorithm yields a result that
-is equivalent to the one obtained by applying the IFDS algorithm to the original IFDS problem.
-Then, we derive a ``Correlated-Calls 
-IDE Problem'' from the original IFDS problem and show 
-that the solution to this problem, when converted to an IFDS result, is more precise
-than the original IFDS result.
-We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
+original IFDS problem, but are more precise than the results of directly applying
+the IFDS algorithm to the original problem.
+%
+We present a formalization of the transformation and prove its correctness:
+specifically, we prove it still soundly considers all paths that are feasible,
+and that it avoids flow along all paths that are infeasible due to
+correlated calls.
+%as follows. 
+%First, we derive an IDE problem that is equivalent to the original IFDS problem,
+%as described by Reps et al.~\cite{sagiv1996precise}.
+%Solving this ``Equivalence-IDE Problem'' with the IDE algorithm yields a result that
+%is equivalent to the one obtained by applying the IFDS algorithm to the original IFDS problem.
+%Then, we derive a ``Correlated-Calls 
+%IDE Problem'' from the original IFDS problem and show 
+%that the solution to this problem, when converted to an IFDS result, is more precise
+%than the original IFDS result.
+%We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
 %This is illustrated schematically
@@
   Detailed proofs of our lemmas and theorems can be found in
-  the supplemental materials that are included with this submission.
+  the appendix.
 }.

### 2015-03-09 sas2015/content/impl.tex
text squeezing pass througth section 4

@@
 \section{Correlated Calls Analysis}\label{sec:cca}
-The correlated-calls analysis is defined as a transformation from an arbitrary IFDS problem to a corresponding IDE problem.
+%The correlated-calls analysis is a transformation from an arbitrary IFDS problem to a corresponding IDE problem.
 The solution of this IDE problem can be converted to a solution of the original IFDS problem.
@@
 %Let $P=(G^\#)$ be an IFDS problem and $Q=(G^\#,\,\edgefn)$ an IDE problem obtained by a conversion from $P$.
-Let $G^\#$ be the exploded supergraph of an IFDS problem. A \emph{transformation}
+Let $G^\#$ be the exploded supergraph of an arbitrary IFDS problem. A \emph{transformation}
 $\mathcal T:\ (G^\#)\to (G^\#,\,L,\,\edgefn)$
-converts it into an equivalent IDE problem. We consider two transformations:
-\begin{itemize}
-    \item an \textit{equivalence transformation} $\transEq$ (pronounced ``t-equiv'') that generates IDE problems with the same precision as the original IFDS problem, and
-    \item a \textit{correlated-calls transformation} $\transCC$ (pronounced ``t-c-c'') that generates IDE problems that exclude infeasible paths.
-\end{itemize}
+converts the IFDS problem into an IDE problem.
+We consider two IFDS-to-IDE transformations: an \textit{equivalence transformation} $\transEq$ (pronounced ``t-equiv'') and
+a \textit{correlated-calls transformation} $\transCC$ (pronounced ``t-c-c'').
 Both transformations keep the exploded supergraph $G^\#$ the same, and only generate different edge functions.
+The solution of the IDE problem
+can be mapped back to an IFDS solution.
+If the equivalence transformation was used, then this solution is identical to the
+solution that would be computed by the IFDS algorithm for the original IFDS problem.
+If the correlated-calls transformation was used, then this solution is more precise
+because it excludes flow along infeasible paths due to correlated calls.
+
 %In each case we also show how to convert the result of the generated IDE problem to a result of the original IFDS problem.
@@
 %\mtodo{``the identity function'' or is it okay ot just say ``the identity''?}.
+\commentout{
 The equivalence transformation is thus defined as:
   $\transEq((G^\#))=(G^\#,\,L^\equiv,\,\mathsf{EdgeFn}^\equiv)$.
+}
 
@@
 Along a $\mathbf0$-edge, the micro function is the identity. 
-All other functions can be described with $\varepsilon_S$.
+%All other functions can be described with $\varepsilon_S$.
 On a ``diagonal'' edge from $\mathbf0$ to a non-$\mathbf0$ fact that corresponds
-to some data-flow fact becoming reachable, $\varepsilon_S(e)$ is applied to the initial
-map $\botcc$ that conservatively allows every receiver to point to an object of any type.
+to some data-flow fact becoming reachable, $\varepsilon_S(e)$ is applied to
+%the initial map
+$\botcc$ that maps every receiver to an object of every possible type.
+%conservatively allows every receiver to point to an object of any type.
 On all other edges, $\varepsilon_S(e)$ is applied to the existing map before the edge.
@@
   Consider the program from Figure~\ref{list:ccexample}, whose exploded supergraph appeared in Figure~\ref{fig:cc_edgefn_example}.
-
+%
   Returning a secret value in method \code{A.foo} creates a ``diagonal'' edge from the $\mathbf0$-fact to the method's return value $r$. 
-  The diagonal edge is labeled with the micro function $\lambda m\,.\,\botcc$. Thus, at the end node of the method, every receiver is mapped to the set of all types~$\bot_T$.
-
-On the end-return edge from \code{A.foo} to \code{main}, the set of types for the receiver \code{a} is restricted by the micro function $\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code A\}]$ on the edge corresponding to the assignment of the return value $r$ to \code v.
-
-Similarly, on the call-start edge from \code{main} to \code{B.bar}, the possible types
-of the receiver \code{a} are further restricted by the micro-function
+  The diagonal edge is labeled with $\lambda m\,.\,\botcc$, so every receiver is mapped to the set of all types~$\bot_T$.
+%  
+On the end-return edge from \code{A.foo} to \code{main}, the set of types of \code{a} is restricted by the micro function $\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code A\}]$ corresponding to the assignment of the return value $r$ to \code v.
+%
+%Similarly,
+On the call-start edge from \code{main} to \code{B.bar}, the possible types
+of \code{a} are further restricted by the micro-function
 $\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code B\}]$.
 on the edge that passes the argument \code{v} to the parameter \code{s}.
-
 The composition of these micro functions results in the empty set as the possible
-types of the receiver \code{a}, indicating that this data-flow path that would
-result in an information leak is actually infeasible.
+types \code{a}, indicating that this
+%data-flow
+path 
+%that would
+%result in an information leak 
+is 
+%actually
+infeasible.
 \end{example}
@@
 
+\commentout{
 Finally, the correlated-calls transformation is defined as
@@
     \end{equation}
+}
 
@@
 
-For each program point $n$, the result of an IFDS analysis gives
-a set of facts $d$ that may be reached at $n$. The result of an IDE analysis
-pairs each such fact~$d$ with a lattice element $\ell$. Formally,
-for an IFDS problem $P$, the result $\resultIFDS$ has type
-$N^* \to D$.
-Similarly, for an IDE problem $Q$, the result $\resultIDE(Q)$
-has type $N \to (D \to L)$.
+An IFDS solution $\resultIFDS$ has type $N^* \to D$: it maps each program point $n$
+to a set of facts $d$ that may be reached at $n$.
+\otodo{This seems wrong: Why is it $N^*$ for IFDS and $N$ for IDE? And shouldn't
+    it be $N \to 2^D$, since you get a set of $d$'s?}
+An IDE solution $\resultIDE$
+pairs each such fact~$d$ with a lattice element $\ell$, so its type
+is $N \to (D \to L)$.
 
-Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
+%For each program point $n$, the result of an IFDS analysis gives
+%a set of facts $d$ that may be reached at $n$. The result of an IDE analysis
+%pairs each such fact~$d$ with a lattice element $\ell$. Formally,
+%for an IFDS problem $P$, the result $\resultIFDS$ has type
+%$N^* \to D$.
+%Similarly, for an IDE problem $Q$, the result $\resultIDE(Q)$
+%has type $N \to (D \to L)$.
+
+In the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
 and $\top$ means unreachable.
-Therefore, a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
-is converted to an IFDS result as follows:
-\begin{equation}\label{eq:transEqDef}
-  \backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
-\end{equation}
-
+Therefore, an IDE solution $\rho$ computed using $\transEq$ is converted to
+and IFDS solution as:
+  $\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}$.
+%a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
+%is converted to an IFDS result as follows:
+%\begin{equation}\label{eq:transEqDef}
+  %\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
+%\end{equation}
+%
 %\otodo{I don't understand this comment. What does it mean?}
-
+%
 In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
 to the empty set of possible types means that the corresponding data-flow path is
-infeasible. Therefore, a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
-converted to an IFDS result as follows:
-\begin{equation}\label{eq:transCcDef}
-    \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.
-\end{equation}
+infeasible. Therefore, an IDE solution $\rho$ computed using
+$\transCC_S$ is converted to an IFDS solution as:
+$\backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}$.
+
+%a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
+%converted to an IFDS result as follows:
+%\begin{equation}\label{eq:transCcDef}
+    %\backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.
+%\end{equation}
 %\otodo{In Equation (5), I changed $\rho(n)(d)$ to $\rho(n)(d)(r)$, because I think
@@
 Conceptually, micro-functions are functions from $L$ to $L$, where $L$
-is the IDE lattice, either $L^\equiv$ or $\lcc$ in our context. However,
-the IDE algorithm requires an efficient representation of micro-functions.
+is the IDE lattice, either $L^\equiv$ or $\lcc$ in our context. 
+The IDE algorithm requires an efficient representation of micro-functions.
 The chosen representation needs to support the basic micro-functions that
-we presented in Section~\ref{seq:transIfdsIde}. The representation must also
+we presented in Section~\ref{seq:transIfdsIde}, and it must
 support function application, comparison, and be closed under function composition
@@
 types $I(r)$ and $U(r)$, where $U(r)$ is required to be a subset of $I(r)$. 
-Intuitively, the micro-function takes the existing set of possible types of the
-receiver $r$, intersects it with $I(r)$, then unions it with $U(r)$.
 We use the notation
 $\setpair{I}{U}$ to represent such a map, and $I(r)$ and $U(r)$ to look up the
-sets corresponding to a particular receiver $r$. We define the meaning $\denote{\setpair{I}{U}}$
-of a representation $\setpair{I}{U}$ as follows: $\denote{\setpair{I}{U}} = \lambda m\,.\,\lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
-In words, the micro-function represented by $\setpair{I}{U}$ takes an existing map $m$
-from receivers to sets of types, and returns a map that maps each receiver $r$ to
-the set $m(r)$ given by the original map $m$ intersected with $I(r)$ and unioned
-with $U(r)$.
+sets corresponding to a particular receiver $r$.
+The micro-function takes the existing set of possible types of the
+receiver $r$, intersects it with $I(r)$, then unions it with $U(r)$:
+$\denote{\setpair{I}{U}} = \lambda m\,.\,\lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
+
+%We define the meaning $\denote{\setpair{I}{U}}$
+%of a representation $\setpair{I}{U}$ as follows: 
+%In words, the micro-function represented by $\setpair{I}{U}$ takes an existing map $m$
+%from receivers to sets of types, and returns a map that maps each receiver $r$ to
+%the set $m(r)$ given by the original map $m$ intersected with $I(r)$ and unioned
+%with $U(r)$.
 
 All of the basic micro-functions defined in Definition~\ref{def:microfn} can be expressed
-in this representation.
+in this representation. The following lemmas show how function comparison, composition, and meet can be implemented using basic set operations
+on $I$ and $U$.
+The proofs of all of the lemmas and theorems are in the Appendix.
 
-The implementation of function application follows directly from the definition of
-the representation: $\setpair{I}{U}(m) = \lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
+%The implementation of function application follows directly from the definition of
+%the representation: $\setpair{I}{U}(m) = \lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
 %\mtodo{Should this be the denotation of $\setpair IU$?}
@@
 
-To compare two micro-functions for equality, it suffices to compare the corresponding
-sets $I(r)$ and $U(r)$ for all receivers $r$. The following lemma shows that this
-implementation of comparison corresponds to equality of the represented micro-functions:
+%To compare two micro-functions for equality, it suffices to compare the corresponding
+%sets $I(r)$ and $U(r)$ for all receivers $r$. The following lemma shows that this
+%implementation of comparison corresponds to equality of the represented micro-functions:
 \begin{restatable}{lemma}{equalEq}
@@
 \end{restatable}
-The proofs of all of the lemmas and theorems are in the Appendix.
 
-The following lemma shows that this implementation corresponds to the composition
-of the denoted functions.
+%The following lemma shows that this implementation corresponds to the composition
+%of the denoted functions.
 \begin{restatable}{lemma}{equalComp}\label{lem:equalComp}
@@
 
-The following lemma shows that this implementation corresponds to the meet
-of the denoted functions:
+%The following lemma shows that this implementation corresponds to the meet
+%of the denoted functions:
 \begin{restatable}{lemma}{equalMeet}\label{lem:equalMeet}
@@
 
-In the following lemma we show that our analysis is sound, i.e. that the result of an IDE problem obtained through a correlated-calls transformation removes only facts that occur on infeasible paths.
+The following lemma shows that our analysis is sound, i.e. 
+that the resulting IDE problem still considers all data-flow
+paths that are actually feasible.
+%that the result of an IDE problem obtained through a correlated-calls transformation removes only facts that occur on infeasible paths.
 
@@
 
-We next show that the result of an IDE problem obtained through a correlated-calls transformation is a subset of the original IFDS result.
+We also show that the result of an IDE problem obtained through a correlated-calls transformation is a subset of the original IFDS result.
 
@@
 \begin{definition}
-Let $c_1$ and $c_2$ be two call sites on a receiver $r\in R$.
-  If both call sites are polymorphic, then we say that $r$ is a \textit{correlated-call receiver}.
+    If $r\in R$ is the receiver of at least two polymorphic
+    call sites, then we call $r$ a \textit{correlated-call receiver}, and we define $\rcc$ as the set of all
+  such receivers.
 \end{definition}
-In other words, a correlated-call receiver is a receiver that has at least two polymorphic call invocations.
-We will denote the set of correlated-call receivers as $\rcc$.
+%In other words, a correlated-call receiver is a receiver that has at least two polymorphic call invocations.
+%We will denote the set of correlated-call receivers as $\rcc$.
 
-We will describe a ``reduced'' correlated-calls transformation in which we only consider receivers from $\rcc$ and ignore other receivers of $R$.
-We will show that IDE problems obtained through ordinary and reduced correlated-calls transformations yield the same results.
-In other words, we show that if a correlated-calls analysis considers only correlated-call receivers, no precision is lost.
+We will show that it is sufficient for the correlated-calls
+micro-functions to be defined only on correlated-call receivers.
+%We will describe a ``reduced'' correlated-calls transformation in which we only consider receivers from $\rcc$ and ignore other receivers of $R$.
+Specifically, a ``reduced'' correlated-calls transformation that
+considers only correlated-call receivers in the micro-functions
+yields the same solution as the full correlated-calls transformation
+(i.e. no precision is lost).
+%We will show that IDE problems obtained through ordinary and reduced correlated-calls transformations yield the same results.
+%In other words, we show that if a correlated-calls analysis considers only correlated-call receivers, no precision is lost.
 
@@
 
+\commentout{
 To summarize, Lemma~\ref{lem:sound} shows that the result of a correlated-calls analysis is sound since it overapproximates the data flow of all possible concrete execution paths.
@@
 Finally, we showed in Lemma~\ref{lem:onlycorrrec} that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result that is obtained when considering all receivers $R$.
+}
 
@@
 types. Therefore, the overall worst-case cost of the correlated-calls IDE analysis
-is $O(ED^3\rcc T)$.
+is $O(ED^3\rcc T)$. Note that in practice, $\rcc$ is much smaller
+than $R$, so Lemma~\ref{lem:onlycorrrec} is significant for 
+performance.
 
-Specifically, the complexity proof for the IDE algorithm requires the implementation of the micro-functions
-to be \textit{efficient} according to the following criteria:
-\begin{enumerate}
-	\item There is a representation for the identity and top functions.
-  \item The representation is closed under the meet and composition operations.
-  \item The micro functions form a finite-height lattice.
-  \item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
-  \item There is a constant bound on the storage space for a micro function representation.
-\end{enumerate}
-We prove these conditions with the following lemma:
+Specifically, the complexity proof for the IDE algorithm requires
+the implementation of the micro-functions to be \textit{efficient}
+according to a list of specific criteria. Our micro-function
+implementation does satisfy the criteria:
+
+\otodo{Give the list of criteria explicitly in the proof in the appendix.}
+%\begin{enumerate}
+	%\item There is a representation for the identity and top functions.
+  %\item The representation is closed under the meet and composition operations.
+  %\item The micro functions form a finite-height lattice.
+  %\item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
+  %\item There is a constant bound on the storage space for a micro function representation.
+%\end{enumerate}
+%We prove these conditions with the following lemma:
 \begin{restatable}{lemma}{efficient}\label{lem:efficient}
@@
 \subsection{Implementation of the Correlated-Calls Analysis}
-The correlated-calls analysis was implemented in the Scala programming language~\cite{odersky2004overview}. 
-The input programs that we analyzed were written in Java. Our implementation analyzed the
-corresponding Java bytecode.
-To retrieve information about an input program, such as its control-flow supergraph or the set of receivers and their types, we used the WALA framework~\cite{fink2012wala}.
-Since WALA currently only contains an implementation of IFDS, we implemented IDE from scratch.
-Instead of using WALA's IFDS implementation, to run an IFDS problem, we converted it to an IDE problem and used our own IDE solver.
+We implemented the correlated-calls analysis in Scala~\cite{odersky2004overview}. 
+Our implementation analyzed Java bytecode from input programs written
+in Java.
+%The input programs that we analyzed were written in Java. Our implementation analyzed the
+%corresponding Java bytecode.
+We used WALA~\cite{fink2012wala}
+to retrieve information about an input program, such as its control-flow supergraph and the set of receivers and their types.
+Since WALA does contain an implementation of the IDE algorithm,
+we implemented it from scratch.
+%currently only contains an implementation of IFDS, we implemented IDE from scratch.
+We will submit our implementation to the artifact evaluation committee, and we are working on contributing it officially to WALA.
+% Instead of using WALA's IFDS implementation, to run an IFDS problem, we converted it to an IDE problem and used our own IDE solver.
 
@@
 
+\commentout{
 The artifact of our implementation can be used to solve any IFDS problem.
 In the presence of correlated calls, the result of the correlated-calls analysis can be more precise than the result obtained with an IFDS solver.
+}

### 2015-03-09 sas2015/content/example.tex
squishing

@@
 all interesting issues arise from interprocedural control flow. In particular,
-since the variable \code{a} may point to either an \code{A}-object or a \code{B}-object, 
+since  \code{a} may point to either an \code{A}-object or a \code{B}-object, 
 the call on line~\ref{line:callfoo} may dispatch to either \code{A.foo()} or to \code{B.foo()},
-and this is reflected by edges  
+as is reflected by edges  
   from the node labeled $\highlight{\code{call}_\code{foo}}{greyblue}$ to the nodes labeled

### 2015-03-09 sas2015/content/appendix.tex
ondrejs comments

@@
 
+\subsubsection*{Efficiency}
+We will next introduce the complexity proof for the correlated-calls algorithm.
+To satisfy the complexity requirements of the IDE algorithm, we need to provide
+an implementation of the IDE lattice and micro-functions that satisfy the following
+list of criteria~\cite{sagiv1996precise}:
+\begin{enumerate}
+	\item There is a representation for the identity and top functions.
+  \item The representation is closed under the meet and composition operations.
+  \item The micro functions form a finite-height lattice.
+  \item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
+  \item There is a constant bound on the storage space for a micro function representation.
+\end{enumerate}
 \efficient*

### 2015-03-09 sas2015/content/impl.tex
ondrejs comments

@@
 
-An IFDS solution $\resultIFDS$ has type $N^* \to D$: it maps each program point $n$
+An IFDS solution $\resultIFDS$ has type $N^* \to 2^D$: it maps each program point $n$
 to a set of facts $d$ that may be reached at $n$.
@@
 pairs each such fact~$d$ with a lattice element $\ell$, so its type
-is $N \to (D \to L)$.
+is $N^* \to (D \to L)$.
 

### 2015-03-09 sas2015/content/impl.tex
comment out \otodos

@@
 to a set of facts $d$ that may be reached at $n$.
-\otodo{This seems wrong: Why is it $N^*$ for IFDS and $N$ for IDE? And shouldn't
-    it be $N \to 2^D$, since you get a set of $d$'s?}
+%\otodo{This seems wrong: Why is it $N^*$ for IFDS and $N$ for IDE? And shouldn't
+    %it be $N \to 2^D$, since you get a set of $d$'s?}
 An IDE solution $\resultIDE$
@@
 
-\otodo{Give the list of criteria explicitly in the proof in the appendix.}
+%\otodo{Give the list of criteria explicitly in the proof in the appendix.}
 %\begin{enumerate}

### 2015-03-09 sas2015/content/background.tex
ondrejs comments
move figures around to save half a page
proofreading pass

@@
 \]
+\vspace{-5mm}
 \begin{example}\label{ex:flowfun}
@@
 
+\input{figures/fig-cc_edge_fn_example}
+
 \begin{example}
@@
 Just as any distributive function from $2^D$ to $2^D$ can be represented with a
-representation relation, it is also possible to represent any distributive functions from
+representation relation, it is also possible to represent any distributive function from
 $\textsf{Env}(D,L)$
@@
     together represent the environment transformer 
-    $\lambda e.e[\psi \to \lambda m.\bot \sqcap \lambda m.m]$.
+    $\lambda e.e[r \to \lambda m.\bot \sqcap \lambda m.m]$.
 

### 2015-03-09 sas2015/content/impl.tex
proofreading pass

@@
 runtime type. Therefore, a data-flow fact
-is unreachable along any feasible path if its corresponding lattice element
+is unreachable along a given path if its corresponding lattice element
 maps any receiver to the empty set of types.
@@
 of \code{a} are further restricted by the micro-function
-$\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code B\}]$.
+$\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code B\}]$
 on the edge that passes the argument \code{v} to the parameter \code{s}.
 The composition of these micro functions results in the empty set as the possible
-types \code{a}, indicating that this
+types of \code{a}, indicating that this
 %data-flow
@@
 Therefore, an IDE solution $\rho$ computed using $\transEq$ is converted to
-and IFDS solution as:
+an IFDS solution as:
   $\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}$.
@@
 \begin{restatable}{lemma}{efficient}\label{lem:efficient}
-  The correlated-call representation of a micro function is efficient and the required operations
+  The correlated-call representation of a micro function is efficient according to the IDE criteria and the required operations
   on micro-functions can be computed in time $O(\rcc T)$.
@@
 We implemented the correlated-calls analysis in Scala~\cite{odersky2004overview}. 
-Our implementation analyzed Java bytecode from input programs written
+Our implementation analyzed Java bytecode compiled from input programs written
 in Java.
@@
 to retrieve information about an input program, such as its control-flow supergraph and the set of receivers and their types.
-Since WALA does contain an implementation of the IDE algorithm,
+Since WALA does not contain an implementation of the IDE algorithm,
 we implemented it from scratch.
 %currently only contains an implementation of IFDS, we implemented IDE from scratch.
-We will submit our implementation to the artifact evaluation committee, and we are working on contributing it officially to WALA.
+We will submit our implementation to the artifact evaluation committee, and we are working on integrating it and contributing it officially to WALA.
 % Instead of using WALA's IFDS implementation, to run an IFDS problem, we converted it to an IDE problem and used our own IDE solver.

### 2015-03-09 sas2015/content/appendix.tex
add section numbers to appendix

@@
-\section*{Appendix}
+\section{Appendix}
 In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}, the table illustrating frequencies of correlated calls from Section~\ref{sec:occur}, and the code discussed in Section~\ref{sec:collex}.
 
-\subsection*{Correlated Calls Occurrences}
+\subsection{Correlated Calls Occurrences}
 Table~\ref{tab:dacapostat} shows how often correlated calls occur in practice. The number of all call sites in a program is denoted as $C$. 
@@
 
-\subsection*{\code{TraversableOnce} Trait from Scala Standard Library}
+\subsection{\code{TraversableOnce} Trait from Scala Standard Library}
 Figure~\ref{fig:traversableonce} presents the code from Scala's \code{TraversableOnce} trait discussed in Section~ref{sec:collex}.
@@
 
-\subsection*{Proofs}
+\subsection{Proofs}
 
-\subsubsection*{Representation of Micro Functions}
+\subsubsection{Representation of Micro Functions}
 We start by presenting the proofs to the lemmas about the representation of micro functions.
@@
 
-\subsubsection*{Efficiency}
+\subsubsection{Efficiency}
 We will next introduce the complexity proof for the correlated-calls algorithm.
@@
 
-\subsubsection*{Soundness and Precision}
+\subsubsection{Soundness and Precision}
 
@@
 
-\subsubsection*{Correlated-Call Receivers}
+\subsubsection{Correlated-Call Receivers}
 We will now present the proof for Lemma~\ref{lem:onlycorrrec} which shows that in a correlated-calls analysis, it is enough to consider only correlated-call receivers~$\rcc$.

### 2015-03-09 sas2015/content/impl.tex
evaluation

--- 2015-03-09 sas2015/content/impl.tex
@@
 
-\subsection{Implementation of the Correlated-Calls Analysis}
+%\subsection{Implementation of the Correlated-Calls Analysis}
+\section{Evaluation}
 We implemented the correlated-calls analysis in Scala~\cite{odersky2004overview}. 
@@
 
+The average running time for small programs such as in Figure~\ref{list:ccexample} is ???~seconds.
+On the SPECjvm98 benchmarks, the average running time is ???~seconds.
+So far we were only able to find a practical benefit from the correlated-calls analysis for programs in which correlated calls were ``artificially'' introduced in control-flow paths relevant to the specific client analysis.
+We are still working on identifying in which client IFDS problems, in combination with which benchmarks, we would encounter a precision improvement.
+
 \commentout{

### 2015-03-12 sas2015/content/background.tex
minor changes

@@
 because it constructs summaries of the effects of called procedures.
-The IFDS framework is applicable to \textit{interprocedural} data-flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
+The IFDS framework is applicable to \textit{interprocedural} data-flow problems whose domain is a \textit{subset} of a \textit{finite} set $D$,
 and whose data-flow functions are \textit{distributive}.
@@
     $v \in D$ may contain a secret value in an execution in which the runtime
-    types of the objects pointed to be the receiver variables are in the sets
+    types of the objects pointed to by the receiver variables are in the sets
     specified by $e(v)$.

### 2015-03-12 sas2015/content/eval.tex
minor changes

--- 2015-03-09 sas2015/content/impl.tex
@@
-  \commentout{
-%\otodo{The following definitions are very general, and not related to the transformation. Can we move them somewhere earlier?}
-\paragraph{Edge Functions}\label{sec:ef}
-
-Let $\mathcal F$ be the set of methods in a program with a signature $s_\mathcal F$.
-\begin{definition}
-  Let $r.c()$ be a call site on a receiver $r\in R$ with runtime type $t\in T$.
-  Let~$s_\mathcal F$ be the method signature corresponding to the call $c()$.
-  For $s_\mathcal F$ and $t$, a \textit{lookup function} returns the method implementation $f\in\mathcal F$ to which the call $r.c()$ is dispatched:
-  \begin{equation}
-    \textsf{lookup}(s_\mathcal F,\,t)=f.
-  \end{equation}
-\end{definition}
-
-\begin{definition}
-  For a method signature $s_\mathcal F$ and a method implementation $f\in\mathcal F$, the static-type function $\tau$ returns the set of types for which the lookup function yields $f$:
-  \begin{equation}
-    \tau(s_\mathcal F,\,f)=\{\,t\ |\ \textsf{lookup}(s_\mathcal F,\,t)=f\}\,.
-  \end{equation}
-\end{definition}
-In other words, $\tau$ computes the set of types for which calls to methods
-with signatures~$s_\mathcal F$ are dispatched to~$f$.
-
-If there is a supergraph path from a method call with signature $s_\mathcal F$ to the start of $f$, then the set $\tau(s_\mathcal F,\,f)$ is always non-empty.
-
-\begin{definition}\label{def:momopoly}
-  A call site is called monomorphic if it can be dispatched to only one method. If a call site can be dispatched to more than one method it is called polymorphic.
-\end{definition}
-
-  Let $r.c()$ be a call on a receiver $r\in R$ with a method signature $s_\mathcal F$ to a function $f\in\mathcal F$.
-  If the call site is monomorphic, then $\tau(s_\mathcal F,\,f)$ contains all types $T'\subseteq T$ that are compatible with the static type of $r$.
-  If the call site is polymorphic, then $\tau(s_\mathcal F,\,f)\subset T'$, since some types $t\in T'$ cause dispatch to a method other than $f$.
-  }
-
-\commentout{
-%\otodo{incorporate into previous section}
-\subsection{Defining IFDS and IDE Problems}
-%In Section~\ref{sec:bg}, we defined what IFDS and IDE problems are, their applications, and their constraints. In this section, we describe how to create instances of IFDS and IDE problems.
-
-\subsubsection{Defining an IFDS Problem}\label{sec:ifdsdef}
-Recall that an IFDS problem instance is defined as a five-tuple
-\[
-    (G^*,\ D,\ F,\ M_F,\,\sqcap)\,,
-\]
-where $G^*=(N^*,\,E^*)$ is the control-flow supergraph of the program, $D$ is the set of data-flow facts, $F\subseteq2^D\to2^D$ is a set of distributive data-flow functions, and the function $$M_F:\,E^*\to(2^D\to2^D)$$ maps the supergraph edges to data-flow functions, and is extended to paths by composition.
-
-In practice, an IFDS problem can be defined by providing an exploded supergraph
-$G^\#=(N^\#,\,E^\#)$.
-Each node of $G^\#$ is a pair $(n,\ d)$, where $n\in N^*$ is a node in the control-flow supergraph and $d\in (D\cup\{\mathbf{0}\}),\ \mathbf0\notin D$, where $\mathbf0$ is an auxiliary fact that is necessary for the IFDS algorithm.
-
-The meaning of an edge in the exploded supergraph is the following.
-Let $(n_1,\,d_1)$ and $(n_2,\,d_2)$ be two nodes in the exploded supergraph $G^\#$.
-Furthermore, assume that if fact $d_1$ at node~$n_1$ holds, then the fact~$d_2$ at node~$n_2$ also holds.
-Then there is an edge $(n_1,\,d_1),\,(n_2,\,d_2)\in E^\#$.
-
-\subsubsection{Defining an IDE Problem}\label{sec:defide}
-An IDE problem instance is a four-tuple
-\[
-    (G^*,\ D,\ L,\ \menv),
-\]
-where $G^*$ and $D$ are defined in the same way as for IFDS.
-$L$ is a finite-height lattice that represents the values to which data-flow facts are mapped in an IDE problem.
-An environment $Env(D, L)$ maps data-flow facts to lattice elements.
-Finally, the map $$M_{\textsf{Env}}:\,E^*\to(\textsf{Env}(D, L)\to \textsf{Env}(D, L))$$ is a function from the control-flow-supergraph edges to environment transformers, extended to paths by composition.
-
-An IDE problem can be defined with a labeled exploded supergraph\footnote{
-    The exploded supergraph in an IDE problem is defined in the same way as in an IFDS problem.
-The only difference is that the $\mathbf0$ fact is denoted as $\Lambda$~\cite{reps1995precise,sagiv1996precise}.
-}, in which an edge function
-\begin{equation}
-  \edgefn:\ E^\#\to(L\to L)
-\end{equation}
-pairs edges with \textit{micro functions}, and is extended to paths by composition.
-
-The set of micro functions of an IDE problem is a subset of $L\to L$ that is closed under function meet and composition.
-
-The meaning of an edge in the labeled exploded supergraph is the following. Let $e=((n_1,\,d_1),\,(n_2,\,d_2))\in E^\#$ be an edge in the exploded supergraph with label $f=\mathsf{EdgeFn}(e)$. Then
-\begin{itemize}
-	\item the fact that $d_1$ holds at node $n_1$ implies that $d_2$ holds at $n_2$;
-  \item if at node $n_1$ the fact $d_1$ was mapped to a lattice element $l_1$ by an environment $Env(D,\,L)$, then the fact $d_2$ at node $n_2$ should be mapped to $f(l_1)$.
-\end{itemize}
-
-As shown in~Sagiv et al.~\cite{sagiv1996precise}, the relationship between environment transformers and edge functions can be described with the following equations.
-For individual edges $(n_1,\,n_2)\in E^*$,
-\begin{align}\label{eq:envTransToEdgeFnEdge}
-  \menv&((n_1,\,n_2))(\textsf{env})(d)\notag\\
-  &=\edgefn((n_1,\,\mathbf0),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,,
-\end{align}
-where $\textsf{env}$ is an environment $\textsf{Env}(D,\,L)$.
-Informally, for a given control-flow-supergraph edge $e$ and data-flow fact $d$, the $M_\textsf{Env}$ function captures the meet of the edge function applied to all possible exploded-graph edges along $e$.
-
-For paths $p$ that start with the entry point~$\startmain$,
-\begin{equation}\label{eq:envTransToEdgefn}
-  \menv(p)(\Omega)(d)=\bigsqcap_{r\in\mathsf{RP}(p,\,d)}\edgefn(r)(\top)\,,
-\end{equation}
-where $n\in N^*$, $d\in D$, $p\in\ivp(n)$, and $\mathsf{RP}$ is the set of all interprocedurally realizable paths.
-
-To summarize, an IDE problem can be defined by a labeled exploded supergraph 
-\begin{equation}(G^\#,\,L,\,\mathsf{EdgeFn})\,,\end{equation}
-where each edge of the exploded supergraph corresponds to a micro function.
-}
-
-\section{Correlated Calls Analysis}\label{sec:cca}
-%The correlated-calls analysis is a transformation from an arbitrary IFDS problem to a corresponding IDE problem.
-The solution of this IDE problem can be converted to a solution of the original IFDS problem.
-The converted IFDS result can be more precise than the original IFDS result because it avoids infeasible paths corresponding to correlated calls.
-
-%In this section, we first discuss what is necessary to define IFDS and IDE problems.
-Next we describe how to convert any IFDS problem into an equivalent IDE problem, and, given a solution to the generated IDE problem, how to obtain the result of the original IFDS problem.
-We then show how to transform an IFDS problem into an IDE problem using the correlated-calls transformation, and how to convert the solution to the latter IDE problem into a more precise IFDS result.
-
-\subsection{Transformations from IFDS to IDE}\label{seq:transIfdsIde}
-
-%The correlated-call analysis transforms an existing IFDS problem into a special kind of IDE problem. We described what is necessary to define IFDS and IDE problems independently.
-
-%Let $P=(G^\#)$ be an IFDS problem and $Q=(G^\#,\,\edgefn)$ an IDE problem obtained by a conversion from $P$.
-Let $G^\#$ be the exploded supergraph of an arbitrary IFDS problem. A \emph{transformation}
-$\mathcal T:\ (G^\#)\to (G^\#,\,L,\,\edgefn)$
-converts the IFDS problem into an IDE problem.
-We consider two IFDS-to-IDE transformations: an \textit{equivalence transformation} $\transEq$ (pronounced ``t-equiv'') and
-a \textit{correlated-calls transformation} $\transCC$ (pronounced ``t-c-c'').
-Both transformations keep the exploded supergraph $G^\#$ the same, and only generate different edge functions.
-The solution of the IDE problem
-can be mapped back to an IFDS solution.
-If the equivalence transformation was used, then this solution is identical to the
-solution that would be computed by the IFDS algorithm for the original IFDS problem.
-If the correlated-calls transformation was used, then this solution is more precise
-because it excludes flow along infeasible paths due to correlated calls.
-
-%In each case we also show how to convert the result of the generated IDE problem to a result of the original IFDS problem.
-
-%An overview of the transformations is shown in Figure~\ref{fig:transformations}.
-
-\subsubsection{Equivalence Transformation}\label{sec:equivtrans}
-%We start with an equivalence transformation $\transEq$ to present a simple IFDS-to-IDE conversion that does not change the result of the original IFDS problem.
-We will compare the correlated-calls transformation with the equivalence transformation, and use the latter to show  that the correlated-calls analysis results in a
-%precision improvement of the original IFDS problem result.
-
-%\paragraph{Converting IFDS problems to IDE problems}
-%Since IDE is a generalization of IFDS, any IFDS problem can be converted into an equivalent IDE problem~\cite{sagiv1996precise}.
-The lattice
-for the equivalence transformation $\transEq$ 
-is the two-point lattice
-    $L^\equiv=\{\bot,\ \top\}$,
-where $\bot$ means ``reachable'', and $\top$ means ``not reachable''. 
-The edge functions $\edgefn^\equiv$ are defined as
-\begin{equation}
-    \edgefn^\equiv=
-    \begin{cases}
-        \lambda e\,.\,\lambda m\,.\,\bot&\text{if $e=(n_1,\mathbf0)\to(n_2,d_2)$, where $d_2 \neq \mathbf0$;}\\
-      \lambda e\,.\,\id&\text{otherwise.}
-    \end{cases}
-\end{equation}
-At a~``diagonal'' edge from a $\mathbf0$-fact to a non-$\mathbf0$-fact
-$d$, the micro function returns $\bot$
-to make
-the fact $d$ reachable. All other micro-functions are the identity function.
-%\mtodo{``the identity function'' or is it okay ot just say ``the identity''?}.
-\commentout{
-The equivalence transformation is thus defined as:
-  $\transEq((G^\#))=(G^\#,\,L^\equiv,\,\mathsf{EdgeFn}^\equiv)$.
-}
-
-%Thus, in $\transEq$, all non-diagonal edges in the original IFDS problem are mapped to identity functions.
-
-\subsubsection{Correlated-Calls Transformation}\label{sec:cctrans}
-
-%To improve the precision of an IFDS problem, we can convert it to a special type of IDE problem, and use lattice elements to provide us with additional information about a node.
-%When converting the IDE result to an IFDS result, lattice elements will tell us whether to make the corresponding exploded nodes reachable. This is the idea of the correlated-calls analysis.
-
-%\paragraph{Lattice Elements}
-In the correlated-calls transformation, the 
-%Just like in the equivalence transformation $\transEq$, the exploded supergraph for $\transCC$ is the same as in the original IFDS problem. The 
-lattice elements are maps from receivers to sets of types:
-    $\lcc=\left\{\,m:\ R\to2^T\right\}$,
-where $R$ is the set of receivers and $T$ is the set of all types.
-For each receiver~$r$, the map gives an overapproximation of the possible
-runtime types of $r$.
-Sets of types are ordered by the superset relation, and this is lifted to maps from receivers
-to sets of types, so the bottom element $\botcc$ maps every receiver to the set of all types,
-and the top element $\topcc$ maps every receiver to the empty set of types.
-During an actual execution, every receiver $r$ points to an object of some
-runtime type. Therefore, a data-flow fact
-is unreachable along a given path if its corresponding lattice element
-maps any receiver to the empty set of types.
-
-\commentout{
-The type power set $2^T$ is also a lattice with a bottom element 
-\begin{align*}
-\bot_T&=T
-\intertext{and top element}
-\top_T&=\varnothing.
-\intertext{The top element of the function lattice}
-\topcc&=\lambda r.\top_T
-\intertext{is a function that maps any receiver to the empty set\footnote{%
-  We prove that $\lcc$ is a lattice in the Proof of Lemma~\ref{lem:efficient}%
-}. 
-The bottom element}
-\botcc&=\lambda r.\bot_T
-\end{align*}
-maps any receiver to all types in the program.
-
-To understand the meaning of lattice elements in a correlated-call analysis, suppose that an IFDS problem has been converted to an IDE problem using the correlated-calls transformation. 
-Assume also that $s$ is the entrypoint of the program, $n$ is a node in the exploded supergraph, and that in the IDE result, $n$ is mapped to a lattice element $l\in \lcc$. 
-Then the purpose of $l$ is to provide information about the set of types of the objects that may be referenced by each receiver at runtime at a path from $s$ to $n$. 
-If a receiver is mapped to the empty set $\top_T$, it means that for the given program point, the receiver cannot reference an object of any type.
-In other words, the corresponding data-flow fact is considered not reachable.
-}
-
-%\paragraph{Micro Functions}\label{sec:micro}
-%Unlike in the equivalence transformation, the micro functions returned by the edge function $\edgefn^\Subset$ are not always identity functions.
-
-A micro-function $f\in\lcc\to \lcc$ defines how the map from receivers to types should
-be updated when an instruction is executed.
-The micro-function for most kinds of instructions is the identity.
-On a call to and return from a specific method $m$ called on receiver $r$,
-the micro-function restricts the receiver-to-type map to map $r$ only to
-types consistent with the polymorphic dispatch to method $m$.
-Finally, when an instruction assigns an object of unknown type to a receiver
-$r$, the corresponding micro-function updates the map to map $r$ to the
-set of all types. This is made precise by the following definition:
-\begin{definition}\label{def:microfn}
-Given a previously fixed set $S \subseteq R$ of receivers, the micro-function $\varepsilon_S(e)$
-of a supergraph edge $e$ is defined as:
-                    %\otodo{define $n_1(e)$ globally somewhere early on, and consider using a more decriptive name like src instead of $n_1$}
-  \begin{align}\label{eq:varepsilon}
-      &\varepsilon_S(e)= \lambda m\,.\,\\
-        &\begin{cases}
-            m[r\to m(r)\cap \tau(s,\,f)],
-            &\text{\parbox{75mm}{
-                    if $e$ is a call-start edge $r.c() \to \textsf{start}_f$ that calls
-                procedure $f$ with signature $s$,
-                and $r\in S$;}}\\[3ex]
-        \parbox{30mm}{\[\begin{array}{l}
-                m[r\to m(r)\cap \tau(s,\,f)]\\
-            [v_1\to\bot_T] \ldots [v_k\to\bot_T],
-        \end{array}
-        \]
-        }
-        &
-        \text{\parbox{75mm}{
-                if $e$ is an end-return edge
-                $\textsf{end}_f \to \textsf{return}_{r.c()}$
-                from method $f$ with signature $s$ to the return node corresponding
-                to the call $r.c()$,
-                $v_1,\,\dots,\,v_k\in S$ are the local variables
-                in $f$,
-                and $r\in S$;}}\\
-            m\left[r\to \bot_T\right],
-            &\text{\parbox{75mm}{if $e = n_1 \to n_2$ and $n_1$ contains an assignment
-                    to $r\in S$;}}\\
-            m
-                &\text{otherwise.}
-        \end{cases}
-  \end{align}
-\end{definition}
-
-In the above definition, the purpose of the set $S$ is to limit the set of considered receivers. We will use $S$ in Section~\ref{sec:ccreceivers}.
-
-%Let $e=(n_1,\,n_2)\in E^\#$ be an edge in the exploded supergraph.
-%$\edgefn^\Subset(e)$ returns a micro function $f\subset\lcc\to \lcc$.
-%Given a micro function (a map from receivers to sets of types) $m\in \lcc$, $f(m)$ returns a new map from receivers to sets of types.
-%In other words, $f$ shows how to update the map from receivers to sets of types when we encounter program point $n_1$.
-
-%Let $f_1$ and $f_2$ be two micro functions such that ${f_1=\lambda m\,.\,\lambda r\,.\,t_1(r)}$ and ${f_2={\lambda m\,.\,\lambda r\,.\,t_2(r)}}$.
-We define the meet operation on micro-functions as follows:
-%\begin{equation}\label{eq:micromeet}
-  %\lambda m\,.\,\lambda r\,.\,t_1(r)\sqcap\lambda m\,.\,\lambda r\,.\,t_2(r)
-  %=\lambda m\,.\,\lambda r\,.\,t_1(r)\cup t_2(r)\,.
-%\end{equation}
-%
-%The composition of micro functions is defined as ordinary function composition.
-
-We can now define $\edgefn$, which assigns a micro-function to each edge in
-the exploded supergraph. 
-Along a $\mathbf0$-edge, the micro function is the identity. 
-%All other functions can be described with $\varepsilon_S$.
-On a ``diagonal'' edge from $\mathbf0$ to a non-$\mathbf0$ fact that corresponds
-to some data-flow fact becoming reachable, $\varepsilon_S(e)$ is applied to
-%the initial map
-$\botcc$ that maps every receiver to an object of every possible type.
-%conservatively allows every receiver to point to an object of any type.
-On all other edges, $\varepsilon_S(e)$ is applied to the existing map before the edge.
-The is formalized in the following definition.
-\begin{definition}\label{def:edgefn}
-For each edge $e = (n_1,d_1) \to (n_2,d_2)$, $\ccedgefn S(e)$ is defined as follows:
-  \begin{equation}\label{eq:edgefndef}
-      \ccedgefn S(e)=
-        \begin{cases}
-          \id  &\text{if $d_1=d_2=\mathbf0$},\\
-          \lambda m\,.\,\varepsilon_S(e)(\botcc) &\text{if $d_1=\mathbf0$ and $d_2\ne\mathbf0$},\\
-          \lambda m\,.\,\varepsilon_S(e)(m)  &\text{otherwise.}
-        \end{cases}
-  \end{equation}
-  %We define both $\ccedgefn S$ and $\varepsilon_S$ to be extended to paths by composition.
-\end{definition}
-
-\begin{example}
-  Consider the program from Figure~\ref{list:ccexample}, whose exploded supergraph appeared in Figure~\ref{fig:cc_edgefn_example}.
-%
-  Returning a secret value in method \code{A.foo} creates a ``diagonal'' edge from the $\mathbf0$-fact to the method's return value $r$. 
-  The diagonal edge is labeled with $\lambda m\,.\,\botcc$, so every receiver is mapped to the set of all types~$\bot_T$.
-%  
-On the end-return edge from \code{A.foo} to \code{main}, the set of types of \code{a} is restricted by the micro function $\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code A\}]$ corresponding to the assignment of the return value $r$ to \code v.
-%
-%Similarly,
-On the call-start edge from \code{main} to \code{B.bar}, the possible types
-of \code{a} are further restricted by the micro-function
-$\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code B\}]$
-on the edge that passes the argument \code{v} to the parameter \code{s}.
-The composition of these micro functions results in the empty set as the possible
-types of \code{a}, indicating that this
-%data-flow
-path 
-%that would
-%result in an information leak 
-is 
-%actually
-infeasible.
-\end{example}
-
-%After we have shown the definitions for the meet and composition operations, we will show in Example~\ref{ex:cc} how the correlated-calls analysis uses the presented micro functions to detect infeasible paths.
-
-\commentout{
-Finally, the correlated-calls transformation is defined as
-    \begin{equation}
-      \transCC_S((G^\#))=\left(G^\#,\,\lcc_S,\,\ccedgefn S\right).
-    \end{equation}
-}
-
-%Then, for an edge $e$, the correlated-call micro functions can be defined as $\ccedgefn R$ and a correlated-calls transformation is defined as $\transCC_R$.
-
-\subsection{Converting IDE Results to IFDS Results}\label{sec:ideToIfds}
-
-An IFDS solution $\resultIFDS$ has type $N^* \to 2^D$: it maps each program point $n$
-to a set of facts $d$ that may be reached at $n$.
-%\otodo{This seems wrong: Why is it $N^*$ for IFDS and $N$ for IDE? And shouldn't
-    %it be $N \to 2^D$, since you get a set of $d$'s?}
-An IDE solution $\resultIDE$
-pairs each such fact~$d$ with a lattice element $\ell$, so its type
-is $N^* \to (D \to L)$.
-
-%For each program point $n$, the result of an IFDS analysis gives
-%a set of facts $d$ that may be reached at $n$. The result of an IDE analysis
-%pairs each such fact~$d$ with a lattice element $\ell$. Formally,
-%for an IFDS problem $P$, the result $\resultIFDS$ has type
-%$N^* \to D$.
-%Similarly, for an IDE problem $Q$, the result $\resultIDE(Q)$
-%has type $N \to (D \to L)$.
-
-In the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
-and $\top$ means unreachable.
-Therefore, an IDE solution $\rho$ computed using $\transEq$ is converted to
-an IFDS solution as:
-  $\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}$.
-%a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
-%is converted to an IFDS result as follows:
-%\begin{equation}\label{eq:transEqDef}
-  %\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
-%\end{equation}
-%
-%\otodo{I don't understand this comment. What does it mean?}
-%
-In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
-to the empty set of possible types means that the corresponding data-flow path is
-infeasible. Therefore, an IDE solution $\rho$ computed using
-$\transCC_S$ is converted to an IFDS solution as:
-$\backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}$.
-
-%a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
-%converted to an IFDS result as follows:
-%\begin{equation}\label{eq:transCcDef}
-    %\backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.
-%\end{equation}
-%\otodo{In Equation (5), I changed $\rho(n)(d)$ to $\rho(n)(d)(r)$, because I think
-%    the original was incorrect. Marianna, please check that this correction is correct.}
-
-\commentout{
-
-The output of an IFDS analysis states whether a node is reachable in the exploded supergraph.
-This means that for an IFDS problem $P$, the IFDS-analysis result $\resultIFDS(P):\ N^*\to 2^D$ is a map from nodes of the control-flow supergraph to sets of facts:
-\begin{equation}
-  \resultIFDS(P)=\{(n,\,\mvp F(n))\,|\,n\in N^*\}\,.
-\end{equation}
-
-\begin{mdelete}
-\begin{example}\label{ex:ifdsresult}
-  The solution to the taint-analysis IFDS problem $\mathcal P$ in Figure~\ref{list:examplejava} whose exploded supergraph is presented in Figure~\ref{fig:exampleexploded} looks as follows:
-  \small\begin{align*}
-    \resultIFDS(\mathcal P)=\{&(\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\{\texttt a\}),
-      &(\highlight{\textsf{start}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
-      &\qquad\qquad(\highlight{\textsf{return}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
-%      
-      &(\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\{\texttt a\}),
-      &(\highlight{\texttt{if(s==null)}}{lightsalmonpink},\,\{\texttt s\}),
-      &\qquad\qquad(\highlight{\texttt{return r}}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
-%
-      &(\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\{\texttt a,\,\texttt b\}),
-      &(\highlight{\textsf{call}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
-      &\qquad\qquad(\highlight{\textsf{end}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\})\}.\\
-%
-      &(\highlight{\textsf{end}_\texttt{main}}{greyblue},\,\{\texttt a,\,\texttt b\}),&(\highlight{\texttt{return s}}{lightsalmonpink},\,\{\texttt s\}),
-  \end{align*}\normalsize
-  All other nodes of the control-flow supergraph are mapped to the empty set.
-\end{example}
-\end{mdelete}
-
- The IDE analysis associates a lattice element with each node in the exploded supergraph.
-For an IDE problem $Q$, the result $\resultIDE(Q):\ N^\#\to L$ maps nodes of the exploded supergraph to lattice elements (see~\eqref{eq:mvpdef}):
-\begin{equation}\label{eq:ideresult}
-  \resultIDE(Q)=\{((n,\,d),\,\mvp{\textsf{Env}}(n,\,d))\ |\ n\in N^*,\,d\in D\}\,.
-\end{equation}
-In other words, for each fact $d\in D$ at a given node $n\in N^*$, $\resultIDE(Q)(n,\,d)$ returns a lattice element. If a fact $d\in D$ is unreachable, $\resultIDE(Q)(n,\,d)=\top$.
-
-In the case of an equivalence transformation from IFDS to IDE, if a node in the IFDS result is reachable, it will be also reachable in the IDE result, and it will be mapped to the bottom lattice element.
-For an exploded node in the IDE result, being mapped to the top element means being not reachable.
-
-The~domain of an equivalence-IDE result 
-\begin{equation}
-  \resultEq=\resultIDE(\transEq(P))
-\end{equation}
-consists of pairs of control-flow-supergraph nodes and data-flow facts.
-The range of the result is the set of lattice elements.
-To transform an IDE result to an IFDS result, we need to map each control-flow-supergraph node to the set of facts with which it is paired, provided that the pair is mapped to the bottom lattice element.
-
-\begin{mdelete}
-\begin{example}\label{ex:ideresult}
-  Converting the IFDS problem $\mathcal P$ from Example~\ref{ex:ifdsresult} into an equivalent IDE problem and solving it will yield the following result:
-    \small\begin{align*}
-    \resultIDE(\transEq(\mathcal P))=\{&((\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\texttt a),\,\bot),\\
-      &((\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
-      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
-      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt b),\,\bot),\\
-      &\dots\}.\\
-    \end{align*}\normalsize
-  Suppose that for a pair $(n,\,d)$, where $n\in N^*$ and $d\in D$, there is no corresponding result in ~$\resultIFDS(\mathcal P)$ (see Example~\ref{ex:ifdsresult}).
-Then $(n,\,d)$ appears in $\resultIDE(\transEq(\mathcal P))$ as $((n,\,d),\,\top)$.
-\end{example}
-\end{mdelete}
-
-Let $\rho$ be the result of an equivalence-IDE analysis for an IFDS problem $P$:
-\[
-  \rho=\resultIDE(\transEq(P)).
-\]
-For a node $n\in N^*$, let $D_n^\equiv(\rho)$ be a set of data-flow facts such that
-\begin{equation}
-  D_n^\equiv(\rho)=\{d\ |\ d\in D\,\wedge\,\rho(n,\,d)\ne\top\}\,.
-\end{equation}
-Then the transformation function
-$\backEq:\,(N^\#\to L)\to(N^*\to2^D)$
-from an IDE result to~an~IFDS result looks as follows:
-\begin{equation}
-  \backEq\left(\rho\right)=
-    \left\{(n,\,D_n^\equiv(\rho))\ |\ n\in N^*\right\}\,.
-\end{equation}
-
-Obviously, if applied to the result of an equivalence-IDE problem, $\backEq$ returns a result equivalent to the original IFDS problem result.
-In other words, for any IFDS problem $P$ with supergraph $N^*$, and any node $n\in N^*$,
-\begin{equation}
-  \backEq\left(\resultIDE(\transEq(P))\right)(n)=\resultIFDS(P)(n)\,.
-\end{equation}
-
-\begin{example}
-  Converting the result in Example~\ref{ex:ideresult} with the equivalence-transformation from an IDE result to an IFDS result $\backEq$ will yield the same result as in Example~\ref{ex:ifdsresult}.
-\end{example}
-
-Let $P$ be an IFDS problem. 
-Let $E:\,N\times D$ be the domain of the IDE result $\resultIDE(Q)$.
-To convert $\resultIDE(\transCC_R(P))$ to an IFDS result, we need to map the control-flow-supergraph nodes $n\in N^*$ to the corresponding facts $d\in D$. 
-Unlike in~$\backEq$, we will only map each~$n$ to the facts~$d$ for~which~$\resultIDE(\transCC_R(P))(n,\,d)$ does not contain an~empty mapping for~any~receiver.
-
-For a node $n\in N^*$ and a correlated-calls IDE problem result $\rho=\resultIDE(\transCC_S(P))$, let $D_n^\Subset(\rho)$ be a set of data-flow facts defined as
-\begin{equation}\label{eq:dnq}
-  D_n^\Subset(\rho)=\left\{d\ |\ 
-    d\in\mvp F(n)\,\wedge\,\forall r\in R:\ \rho(n,\ d)(r)\ne\top_T\right\}.
-\end{equation}
-Then, for a set $S\subseteq R$, the~correlated-calls-conversion function from a~correlated-calls IDE~result $\rho$ to~an~IFDS~result looks as~follows:
-\begin{equation}\label{eq:ucc}
-  \backCC\left(\rho\right)=
-    \left\{(n,\,D_n^\Subset(\rho)\ | \ n\in N^*\right\}.
-\end{equation}
-}
-
-\subsection{Implementation of Correlated Calls Micro-Functions}
-%\otodo{move material from following section here}
-
-Conceptually, micro-functions are functions from $L$ to $L$, where $L$
-is the IDE lattice, either $L^\equiv$ or $\lcc$ in our context. 
-The IDE algorithm requires an efficient representation of micro-functions.
-The chosen representation needs to support the basic micro-functions that
-we presented in Section~\ref{seq:transIfdsIde}, and it must
-support function application, comparison, and be closed under function composition
-and meet. We now propose such a representation for the correlated-calls micro-functions.
-
-The representation of a micro-function is a map from receivers to pairs of sets of
-types $I(r)$ and $U(r)$, where $U(r)$ is required to be a subset of $I(r)$. 
-We use the notation
-$\setpair{I}{U}$ to represent such a map, and $I(r)$ and $U(r)$ to look up the
-sets corresponding to a particular receiver $r$.
-The micro-function takes the existing set of possible types of the
-receiver $r$, intersects it with $I(r)$, then unions it with $U(r)$:
-$\denote{\setpair{I}{U}} = \lambda m\,.\,\lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
-
-%We define the meaning $\denote{\setpair{I}{U}}$
-%of a representation $\setpair{I}{U}$ as follows: 
-%In words, the micro-function represented by $\setpair{I}{U}$ takes an existing map $m$
-%from receivers to sets of types, and returns a map that maps each receiver $r$ to
-%the set $m(r)$ given by the original map $m$ intersected with $I(r)$ and unioned
-%with $U(r)$.
-
-All of the basic micro-functions defined in Definition~\ref{def:microfn} can be expressed
-in this representation. The following lemmas show how function comparison, composition, and meet can be implemented using basic set operations
-on $I$ and $U$.
-The proofs of all of the lemmas and theorems are in the Appendix.
-
-%The implementation of function application follows directly from the definition of
-%the representation: $\setpair{I}{U}(m) = \lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
-%\mtodo{Should this be the denotation of $\setpair IU$?}
-%\otodo{No. It is an implementation of the apply operation.}
-
-%To compare two micro-functions for equality, it suffices to compare the corresponding
-%sets $I(r)$ and $U(r)$ for all receivers $r$. The following lemma shows that this
-%implementation of comparison corresponds to equality of the represented micro-functions:
-\begin{restatable}{lemma}{equalEq}
-\label{lem:equalEq}
-    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
-    \begin{equation}
-        \forall r\,.\,I(r) = I'(r) \land U(r) = U'(r)
-        \iff
-        \denote{\setpair{I}{U}} = \denote{\setpair{I'}{U'}}.
-    \end{equation}
-\end{restatable}
-
-%The following lemma shows that this implementation corresponds to the composition
-%of the denoted functions.
-\begin{restatable}{lemma}{equalComp}\label{lem:equalComp}
-    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
-    \[
-        \denote{\setpair{I}{U} \circ \setpair{I'}{U'}}
-        = 
-        \denote{\setpair{I}{U}} \circ \denote{\setpair{I'}{U'}},
-    \]
-    where the composition of two micro-function representations is defined as follows:
-$$\setpair{I}{U} \circ \setpair{I'}{U'} = \setpair{\lambda r\,.\,(I(r) \cap I'(r))\cup U(r)}{\lambda r\,.\,(I(r)\cap U'(r))\cup U(r)}.$$
-\end{restatable}
-
-%The following lemma shows that this implementation corresponds to the meet
-%of the denoted functions:
-\begin{restatable}{lemma}{equalMeet}\label{lem:equalMeet}
-\label{lem:equalMeet}
-    Let $\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
-     =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.
-    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
-    \begin{equation}
-        \denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}
-        = 
-        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}},
-    \end{equation}
-    where the meet of two micro-function representations is defined as follows:
-$$\setpair{I}{U} \sqcap \setpair{I'}{U'} = \setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}.$$
-\end{restatable}
-
-\subsection{Theoretical Results}
-
-The following lemma shows that our analysis is sound, i.e. 
-that the resulting IDE problem still considers all data-flow
-paths that are actually feasible.
-%that the result of an IDE problem obtained through a correlated-calls transformation removes only facts that occur on infeasible paths.
-
-\begin{restatable}[Soundness]{lemma}{sound}\label{lem:sound}
-  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, and let $d\in D$.
-  If $d\in M_F(p)(\varnothing),$
-  then
-  $
-    d\in \backCC\left(\resultIDE(\transCC_R(P))\right)(n)\,.
-  $
-\end{restatable}
-
-We also show that the result of an IDE problem obtained through a correlated-calls transformation is a subset of the original IFDS result.
-
-\begin{restatable}[Precision]{lemma}{precision}\label{lem:subsetifds}
-    For an IFDS problem $P$ and all ${n\in N^*}$,
-    \begin{equation}
-      \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
-      \subseteq
-      \resultIFDS(P)(n)\,.
-    \end{equation}
-\end{restatable}
-
-\subsection{Correlated-Call Receivers}\label{sec:ccreceivers}
-We will now show that in a correlated-calls transformation, it is enough to consider only some of the receivers of set $R$.
-
-\begin{definition}
-    If $r\in R$ is the receiver of at least two polymorphic
-    call sites, then we call $r$ a \textit{correlated-call receiver}, and we define $\rcc$ as the set of all
-  such receivers.
-\end{definition}
-%In other words, a correlated-call receiver is a receiver that has at least two polymorphic call invocations.
-%We will denote the set of correlated-call receivers as $\rcc$.
-
-We will show that it is sufficient for the correlated-calls
-micro-functions to be defined only on correlated-call receivers.
-%We will describe a ``reduced'' correlated-calls transformation in which we only consider receivers from $\rcc$ and ignore other receivers of $R$.
-Specifically, a ``reduced'' correlated-calls transformation that
-considers only correlated-call receivers in the micro-functions
-yields the same solution as the full correlated-calls transformation
-(i.e. no precision is lost).
-%We will show that IDE problems obtained through ordinary and reduced correlated-calls transformations yield the same results.
-%In other words, we show that if a correlated-calls analysis considers only correlated-call receivers, no precision is lost.
-
-\begin{restatable}{lemma}{onlycorrrec}\label{lem:onlycorrrec}
-Let $P$ be an IFDS problem. Then  
-  \begin{equation}
-    \backCC\left(\resultIDE\left(\transCC_\rcc(P)\right)\right)=\backCC(\resultIDE\left(\transCC_R(P)\right))\,.
-  \end{equation}
-\end{restatable}
-
-\commentout{
-To summarize, Lemma~\ref{lem:sound} shows that the result of a correlated-calls analysis is sound since it overapproximates the data flow of all possible concrete execution paths.
-We have also shown in Lemma~\ref{lem:subsetifds} that for an IFDS problem $P$, the correlated-calls analysis improves the precision of the original IFDS result $\resultIFDS(P)$, because the correlated-calls result $\resultIDE(\transCC(P))$ underapproximates an equivalence-IDE result $\resultIDE(\transEq(P))$.
-Finally, we showed in Lemma~\ref{lem:onlycorrrec} that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result that is obtained when considering all receivers $R$.
-}
-
-%This is the general idea of the correlated-calls analysis.
-The analysis involves a transformation from IFDS to IDE problems.
-To implement an IDE problem, it is necessary to define a representation of lattice elements and micro functions.
-An efficient representation of those data structures for the correlated-calls analysis is presented in the next section.
-
-\subsection{Efficiency}
-%\otodo{Sagiv et al. define a notion of an ``efficient'' implementation of micro-functions.
-%    If the micro-functions are ``efficient'', then the asymptotic complexity bounds proven by
-%    Sagiv hold. Our implementation is ``efficient'' if we assume that the number of correlated
-%    receivers is a constant independent of the size of the program. That seems a stretch. If
-%    it's linear in the size of the program, then we would need to add a factor to their complexity
-%    bounds. Their bound is $O(ED^3)$, while ours would be $O(ED^3R)$. But then we can't directly use their complexity proof; we would have to adapt it.
-%    I'm leaning towards leaving out any mention of ``efficient'' implementation.}
-
-Both the IFDS and IDE algorithms have been proven
-to run in $O(ED^3)$ time~\cite{reps1995precise,sagiv1996precise},
-where $E$ is the number of edges in the (non-exploded) supergraph, and $D$ is the size
-of the set of facts.
-The IDE algorithm may evaluate micro-functions up to $O(ED^3)$ times,
-so this running time must be multiplied by the cost of evaluating a
-micro-function. We show that the micro-functions in the correlated-calls
-IDE analysis can be evaluated in time $O(\rcc T)$, where $\rcc$ is the number
-of correlated-call receivers $\rcc$ and the $T$ is the number of run-time
-types. Therefore, the overall worst-case cost of the correlated-calls IDE analysis
-is $O(ED^3\rcc T)$. Note that in practice, $\rcc$ is much smaller
-than $R$, so Lemma~\ref{lem:onlycorrrec} is significant for 
-performance.
-
-Specifically, the complexity proof for the IDE algorithm requires
-the implementation of the micro-functions to be \textit{efficient}
-according to a list of specific criteria. Our micro-function
-implementation does satisfy the criteria:
-
-%\otodo{Give the list of criteria explicitly in the proof in the appendix.}
-%\begin{enumerate}
-	%\item There is a representation for the identity and top functions.
-  %\item The representation is closed under the meet and composition operations.
-  %\item The micro functions form a finite-height lattice.
-  %\item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
-  %\item There is a constant bound on the storage space for a micro function representation.
-%\end{enumerate}
-%We prove these conditions with the following lemma:
-\begin{restatable}{lemma}{efficient}\label{lem:efficient}
-  The correlated-call representation of a micro function is efficient according to the IDE criteria and the required operations
-  on micro-functions can be computed in time $O(\rcc T)$.
-\end{restatable}
-
-%From this lemma, we conclude that the correlated-calls analysis runs in time
-%$O(ED^3\rcc T)$. In other words, the asymptotic cost of the added precision of
-%the correlated-calls analysis is increased by a factor of $O(\rcc T)$ compared
-%to the original IFDS analysis.
-
 %\subsection{Implementation of the Correlated-Calls Analysis}
 \section{Evaluation}
+  \label{sec:Evaluation}
+
 We implemented the correlated-calls analysis in Scala~\cite{odersky2004overview}. 
-Our implementation analyzed Java bytecode compiled from input programs written
+Our implementation analyzes JVM bytecode compiled from input programs written
 in Java.
@@
 %corresponding Java bytecode.
-We used WALA~\cite{fink2012wala}
+We use WALA~\cite{fink2012wala}
 to retrieve information about an input program, such as its control-flow supergraph and the set of receivers and their types.

### 2015-03-12 sas2015/content/example.tex
fiddle with figures
move figures around to save half a page
proofreading pass
minor changes

@@
 %on line~\ref{line:Bbar} 
-is assumed to be a sink (e.g. the call to \code{System.out.println()} in code{B.bar()}.
+is assumed to be a sink (e.g., the call to \code{System.out.println()} in \code{B.bar()}).
 %a security-sensitive operation.
@@
 for \code{B.foo()} and \code{B.bar()}.
-Consequently, paths such as the one highlighted in
+Consequently, paths such as the one shown in bold in
 Figure~\ref{fig:examplesupergraph} where the calls dispatch to
@@
 Out of these polymorphic call sites, a significant fraction (39\%) are correlated 
-call sites $C^\Subset$. We also see that, on average,  each correlated-call receiver is involved in three correlated calls.
+call sites $C^\Subset$. We also see that, on average,  each correlated-call receiver is involved in approximately
+three correlated calls.
 

### 2015-03-12 sas2015/content/impl.tex
minor changes

--- 2015-03-09 sas2015/content/impl.tex
@@
 %to the original IFDS analysis.
-
-\subsection{Implementation of the Correlated-Calls Analysis}
-We implemented the correlated-calls analysis in Scala~\cite{odersky2004overview}. 
-Our implementation analyzed Java bytecode compiled from input programs written
-in Java.
-%The input programs that we analyzed were written in Java. Our implementation analyzed the
-%corresponding Java bytecode.
-We used WALA~\cite{fink2012wala}
-to retrieve information about an input program, such as its control-flow supergraph and the set of receivers and their types.
-Since WALA does not contain an implementation of the IDE algorithm,
-we implemented it from scratch.
-%currently only contains an implementation of IFDS, we implemented IDE from scratch.
-We will submit our implementation to the artifact evaluation committee, and we are working on integrating it and contributing it officially to WALA.
-% Instead of using WALA's IFDS implementation, to run an IFDS problem, we converted it to an IDE problem and used our own IDE solver.
-
-We tested the implementation of the correlated-calls analysis using an IFDS taint-analysis implementation as a client analysis.
-We converted the IFDS taint analysis into an IDE problem with an implementation of $\transCC_\rcc$.
-
-We extensively tested the correlated-calls analysis to ensure that in the absence of correlated calls in an input program, the analysis produced the same results as an IFDS-equivalent analysis, and in the presence of correlated calls, the result was more precise.
-
-\commentout{
-The artifact of our implementation can be used to solve any IFDS problem.
-In the presence of correlated calls, the result of the correlated-calls analysis can be more precise than the result obtained with an IFDS solver.
-}

### 2015-03-12 sas2015/content/intro.tex
minor changes

@@
 The \textit{Interprocedural Finite Distributive Subset} (IFDS) algorithm~\cite{reps1995precise}
-is one general data-flow analysis algorithm that 
+is a general data-flow analysis algorithm that 
 %by  Reps, Horwitz, and Sagiv
@@
 method calls are polymorphic
-(i.e. the method invoked depends on the run-time type of the receiver),
+(i.e., the method invoked depends on the run-time type of the receiver),
 %(i.e., if they dispatch to different method definitions 
@@
 %
+Our implementation is discussed in Section~\ref{sec:Evaluation}.
+%
 Related work is discussed in Section~\ref{sec:Related}.

### 2015-03-12 sas2015/content/related.tex
minor changes

@@
 
-The IFDS algorithm is implemented in two popular static-analysis frameworks for Java bytecode, the T.J.~Watson Libraries for~Analysis (WALA)~\cite{fink2012wala} and Heros~\cite{bodden2012inter}.
+%The IFDS algorithm is implemented in two popular static-analysis frameworks for Java bytecode, the T.J.~Watson Libraries for~Analysis (WALA)~\cite{fink2012wala} and Heros~\cite{bodden2012inter}.
 
@@
 between dynamically dispatched method calls, their approach eliminates
-infeasible paths between reads and writes of different members
+infeasible paths between reads and writes of different properties
 %(the JavaScript analogue of fields) 

### 2015-03-12 sas2015/content/related.tex
tweaks to save space

@@
 \commentout{(detecting errors and validating properties of programs at compile time)}%
-~\cite{DBLP:conf/birthday/KreikerRRSWY13}.
-IFDS has been broadly used~\cite{DBLP:conf/pldi/ArztRFBBKTOM14,tripp2009taj} and extended~\cite{DBLP:conf/sigsoft/LerchHBM14} to solve taint-analysis problems.
+~\cite{DBLP:conf/birthday/KreikerRRSWY13}. IFDS has been used~\cite{DBLP:conf/pldi/ArztRFBBKTOM14,tripp2009taj} and extended~\cite{DBLP:conf/sigsoft/LerchHBM14} to solve taint-analysis problems.
 
@@
 
-Several extensions of the IFDS algorithm have been proposed to improve its precision,
-efficiency, and expressiveness. Naeem and Lhot\'ak~\cite{naeem2010pei} propose
-four extensions: two to improve efficiency on certain kinds of IFDS problems,
-one to improve expressiveness to a wider range of IFDS problems, and one
-to improve precision when applying the IFDS algorithm to programs in SSA form.
-All of these extensions are orthogonal to and could be combined with the approach
-that we present in this paper. In contrast to these techniques, our approach targets
+Naeem and Lhot\'ak~\cite{naeem2010pei} proposed several extensions of IFDS.
+In particular, they propose several techniques for improving the algorithm's 
+efficiency, as well as a technique that improves expressiveness by extending
+applicability to a wider class of dataflow analysis problems. 
+These extensions are orthogonal to, and could be combined with the approach
+presented in this paper. Our work differs from theirs by targeting
 analysis precision, not efficiency or expressiveness.
@@
 
-Two other extensions target efficiency. Bodden et~al.~\cite{bodden2013spl} presents a framework
+Bodden et~al.~\cite{bodden2013spl} presents a framework
 for applying IFDS analyses to software product lines. Their approach enables the analysis of
@@
 
-The idea of using correlated calls to remove infeasible paths in data-flow analyses of object-oriented programs was introduced by Tip~\cite{DBLP:journals/scp/Tip15}.
-The possibility of using IDE to achieve this is mentioned, but not elaborated upon.
-Our work presents a concrete solution to the problem and an implementation of that solution.
+The idea of using correlated calls to remove infeasible paths in data-flow analyses of object-oriented programs 
+was introduced by Tip~\cite{DBLP:journals/scp/Tip15}. The possibility of using IDE to achieve this is mentioned, 
+but not elaborated upon. Our work is the first to present and implement a concrete solution.
 
-Sridharan et~al.'s improvements to the precision of pointer analysis
-for Ja\-va\-Script programs~\cite{DBLP:conf/ecoop/SridharanDCST12} also
-eliminate infeasible paths. Instead of infeasible paths
+Recent work on correlation tracking for JavaScript~\cite{DBLP:conf/ecoop/SridharanDCST12} 
+also eliminates infeasible paths. Instead of infeasible paths
 between dynamically dispatched method calls, their approach eliminates
 infeasible paths between reads and writes of different properties
-%(the JavaScript analogue of fields) 
 of an object. 
@@
 points-to analysis is orthogonal to our work because it analyzes the
-flow of data (pointers), while we analyze control flow paths instead.
+flow of data (pointers), whereas we analyze control flow paths.
 Also, object-sensitive points-to analysis is flow-insensitive, while
-the IFDS and IDE algorithms are flow-sensitive, and our transformation only makes sense
-in a flow-sensitive setting (since a flow-insensitive analysis already
-introduces many more infeasible control flow paths).
+IFDS and IDE are flow-sensitive analyses. Note that our transformation only makes sense
+in a flow-sensitive setting since a flow-insensitive analysis already
+introduces many infeasible control flow paths.
 

### 2015-03-13 sas2015/content/background.tex
fixes to previous fixes

@@
 because it constructs summaries of the effects of called procedures.
-The IFDS framework is applicable to \textit{interprocedural} data-flow problems whose domain is a \textit{subset} of a \textit{finite} set $D$,
+The IFDS framework is applicable to \textit{interprocedural} data-flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
 and whose data-flow functions are \textit{distributive}.

### 2015-03-13 sas2015/content/impl.tex
fixes to previous fixes

@@
 \begin{restatable}{lemma}{efficient}\label{lem:efficient}
-  The correlated-call representation of a micro function is efficient according to the IDE criteria and the required operations
+  The correlated-call representation of a micro function is efficient according to the IDE criteria~\cite{sagiv1996precise} and the required operations
   on micro-functions can be computed in time $O(\rcc T)$.

### 2015-03-14 sas2015/content/background.tex
whose domain consists of subsets

@@
 because it constructs summaries of the effects of called procedures.
-The IFDS framework is applicable to \textit{interprocedural} data-flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
+The IFDS framework is applicable to \textit{interprocedural} data-flow problems whose domain consists of \textit{subsets} of a \textit{finite} set $D$,
 and whose data-flow functions are \textit{distributive}.

### 2015-03-14 sas2015/content/impl.tex
Revert "evaluation"
This reverts commit 378e84e1c21b63e748965ae7a167c997cd1ec0b5.

@@
 
-%\subsection{Implementation of the Correlated-Calls Analysis}
-\section{Evaluation}
+\subsection{Implementation of the Correlated-Calls Analysis}
 We implemented the correlated-calls analysis in Scala~\cite{odersky2004overview}. 
@@
 
-The average running time for small programs such as in Figure~\ref{list:ccexample} is ???~seconds.
-On the SPECjvm98 benchmarks, the average running time is ???~seconds.
-So far we were only able to find a practical benefit from the correlated-calls analysis for programs in which correlated calls were ``artificially'' introduced in control-flow paths relevant to the specific client analysis.
-We are still working on identifying in which client IFDS problems, in combination with which benchmarks, we would encounter a precision improvement.
-
 \commentout{

### 2015-03-17 sas2015/content/impl.tex
discuss experimental results

--- 2015-03-13 sas2015/content/impl.tex
@@
 %to the original IFDS analysis.
+
+\subsection{Implementation of the Correlated-Calls Analysis}
+
+We implemented the correlated-calls analysis in Scala~\cite{odersky2004overview}. 
+Our implementation analyzes JVM bytecode compiled from input programs written
+in Java.
+%
+We use WALA~\cite{fink2012wala} to retrieve information about an input program, such 
+as its control-flow supergraph and the set of receivers and their types.
+Since WALA does not contain an implementation of the IDE algorithm,
+we implemented it from scratch.
+We will submit our implementation to the artifact evaluation committee, and are also 
+working on contributing our infrastructure to WALA.
+
+We tested our correlated-calls analysis using an IFDS taint-analysis  
+as a client analysis. To this end, we converted the IFDS taint analysis into an IDE problem with an 
+implementation of $\transCC_\rcc$. We extensively tested the correlated-calls analysis to ensure that, in 
+the absence of correlated calls, the analysis produces the same results as an IFDS-equivalent analysis, and that 
+it produces more precise results in the presence of correlated calls as expected.
+
+To evaluate the practicality of our work, we applied two variants of the IFDS taint analysis
+to the SPEC JVM98 benchmarks: (i) an equivalent IDE taint analysis obtained using $\transEq$, and (ii)
+an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
+calls. Unfortunately, for the specific combination of this IFDS client analysis and these benchmark
+programs, the precise tracking of data flow in the presence of correlated calls does not impact precision. 
+However, the good news is that the running times of the two analyses are roughly the same, ranging from 
+a few seconds on the smaller SPEC programs to about two hours on \texttt{javac} in each cases (see the Appendix
+for more details on these results).  This suggests that the overhead of tracking correlated calls is manageable,
+and that our technique may be worthwhile in other scenarios.
+
+\commentout{
+The artifact of our implementation can be used to solve any IFDS problem.
+In the presence of correlated calls, the result of the correlated-calls analysis can be more precise than the result obtained with an IFDS solver.
+}

### 2015-03-17 sas2015/content/appendix.tex
adding start of table with running times

@@
 \input{tables/stats}
+
+\subsection{Running Times}
+The running times $t_\Subset$ of the correlated-calls and $t_\equiv$ equivalence analyses are shown in Table~\ref{tab:runtimes}.
+In the table, $N^*$ denotes the number of nodes in the control-flow graph of the whole program, $N^*_r$ the number of reachable nodes in the control-flow supergraph, and $N^\#_r$ the number of nodes in the exploded supergraph.
+\input{tables/runstats}
 

### 2015-03-17 sas2015/content/impl.tex
cases -> case

@@
 However, the good news is that the running times of the two analyses are roughly the same, ranging from 
-a few seconds on the smaller SPEC programs to about two hours on \texttt{javac} in each cases (see the Appendix
+a few seconds on the smaller SPEC programs to about two hours on \texttt{javac} in each case (see the Appendix
 for more details on these results).  This suggests that the overhead of tracking correlated calls is manageable,

### 2015-03-17 sas2015/content/appendix.tex
reorder table columns in a logical order

--- 2015-03-09 sas2015/content/appendix.tex
@@
 \input{tables/stats}
+
+\subsection{Running Times}
+The running times $t_\Subset$ of the correlated-calls and $t_\equiv$ equivalence analyses are shown in Table~\ref{tab:runtimes}.
+In the table, $N^*$ denotes the number of nodes in the control-flow graph of the whole program, $N^*_r$ the number of reachable nodes in the control-flow supergraph, and $N^\#_r$ the number of reachable nodes in the exploded supergraph.
+\input{tables/runstats}
 

### 2015-03-17 sas2015/content/appendix.tex
remove total number of nodes column

--- 2015-03-09 sas2015/content/appendix.tex
@@
 \input{tables/stats}
+
+\subsection{Running Times}
+The running times $t_\Subset$ of the correlated-calls and $t_\equiv$ equivalence analyses are shown in Table~\ref{tab:runtimes}.
+In the table, $N^*_r$ the number of reachable nodes in the control-flow supergraph, and $N^\#_r$ the number of reachable nodes in the exploded supergraph.
+\input{tables/runstats}
 

### 2015-03-17 sas2015/content/impl.tex
squeezing text

@@
 
-To evaluate the practicality of our work, we applied two variants of the IFDS taint analysis
+To evaluate the practicality of our approach, we applied two variants of the IFDS taint analysis
 to the SPEC JVM98 benchmarks: (i) an equivalent IDE taint analysis obtained using $\transEq$, and (ii)
 an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
-calls. Unfortunately, for the specific combination of this IFDS client analysis and these benchmark
-programs, the precise tracking of data flow in the presence of correlated calls does not impact precision. 
-However, the good news is that the running times of the two analyses are roughly the same, ranging from 
+calls. 
+The results suggest that the overhead of tracking correlated calls is very minor: the running times of the two analyses are roughly the same, ranging from 
 a few seconds on the smaller SPEC programs to about two hours on \texttt{javac} in each case (see the Appendix
-for more details on these results).  This suggests that the overhead of tracking correlated calls is manageable,
-and that our technique may be worthwhile in other scenarios.
+for detailed results).
+%This suggests that the overhead of tracking correlated calls is manageable,
+%and that our technique may be worthwhile in other scenarios.  
+For the specific combination of this IFDS client analysis and these benchmark
+programs, tracking correlated calls did not impact precision.
 

### 2015-03-17 sas2015/content/appendix.tex
typo

@@
 \subsection{\code{TraversableOnce} Trait from Scala Standard Library}
-Figure~\ref{fig:traversableonce} presents the code from Scala's \code{TraversableOnce} trait discussed in Section~ref{sec:collex}.
+Figure~\ref{fig:traversableonce} presents the code from Scala's \code{TraversableOnce} trait discussed in Section~\ref{sec:collex}.
 

### 2015-03-17 sas2015/content/impl.tex
changes suggested by Frank

@@
 calls. 
-The results suggest that the overhead of tracking correlated calls is very minor: the running times of the two analyses are roughly the same, ranging from 
-a few seconds on the smaller SPEC programs to about two hours on \texttt{javac} in each case (see the Appendix
+The results suggest that the overhead of tracking correlated calls is minor: the running times of the two analyses are roughly the same,
+except on the \texttt{javac} benchmark, where the correlated-calls analysis takes about twice as long as the equivalence analysis.
+The absolute times range from 
+a few seconds on the smaller SPEC programs to about two hours on \texttt{javac} (see the Appendix
 for detailed results).
+Our implementation is a research prototype and many opportunities for
+optimization remain.
 %This suggests that the overhead of tracking correlated calls is manageable,

### 2015-03-17 sas2015/content/background.tex
squishing a single word to get half a page of space
text squeezing

@@
 The correlated-calls analysis works by transforming an IFDS problem to an IDE problem, solving the IDE problem, and transforming the IDE result to a solution to the original IFDS problem.
-This section defines basic terminology and presents the IFDS and IDE algorithms.
+This section defines terminology and presents the IFDS and IDE algorithms.
 %\ftodo{
@@
 \textit{interprocedural} \textit{distributive} \textit{environment}
-problems. An \textit{environment} problem is an analysis whose data-flow
+problems. An \textit{environment} problem is one whose data-flow
 lattice is the lattice $\textsf{Env}(D,L)$ of maps from a finite set $D$ to a meet semilattice

### 2015-03-17 sas2015/content/intro.tex
tweaks to save space
text squeezing

@@
 %
-Section~\ref{sec:cca} presents the correlated-calls transformation
-and sketches a proof of its correctness%
+Section~\ref{sec:cca} presents the correlated-calls transformation,
+sketches a proof of its correctness,%
 \footnote{
@@
   the appendix.
-}.
+} and discusses our implementation.
 %
-Our implementation is discussed in Section~\ref{sec:Evaluation}.
+%Our implementation is discussed in Section~\ref{sec:Evaluation}.
 %
@@
 %
-Finally, conclusions and directions for future work are presented in Section~\ref{sec:Conclusions}.
+Finally, Section~\ref{sec:Conclusions} presents conclusions and directions for future work.

### 2015-03-17 sas2015/content/concl.tex
trimming in conclusions

--- 2015-03-07 sas2015/content/concl.tex
@@
 We present an approach for transforming an IFDS problem into an IDE problem
-in which path feasibility is encoded into the functions that are associated
+in which path feasibility is encoded into functions associated
 with edges in an exploded control-flow supergraph. The solution to this
 IDE problem can be mapped back to the solution space of the original IFDS
-problem, and is more precise for some client programs because the flow of data along
+problem, and is more precise for some client programs because data flow along
 infeasible paths is prevented. We present a formalization of the
-transformation and prove its correctness. We also briefly report on
+transformation, prove its correctness, and briefly report on
 preliminary experiments with our prototype implementation. Full proof
-details are available as supplemental materials with this submission,
+details are available in the Appendix,
 and we plan to submit our implementation and experimental data to the
 artifact evaluation committee. 
+%  
+As future work, it is possible to adapt our approach to work on IDE
+problems. We would convert an initial IDE problem into a more complex IDE problem, 
+such that the solution of the latter generates a more precise
+solution to former, by preventing data flow along infeasible paths.

### 2015-03-17 sas2015/content/background.tex
more text squeezing

@@
 
-In this paper, we denote a map $m$ as a set of pairs of keys and values, in which each key appears at most once.
-For any map $m$,  $m(k)$ is the value paired with the key $k$ in $m$. We denote by $m[x\to y]$ a map that maps $x$ to $y$, and every other key $k$ to $m(k)$.
+We denote a map $m$ as a set of pairs of keys and values, with each key appearing at most once.
+For a map $m$,  $m(k)$ is the value paired with the key $k$. We denote by $m[x\to y]$ a map that maps $x$ to $y$ and every other key $k$ to $m(k)$.
 
@@
 \textit{interprocedural} \textit{distributive} \textit{environment}
-problems. An \textit{environment} problem is one whose data-flow
+problems. An IDE problem is one whose data-flow
 lattice is the lattice $\textsf{Env}(D,L)$ of maps from a finite set $D$ to a meet semilattice
@@
 
-The meet of two environment transformers $t_1, t_2$ can be computed by taking the union of the edges
+The meet of two environment transformers $t_1, t_2$ is computed as the union of the edges
 in their pointwise representations. When the same edge appears in the pointwise representations of
@@
 The IDE algorithm operates on the same exploded supergraph as the IFDS algorithm
-(except that the edges are labelled with micro-functions). For each pair $(n,d)$ of
-node and fact, the algorithm computes a micro-function equal to the meet of the micro-functions
+(but its edges are labelled with micro-functions). For each pair $(n,d)$ of
+node and fact, IDE computes a micro-function equal to the meet of the micro-functions
 of all the realizable paths from the program entry point to the pair.

### 2015-03-17 sas2015/content/impl.tex
text squeezing
more text squeezing

@@
 The IDE algorithm requires an efficient representation of micro-functions.
-The chosen representation needs to support the basic micro-functions that
+The representation must support the basic micro-functions that
 we presented in Section~\ref{seq:transIfdsIde}, and it must
@@
 types. Therefore, the overall worst-case cost of the correlated-calls IDE analysis
-is $O(ED^3\rcc T)$. Note that in practice, $\rcc$ is much smaller
+is $O(ED^3\rcc T)$. In practice, $\rcc$ is much smaller
 than $R$, so Lemma~\ref{lem:onlycorrrec} is significant for 

### 2015-03-17 sas2015/content/impl.tex

@@
 calls. 
-The results suggest that the overhead of tracking correlated calls is minor: the running times of the two analyses are roughly the same,
-except on the \texttt{javac} benchmark, where the correlated-calls analysis takes about twice as long as the equivalence analysis.
+The results suggest that the overhead of tracking correlated calls is acceptable. In particular, the correlated-calls analysis takes at most twice as long as the equivalence analysis.
 The absolute times range from 

### 2015-05-18 sas2015/content/impl.tex
review comments

@@
 We consider two IFDS-to-IDE transformations: an \textit{equivalence transformation} $\transEq$ (pronounced ``t-equiv'') and
-a \textit{correlated-calls transformation} $\transCC$ (pronounced ``t-c-c'').
+a \textit{correlated-calls transformation} $\transCC_S$ (pronounced ``t-c-c'') for a set of receivers $S$.
 Both transformations keep the exploded supergraph $G^\#$ the same, and only generate different edge functions.
@@
 %\paragraph{Lattice Elements}
-In the correlated-calls transformation, the 
+In the correlated-calls transformation $\transCC_R$, the 
 %Just like in the equivalence transformation $\transEq$, the exploded supergraph for $\transCC$ is the same as in the original IFDS problem. The 
@@
     $\lcc=\left\{\,m:\ R\to2^T\right\}$,
-where $R$ is the set of receivers and $T$ is the set of all types.
+where $R$ is the set of considered receivers and $T$ is the set of all types.
 For each receiver~$r$, the map gives an overapproximation of the possible
@@
                 in $f$,
-                and $r\in S$;}}\\
+                and $r\in S$;}}\\[5ex]
             m\left[r\to \bot_T\right],
             &\text{\parbox{75mm}{if $e = n_1 \to n_2$ and $n_1$ contains an assignment
-                    to $r\in S$;}}\\
+                    to $r\in S$;}}\\[2ex]
             m
@@
 \begin{restatable}[Soundness]{lemma}{sound}\label{lem:sound}
-  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, and let $d\in D$.
+  Let $P$ be an IFDS problem and $p=[\startmain,\,\dots,\,n]$ a concrete execution path, and let $d\in D$.
   If $d\in M_F(p)(\varnothing),$
   then
-  $
+  $$
     d\in \backCC\left(\resultIDE(\transCC_R(P))\right)(n)\,.
-  $
+  $$
 \end{restatable}

### 2015-05-18 sas2015/code/ccexample.java

@@ -7,8 +7,8 @@ class B extends A {
     return "not secret";
   } /*@\label{line:Bfoo}@*/
   void bar(String s) {
-    System.out.println(s); 
-  } /*@\label{line:Bbar}@*/
+    System.out.println(s); /*@\label{line:Bbar}@*/
+  } 
 }
 
 class Main {

### 2015-06-08 sas2015/content/appendix.tex
moving table 2 to section 4.7

@@
 \input{tables/stats}
-
-\subsection{Running Times}
-The running times $t_\Subset$ of the correlated-calls and $t_\equiv$ equivalence analyses are shown in Table~\ref{tab:runtimes}.
-In the table, $N^*_r$ the number of reachable nodes in the control-flow supergraph, and $N^\#_r$ the number of reachable nodes in the exploded supergraph.
-\input{tables/runstats}
 

### 2015-06-08 sas2015/content/impl.tex
moving table 2 to section 4.7

@@
 calls.
+
+The running times $t_\Subset$ of the correlated-calls and $t_\equiv$ equivalence analyses are shown in Table~\ref{tab:runtimes}.
+In the table, $N^*_r$ is the number of reachable nodes in the control-flow supergraph, and $N^\#_r$ the number of reachable nodes in the exploded supergraph.
+\input{tables/runstats}
+
 The results suggest that the overhead of tracking correlated calls is acceptable. In particular, the correlated-calls analysis takes at most twice as long as the equivalence analysis.
 The absolute times range from 
-a few seconds on the smaller SPEC programs to about two hours on \texttt{javac} (see the Appendix
-for detailed results).
+a few seconds on the smaller SPEC programs to about two hours on \texttt{javac}.
+
 Our implementation is a research prototype and many opportunities for

### 2015-06-08 sas2015/response.txt
adding reviews and response

We thank the reviewers for their insightful and helpful comments.

Reviewer 1 asks two important questions: why we are comparing the correlated-calls (CC) analysis to the equivalence-IDE analysis, and why do we not compare the CC analysis to the IFDS analysis instead. 
We will emphasize in the revised version that the equivalence analysis is there for two reasons: 
i) to explain how a CC-IDE problem can be derived from an IDE problem that has the same meaning as the original IFDS problem; 
ii) to provide a base line against which to compare the efficiency of the CC analysis. 
We compare the efficiency of the CC-analysis against the equivalence-IDE analysis instead of the IFDS analysis because the time complexities of an IFDS and an equivalent IDE analysis are the same: an equivalent IDE analysis is just an IFDS analysis in which all edges are labeled with identity micro functions, and all operations on those functions are optimized to be constant-time. We will also add this clarification to Section 4.7.

Reviewer 1 mentions that in Table 2, it would be useful to include numbers to reflect the exact precision improvement of the correlated-calls analysis. As we discussed in Section 4.7, for the particular combination of taint analysis and the SPEC JVM’97 benchmarks, we did not observe a gain in precision. These numbers were presented to show that the running time of the analysis is reasonable. Reviewer 1 also suggests moving Table 2 to Section 4.7; we will do so if space permits.

Reviewer 2 points out interesting related work by Isil Dillig on data-flow analysis that handles missing libraries. We will read and address this work in the Related Work section. We will also revise that section to include a more detailed comparison to context sensitivity, as Reviewer 3 requests, in particular related to the Cartesian Product Algorithm.

Reviewer 1 and 3 made several insightful suggestions to improve the readability of the paper. We will address minor issues (clarifications, notation, and formatting) in the revised version.

### 2015-06-08 sas2015/content/related.tex
added CPA reference

@@
 Our approach superficially resembles, but is orthogonal, to context
-sensitivity, including such variations as object sensitivity~\cite{DBLP:conf/issta/MilanovaRR02,DBLP:journals/tosem/MilanovaRR05}.
+sensitivity, including the CPA algorithm~\cite{Agesen:95} and such variations as object sensitivity~\cite{DBLP:conf/issta/MilanovaRR02,DBLP:journals/tosem/MilanovaRR05}.
 Context-sensitive

### 2015-06-08 sas2015/content/related.tex
tweak

--- 2015-03-12 sas2015/content/related.tex
@@
 
-Our approach superficially resembles, but is orthogonal, to context
-sensitivity, including such variations as object sensitivity~\cite{DBLP:conf/issta/MilanovaRR02,DBLP:journals/tosem/MilanovaRR05}.
+Our approach superficially resembles, but is orthogonal to, context
+sensitivity, including the CPA algorithm~\cite{Agesen:95} and such variations as object sensitivity~\cite{DBLP:conf/issta/MilanovaRR02,DBLP:journals/tosem/MilanovaRR05}.
 Context-sensitive

### 2015-06-16 sas2015/content/background.tex
corrections

@@
 can be decomposed into its effect on $\top_{\textsf{Env}}$ and on a set of environments $\top_{\textsf{Env}}[d_i\to l]$
-that map every element to $\top$ except one ($d_i$):
+that map every element to $\top$ except one ($d_i$). Formally,
 \[
@@
     together represent the environment transformer 
-    $\lambda e.e[r \to \lambda m.\bot \sqcap \lambda m.m]$.
+    $\lambda e.e[\texttt{ret} \to \lambda m.\bot \sqcap \lambda m.m]$.
 
     To eliminate infeasible paths due to correlated calls, we encode the taint
-    analysis using environments $\textsf{Env}(D,L)$, where $D$ is the set of
+    analysis using environments $e\in\textsf{Env}(D,L)$, where $D$ is the set of
     variables and $L$ is a map from receiver variables to sets of possible

### 2015-06-16 sas2015/content/impl.tex
corrections

@@
 infeasible. Therefore, an IDE solution $\rho$ computed using
-$\transCC_S$ is converted to an IFDS solution as:
-$\backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}$.
+$\transCC_S$ is converted to an IFDS solution as
+\begin{equation}
+	\backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.\label{eq:transCcDef}
+\end{equation}
 
@@
 To evaluate the practicality of our approach, we applied two variants of the IFDS taint analysis
-to the SPEC JVM98 benchmarks: (i) an equivalent IDE taint analysis obtained using $\transEq$, and (ii)
-an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
+to the SPEC JVM98 benchmarks: 
+\begin{enumerate}[(i)]
+	\item an equivalent IDE taint analysis obtained using $\transEq$, and
+	\item an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
 calls.
+\end{enumerate}
+The equivalence analysis is there for two reasons: 
+\begin{enumerate}[(i)]
+	\item  to explain how a correlated-calls-IDE problem can be derived from an IDE problem that has the same meaning as the original IFDS problem; 
+	\item (ii) to provide a base line against which to compare the efficiency of the correlated-calls analysis.
+\end{enumerate}
+We compare the efficiency of the correlated-calls analysis against the equivalence-IDE analysis instead of the IFDS analysis because the time complexities of an IFDS and an equivalent IDE analysis are the same: an equivalent IDE analysis is just an IFDS analysis in which all edges are labeled with identity micro functions, and all operations on those functions are optimized to be constant-time.
 

### 2015-06-16 sas2015/content/related.tex
corrections

--- 2015-03-12 sas2015/content/related.tex
@@
 
-Our approach superficially resembles, but is orthogonal, to context
-sensitivity, including such variations as object sensitivity~\cite{DBLP:conf/issta/MilanovaRR02,DBLP:journals/tosem/MilanovaRR05}.
+Our approach superficially resembles, but is orthogonal to, context
+sensitivity, including the CPA algorithm~\cite{Agesen:95} and such variations as object sensitivity~\cite{DBLP:journals/tosem/MilanovaRR05}.
 Context-sensitive

### 2015-06-16 sas2015/content/concl.tex
adding techreport and paper

@@
 preliminary experiments with our prototype implementation. Full proof
-details are available in the Appendix,
+details are available in the \reportOrAppendix,
 and we plan to submit our implementation and experimental data to the

### 2015-06-16 sas2015/content/impl.tex
adding techreport and paper

--- 2015-06-08 sas2015/content/impl.tex
@@
 on $I$ and $U$.
-The proofs of all of the lemmas and theorems are in the Appendix.
+The proofs of all of the lemmas and theorems are in the \reportOrAppendix.
 
@@
 To evaluate the practicality of our approach, we applied two variants of the IFDS taint analysis
-to the SPEC JVM98 benchmarks: (i) an equivalent IDE taint analysis obtained using $\transEq$, and (ii)
-an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
+to the SPEC JVM98 benchmarks: 
+(i) an equivalent IDE taint analysis obtained using $\transEq$, and
+(ii) an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
 calls.
+
+The equivalence analysis is there for two reasons: 
+(i)  to explain how a correlated-calls-IDE problem can be derived from an IDE problem that has the same meaning as the original IFDS problem, and 
+(ii) to provide a base line against which to compare the efficiency of the correlated-calls analysis.
+
+We compare the efficiency of the correlated-calls analysis against the equivalence-IDE analysis instead of the IFDS analysis because the time complexities of an IFDS and an equivalent IDE analysis are the same: an equivalent IDE analysis is just an IFDS analysis in which all edges are labeled with identity micro functions, and all operations on those functions are optimized to be constant-time.
 

### 2015-06-16 sas2015/content/intro.tex
review comments
corrections
adding techreport and paper

@@
 Section~\ref{sec:cca} presents the correlated-calls transformation, 
-sketches a proof of its correctness,%
+states the correctness properties%
 \footnote{
   Detailed proofs of our lemmas and theorems can be found in
-  the appendix.
-} and discusses our implementation.
+  the \reportOrAppendix.
+}, and discusses our implementation.
 %

### 2015-06-16 sas2015/content/impl.tex
applying Frank's comments

--- 2015-06-08 sas2015/content/impl.tex
@@
 Since WALA does not contain an implementation of the IDE algorithm,
-we implemented it from scratch.
-We will submit our implementation to the artifact evaluation committee, and are also 
-working on contributing our infrastructure to WALA.
+we implemented it from scratch;
+%We will submit our implementation to the artifact evaluation committee, 
+we are working on contributing our infrastructure to WALA.
 
@@
 To evaluate the practicality of our approach, we applied two variants of the IFDS taint analysis
-to the SPEC JVM98 benchmarks: (i) an equivalent IDE taint analysis obtained using $\transEq$, and (ii)
-an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
+to the SPEC JVM98 benchmarks: 
+(i) an equivalent IDE taint analysis obtained using $\transEq$, and
+(ii) an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
 calls.
+
+The equivalence analysis is there for two reasons: 
+(i)  to explain how a correlated-calls-IDE problem can be derived from an IDE problem that has the same meaning as the original IFDS problem, and 
+(ii) to provide a base line against which to compare the efficiency of the correlated-calls analysis\footnote{
+We compare the efficiency of the correlated-calls analysis against the equivalence-IDE analysis instead of the IFDS analysis because the time complexities of an IFDS and an equivalent IDE analysis are the same: an equivalent IDE analysis is just an IFDS analysis in which all edges are labeled with identity micro functions, and all operations on those functions are optimized to be constant-time.
+}.
 
@@
 programs, tracking correlated calls did not impact precision.
-
-\commentout{
-The artifact of our implementation can be used to solve any IFDS problem.
-In the presence of correlated calls, the result of the correlated-calls analysis can be more precise than the result obtained with an IFDS solver.
-}

### 2015-06-18 sas2015/content/example.tex
applying Frank's comments
fixing appendix sentence

@@
 Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis.
-The results are shown in Table~\ref{tab:dacapostat} in the Appendix.
+The results are shown in\techreport{ Table~\ref{tab:dacapostat} in } the~\reportOrAppendix.
 
@@
 The relevant code from \textsf{TraversableOnce} and other related traits is shown
-in Figure~\ref{fig:traversableonce} in the Appendix.
+\techreport{in Figure~\ref{fig:traversableonce} }in the \reportOrAppendix.

### 2015-06-18 sas2015/content/impl.tex
squeezing

@@
 $\transCC_S$ is converted to an IFDS solution as
+\vspace{-.4cm}
 \begin{equation}
@@
 (i)  to explain how a correlated-calls-IDE problem can be derived from an IDE problem that has the same meaning as the original IFDS problem, and 
-(ii) to provide a base line against which to compare the efficiency of the correlated-calls analysis\footnote{
+(ii) to provide a base line against which to compare the efficiency of the correlated-calls analysis%\footnote{
 We compare the efficiency of the correlated-calls analysis against the equivalence-IDE analysis instead of the IFDS analysis because the time complexities of an IFDS and an equivalent IDE analysis are the same: an equivalent IDE analysis is just an IFDS analysis in which all edges are labeled with identity micro functions, and all operations on those functions are optimized to be constant-time.
-}.
+%}
+.
 
@@
 In the table, $N^*_r$ is the number of reachable nodes in the control-flow supergraph, and $N^\#_r$ the number of reachable nodes in the exploded supergraph.
+\vspace{-.7cm}
 \input{tables/runstats}

### 2015-06-19 sas2015/content/impl.tex
fix sentence punctuation

--- 2015-06-16 sas2015/content/impl.tex
@@
 (ii) to provide a base line against which to compare the efficiency of the correlated-calls analysis.
-
+%\footnote{
 We compare the efficiency of the correlated-calls analysis against the equivalence-IDE analysis instead of the IFDS analysis because the time complexities of an IFDS and an equivalent IDE analysis are the same: an equivalent IDE analysis is just an IFDS analysis in which all edges are labeled with identity micro functions, and all operations on those functions are optimized to be constant-time.
+%}
 

### 2015-06-19 sas2015/content/concl.tex
add funding acknowledgement

--- 2015-03-17 sas2015/content/concl.tex
@@
 preliminary experiments with our prototype implementation. Full proof
-details are available in the Appendix,
-and we plan to submit our implementation and experimental data to the
-artifact evaluation committee. 
+details are available in the \reportOrAppendix.
 %  
@@
 solution to former, by preventing data flow along infeasible paths.
+
+\paragraph{Acknowledgement.}
+This research was supported by the Natural Sciences and Engineering
+Research Council of Canada and the Ontario Ministry of Research and
+Innovation.

### 2015-06-19 sas2015/main.tex
minor changes
Revert moving eval into its own file
This reverts part of commit f0c85eb906134e1e78bd74221291d1eb96851932.
adding techreport and paper
moving bibliography to prev page
applying Frank's comments
add technical report number as subtitle
move acknowledgement to footnote on first page to save space

--- 2014-12-17 main.tex
@@
-\documentclass[runningheads,a4paper]{llncs}
-
 \usepackage{style/packages}
@@
 
-\title{Precise Data Flow Analysis\\in the Presence of Correlated Method Calls}
+\title{Precise Data Flow Analysis\\in the Presence of Correlated Method Calls\footnote{This research was supported by the Natural Sciences and Engineering Research Council of Canada and the Ontario Ministry of Research and Innovation.}}
 \titlerunning{Data Flow Analysis in the Presence of Correlated Calls}
+\techreport{\subtitle{David R. Cheriton School of Computer Science Technical Report CS-2015-07}}
 
@@
 
+%\author{\institute{}}
+
 \pagenumbering{arabic}
@@
 \input{content/impl}
-%\input{content/datastr}
-%\input{content/eval}
+%\input{content/old/datastr}
+%\input{content/old/eval}
 \input{content/related}
@@
 
-\bibliographystyle{plain}
+\vspace{.8cm}
+\makeatletter
+\patchcmd{\@makeschapterhead}{\vskip40}{\vskip10}{}{}
+\makeatother
+
+\bibliographystyle{myplain}
+\begingroup
+\let\clearpage\relax
 \bibliography{bib/ref}
+\endgroup
 
-\input{content/appendix}
+\techreport{\newpage\input{content/appendix.tex}}
 \end{document}

### 2015-06-19 sas2015_final/content/abstract.tex
creating final version without comments and redundant files

--- 2015-03-08 sas2015/content/abstract.tex
@@
 	transform an IFDS problem into an \textit{Interprocedural Distributive 
-	Environment} (IDE) problem, in which edge functions ``filter out'' data flow 
+	Environment} (IDE) problem, in which edge functions filter out data flow 
 	along infeasible paths. A solution

### 2015-06-19 sas2015_final/content/appendix.tex
creating final version without comments and redundant files

--- 2015-06-08 sas2015/content/appendix.tex
@@
 \begin{proof}
-   % OL: Can't we just say the following?
    First, we need to show that for all $r\in R$, if $I(r)=I'(r)$ and $U(r)=U'(r)$, then $\denote{\setpair IU}=\denote{\setpair{I'}{U'}}$. Indeed, we can see that
@@
 
-%OL: Again, we can keep it simpler:
 For the other direction:
@@
 \end{align*}
-%\mtodo{I agree that this is much better than what I had. I think from $I(r) = I(r) \cap I'(r)$ we can conclude that $I(r)=I'(r)$.}
-%\otodo{No. {1,2} = {1,2} \cap {1,2,3}, but {1,2} is not equal to {1,2,3}.}
 Symmetrically, we can also establish that $\forall r.I'(r) \subseteq I(r)$ by applying the functions to $I'$ instead of to $I$. Therefore, $I = I'$.
@@
 \equalComp*
-%\otodo{The (m)(r) does not seem necessary. Can we replace $r'$ with $r$ and $m'$ with $m$?}
 \begin{proof}
@@
     \item All operations can be computed in $O(\rcc\times T)$ time.
-%Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
     \item The space bound is $O(\rcc\times T)$.\qedhere
@@
 As previously we will denote the top element in the environment lattice as~$\top_\textsf{Env}$.
-%\otodo{I've been using $\top_\textsf{Env}$ for clarity.}
 
@@
 Then, according to~\eqref{eq:envTransToEdgeFnEdge},
-%\mtodo{Is it okay that in~\eqref{eq:envTransToEdgeFnEdge}, we use $\edgefn$, and below we use $\ccedgefn R$?}
-%\otodo{Yes, that's fine.}
   \begin{align*}
@@
     The fact that $\mpd(r)\ne\top_T$ means that there exists a realizable path corresponding to the fact $d$ along path $p$, and, by definition, $d$ must be contained in $M_F(p)(\varnothing)$.
-    %\mtodo{Is this hand-wavy?}
-    %\otodo{No, I think it's fine.}
 \end{proof}
@@
 \begin{proof}
-    %\otodo{It's Section 3.2.}
-    %\mtodo{Section 3.2 talks about the IFDS algorithm, but it doesn't explicitly say how the result of an IFDS analysis looks like and doesn't introduce the notation $\resultIFDS$.}
   Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
@@
 
-%\otodo{restate the lemma before the proof}
 \onlycorrrec*
@@
 
-  \commentout{
-  \begin{align*}
-    \backCC(\resultIDE\left(\transCC_R(P)\right))
-    &=\left\{(n,\,D_n^\Subset(\resultIDE(\transCC_R(P))))\ |\ n\in N^*\right\}.
-  \end{align*}
-  According to~\eqref{eq:dnq} and~Lemma~\ref{lem:recindep}, for a given $n\in N^*$,
-  \begin{align*}
-    D_n^\Subset&(\resultIDE(\transCC_R(P))))\\
-    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall r\in R:\ \left\{(r,\,\resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r))\ |\ r\in R\right\}(r)\ne\top_T\right\}\\
-    &=\left\{d\ |\ d\in\mvp F(n)\,\wedge\,\forall\bm{r\in R}:\ \resultIDE(\transCC_{\{r\}}(P))(n,\,d)(r)\ne\top_T\right\}.
-  \end{align*}
-  }
 Since, according to Lemma~\ref{lem:ccrectop}, $\resultIDE(\transCC_{\{r\}}(P))(n)(d)(r)$ can only be equal to $\top_T$ when $r\in\rcc$, we can conclude that

### 2015-06-19 sas2015_final/content/background.tex
creating final version without comments and redundant files

--- 2015-06-16 sas2015/content/background.tex
@@
 \section{Background}\label{sec:bg}
-%The purpose of the correlated-calls analysis is to solve IFDS problems more precisely than using the standard IFDS algorithm by ruling out some infeasible paths.
-The correlated-calls analysis works by transforming an IFDS problem to an IDE problem, solving the IDE problem, and transforming the IDE result to a solution to the original IFDS problem.
 This section defines terminology and presents the IFDS and IDE algorithms.
-%\ftodo{
-  %Shall we add a sentence saying that readers familiar with these algorithms may skip this section?
-%}
 
 \subsection{Terminology and Notation}
-%We will start by introducing several concepts used by the IFDS and IDE analyses.
-%\begin{mdelete}\mtodo{We already say (but less precisely) what a CFG is in the introduction.}
 The \textit{control-flow graph} of a procedure is a directed graph whose nodes are instructions, which contains an edge from $n_1$ to $n_2$ whenever
@@
 to the site of the most recent call that has not yet been matched by a return. 
-%\ftodo{Can we explain/define the notion of the ``most recent unmatched call'' more precisely?}
 The set of all valid paths from the program entry point to
@@
 The IFDS framework~\cite{reps1995precise} is a precise and efficient algorithm for data-flow analysis
-%. IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and
 that has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
@@
 The input to the IFDS algorithm is specified as
-%Formally, a data-flow analysis problem is suitable for an IFDS analysis if it can be encoded as an IFDS problem
   $(G^*,\,D,\,F,\,M_F,\,\sqcap)$,
@@
 $\mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top_\textsf{Env})$,
-%\mtodo{Should it be $\Omega$ instead of $\top$?}
 where $\top_\textsf{Env} = \lambda d.\top$ is the top element of the lattice of environments,
@@
 as exploded supergraph edges labelled with micro-functions.
-%\mtodo{Should we cite the ``Practical extensions'' paper here that talks about the on-demand IFDS algorithm?}
 Specifically,
@@
 $\textsf{EdgeFn}((n,\,d),\,(n',\,d'))$ returns the micro-function that appears on the exploded supergraph edge $e$.
-%Like in the IFDS algorithm,
 In an implementation, it can be convenient to split the function $\textsf{EdgeFn}$ into separate functions that handle the cases when $n\to n'$ is an intraprocedural edge, a call-to-return edge, a call-to-start edge, or an end-to-return edge.

### 2015-06-19 sas2015_final/content/example.tex
creating final version without comments and redundant files

--- 2015-06-18 sas2015/content/example.tex
@@
 Figure~\ref{list:ccexample} shows a small Java program.
-%that we will use to illustrate
-%how our technique improves the precision of a simple taint analysis.
 The program
@@
 \code{foo()} and \code{bar()} that are overridden in \code{B}.  
-%To keep the 
-%example small and self-contained, it is 
 We assume  that secret values are created by 
@@
 line~\ref{line:Afoo}. 
-%Furthermore, it is assumed that 
 Any write to standard output 
-%via calls \code{System.out.println()} such as the one in method \code{B.bar()} 
-%on line~\ref{line:Bbar} 
 is assumed to be a sink (e.g., the call to \code{System.out.println()} in \code{B.bar()}).
-%a security-sensitive operation.
 Depending on the number of 
 arguments passed to the program, the \code{main()} method of the example program creates 
-either an \code{A}-object or a \code{B}-object%
-%on line~\ref{line:createObject}
-. The 
+either an \code{A}-object or a \code{B}-object. The 
 program then calls \code{foo()} on this object
 on line~\ref{line:callfoo}, which is 
-followed by a call to \code{bar()} on the same object%
-%on line~\ref{line:callbar}
-.
+followed by a call to \code{bar()} on the same object.
 
-%The specific question that we would like to answer for the example program of
-%Figure~\ref{list:ccexample} is the following:
 We wish to answer the following question: Is it possible for the untrusted value 
-that is read on line~\ref{line:Afoo} to flow to the print statement% %on line~\ref{line:Bbar}
-?
-%To determine whether such a flow of tainted data is possible,
+that is read on line~\ref{line:Afoo} to flow to the print statement?
 Consider the control-flow
@@
 
-\commentout{
-In summary, the example discussed in this section shows how the precision of 
-IFDS-based taint analysis can be improved by taking into account how paths
-become infeasible in the presence of correlated calls. In particular, we have
-shown how a false positive reported by a standard IFDS-based algorithm is eliminated.
-}
 While the discussion in this section has focused on the specific problem of taint analysis,
@@
 In these programs, on average, 3\% of all call sites $C$ are polymorphic call sites $C_P$.
-%\mtodo{Should we explain in a footnote why the number of polymorphic call sites is so low?}
-%\otodo{We don't have an explanation.}
 Out of these polymorphic call sites, a significant fraction (39\%) are correlated 
@@
 \inputMintedNoLNs{scala}{collectionsExample.scala}
-%\otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
 When \code{this} refers to an iterator rather than a collection, the call to \code{this.size}
@@
 code is guarded with a test: \code{if (this.isTraversableAgain) ...}
-%\inputMintedNoLNs{scala}{isTraversable.scala}
 When the \code{isTraversableAgain} method returns false, as it does for

### 2015-06-19 sas2015_final/content/impl.tex
creating final version without comments and redundant files

--- 2015-06-19 sas2015/content/impl.tex
@@
-  \commentout{
-%\otodo{The following definitions are very general, and not related to the transformation. Can we move them somewhere earlier?}
-\paragraph{Edge Functions}\label{sec:ef}
-
-Let $\mathcal F$ be the set of methods in a program with a signature $s_\mathcal F$.
-\begin{definition}
-  Let $r.c()$ be a call site on a receiver $r\in R$ with runtime type $t\in T$.
-  Let~$s_\mathcal F$ be the method signature corresponding to the call $c()$.
-  For $s_\mathcal F$ and $t$, a \textit{lookup function} returns the method implementation $f\in\mathcal F$ to which the call $r.c()$ is dispatched:
-  \begin{equation}
-    \textsf{lookup}(s_\mathcal F,\,t)=f.
-  \end{equation}
-\end{definition}
-
-\begin{definition}
-  For a method signature $s_\mathcal F$ and a method implementation $f\in\mathcal F$, the static-type function $\tau$ returns the set of types for which the lookup function yields $f$:
-  \begin{equation}
-    \tau(s_\mathcal F,\,f)=\{\,t\ |\ \textsf{lookup}(s_\mathcal F,\,t)=f\}\,.
-  \end{equation}
-\end{definition}
-In other words, $\tau$ computes the set of types for which calls to methods
-with signatures~$s_\mathcal F$ are dispatched to~$f$.
-
-If there is a supergraph path from a method call with signature $s_\mathcal F$ to the start of $f$, then the set $\tau(s_\mathcal F,\,f)$ is always non-empty.
-
-\begin{definition}\label{def:momopoly}
-  A call site is called monomorphic if it can be dispatched to only one method. If a call site can be dispatched to more than one method it is called polymorphic.
-\end{definition}
-
-  Let $r.c()$ be a call on a receiver $r\in R$ with a method signature $s_\mathcal F$ to a function $f\in\mathcal F$.
-  If the call site is monomorphic, then $\tau(s_\mathcal F,\,f)$ contains all types $T'\subseteq T$ that are compatible with the static type of $r$.
-  If the call site is polymorphic, then $\tau(s_\mathcal F,\,f)\subset T'$, since some types $t\in T'$ cause dispatch to a method other than $f$.
-  }
-
-\commentout{
-%\otodo{incorporate into previous section}
-\subsection{Defining IFDS and IDE Problems}
-%In Section~\ref{sec:bg}, we defined what IFDS and IDE problems are, their applications, and their constraints. In this section, we describe how to create instances of IFDS and IDE problems.
-
-\subsubsection{Defining an IFDS Problem}\label{sec:ifdsdef}
-Recall that an IFDS problem instance is defined as a five-tuple
-\[
-    (G^*,\ D,\ F,\ M_F,\,\sqcap)\,,
-\]
-where $G^*=(N^*,\,E^*)$ is the control-flow supergraph of the program, $D$ is the set of data-flow facts, $F\subseteq2^D\to2^D$ is a set of distributive data-flow functions, and the function $$M_F:\,E^*\to(2^D\to2^D)$$ maps the supergraph edges to data-flow functions, and is extended to paths by composition.
-
-In practice, an IFDS problem can be defined by providing an exploded supergraph
-$G^\#=(N^\#,\,E^\#)$.
-Each node of $G^\#$ is a pair $(n,\ d)$, where $n\in N^*$ is a node in the control-flow supergraph and $d\in (D\cup\{\mathbf{0}\}),\ \mathbf0\notin D$, where $\mathbf0$ is an auxiliary fact that is necessary for the IFDS algorithm.
-
-The meaning of an edge in the exploded supergraph is the following.
-Let $(n_1,\,d_1)$ and $(n_2,\,d_2)$ be two nodes in the exploded supergraph $G^\#$.
-Furthermore, assume that if fact $d_1$ at node~$n_1$ holds, then the fact~$d_2$ at node~$n_2$ also holds.
-Then there is an edge $(n_1,\,d_1),\,(n_2,\,d_2)\in E^\#$.
-
-\subsubsection{Defining an IDE Problem}\label{sec:defide}
-An IDE problem instance is a four-tuple
-\[
-    (G^*,\ D,\ L,\ \menv),
-\]
-where $G^*$ and $D$ are defined in the same way as for IFDS.
-$L$ is a finite-height lattice that represents the values to which data-flow facts are mapped in an IDE problem.
-An environment $Env(D, L)$ maps data-flow facts to lattice elements.
-Finally, the map $$M_{\textsf{Env}}:\,E^*\to(\textsf{Env}(D, L)\to \textsf{Env}(D, L))$$ is a function from the control-flow-supergraph edges to environment transformers, extended to paths by composition.
-
-An IDE problem can be defined with a labeled exploded supergraph\footnote{
-    The exploded supergraph in an IDE problem is defined in the same way as in an IFDS problem.
-The only difference is that the $\mathbf0$ fact is denoted as $\Lambda$~\cite{reps1995precise,sagiv1996precise}.
-}, in which an edge function
-\begin{equation}
-  \edgefn:\ E^\#\to(L\to L)
-\end{equation}
-pairs edges with \textit{micro functions}, and is extended to paths by composition.
-
-The set of micro functions of an IDE problem is a subset of $L\to L$ that is closed under function meet and composition.
-
-The meaning of an edge in the labeled exploded supergraph is the following. Let $e=((n_1,\,d_1),\,(n_2,\,d_2))\in E^\#$ be an edge in the exploded supergraph with label $f=\mathsf{EdgeFn}(e)$. Then
-\begin{itemize}
-	\item the fact that $d_1$ holds at node $n_1$ implies that $d_2$ holds at $n_2$;
-  \item if at node $n_1$ the fact $d_1$ was mapped to a lattice element $l_1$ by an environment $Env(D,\,L)$, then the fact $d_2$ at node $n_2$ should be mapped to $f(l_1)$.
-\end{itemize}
-
-As shown in~Sagiv et al.~\cite{sagiv1996precise}, the relationship between environment transformers and edge functions can be described with the following equations.
-For individual edges $(n_1,\,n_2)\in E^*$,
-\begin{align}\label{eq:envTransToEdgeFnEdge}
-  \menv&((n_1,\,n_2))(\textsf{env})(d)\notag\\
-  &=\edgefn((n_1,\,\mathbf0),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,,
-\end{align}
-where $\textsf{env}$ is an environment $\textsf{Env}(D,\,L)$.
-Informally, for a given control-flow-supergraph edge $e$ and data-flow fact $d$, the $M_\textsf{Env}$ function captures the meet of the edge function applied to all possible exploded-graph edges along $e$.
-
-For paths $p$ that start with the entry point~$\startmain$,
-\begin{equation}\label{eq:envTransToEdgefn}
-  \menv(p)(\Omega)(d)=\bigsqcap_{r\in\mathsf{RP}(p,\,d)}\edgefn(r)(\top)\,,
-\end{equation}
-where $n\in N^*$, $d\in D$, $p\in\ivp(n)$, and $\mathsf{RP}$ is the set of all interprocedurally realizable paths.
-
-To summarize, an IDE problem can be defined by a labeled exploded supergraph 
-\begin{equation}(G^\#,\,L,\,\mathsf{EdgeFn})\,,\end{equation}
-where each edge of the exploded supergraph corresponds to a micro function.
-}
-
 \section{Correlated Calls Analysis}\label{sec:cca}
-%The correlated-calls analysis is a transformation from an arbitrary IFDS problem to a corresponding IDE problem.
-The solution of this IDE problem can be converted to a solution of the original IFDS problem.
-The converted IFDS result can be more precise than the original IFDS result because it avoids infeasible paths corresponding to correlated calls.
-
-%In this section, we first discuss what is necessary to define IFDS and IDE problems.
-Next we describe how to convert any IFDS problem into an equivalent IDE problem, and, given a solution to the generated IDE problem, how to obtain the result of the original IFDS problem.
-We then show how to transform an IFDS problem into an IDE problem using the correlated-calls transformation, and how to convert the solution to the latter IDE problem into a more precise IFDS result.
 
@@
 
-%The correlated-call analysis transforms an existing IFDS problem into a special kind of IDE problem. We described what is necessary to define IFDS and IDE problems independently.
-
-%Let $P=(G^\#)$ be an IFDS problem and $Q=(G^\#,\,\edgefn)$ an IDE problem obtained by a conversion from $P$.
 Let $G^\#$ be the exploded supergraph of an arbitrary IFDS problem. A \emph{transformation}
@@
 
-%In each case we also show how to convert the result of the generated IDE problem to a result of the original IFDS problem.
+\subsubsection{Equivalence Transformation}\label{sec:equivtrans}
 
-%An overview of the transformations is shown in Figure~\ref{fig:transformations}.
-
-\subsubsection{Equivalence Transformation}\label{sec:equivtrans}
-%We start with an equivalence transformation $\transEq$ to present a simple IFDS-to-IDE conversion that does not change the result of the original IFDS problem.
-We will compare the correlated-calls transformation with the equivalence transformation, and use the latter to show  that the correlated-calls analysis results in a
-%precision improvement of the original IFDS problem result.
-
-%\paragraph{Converting IFDS problems to IDE problems}
-%Since IDE is a generalization of IFDS, any IFDS problem can be converted into an equivalent IDE problem~\cite{sagiv1996precise}.
 The lattice
@@
 the fact $d$ reachable. All other micro-functions are the identity function.
-%\mtodo{``the identity function'' or is it okay ot just say ``the identity''?}.
-\commentout{
-The equivalence transformation is thus defined as:
-  $\transEq((G^\#))=(G^\#,\,L^\equiv,\,\mathsf{EdgeFn}^\equiv)$.
-}
-
-%Thus, in $\transEq$, all non-diagonal edges in the original IFDS problem are mapped to identity functions.
 
@@
 
-%To improve the precision of an IFDS problem, we can convert it to a special type of IDE problem, and use lattice elements to provide us with additional information about a node.
-%When converting the IDE result to an IFDS result, lattice elements will tell us whether to make the corresponding exploded nodes reachable. This is the idea of the correlated-calls analysis.
-
-%\paragraph{Lattice Elements}
 In the correlated-calls transformation $\transCC_R$, the 
-%Just like in the equivalence transformation $\transEq$, the exploded supergraph for $\transCC$ is the same as in the original IFDS problem. The 
 lattice elements are maps from receivers to sets of types:
@@
 
-\commentout{
-The type power set $2^T$ is also a lattice with a bottom element 
-\begin{align*}
-\bot_T&=T
-\intertext{and top element}
-\top_T&=\varnothing.
-\intertext{The top element of the function lattice}
-\topcc&=\lambda r.\top_T
-\intertext{is a function that maps any receiver to the empty set\footnote{%
-  We prove that $\lcc$ is a lattice in the Proof of Lemma~\ref{lem:efficient}%
-}. 
-The bottom element}
-\botcc&=\lambda r.\bot_T
-\end{align*}
-maps any receiver to all types in the program.
-
-To understand the meaning of lattice elements in a correlated-call analysis, suppose that an IFDS problem has been converted to an IDE problem using the correlated-calls transformation. 
-Assume also that $s$ is the entrypoint of the program, $n$ is a node in the exploded supergraph, and that in the IDE result, $n$ is mapped to a lattice element $l\in \lcc$. 
-Then the purpose of $l$ is to provide information about the set of types of the objects that may be referenced by each receiver at runtime at a path from $s$ to $n$. 
-If a receiver is mapped to the empty set $\top_T$, it means that for the given program point, the receiver cannot reference an object of any type.
-In other words, the corresponding data-flow fact is considered not reachable.
-}
-
-%\paragraph{Micro Functions}\label{sec:micro}
-%Unlike in the equivalence transformation, the micro functions returned by the edge function $\edgefn^\Subset$ are not always identity functions.
-
 A micro-function $f\in\lcc\to \lcc$ defines how the map from receivers to types should
@@
 of a supergraph edge $e$ is defined as:
-                    %\otodo{define $n_1(e)$ globally somewhere early on, and consider using a more decriptive name like src instead of $n_1$}
+
   \begin{align}\label{eq:varepsilon}
@@
 
-%Let $e=(n_1,\,n_2)\in E^\#$ be an edge in the exploded supergraph.
-%$\edgefn^\Subset(e)$ returns a micro function $f\subset\lcc\to \lcc$.
-%Given a micro function (a map from receivers to sets of types) $m\in \lcc$, $f(m)$ returns a new map from receivers to sets of types.
-%In other words, $f$ shows how to update the map from receivers to sets of types when we encounter program point $n_1$.
-
-%Let $f_1$ and $f_2$ be two micro functions such that ${f_1=\lambda m\,.\,\lambda r\,.\,t_1(r)}$ and ${f_2={\lambda m\,.\,\lambda r\,.\,t_2(r)}}$.
-We define the meet operation on micro-functions as follows:
-%\begin{equation}\label{eq:micromeet}
-  %\lambda m\,.\,\lambda r\,.\,t_1(r)\sqcap\lambda m\,.\,\lambda r\,.\,t_2(r)
-  %=\lambda m\,.\,\lambda r\,.\,t_1(r)\cup t_2(r)\,.
-%\end{equation}
-%
-%The composition of micro functions is defined as ordinary function composition.
-
 We can now define $\edgefn$, which assigns a micro-function to each edge in
@@
 Along a $\mathbf0$-edge, the micro function is the identity. 
-%All other functions can be described with $\varepsilon_S$.
 On a ``diagonal'' edge from $\mathbf0$ to a non-$\mathbf0$ fact that corresponds
 to some data-flow fact becoming reachable, $\varepsilon_S(e)$ is applied to
-%the initial map
 $\botcc$ that maps every receiver to an object of every possible type.
-%conservatively allows every receiver to point to an object of any type.
 On all other edges, $\varepsilon_S(e)$ is applied to the existing map before the edge.
@@
   \end{equation}
-  %We define both $\ccedgefn S$ and $\varepsilon_S$ to be extended to paths by composition.
 \end{definition}
@@
   Consider the program from Figure~\ref{list:ccexample}, whose exploded supergraph appeared in Figure~\ref{fig:cc_edgefn_example}.
-%
   Returning a secret value in method \code{A.foo} creates a ``diagonal'' edge from the $\mathbf0$-fact to the method's return value $r$. 
   The diagonal edge is labeled with $\lambda m\,.\,\botcc$, so every receiver is mapped to the set of all types~$\bot_T$.
-%  
 On the end-return edge from \code{A.foo} to \code{main}, the set of types of \code{a} is restricted by the micro function $\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code A\}]$ corresponding to the assignment of the return value $r$ to \code v.
-%
-%Similarly,
 On the call-start edge from \code{main} to \code{B.bar}, the possible types
@@
 types of \code{a}, indicating that this
-%data-flow
 path 
-%that would
-%result in an information leak 
 is 
-%actually
 infeasible.
 \end{example}
-
-%After we have shown the definitions for the meet and composition operations, we will show in Example~\ref{ex:cc} how the correlated-calls analysis uses the presented micro functions to detect infeasible paths.
-
-\commentout{
-Finally, the correlated-calls transformation is defined as
-    \begin{equation}
-      \transCC_S((G^\#))=\left(G^\#,\,\lcc_S,\,\ccedgefn S\right).
-    \end{equation}
-}
-
-%Then, for an edge $e$, the correlated-call micro functions can be defined as $\ccedgefn R$ and a correlated-calls transformation is defined as $\transCC_R$.
 
@@
 to a set of facts $d$ that may be reached at $n$.
-%\otodo{This seems wrong: Why is it $N^*$ for IFDS and $N$ for IDE? And shouldn't
-    %it be $N \to 2^D$, since you get a set of $d$'s?}
 An IDE solution $\resultIDE$
@@
 is $N^* \to (D \to L)$.
-
-%For each program point $n$, the result of an IFDS analysis gives
-%a set of facts $d$ that may be reached at $n$. The result of an IDE analysis
-%pairs each such fact~$d$ with a lattice element $\ell$. Formally,
-%for an IFDS problem $P$, the result $\resultIFDS$ has type
-%$N^* \to D$.
-%Similarly, for an IDE problem $Q$, the result $\resultIDE(Q)$
-%has type $N \to (D \to L)$.
 
@@
   $\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}$.
-%a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
-%is converted to an IFDS result as follows:
-%\begin{equation}\label{eq:transEqDef}
-  %\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
-%\end{equation}
-%
-%\otodo{I don't understand this comment. What does it mean?}
-%
 In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
@@
 
-%a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
-%converted to an IFDS result as follows:
-%\begin{equation}\label{eq:transCcDef}
-    %\backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.
-%\end{equation}
-%\otodo{In Equation (5), I changed $\rho(n)(d)$ to $\rho(n)(d)(r)$, because I think
-%    the original was incorrect. Marianna, please check that this correction is correct.}
-
-\commentout{
-
-The output of an IFDS analysis states whether a node is reachable in the exploded supergraph.
-This means that for an IFDS problem $P$, the IFDS-analysis result $\resultIFDS(P):\ N^*\to 2^D$ is a map from nodes of the control-flow supergraph to sets of facts:
-\begin{equation}
-  \resultIFDS(P)=\{(n,\,\mvp F(n))\,|\,n\in N^*\}\,.
-\end{equation}
-
-\begin{mdelete}
-\begin{example}\label{ex:ifdsresult}
-  The solution to the taint-analysis IFDS problem $\mathcal P$ in Figure~\ref{list:examplejava} whose exploded supergraph is presented in Figure~\ref{fig:exampleexploded} looks as follows:
-  \small\begin{align*}
-    \resultIFDS(\mathcal P)=\{&(\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\{\texttt a\}),
-      &(\highlight{\textsf{start}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
-      &\qquad\qquad(\highlight{\textsf{return}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
-%      
-      &(\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\{\texttt a\}),
-      &(\highlight{\texttt{if(s==null)}}{lightsalmonpink},\,\{\texttt s\}),
-      &\qquad\qquad(\highlight{\texttt{return r}}{lightsalmonpink},\,\{\texttt r,\,\texttt s\}),\\
-%
-      &(\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\{\texttt a,\,\texttt b\}),
-      &(\highlight{\textsf{call}_\texttt f}{lightsalmonpink},\,\{\texttt s\}),
-      &\qquad\qquad(\highlight{\textsf{end}_\texttt f}{lightsalmonpink},\,\{\texttt r,\,\texttt s\})\}.\\
-%
-      &(\highlight{\textsf{end}_\texttt{main}}{greyblue},\,\{\texttt a,\,\texttt b\}),&(\highlight{\texttt{return s}}{lightsalmonpink},\,\{\texttt s\}),
-  \end{align*}\normalsize
-  All other nodes of the control-flow supergraph are mapped to the empty set.
-\end{example}
-\end{mdelete}
-
- The IDE analysis associates a lattice element with each node in the exploded supergraph.
-For an IDE problem $Q$, the result $\resultIDE(Q):\ N^\#\to L$ maps nodes of the exploded supergraph to lattice elements (see~\eqref{eq:mvpdef}):
-\begin{equation}\label{eq:ideresult}
-  \resultIDE(Q)=\{((n,\,d),\,\mvp{\textsf{Env}}(n,\,d))\ |\ n\in N^*,\,d\in D\}\,.
-\end{equation}
-In other words, for each fact $d\in D$ at a given node $n\in N^*$, $\resultIDE(Q)(n,\,d)$ returns a lattice element. If a fact $d\in D$ is unreachable, $\resultIDE(Q)(n,\,d)=\top$.
-
-In the case of an equivalence transformation from IFDS to IDE, if a node in the IFDS result is reachable, it will be also reachable in the IDE result, and it will be mapped to the bottom lattice element.
-For an exploded node in the IDE result, being mapped to the top element means being not reachable.
-
-The~domain of an equivalence-IDE result 
-\begin{equation}
-  \resultEq=\resultIDE(\transEq(P))
-\end{equation}
-consists of pairs of control-flow-supergraph nodes and data-flow facts.
-The range of the result is the set of lattice elements.
-To transform an IDE result to an IFDS result, we need to map each control-flow-supergraph node to the set of facts with which it is paired, provided that the pair is mapped to the bottom lattice element.
-
-\begin{mdelete}
-\begin{example}\label{ex:ideresult}
-  Converting the IFDS problem $\mathcal P$ from Example~\ref{ex:ifdsresult} into an equivalent IDE problem and solving it will yield the following result:
-    \small\begin{align*}
-    \resultIDE(\transEq(\mathcal P))=\{&((\highlight{\textsf{return}_\texttt{secret}}{greyblue},\,\texttt a),\,\bot),\\
-      &((\highlight{\textsf{call}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
-      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt a),\,\bot),\\
-      &((\highlight{\textsf{return}_\texttt{A.f}}{greyblue},\,\texttt b),\,\bot),\\
-      &\dots\}.\\
-    \end{align*}\normalsize
-  Suppose that for a pair $(n,\,d)$, where $n\in N^*$ and $d\in D$, there is no corresponding result in ~$\resultIFDS(\mathcal P)$ (see Example~\ref{ex:ifdsresult}).
-Then $(n,\,d)$ appears in $\resultIDE(\transEq(\mathcal P))$ as $((n,\,d),\,\top)$.
-\end{example}
-\end{mdelete}
-
-Let $\rho$ be the result of an equivalence-IDE analysis for an IFDS problem $P$:
-\[
-  \rho=\resultIDE(\transEq(P)).
-\]
-For a node $n\in N^*$, let $D_n^\equiv(\rho)$ be a set of data-flow facts such that
-\begin{equation}
-  D_n^\equiv(\rho)=\{d\ |\ d\in D\,\wedge\,\rho(n,\,d)\ne\top\}\,.
-\end{equation}
-Then the transformation function
-$\backEq:\,(N^\#\to L)\to(N^*\to2^D)$
-from an IDE result to~an~IFDS result looks as follows:
-\begin{equation}
-  \backEq\left(\rho\right)=
-    \left\{(n,\,D_n^\equiv(\rho))\ |\ n\in N^*\right\}\,.
-\end{equation}
-
-Obviously, if applied to the result of an equivalence-IDE problem, $\backEq$ returns a result equivalent to the original IFDS problem result.
-In other words, for any IFDS problem $P$ with supergraph $N^*$, and any node $n\in N^*$,
-\begin{equation}
-  \backEq\left(\resultIDE(\transEq(P))\right)(n)=\resultIFDS(P)(n)\,.
-\end{equation}
-
-\begin{example}
-  Converting the result in Example~\ref{ex:ideresult} with the equivalence-transformation from an IDE result to an IFDS result $\backEq$ will yield the same result as in Example~\ref{ex:ifdsresult}.
-\end{example}
-
-Let $P$ be an IFDS problem. 
-Let $E:\,N\times D$ be the domain of the IDE result $\resultIDE(Q)$.
-To convert $\resultIDE(\transCC_R(P))$ to an IFDS result, we need to map the control-flow-supergraph nodes $n\in N^*$ to the corresponding facts $d\in D$. 
-Unlike in~$\backEq$, we will only map each~$n$ to the facts~$d$ for~which~$\resultIDE(\transCC_R(P))(n,\,d)$ does not contain an~empty mapping for~any~receiver.
-
-For a node $n\in N^*$ and a correlated-calls IDE problem result $\rho=\resultIDE(\transCC_S(P))$, let $D_n^\Subset(\rho)$ be a set of data-flow facts defined as
-\begin{equation}\label{eq:dnq}
-  D_n^\Subset(\rho)=\left\{d\ |\ 
-    d\in\mvp F(n)\,\wedge\,\forall r\in R:\ \rho(n,\ d)(r)\ne\top_T\right\}.
-\end{equation}
-Then, for a set $S\subseteq R$, the~correlated-calls-conversion function from a~correlated-calls IDE~result $\rho$ to~an~IFDS~result looks as~follows:
-\begin{equation}\label{eq:ucc}
-  \backCC\left(\rho\right)=
-    \left\{(n,\,D_n^\Subset(\rho)\ | \ n\in N^*\right\}.
-\end{equation}
-}
-
 \subsection{Implementation of Correlated Calls Micro-Functions}
-%\otodo{move material from following section here}
 
@@
 
-%We define the meaning $\denote{\setpair{I}{U}}$
-%of a representation $\setpair{I}{U}$ as follows: 
-%In words, the micro-function represented by $\setpair{I}{U}$ takes an existing map $m$
-%from receivers to sets of types, and returns a map that maps each receiver $r$ to
-%the set $m(r)$ given by the original map $m$ intersected with $I(r)$ and unioned
-%with $U(r)$.
-
 All of the basic micro-functions defined in Definition~\ref{def:microfn} can be expressed
@@
 
-%The implementation of function application follows directly from the definition of
-%the representation: $\setpair{I}{U}(m) = \lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
-%\mtodo{Should this be the denotation of $\setpair IU$?}
-%\otodo{No. It is an implementation of the apply operation.}
-
-%To compare two micro-functions for equality, it suffices to compare the corresponding
-%sets $I(r)$ and $U(r)$ for all receivers $r$. The following lemma shows that this
-%implementation of comparison corresponds to equality of the represented micro-functions:
 \begin{restatable}{lemma}{equalEq}
@@
 
-%The following lemma shows that this implementation corresponds to the composition
-%of the denoted functions.
 \begin{restatable}{lemma}{equalComp}\label{lem:equalComp}
@@
 
-%The following lemma shows that this implementation corresponds to the meet
-%of the denoted functions:
 \begin{restatable}{lemma}{equalMeet}\label{lem:equalMeet}
@@
 paths that are actually feasible.
-%that the result of an IDE problem obtained through a correlated-calls transformation removes only facts that occur on infeasible paths.
 
@@
 \end{definition}
-%In other words, a correlated-call receiver is a receiver that has at least two polymorphic call invocations.
-%We will denote the set of correlated-call receivers as $\rcc$.
 
@@
 micro-functions to be defined only on correlated-call receivers.
-%We will describe a ``reduced'' correlated-calls transformation in which we only consider receivers from $\rcc$ and ignore other receivers of $R$.
 Specifically, a ``reduced'' correlated-calls transformation that
@@
 (i.e. no precision is lost).
-%We will show that IDE problems obtained through ordinary and reduced correlated-calls transformations yield the same results.
-%In other words, we show that if a correlated-calls analysis considers only correlated-call receivers, no precision is lost.
 
@@
 
-\commentout{
-To summarize, Lemma~\ref{lem:sound} shows that the result of a correlated-calls analysis is sound since it overapproximates the data flow of all possible concrete execution paths.
-We have also shown in Lemma~\ref{lem:subsetifds} that for an IFDS problem $P$, the correlated-calls analysis improves the precision of the original IFDS result $\resultIFDS(P)$, because the correlated-calls result $\resultIDE(\transCC(P))$ underapproximates an equivalence-IDE result $\resultIDE(\transEq(P))$.
-Finally, we showed in Lemma~\ref{lem:onlycorrrec} that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result that is obtained when considering all receivers $R$.
-}
-
-%This is the general idea of the correlated-calls analysis.
-The analysis involves a transformation from IFDS to IDE problems.
-To implement an IDE problem, it is necessary to define a representation of lattice elements and micro functions.
-An efficient representation of those data structures for the correlated-calls analysis is presented in the next section.
-
 \subsection{Efficiency}
-%\otodo{Sagiv et al. define a notion of an ``efficient'' implementation of micro-functions.
-%    If the micro-functions are ``efficient'', then the asymptotic complexity bounds proven by
-%    Sagiv hold. Our implementation is ``efficient'' if we assume that the number of correlated
-%    receivers is a constant independent of the size of the program. That seems a stretch. If
-%    it's linear in the size of the program, then we would need to add a factor to their complexity
-%    bounds. Their bound is $O(ED^3)$, while ours would be $O(ED^3R)$. But then we can't directly use their complexity proof; we would have to adapt it.
-%    I'm leaning towards leaving out any mention of ``efficient'' implementation.}
 
@@
 
-%\otodo{Give the list of criteria explicitly in the proof in the appendix.}
-%\begin{enumerate}
-	%\item There is a representation for the identity and top functions.
-  %\item The representation is closed under the meet and composition operations.
-  %\item The micro functions form a finite-height lattice.
-  %\item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
-  %\item There is a constant bound on the storage space for a micro function representation.
-%\end{enumerate}
-%We prove these conditions with the following lemma:
 \begin{restatable}{lemma}{efficient}\label{lem:efficient}
@@
 \end{restatable}
-
-%From this lemma, we conclude that the correlated-calls analysis runs in time
-%$O(ED^3\rcc T)$. In other words, the asymptotic cost of the added precision of
-%the correlated-calls analysis is increased by a factor of $O(\rcc T)$ compared
-%to the original IFDS analysis.
 
@@
 in Java.
-%
 We use WALA~\cite{fink2012wala} to retrieve information about an input program, such 
@@
 we implemented it from scratch;
-%We will submit our implementation to the artifact evaluation committee, 
 we are working on contributing our infrastructure to WALA.
@@
 (ii) to provide a base line against which to compare the efficiency of the correlated-calls analysis.
-%\footnote{
 We compare the efficiency of the correlated-calls analysis against the equivalence-IDE analysis instead of the IFDS analysis because the time complexities of an IFDS and an equivalent IDE analysis are the same: an equivalent IDE analysis is just an IFDS analysis in which all edges are labeled with identity micro functions, and all operations on those functions are optimized to be constant-time.
-%}
 
@@
 optimization remain.
-%This suggests that the overhead of tracking correlated calls is manageable,
-%and that our technique may be worthwhile in other scenarios.  
 For the specific combination of this IFDS client analysis and these benchmark

### 2015-06-19 sas2015_final/content/intro.tex
creating final version without comments and redundant files

--- 2015-06-16 sas2015/content/intro.tex
@@
 
-\commentout{
-Data-flow analysis computes an approximation of how values may flow  
-through a program, and has applications in compiler optimization, 
-programming tools, and computer security, and many other areas.
-Data-flow analyses operate on \textit{control-flow graphs} (CFGs)
-that model 
-the order in which the instructions of a program are executed. This is
-typically done by associating \textit{flow functions} that represent how 
-data is propagated with the edges of the CFG.  A 
-\textit{confluence operator} specifies how the data facts that have been 
-computed along different paths should be merged when the paths join.
-}
-
-%Since a CFG is an over-approximation of the possible flows 
 A control-flow graph (CFG) is an over-approximation of the possible flows 
@@
 is a general data-flow analysis algorithm that 
-%by  Reps, Horwitz, and Sagiv
-%is a general data-flow analysis
-%algorithm
-%for computing solutions to finite distributive data-flow problems such 
-%that can be instantiated to solve problems such
-%as reaching definitions, available expressions, and taint analysis.
-%A distinguishing 
-%characteristic of IFDS is that it
 avoids infeasible interprocedural paths in which calls 
-and returns to/from functions are not properly matched. %Sagiv, Reps, and Horwitz
-%also presented
+and returns to/from functions are not properly matched. 
 The \textit{Interprocedural Distributive Environment} (IDE) algorithm~\cite{sagiv1996precise}
 has the same property, but
-%that similarly only considers properly matched call/return
-%edges, but that 
 supports a broader range of data-flow problems.
-%by expanding the 
-%domain of flow functions to \textit{environments} that go beyond the data-flow facts 
-%considered by IFDS.
 
@@
 methods are dynamically dispatched on the same receiver object.
-%\mtodo{Should we define the term ``receiver''?}
-%In such cases,
 If the
@@
 (i.e., the method invoked depends on the run-time type of the receiver),
-%(i.e., if they dispatch to different method definitions 
-%depending on the type of the receiver expression at run time),
 then their dispatch 
@@
 but did not present any concrete algorithm to take advantage of it.
-%, and we are not aware 
-%of any existing data-flow analysis that is capable of avoiding infeasible paths that arise 
-%in the presence of correlated method calls.
-% (see Section~\ref{sec:Related} for a discussion
-%of related work).
 
-%\input{figures/fig-transformation}
-
-%The approach taken in our work is to 
 Our approach transforms an IFDS problem into an
@@
 the IFDS algorithm to the original problem.
-%
 We present a formalization of the transformation and prove its correctness:
@@
 correlated calls.
-%as follows. 
-%First, we derive an IDE problem that is equivalent to the original IFDS problem,
-%as described by Reps et al.~\cite{sagiv1996precise}.
-%Solving this ``Equivalence-IDE Problem'' with the IDE algorithm yields a result that
-%is equivalent to the one obtained by applying the IFDS algorithm to the original IFDS problem.
-%Then, we derive a ``Correlated-Calls 
-%IDE Problem'' from the original IFDS problem and show 
-%that the solution to this problem, when converted to an IFDS result, is more precise
-%than the original IFDS result.
-%We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
-%This is illustrated schematically
-%in Figure~\ref{fig:transformations}%
-%\footnote{ 
-%  The labels %$\resultIDE$, $\resultIFDS$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$
-%  on edges in 
-%  Figure~\ref{fig:transformations} reflect a number of mappings and %projections 
-%  that will be defined in Section~\ref{sec:cca} and that can be %ignored here.
-%}.
 
@@
 
-%We also report on preliminary experiments in which our correlated-calls transformation
-%is applied to an IFDS formulation of a simple taint analysis. Our results show that
-%solving the resulting IDE problem avoids infeasible paths due to correlated calls as
-%expected.
-%
-%In summary, the contributions of this paper are as follows:
-%\begin{itemize}
-%  \item
-%    We present a general approach for transforming IFDS problems into corresponding
-%    IDE problems that avoid infeasible paths due to correlated method calls and
-%    prove its correctness. 
-%  \item
-%    We implemented the approach in Scala, on top of the WALA program analysis framework
-%    and report on preliminary experiments. 
-%\end{itemize}
-
 The remainder of this paper is organized as follows.
-%
 Section~\ref{sec:MotivatingExample} presents a motivating example.
-%
 Section~\ref{sec:bg} reviews the IFDS and IDE algorithms.
-%
 Section~\ref{sec:cca} presents the correlated-calls transformation, 
@@
 }, and discusses our implementation.
-%
-%Our implementation is discussed in Section~\ref{sec:Evaluation}.
-%
 Related work is discussed in Section~\ref{sec:Related}.
-%
 Finally, Section~\ref{sec:Conclusions} presents conclusions and directions for future work.

### 2015-06-19 sas2015_final/content/related.tex
creating final version without comments and redundant files

--- 2015-06-16 sas2015/content/related.tex
@@
   \label{sec:Related}
-%\otodo{Should we remove first initials in this section?}
 The IFDS algorithm is an instance of the functional approach to data-flow analysis developed by Sharir and Pnueli~\cite{pnueli1981two}.
-\commentout{
-Their algorithm is based on computing \textit{summary functions} that return the data-flow value at the end of a procedure, given the data-flow value at the start of the procedure.
-IFDS problems form a more restricted set of data-flow problems: unlike in the functional approach, IFDS flow functions have to be distributive, and the set of data-flow facts $D$ has to be finite.
-However, the IFDS algorithm is more general than Sharir's and Pnueli's algorithm in that it can handle programs containing local variables and parameters in recursive methods.
-}
-IFDS has been used to encode a variety of data-flow problems such as typestate analysis%
-\commentout{(determining which operations can be performed on an object at a given program point)}~\cite{naeem2008typestate,DBLP:conf/pldi/ZhangMGNY14} and shape analysis%
-\commentout{(detecting errors and validating properties of programs at compile time)}%
+IFDS has been used to encode a variety of data-flow problems such as typestate analysis~\cite{naeem2008typestate,DBLP:conf/pldi/ZhangMGNY14} and shape analysis%
 ~\cite{DBLP:conf/birthday/KreikerRRSWY13}. IFDS has been used~\cite{DBLP:conf/pldi/ArztRFBBKTOM14,tripp2009taj} and extended~\cite{DBLP:conf/sigsoft/LerchHBM14} to solve taint-analysis problems.
-
-%The IFDS algorithm is implemented in two popular static-analysis frameworks for Java bytecode, the T.J.~Watson Libraries for~Analysis (WALA)~\cite{fink2012wala} and Heros~\cite{bodden2012inter}.
-
-\commentout{
-WALA is a framework for static analysis on Java bytecode developed by the IBM T.J.~Watson Research Center.
-In the implementation of our work, we use WALA to build and traverse the supergraph (a special kind of control-flow graph) of a Java program\footnote{However, we do not use WALA's IFDS implementation, as explained in~Section~\ref{chapter:eval}.}.
-
-Soot is a framework for program analysis and optimization on Java bytecode, developed by the Sable Research Group at McGill University.
-Unlike WALA, Soot also has an implementation of the IDE algorithm.
-The IFDS and IDE implementations for Soot are part of the Heros project~\cite{bodden2012inter}.
-
-Whereas one advantage of Soot's IFDS implementation (and other static analysis tools) is ease of use and extensibility, WALA's primary focus is efficiency.
-For example, WALA uses bit-vectors to represent some of the analysis data types, like local variables and parameters.
-Another difference is that WALA's intermediate representation of a program uses static single assignment (SSA) form~\cite{cytron1991efficiently}.
-SSA form is a representation of the program in which each variable has only one definition (assignment).
-SSA can make data-flow analysis simpler and more efficient~\cite{appel1998ssa}.
-}
 
@@
 
-\commentout{
-Work on improving the IFDS algorithm includes the Practical Extensions to the IFDS algorithm~\cite{naeem2010pei}.
-\commentout{The paper presents four extensions to the IFDS algorithm.}
-Two of the four extensions improve the efficiency of the IFDS analysis for certain classes of IFDS problems. Another extension widens the class of problems applicable for the IFDS analysis. 
-\commentout{However, those extensions do not affect the precision of IFDS problems.}
-Our analysis, in contrast, does not improve the efficiency or generality of IFDS, but it allows us to solve IFDS problems more precisely.
-The fourth extension is targeted towards programs that are represented in SSA form.
-Executing the IFDS analysis on such programs results in loss of precision in the presence of control-flow constructs (e.g.
-conditionals and loops), compared to programs in non-SSA form.
-The extension makes the IFDS analysis on programs in SSA form as precise as on programs that are not represented in SSA form.
-In contrast, the correlated-calls analysis is applicable to programs in both SSA and non-SSA forms.
-Even if applied to a program in SSA form, our analysis and the extension improve the precision of IFDS in unrelated situations: the first analysis handles correlated calls, and the latter handles control-flow constructs.
-Thus, an IFDS analysis could benefit from both precision improvements independently.
-}
-
 Bodden et~al.~\cite{bodden2013spl} presents a framework
@@
 Rodriguez and Lhot\'ak evaluate a parallelized implementation of the IFDS algorithm using actors~\cite{rodriguez2010concurrent} that can take advantage of multiple processors.
-%However, neither of those works is concerned with improving the precision of IFDS results.
-
-\commentout{
-The correlated-calls analysis improves the precision of a data-flow analysis by eliminating a special type of infeasible paths.
-This is similar to the idea of context-sensitive analysis: just as a context-sensitive analysis eliminates infeasible paths from the end of a procedure to the call sites that do not match the given procedure call, the correlated-calls analysis eliminates infeasible paths caused by correlated method calls.
-}
 
@@
 of an object. 
-%Unlike in more static languages,
-%property names in JavaScript are first class values (strings). When a loop indexed by
-%property names updates the properties of objects, the loop body is extracted into a function
-%and analyzed context sensitively with a separate context for each property name.
 The approach differs from ours in that it targets points-to analysis rather
@@
 and in that it employs context sensitivity to improve precision.
-
-\commentout{
-The idea of eliminating infeasible paths caused by correlated calls is similar to M.~Sridharan et~al.'s work on improving the precision of pointer analysis for JavaScript programs~\cite{DBLP:conf/ecoop/SridharanDCST12}.
-For each pointer, a pointer analysis determines the possible set of objects (the \textit{points-to} set) that the pointer can reference at a given program point.
-In JavaScript, it is challenging to compute the points-to set of fields because in general, field names can be derived from arbitrary expressions and bound at runtime.
-As a result, an imprecise data-flow analysis will include infeasible paths between values of the form \verb'o[p]' (access of a property \verb'p' of object \verb'o'), where at compile time, \verb'p' can be bound to different values.
-The idea of the paper is to track all dynamic property accesses (reads and writes) on an object \verb'o' with property name \verb'p'.
-The code snippets containing the references \verb'o[p]' are then extracted into a separate function $f$.
-The analysis is then run so that for each possible value of \verb'p', $f$ is analyzed separately; therefore, for a given property name, all correlated objects with that name are analyzed together.
-
-The differences between this method of tracking correlated calls and our analysis are the following.
-\begin{itemize}
-  \item \textit{Type of target data-flow analysis} whose precision is to be improved.
-Our analysis improves the precision of IFDS data-flow analyses, whereas the JavaScript analysis improves the precision of pointer analysis.
-  \item \textit{Target language}. Our analysis is for object-oriented languages where polymorphic methods, and not property names (which are known at compile time), cause infeasible paths.
-  \item \textit{Different handling of correlated calls}.
-Extracting code that contains correlated calls into separate methods would not prevent infeasible paths.
-Instead, our analysis uses IDE flow functions to detect and eliminate infeasible paths caused by correlated calls.
-\end{itemize}
-}
 

### 2015-06-19 sas2015_final/code/ccexample.java

@@ -1,0 +1,21 @@
+class A {
+  String foo { return secret(); } /*@\label{line:Afoo}@*/
+  void bar(String s) {} /*@\label{line:Abar}@*/
+}
+class B extends A {
+  String foo {
+    return "not secret";
+  } /*@\label{line:Bfoo}@*/
+  void bar(String s) {
+    System.out.println(s); /*@\label{line:Bbar}@*/
+  } 
+}
+
+class Main {
+  static void main(String[] args) {
+    A a = (args == null) /*@\label{line:createObject}@*/
+        ? new A() : new B(); 
+    String v = a.foo(); /*@\label{line:callfoo}@*/
+    a.bar(v); /*@\label{line:callbar}@*/
+  }
+}
